### 2022-09-11 master_thesis_version/main.tex
basic setup

\documentclass{report}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{nicematrix}
\usepackage{subcaption}
\usepackage{pdfpages}
\usepackage{algpseudocode}
\DeclareMathOperator*{\argmin}{arg\,min}

\usepackage{listings}
\lstset { %
    language=C++,
    backgroundcolor=\color{white}, % set backgroundcolor
    numbers=none,
    frame=shadowbox,
    basicstyle=\footnotesize,% basic font setting
}

\NiceMatrixOptions{cell-space-top-limit = 4pt}
\NiceMatrixOptions{cell-space-bottom-limit = 4pt}

\usepackage{bm}
\usepackage{appendix}

\newtheorem{definition}{Definition}
\newtheorem{proposition}{Proposition}
\newtheorem*{remark}{Remark}

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{tcolorbox}
\tcbuselibrary{theorems}
\newtcbtheorem
  []% init options
  {tcb-def}% name
  {Definition}% title
  {%
    colback=green!5,
    colframe=green!35!black,
    fonttitle=\bfseries,
  }% options
  {def}% prefix
\newtcbtheorem
  []% init options
  {tcb-prop}% name
  {Proposition}% title
  {%
    colback=blue!5,
    colframe=blue!80!black,
    fonttitle=\bfseries,
  }% options
  {prop}% prefix

\usepackage{natbib}
\usepackage[figurename=Fig.,tablename=Tab.,labelfont={bf}]{caption}
\usepackage{listings}
\usepackage{tikz}
\usetikzlibrary{positioning, decorations.markings, arrows, intersections}
\bibliographystyle{apalike}
\setcitestyle{authoryear,open={(},close={)}} %Citation-related commands
\usepackage[linkbordercolor=green]{hyperref}
\usepackage{geometry}
\geometry{a4paper,scale=0.8}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}

\lstset{style=mystyle}

\newcommand{\mathcolorbox}[2]{\colorbox{#1}{$\displaystyle #2$}}
\newcommand{\note}[1]{{\footnotesize \textcolor{blue}{[\textbf{#1}]}}}

\title{\textbf{Asymptotic-preserving Plasma Model in 3D}}
\author{Tianwei Yu}
\date{\today}

\begin{document}

\begin{titlepage}
\noindent \includegraphics[]{ETHlogo.pdf}

\centering
\vspace*{7cm}

\textbf{\LARGE Asymptotic-Preserving Plasma Model in 3D}

\vspace{3cm}
\large

Master thesis

\vspace{0.25cm}

\textbf{Tianwei Yu}

\vspace{0.25cm}

\today

\vspace{7cm}

Supervisor: Prof. Dr. Ralf Hiptmair

\vspace{0.25cm}

Department of Mathematics, ETH Z\"{u}rich

\end{titlepage}

\chapter*{Abstract}
Plasma physics involves complex phenomena characterized by multiple scales, for example, the propagation of electromagnetic fields, the interaction between charged particles and electromagnetic fields, and the drift of fluids. To numerically simulate plasmas, discretization schemes that can automatically adapt to the scale of interest and remain stable regardless of the system scales are desirable. In this thesis, we discuss asymptotic-preserving (AP) schemes for the Euler-Maxwell system parametrized by the dimensionless Debye length $\lambda$ in a 3D setting for multi-species plasma modeling. The key capability of the AP scheme is the uniform performance, in the sense of stability and convergence, for a series of problems that are parametrized by arbitrary $\lambda$ and constitute a singular perturbation as $\lambda \rightarrow 0$. As the first part of the thesis, the AP property, still being a vague concept throughout literature, is clarified by two aspects: asymptotic-stability and asymptotic-consistency, which respectively refer to the unconditional stability on the asymptotic parameter and the convergence of the limit scheme to the limit model. Two propositions discussing some sufficient conditions for general AP schemes are presented, hopefully providing deeper insights into the AP property and some guidance for devising AP schemes. In the sequel, we reproduce the results in \cite{degond_2012}, based on which we extend the 1D two-fluid discrete Euler-Maxwell model to a more general model in a 3D setting that involves multiple species, friction terms, and possibly other source terms. The 3D discrete model for the Euler-Maxwell system is implemented based on the frameworks of Finite Volume Method (FVM) and Finite Integration Technique (FIT) for the Euler system and the Maxwell system respectively. Details about the procedure of time-stepping and the assembly of the linear system due to implicitness are provided. An essential aspect lies in the choice of right boundary conditions that are compatible with both non-limit and limit models. The discrete model is tested on a case that is adapted from \cite{fuchs_2021} due to the difficulty arising from the insulating solid domain. As verification, the scheme is checked on the subsystems and is compared with the corresponding 1D discrete model. The numerical results on the fully-coupled system with $\lambda$ ranging in $[0,1]$ manifest a continuous transition from the non-neutral model ($\lambda = \mathcal{O}(1)$) to the quasi-neutral model ($\lambda = 0$), which, as well as the convergence of the solutions over time, implies that the scheme is AP.

\chapter*{Acknowledgements}
First, I would like to extend my deepest gratitude to my supervisor Prof. Ralf Hiptmair. His proposal for this thesis combines fluid dynamics, a topic that I am familiar with, and electromagnetism, a completely new world for me. With reasonable amounts of theoretical and implementation work, I had much fun in the process of freely exploring the knowledge and accomplishing the task step by step. His constant and insightful input was always inspiring at the moment when I was lost. In a word, it was a pleasant, adventurous, and memorable journey.

My appreciation also goes to Dr. Roman Fuchs, who gave me a lot of guidance on familiarizing myself with the topic and the underlying C++ code. I would also like to acknowledge the help of my colleague Langwen Huang in the configuration of the running environment on the cluster, which potentially saved me considerable time.

Meanwhile, I would like to thank my girlfriend, friends, and flatmates for their company and support during the thesis work as well as my Master's life. I wish them all a bright future.

In the end, I would like to express my special gratitude to my parents for their financial support and emotional care. They are always my strongest back no matter what setbacks I encounter.

\tableofcontents
\chapter{Introduction}
\section{Plasma}
Often described as the fourth state of matter, plasma is an ionized gas phase substance that consists of positively-charged \emph{ions}, negatively-charged \emph{electrons} and neutrally-charged atoms. Although plasmas seem to be intangible in our daily life, most of the material in the universe is in the plasma state \citep{gurnett2005}. They are largely associated with various astrophysical phenomena like sunspots, solar flares, planetary radiation belts. Regarding terrestrial plasmas, they can be found or exploited in many situations, for instance, lightning, gas-discharge lamps, controlled thermonuclear fusion.

A plasma is classically defined as \emph{a quasi-neutral gas of charged particles showing collective behavior} \citep{chen_1994}. The \emph{collective} behavior arises due to the long-range nature of $1/r$ Coulumb potential \citep{gibbon2020}. Besides, the dynamics of plasma particles are largely determined by an internally-driven electromagnetic field, in the sense that the charges generate an electric field, and carry an electric current that induces a magnetic field. In contrast, a gas in a neutral state is largely characterized by inter-particle collision. The second key feature, \emph{quasi-neutrality}, refers to the tendency to keep the overall charges neutral in the scale of the Debye length $\lambda_D$, which is an important plasma parameter and will be elucidated in the later section.

In classical plasma theory, three criteria must be satisfied to distinguish plasmas from ionized gases \citep{chen2016}. First, the quasi-neutrality requires that the Debye length $\lambda_D$ is much smaller than the system scale $L$. Second, to make the quasi-neutrality a statistically valid concept, the number $N_D$ of particles in a ``Debye sphere ", namely $N_D := n4/3\pi\lambda_D^3$ with $n$ being the number density of particles, must be large enough. The third criterion states the dominance of the electromagnetic forces over the hydrodynamics forces in driving the motions of particles.

\subsection{Fluid model}
To describe the dynamics of plasmas, a natural and extremely precise way is to treat it as a collection of particles and to monitor the positions and velocities of each particle, namely \emph{N-body dynamics}. It has been proven powerful in analytically describing effects relevant to plasmas \citep{escande2015}.  However, a typical plasma density might be $10^{18}$ particles per $m^3$ \citep{chen2016}, which is way far from affordable for today's computers if one attempts to numerically simulate it. Therefore, relatively crude models are necessary for plasma simulations. The \emph{kinetic model} is another successful tool to describe plasmas. It compiles the state of a collection of particles in the form of probabilistic distributions of velocity and usually consists of the Vlasov-Maxwell equations with velocity distribution functions as variables. See \cite{chaudhary2018} for details on the kinetic description of plasmas.

An even simpler model, \emph{fluid model}, described by the Euler-Maxwell equations, can be derived by taking the moments of the Vlasov-Maxwell equations supplemented with some closure assumption. Specifically, we take the velocity distribution to be $Maxwellian$, by which the distribution can be characterized by its moments. In this way, the fluid model describes the evolution of the moments, e.g. number density, drift velocity, pressure, rather than the distribution. Such a treatment reduces the complexity of the system at the cost of some information. This bridging between the fluid model and the kinetic model applies reasonably for ordinary hydrodynamics where the Maxwellian velocity distribution results from frequent collisions. It seems problematic for a plasma since generally, the collision rate is very low in a plasma due to its dilute nature. However, the experimental work of \cite{langmuir1925} demonstrates the surprising validity of the Maxwellian assumption for plasmas. This phenomenon is known as \emph{Langmuir paradox} which remains unsolved. Readers are referred to \cite[][p. 63]{chen2016} for some discussions. It is worth noting that the fluid model suffices for the majority of plasma phenomena, but certain situations exist where neither the fluid model is applicable, nor is the kinetic theory.

In the fluid model of plasma, each species of particles is equipped with a full set of fluid equations into which the Lorentz force and other plasma effects are incorporated. Maxwell's equations govern how an electromagnetic field is generated by the charged fluids, their motions, and changes of the fields. For such a coupled system, various assumptions are usually made to reduce complexity according to specific scenarios. In the simplest case, one considers a fully-ionized plasma and treats the ions, which are about $10^4$ times heavier than electrons, to be immobilized. Such simplification makes sense when phenomena at the scale of electron motions are of particular interest, and thus leads to so-called \emph{one-fluid} model\footnote{In this report, we think of ions, electrons, and neutral atoms as `fluid', and each `fluid' is described by a set of fluid equations. Also, `species' and `fluid' are synonymous here. Notice that in some literature they have different meanings.} in the sense that only one set of fluid equations is sufficient. To study more realistic situations, motions of multiple species of particles ought to be simulated. Furthermore, other effects like viscosity, ionization, recombination, and collisions could play important roles in many applications.

\subsection{Quasi-neutrality} \label{sec:quasi-neutrality}
Let's imagine such a situation: in a neutral\footnote{It means the net charge vanishes everywhere.} plasma with temperature $T_0$ and electron number density $n_0$, the electrons contained in cube volume $d^3$ are, due to thermal motions, separated from ions. The non-zero charge thus gives rise to an induced electric field, and the energy required for this movement is of magnitude $n_0e^2d^2 / \varepsilon_0$ for a single particle. In the absence of external forces, this energy must come only at the expense of the thermal energy \citep{frank_1972}, which is of magnitude $k_BT_0$. Only when the energy required for the displacement is less than the thermal energy can this local unbalance of charges happen. By balancing these two energy magnitudes we get the length scale

\begin{equation*}
    d \sim \left(\frac{\varepsilon_0k_BT_0}{e^2n_0}\right)^{1/2} =: \lambda_D
\end{equation*}
which is termed \emph{Debye length}\footnote{The Debye length is usually defined for electrons. In fact, one can define different Debye lengths for other species.}. The Debye length is a fundamental property of nearly all plasmas of interest \citep{gibbon2020}. Being a crucial plasma parameter, it is a characteristic length scale over which the perturbation of electric charges is screened due to random thermal motions. With a small $\lambda_D$, the mismatch of positive and negative charges would be limited to a small area. Hence the plasma is approximately \emph{neutral}, namely canceling out in net charges, over a relatively large spatial scale. Such phenomenon of effectively shielding the electrostatic field within a distance of the order $\lambda_D$ is called \emph{Debye shielding}.

Now comes the illustration of \emph{quasi-neutrality}, which is a common property of plasmas. Consider $L_0$ as the characteristic length scale of the system, upon which the dimensionless Debye length $\lambda$ is readily defined as
\begin{equation*}
    \lambda := \frac{\lambda_D}{L_0}.
\end{equation*}
When $\lambda_D$ is much smaller than $L_0$, any local charge unbalance is shielded out within distance of the order $L_0$. The quasi-neutrality refers to such a situation that the plasma is neutral enough such that one can take $\rho \approx 0$, but not so neutral that all the interesting electromagnetic forces vanish \citep{chen2016}. In other words, the quasi-neutrality does not render the plasma a neutral gas such that it has no interaction with the electromagnetic field.

From a mathematical viewpoint, the quasi-neutrality assumption causes the degeneracy of Gauss's law for the electric field to the quasi-neutral condition $\rho = 0$. Despite the vanishing electric charge $\rho$, the electric field is \emph{not} divergence-free. Such degeneracy of the system poses challenges when one has to deal with the non-neutral and quasi-neutral models---two systems of different mathematical properties---at the same time.

\section{Asymptotic-preserving schemes}
 Many important partial differential equations (PDEs) systems involve asymptotic parameters (denoted by $\lambda$ from now on), which might take value from $\lambda = \mathcal{O}(1)$ to $\lambda \ll 1$ at different regimes of the targeting problem, e.g. the relaxation of collision term (or Knudsen number \textbf{Kn}) in Boltzmann equations, Mach number \textbf{Ma} in the Navier-Stokes (N-S) equations, and the Debye length $\lambda_D$ in the Euler-Maxwell system. These parameters have close connections with the characteristic scale of the system, e.g. wave speed and relaxation time. As the asymptotic parameter $\lambda$ approaches zero, the limit solution (if exists) is described by a set of PDEs of a different type from the non-limit one. A \emph{singular perturbation} problem hence arises (See \cite{mark_1995} for related theories). For instance, the Boltzmann equation tends to the compressible N-S equations as \textbf{Kn} $\rightarrow 0$; the compressible N-S equations approach the incompressible case as \textbf{Ma} $\rightarrow 0$, and the fluid pressure switches its hyperbolic character to the elliptic one. To give an intuition about the singular perturbation, consider a toy model
 \begin{equation} \label{equ:toy-model}
     \lambda u' + u = 0, u:[0,\infty]\rightarrow\mathbb{R},
 \end{equation}
 which is a first-order ordinary differential equation (ODE). Let $\lambda$ go to zero, the (pointwise) limit solution satisfies 
 \begin{equation*}
     u = 0,
 \end{equation*}
 which is no longer a first-order ODE.

 Following \cite{jin_2010}, we refer to the original system ($\lambda = \mathcal{O}(1)$) as \emph{microscopic} model while the limiting system ($\lambda \rightarrow 0$) as \emph{macroscopic} model, denoting them by $P^\lambda$ and $P^0$ respectively. If either the macroscopic or the microscopic model is uniformly valid in the whole domain, one can devise schemes accordingly. In fluid dynamics, for example, different solvers are tailored for compressible and incompressible flows. Applying schemes for $\lambda = \mathcal{O}(1)$ to the problem with $\lambda \ll 1$ would be problematic because schemes for $P^\lambda$ are usually subject to CFL-like conditions dependent on $\lambda$. For instance, \textbf{Ma} is inversely proportional to the sound speed; Debye length is inversely proportional to the wave speed. Under-resolving these small scales usually lead to instability. Therefore, $\lambda \ll 1$ would pose very strict restriction on time-step size, leading to prohibitive computational cost. Look back to the toy model (\ref{equ:toy-model}). A reasonable scheme for $\lambda = \mathcal{O}(1)$ is the explicit Euler
 \begin{equation*}
     \lambda\frac{u^{n+1}-u^{n}}{\delta} + u^n = 0.
 \end{equation*}
Yet obviously if the time-step size $\delta$ is fixed, it does not apply to arbitrarily small $\lambda$ due to the stability condition $\delta < 2\lambda$.

 The standard strategy to handle problem $P^\lambda$ with $\lambda \ll 1$ is to solve $P^0$ instead of $P^\lambda$ under the assumption that $P^0$ is a good approximation of $P^\lambda$. For instance, the fluid limit of the Boltzmann equation removes the restrictive stability condition that is dependent on a small relaxation length; the incompressible N-S equations eliminate the need to resolve the sound speed whereas it is necessary in the compressible case. However, challenges occur when sub-domains with $\lambda = \mathcal{O}(1)$ and $\lambda \ll 1$ coexists in the computational domain. To mention some examples, the reentry problem of space shuttles involves both rarefied and dense gases; the plume of a convergence-divergence nozzle experiences \textbf{Kn} from small to very large value \citep{jenny2015}; the plasma sheath near the wall area violates the quasi-neutral assumption in contrast to the quasi-neutral bulk area. To handle such hybrid problems, the classical approach is to split the domain and apply schemes accordingly. However, the criterion for domain splitting is not straightforward and quite empirical. In addition, the projection of solutions from one model to another in the transitional area adds to complexity \citep{jin_2010, degond_2011}. In other words, the non-uniformity of numerical schemes on microscopic and macroscopic models poses a great challenge in handling problems in a transitive regime.

 This dilemma spurs tremendous interests in developing schemes that work \emph{uniformly} well for $\lambda \in [0,1]$ with fixed spatial/time step. Such a scheme is expected to produce satisfactory results without resolving the smallest scale and provide a more elegant and unified solution to problems in a transitive regime. At this point, we introduce the concept of \emph{asymptotic-preserving} (AP) schemes. We resort to the celebrated commuting diagram Fig. \ref{fig:illustration_ap} in \cite{jin_1999} which sketches the property that an AP scheme should possess. As is defined above, $P^\lambda$ and $P^0$ stand for the (solutions of) microscopic and macroscopic models respectively. We introduce the discrete model $P^\lambda_h$ based on some AP scheme, whose solution depends on both the asymptotic parameter $\lambda$ and the spatial (or temporal) step size $h$. We stress that each limit in Fig. \ref{fig:illustration_ap} is attained by letting one parameter go to zero while fixing the other. As a basic requirement, the discrete microscopic model $P^\lambda_h$ should at least converge to its analytic solution $P^\lambda$ as $h\rightarrow0$. The AP property additionally allows the convergence of $P^\lambda_h$ to the limit discrete model $P^0_h$ as $\lambda\rightarrow0$. To accomplish this aim, the stability restriction on $h$ must be independent of $\lambda$. We refer to such property as \emph{asymptotic stability}, following \cite{degond_2011}. Furthermore, the discrete macroscopic model $P^0_h$ must again converge to the macroscopic model $P^0$ as $h\rightarrow0$. Such property is termed \emph{asymptotic consistency}. In other words, a discrete model (scheme) $P^\lambda_h$ is AP if it satisfies the commuting diagram Fig.\ref{fig:illustration_ap}. To make it intuitive, AP schemes preserve the asymptotic limits from the microscopic to the macroscopic models, \emph{at the discrete level} \citep{jin_2010}.

  \begin{figure}
     \centering
     \begin{tikzpicture}
     \node (nw) {\Large $P^\lambda_h$};
     \node (ne) [right=3cm of nw]{\Large $P^\lambda$};
     \node (sw) [below=of nw]{\Large $P^0_h$};
     \node (se) [right=3cm of sw]{\Large $P^0$};
     \draw[->] (nw.east)  -- node [above,midway] {$h\rightarrow0$} (ne.west) ;
     \draw[->] (nw.east)  --  (ne.west) ;
     \draw[->] (nw.south) -- node [left,midway] {$\lambda\rightarrow0$} (sw.north);
     \draw[->] (nw.south) -- node {} (sw.north);
     \draw[->] (sw.east)  -- node [above,midway] {$h\rightarrow0$}(se.west);
     \draw[->] (ne.south) -- node [left,midway] {$\lambda\rightarrow0$} (se.north);
     \end{tikzpicture}
     \caption{Illustration of AP schemes}
     \label{fig:illustration_ap}
 \end{figure}

 We present the definition in a formal way: 
 \begin{definition} \label{def:ap}
 Consider the microscopic model $P^\lambda$ depending on an asymptotic parameter $\lambda$, and assume the macroscopic model $P^0$ exists as the asymptotic limit as $\lambda \rightarrow 0$. The discrete model $P^\lambda_h$, depending both on $\lambda$ and $h$, is \emph{asymptotic-preserving} if
 \begin{itemize}
     \item $P^\lambda_h$ converges to $P^\lambda$ as $h\rightarrow0$ with stability conditions independent of $\lambda$ \emph{(asymptotic stability)};
     \item the asymptotic limit model $P^0_h$ is consistent with $P^0$ \emph{(asymptotic consistency)}.
 \end{itemize}
 \end{definition}
 Looking back again to the model (\ref{equ:toy-model}), one can easily verify that the implicit Euler
 \begin{equation*}
     \lambda\frac{u^{n+1}-u^{n}}{\delta} + u^{n+1} = 0
 \end{equation*}
 is AP.

 Extra properties are also desirable in some cases. In kinetic models with relaxations \citep{jin_2010}, for example, the scheme that can drive \emph{any} initial data into the local equilibrium \emph{in one step} is referred to as \emph{strongly AP}. Instead, if the local equilibrium is reached after long enough, it is referred to as \emph{relaxed AP}. If the initial data is well-prepared and the equilibrium remains for good, it is \emph{weakly AP}. Yet in this thesis, we are only concerned about the essential part of AP property that is specified in Definition \ref{def:ap}.

 Note that the existence of a macroscopic model $P^0$ as the asymptotic limit of microscopic model $P^\lambda$ is presumed. Rigorous proofs of some cases are available, for instance, in \cite{friedman_1968} for general linear PDEs, \cite{klainerman_1981} for the incompressible limit of the Euler equations, \cite{chen_1994, natalini_1996} for conservation laws with stiff relaxation term; \cite{remi_2014} for quasi-neutrality limit in the Euler-Maxwell system. This topic is beyond the scope of this thesis and we just take for granted the existence of such limit models.

 The concept of AP schemes can be traced back to \cite{jin_1995} in which the authors approximate a conservation law by a hyperbolic system with relaxation, and manage to construct a scheme that is stable for an arbitrarily small relaxation parameter. The term ``asymptotic-preserving" was formally introduced in \cite{jin_1999} for handling the diffusive regime of kinetic models. This concept stemmed from and remains very active in kinetic models with stiff relaxations, see \cite{jin_2010} and the references therein. Nonetheless, considerable effort has been put into developing AP schemes for many other problems that admit asymptotic behavior. For instance, in fluid dynamics, the so-called \emph{all-speed} schemes are advantageous when dealing with both compressible and incompressible regimes simultaneously. \cite{degond_2007, haack_2010} devise all-speed schemes for the isentropic Euler equations through fast-slow decomposition of velocity fields. Concerning plasma physics, a number of papers are available dealing with the quasi-neutral limit of the Euler-Poisson (or Euler-Maxwell) system \citep{crispel_2005, degond_2008, degond_2011, degond_2012} and Vlasov-Poisson (or Vlasov-Maxwell) system \citep{degond_2017, degond2017b, zhu_2017}. Besides, \cite{caflisch_1997, berthon2011} concern AP schemes for generic hyperbolic systems with relaxation source terms. For a comprehensive review on AP schemes, readers are referred to \cite{jin_2010} for kinetic and hyperbolic equations, and \cite{degond_2017} for multiscale plasma simulations.

 To devise an AP scheme, one mostly has to consider which terms need to be evaluated implicitly to meet the requirements of the AP property \citep{degond_2011} since stronger stability is usually achieved through implicit treatment in time discretization. We want to stress that unconditionally-stable (with respect to $\lambda$) schemes are not necessarily AP \citep{degond_2011,caflisch_1997}\footnote{It means the asymptotic stability does not necessarily lead to asymptotic consistency as is defined in definition \ref{def:ap}.}. Furthermore, a fully-implicit scheme is very likely to possess AP property, but the computational difficulties arising from solving massive linear or possibly nonlinear equations is potentially a huge cost. As is summarized by \cite{degond_2017}, AP schemes aim to bridge several sets of equations describing the system in different regimes, rather than to alleviate the stability constraints of the numerical methods. In this sense, a fully-implicit scheme is likely to be overkill. We want to achieve the AP property without incurring too much extra cost, which necessitates a smart construction.

 A general methodology for devising AP schemes is suggested by \cite{degond_2012, degond_2017}. They summarize it into two steps. The first step is a ``reformulation" step, where an equivalent form $R^\lambda$ of $P^\lambda$ is to be found such that the $R^\lambda$ explicitly appears as a perturbation of $P^0$. Afterward, one discretizes $P^\lambda$ by a scheme $P^\lambda_h$ with a certain amount of implicitness in such a way that the reformulation procedure can be performed at the discrete level, and leads to a reformulated discrete model $R^\lambda_h$ that is consistent to $R^\lambda$. However, this procedure is somehow heuristic, and its applicability to other perturbation problems remains questionable. It is also infeasible to rigorously prove the AP property for a given scheme, which is largely owing to the fuzzy notations of ``convergence" of numerical schemes. Even the linearized stability, as a necessary condition, is difficult to analyze in a multi-dimensional framework. Therefore, for the time being, we can state the AP property and devise the AP scheme merely in a heuristic way, and mostly has to resort to numerical experiments for verification.

 To summarize, the advantage of AP schemes over classical ones is twofold: for problems involving different regimes, the macroscopic regime ($\lambda \ll 1$) does not suffer from the strict stability requirement whereas the microscopic regime ($\lambda \sim \mathcal{O}(1)$) can be resolved as usual; the scale of interest, namely the resolution that we desire, is free to choose regardless of the value of the asymptotic parameter that represents the scale of the system.

\chapter{Discussion on Asymptotic-preserving Property}

On portraying the AP property through the commuting diagram Fig. \ref{fig:illustration_ap} and Definition \ref{def:ap}, we convey the principle of how an AP scheme is supposed to behave. Yet these illustrations are somehow given in general terms and lack precise statements. Another concern lies in the potential entanglement between the two requirements of AP schemes, namely asymptotic stability and asymptotic consistency Since these two statements are very strong, decomposing them into weaker ones is likely to help identify essential components to yield AP property. Due to the shortage of theoretical analysis on AP schemes, we humbly make some attempts here.

In this chapter, the AP property, as well as the related arguments, are rephrased in a relatively rigorous way. Specifically, we want to explore the connection of the four asymptotic relations depicted in the commuting diagram Fig. \ref{fig:illustration_ap}, relying on which we try to present an argument about a set of sufficient conditions that lead to an AP scheme.

Based on the formulation the commuting diagram Fig. \ref{fig:illustration_ap}, we rephrase the AP property by a uniform convergence statement: a discrete model $P^\lambda_h$ is AP if and only if
\begin{equation} \label{arg:ap}
    \exists C, k > 0,\ \ \  \|P^\lambda_h - P^\lambda\| \leq Ch^k,\ \ \ \forall \lambda \in [0,1]  
\end{equation}
where $\|\cdot\|$ represents some suitable norm.
We repeat the definitions: the asymptotic parameter $\lambda$; the discretization parameter $h$, e.g., time step size and cell size; the (solution of) discrete model $P^\lambda_h$; the (solution of)  continuous model $P^\lambda$. This amounts to stating a scheme that converges to the analytical solution uniformly well for arbitrary $\lambda$ and especially for the macroscopic model $P^0$, which is nothing but the philosophy of AP schemes.

Next, we present an argument that relates the convergence relationships in the commuting diagram with the above uniform convergence statement.
\begin{proposition} \label{prop:1}
Assume $P^0_h$ is well-defined. If the following conditions are satisfied
\begin{itemize}
    \item[$(*)$] $P^\lambda_h \xrightarrow[]{h\rightarrow0}P^\lambda$ in the sense that $\exists \alpha, \Tilde{\alpha}, C_1$ being constant independent of $h, \lambda$ such that
    \begin{equation*}
        \|P^\lambda_h - P^\lambda\| \leq C_1\frac{h^\alpha}{\lambda^{\Tilde{\alpha}}},\ \ \ \forall \lambda \in (0,1],
    \end{equation*}
    \item[$(**)$] $P^\lambda_h \xrightarrow[]{\lambda\rightarrow0} P^0_h$ in the sense that $\exists \beta, C_2$ being constant independent of $h, \lambda$ such that
    \begin{equation*}
        \|P^\lambda_h - P^0_h\| \leq C_2\lambda^\beta,\ \ \ \forall h > 0,
    \end{equation*}
    \item[$(\$)$] $P^\lambda \xrightarrow[]{\lambda\rightarrow0}P^0$ in the sense that $\exists C_3, \gamma$ being constant independent of $h, \lambda$ such that
    \begin{equation*}
        \| P^\lambda - P^0\| \leq C_3\lambda^\gamma, \ \ \ \forall \lambda \in [0,1],
    \end{equation*}
\end{itemize}
Then we have $P^\lambda_h \xrightarrow[]{h\rightarrow0} P^\lambda$ uniformly on $\lambda$, namely argument (\ref{arg:ap}).
\end{proposition}
\begin{proof}
Let $\epsilon$ be a constant satisfying $\alpha - \epsilon > 0$. For any $\lambda \in [0,1]$, we have the following two situations.

If $\lambda^{\Tilde{\alpha}} < h^{\alpha - \epsilon}$, we pick $\Tilde{\lambda} = h^\frac{\alpha - \epsilon}{\Tilde{\alpha}}$, and we have
\begin{align*}
    \|P^\lambda_h - P^\lambda\| &\leq \|P^\lambda_h - P^{\Tilde{\lambda}}_h\| + \|P^{\Tilde{\lambda}}_h - P^{\Tilde{\lambda}}\| + \|P^{\Tilde{\lambda}} - P^\lambda\| \\
    & \leq C_2(\lambda^\beta + \Tilde{\lambda}^\beta) + C_1\frac{h^\alpha}{{\Tilde{\lambda}}^{\Tilde{\alpha}}} + C_3(\Tilde{\lambda}^\gamma + \lambda^\gamma) \\
    & \leq 2C_2h^{\frac{\alpha - \epsilon}{\Tilde{\alpha}}\beta} + C_1h^\epsilon + 2C_3 h^{\frac{\alpha - \epsilon}{\Tilde{\alpha}}\gamma} \\
    & \leq 5\text{max}\{C_1,C_2,C_3\}h^{\text{min}\{\frac{\alpha - \epsilon}{\Tilde{\alpha}}\beta, \epsilon, \frac{\alpha - \epsilon}{\Tilde{\alpha}}\gamma\}}.
\end{align*}
The triangle inequality is applied to the first and second inequalities.

If $\lambda^{\Tilde{\alpha}} \geq h^{\alpha - \epsilon}$, we can directly apply condition $(*)$, which results in
\begin{align*}
    \|P^\lambda_h - P^\lambda\| \leq C_1\frac{h^\alpha}{\lambda^{\Tilde{\alpha}}} \leq C_1h^\epsilon.
\end{align*}
Combine these two situations, and we can conclude.
\end{proof}
Condition $(*)$ amounts to saying that the scheme converges to the right solution only when the discretization parameter $h$ resolves $\lambda$ in some way. Otherwise, the scheme diverges. This should be easily met by any classical scheme which is not necessarily AP. The asymptotic stability is enforced in Condition $(**)$ which implies that for a fixed $h$, no $\lambda$ should incur instability. Being the underlying assumption, the convergence of the microscopic model to the macroscopic model, as is depicted by Condition $(\$)$, is always taken for granted throughout the thesis. Therefore, Condition $(*)$ and $(\$)$ are usually satisfied by a suitable problem and a classical scheme. Proposition \ref{prop:1} hence provides some guidance on how to design an AP scheme, that is, to incorporate Condition $(**)$ into the scheme.

In the sequel, we consider a single-step scheme in the form $u_{\lambda,h}^{m+1} = \Phi_{\lambda,h}^m u_{\lambda,h}^{m}$, where $\Phi_{\lambda,h}^m$ is the discrete evolving operator, and $u_{\lambda,h}^{m}$ is the numerical solution at $m$-th time step. Instead of directly arguing the convergence of solutions, as Proposition \ref{prop:1}, starting from such a scheme allows us to have finer control of their properties, especially the stability and consistency. The conclusion based on the scheme is more revealing in understanding AP properties and more instructive in the construction of AP schemes.

\begin{proposition}{\emph{(A sufficient argument for AP schemes)}} \label{prop:2}

Consider a suitable norm $\|\cdot\|$ and a normed space $\mathcal{V}$ as the solution space. For a singular perturbation problem $P^\lambda$, assume Condition $(\$)$ in Proposition \ref{prop:1} is satisfied, and the solutions are uniformly bounded, that is, $\|\Tilde{u}_\lambda\| \leq C_u,\ \forall \lambda \in [0,1].$
For a single-step scheme $u_{\lambda,h}^{m+1} = \Phi_{\lambda,h}^m u_{\lambda,h}^{m}$, assume $\Phi_{0,h}^m$ is well-defined. We denote the exact solution by $\Tilde{u}_{\lambda,h}^m$. If the scheme satisfies the following conditions
\begin{itemize}
    \item[\emph{(AS)}]  $\Phi_{\lambda,h}(\cdot)$ is $(1+hC_\Phi)$-Lipschitz $\forall\lambda\in[0,1]$  where the constant $C_\Phi$ does not depend on $\lambda, h, m$;

    \item[\emph{(C)}] the non-limit scheme is \emph{consistent} in the sense that 
    \begin{equation*}
        \| \Tilde{u}^{m+1}_{\lambda,h} - \Phi_{\lambda,h}^m\Tilde{u}^{m}_{\lambda,h}\| \leq C_c\frac{h^2}{\lambda}, \ \ \ \forall \lambda \in (0,1],
    \end{equation*}
    where the constant $C_c$ does not depend on $\lambda, h, m$;

    \item[\emph{(AC)}] the limiting scheme is \emph{consistent} in the sense that 
    \begin{equation*}
        \| \Tilde{u}^{m+1}_{0,h} - \Phi_{0,h}^m\Tilde{u}^{m}_{0,h}\| \leq \Tilde{C_c}h^2, 
    \end{equation*}
    where the constant $\Tilde{C_c}$ does not depend on $h, m$;

    \item[\emph{(L)}] $\Phi_{\lambda,h}^m$ is Lipschitz with respect to $\lambda$ in the sense that
    \begin{equation*}
        \| (\Phi_{\lambda,h}^m - \Phi_{0,h}^m)u \| \leq \Tilde{C}_\Phi\|u\|h\lambda,\ \ \ \forall u \in \mathcal{V}, 
    \end{equation*}
    where the constant $\Tilde{C}_\Phi$ does not depend on $h$,
\end{itemize}
then the scheme is AP in the sense of (\ref{arg:ap}).
\end{proposition}
\begin{proof}[Proof]
Providing Proposition \ref{prop:1}, it suffices to check Condition $(*)$ and $(\$)$.

For $\lambda > 0$, define the error $e^{m}_{\lambda,h} := \Tilde{u}_{\lambda,h}^{m} - u_{\lambda,h}^{m}$, and we have 
\begin{align*}
    e^{m+1}_{\lambda,h} = \Tilde{u}_{\lambda,h}^{m+1} - \Phi^m_{\lambda,h} \Tilde{u}_{\lambda,h}^{m} + \Phi^m_{\lambda,h} \Tilde{u}_{\lambda,h}^{m} - \Phi^m_{\lambda,h}u_{\lambda,h}^{m}.
\end{align*}
By triangle inequality,
\begin{align*}
    \|e^{m+1}_{\lambda,h}\| \leq \|\Tilde{u}_{\lambda,h}^{m+1} - \Phi^m_{\lambda,h} \Tilde{u}_{\lambda,h}^{m}\| + \|\Phi^m_{\lambda,h} \Tilde{u}_{\lambda,h}^{m} - \Phi^m_{\lambda,h}u_{\lambda,h}^{m}\|
\end{align*}
By (AS) and (C), 
\begin{align*}
    \|e^{m+1}_{\lambda,h}\| \leq (1+hC_\Phi)\|e^m_{\lambda,h}\|+ C_c\frac{h^2}{\lambda},
\end{align*}
and thus by induction,
\begin{align*}
    \|e^{m+1}_{\lambda,h}\| \leq (1+hC_\Phi)^{m+1}\|e^0_{\lambda,h}\| + \sum_{i=0}^{m}(1+hC_\Phi)^iC_c\frac{h^2}{\lambda}.
\end{align*}
Since it is reasonable to take $\|e^0_{\lambda,h}\|=0$ and
\begin{align*}
    \sum_{i=0}^{m}(1+hC_\Phi)^i = \frac{(1+hC_\Phi)^{m+1} - 1}{hC_\Phi} = \frac{(1+hC_\Phi)^{T/h} - 1}{hC_\Phi} \leq \frac{e^{C_\Phi T}-1}{hC_\Phi}, 
\end{align*}
we obtain
\begin{align*}
    \|e^{m+1}_{\lambda,h}\| \leq \frac{e^{C_\Phi T}-1}{C_\Phi}C_c\frac{h}{\lambda}, 
\end{align*}
namely Condition $(*)$ in Proposition \ref{prop:1}.
By the same procedure and Condition (AC), we can draw the similar conclusion for the case $\lambda = 0$,
\begin{align}\label{equ:prop2-arg1}
    \|e^{m+1}_{0,h}\| \leq \frac{e^{C_\Phi T}-1}{C_\Phi}\Tilde{C}_ch, 
\end{align}

Secondly, we want to prove (\$) in Proposition \ref{prop:1}. Set $\lambda = 0$ in the scheme,
\begin{align*}
    u_{0,h}^{m+1} = \Phi^m_{0,h} u_{0,h}^{m}.
\end{align*}
Define $\varepsilon^{m}_{\lambda,h} := u_{\lambda,h}^{m} - u_{0,h}^{m}$, and we have
\begin{align*}
    \varepsilon^{m+1}_{\lambda,h} = \Phi^m_{\lambda,h} u_{\lambda,h}^{m} - \Phi^m_{0,h} u_{0,h}^{m}.
\end{align*}
By triangle inequality,
\begin{align*}
    \|\varepsilon^{m+1}_{\lambda,h}\| \leq \|\Phi^m_{\lambda,h} u_{\lambda,h}^{m} - \Phi^m_{\lambda,h} u_{0,h}^{m}\| + \|\Phi^m_{\lambda,h} u_{0,h}^{m} - \Phi^m_{0,h} u_{0,h}^{m}\|.
\end{align*}
By (AS) and (L),
\begin{align*}
    \|\varepsilon^{m+1}_{\lambda,h}\| \leq (1+hC_\Phi)\|\varepsilon^{m}_{\lambda,h}\| + \Tilde{C}_{\Phi}\|u_{0,h}^{m}\|h\lambda.
\end{align*}
From the definition $u_{0,h}^{m} = \Tilde{u}_{0,h}^{m} - e_{0,h}^{m}$, we deduce by (\ref{equ:prop2-arg1}) and boundedness on solutions that
\begin{align} \label{equ:prop2-arg2}
    \|\varepsilon^{m+1}_{\lambda,h}\| \leq (1+hC_\Phi)\|\varepsilon^{m}_{\lambda,h}\| + \Tilde{C}_{\Phi}\left[C_u + \frac{e^{C_\Phi T}-1}{C_\Phi}C_ch\right]h\lambda.
\end{align}
By induction as before, we end up getting
\begin{align*}
    \|\varepsilon^{m+1}_{\lambda,h}\| \leq \frac{e^{C_\Phi T}-1}{C_\Phi}\left[C_u + \frac{e^{C_\Phi T}-1}{C_\Phi}C_ch\right]\Tilde{C}_{\Phi}\lambda,
\end{align*}
Since we are concerned with the behavior of $h\rightarrow0$, one can assume $h < 1$ without loss of generality.

On yielding (\ref{equ:prop2-arg1}) and (\ref{equ:prop2-arg2}), we can conclude by Proposition \ref{prop:1}.
\end{proof}

One can interpret Proposition \ref{prop:2} in this way: for a scheme that is already stable and consistent pointwise with respect to $\lambda > 0$, by requiring the asymptotic stability (AS), consistency in the limiting case (AS), as well as Condition (L), can one attain AP property. We would like to stress that Condition (AS) is weaker than the asymptotic consistency in Definition \ref{def:ap} which states the convergence of the limiting model. In exchange, we have to additionally enforce (L).

To summarize, we try to dig in and present some concrete statements for the sake of unveiling the essential qualifications for an AP scheme. Proposition \ref{prop:1} serves to concretize the commuting diagram Fig. \ref{fig:illustration_ap}, and illuminates how these converging relations result in AP property. Further specification is manifested in Proposition \ref{prop:2} which proposes a sufficient condition and tries to give some definite clues about the properties worth paying attention to construct an AP scheme.             
\chapter{Discretization of the Euler-Maxwell System} \label{chap:discretization_euler_maxwell}
Throughout the thesis, we are dealing with the numerical treatment of the \emph{Euler-Maxwell} system as a fluid description of multi-species plasmas. Hence, before specifying the schemes, we would like to give a preliminary introduction to the discretization of this system. This chapter is organized as follows: first, the governing equations of the Euler-Maxwell system are presented. In the sequel, two discretization framework, Finite Volume Method (FVM) and Finite Integration Technique (FIT), are briefly introduced, serving to discretize the Euler system and the Maxwell system respectively. Lastly, we discuss the interpolation of electromagnetic fields, which is dispensable in coupling the two subsystems.

\section{Governing equations for multi-species plasma modeling}
In plasma modeling, the system is composed of two subsystems. One governs the behavior of electric and magnetic fields while the other rules the motions of gas particles. We refer to the former one as \emph{Maxwell system} and the latter one as \emph{Euler system} under the framework of the fluid plasma model.

The Maxwell system is described by Maxwell's equations whose expression in SI units read
\begin{align}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday} \\ 
    \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= -\mathbf{J}, \label{equ:maxwell_ampere} \\
    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B}\\
    \nabla \cdot \mathbf{D} &= \rho, \label{equ:maxwell_gauss_D}
\end{align}
where the involved quantities are magnetic flux density $\mathbf{B}$, electric field intensity $\mathbf{E}$, electric induction $\mathbf{D}$, magnetic field intensity $\mathbf{H}$, electric current density $\mathbf{J}$ and electric charge density $\rho$. These equations are known as Faraday's law (\ref{equ:maxwell_faraday}), Amp\`{e}re's law (\ref{equ:maxwell_ampere}), Gauss's law for magnetism (\ref{equ:maxwell_gauss_B}) and Gauss's law for electric field (\ref{equ:maxwell_gauss_D}). For simplicity, we only consider isotropic and homogeneous mediums in vacuum. The quantities are thus related by the linear constitutive relations 
\begin{equation*}
    \mathbf{D} = \varepsilon_0 \mathbf{E}, \ \ \ \mathbf{B} = \mu_0\mathbf{H}, 
\end{equation*}
where $\varepsilon_0$ and $\mu_0$ are the vacuum permittivity and permeability of the medium. By definition of the electric current density $\mathbf{J}$ and electric charge density $\rho$, they are supposed to satisfy the continuity equation
\begin{equation} \label{equ:charge_continuity}
    \partial_t\rho + \nabla \cdot \mathbf{J} = 0.
\end{equation}
Besides, on taking the divergence of equations (\ref{equ:maxwell_faraday}) and (\ref{equ:maxwell_ampere}) together with the relation (\ref{equ:charge_continuity}), it is possible to verify that Gauss's laws (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) are consequences of (\ref{equ:maxwell_faraday}) and (\ref{equ:maxwell_ampere}) provided that (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) are satisfied at the initial time. In other words, Gauss's laws (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) are redundant, and Faraday's law (\ref{equ:maxwell_faraday}) and Amp\`{e}re's law (\ref{equ:maxwell_ampere}) suffice.

In the Euler system, the motions of gas particles are accounted for through the \emph{Euler equations}. Specifically, we equip each species with one set of (compressible) Euler equations, taking into account the effect of electromagnetic fields as well as other processes like collisions and recombination. The generic expressions read
\begin{align} \label{equ:euler_}
    \partial_t
    \begin{bmatrix}
    n_* \\
    m_*n_* \mathbf{u}_* \\
    m_*n_* e_*
    \end{bmatrix}
    + \nabla \cdot
    \begin{bmatrix}
    n_* \mathbf{u}_* \\
    m_*n_* \mathbf{u}_* \otimes \mathbf{u}_* + p_*\mathbb{I} \\
    m_*n_* h_* \mathbf{u}_*
    \end{bmatrix}
    =
    \begin{bmatrix}
    0 \\
    q_*n_*(\mathbf{E} + \mathbf{u}_* \times \mathbf{B}) \\
    \mathbf{J}_* \cdot \mathbf{E}
    \end{bmatrix}
    +
    \begin{bmatrix}
    \Gamma_* \\
    \mathbf{R}_* \\
    Q_*
    \end{bmatrix}.
\end{align}
The subscript $*$ represents the indices for different species, and by convention we assign $* = e$ to electrons, $* = i$ to ions, and $* = n$ to neutral atoms. The involved fluid quantities are: number density $n_*$, particle mass $m_*$,  charge number $q_*$, velocity $\mathbf{u}_*$, pressure $p_*$, specific total energy $e_* := \frac{1}{2}|\mathbf{u}_*|^2 + \frac{p_*}{m_*n_*(\gamma - 1)}$, specific total enthalpy $h_* := e_* + \frac{p_*}{m_*n_*}$ and current density $\mathbf{J}_* := q_*n_*\mathbf{u}_*$. All the species are assumed ideal gases with heat capacity ratio $\gamma=5/3$ for monatomic gases. The left-hand side of the equations describes the convection of plasma fluids. The first term at the right-hand side denotes Lorentz force in the momentum equation and Joule heating in the energy equation. $\Gamma_*, \mathbf{R}_*, Q_*$ are generic terms that include effects of inter-species collision, ionization, recombination, etc. The three equations respectively describes how the mass, momentum and energy of plasma fluids change over time.

It should be noted that by such a fluid model several assumptions are implicitly presumed. The intra-species collision rate is assumed to be high and isotropic so that the thermal equilibrium holds all the time, and one temperature is sufficient to characterize the thermal energy, which also explains the isotropic pressure. Actually, in some cases, a plasma species can exhibit two temperatures in different directions because of anisotropic thermal motions \citep{chen2016}. Additionally, the viscosity of plasma fluids, which gives rise to the off-diagonal elements of the stress tensor, is neglected in the Euler equations.

Combination of the two sets of equations (\ref{equ:maxwell_faraday}) to (\ref{equ:maxwell_gauss_D}) and (\ref{equ:euler_}) leads to the governing equations for a multi-species plasma model. The coupling of the two subsystems takes effect through the following relations that connect the fluid and electromagnetic quantities
\begin{equation*}
    \rho = \sum_* q_*n_*, \ \ \  \mathbf{J} = \sum_* q_*n_*\mathbf{u}_*. 
\end{equation*}
\subsection{Collision term}
The collisions within each species are accounted for by the pressure term which results from the Maxwellian assumption on the velocity distribution, while the intra-species collisions have to be included through source terms. If we consider a fully-ionized plasma that is composed of ions (with charge number $Z$) and electrons, their collisions are mostly \emph{Coulomb collision} \citep[][sec. 5.6.2]{chen2016}. That is, different from the billiard-ball collision, an electron already feels a force from a distance when it approaches an ion and is deflected gradually. Such collisions are modeled by friction terms as follows, and we simply present the expressions without derivation (see \citep[][sec. 5.6.2]{chen2016}):
\begin{equation} \label{equ:collision}
    \mathbf{R}_{e}^{\text{coll}} = \frac{\pi Ze^4m_e^{1/2}}{(4\pi\varepsilon_0)^2(k_BT_e)^{3/2}}\text{ln}\Lambda n_en_i(\mathbf{u}_i - \mathbf{u}_e) = - \mathbf{R}_{i}^{\text{coll}},  
\end{equation}
which models the collision force that is applied on the electrons. ln$\Lambda$ is called the \emph{Coulomb logarithm}, which typically takes a numerical value of order 10–20 . Because of the conservation of momentum, the collision term experienced by ions $\mathbf{R}_{i}^{\text{coll}}$ is just the negative of $\mathbf{R}_{e}^{\text{coll}}$.

\section{Spatial discretization of Euler system: Finite Volume Method}
We employ the finite volume method (FVM) to discretize the Euler system. As a classical framework for solving conservation laws and hyperbolic systems, FVM is derived from the integral form of the equations in each cell. It is the cell average of quantities that evolves at each time step, based on the \emph{numerical flux} through the cell boundary. The construction of the numerical flux, which serves to approximate the real flux, is the essence of constructing an FVM scheme. Due to the convection nature of fluid dynamics, the numerical fluxes are supposed to respect the convection direction, namely, the \emph{upwind scheme} is preferable. To this end, people resort to the approximated solution of \emph{Riemann problems}. The method is briefly illustrated in the following. For detailed information, see the textbook \cite{leveque_2002}.

The Euler equations (\ref{equ:euler_}) can be generalized into the form of conservation law with source terms:
\begin{equation} \label{equ:euler_conservation}
    \partial_t \mathbf{U} + \nabla \cdot \mathbf{F}(\mathbf{U}) = \mathbf{RHS},
\end{equation}
where $\mathbf{U}$ stands for the conservative variable, $\mathbf{F}(\mathbf{U})$ is the flux density, and $\mathbf{RHS}$ is the source term.

To obtain the semi-discretization, we first integrate (\ref{equ:euler_conservation}) over a cell $V_i$ 
\begin{equation} \label{equ:euler_grid} 
    \partial_t \overline{\mathbf{U}}_i + \frac{1}{|V_i|}\sum_{j:A_j\in\partial V_i} |A_j|\underbrace{\frac{1}{|A_j|}\iint_{A_j}\mathbf{F}(\mathbf{U})\cdot \mathbf{n}_j \text{d}A}_{\overline{\mathbf{F}}_j} = \underbrace{\frac{1}{|V_i|}\iiint_{V_i} \mathbf{RHS} \text{d}V}_{\overline{\mathbf{RHS}}_i}
\end{equation}
where $\overline{\mathbf{U}}_i := \iiint_{V_i} \mathbf{U} \text{d}V / |V_i|$ calculates the cell average, $\mathbf{n}_j$ is the outer normal vector of face $A_j$ with respect to the cell $V_i$. We approximate the analytic flux $\overline{\mathbf{F}}_j$ in (\ref{equ:euler_grid}) by the numerical flux $\overline{\mathbf{F}}\left(\overline{\mathbf{U}}_i, \overline{\mathbf{U}}_{k(i,j)}, \mathbf{n}_j\right)$, where $k(i,j)$ returns the index of the adjacent cell that shares $A_j$ with cell $V_i$. Classical numerical fluxes include Lax-Friedrich flux, Rusanov flux, Engquist-Osher flux, see \cite[][p. 44-46]{mishra_2019}. Finally, we end up with the semi-discretized equation:
\begin{equation*}
    \partial_t \overline{\mathbf{U}}_i + \frac{1}{|V_i|}\sum_{j:A_j\in\partial V_i} |A_j| \overline{\mathbf{F}}\left(\overline{\mathbf{U}}_i, \overline{\mathbf{U}}_{k(i,j)}, \mathbf{n}_j\right) = \overline{\mathbf{RHS}}_i.
\end{equation*}
The Rusanov flux in multi-dimensions on face $A_j$ reads\footnote{See Appendix \ref{app:flux} for detailed derivation.}
\begin{equation} \label{equ:rusanov-flux-3d}
    \overline{\mathbf{F}}\left(\overline{\mathbf{U}}_L, \overline{\mathbf{U}}_R, \mathbf{n}\right) = \frac{1}{2}\left[\mathbf{F}(\overline{\mathbf{U}}_L)\cdot\mathbf{n} + \mathbf{F}(\overline{\mathbf{U}}_R)\cdot\mathbf{n}\right] - \frac{1}{2}\overline{s}\left(\overline{\mathbf{U}}_R - \overline{\mathbf{U}}_L\right),  
\end{equation}
where $\overline{s} = \text{max}(s(\overline{\mathbf{U}}_L), s(\overline{\mathbf{U}}_R))$ with $s(\mathbf{U}) := |\mathbf{u}\cdot\mathbf{n}| + \sqrt{\gamma p/\rho}$ representing the largest wave speed.

\section{Spatial discretization of Maxwell system: Finite Integration Technique}
The Finite Integration Technique (FIT), originally proposed by \cite{weiland_1977}, is adopted as the discretized model for the Maxwell system in our work. Just like FVM, FIT starts from the integral form of Maxwell's equations \emph{on a mesh doublet} and yields the so-called \emph{Maxwell's Grid Equations}. The quantities to be evolved are global quantities like the electric voltage assigned to a line and the magnetic flux assigned to a surface, rather than the local quantities like a component-wise electric field.

The FIT can be treated as a generalization of Yee's method \citep{yee_1966}, which is also known as Finite-Difference Time-Domain (FDTD). The FDTD method, in its standard formulation, is based on structured Cartesian grids, discretizing Maxwell's equations in a finite-difference manner. Coupled with the leap-frog time scheme, the FDTD method does not need to invoke an iterative solver at each time-step like the Finite Element Method (FEM), which makes it computationally efficient and easy-to-implement approach for solving a wide range of time-domain electromagnetic problems. The explicit time-domain FIT on Cartesian grids is computationally equivalent to the FDTD method. Inheriting the advantages of the FDTD method, FIT is furthermore able to handle complex geometry with unstructured mesh, and, thanks to the absence of approximation error in deriving the Maxwell's Grid Equations, provides powerful tools for the analysis of consistency, stability, and other issues \citep{weiland_2003}. Although originally developed for electromagnetism, FIT is also applicable in other types of wave-field problems, like acoustic and elastodynamic waves, as is summarized in \cite{marklein_2002}.

\subsection{Mesh duality} \label{sec:mesh_duality}

A mesh doublet $(\mathcal{M}, \Tilde{\mathcal{M}})$ is required for the formulation of FIT in the need of incorporating the material laws. The spatial domain is discretized by two meshes that interlace with each other. They are called \emph{primal} mesh $\mathcal{M}$ and \emph{dual} mesh $\Tilde{\mathcal{M}}$. The essential duality property requires that \emph{each edge of one mesh penetrates a face of the other mesh and that each vertex of one mesh lies at the center of a cell of the other mesh} \citep{weiland_2003}. We demonstrate such interlacing character by an example in Fig. \ref{fig:illustration_primal_dual}, where the primal mesh is composed of triangular prisms and the dual mesh is composed of hexagon prisms. The dual mesh can be generated as the Voronoi decomposition of the primal mesh \citep{fuchs_2021}. Compared to the constraint of FDTD to Cartesian meshes, FIT is compatible with a wide range of mesh types. An example of primal and dual meshes is given in Fig. \ref{fig:primal_dual_meshes}.

To clarify the terminology, the \emph{vertices, edges, faces} and \emph{volumes} (denoted by $P,L,A$ and $V$ respectively) make up a mesh. Also, they are uniformly termed \emph{facets} with zero, one, two and three dimensions.

\begin{figure}
    \centering
    \begin{tikzpicture}
    \def\primalstyle{thick}
    \def\dualstyle{thick}
    \coordinate (P0) at (0cm, 0cm);
    \foreach \i in {1,2,...,6}
    {
    \coordinate (P\i) at ({60*\i-30}:2cm);
    \draw[\primalstyle] (P0) -- (P\i);
    }
    \draw[\primalstyle] (P1) -- (P2) node[left=5mm]{\Large $\mathcal{M}$} -- (P3) -- (P4) -- (P5) -- (P6) -- cycle;
    \begin{scope}[shift={(3cm,0.5cm)}]
        \coordinate (PP0) at (0cm, 0cm);
        \foreach \i in {1,2,...,6}
        {
        \coordinate (PP\i) at ({60*\i-30}:2cm);
        \draw[gray] (PP0) -- (PP\i);
        }
    \end{scope}

    \draw[\primalstyle] (PP1) -- (PP2);
    \draw[gray] (PP2) -- (PP3);
    \draw[gray] (PP3) -- (PP4);
    \draw[gray] (PP4) -- (PP5);
    \draw[\primalstyle] (PP5) -- (PP6);
    \draw[\primalstyle] (PP6) -- (PP1);

    \draw[gray] (P0) -- (PP0);
    \draw[\primalstyle] (P1) -- (PP1);
    \draw[\primalstyle] (P2) -- (PP2);
    \draw[gray] (P3) -- (PP3);
    \draw[gray] (P4) -- (PP4);
    \draw[\primalstyle] (P5) -- (PP5);
    \draw[\primalstyle] (P6) -- (PP6);

    \foreach \i in {1,2,...,6}
    {
    \coordinate (D\i) at ({60*\i-60}:{2./1.737});
    }
    \draw[dashed, blue] (D1) -- (D2) -- (D3) -- (D4) -- (D5) -- (D6) -- cycle;
    \begin{scope}[shift={(1.5,0.25)}]
        \foreach \i in {1,2,...,6}
        {
        \coordinate (DD\i) at ({60*\i-60}:{2./1.737});
        }
    \end{scope}
    \draw[blue] (DD1) -- (DD2) -- (DD3) -- (DD4) -- (DD5) -- (DD6) -- cycle;
    \draw[blue] (D1) -- (DD1);
    \draw[blue] (D2) -- (DD2);
    \draw[blue] (D3) -- (DD3);
    \draw[blue] (D4) -- (DD4);
    \draw[blue] (D5) -- (DD5);
    \draw[blue] (D6) -- (DD6);

    \begin{scope}[shift={(-1.5,-0.25)}]
        \foreach \i in {1,2,...,6}
        {
        \coordinate (DDD\i) at ({60*\i-60}:{2./1.737});
        }
    \end{scope}
    \draw[blue, ultra thick] (DDD1) -- (DDD2) -- (DDD3) node[left=3mm]{\textcolor{blue}{\Large $\Tilde{\mathcal{M}}$}} -- (DDD4) -- (DDD5) -- (DDD6) -- cycle;
    \draw[blue, ultra thick] (D1) -- (DDD1);
    \draw[blue, ultra thick] (D2) -- (DDD2);
    \draw[blue, ultra thick] (D3) -- (DDD3);
    \draw[blue] (D4) -- (DDD4);
    \draw[blue] (D5) -- (DDD5);
    \draw[blue, ultra thick] (D6) -- (DDD6);

    \fill[blue!50, opacity=0.2] (D1) -- (D2) -- (D3) -- (D4) -- (D5) -- (D6);

    \end{tikzpicture}
    \caption{Illustration of primal and dual meshes. Six primal cells, which are triangle prisms, are depicted by black and gray edges. One dual cell, which is a hexagon prism, is depicted by blue edges. The dashed hexagon represents the intersection of the dual cell and primal cells. This particular type of mesh composed of prisms is picked as a demonstration since it is used in our numerical experiments.}
    \label{fig:illustration_primal_dual}
\end{figure}
\subsection{Spatial semi-discretization} \label{sec:fit}
The FIT is established based on the integral form of Maxwell's equations:
\begin{align}
    &\oint_{\partial A} \mathbf{E} \cdot d\mathbf{s} \ = - \iint_A \frac{\partial \mathbf{B}}{\partial t} \cdot d\mathbf{A}, \label{equ:maxwell_int_faraday}\\
    &\oint_{\partial A} \mathbf{H} \cdot d\mathbf{s} \ = \iint_A \left(\frac{\partial \mathbf{D}}{\partial t} + \mathbf{J}\right) \cdot d\mathbf{A}, \label{equ:maxwell_int_ampere}\\
    &\oint_{\partial V} \mathbf{B} \cdot d\mathbf{A} = 0, \label{equ:maxwell_int_gauss_B}\\
    &\oint_{\partial V} \mathbf{D} \cdot d\mathbf{A} = \iiint_V \rho dV. \label{equ:maxwell_int_gauss_D}
\end{align}
where $A, V$ stand for any 2-D faces and 3-D cells in the spatial domain. These equations are consequence of curl theorem and divergence theorem, and correspond to the integral form of Faraday's law (\ref{equ:maxwell_int_faraday}), Ampere's law (\ref{equ:maxwell_int_ampere}) and Gauss's laws for magnetic flux (\ref{equ:maxwell_int_gauss_B}) and electric induction (\ref{equ:maxwell_int_gauss_D}). The fields are related by the material laws
\begin{align} \label{equ:maxwell_material_laws}
    \mathbf{B} = \mu_0 \mathbf{H},\ \ \ \mathbf{D} = \varepsilon_0 \mathbf{E}.
\end{align}

The discrete Maxwell system is obtained by applying and collecting the equations (\ref{equ:maxwell_int_faraday}) (\ref{equ:maxwell_int_gauss_B}) on each facet of the primal mesh $\mathcal{M}$ and the equations (\ref{equ:maxwell_int_ampere}) (\ref{equ:maxwell_int_gauss_D}) on each facet of the dual mesh $\Tilde{\mathcal{M}}$. We denote the vertices by $(P_i)_{i=1}^{N_P}$, $(\Tilde{P}_i)_{i=1}^{N_{\Tilde{P}}}$, edges by $(L_i)_{i=1}^{N_L}$, $(\Tilde{L}_i)_{i=1}^{N_{\Tilde{L}}}$, faces by $(A_i)_{i=1}^{N_A}$, $(\Tilde{A}_i)_{i=1}^{N_{\Tilde{A}}}$, and cells by $(V_i)_{i=1}^{N_V}$, $(\Tilde{V}_i)_{i=1}^{N_{\Tilde{V}}}$ where the ones with tilde belong to the dual mesh. Recall the duality property that $\mathcal{M}$ and $\mathcal{M}'$ interlaces with each other in the sense that each edge penetrates a face of the other mesh. This leads to $N_L = N_{\Tilde{A}}$ and $N_A = N_{\Tilde{L}}$\footnote{Note that here the influence of boundary is not considered.}. The equations (\ref{equ:maxwell_int_faraday}) to (\ref{equ:maxwell_int_gauss_D}) can be rewritten into

\begin{align}
    &\sum_{j:L_j\in\partial A_i} \underbrace{\int_{L_j} \mathbf{E} \cdot d\mathbf{s}}_{e_j} = - \frac{\partial}{\partial t} \underbrace{\iint_{A_i} \mathbf{B} \cdot d\mathbf{A}}_{b_i},\ \ \ i = 1,...,N_A, \label{equ:maxwell_grid_faraday} \\
    &\sum_{j:\Tilde{L}_j\in\partial \Tilde{A}_i} \underbrace{\int_{\Tilde{L}_j} \mathbf{H} \cdot d\mathbf{s}}_{h_j} = \frac{\partial}{\partial t} \underbrace{\iint_{\Tilde{A}_i} \mathbf{D} \cdot d\mathbf{A}}_{d_i} + \underbrace{\iint_{\Tilde{A}_i} \mathbf{J} \cdot d\mathbf{A}}_{j_i}, \ \ \ i = 1,...,N_{\Tilde{A}}, \label{equ:maxwell_grid_ampere}\\
    &\sum_{j:A_j\in \partial V_i} \iint_{A_j} \mathbf{B} \cdot d\mathbf{A} = 0,\ \ \ i = 1,..., N_V,\label{equ:maxwell_grid_gauss_B}\\
    &\sum_{j:\Tilde{A}_j \in \partial\Tilde{V}_i}\iint_{\Tilde{A}_j} \mathbf{D} \cdot d\mathbf{A} = \underbrace{\iiint_{\Tilde{V}_i} \rho dV}_{q_i},\ \ \ i = 1,...,N_{\Tilde{V}}. \label{equ:maxwell_grid_gauss_D}
\end{align}
For the sake of neat illustration, we temporarily neglect the boundary conditions which will be discussed later. As is indicated in (\ref{equ:maxwell_grid_faraday})(\ref{equ:maxwell_grid_ampere}) by the underbraces, the discrete variables are chosen as the integral quantities of field vectors on edges or faces. Packing these scalar quantities into vectors, we define
\begin{equation} \label{equ:fit_scale_vector}
    \mathbf{e} := (e_i)_{i=1}^{N_L},\ \ \mathbf{b} := (b_i)_{i=1}^{N_A}, \ \ \mathbf{h} := (h_i)_{i=1}^{N_{\Tilde{L}}}, \ \ \mathbf{d} := (d_i)_{i=1}^{N_{\Tilde{A}}}, \ \ \mathbf{j} := (j_i)_{i=1}^{N_{\Tilde{A}}}, \ \ \mathbf{q} := (q_i)_{i=1}^{N_{\Tilde{V}}}.
\end{equation}

The next step is to transform the discrete Maxwell system (\ref{equ:maxwell_grid_faraday}) to (\ref{equ:maxwell_grid_gauss_D}) into a set of algebraic equations. One should note that the sign of each scalar depends on the orientation of the facet on which it is integrated. To uniquely determine the meaning of these quantities, an \emph{internal orientation} is assigned to every facet of the primal mesh $\mathcal{M}$. This attribute defines the orientations of edges and outer normals of faces. Besides, since the application of curl theorem and divergence theorem entails the orientation relations of edge-to-face and face-to-volume respectively, another orientation attribute, \emph{induced orientation}, is introduced to specify this topology. An induced orientation of a $k$-dim facet $f$ with respect to a $(k+1)$-dim facet $f'$ that contains $f$ is determined by the internal orientation of $f'$ according to some rule. An example is shown in Fig. \ref{fig:illustration_external_orientation}.
These topological attributes are inherent for a mesh and can be set at will.

\begin{figure}
    \centering

\begin{tikzpicture}
\coordinate (P1) at (0,0);
\coordinate (P2) at (2,2);
\draw[decoration={markings, 
    mark= at position 0.55 with {\arrow[scale=1.5]{to}}}
    ,postaction={decorate}, very thick, blue] (P1) -- (P2);
\node at (1,1.5) {\textcolor{blue}{$L$}};
\draw[fill=black] (P1) circle (0.1) node[above=3mm] {$P_1$} node[below=2mm] {$(-)$};
\draw[fill=black] (P2) circle (0.1) node[above=2mm] {$P_2$} node[below=2mm] {$(+)$};

\begin{scope}[shift={(5, 0)}]
\coordinate (Q1) at (0,0);
\coordinate (Q2) at (2cm, -0.5cm);
\coordinate (Q3) at (3cm, 1cm);
\draw[decoration={markings, 
    mark= at position 0.5 with {\arrow[scale=1]{to}}}
    , postaction={decorate}, very thick] (Q1) -- node[below=1.5mm]{$L_1$} (Q2);
    \draw[decoration={markings, 
    mark= at position 0.5 with {\arrow[scale=1]{to}}}
    , postaction={decorate}, very thick] (Q2) -- node[right,yshift=-1.5mm]{$L_2$} (Q3);
    \draw[decoration={markings, 
    mark= at position 0.5 with {\arrow[scale=1]{to}}}
    , postaction={decorate}, very thick] (Q3) -- node[above,xshift=-3mm] {$L_3$}(Q1);

\fill[blue, opacity=0.25] (Q1) -- (Q2) -- (Q3);
\draw[decoration={markings, 
    mark= at position 1 with {\arrow[scale=1.5]{to}}}
    , postaction={decorate}, very thick, blue](barycentric cs:Q1=1,Q2=1,Q3=1) -- ([shift={(0,2cm)}] barycentric cs:Q1=1,Q2=1,Q3=1) node[right,xshift=1mm] {\textcolor{blue}{$A$}}; 
\end{scope}

\begin{scope}[shift={(12,0)}]
\coordinate (S1) at (0,0);
\coordinate (S2) at (-1,0.5);
\coordinate (S3) at (1.5,1);
\coordinate (S4) at (0.5,2.5);
\draw[very thick, blue] (S1) -- (S2) -- (S4) -- cycle;
\fill[gray, opacity=0.2] (S1) -- (S2) -- (S4);
\draw[very thick, blue] (S1) -- (S3) -- (S4) -- cycle;
\fill[gray, opacity=0.2] (S1) -- (S3) -- (S4);
\draw[blue, thin] (S2) -- (S3);
\draw[decoration={markings, 
    mark= at position 1 with {\arrow[scale=1]{to}}}
    , postaction={decorate}, very thick] (barycentric cs:S1=1,S2=1,S4=1) -- ([shift={(-1,0.5)}] barycentric cs:S1=1,S2=1,S4=1) node[above] {$A_1$};
\coordinate (O1) at (barycentric cs:S1=1,S2=1,S3=1);
\coordinate (O2) at ([shift={(0,-1)}] barycentric cs:S1=1,S2=1,S3=1);
\coordinate (S)  at (intersection of O1--O2 and S1--S3);
\draw[very thick, dotted] (O1) -- (S);
\draw[decoration={markings, 
    mark= at position 1 with {\arrow[scale=1]{to}}}
    , postaction={decorate}, very thick] (S) -- (O2) node[right] {$A_2$};
\draw[decoration={markings, 
    mark= at position 1 with {\arrow[scale=1]{to}}}
    , postaction={decorate}, very thick] (barycentric cs:S1=1,S3=1,S4=1) -- ([shift={(1,0.4)}] barycentric cs:S1=1,S3=1,S4=1) node[right] {$A_3$} ;
\node at (S4) [left, xshift=-2mm] {\textcolor{blue}{$V$}};
\end{scope}
\end{tikzpicture}
    \caption{Illustration of induced orientations. As per our rule, the ending vertex of an edge is positively oriented while the starting point is negatively oriented; the orientations of edges with respect to a face obey the right-hand rule; a face of a volume are oriented with its outer normal. Note that the rule can be freely set.}
    \label{fig:illustration_external_orientation}
\end{figure}

With the aid of both internal and induced orientations, the facet-to-facet relations can be summarized by matrices containing only $\{-1,0,0\}$, which are called \emph{incidence matrices}. To describe the primal face-to-edge incidence relation, for instance, a sparse $N_A \times N_L$-matrix $\mathbb{C}$ is assembled whose $(i,j)$-entry is assigned $+1$ if the internal orientation of edge $L_j$ and its induced orientation with respect to face $A_i$ coincides; it is assigned $-1$ if two orientations are opposite; and assigned $0$ if $L_j$ is not a subset of the boundary of $A_i$. Discrete Faraday's law (\ref{equ:maxwell_grid_faraday}) is thus reformulated by:
\begin{equation*}
    \mathbb{C}\mathbf{e} = - \frac{\text{d}}{\text{d}t} \mathbf{b}.
\end{equation*}
As the incidence matrix $\mathbb{C}$ makes up the curl operator in a discrete manner, it is referred to as the \emph{discrete curl operator} for a certain primal mesh.

Given $\mathcal{M}$, the generation of $\Tilde{\mathcal{M}}$ is usually affiliated to $\mathcal{M}$ in terms of geometry, indexing, and topology. Although the latter two attributes can be defined with no dependence on $\mathcal{M}$, conventionally one specifies them relying on those of $\mathcal{M}$ for the sake of convenience in both formulation and implementation. Recall that primal edges (resp. faces) and dual faces (resp. edges) intersect in a one-to-one manner. Therefore, one can equate the index of a dual edge (resp. face) to that of its intersecting primal face (resp. edge). Furthermore, the internal orientation of a dual facet can be linked to that of its associated primal facet. With these constraints, discrete Ampere's law (\ref{equ:maxwell_grid_ampere}) can be reformulated into:
\begin{equation*}
    \Tilde{\mathbb{C}}\mathbf{h} = \frac{\text{d}}{\text{d}t} \mathbf{d} + \mathbf{j},
\end{equation*}
where $\Tilde{\mathbb{C}}$ is the dual face-to-edge incidence matrix of size $N_{\Tilde{A}} \times N_{\Tilde{L}}$, satisfying $\Tilde{\mathbb{C}} = \mathbb{C}^T$.

In a similar way, discrete Gauss's laws (\ref{equ:maxwell_grid_gauss_B})(\ref{equ:maxwell_grid_gauss_D}) is rewritten into:
\begin{equation*}
    \mathbb{D}\mathbf{b} = 0, \ \ \ \  \Tilde{\mathbb{D}}\mathbf{d} = \mathbf{q},
\end{equation*}
with $\mathbb{D}$ being the primal cell-to-face incidence matrix of size $N_{V} \times N_{A}$, and $\Tilde{\mathbb{D}}$ being the dual cell-to-face incidence matrix of size $N_{\Tilde{V}} \times N_{\Tilde{A}}$. Since they serve as the discrete version of the div operator, they are also referred to as \emph{discrete div operator}. It is readily to be checked the following relations 
\begin{equation*}
    \mathbb{D}\mathbb{C} = 0, \ \ \ \ \Tilde{\mathbb{D}}\Tilde{\mathbb{C}} = 0,
\end{equation*}
which is the discrete version of the vector calculus $\nabla \cdot (\nabla \times u) = 0$.

Additionally, the grad operator at the discrete level can be constructed by edge-to-vertex incidence matrices $\mathbb{G}$ of size $N_L \times N_P$ and $\Tilde{\mathbb{G}}$ of size $N_{\Tilde{L}} \times N_{\Tilde{P}}$. Given an electric potential vector $\bm{\varphi}$ whose components are defined at primal vertices, for example, the edge voltage vector $\mathbf{e}$ can thus be computed by
\begin{equation*}
    \mathbf{e} = \mathbb{G}\bm{\varphi}.
\end{equation*}

The material laws (\ref{equ:maxwell_material_laws}) need to be reformulated within this framework. The relations between scalar vectors, in the form of $\mathbf{b} = \mathbb{M}_\mu \mathbf{h}$ and $\mathbf{d} = \mathbb{M}_\varepsilon \mathbf{e}$, are to be derived. In the simplest case where permittivity $\mu$ and permeability $\varepsilon$ are homogeneous in the domain, and the orthogonality\footnote{The edges of one mesh penetrate the faces of the other mesh in an orthogonal manner.} of ($\mathcal{M}, \Tilde{\mathcal{M}}$) pair is ensured, the material matrices are diagonal with entries

\begin{equation*}
    \mathbb{M}_\mu[i,i] = \frac{\mu|A_i|}{|\Tilde{L}_i|}, \ \ \ \ \mathbb{M}_\varepsilon[i,i] = \frac{\varepsilon |\Tilde{A}_i|}{|L_i|},
\end{equation*}
where $|\cdot|$ means taking length or area.

To summarize, the FIT framework enables us to transform Maxwell’s equations into algebraic equations given the mesh pair ($\mathcal{M}, \Tilde{\mathcal{M}}$). The resulting system of algebraic equations is called Maxwell's Grid Equations (MGE). Let's put together the original form of the Maxwell system as well as the MGE:

\begin{minipage}{0.3\textwidth}
\begin{align*}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \\
    \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= -\mathbf{J}, \\
    \nabla \cdot \mathbf{B} &= 0,  \\
    \nabla \cdot \mathbf{D} &= \rho, \\
    \mathbf{H} &= \mu^{-1} \mathbf{B}, \\
    \mathbf{D} &= \varepsilon \mathbf{E}. 
\end{align*}
\end{minipage}
\begin{minipage}{0.1\textwidth}
\centering
\begin{tikzpicture}
\draw[thick, -{to}] (0,0) -- node[above]{$(\mathcal{M}, \Tilde{\mathcal{M}})$} (1.5,0);
\end{tikzpicture}
\end{minipage}
\begin{minipage}{0.3\textwidth}
\begin{align*}
    \dot{\mathbf{b}} + \mathbb{C}\mathbf{e} &= 0 , \\
    \dot{\mathbf{d}} - \Tilde{\mathbb{C}}\mathbf{h} &= - \mathbf{j}, \\
    \mathbb{D}\mathbf{b} &= 0,  \\
    \Tilde{\mathbb{D}}\mathbf{d} &= \mathbf{q},  \\
    \mathbf{h} &= \mathbb{M}_\mu^{-1} \mathbf{b}, \\
    \mathbf{d} &= \mathbb{M}_{\varepsilon} \mathbf{e}. 
\end{align*}
\end{minipage}
\begin{minipage}{0.2\textwidth}
Topological relations:
\begin{align*}
    \Tilde{\mathbb{C}} = \mathbb{C}^T \\
    \mathbb{D}\mathbb{C} = 0 \\
    \Tilde{\mathbb{D}}\Tilde{\mathbb{C}} = 0
\end{align*}
\end{minipage}

\hfill

Note that this transformation does not introduce approximations \emph{except for} the discrete material laws. The essence of FIT lies in that the complexity of continuous electric and magnetic field quantities
is reduced to a finite number of well-defined discrete unknowns \citep{weiland_2003}.

\subsection{Boundary treatment} \label{sec:boundary_treatment}

So far we have not discussed the boundary treatment. In fact, in the formulation of MGE, no boundary of the spatial domain is taken into account and all the scalar vectors should be treated of infinite length. Yet in a computer simulation, the computational domain has to be bounded, and the introduction of boundary complicates the situation. Under the framework of FIT, the issue is twofold: 1) The staggered mesh doublet ($\mathcal{M}, \Tilde{\mathcal{M}}$) entails cut-off cells at the boundary such that the boundaries of both meshes match up. To close the cut-off cells, we need auxiliary facets and quantities attached to them. 2) The auxiliary edges might not be straight and the auxiliary faces might not be flat, which necessitates a versatile data structure to include such situations. The boundary effect is shown in Fig. \ref{fig:illustraion_dual_boundary}. How these auxiliary quantities are incorporated into the discrete system is explained in Chapter \ref{chap:numerical_experiments_in_3d} along with the specific case.

\begin{figure}
    \centering
    \begin{tikzpicture}
    \coordinate (A1) at (0,0);
    \coordinate (A2) at (2,-0.7);
    \coordinate (A3) at (1.2,1);
    \coordinate (A4) at (-0.5,1.5);
    \draw[thick] (A1) node[left] {$\mathcal{M}$} -- (A2) -- (A3) -- cycle;
    \draw[thick] (A1) -- (A4) -- (A3);
    \begin{scope}[shift={(2,0.5)}]
        \coordinate (B1) at (0,0);
        \coordinate (B2) at (2,-0.7);
        \coordinate (B3) at (1.2,1);
        \coordinate (B4) at (-0.5,1.5);
        \draw[thick] (B2) -- (B3) -- (B4);
        \draw[gray]  (B1) -- (B3);
        \draw[gray]  (B1) -- (B2);
        \draw[gray]  (B1) -- (B4);
    \end{scope}
    \begin{scope}[shift={(4,1)}]
        \coordinate (C1) at (0,0);
        \coordinate (C2) at (2,-0.7);
        \coordinate (C3) at (1.2,1);
        \coordinate (C4) at (-0.5,1.5);
        \draw[thick] (C2) -- (C3) -- (C4);
        \draw[gray]  (C1) -- (C3);
        \draw[gray]  (C1) -- (C2);
        \draw[gray]  (C1) -- (C4);
    \end{scope}
    \draw[thick] (A4) -- (B4) -- (C4);
    \draw[thick] (A3) -- (B3) -- (C3);
    \draw[thick] (A2) -- (B2) -- (C2);
    \draw[gray]  (A1) -- (C1);
    \coordinate (O1) at (barycentric cs:A3=1,B3=1);
    \coordinate (O2) at (barycentric cs:A3=1,B3=1,A4=1,B4=1);
    \coordinate (O5) at (barycentric cs:A3=1,B3=1,A2=1,B2=1);
    \draw[blue, very thick] (O2) -- (O1) -- (O5);
    \coordinate (O3) at (barycentric cs:A1=1,A3=1,A4=1,B1=1,B3=1,B4=1);
    \coordinate (O4) at (barycentric cs:A1=1,A2=1,A3=1,B1=1,B2=1,B3=1);
    \draw[blue] (O2) -- (O3) -- (O4) -- (O5);
    \coordinate (OO1) at ([shift={(2,0.5)}]O1);
    \coordinate (OO2) at ([shift={(2,0.5)}]O2);
    \coordinate (OO3) at ([shift={(2,0.5)}]O3);
    \coordinate (OO4) at ([shift={(2,0.5)}]O4);
    \coordinate (OO5) at ([shift={(2,0.5)}]O5);
    \draw[very thick, blue] (OO2) -- (OO1) -- (OO5) node[right] {\textcolor{blue}{$\Tilde{\mathcal{M}}$}};
    \draw[blue] (OO2) -- (OO3) -- (OO4) -- (OO5);
    \draw[very thick, blue] (O2) -- (OO2);
    %\draw[very thick, blue] (O1) -- (OO1);
    \draw[very thick, blue] (O5) -- (OO5);
    \draw[blue] (O3) -- (OO3);
    \draw[blue] (O4) -- (OO4);
    \fill[gray,opacity=0.2] (A4) -- (A3) -- (C3) -- (C4);
    \fill[gray,opacity=0.2] (A3) -- (A2) -- (C2) -- (C3);
    \end{tikzpicture}
    \caption{Illustration of a cut-off dual cell at the boundary. Compared to the interior case, the dual cells at boundary are cut off. Besides, an extra dual face (with thick blue edges) as well as their edges are supplemented to close the dual mesh. Note that this supplementary face is not necessarily flat, and its edges are not necessarily straight, as is shown here.}
    \label{fig:illustraion_dual_boundary}
\end{figure}

\section{Interpolation of electromagnetic quantities} \label{sec:interpolation}
The coupling of the two subsystems is bidirectional, in the sense that the Maxwell system impacts the Euler system through the Lorentz force while the latter provides information about charges and currents to the former. Since the currents, as is indicated by (\ref{equ:maxwell_grid_ampere}), are defined at dual faces and appear as mass fluxes in the fluid equations, the Euler system is discretized on the dual mesh. Therefore, an issue occurs because the component-wise electromagnetic fields are required to compute the Lorentz force inside the dual cells whereas the Maxwell system can only provide the integral form due to the nature of FIT. Hence the interpolation from the integral form on either edges or faces to the vector form at the cell center has to be tackled.

The problem is summarized as:
\begin{itemize}
    \item[-] Given the flux at each face of a polyhedron, reconstruct the vector field at the cell center;
    \item[-] Given the projection at each edge of a polyhedron, reconstruct the vector field at the cell center. 
\end{itemize}
We adopt the principle of least square fitting, and try to reconstruct the \emph{constant} vector field inside each cell. Specifically, assuming a polyhedral cell with $k$ faces with areas $\{A_i\}_{i=1}^k$, normal vectors $\{\mathbf{n}_i\}_{i=1}^k$ and fluxes $\{f_i\}_{i=1}^k$, one wants to find a vector $\mathbf{h}$ satisfying 
\begin{equation*}
    \mathbf{h} = \argmin_{h\in \mathbb{R}^3} \sum_{i=1}^k(A_i\mathbf{h} \cdot \mathbf{n}_i - f_i)^2.   
\end{equation*}
The solution can be easily expressed as
\begin{equation*}
    \mathbf{h} = (\mathbb{K}^T\mathbb{K})^{-1}\mathbb{K}^T\mathbf{f},
\end{equation*}
where
\begin{equation*}
    \mathbb{K} = [A_1\mathbf{n}_1, A_2\mathbf{n}_2, \cdots, A_k\mathbf{n}_k]^T,\ \ \ \mathbf{f} = [f_1, f_2, \cdots, f_k]^T,
\end{equation*}
and each vector in $\mathbb{R}^3$ is treated as a column vector.

The interpolation based on the integral quantities on edges can be done similarly, namely to find a constant vector field that minimizes the square error. This approach amounts to a first-order interpolation in the sense that a constant vector field can be precisely reconstructed. Assembling the local interpolation of each dual cell, we end up getting the global interpolation relation
\begin{equation}
    \mathbf{E} = \Tilde{\mathbb{R}}_E\mathbf{e},
    \ \ \ \ 
    \mathbf{B} = \Tilde{\mathbb{R}}_B\mathbf{b},
\end{equation}
where $\mathbf{e}, \mathbf{b}$ are electric voltage vector and magnetic flux vector defined in (\ref{equ:fit_scale_vector}); $\mathbf{E} := (\mathbf{E}_i)_{i=1}^{N_{\Tilde{V}}}$ and $\mathbf{B} := (\mathbf{B}_i)_{i=1}^{N_{\Tilde{V}}}$ are $N_{\Tilde{V}} \times 3$ matrices stacking the interpolated $\mathbf{E}$-field and $\mathbf{B}$-field at each dual cell center; $\Tilde{\mathbb{R}}_E$ and $\Tilde{\mathbb{R}}_B$ are thus rank-3 tensors that perform interpolation.

The problem of the reconstruction of vector fields on unstructured meshes is a widely studied topic. Apart from the least-square method, other methods include Perot's method \citep{perot_2000}, finite-element-based methods, etc., which potentially can achieve higher-order accuracy. See \cite[][sec. 3.4.4]{fuchs_2021} and the references therein.

\chapter{Asymptotic-preserving Schemes for Euler-Maxwell System}
The objective of AP schemes is to solve problems over different regimes, that is, problems with a huge gap in a certain characteristic scale $\lambda$. An AP scheme expects to provide a uniformly working discretization for arbitrary value of $\lambda$. To this end, two central issues must be solved: first, the dependence of a stability-induced constraint on $\lambda$ has to be alleviated; second, $\lambda \rightarrow 0$ usually poses a singular perturbation problem, and the limiting scheme is supposed to remain valid and consistent to the limiting model.

A plasma is a multi-scale system that involves several scales, e.g. the wave speeds of electromagnetic fields and plasma fluids, and the plasma thermal speed that impacts its response to an external electromagnetic field. The identification of the impact of different characteristic scales is realized by rescaling the equations. The scale of interest in this work is the Debye length $\lambda_D$ that has a strong connection with the quasi-neutrality of plasma.

This chapter is organized as follows. First, we define several typical quantities relying on which the Euler-Maxwell system is rescaled. By making assumptions on the magnitude relations between these typical quantities, the parametrization of the system is limited to the dimensionless Debye length $\lambda$ and the quasi-neutral behavior can thus be identified. Afterward comes the presentation of an AP scheme. The asymptotic stability and consistency, namely the two properties as are defined in definition \ref{def:ap}, are discussed for this scheme. At last, we talk about two issues, namely boundary conditions and the presence of an insulating domain, that hinders the construction of AP schemes in the way that they could undermine the well-posedness of the problem in the limiting case.

\section{Rescaling of Euler-Maxwell system} \label{sec:rescaling}
The multi-scale nature of the Euler-Maxwell system is revealed by defining different dimensionless parameters. In particular, the quasi-neutrality approximation is clarified. The rescaling procedure mostly sticks to that of \cite{degond_2017}.

First, typical values for each quantity, as well as the characteristic length and time scale are specified. Rescaled by these values, the magnitude of each term of the equations can be compared according to the presumption on the magnitude of these typical values. We define $\overline{x}$ and $\overline{t}$ as space and time scale of interest, by which the reference velocity $\overline{v}$ is defined as $\overline{x}/\overline{t}$. The typical magnitudes of electromagnetic fields are $\overline{E}$ and $\overline{B}$. The typical magnitudes of fluid quantities are denoted by $\overline{u}$ for plasma drift velocity, $\overline{n}$ for plasma number density, $\overline{T}$ for plasma temperature. On top of that, the typical pressure is set $\overline{n}k_B\overline{T}$ with $k_B$ being the Boltzmann constant; the typical value for the specific total energy and enthalpy is set $\overline{u}^2$. Together with the physical parameters, namely, permittivity $\varepsilon_0$, permeability $\mu_0$, light speed $c^2 = (\varepsilon_0\mu_0)^{-1}$, Boltzmann constant $k_B$, the elementary charge $e$, and ion mass $m_i$, the following dimensionless parameters are induced,
\begin{align*} 
    \xi &:= \frac{\overline{v}}{c} \text{ the velocity of interest to the light speed}, &\\
    \zeta &:= \frac{\overline{u}}{\overline{v}} \text{ the plasma velocity to the speed of interest}, &\\
    M &:= \frac{\overline{u}}{v_{th,i}} \text{ the plasma drift velocity to the thermal speed of ions, where } v_{th,i} := \left(\frac{k_B \overline{T}}{m_i}\right)^{1/2}, &\\
    \eta &:= \frac{e\overline{E}\overline{x}}{m_i\overline{u}^2} \text{ the electric energy to the kinetic energy of ions}, &\\
    \beta &:= \frac{\overline{v}\overline{B}}{\overline{E}} \text{ the induced electric field to the total electric field}, &\\
    \lambda &:= \frac{\lambda_D}{\overline{x}} \text{ the dimensionless Debye length, where }\lambda_D := \left(\frac{\varepsilon_0k_B\overline{T}}{e^2\overline{n}}\right)^{1/2}, &\\
    \varepsilon_*^2 &:= \frac{m_*}{m_i} \text{ the species mass ratio to the ion mass},\ \  * \in \{i,e,n,\cdots\}, &\\
    g &:= \frac{1}{\overline{n}\lambda_D^3} \text{ the plasma parameter\footnotemark}.&
\end{align*}
\footnotetext{It is basically the reciprocal of the number of particles per Debye sphere, see \cite[][sec. 1.1]{gibbon2020}. Classical plasma theory assumes $g \ll 1$.}

The Euler-Maxwell system (\ref{equ:maxwell_faraday}) to (\ref{equ:euler_}) is readily to be rescaled by nondimensionalizing each quantity with respect to its typical value. By abuse of notation, the dimensionless quantities have the same symbol with their original ones without incurring any ambiguity. For simplicity, we only consider the collision terms, namely $\Gamma_* = 0, \mathbf{R}_* = \mathbf{R}_*^\text{coll}, Q_* = 0$ in (\ref{equ:euler_}), while neglecting other effects. The rescaled Euler-Maxwell system reads
\begin{align}
    \beta \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday_rescalling} \\ 
    \lambda^2 \partial_t \mathbf{E} - \frac{\beta \lambda^2}{\xi^2}\nabla \times \mathbf{B} &= - \frac{\zeta}{\eta M^2}\mathbf{J}, \label{equ:maxwell_ampere_rescalling} \\
    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B_rescalling}\\
    \lambda^2 \eta M^2 \nabla \cdot \mathbf{E} &= \rho, \label{equ:maxwell_gauss_D_rescalling} \\
    \partial_t
    \begin{bmatrix}
    n_* \\
    n_* \mathbf{u}_* \\
    n_* e_*
    \end{bmatrix}
    + \nabla \cdot
    \begin{bmatrix}
    \zeta n_* \mathbf{u}_* \\
    \zeta n_* \mathbf{u}_* \otimes \mathbf{u}_* + \zeta M^{-2} \varepsilon_*^{-2} p_*\mathbb{I} \\
    \zeta n_* h_* \mathbf{u}_*
    \end{bmatrix}
    &=
    \begin{bmatrix}
    0 \\
    \eta \zea \varepsilon_*^{-2} q_* n_*\mathbf{E} + \eta \zeta^2 \beta \varepsilon_*^{-2} q_* n_* \mathbf{u}_* \times \mathbf{B} \\
    \zeta \eta \varepsilon_*^{-2} \mathbf{J}_* \cdot \mathbf{E}
    \end{bmatrix} +
    \begin{bmatrix}
    0 \\
    \varepsilon_*^{-2}\mathbf{R}_*^{\text{coll}} \\
    0 
    \end{bmatrix}, \label{equ:euler_rescalling}
\end{align}
where the equation of state becomes $e_* = \frac{1}{2}|\mathbf{u_*}|^2 + M^{-2}\frac{p_*}{\epsilon^2_* n_* (\gamma - 1)}$ and $h_* = e_* + M^{-2}\frac{p_*}{\epsilon^2_* n_*}$. For a fully-ionized gas, we have the original expression of $\mathbf{R}_*^{\text{coll}}$ in (\ref{equ:collision}), and its rescaled expression becomes
\begin{equation*}
    \mathbf{R}_i^{\text{coll}} = \frac{Z\text{ln}\Lambda}{16\pi}g\lambda^{-1}M^{-1}\varepsilon_en_en_i(\mathbf{u}_i - \mathbf{u}_e). 
\end{equation*}

Following the assumption in \cite{degond_2017}, the reference speed $\overline{v}$ is of the same scale with the plasma speed $\overline{u}$ and the thermal speed $v_{th,i}$ whereas it is much smaller than the light speed $c$. To study the quasi-neutral regime, the dimensionless Debye length $\lambda$ is an asymptotic parameter ranging in $[0,1]$. It is assumed that $\alpha$ has the same magnitude as $\lambda$, and $\eta$ and $\beta$ are of order one.

Special treatment is needed for the collision term. One would notice the inverse proportionality to $\lambda$, which would introduce a singular perturbation to the Euler system as $\lambda \rightarrow 0$. However, the validity of such a collision model is doubtful when $\lambda \rightarrow 0$. From the physical viewpoint, the shielding effect characterized by Debye length $\lambda$ makes the impact parameter no larger than $\lambda$. The $\lambda \rightarrow 0$ limit implies that the collisions happen in the atomic length scale, in which quantum-mechanical effects must be taken into effect \citep{frank_1972}. Therefore, for simplicity, we decide to assume $g \sim \lambda$ and keep the prefactor of collision term constant $\alpha^{\text{coll}}$ throughout the simulation\footnote{The reasonableness of this assumption is questionable.}.

In summary, we make the following choices
\begin{align*}
    \xi \sim g \sim \lambda \in [0,1], \ \ \ \zeta \sim M \sim \eta \sim \beta \sim \mathcal{O}(1).
\end{align*}

Under such assumptions on these dimensionless parameters, the rescaled Euler-Maxwell system is simplified into a parametrized system with the dimensionless Debye length $\lambda$ being the asymptotic parameter
\begin{align}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday_rescaled} \\ 
    \lambda^2 \partial_t \mathbf{E} - \nabla \times \mathbf{B} &= - \mathbf{J}, \label{equ:maxwell_ampere_rescaled} \\
    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B_rescaled}\\
    \lambda^2 \nabla \cdot \mathbf{E} &= \rho, \label{equ:maxwell_gauss_D_rescaled} \\
    \partial_t
    \begin{bmatrix}
    n_* \\
    n_* \mathbf{u}_* \\
    n_* e_*
    \end{bmatrix}
    + \nabla \cdot
    \begin{bmatrix}
    n_* \mathbf{u}_* \\
    n_* \mathbf{u}_* \otimes \mathbf{u}_* + \varepsilon_*^{-2} p_*\mathbb{I} \\
    n_* h_* \mathbf{u}_*
    \end{bmatrix}
    &=
    \begin{bmatrix}
    0 \\
    \varepsilon_*^{-2} q_* n_* (\mathbf{E} + \mathbf{u}_* \times \mathbf{B}) \\
    \varepsilon_*^{-2} \mathbf{J}_* \cdot \mathbf{E}
    \end{bmatrix}+
    \begin{bmatrix}
    0 \\
    \varepsilon_*^{-2}\mathbf{R}_*^{\text{coll}} \\
    0 
    \end{bmatrix}, \label{equ:euler_rescaled}
\end{align}
with the equation of state $e_* = \frac{1}{2}|\mathbf{u_*}|^2 + \frac{p_*}{\varepsilon^2_* n_* (\gamma - 1)}$ and $h_* = e_* + \frac{p_*}{\varepsilon^2_* n_*}$. For a fully-ionized gas with only ions and electrons, 
\begin{equation} \label{equ:collision_rescaled} 
    \mathbf{R}_i^{\text{coll}} = \alpha^{\text{coll}}n_en_i(\mathbf{u}_i - \mathbf{u}_e) = - \mathbf{R}_e^{\text{coll}}.
\end{equation}

Although the rescaling of the equations involves considerable physical intuitions on the decision of typical values and their magnitudes, which is crucial to reach a physically meaningful problem, we are now in a position to forget this reasoning, and focus on the singular perturbation problem parameterized by $\lambda$. The rescaling enables us to identify the magnitude of each term of the equations, which is revealed by the prefactor polynomial of $\lambda$. The consequence of vanishing $\lambda$, namely the quasi-neutrality, will be discussed in the next section.

\section{Quasi-neutral limit} \label{sec:quasi-neutral_limit}
As is already discussed in section \ref{sec:quasi-neutrality}, the quasi-neutrality, being an important character of plasmas, refers to the fact that the net charge of the free electrons and ions in plasmas cancel out over an area of the same order as the Deybe length $\lambda_D$. When the typical length scale $\overline{x}$ is of magnitudes larger than $\lambda_D$, the condition $\rho = 0$ can be approximately satisfied.

Such behavior is clearly explained through the rescaled Euler-Maxwell system (\ref{equ:maxwell_faraday_rescaled}) to (\ref{equ:euler_rescaled}). By formally taking dimensionless Debye length $\lambda$ to zero\footnote{The convergence of the solutions as $\lambda$ tending to zero is discussed in \cite[][chap. 2]{remi_2014}}, the Maxwell system becomes 
\begin{align}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday_limit} \\ 
    - \nabla \times \mathbf{B} &= - \mathbf{J}, \label{equ:maxwell_ampere_limit} \\
    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B_limit}\\
     0 &= \rho. \label{equ:maxwell_gauss_D_limit}
\end{align}
One can notice that the quasi-neutral condition (\ref{equ:maxwell_gauss_D_limit}) is the consequence of taking $\lambda = 0$ in Gauss's law for electric field (\ref{equ:maxwell_gauss_D_rescaled}). Like the non-neutral case, Gauss's laws (\ref{equ:maxwell_gauss_B_limit}) (\ref{equ:maxwell_gauss_D_limit}) are the consequence of (\ref{equ:maxwell_faraday_limit}) (\ref{equ:maxwell_ampere_limit}) provided (\ref{equ:maxwell_gauss_B_limit}) (\ref{equ:maxwell_gauss_D_limit}) are satisfied at the initial time.

The vanishing time derivative of $\mathbf{E}$-field is an indicator of the singular perturbation nature of the quasi-neutral model. To be specific, in the non-neutral model the $\mathbf{E}$-field evolves with time whereas in the quasi-neutral model it responds instantaneously to other quantities according to the constraint (\ref{equ:maxwell_ampere_limit}). To make it clear, we replace the equation (\ref{equ:maxwell_ampere_rescaled}) by the sum of the curl of (\ref{equ:maxwell_faraday_rescaled}) and the time-derivative of (\ref{equ:maxwell_ampere_rescaled}). Meanwhile exploiting the momentum equation in (\ref{equ:euler_rescaled}) to express $\partial_t\mathbf{J}$, we end up getting the reformulated Maxwell's equations
\begin{align}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday_reform}\\
    \lambda^2\partial_t^2 \mathbf{E} + \nabla \times \nabla \times \mathbf{E} &= - a\mathbf{E} - \mathbf{b}, \label{equ:maxwell_ampere_reform}\\
    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B_reform}\\
    \lambda^2\nabla \cdot \mathbf{E} &= \rho, \label{equ:maxwell_gauss_D_reform}
\end{align}
where
\begin{equation*}
    a = \sum_*\varepsilon_*^{-2}q_*^2n_*, \ \ \ \mathbf{b} = \sum_* \epsilon_*^{-2}q_*^2n_*\mathbf{u}_*\times\mathbf{B} - q_*\nabla\cdot(n_* \mathbf{u}_* \otimes \mathbf{u}_* + \varepsilon_*^{-2}p_*\mathbb{I}).
\end{equation*}
It is easy to check that (\ref{equ:maxwell_faraday_reform}) to (\ref{equ:maxwell_ampere_reform}) is equivalent to (\ref{equ:maxwell_faraday_rescaled}) to (\ref{equ:maxwell_gauss_D_rescaled}) as soon as (\ref{equ:maxwell_ampere_rescaled}) is satisfied at the initial time. The equation (\ref{equ:maxwell_ampere_reform}) implies the shift from the hyperbolic nature to the elliptic nature of the $\mathbf{E}$-field as $\lambda\rightarrow0$. One of the key aims of designing an AP scheme is to reproduce this shift at the discrete level.

\section{AP schemes}
In this section, we present the full discretization with AP property. The general approach for spatial discretizations of both the Euler and Maxwell's equations has been introduced in chapter \ref{chap:discretization_euler_maxwell}. As stability is a central issue for the AP property, this section is mostly devoted to the time discretization of the Euler-Maxwell system.

We want to first recall the objective of AP schemes and make clear the direction to proceed towards. By definition \ref{def:ap}, the stability condition that does not depend on $\lambda$ and the consistency of the limit scheme with the quasi-neutral system have to be fulfilled. Furthermore, what is desired for the numerical treatment of Maxwell's equations is that Gauss's law is satisfied at the discrete level. To sum up, the following properties of the constructed scheme are to be realized:

\begin{itemize}
    \item[I] stable regardless of the value of $\lambda$;
    \item[II] the limit scheme by taking $\lambda = 0$ is valid\footnote{By ``valid" we mean the scheme is a valid recursion such that the state at $t^{m+1}$ can be \emph{uniquely} computed by that at $t^m$.} and consistent to its continuous counterpart (\ref{equ:maxwell_faraday_limit}) to (\ref{equ:maxwell_gauss_D_limit});
    \item[III] Gauss's law (\ref{equ:maxwell_gauss_D_rescaled}) is fulfilled at the discrete level for any $\lambda$. \label{condition3}
\end{itemize}

Given the mesh pair $(\mathcal{M}, \Tilde{\mathcal{M}})$, Maxwell's equations are handled by the FIT framework while FVM is applied to Euler equations on the dual mesh 
$\Tilde{\mathcal{M}}$. Naturally extending the AP scheme for 1D two-fluid plasma proposed in \cite{degond_2012} to which the detailed constructing procedure should be referred, we straightforwardly present the full-discretization scheme for 3D multi-species plasma:

\begin{align}
    \delta_m^{-1} (\mathbf{b}^{m+1} - \mathbf{b}^{m}) \hspace{0.4cm}&\;+\; \hspace{1.5cm}\mathbb{C}\textcolor{blue}{\mathbf{e}^{m+1}}\hspace{1.25cm}=\; 0, \label{equ:maxwell_faraday_ap}\\
    \lambda^2\delta_m^{-1}(\mathbf{d}^{m+1} - \mathbf{d}^m) \hspace{0.4cm}&\;-\; \hspace{1.5cm}\Tilde{\mathbb{C}}\textcolor{blue}{\mathbf{h}^{m+1}} \hspace{1.22cm}=\; - \textcolor{blue}{\mathbf{j}^{m+1}}, \label{equ:maxwell_ampere_ap}\\
    \delta_m^{-1}(\mathbf{U}_{*,k}^{m+1} - \mathbf{U}_{*,k}^{m}) \hspace{0.10cm}&\;+\;  \frac{1}{|\Tilde{V}_k|}\sum_{j:\Tilde{A}_j\in\partial\Tilde{V}_k}|\Tilde{A}_j|\textcolor{blue}{\overline{\mathbf{F}}_{*,j}^{m+1/2}} \hspace{0.05cm}=\; \textcolor{blue}{\mathbf{RHS}_{*,k}^{m+1/2}}, \label{equ:euler_ap}
\end{align}
where 
\begin{align}
    \mathbf{U}_{*,k}^{m} &=
    \begin{bmatrix}
    n_* \\
    n_* \mathbf{u}_* \\
    n_* e_*
    \end{bmatrix}^m_k, \\
    \overline{\mathbf{F}}_{*,j}^{m+1/2} &=
    \begin{bmatrix}
    f^{m+1}_{n,*,j} \\
    \bm{f}^m_{u,*,j} \\
    f^m_{e,*,j} 
    \end{bmatrix}
    = 
    \begin{bmatrix}
    \frac{1}{2}\left[\textcolor{blue}{(nu_{\bot})_{*,k}^{m+1}} + \textcolor{blue}{(nu_{\bot})_{*,k+1}^{m+1}}\right] - \frac{1}{2}s^m_{*,k+1/2}(n_{*,k+1}^m - n_{*,k}^m) \\
    \frac{1}{2}\left[(nu_{\bot}\mathbf{u})^m_{*,k} + (nu_{\bot}\mathbf{u})^m_{*,k+1} + p_{*,k}^m\mathbf{n}_j + p_{*,k+1}^m\mathbf{n}_j\right] - \frac{1}{2}s^m_{*,k+1/2}\left[(n\mathbf{u})^m_{*,k+1} - (n\mathbf{u})^m_{*,k}\right] \\
    \frac{1}{2}\left[(nhu_\bot)^m_{*,k} + (nhu_\bot)^m_{*,k+1}\right] - \frac{1}{2}s^m_{*,k+1/2}\left[(ne)^m_{*,k+1} - (ne)^m_{*,k}\right]
    \end{bmatrix}, \label{equ:flux_ap}\\
    \mathbf{RHS}_{*,k}^{m+1/2} &=
    \begin{bmatrix}
    0 \\
    \varepsilon_*^{-2}q_*\left[n_*^m\textcolor{blue}{\mathbf{E}^{m+1}} + (n\mathbf{u})^m_*\times\mathbf{B}^m\right] \\
    \varepsilon_*^{-2}q_*(n\mathbf{u})^m_* \cdot \textcolor{blue}{\mathbf{E}^{m+1}}
    \end{bmatrix}_k +
    \begin{bmatrix}
    0 \\
    \varepsilon_*^{-2}\textcolor{blue}{\mathbf{R}_{*,k}^{\text{coll},m+1}} \\
    0
    \end{bmatrix}, \label{equ:rhs_ap}\\
    \mathbf{R}_{*,k}^{\text{coll},m+1} &= 
    \begin{cases}
    \alpha^\text{coll}\left[n_{e,k}^m\textcolor{blue}{(n\mathbf{u})^{m+1}_{i,k}} - n_{i,k}^m\textcolor{blue}{(n\mathbf{u})^{m+1}_{e,k}}\right] \text{  if  } * = e \\
    \alpha^\text{coll}\left[n_{i,k}^m\textcolor{blue}{(n\mathbf{u})^{m+1}_{e,k}} - n_{e,k}^m\textcolor{blue}{(n\mathbf{u})^{m+1}_{i,k}}\right] \text{  if  } * = i
    \end{cases}  \\
    \mathbf{j}^{m+1} &= \left(\sum_*\pm q_*\textcolor{blue}{f^{m+1}_{n,*,j}}|\Tilde{A}_j|\right)_{j=1}^{N_{\Tilde{A}}}, \label{equ:current_ap}\\
    \mathbf{d}^m &= \mathbb{M}_\varepsilon \mathbf{e}^m, \ \ \ \mathbf{h}^m = \mathbb{M}_\mu^{-1} \mathbf{b}^m. \label{equ:material_law}
\end{align}
In the above scheme, the superscript $m$ indicates the number of iterations, and the quantities with superscript $m+1/2$ implies its dependency on the quantities at both $m$-th and $(m+1)$-th iterations; $\delta_m$ is the time step size for the $m$-th iteration. The numerical flux (\ref{equ:flux_ap}), where $u_\perp$ stands for the velocity component normal to the dual face $\Tilde{A}_j$, is just the application of the generic Rusanov flux (\ref{equ:rusanov-flux-3d}) on the Euler equations, see also the expression (\ref{equ:rusanov_flux_euler}) in the appendix.

By abuse of notations, quantities with subscript $k+1$ are associated with the adjacent cell of $\Tilde{V}_k$ with respect to $\Tilde{A}_j$, which should not be confused with its real index. $\mathbf{n}_j$ is the outer normal of $\Tilde{A}_j$ as a face of $\Tilde{V}_k$. Since the equations have been rescaled into the dimensionless form, the material matrices $\mathbb{M}_\varepsilon = \text{diag}(\{|\Tilde{A}_i|/{|L_i|}\}_i)$, $\mathbb{M}_\varepsilon = \text{diag}(\{{|A_i|}/{|\Tilde{L}_i|}\}_i)$ now only depend on the meshes.

Recall that the discrete Euler system (\ref{equ:euler_ap}) is defined on the dual mesh $\Tilde{\mathcal{M}}$, and hence $\mathbf{E}^{m+1}$ and $\mathbf{B}^m$ in (\ref{equ:rhs_ap}) are the interpolated vector fields at dual cell center as is illustrated in section \ref{sec:interpolation}. The $\pm$ in (\ref{equ:current_ap}) arises from the fact that the direction of numerical fluxes is determined by the outer normal of each cell whereas each component in $\mathbf{j}^{m+1}$ is defined to be aligned with the internal orientation of the dual face it associates with. Hence a flip of the sign may be necessary.

First, we would like to discuss the necessity of the implicit terms (highlighted in blue color). The implicit treatment of electric field in (\ref{equ:rhs_ap}) is a must to ensure stability and is justified in \cite{fabre_1992} for the Euler-Poisson system. It is reasonable to infer that it applies equally to the Euler-Maxwell system. To guarantee Gauss's law at the discrete level, the current in (\ref{equ:maxwell_ampere_ap}), as well as the mass flux in (\ref{equ:flux_ap}), must be at the same implicit level. The reformulated Ampere's law (\ref{equ:maxwell_ampere_reform}) gives us some clue that in the quasi-neutral case the right-hand side, arising from the electric current, must be implicit to lead to a valid and unique time-stepping. Furthermore, we stress that the current (\ref{equ:current_ap}) is evaluated by the numerical mass flux rather than its original definition $\sum_*n_*q_*\mathbf{u}_*$ for the sake of consistency to the discrete Gauss's law. The implicitness of the electric field in (\ref{equ:maxwell_faraday_ap}) and the magnetic flux in (\ref{equ:maxwell_ampere_ap}) is necessary for unconditional stability with respect to $\lambda$, as is demonstrated by \cite{degond_2012} through a linearized analysis. The implicitness of the friction term is owing to the stiffness incurred from a potentially large value of $\varepsilon^{-2}_*\alpha^\text{coll}$.

Now we deduce the limiting scheme and check its validity and consistency. By formally setting $\lambda = 0$ in the AP scheme (\ref{equ:maxwell_faraday_ap}) to (\ref{equ:euler_ap}), the equation for evolving the electric edge voltages (\ref{equ:maxwell_ampere_ap}) degenerates into a constraint that should be satisfied at each step, namely
\begin{equation*}
     \Tilde{\mathbb{C}}\mathbb{M}_\mu^{-1}\mathbf{b}^{m+1} = - \mathbf{j}^{m+1}.
\end{equation*}
We want to check the consistency of the limiting scheme with the quasi-neutral model, and especially to check if the constraint (\ref{equ:maxwell_ampere_reform}) when $\lambda = 0$ is correctly discretized. To that end, we mimic the procedure to derive (\ref{equ:maxwell_ampere_reform}) in a discrete way, which leads to
\begin{equation*}
    (\Tilde{\mathbb{C}}\mathbb{M}_\mu^{-1}\mathbb{C}\mathbf{e}^{m+1})_j / |\Tilde{A}_j| = - \frac{1}{2}(a_{j,k}^m\mathbf{E}^{m+1}_{j,k} + a_{j,k+1}^m\mathbf{E}^{m+1}_{j,k+1})\cdot \mathbf{n}_j - \frac{1}{2}(\mathbf{b}_{j,k}^m + \mathbf{b}_{j, k+1}^m) \cdot \mathbf{n}_j - \pi_j^m,
\end{equation*}
where
\begin{align*}
    a_{j,k}^m &= \sum_*\pm\varepsilon_*^{-2}q_*^2n^m_{*,k}, \\
    \mathbf{b}_{j,k}^m &= \sum_*\pm\varepsilon_*^{-2}q_*\left[(n\mathbf{u})^m_{*,k}\times\mathbf{B}^m_k - \frac{1}{|\Tilde{V}_k|}\sum_{i:\Tilde{A}_i\in\partial\Tilde{V}_k}|\Tilde{A}_i|\bm{f}_{u,*,i}^m\right], \\
    \pi^m_j &= - \frac{1}{2} \delta_m^{-1} \sum_* \pm q_* \left[s_{*,k+1/2}^m(n^m_{*,k+1} - n^m_{*,k}) - s^{m-1}_{*,k+1/2}(n^{m-1}_{*,k+1} - n^{m-1}_{*,k})\right].
\end{align*}
Comparison with (\ref{equ:maxwell_ampere_reform}) manifests the consistency when $\lambda = 0$, given the fact that $\pi^m_j = \mathcal{O}(h)$ where h is cell size.

One should be aware that such a scheme merely meets the necessary conditions of AP property while we do not rigorously prove that it is AP. The difficulty to prove the nonlinear stability for such a complex system is notorious. Also as is mentioned throughout the thesis, the convergence of the continuous solutions as $\lambda \rightarrow 0$ is taken for granted. Therefore, instead of rigorously proving the scheme to be AP, the procedure shown here should be treated as a heuristic approach for constructing AP schemes, and one should always turn to numerical experiments for verification.

\section{CFL condition}

It has been shown in \cite{degond_2012} that the stability-induced constraint on the time-step size does not depend on the value of $\lambda$ thanks to the implicitness in the discrete Maxwell system. However, the Euler system is discretized by an explicit scheme and thus still subject to a CFL condition which we want to specify here.

In standard conservation laws where no source term is present, the CFL condition is solely dependent on the numerical flux (recall Rusanov flux (\ref{equ:rusanov-flux-3d})) and mesh size $\delta_x$. Classically one restricts the time step size by $\delta_t < \delta_x/s$ where $s$ represents the maximum wave speed over all the cells.

To be noticed is that the presence of source terms might poses more constraint. Let us consider the model equation
\begin{equation*}
    \partial_tu + c\partial_xu = \beta u, 
\end{equation*}
where $c>0$ and $\beta<0$ are constant. By a first-order upwind scheme
\begin{equation*}
    \delta_t^{-1}(u^{m+1}_k - u^m_k) + c\delta_x^{-1}(u^m_k - u^m_{k-1}) = \beta u^m_k,
\end{equation*}
we can perform Neumann analysis and deduce the CFL condition
\begin{equation*}
    \delta_t \leq \left[\frac{c}{\delta_x} + \frac{\beta}{2}\right]^{-1}.
\end{equation*}
On noticing the source term $\varepsilon_*^{-2}q_*(n\mathbf{u})^m_*\times\mathbf{B}^m$ in the momentum equation, we heuristically take the following restriction
\begin{equation*}
    \delta_t^m \leq \min_*\bigg\{\left[\frac{s^m_*}{\delta_x} + \frac{\varepsilon^{-2}_*|q_*||\mathbf{B}^m|}{2}\right]^{-1}\bigg\},
\end{equation*}
which is proven necessary by numerical experiments.

A short remark goes to the factor $\varepsilon_*^{2}$, the mass ratio with respect to a reference mass. Because of the small mass of electrons, this factor can be very penalizing as it leads to a stiff time-stepping for heavy species. It is possible and interesting to devise a scheme that is AP with respect to the limit of vanishing $\varepsilon_e^{2}$ \citep{degond_2008}.

\section{Impact of boundary conditions} \label{sec:impact_of_bc}
We want to talk about the problems that may arise due to inappropriate BCs when taking $\lambda \rightarrow 0$. Since the scheme is supposed to work for both regimes, the BCs ought to be uniformly well-posed. An example is given to convey the idea. Let's look at the continuous non-neutral Amp\`{e}re's law (\ref{equ:maxwell_ampere_rescaled})
\begin{equation*}
    \lambda^2 \partial_t \mathbf{E} - \nabla \times \mathbf{B} = - \mathbf{J},
\end{equation*}
which loses its hyperbolic character and becomes a constraint when $\lambda \rightarrow 0$. Now consider two boundary conditions
\begin{itemize}
    \item[-]  $\mathbf{E}\cdot\mathbf{n} = 0$ on $\partial\Omega$;
    \item[-] $\nabla \times \mathbf{B} \cdot\mathbf{n} = \mathbf{J}\cdot\mathbf{n}$ on $\partial\Omega$. 
\end{itemize}
They are equivalent when $\lambda$ is non-zero provided $\mathbf{E}\cdot\mathbf{n}|_{\partial\Omega}$ is zero at the initial time. However, setting $\lambda = 0$ destroys the equivalence. The second BC no longer implies the first one and becomes redundant since the quasi-neutral Amp\`{e}re's law already enforces such condition, which ruins the well-posedness of the quasi-neutral problem. Hence the first BC is the one that is supposed to be employed.

From the viewpoint of the discrete model, the continuous equations are discretized into a set of algebraic equations according to the scheme, and they are assembled into a linear system that needs to be solved at each time step. The redundancy of the second BC at limiting case results in the singularity of the linear system since the BC can be derived by linear operations from the algebraic form of the PDEs. This issue and how BCs are incorporated in the numerical scheme will be elaborated in Chapter \ref{chap:numerical_experiments_in_3d}.

\section{Impact of insulating domain} \label{sec:impact_insulating_domain}

In many applications, plasmas might be confined by insulating solid walls in which the electromagnetic fields are of interest as well. An example is sketched in Fig. \ref{fig:sketch_domain_fusch} which is the test case in \cite{fuchs_2021}. The plasma is enclosed by an insulating solid sleeve where no charged particles exist. Such a setting implies that the plasma domain, where the Euler system is defined, does not make up the whole domain, where the Maxwell system is defined. 
\begin{figure}
    \centering
    \begin{tikzpicture}
    \coordinate (O1) at (0,0);
    \draw[very thick] (O1) circle (1) node {Cathode};
    \fill[blue, opacity=0.2] (O1) circle (1);
    \draw[very thick] (O1) circle (1.5);
    \coordinate (O2) at (4.5,1) ;
    \draw[gray] (O2) circle (1);
    \node at (O2) {Anode};
    \node at (barycentric cs:O1=1,O2=1) {Plasma}; 
    \fill[red, opacity=0.2] (O2) circle (1);
    \coordinate (S1) at ([shift={(-0.196,0.98)}]O1);
    \coordinate (S2) at ([shift={(-0.196,0.98)}]O2);
    \coordinate (P1) at ([shift={(0.196,-0.98)}]O1);
    \coordinate (P2) at ([shift={(0.196,-0.98)}]O2);
    \draw[gray] (S1) -- (S2);
    \draw[gray] (P1) -- (P2);
    \coordinate (SS1) at ([shift={({-0.196*1.5},{0.98*1.5})}]O1);
    \coordinate (SS2) at ([shift={({-0.196*1.5},{0.98*1.5})}]O2);
    \coordinate (PP1) at ([shift={({0.196*1.5},{-0.98*1.5})}]O1);
    \coordinate (PP2) at ([shift={({0.196*1.5},{-0.98*1.5})}]O2);
    \draw[very thick] (SS1) -- (SS2);
    \draw[very thick] (PP1) -- (PP2); 
    \draw[gray] (SS2) arc (101.31:180+101.31:1.5);
    \draw[very thick] (PP2) arc (101.31-180:101.31:1.5);
    \draw[-to] (barycentric cs:SS1=1,SS2=1,S1=1,S2=1) to[out=90,in=0] ([shift={(-0.5,0.5)}]barycentric cs:SS1=1,SS2=1,S1=1,S2=1) node[left] {Solid};
    \begin{scope}[shift={(5.5,-1.4)}]
    \draw[blue, -to] (0,0) -- (0.7,0.14) node[right]{\small $z$};
    \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
    \draw[blue, -to] (0,0) -- (0.7,0) node[below]{\small $y$};
    \end{scope}
    \end{tikzpicture}
    \caption{Sketch of the computational domain of the case in \cite{fuchs_2021}. Different from the one in this thesis (see Fig. \ref{fig:sketch_domain}), there is a solid enclosing sleeve, and the plasma is confined at the inner area.}
    \label{fig:sketch_domain_fusch}
\end{figure}
Consequently, the following Maxwell's equations to be solved in the insulating solid domain
\begin{align}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:tmp__1}\\ 
    \lambda^2 \partial_t \mathbf{E} - \nabla \times \mathbf{B} &= 0,  \label{equ:tmp__3}\\
    \nabla \cdot \mathbf{B} &= 0, \\
    \lambda^2 \nabla \cdot \mathbf{E} &= 0 \label{equ:tmp__2}.
\end{align}
Supplemented by suitable BCs, the problem is well-posed for $\lambda > 0$. Nonetheless, the $\lambda \rightarrow 0$ limit would lose control of the irrotational part of $\mathbf{E}$-field since only the term curl$\mathbf{E}$ remains in the equations when $\lambda = 0$ (equation (\ref{equ:tmp__2}) becomes trivial) and the BCs are not sufficient to uniquely determine an irrotational vector field.

To circumvent this problem, one can possibly, as \cite{fuchs_2021}, define a small electrical conductivity $\sigma$ for the insulating domain so that Amp\`{e}re's law becomes
\begin{equation*}
    \lambda^2 \partial_t \mathbf{E} - \nabla \times \mathbf{B} = \sigma\mathbf{E},
\end{equation*}
and the $\lambda \rightarrow 0$ limit model regains well-posedness.

The quasi-neutral limit of the Maxwell system in insulating mediums shares much similarity with the eddy current approximation where the propagation speed, namely the light speed, is treated as infinite, and the displacement current $\partial_t\mathbf{D}$ is hence omitted. Recall that in Section \ref{sec:rescaling} we assume $\lambda$ has the same order as $\xi$, the ratio of the typical speed and light speed. Therefore, although the Debye length is not defined in the solid domain where no plasma exists, the $\lambda \rightarrow 0$ limit of the Maxwell system (\ref{equ:tmp__1}) to (\ref{equ:tmp__2}) is supposed to be interpreted as the eddy current approximation. Due to the disappearance of the divergence-free constraint (\ref{equ:tmp__2}) when $\lambda = 0$, the system is not well-posed. This failure might be resolved by enforcing vanishing divergence of the $\mathbf{E}$-field at the $\lambda \rightarrow 0$ limit, which is no longer a consequence of Amp\`{e}re's law (\ref{equ:tmp__3}). In this thesis, we do not pursue this way. One would later see that in the numerical experiments, for simplicity, we cancel the solid domain and extend the plasma domain to the whole domain. Similar to applying a small conductivity, this way recovers the connection between the current density and the $\mathbf{E}$-field.

\chapter{Numerical Experiments in 1D}
This chapter is devoted to reproducing the results in \cite{degond_2012} upon which our generalized scheme is built. In their work, 1D problems of one-fluid and two-fluid models are treated by FDTD, in the sense that quantities are defined on staggered structured meshes. As is mentioned before, the FDTD method is a subset of the FIT method, and they are equivalent under Cartesian meshes. One can interpret the FIT treatment of 1D problems through the projection of quantities defined on a 3D Cartesian mesh dual onto a 1D axis, as is depicted in Fig. \ref{fig:1d-frame}.

Although Maxwell's equations are inherently 3D, their reduction in 1D can be derived based on some assumptions and, thanks to great simplification on notations and implementations, helps to test numerical schemes. In this chapter, three cases are tested: one-fluid and two-fluid models tested in \cite{degond_2012}, and additionally the two-fluid model with friction terms. The verification is meant to pave the way for testing in the 3D setting.

\section{One-fluid model}
In the one-fluid model, only the dynamics of electrons are to be simulated while the background ions are fixed with a uniform number density of unity. The ions are singly-charged throughout the thesis if not specifically stated. Since ions are much heavier than electrons, such a model is a reasonable approximation when only the short-term behavior is of interest so that ions have no time to respond.

The rescaled one-fluid Euler-Maxwell system\footnote{In \cite{degond_2012}, the equation (2.11) is wrong since the mass ratio $\varepsilon^2$ is missing whereas it is necessary to reproduce their results.} is adapted from the general system (\ref{equ:maxwell_faraday_rescaled}) to (\ref{equ:euler_rescaled}) by only keeping one set of fluid equations to describe electrons and setting the number density of ions to be unity:
\begin{align}
    & \partial_t n + \nabla\cdot(n \mathbf{u}) = 0, \label{equ:EM_1f_n}\\
    \varepsilon^2[& \partial_t (n \mathbf{u}) + \nabla \cdot (n \mathbf{u} \otimes \mathbf{u})] + \nabla p(n) = -n(\mathbf{E} + \mathbf{u} \times \mathbf{B}), \label{equ:EM_1f_nu}\\
    & \partial_t \mathbf{B} + \nabla \times \mathbf{E} = 0 \label{equ:EM_1f_faraday}. \\
    \lambda^2 & \partial_t \mathbf{E} - \nabla \times \mathbf{B} = n \mathbf{u}, \label{equ:EM_1f_ampere}\\
    & \nabla\cdot \mathbf{B} = 0, \label{equ:EM_1f_gauss_B} \\
    \lambda^2 & \nabla\cdot \mathbf{E} = 1 - n \label{equ:EM_1f_gauss_E}.
\end{align}
where $n$ and $\mathbf{u}$ stands for electron number density and velocity, $\varepsilon^2$ now stands for electron-ion mass ratio $m_e/m_i$ which is taken to be $10^{-4}$ here. Note that the energy equation is removed by assuming adiabatic process, and the equation of state $p(n) = n^\gamma$ with $\gamma = 5/3$ is supplemented.

\subsection{Governing equations in 1D} \label{sec:1f-eqs-1d}
The 3D problem is projected onto the 1D axis by assuming vanishing traverse derivatives (see Fig. \ref{fig:1d-frame} for the definition of reference frame). Besides, $u_y, E_y, B_x, B_z$ are set zero for simplicity, which amounts to considering the TE mode. The collision between particles is omitted for the time being. 
\begin{figure}
    \centering
    \includegraphics[scale=0.2]{1d_frame.png}
    \caption{Projection of the 3D model onto $z$-axis. Let us consider a Cartesian mesh doublet. The reduction is accomplished by assigning the quantities defined on each cross-section, which is parallel to the $x$-$y$ plane, to its intersection point at $z$-axis. Since it is assumed that no variations occur in each cross-section, the quantities in 3D can be compressed by the ones that locate at each mesh point on the $z$-axis.}
    \label{fig:1d-frame}
\end{figure}

Take all the traverse derivatives $\partial_x, \partial_y$ and $u_y, E_y, B_x, B_z$ to be zero, we get the one-fluid Euler-Maxwell system in 1D:
\begin{align*}
    \partial_t n + \partial_z(nu_z) &= 0, \\
    \varepsilon^2[\partial_t(nu_x) + \partial_z(nu_zu_x)] &= - n(E_x - u_zB_y), \\
    \varepsilon^2[\partial_t(nu_z) + \partial_z(nu_z^2)] + \partial_z(p(n)) &= -n(E_z + u_xB_y), \\
    \partial_t B_y + \partial_z E_x &= 0, \\
    \lambda^2 \partial_t E_x + \partial_z B_y &= nu_x, \\
    \lambda^2 \partial_t E_z &= nu_z, \\
    \lambda^2 \partial_z E_z &= 1 - n,
\end{align*}
as well as the quasi-neutral limit by taking $\lambda \rightarrow 0$:
\begin{align*}
    n &= 1\\
    \varepsilon^2 \partial_t(u_x) &= - E_x, \\
    E_z + u_xB_y &= 0, \\
    u_z &= 0 \\
    \partial_t B_y + \partial_z E_x &= 0, \\
    \partial_z B_y &= nu_x
\end{align*}

\subsection{Full discretization} \label{sec:1f1d-discretization}
Adapt the AP scheme (\ref{equ:maxwell_faraday_ap}) to (\ref{equ:euler_ap}) to this case, and we end up with
\begin{align}
    \frac{n^{m+1}_k - n^m_k}{\delta^m} + \frac{\textcolor{blue}{f^{m+1/2}_{n,k+1/2} - f^{m+1/2}_{n,k-1/2}}}{h} &= 0, \label{equ:1f1d-n}\\
    \frac{(nu_x)^{m+1}_k - (nu_x)^m_k}{\delta^m} + \frac{f^{m}_{u_x,k+1/2} - f^{m}_{u_x,k-1/2}}{h} &= -\frac{n^m_k \textcolor{blue}{E^{m+1}_{x,k}}}{\varepsilon^2} + \frac{n^m_k u^m_{z,k}\Tilde{B}^m_{y,k}}{\varepsilon^2}, \label{equ:1f1d-nux}\\
    \frac{(nu_z)^{m+1}_k - (nu_z)^m_k}{\delta^m} + \frac{f^{m}_{u_z,k+1/2} - f^{m}_{u_z,k-1/2}}{h} &= - \frac{n^m_k \textcolor{blue}{\Tilde{E}^{m+1}_{z,k}}}{\varepsilon^2} - \frac{n^m_k u^m_{x,k}\Tilde{B}^m_{y,k}}{\varepsilon^2}, \label{equ:1f1d-nuz}\\ 
    \frac{B^{m+1}_{y,k+1/2} - B^{m}_{y,k+1/2}}{\delta^m} + \frac{\textcolor{blue}{E^{m+1}_{x,k+1} - E^{m+1}_{x,k}}}{h} &= 0, \label{equ:1f1d-By}\\
    \lambda^2 \frac{E^{m+1}_{x,k} - E^{m}_{x,k}}{\delta^m} + \frac{\textcolor{blue}{B^{m+1}_{y,k+1/2} - B^{m+1}_{y,k-1/2}}}{h} &= \textcolor{blue}{(nu_x)^{m+1}_k}, \label{equ:1f1d-Ex}\\
    \lambda^2 \frac{E^{m+1}_{z,k+1/2} - E^{m}_{z,k+1/2}}{\delta^m} &= \textcolor{blue}{f^{m+1}_{n,k+1/2}}, \label{equ:1f1d-Ez}
\end{align}
where 
\begin{equation*}
    \Tilde{E}^m_{z,k} = \frac{1}{2}(E^m_{z,k+1/2} + E^m_{z,k-1/2}), \ \ \ \Tilde{B}^m_{y,k} = \frac{1}{2}(B^m_{y,k+1/2} + B^m_{y,k-1/2}),
\end{equation*}
is the consequence of interpolation of electromagnetic field, 
and the fluxes read
\begin{align*}
    f^{m+1/2}_{n,k+1/2} & = \frac{1}{2}[\textcolor{blue}{(nu_z)^{m+1}_k + (nu_z)^{m+1}_{k+1}} + \mu^m_{k+1/2}(n^m_k - n^m_{k+1})], \\
    f^{m}_{u_x,k+1/2} & = \frac{1}{2}[(nu_zu_x)^{m}_k + (nu_zu_x)^{m}_{k+1} + \mu^m_{k+1/2}((nu_x)^m_k - (nu_x)^m_{k+1})], \\
    f^{m}_{u_z,k+1/2} & = \frac{1}{2}[(nu_z^2 + p(n)/\varepsilon^2)^{m}_k + (nu_z^2 + p(n)/\varepsilon^2)^{m}_{k+1} + \mu^m_{k+1/2}((nu_z)^m_k - (nu_z)^m_{k+1})]. \\
\end{align*}

\subsection{Numerical results}
A Riemann problem, namely a discontinuous initial condition with two states, is considered. The spatial domain is $[-0.1, 0.1]$. Initially, 
\begin{align*}
    & n(z,0) = 1,\ \ u_z(z,0) = \chi_{[-0.1,0]}(z) - \chi_{[0,0.1]}(z), \\
    & u_x(z,0) = B_y(z,0) = E_x(z,0) = E_z(z,0) = 0.
\end{align*}
Homogeneous Neumann boundary condition is enforced for all the variables for simplicity whereas more sophisticate BC\footnote{In \cite{degond_2012}, Silver-M\"{u}ller condition is used.} is employed in \cite{degond_2012}. The experiments show that no distinct difference occurs.

To verify the implementation, a grid convergence study is done, see Fig. \ref{fig:grid_study_1d1f}. Due to the discontinuity of solutions, the expected convergence rate for $L^1$-norm error is $1/2$. Since no analytic solution is available, the reference solution is obtained using very fine mesh ($N = 16385$). In addition, the convergence of the number density and the $z$-momentum as the underlying mesh being refined is displayed in Fig. \ref{fig:grid_study_field_1d1f} for $\lambda = 0.01$. Conformity with the results in \cite{degond_2012} is demonstrated by Fig. \ref{fig:lambdas_1d1f} and \ref{fig:lambdas_ref_1d1f}. For $\lambda = 1$, the coupling of fluid motions and electromagnetic fields is weak so that the solution behaves like a shock tube. With decreasing $\lambda$, the coupling effect becomes noticeable. For $\lambda \ll 1$, the solutions converge to quasi-neutral limit. The performance of the scheme when $\lambda = 0$ is also shown in Fig. \ref{fig:lambdas_1d1f}, which leads to a valid solution and nicely reproduces the theoretical solution ($n = 1$ and $u_z = 0$). Slight difference happens for the $z$-momentum when $\lambda = 10^{-4}$, which might result from the different treatment of BC.

\begin{figure}
    \centering
    \includegraphics{grid_study_1d1f.eps}
    \caption{Grid convergence study for solutions for $\lambda = 10^{-2}$ at $T = 0.0003$. The reference solution is generated by simulation with $N = 16385$. The rate of convergence is roughly 0.5.}
    \label{fig:grid_study_1d1f}
\end{figure}
\begin{figure}
    \centering
    \includegraphics{grid_study_field_1d1f.eps}
    \caption{Comparison of solutions generated by meshes of different sizes. The solutions are computed for $\lambda = 0.01$ at $t=0.0005$.}
    \label{fig:grid_study_field_1d1f}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[scale=1]{lambdas_1d1f.eps}
    \caption{1D one-fluid case of $\lambda = 1, 10^{-2}, 10^{-4}, 0$ at $t = 0.0005$ with $N = 10^3$.}
    \label{fig:lambdas_1d1f}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[scale=0.4]{lambdas_ref_1d1f.png}
    \caption{Results of \cite{degond_2012} at $T = 0.0005$ with $N = 10^3$. }
    \label{fig:lambdas_ref_1d1f}
\end{figure}

\section{Two-fluid model} \label{sec:two_fluid_model}
\subsection{Governing equations in 1D} \label{sec:1d_two_fluid_equations}
Compared to one-fluid model, in two-fluid model the motion of ions is taken into account through one more set of fluid equations. The rescaled two-fluid Euler-Maxwell system reads
\begin{align*}
    \partial_t n_i + \nabla\cdot(n_i \mathbf{u}_i) &= 0, \\
    \partial_t (n_i \mathbf{u}_i) + \nabla \cdot (n_i \mathbf{u}_i \otimes \mathbf{u}_i) + \nabla p(n_i) &= n_i(\mathbf{E} + \mathbf{u}_i \times \mathbf{B}),\\
    \partial_t n_e + \nabla\cdot(n_e \mathbf{u}_e) &= 0, \\
    \varepsilon^2[\partial_t (n_e \mathbf{u}_e) + \nabla \cdot (n_e \mathbf{u}_e \otimes \mathbf{u}_e)] + \nabla p(n_e) &= -n_e(\mathbf{E} + \mathbf{u}_e \times \mathbf{B}),\\
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0. \\
    \lambda^2 \partial_t\mathbf{E} - \nabla \times \mathbf{B} &= -(n_i \mathbf{u}_i - n_e \mathbf{u}_e),\\
    \nabla\cdot \mathbf{B} &= 0, \\
    \lambda^2 \nabla\cdot \mathbf{E} &= n_i - n_e,
\end{align*}

Following the same assumption as Section \ref{sec:1f-eqs-1d} and supplementing the mass and momentum equations for ions, we obtain the two-fluid Euler-Maxwell system in 1D:
\begin{align*}
    \partial_t n_i + \partial_z(n_i u_{iz}) &= 0, \\
    \partial_t(n_i u_{ix}) + \partial_z(n_i u_{iz} u_{ix}) &= n_i(E_x - u_{iz} B_y), \\
    \partial_t(n_i u_{iz}) + \partial_z(n_i u_{iz}^2 + P(n_i)) &= n_i(E_z + u_{ix} B_y), \\
    \partial_t n_e + \partial_z(n_e u_{ez}) &= 0, \\
    \varepsilon^2 [ \partial_t(n_e u_{ex}) + \partial_z(n_e u_{ez} u_{ex}) ] &= - n_e(E_x - u_{ez} B_y), \\
    \varepsilon^2 [ \partial_t(n_e u_{ez}) + \partial_z(n_e u_{ez}^2) ] + \partial_z(P(n_e)) &= -n_e(E_z + u_{ex} B_y), \\
    \partial_t B_y + \partial_z E_x &= 0, \\
    \lambda^2 \partial_t E_x + \partial_z B_y &= n_e u_{ex} - n_i u_{ix}, \\
    \lambda^2 \partial_t E_z &= n_e u_{ez} - n_i u_{iz}, \\
    \lambda^2 \partial_z E_z &= n_i - n_e,
\end{align*}
where the subscript $i$ and $e$ represent ion and electron variables respectively.

The discretization follows the same principle as illustrated in Section \ref{sec:1f1d-discretization} and thus is omitted here.

\subsection{Numerical results} \label{sec:1d_two_fluid_numerical_results}
The same case as the previous one is tested here. The initial condition remains unchanged for electron variables and electromagnetic fields. Additionally, for ion variables, we set
\begin{align*}
    n_i(z,0) = 1, \ \ u_{ix}(z,0) = u_{iz}(z,0) = 0, 
\end{align*}
namely, the ion is uniform and at rest at the initial time.
\begin{figure}
    \centering
    \includegraphics{grid_study_field_1d2f.eps}
    \caption{Comparison of solutions generated by meshes of different sizes. The solutions are computed for $\lambda = 0.01$ at $t = 5 \times 10^{-4}$.}
    \label{fig:grid_study_field_1d2f}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[scale=1]{lambdas_1d2f.eps}
    \caption{1D two-fluid case of $\lambda = 1, 10^{-2}, 10^{-4}, 0$ at $t = 5\times10^{-4}$ with $N = 10^3$.}
    \label{fig:lambdas_1d2f}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[scale=0.45]{lambdas_ref_1d2f_1.png}
    \includegraphics[scale=0.45]{lambdas_ref_1d2f_2.png}
    \caption{Results of \cite{degond_2012} at $t = 5\times10^{-4}$ with $N = 10^3$.}
    \label{fig:lambdas_ref_1d2f}
\end{figure}

For the sake of verification, the convergence of certain quantities as the mesh being refined is demonstrated in Fig. \ref{fig:grid_study_field_1d2f} for $\lambda = 0.01$. Results of the same resolution ($N = 10^4$) with different $\lambda$ are shown in Fig. \ref{fig:lambdas_1d2f}. As reference, results in \cite{degond_2012} are shown in Fig. \ref{fig:lambdas_ref_1d2f}. They almost\footnote{Obviously, electron momentum when $\lambda = 10^{-4}$ in Fig. \ref{fig:lambdas_ref_1d2f} is incorrect since electron and ion momentum are supposed to be equal in quasi-neutral limit} coincide. Besides, the case corresponding to $\lambda = 0$ provided in Fig. \ref{fig:lambdas_1d2f} shows consistency with the quasi-neutral condition $n_i = n_e$ and $n_eu_{ez} = n_iu_{iz}$.

\section{Two-fluid model with collision term} \label{sec:1d2f_coll}
\subsection{Governing equations}
As one step further towards a more realistic model, we take into account the collision between electrons and ions by including the friction term (\ref{equ:collision_rescaled}). The inclusion of collision term leads to the equations
\begin{align*}
    \partial_t n_i + \nabla\cdot(n_i \mathbf{u}_i) &= 0, \\
    \partial_t (n_i \mathbf{u}_i) + \nabla \cdot (n_i \mathbf{u}_i \otimes \mathbf{u}_i) + \nabla p(n_i) &= n_i(\mathbf{E} + \mathbf{u}_i \times \mathbf{B}) + \colorbox{orange!20}{$\alpha^\text{coll} n_en_i(\mathbf{u}_i - \mathbf{u}_e)$},\\
    \partial_t n_e + \nabla\cdot(n_e \mathbf{u}_e) &= 0, \\
    \varepsilon^2[\partial_t (n_e \mathbf{u}_e) + \nabla \cdot (n_e \mathbf{u}_e \otimes \mathbf{u}_e)] + \nabla p(n_e) &= -n_e(\mathbf{E} + \mathbf{u}_e \times \mathbf{B}) + \colorbox{orange!20}{$\alpha^\text{coll}  n_en_i(\mathbf{u}_e - \mathbf{u}_i)$},\\
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0. \\
    \lambda^2 \partial_t\mathbf{E} - \nabla \times \mathbf{B} &= -(n_i \mathbf{u}_i - n_e \mathbf{u}_e),\\
    \nabla\cdot \mathbf{B} &= 0, \\
    \lambda^2 \nabla\cdot \mathbf{E} &= n_i - n_e,
\end{align*}
where $\alpha^\text{coll}$ is the dimensionless prefactor and we treat it as a pre-defined parameter.

In our 1D setting, the governing equations become
\begin{align*}
    \partial_t n_i + \partial_z(n_i u_{iz}) &= 0, \\
    \partial_t(n_i u_{ix}) + \partial_z(n_i u_{iz} u_{ix}) &= n_i(E_x - u_{iz} B_y) + \colorbox{orange!20}{$\alpha^\text{coll} n_e n_i (u_{ex} - u_{ix})$}, \\
    \partial_t(n_i u_{iz}) + \partial_z(n_i u_{iz}^2 + P(n_i)) &= n_i(E_z + u_{ix} B_y) + \colorbox{orange!20}{$\alpha^\text{coll} n_e n_i (u_{ez} - u_{iz})$}, \\
    \partial_t n_e + \partial_z(n_e u_{ez}) &= 0, \\
    \varepsilon^2 [ \partial_t(n_e u_{ex}) + \partial_z(n_e u_{ez} u_{ex}) ] &= - n_e(E_x - u_{ez} B_y) + \colorbox{orange!20}{$\alpha^\text{coll} n_e n_i (u_{ix} - u_{ex})$}, \\
    \varepsilon^2 [ \partial_t(n_e u_{ez}) + \partial_z(n_e u_{ez}^2) ] + \partial_z(P(n_e)) &= -n_e(E_z + u_{ex} B_y) + \colorbox{orange!20}{$\alpha^\text{coll} n_e n_i (u_{iz} - u_{ez})$}, \\
    \partial_t B_y + \partial_z E_x &= 0, \\
    \lambda^2 \partial_t E_x + \partial_z B_y &= n_e u_{ex} - n_i u_{ix}, \\
    \lambda^2 \partial_t E_z &= n_e u_{ez} - n_i u_{iz}, \\
    \lambda^2 \partial_z E_z &= n_i - n_e.
\end{align*}

\subsection{Full discretization}
The full discretization is merely the one used in the previous section plus implicit collision terms. The implicitness is owing to the stiffness incurred from the potentially large value of $\varepsilon^{-2}\alpha^\text{coll}$.
\begin{align*}
    \frac{n^{m+1}_{i,k} - n^m_{i,k}}{\delta^m} + \frac{\textcolor{blue}{f^{m+1/2}_{n_i,k+1/2} - f^{m+1/2}_{n_i,k-1/2}}}{h} &= 0, \\
    \frac{(n_iu_{ix})^{m+1}_k - (n_iu_{ix})^m_k}{\delta^m} + \frac{f^{m}_{u_{ix},k+1/2} - f^{m}_{u_{ix},k-1/2}}{h} &= n^m_{i,k}( \textcolor{blue}{E^{m+1}_{x,k}} - u^m_{iz,k}\Tilde{B}^m_{y,k}) \\
    & + \colorbox{orange!20}{$\alpha^\text{coll} \left[n^m_{i,k}\textcolor{blue}{(n_eu_{ex})^{m+1}_k} - n^m_{e,k}\textcolor{blue}{(n_iu_{ix})^{m+1}_k}\right]$},\\
    \frac{(n_iu_{iz})^{m+1}_k - (n_iu_{iz})^m_k}{\delta^m} + \frac{f^{m}_{u_{iz},k+1/2} - f^{m}_{u_{iz},k-1/2}}{h} &= n^m_{i,k}(\textcolor{blue}{\Tilde{E}^{m+1}_{z,k}} + u^m_{ix,k}\Tilde{B}^m_{y,k}) \\
    & + \colorbox{orange!20}{$\alpha^\text{coll} \left[n^m_{i,k}\textcolor{blue}{(n_eu_{ez})^{m+1}_k} - n^m_{e,k}\textcolor{blue}{(n_iu_{iz})^{m+1}_k}\right]$},\\
    \frac{n^{m+1}_{e,k} - n^m_{e,k}}{\delta^m} + \frac{\textcolor{blue}{f^{m+1/2}_{n_e,k+1/2} - f^{m+1/2}_{n_e,k-1/2}}}{h} &= 0,  \\
    \varepsilon^2\frac{(n_eu_{ex})^{m+1}_k - (n_eu_{ex})^m_k}{\delta^m} + \frac{f^{m}_{u_{ex},k+1/2} - f^{m}_{u_{ex},k-1/2}}{h} &= - n^m_{e,k}( \textcolor{blue}{E^{m+1}_{x,k}} - u^m_{ez,k}\Tilde{B}^m_{y,k}) \\
    & - \colorbox{orange!20}{$\alpha^\text{coll} \left[n^m_{i,k}\textcolor{blue}{(n_eu_{ex})^{m+1}_k} - n^m_{e,k}\textcolor{blue}{(n_iu_{ix})^{m+1}_k}\right]$},\\
    \varepsilon^2\frac{(n_eu_{ez})^{m+1}_k - (n_eu_{ez})^m_k}{\delta^m} + \frac{f^{m}_{u_{ez},k+1/2} - f^{m}_{u_{ez},k-1/2}}{h} &= - n^m_{e,k}(\textcolor{blue}{\Tilde{E}^{m+1}_{z,k}} + u^m_{ix,k}\Tilde{B}^m_{y,k}) \\
    & - \colorbox{orange!20}{$\alpha^\text{coll} \left[n^m_{i,k}\textcolor{blue}{(n_eu_{ez})^{m+1}_k} - n^m_{e,k}\textcolor{blue}{(n_iu_{iz})^{m+1}_k}\right]$},\\    
    \frac{B^{m+1}_{y,k+1/2} - B^{m}_{y,k+1/2}}{\delta^m} + \frac{\textcolor{blue}{E^{m+1}_{x,k+1} - E^{m+1}_{x,k}}}{h} &= 0, \\
    \lambda^2 \frac{E^{m+1}_{x,k} - E^{m}_{x,k}}{\delta^m} + \frac{\textcolor{blue}{B^{m+1}_{y,k+1/2} - B^{m+1}_{y,k-1/2}}}{h} &= \textcolor{blue}{(n_eu_{ex})^{m+1}_k - (n_iu_{ix})^{m+1}_k}, \\
    \lambda^2 \frac{E^{m+1}_{z,k+1/2} - E^{m}_{z,k+1/2}}{\delta^m} &= \textcolor{blue}{f^{m+1}_{n_e,k+1/2} - f^{m+1}_{n_i,k+1/2}}. \\
\end{align*}

\subsection{Numerical results}
We set the friction coefficient $\alpha^\text{coll} = 644$, and stick to the previous initial condition
\begin{align*}
    & n_e(z,0) = n_i(z,0) = 1,\\
    & u_{ez}(z,0) = u_{iz}(z,0) = \chi_{[-0.1,0]}(z) - \chi_{[0,0.1]}(z), \\
    & u_{ex}(z,0) = u_{ix}(z,0) = B_y(z,0) = E_x(z,0) = E_z(z,0) = 0.
\end{align*}
The case with a cell number $N = 1000$ and terminal time $t_{\text{end}} = 0.02$ is tested for $\lambda = 1, 10^{-2}, 10^{-4}, 0$. The number densities and momenta of ions and electrons are shown in Fig. \ref{fig:lambdas_1d2fc}.
\begin{figure}
    \centering
    \includegraphics{lambdas_1d2fc_const.eps}
    \caption{1D two-fluid case with friction terms. Results for $\lambda = 1, 10^{-2}, 10^{-4}, 0$ at $t = 0.02$ with $N = 1000$.}
    \label{fig:lambdas_1d2fc}
\end{figure}
\begin{figure}
    \centering
    \includegraphics{grid_study_field_1d2fc.eps}
    \caption{Comparison of solutions generated by meshes of different sizes. The solutions are computed for $\lambda = 10^{-4}$ at $t = 0.02$.}
    \label{fig:grid_study_field_1d2fc}
\end{figure}
With decreasing $\lambda$, as expected, the densities and $z$-momenta of ion and electron gradually approach each other. However, when $\lambda = 10^{-4}$, spurious spikes exist at the discontinuity of electron momentum field and can be diminished by refining the mesh, as is shown in Fig. \ref{fig:grid_study_field_1d2fc} which also manifests the convergence with respect to the mesh refinement.
\section{Summary}
We have verified the AP scheme proposed in \cite{degond_2012} by reproducing the numerical solutions of one-fluid and two-fluid Euler-Maxwell systems in 1D. Besides, it is also ensured that the inclusion of friction term does not undermine the AP property. To summarize, the scheme works uniformly for $\lambda \in [0,1]$ in the sense that no instability occurs and the transition of different regimes is smooth. Within expect, the quasi-neutral condition $n_i = n_e$ is observed for the limiting case.

In the sequel, the performance of the AP scheme on problems in 3D is to be checked. It expects to pose more challenges due to the boundary treatment in FIT and the inherently more complex 3D structures of Maxwell's equations.

\chapter{Numerical Experiments in 3D} \label{chap:numerical_experiments_in_3d}

In the previous chapter, we have gone through problems in a 1D setting, and have conveyed the basic idea of simulating plasma by AP schemes. As Maxwell's equations are inherently 3D, doing simulations in 3D is essential to gain realistic results.

We test the AP scheme on a case that is adapted\footnote{Keeping the geometry and BCs being unchanged, we remove the enclosing solid dielectric domain such that the plasma domain coincides with the electromagnetic domain. The reason is illustrated in Section \ref{sec:impact_insulating_domain}.} from the one used in \cite[][chap. 1 sec. 4]{fuchs_2021}---a cylindrical tube filled with plasmas and applied external potentials on both ends.

In this chapter, a description of the problem is first given, including the domain geometry and boundary conditions. Considerable words are devoted to the enforcement of BCs as well as their well-posedness from an algebraic perspective. Afterward, we elaborate on the procedure of time-stepping, especially the assembling of the linear system. The validity of such a linear system over arbitrary $\lambda$ is critical for attaining the AP property.

Instead of directly cutting to the fully-coupled system, we first test the behavior of the scheme on the subsystems of the Euler-Maxwell system as verification. Finally, we present the numerical results of the fully-coupled Euler-Maxwell system, on which the AP property is to be verified.

\section{Problem description and mesh generation} \label{sec:problem_description}
The problem setting is a cylindrical domain filled with plasma fluids, and with two electrodes on each end, as is sketched in Fig. \ref{fig:sketch_domain}. From the viewpoint of the Euler system, the cylinder is enclosed by a non-penetrating wall whereas the plasma fluids are allowed to inflow and outflow through the electrode surfaces. Regarding the Maxwell system, external electric potentials are applied on the electrodes, and the enclosing boundary is considered insulating.

Under such a setting, the motions of charged particles of the plasma are driven by the external potential, giving rise to an electromagnetic field, which in turn exerts Lorentz force on the charged particles. This setting is intended for simulating electric arcs.

We discretize the spatial domain by an unstructured mesh doublet ($\mathcal{M}, \Tilde{\mathcal{M}}$) which consists of prisms aligned with the axial direction. The mesh generation is realized by the code developed in \cite{fuchs_2021}. The detailed algorithm is omitted. In principle, a circle is first discretized with a 2D mesh which afterward is extended along the axial direction to form the 3D mesh. Based on the generated primal mesh, a dual mesh conforming to the duality requirements, as is illustrated in Section \ref{sec:mesh_duality}, can be constructed with additional attention on the cut-off boundary that is discussed in Section \ref{sec:boundary_treatment}. An example of the primal and dual meshes is shown in Fig. \ref{fig:primal_dual_meshes}.

\begin{figure}
    \centering
    \begin{tikzpicture}
    \coordinate (O1) at (0,0);
    \draw[very thick] (O1) circle (1) node {Cathode};
    \fill[blue, opacity=0.2] (O1) circle (1);
    \draw[very thick] (O1) circle (1.5);
    \coordinate (O2) at (4.5,1) ;
    \draw[gray] (O2) circle (1);
    \node at (O2) {Anode};
    \node at (barycentric cs:O1=1,O2=1) {Plasma}; 
    \fill[red, opacity=0.2] (O2) circle (1);
    \coordinate (S1) at ([shift={(-0.196,0.98)}]O1);
    \coordinate (S2) at ([shift={(-0.196,0.98)}]O2);
    \coordinate (P1) at ([shift={(0.196,-0.98)}]O1);
    \coordinate (P2) at ([shift={(0.196,-0.98)}]O2);
    \coordinate (SS1) at ([shift={({-0.196*1.5},{0.98*1.5})}]O1);
    \coordinate (SS2) at ([shift={({-0.196*1.5},{0.98*1.5})}]O2);
    \coordinate (PP1) at ([shift={({0.196*1.5},{-0.98*1.5})}]O1);
    \coordinate (PP2) at ([shift={({0.196*1.5},{-0.98*1.5})}]O2);
    \draw[very thick] (SS1) -- (SS2);
    \draw[very thick] (PP1) -- (PP2); 
    \draw[gray] (SS2) arc (101.31:180+101.31:1.5);
    \draw[very thick] (PP2) arc (101.31-180:101.31:1.5);
    \begin{scope}[shift={(5.5,-1.4)}]
    \draw[blue, -to] (0,0) -- (0.65,0.12) node[right]{\small $z$};
    \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
    \draw[blue, -to] (0,0) -- (0.7,0) node[below]{\small $y$};
    \end{scope}
    \end{tikzpicture}
    \caption{Sketch of the computational domain: a cylinder filled with plasma and with two electrodes at the ends.}
    \label{fig:sketch_domain}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[scale=0.4]{primal_mesh.png}
    \hspace{2cm}
    \includegraphics[scale=0.4]{dual_mesh.png}
    \caption{Primal (left) and dual (right) meshes used for the 3D testing case. They are generated by the code developed in \cite{fuchs_2021}.}
    \label{fig:primal_dual_meshes}
\end{figure}

\section{Boundary conditions} \label{sec:numerical_experiement_bc}

\begin{figure}
    \centering
    \begin{tikzpicture}
        \coordinate (A1) at (0,1.5);
        \coordinate (A2) at (0,1);
        \coordinate (A3) at (0,-1);
        \coordinate (A4) at (0,-1.5);
        \coordinate (B1) at (6,1.5);
        \coordinate (B2) at (6,1);
        \coordinate (B3) at (6,-1);
        \coordinate (B4) at (6,-1.5);
        \draw[very thick] (A2) -- (A1) -- node[above]{$\Gamma_I$} (B1) -- (B2);
        \draw[very thick] (A3) -- (A4) -- node[below]{$\Gamma_I$} (B4) -- (B3);
        \draw[very thick, blue] (A2) -- node[left]  {$\Gamma_-$}  (A3);
        \draw[very thick, red]  (B2) -- node[right] {$\Gamma_+$}  (B3);
        \node at (3,0) {$\Omega$};
    \end{tikzpicture}
    \begin{tikzpicture}
        \coordinate (A1) at (0,1.5);
        \coordinate (A2) at (0,1);
        \coordinate (A3) at (0,-1);
        \coordinate (A4) at (0,-1.5);
        \coordinate (B1) at (6,1.5);
        \coordinate (B2) at (6,1);
        \coordinate (B3) at (6,-1);
        \coordinate (B4) at (6,-1.5);
        \draw[very thick] (A2) -- (A1) -- node[above]{$\nabla \times \mathbf{H}\cdot \mathbf{n} = 0$, reflective wall}  node[below, gray]{$\nabla \times \mathbf{E} \cdot \mathbf{n} = 0$ on the whole boundary} (B1) -- (B2);
        \draw[very thick] (A3) -- (A4) -- node[below]{$\nabla \times \mathbf{H}\cdot \mathbf{n} = 0$, reflective wall} (B4) -- (B3);
        \draw[very thick, dashed, blue] (A2) -- node[left, yshift=0.3cm] {$\varphi^-(t)$} node[left, yshift=-0.3cm] {\textcolor{black}{open}} (A3);
        \draw[very thick, dashed, red]  (B2) -- node[right, yshift=0.3cm]  {$\varphi^+(t)$} node[right, yshift=-0.3cm] {\textcolor{black}{open}}  (B3);
        \node at (3,0) {\textbf{Plasma}};
        \begin{scope}[shift={(6.5,-1.6)}]
        \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
        \draw[blue, -to] (0,0) -- (0.7,0) node[right]{\small $z$};
        \end{scope}
    \end{tikzpicture}
    \caption{Illustration of the boundary conditions: (left) notation of each part of the boundary; (right) boundary conditions at each part of the boundary.}
    \label{fig:bc}
\end{figure}

Before presenting the BCs, we notate the different parts of the computational domain. The whole domain is $\Omega \subset \mathbb{R}^3$ consisting of the interior $\Omega^\circ$ and boundary $\partial \Omega := \Gamma$. The cathode and anode are modeled by a 2D surface without thickness and thus lie on the boundary. They are notated $\Gamma_-$ and $\Gamma_+$ respectively. The rest of the boundary $\Gamma_I := \Gamma \backslash (\Gamma_- \cup \Gamma_+)$ is the insulating boundary. These are visualized in Fig. \ref{fig:bc} (left).

We would like to stress that the boundary of the plasmas domain, namely the domain where the Euler equations are defined, coincides with the artificial truncation for the electromagnetic field.

For Maxwell's equations, we adopt the so-called \emph{ECE boundary conditions} in the sense that 1) at the electrodes electric potentials $\varphi^-(t)$ and $\varphi^+(t)$ are enforced externally
; 2) the tangential $\mathbf{E}$-field is curl-free on $\Gamma$; 3) the tangential $\mathbf{H}$-field is curl-free at $\Gamma_I$.

For the Euler system, the wall boundary is considered \emph{reflective} and requires vanishing normal velocity. At $\Gamma_+$ and $\Gamma_-$ where the electrodes lie, we stick to \cite{fuchs_2021}, and employ the \emph{open} BC, allowing the fluids to freely pass in the sense of zero gradients of the fluid quantities.

Since the electrons and ions cannot penetrate the reflective wall, the orthogonal current vanishes on $\Gamma_I$. By Amp\`{e}re's law (\ref{equ:maxwell_ampere_rescaled}) the insulating BC $\text{curl}\mathbf{H} \cdot \mathbf{n} = 0$ is equivalent to $\mathbf{D}\cdot\mathbf{n} = 0$ provided $\mathbf{D}\cdot\mathbf{n} = 0$ is satisfied at the initial time. To study the asymptotic behavior of the system, the latter one is suitable and thus is actually adopted because of the reason discussed in Section \ref{sec:impact_of_bc}.

To summarize, 
\begin{align}
    \varphi &= \varphi^-(t)\ \ \text{on} \ \ \Gamma_-, \label{equ:bc_1}\\
    \varphi &= \varphi^+(t)\ \ \text{on} \ \ \Gamma_+, \label{equ:bc_2}\\
    \text{curl} \mathbf{E} \cdot \mathbf{n} &= 0\ \ \text{on} \ \  \Gamma_I,  \label{equ:bc_3}\\
    \text{curl} \mathbf{H} \cdot \mathbf{n} = 0 \Leftrightarrow \mathbf{D} \cdot \mathbf{n} &= 0\ \  \text{on} \ \  \Gamma_I, \label{equ:bc_4}\\
    \mathbf{u_*}\cdot \mathbf{n} &= 0 \ \ \text{on} \ \ \Gamma_I, \label{equ:bc_5}\\
    \text{grad}\mathbf{U_*} \cdot \mathbf{n} &= \mathbf{0} \ \ \text{on} \ \ \Gamma_+\cup\Gamma_-. \label{equ:bc_6}
\end{align}
where $\mathbf{n}$ denotes the outer normal vector. Recall that $\mathbf{u}_*$ and $\mathbf{U}_*$ denotes the velocity and conservative fluid quantities of species $*$.

To verify that the BCs lead to a well-posed problem, especially for Maxwell's equations\footnote{The BCs for the Euler system are rather classical. See \cite[][Chap. 7]{leveque_2002} for a general introduction, or \cite[][sec. 2e]{mishra_2019b} for the specific implementation for the Euler equations.}, we want to check that these BCs in the discrete level lead to a solvable linear system. A \emph{necessary} condition is that \emph{the number of unknown variables and the number of (independent) algebraic equations coincide}.

We would like to remark that the time-stepping for Euler equations (\ref{equ:euler_ap}) do not involve solving any linear system since the implicit mass term in (\ref{equ:flux_ap}) can be obtained through the momentum equations. As for the implicit term $\mathbf{E}^{m+1}$ in the source term (\ref{equ:rhs_ap}), it is obtained through updating the Maxwell system. Therefore, only the evolution of the Maxwell system entails solving a linear system, whose validity is discussed here.

First, a meticulous classification and counting for facets of meshes are done as follows:
\begin{align*}
    \#\  \text{primal cell}\ \  &N_V \\
    \#\  \text{primal edge}\ \  &N_L := \underbrace{N^+_L + N^-_L + N^I_L}_{N^\partial_L} + N^\circ_L  \\
    \#\  \text{primal face}\ \  &N_A := \underbrace{N_A^+ + N_A^- + N^I_A}_{N^\partial_A} + N^\circ_A  \\
    \#\  \text{primal vertex}\ \  &N_P := \underbrace{N_P^+ + N_P^- + N^I_P}_{N^\partial_P} + N^\circ_P \\
    \#\  \text{dual cell}\ \  &N_{\Tilde{V}} := N_p \\
    \#\  \text{dual edge}\ \  &N_{\Tilde{L}} := \underbrace{N^\partial_{\Tilde{L}}}_{=N^\partial_L} + \underbrace{N^\circ_{\Tilde{L}}}_{=N_A} \\
    \#\  \text{dual face}\ \  &N_{\Tilde{A}} := \underbrace{N^\partial_{\Tilde{A}}}_{=N^\partial_P} + \underbrace{N^\circ_{\Tilde{A}}}_{=N_L}
\end{align*}
where the superscripts indicate the domains to which facets belong to, and $+,-,I,\circ,\partial$ represent $\Gamma_+, \Gamma_-, \Gamma_I, \Omega^\circ, \partial \Omega$ respectively. As is discussed in Section \ref{sec:boundary_treatment}, auxiliary dual facets are needed to trim $\Tilde{\mathcal{M}}$ such that $\mathcal{M}$ and $\Tilde{\mathcal{M}}$ share the same boundary. By inspecting Fig. \ref{fig:illustraion_dual_boundary}, one can realize that the auxiliary dual edges have the same number as the primal boundary edges since they intersect with each other; the auxiliary dual faces have the same number as the primal boundary vertices. These amount to $N^\partial_{\Tilde{L}} = N^\partial_L, N^\partial_{\Tilde{A}} = N^\partial_P$. Note that these number relationships are attained on the premise that non-straight edges and non-flat faces are admissible.

Next, we count the number of unknowns. From the BCs (\ref{equ:bc_1})(\ref{equ:bc_3})  we know that the tangential $\mathbf{E}$-field is irrotational at the whole boundary $\partial\Omega$, which allows a scalar potential function $\varphi$ on $\partial \Omega$ with $\text{grad}_\tau \varphi = \mathbf{E}_\tau$. In the discrete case, $\bm{\varphi}$ is a scalar vector whose entries are defined on each primal vertex on $\partial \Omega$. The collection of boundary electric voltage $\mathbf{e}^\partial$ is retrieved by $\mathbf{e}^\partial = \mathbb{G}_\partial \bm{\varphi}$ where $\mathbb{G}_\partial$ stands for the discrete grad operator on the boundary. Besides, additional dual edges and faces at boundary, to which the integrals of the $\mathbf{H}$-field and the $\mathbf{D}$-field are assigned, give rise to unknown $\mathbf{h^\partial}$ and $\mathbf{d^\partial}$ vectors of sizes $N^\partial_{\Tilde{L}}$ and $N^\partial_{\Tilde{A}}$. The counting of unknown variables is as follows:
\begin{equation*}
    |\mathbf{e}| = N_L, \ \ \ |\mathbf{b}|=N_A, \ \ \ |\mathbf{h}^\partial|=N^\partial_{\Tilde{L}},\ \ \ |\mathbf{d}^\partial| = N^\partial_{\Tilde{A}}, \ \ \ |\bm{\varphi}| = N^\partial_P,
\end{equation*}
where $|\cdot|$ denotes the size of vector.

Lastly, we collect all the algebraic equations derived from the Maxwell system. The coupling term $\mathbf{j}^{m+1}$ in discrete Ampere's law (\ref{equ:maxwell_ampere_ap}) can be rewritten by electric variables, which will be demonstrated in (\ref{equ:tmp5})(\ref{equ:tmp6}) at the next section. The discrete Faraday's law (\ref{equ:maxwell_faraday_ap}) updates the scalar vector $\mathbf{b}$ which is composed of integrals of $\mathbf{B}$-field on each primal face; the discrete Amp\`{e}re's law (\ref{equ:maxwell_ampere_ap}) updates $\mathbf{d}$ which is composed of integrals of $\mathbf{D}$-field on each dual face; the relation $\mathbf{e}^\partial = \mathbb{G}_\partial \bm{\varphi}$ entails $N^\partial_L$ equations each of which is defined on a boundary primal edge; the entries of $\bm{\varphi}$ that locate on the electrodes are assigned externally; the insulating BC (\ref{equ:bc_4}) needs to be satisfied at each dual face that lies in $\Gamma_I$. In summary, the counting of algebraic equations is as follows:
\begin{align*}
    \text{discrete Faraday law (\ref{equ:maxwell_faraday_ap})} \ \ &\longrightarrow\ \  N_A \ \ \text{equations} \\
    \text{discrete Ampere law (\ref{equ:maxwell_ampere_ap})} \ \ &\longrightarrow\ \  N_{\Tilde{A}} \ \ \text{equations} \\
     \mathbf{E}_\tau = \text{grad}_\tau \varphi \Rightarrow \mathbf{e}^\partial = \mathbb{G}_\partial \bm{\varphi} \ \ &\longrightarrow\ \  N^\partial_L \ \ \text{equations} \\
    \text{enforced potentials}\ \ \varphi^+(t), \varphi^-(t) \ \ &\longrightarrow\ \  N_P^+ + N_P^- \ \ \text{equations} \\
    \text{insulating BC (\ref{equ:bc_4})} \ \ &\longrightarrow\ \  N_{\Tilde{A}}^I = N_P^I \ \ \text{equations}.
\end{align*}
It is straightforward to check that the numbers of unknowns and the equations match. Specifically, 
\begin{align*}
    \#\text{ of unknowns} &= \colorbox{orange!20}{$N_L$} + \colorbox{blue!20}{$N_A$} + \colorbox{gray!20}{$N_{\Tilde{L}}^\partial$} + \colorbox{orange!20}{$N_{\Tilde{A}}^\partial$} + \colorbox{green!20}{$N_P^\partial$}, \\
    \#\text{ of equations} &= \colorbox{blue!20}{$N_A$} + \colorbox{orange!20}{$N_{\Tilde{A}}$} + \colorbox{gray!20}{$N_L^\partial$} + \colorbox{green!20}{$N_P^+ + N_P^- + N_P^I$},
\end{align*}
where the terms with the same color can be equated by applying the counting relations listed above.

However, the matching of numbers of unknowns and equations does not necessarily result in a valid linear system. Inappropriate BCs could cause the singularity of the linear system, as is discussed in Section \ref{sec:impact_of_bc}.

\section{Procedure of time-stepping}
In this section, we would like to present the concrete strategy to evolve the whole system, namely calculating variables at $t_{m+1}$ given their values at $t_m$. On one hand, the impact of BCs is not considered when presenting the AP scheme (\ref{equ:maxwell_faraday_ap}) to (\ref{equ:current_ap}). On the other hand, a clever and detailed strategy of establishing the linear system at every time step is necessary.

To avoid any confusion, the definition of the quantities is repeated in Tab. \ref{tab:def_size_var}. For better illustration, matrices used in this section are supplemented with both superscript and subscript indicating the size. For instance, $\mathbb{C}^A_L$ indicates the discrete curl operator of size $N_A \times N_L$ with respect to primal faces and edges; $\Tilde{\mathbb{C}}^{A_I}_{\partial L}$ stands for the discrete curl operator of size $N_{\Tilde{A}}^{I} \times N_{\Tilde{L}}^\partial$ with respect to dual faces on $\Gamma_I$ and edges on $\partial \Gamma$.

\begin{table}[]
    \centering
\begin{tabular}{c c c}
     \hline
     \textbf{Notation}  & \textbf{Meaning}  & \textbf{Size} \\
     \hline
     $\mathbf{e}$ & integral of $\mathbf{E}$-field at primal edges& $N_L$ \\
     $\mathbf{e^\circ}$ & components of $\mathbf{e}$ lying in $\Omega^\circ$ & $N_L^\circ$ \\
     $\mathbf{e^\partial}$ & components of $\mathbf{e}$ lying on $\partial \Omega$ & $N_L^\partial$ \\
     $\mathbf{E}$ & cell average of $\mathbf{E}$-field for dual cells & $N_{\Tilde{V}}$ \\ 
     $\bm{\varphi}$ & electric potentials at primal vertices & $N_P^\partial$ \\
     $\bm{\varphi}^+$ & components of $\bm{\varphi}$ lying on $\Gamma^+$ & $N_P^+$ \\
     $\bm{\varphi}^-$ & components of $\bm{\varphi}$ lying on $\Gamma^-$ & $N_P^-$ \\
     $\mathbf{b}$ & integral of $\mathbf{B}$-field at primal faces & $N_A$ \\
     $\mathbf{d}^\partial$ & integral of $\mathbf{D}$-field at boundary dual faces & $N_{\Tilde{A}}^\partial = N_P^\partial$ \\
     $\mathbf{h}^\partial$ & integral of $\mathbf{H}$-field at boundary dual edges & $N_{\Tilde{L}}^\partial = N_L^\partial$ \\
     $\mathbf{j}$ & current through dual faces & $N_{\Tilde{A}}$ \\
     $\mathbf{j}^\circ$ & components of $\mathbf{j}$ lying in $\Omega^\circ$ & $N_{\Tilde{A}}^\circ$ \\
     $\mathbf{j}^\partial$ & components of $\mathbf{j}$ lying on $\partial \Omega$ & $N_{\Tilde{A}}^\partial$ \\
     \hline
\end{tabular}
    \caption{Definitions and sizes of scalar vectors for each quantity.}
    \label{tab:def_size_var}
\end{table}

With extra quantities at boundary, the schemes (\ref{equ:maxwell_faraday_ap}) (\ref{equ:maxwell_ampere_ap}) turn into
\begin{align}
    \delta_m^{-1} (\mathbf{b}^{m+1} - \mathbf{b}^{m}) + \mathbb{C}_L^A\mathbf{e}^{m+1} \hspace{3.08cm}&= 0, \label{equ:tmp7}\\
    \lambda^2\delta_m^{-1}\mathbb{M}_\varepsilon(\mathbf{e}^{m+1} - \mathbf{e}^m) - \Tilde{\mathbb{C}}_{L^\circ}^{A^\circ}\mathbb{M}_\mu^{-1}\mathbf{b}^{m+1} - \Tilde{C}^{A^\circ}_{\partial L} \mathbf{h}^{\partial, m+1} &= - \mathbf{j}^{\circ,m+1}, \label{equ:tmp8}\\
     \lambda^2\delta_m^{-1}(\mathbf{d}^{\partial,m+1} - \mathbf{d}^{\partial, m}) - \Tilde{\mathbb{C}}^{\partial A}_{\partial L} \mathbf{h}^{\partial,m+1} \hspace{2.60cm}&= - \mathbf{j}^{\partial,m+1}. \label{equ:tmp9}
\end{align}
The equations (\ref{equ:tmp8}) (\ref{equ:tmp9}) arise due to the discrete Faraday law at $\Omega^\circ$ and on $\partial \Omega$.

The discretized BCs (\ref{equ:bc_1}) to (\ref{equ:bc_4}) appear as
\begin{align}
    \mathbf{e}^{\partial,m} &= \mathbb{G}^{\partial L}_{\partial P} \bm{\varphi}^m, \label{equ:tmp10}\\
    \begin{bmatrix}
    \bm{\varphi}^+ \\
    \bm{\varphi}^- 
    \end{bmatrix}^m &= \mathbb{S}^{\pm}_{\partial P} \bm{\varphi}^m =
    \begin{bmatrix}
    \varphi^+(t_m) \\
    \varphi^-(t_m) 
    \end{bmatrix},\label{equ:tmp11}\\
    \Tilde{\mathbb{S}}^{A_I}_{\partial A} \mathbf{d}^{\partial,m} &= 0, \label{equ:tmp12}
\end{align}
where $\mathbb{G}^{\partial L}_{\partial P}$ is the discrete gradient operator applied on $\partial \Omega$;
$\mathbb{S}^{\pm}_{\partial P}$ is a matrix with entries $\in \{0,1\}$ responsible for selecting the potentials at $\Gamma^+$ and $\Gamma^-$; $\Tilde{\mathbb{S}}^{P_I}_{\partial P}$ is also a selecting matrix that picks dual faces on $\Gamma^I$ from those at $\partial\Omega$.

With proper ordering of components in $\mathbf{e}$ and (\ref{equ:tmp10}), we derive all the edge voltages $\mathbf{e}$ from interior edge voltages $\mathbf{e}^\circ$ and boundary potentials $\bm{\varphi}$ through 
\begin{align*}
    \mathbf{e}^m =
    \begin{bmatrix}
    \mathbf{e}^\circ \\ \mathbf{e}^\partial
    \end{bmatrix}^m =
    \underbrace{
    \begin{bmatrix}
    \mathbb{I} & 0 \\ 0 & \mathbb{G}^{\partial L}_{\partial P}
    \end{bmatrix}}_{\mathbb{Q}_{L^\circ,\partial P}^{L}}
    \begin{bmatrix}
    \mathbf{e}^\circ \\ \bm{\varphi}
    \end{bmatrix}^m.
\end{align*}

The last piece of the puzzle to be filled is the relation connecting $\mathbf{j}^{m+1}$ and the electrical quantities -- namely, a generalized Ohm's law\footnote{By ``generalized" we mean that it is merely a formula relating the current density and $\mathbf{E}$-field at the discrete model. There is no counterpart for the continuous model, and it is not the \emph{discretized} Ohm's law, either.} -- such that the linear system (\ref{equ:tmp7}) to (\ref{equ:tmp9}) can be closed and solved. The derivation of generalized Ohm's law resorts to the discrete Euler system (\ref{equ:euler_ap}). In the following, we provide the derivations for models with and without friction terms.

\subsubsection{Model without friction}
By the scheme (\ref{equ:euler_ap}) for the Euler equations, we get 
\begin{equation} \label{equ:tmp1}
    \left[(n\mathbf{u})_{*,k}\right]^{m+1} = \left[\delta_m \varepsilon^{-2}_* q_* n^m_{*,k}\mathbf{E}^{m+1}_k \right] + \underbrace{\left[(n\mathbf{u})_{*,k}\right]^{m} - \left[\frac{\delta_m}{|{\Tilde{V}}_k|}\sum_{j:\Tilde{A}_j\in\partial\Tilde{V}_k}|\Tilde{A}_j|\bm{f}^m_{u,*,j}\right] + \left[\delta_m \varepsilon^{-2}_* q_*(n\mathbf{u})^m_{*,k} \times \mathbf{B}^m_{k}\right]}_{\bm{\eta}^m_*}
\end{equation}
with $[\cdot]$ meaning packing the quantities into a vector. Recall the interpolation relation
\begin{equation*}
    \mathbf{E} = \Tilde{\mathbb{R}}^{V_f}_{A}
    \begin{bmatrix}
    \mathbf{e} \\
    \mathbf{d}^\partial 
    \end{bmatrix},
    \ \ \ \ 
    \mathbf{B} = \Tilde{\mathbb{R}}^{V_f}_{L}
    \begin{bmatrix}
    \mathbf{b} \\
    \mathbf{h}^\partial 
    \end{bmatrix},
\end{equation*}
with which (\ref{equ:tmp1}) is rewritten as
\begin{equation} \label{equ:tmp2}
    \left[(n\mathbf{u})_{*,k}\right]^{m+1} = \text{diag}(\delta_m \varepsilon^{-2}_* q_* n^m_{*,k}) \Tilde{\mathbb{R}}^{V_f}_{A} 
    \begin{bmatrix}
    \mathbf{e} \\
    \mathbf{d}^\partial 
    \end{bmatrix}^{m+1} + \bm{\eta}^m_*.
\end{equation}
Thanks to the linear nature of numerical flux (\ref{equ:flux_ap}), we can express the mass flux by linear operation 
\begin{equation} \label{equ:tmp3}
    \left[f_{n,*,j}\right]^{m+1} = \frac{1}{2} \Tilde{\mathbb{A}}_{V_f}^{A_f} :  \left[(n\mathbf{u})_{*,k}\right]^{m+1} - \frac{1}{2} [s_{*,j}]^m \odot \Tilde{\mathbb{D}}_{V_f}^{A_f} [n_{*,k}]^m,
\end{equation}
where $:$ represents two contraction, $\odot$ represents component-wise product. The meanings of 3-rank tensor $\Tilde{\mathbb{A}}_{V_f}^{A_f}$ and matrix $\Tilde{\mathbb{D}}_{V_f}^{A_f}$ should be self-explanatory by scrutinizing on its component-wise expression (\ref{equ:flux_ap}). We stress that the boundary conditions for the Euler equations are included in these two linear operators.

Plug (\ref{equ:tmp2}) into (\ref{equ:tmp3}), and we get
\begin{equation} \label{equ:tmp4}
    \left[f_{n,*,j}\right]^{m+1} = \underbrace{\frac{1}{2} \Tilde{\mathbb{A}}_{V_f}^{A_f} : \text{diag}(\delta_m \varepsilon^{-2}_* q_* n^m_{*,k}) \Tilde{\mathbb{R}}^{V_f}_{A}}_{\Tilde{\mathbb{T}}_{A,*}^{A,m}}   
    \begin{bmatrix}
    \mathbf{e} \\
    \mathbf{d}^\partial 
    \end{bmatrix}^{m+1} + \underbrace{\frac{1}{2}\Tilde{\mathbb{A}}_{V_f}^{A_f} :\bm{\eta}^m_* - \frac{1}{2} [s_{*,j}]^m \odot \Tilde{\mathbb{D}}_{V_f}^{A_f} [n_{*,k}]^m}_{\bm{\mu}^m_*}.
\end{equation}

\subsubsection{Two-fluid model with friction}
We include the friction term (\ref{equ:collision_rescaled}). Adding friction terms would lead to extra complexity since they are discretized implicitly. For the sake of simplicity, only the two-fluid (electron-ion) model is tackled here. Following the same procedure as before, first, we need the discretized relation between momenta and $\mathbf{E}$-field. After lengthy calculation, we end up getting
\begin{multline}\label{equ:tmp13}
    [n\mathbf{u}_{i,k}]^{m+1} = \left[\frac{1 + \delta_m \alpha \varepsilon_e^{-2} n_{i,k}^m + \delta_m \alpha \varepsilon_e^{-2} \frac{q_e}{q_i}n_{e,k}^m }{1 + \delta_m \alpha (\varepsilon^{-2}_e n_{i,k}^m + \varepsilon_i^{-2} n_{e,k}^m)} \delta_m \varepsilon^{-2}_i q_i n_{i,k}^m \mathbf{E}^{m+1}_k\right] \\
    + \left[\frac{\delta_m \alpha \varepsilon_i^{-2} n_{i,k}^m}{1 + \delta_m \alpha (\varepsilon^{-2}_e n_{i,k}^m + \varepsilon^{-2}_i n_{e,k}^m)}\right] \odot \bm{\eta}_e^m + \left[\frac{1 + \delta_m \alpha \varepsilon^{-2}_e n_{i,k}^m}{1 + \delta_m \alpha (\varepsilon^{-2}_e n_{i,k}^m + \varepsilon^{-2}_i n_{e,k}^m)}\right] \odot \bm{\eta}_i^m,
\end{multline}
where $\alpha$ is the friction coefficient, and $\bm{\eta}_e^m, \bm{\eta}_i^m$ are defined in (\ref{equ:tmp1}). Again by (\ref{equ:tmp3}) we derive the expression for mass fluxes in the same form as (\ref{equ:tmp4}). In this case, 
\begin{align}
     \Tilde{\mathbb{T}}_{A, i}^{A, m} &= \frac{1}{2} \Tilde{\mathbb{A}}_{V_f}^{A_f} : \text{diag}\left(\frac{1 + \delta_m \alpha \varepsilon_e^{-2} n_{i,k}^m + \delta_m \alpha \varepsilon_e^{-2} \frac{q_e}{q_i}n_{e,k}^m }{1 + \delta_m \alpha (\varepsilon^{-2}_e n_{i,k}^m + \varepsilon_i^{-2} n_{e,k}^m)}\delta_m \varepsilon^{-2}_i q_i n^m_{i,k}\right) \Tilde{\mathbb{R}}^{V_f}_{A}, \label{equ:tmp14} \\
     \bm{\mu}^m_i &= \frac{1}{2}\Tilde{\mathbb{A}}_{V_f}^{A_f} :\left(\left[\frac{\delta_m \alpha \varepsilon_i^{-2} n_{i,k}^m}{1 + \delta_m \alpha (\varepsilon^{-2}_e n_{i,k}^m + \varepsilon^{-2}_i n_{e,k}^m)}\right] \odot \bm{\eta}_e^m + \left[\frac{1 + \delta_m \alpha \varepsilon^{-2}_e n_{i,k}^m}{1 + \delta_m \alpha (\varepsilon^{-2}_e n_{i,k}^m + \varepsilon^{-2}_i n_{e,k}^m)}\right] \odot \bm{\eta}_i^m \right) \nonumber \\
     &\hspace{10cm} - \frac{1}{2} [s_{i,j}]^m \odot \Tilde{\mathbb{D}}_{V_f}^{A_f} [n_{i,k}]^m. \label{equ:tmp15}
\end{align}
The counterpart of (\ref{equ:tmp14})(\ref{equ:tmp15}) for electron is straightforward by switching the subscript $e$ and $i$. Then the mass fluxes for different species remain the same as (\ref{equ:tmp4}), namely
\begin{equation}
    \left[f_{n,*,j}\right]^{m+1} = \Tilde{\mathbb{T}}_{A,*}^{A,m} 
    \begin{bmatrix}
    \mathbf{e} \\
    \mathbf{d}^\partial 
    \end{bmatrix}^{m+1} + \bm{\mu}^m_*.
\end{equation}

Now we have had the relation of the mass fluxes and the $\mathbf{E}$-field related quantities at $t_{m+1}$. By definition of the current density (\ref{equ:current_ap}) we end up with the expression for the generalized Ohm's law 
\begin{equation} \label{equ:tmp5}
    \mathbf{j}^{m+1} = \sum_*q_*\text{diag}(|\Tilde{A}_j|)\left[f_{n,*,j}\right]^{m+1} = \underbrace{\sum_*q_*\text{diag}(|\Tilde{A}_j|) \Tilde{\mathbb{T}}_{A,*}^{A,m}}_{\mathbb{M}_\sigma^m} \begin{bmatrix}
    \mathbf{e} \\
    \mathbf{d}^\partial 
    \end{bmatrix}^{m+1} + \underbrace{\sum_*q_*\text{diag}(|\Tilde{A}_j|) \bm{\mu}^m_*}_{\mathbf{j}^m_\text{aux}},
\end{equation}
The generalized Ohm's law (\ref{equ:tmp5}) is further split into
\begin{equation} \label{equ:tmp6}
    \mathbf{j}^{m+1} =
    \begin{bmatrix}
    \mathbf{j}^{\circ,m+1} \\
    \mathbf{j}^{\partial, m+1}
    \end{bmatrix} =
    \begin{bmatrix}
    \mathbb{M}_{\sigma,11}^m & \mathbb{M}_{\sigma,12}^m \\
    \mathbb{M}_{\sigma,21}^m & \mathbb{M}_{\sigma,22}^m
    \end{bmatrix}
    \begin{bmatrix}
    \mathbf{e} \\
    \mathbf{d}^\partial 
    \end{bmatrix}^{m+1} +
    \begin{bmatrix}
    \mathbf{j}^{\circ, m}_\text{aux} \\
    \mathbf{j}^{\partial,m}_\text{aux}
    \end{bmatrix}.
\end{equation}
Combine (\ref{equ:tmp7}) to (\ref{equ:tmp12}) and (\ref{equ:tmp6}), we end up with the assembled linear system
\begin{multline} \label{equ:linear_system}
    \begin{bNiceArray}{wc{4cm} wc{4cm} wc{2cm} c}[margin, hvlines,rules/color=blue]
    \Block{1-2}{\left(\lambda^2\delta_m^{-1}\mathbb{M}_\varepsilon + \Tilde{\mathbb{C}}^{A^\circ}_{L^\circ}\mathbb{M}^{-1}_\mu \delta_m \mathbb{C}^A_L + \mathbb{M}^m_{\sigma,11}\right)\mathbb{Q}_{L^\circ,\partial P}^{L}} & & \Block{2-1}{-\Tilde{\mathbb{C}}^{A}_{\partial L}} & \mathbb{M}^m_{\sigma,12} \\
    \Block{1-2}{\mathbb{M}^m_{\sigma,21}\mathbb{Q}_{L^\circ,\partial P}^{L}} & & & \lambda^2\delta_m^{-1}\mathbb{I} + \mathbb{M}^m_{\sigma,22} \\
    0 & \mathbb{S}^{\pm}_{\partial P} & 0 & 0 \\
    0 & 0 & 0 & \Tilde{\mathbb{S}}^{A_I}_{\partial A}
    \end{bNiceArray}
    \begin{bNiceArray}{c}
    \mathbf{e}^\circ \\
    \bm{\varphi}  \\
    \mathbf{h}^\partial \\
    \mathbf{d}^\partial 
    \end{bNiceArray}^{m+1}  \\ =
    \begin{bNiceArray}{c}
    \lambda^2\delta_m^{-1}\mathbb{M}_\varepsilon\mathbf{e}^m + \Tilde{\mathbb{C}}^{A^\circ}_{L^\circ} \mathbb{M}^{-1}_\mu\mathbf{b}^m - \mathbf{j}^{\circ,m}_{\text{aux}} \\
    \lambda^2\delta_m^{-1}\mathbf{d}^{\partial,m} - \mathbf{j}^{\partial,m}_\text{aux} \\
    \bm{\varphi}^+(t_{m+1}) \\
    \bm{\varphi}^-(t_{m+1}) \\
    0 
    \end{bNiceArray}
\end{multline}
As soon as $\mathbf{e}^{\circ,m+1}, \bm{\varphi}^{m+1}, \mathbf{h}^{\partial,m+1}, \mathbf{d}^{\partial,m+1}$ are available after solving the linear system, the fluid variables can be updated explicitly according to (\ref{equ:euler_ap}). To this point, the time-stepping is done.

We would like to remark that the whole time-stepping procedure, although appears tedious, does not involve any tricky treatment. What is more important is that the formulation of the linear system helps us to identify problems incurring by the quasi-neutral limit. Upon setting $\lambda = 0$, we want to ensure that the square matrix at the left-hand side remains non-singular, which is indeed the case for our formulation.

\section{Subsystem verification}
Before running the fully-coupled Euler-Maxwell system, subsystems---the Euler solver and Maxwell solver---are separately tested such that we can take confidence in the correctness of the coupled system. The testing closely follows \cite{fuchs_2021}.

\subsubsection{Sod shock tube}
To begin with, we test the fluid solver on Sod shock tube, which is a commonly used case for benchmarking numerical schemes on the Euler equations. Although it is originally a 1D problem, we test it along the $z$-axis in our 3D setup. The result expects to be consistent with the reference solution because of the invariance at the spanwise directions. Fig. \ref{fig:sod_test} shows the results over different mesh sizes as well as the analytical solution \citep{isaac_2017} and indicates the right behavior. 
\begin{figure}
    \centering
    \includegraphics{sod_test.eps}
    \caption{Comparison of results for Sod shock tube case over different mesh refinements and analytical solution. $N$ stands for the number of cells along $z$-axis.}
    \label{fig:sod_test}
\end{figure}
\subsubsection{Uniform steady E-field}
The electric field comes into play in this testing where we expose electrons and ions to the uniform steady E-field $(0,0,1)$, namely unit vector along $z$-axis. For simplicity, two species are assumed to be equal in mass. The magnetic field is set to zero. Collisions among the species are neglected. Initially being static, the electrons and ions expect to be accelerated along the $z$-axis in opposite directions while keeping the temperature unchanged. Fig. \ref{fig:uniform_e_test} shows the behavior we expect. To be noticed is that the temperature slightly decreases over time due to numerical error, and the error is mitigated with mesh refinement.
\begin{figure}
    \centering
    \includegraphics{uniform_E_test.eps}
    \caption{Result when a uniform background $\mathbf{E}$-field exists. The left figure shows the constant accelerations of electrons and ions. The right one indicates the slightly decreasing temperature due to numerical errors.}
    \label{fig:uniform_e_test}
\end{figure}

\subsubsection{Step voltage on anode}
In this case, we test the behavior of the Maxwell system when a step voltage is applied on the anode. Here we consider the domain to be dielectric and be devoid of plasma. In another word, we are dealing with the wave equation
\begin{equation} \label{equ:wave_eq} 
    \lambda^2\partial^2_t\mathbf{E} + \text{curl curl}\mathbf{E} = 0.
\end{equation}
The voltage on anode is given by
\begin{equation*}
    \varphi(t) = \frac{1}{2}\left(1+\text{tanh}\left( \frac{t - 1.0}{0.1}\right) \right).
\end{equation*}
We expect the electric field to produce oscillation with decaying magnitude. Besides, with Debye length $\lambda$ approaching zero, the damping becomes strong since the characteristic time scale is proportional to $\lambda$. Fig. \ref{fig:maxwell_test} (left) shows the $z$-component of $\mathbf{E}$-field at origin up to $t = 15$, and manifests such damping behavior.  
\begin{figure}
    \centering
    \includegraphics{maxwell_test.eps}
    \includegraphics{maxwell_test2.eps}
    \caption{Axial component of the $\mathbf{E}$-field at origin point with step-like voltage on anode. The results are computed under the mesh with 16 cells along axial direction. (left) The domain is an ideal dielectric; (right) the domain is of constant conductivity.}
    \label{fig:maxwell_test}
\end{figure}

If we add to the conductivity of the material, and enforces the Ohm's law $\mathbf{J} = \sigma \mathbf{E}$, the problem to be solved becomes the wave equation with damping term
\begin{equation*}
    \lambda^2\partial^2_t\mathbf{E} + \sigma \partial_t \mathbf{E} - \nabla^2 \mathbf{E} = 0.
\end{equation*}
The introduction of conductivity causes dissipation and thus enhances the damping, as is shown in Fig. \ref{fig:maxwell_test} (right).

\section{Fully-coupled system}
We move on to test the performance of our fully-coupled Euler-Maxwell model (\ref{equ:maxwell_faraday_ap}) to (\ref{equ:current_ap}), and check its AP property.

\subsection{Reduction to 1D}
On noticing the radial symmetry of the domain as well as boundary conditions, the governing equations defined at the axis of symmetry, namely $z$-axis in this case, can be tremendously simplified thanks to vanishing radial components of vector variables and radial derivatives. The Euler-Maxwell system at the axis of symmetry is formulated as 
\begin{align}
    &\partial_t n_* + \partial_z(n_*u_{*,z}) = 0, \\
    &\partial_t (n_* u_{*,z}) + \partial_z(n_*u_{*,z}^2) + \varepsilon_*^{-2} \partial_z P_* = \varepsilon_*^{-2}q_*n_*E_z, \\
    &\partial_t (n_*e_*) + \partial_z (n_* h_* u_{*,z}) = \varepsilon_*^{-2} q_* n_* u_{*,z} E_z, \\
    \lambda^2 &\partial_t E_z = \sum_* - q_* n_* u_{*,z}.
\end{align}
Recall that in section \ref{sec:two_fluid_model} the two-fluid model in 1D setting is discussed and verified. We take the results as reference solutions for the 1D reduction on the $z$-axis of the 3D model. With the same setting as is described in section \ref{sec:1d_two_fluid_numerical_results} and the vanishing anode potentials, we expect the results produced by the purely 1D model and 1D reduction of the 3D model to behave in a similar way, which is shown in Fig. \ref{fig:z_axis_reduction}.
\begin{figure}
    \centering
    \includegraphics{z_axis_reduction.eps}
    \caption{Comparison of 1D two-fluid model and reduced 1D model on $z$-axis from 3D two-fluid model. The results are both generated on meshes with 64 cells along $z$-axis. No friction term exists. $t = 5 \times 10^{-4}.$}
    \label{fig:z_axis_reduction}
\end{figure}

\subsection{Numerical results in 3D} \label{chap:3d_problem}
Now comes the point to finally present the numerical results of the AP scheme on the Euler-Maxwell system in a 3D domain. To recap the problem setting and BCs, see Section \ref{sec:problem_description} and \ref{sec:numerical_experiement_bc}. We consider the two-fluid situation where the plasma is composed of electrons and ions. The mass ratio $m_i / m_e$ is equal to $10^4$. The friction term (\ref{equ:collision_rescaled}) is included with $\alpha^\text{coll} = 32$. Other effects like recombination or ionization are not considered yet.

The initial state is
\begin{equation*}
    n_i(x,y,z,0) = n_e(x,y,z,0) = 1, \ \ \  p_i(x,y,z,0) = p_e(x,y,z,0) = 1.
\end{equation*}
All the other quantities are vanishing initially. The cathode is grounded, and the anode has potential 1.0 throughout the simulation, namely $\varphi^-(t) = 0, \varphi^+(t) = 1.0$. It is intended to see how a stationary system responds to an applied voltage. We would like to remark that such an initial state is conforming to the BCs as well as the quasi-neutral condition $\rho = 0$ so that the quasi-neutrality $\lambda  = 0$ would not incur any initial layer.

In Fig. \ref{fig:3d_vec_field_E_B_ue} we present the vector fields of the numerical solutions for $\lambda = 1.0, 0.01, 0$ at $t = 0.1$, aiming to give an intuitive visualization. First of all, one \emph{a priori} expects the rotational symmetry in the solutions, which serves as a basic criterion to justify the results. In terms of the 3D structure of the electromagnetic fields, the electric field points from the anode to the cathode, and the magnetic field is spiral-shaped and orthogonal to the electric field. The electrons move in the inverse direction of the electric field. Regarding the asymptotic behavior of the AP scheme, the primary concern is its validity in the limiting case. For this case, the scheme manages to produce a meaningful numerical solution when $\lambda = 0$. Besides, by comparing the solutions for different $\lambda$, the smooth transition from the non-neutrality to quasi-neutrality is observed, which is an implication that the scheme reproduces the asymptotic behavior of the analytical solutions from the non-neutral model to the quasi-neutral one.
\begin{figure}
    \centering
    \includegraphics[scale=0.35]{E_lambda_1.png}
    \includegraphics[scale=0.35]{B_lambda_1.png}
    \includegraphics[scale=0.35]{ue_lambda_1.png} \\
    (a) $\lambda = 1.0$ \\
    \includegraphics[scale=0.35]{E_lambda_1e-2.png}
    \includegraphics[scale=0.35]{B_lambda_1e-2.png}
    \includegraphics[scale=0.35]{ue_lambda_1e-2.png} \\
    (b) $\lambda = 0.01$ \\
    \includegraphics[scale=0.35]{E_lambda_0.png}
    \includegraphics[scale=0.35]{B_lambda_0.png}
    \includegraphics[scale=0.35]{ue_lambda_0.png} \\
    (c) $\lambda = 0$
    \caption{Snapshots of the $\mathbf{E}$-field, $\mathbf{B}$-field, and $\mathbf{u}_e$ for different $\lambda$ at $t = 10$ based on a primal mesh with 1920 cells (8 cells along $z$-axis). } 
    \label{fig:3d_vec_field_E_B_ue}
\end{figure}

We perform the grid study and show the result in Fig. \ref{fig:grid_study_3d}. Meshes with different refinement levels are tested for $\lambda = 1$ and $0.1$ at $t = 1$, and the norms of the quantities are calculated. Due to the high computational cost incurred by the curse of dimensionality, only meshes with limited size are tested and the asymptotic regime of the grid study might be not reached. Nevertheless, it still helps to reveal the independence of solutions with respect to meshes --- the norms of electron density and the magnetic field do not deviate in a divergent manner. The exception of the norm of the electric field possibly results from the singularity caused by the interface of the contacting and insulating surfaces, as will be seen later. 
In Fig. \ref{fig:grid_study_3d_clip_lambda-1e-1} and \ref{fig:grid_study_3d_clip_lambda-0}, we plot the distribution of certain quantities at the cross-section based on different meshes for $\lambda = 0.1$ and $0$ at $t = 1$. Thanks to the rotational symmetry of the problem, the solution at the cross-section suffices to characterize the whole solution. The figures again demonstrate the stability of the numerical solutions with respect to mesh refinement in the sense that qualitatively the same solutions are produced by a series of meshes of different sizes. We would like to point out that singularity arises in the $\mathbf{E}$-field at the interface of contacting and insulating surfaces (two points at the left end and two at the right end). In numerical experiments, we observe an increasing magnitude of the $\mathbf{E}$-field at these points as the mesh is refined. Furthermore, it is noted from Fig. \ref{fig:grid_study_3d_clip_lambda-0} (last two rows) that when $\lambda = 0$, the charges carried by ions and electrons cancel out everywhere as indicated by the quasi-neutral condition $\rho = 0$.

\begin{figure}
    \centering
    \includegraphics[scale=0.9]{norm_vs_nCell-T_1.eps}
    \caption{1-norms of quantities with respect to different mesh size: The results are computed for $\lambda = 1$ and $0.1$ at $t = 1$.}.
    \label{fig:grid_study_3d}
\end{figure}

\begin{figure}
    \centering
    Refinement 1\hspace{2.5cm}Refinement 2\hspace{2.5cm}Refinement 3\hspace{1cm}

    \includegraphics[scale=0.27]{clip_E_T-1_lambda-1e-1_8-2-2.png}
    \includegraphics[scale=0.27]{clip_E_T-1_lambda-1e-1_16-3-3.png}
    \includegraphics[scale=0.27]{clip_E_T-1_lambda-1e-1_32-3-4.png}
    \includegraphics[scale=0.27]{clip_B_T-1_lambda-1e-1_8-2-2.png}
    \includegraphics[scale=0.27]{clip_B_T-1_lambda-1e-1_16-3-3.png}
    \includegraphics[scale=0.27]{clip_B_T-1_lambda-1e-1_32-3-4.png}
    \includegraphics[scale=0.27]{clip_ne_T-1_lambda-1e-1_8-2-2.png}
    \includegraphics[scale=0.27]{clip_ne_T-1_lambda-1e-1_16-3-3.png}
    \includegraphics[scale=0.27]{clip_ne_T-1_lambda-1e-1_32-3-4.png}
    \includegraphics[scale=0.27]{clip_ni_T-1_lambda-1e-1_8-2-2.png}
    \includegraphics[scale=0.27]{clip_ni_T-1_lambda-1e-1_16-3-3.png}
    \includegraphics[scale=0.27]{clip_ni_T-1_lambda-1e-1_32-3-4.png}
    \caption{Quantities at the cross-section generated by meshes with different refinement level. Refinement 1: 1920 primal cells; Refinement 2: 14592 primal cells; Refinement 3: 30720 primal cells. The snapshots are computed for $\lambda = 0.1$ at $t = 1$.}
    \label{fig:grid_study_3d_clip_lambda-1e-1}
\end{figure}

\begin{figure}
    \centering
    Refinement 1\hspace{2.5cm}Refinement 2\hspace{2.5cm}Refinement 3\hspace{1cm}

    \includegraphics[scale=0.27]{slice_E_T-1_lambda-0_8-2-2.png}
    \includegraphics[scale=0.27]{slice_E_T-1_lambda-0_16-3-3.png}
    \includegraphics[scale=0.27]{slice_E_T-1_lambda-0_32-3-4.png}
    \includegraphics[scale=0.27]{slice_B_T-1_lambda-0_8-2-2.png}
    \includegraphics[scale=0.27]{slice_B_T-1_lambda-0_16-3-3.png}
    \includegraphics[scale=0.27]{slice_B_T-1_lambda-0_32-3-4.png}
    \includegraphics[scale=0.27]{slice_ne_T-1_lambda-0_8-2-2.png}
    \includegraphics[scale=0.27]{slice_ne_T-1_lambda-0_16-3-3.png}
    \includegraphics[scale=0.27]{slice_ne_T-1_lambda-0_32-3-4.png}
    \includegraphics[scale=0.27]{slice_ni_T-1_lambda-0_8-2-2.png}
    \includegraphics[scale=0.27]{slice_ni_T-1_lambda-0_16-3-3.png}
    \includegraphics[scale=0.27]{slice_ni_T-1_lambda-0_32-3-4.png}
    \caption{Quantities at the cross-section generated by meshes with different refinement level. Refinement 1: 1920 primal cells; Refinement 2: 14592 primal cells; Refinement 3: 30720 primal cells. The snapshots are computed for $\lambda = 0$ at $t = 1$.}
    \label{fig:grid_study_3d_clip_lambda-0}
\end{figure}

To inspect how the system evolves, we extract the time histories of certain quantities at the origin (the center of the tube) up to $t = 10$ and display them in Fig. \ref{fig:origin-data_vs_time}. Being originally at rest, the system is excited by the suddenly applied voltage and generates oscillations that dampen over time. In general, a large value of $\lambda$ leads to stronger oscillations with larger amplitude whereas smaller $\lambda$ incurs more damping and the system rapidly reaches a steady state. It is a reflection of the shielding effect of plasma which is characterized by the Debye length. It can also be noticed that the electron velocity becomes steady much sooner than ion velocity, which is a consequence of the huge difference in inertia. Besides, the convergence of the discrete model as $\lambda \rightarrow 0$ can be observed---the solution becomes steady over time.
\begin{figure}
    \centering
    \includegraphics[scale=0.9]{origin-data_vs_time.eps}
    \caption{Time histories of quantities at the origin for different $\lambda$. The simulation is done on a mesh with 1920 primal cells with 8 layers along $z$-axis.}
    \label{fig:origin-data_vs_time}
\end{figure}

A critical sign of quasi-neutrality is the vanishing charge. In fact, in Section \ref{sec:quasi-neutral_limit} we discuss the limiting model where $\rho = 0$ is satisfied. To examine that, the quantities at the $z$-axis over different $\lambda$ are provided in Fig. \ref{fig:zaxis-data_vs_z-T_10}. The right figure demonstrates the approaching and eventual coincidence of electron and ion densities as $\lambda \rightarrow 0$. Furthermore, with relatively small but non-zero $\lambda$, the bulk of the plasma is approximately neutral while the area near the electrodes is not, which is known as a plasma sheath and within such an area the quasi-neutrality is usually inappropriate.
\begin{figure}
    \centering
    \includegraphics{zaxis-data_vs_z-T_10.eps}
    \caption{Quantities along $z$-axis for different $\lambda$: The results are computed at $t = 10$ on a mesh with 1920 primal cells with 8 layers along $z$-axis.}.
    \label{fig:zaxis-data_vs_z-T_10}
\end{figure}

In Fig. \ref{fig:clip-ne-nue-T_10} the distribution of the electron number density and velocity at the cross-section is displayed. In the non-neutral case, the electrons accumulate near the anode, and the velocity is distributed rather uniformly. With the model approaching quasi-neutrality $\lambda = 0$, the electrons move slower in the bulk area while they are accelerated to high speed at the edge of electrodes, and they tend to accumulate in the middle pass.
\begin{figure}
    \centering
    \begin{subfigure}[b]{0.4\textwidth}
        \centering
        \includegraphics[scale=0.4]{clip-ne-nue-T_10-lambda_1.png}
        \caption{$\lambda = 1$}
    \end{subfigure}
    \begin{subfigure}[b]{0.4\textwidth}
        \centering
        \includegraphics[scale=0.4]{clip-ne-nue-T_10-lambda_1e-1.png}
        \caption{$\lambda = 0.1$}
    \end{subfigure}
    \begin{subfigure}[b]{0.4\textwidth}
        \centering
        \includegraphics[scale=0.4]{clip-ne-nue-T_10-lambda_1e-2.png}
        \caption{$\lambda = 0.01$}
    \end{subfigure}
    \hspace{0.2cm}
    \begin{subfigure}[b]{0.4\textwidth}
        \centering
        \includegraphics[scale=0.38]{clip-ne-nue-T_10-lambda_0.png}
        \caption{$\lambda = 0$}
    \end{subfigure}
    \caption{Electron number density and velocity vector at the cross-section. The results are computed at $t = 10$ on a mesh with 1920 primal cells with 8 layers along $z$-axis. The velocity vector lengths, which indicates the magnitude, are rescaled by the same factor.}
    \label{fig:clip-ne-nue-T_10}
\end{figure}

\section{Summary}
To evaluate the performance of the scheme (\ref{equ:maxwell_faraday_ap}) to (\ref{equ:euler_ap}), we need to examine the two criterion in Definition \ref{def:ap} which states the asymptotic stability and consistency. Both properties are \emph{experimentally} checked in a 3D setting. The former one, referring to the unconditional stability on $\lambda$, is confirmed as the program achieves meaningful solutions for arbitrary $\lambda$ without adjusting the time step size. The latter one requires the convergence of the limit scheme to the limit model, which is supported by two facts: the smooth transition of numerical solutions over $\lambda \in [0,1]$ and the conformity of the quasi-neutral condition $n_i = n_e$.

\chapter{Extension to Insulating Domain}
As is mentioned in Section \ref{sec:impact_insulating_domain}, the scheme so far could not directly handle the case with an insulating domain $\Omega_I$ where no plasma fluid is there. An example is shown in Fig. \ref{fig:sketch_domain_fusch}. Now the plasma domain is enclosed by a insulating sleeve.

We repeat the dilemma again: the scheme fails for $\lambda \rightarrow 0$. The Maxwell system in $\Omega_I$ is    
\begin{align}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:ex_1}\\ 
    \lambda^2 \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= 0,  \label{equ:ex_2}\\
    \nabla \cdot \mathbf{B} &= 0, \label{equ:ex_3}\\
    \lambda^2 \nabla \cdot \mathbf{D} &= 0 \label{equ:ex_4}.
\end{align}
In non-neutral regime, namely $\lambda = \mathcal{O}(1)$, the Maxwell system in $\Omega_I$ is well-posed and Gauss's laws (\ref{equ:ex_3}) (\ref{equ:ex_4}) are redundant. Therefore, they are \emph{implicitly} satisfied (up to numerical errors) in the scheme. Nonetheless, the quasi-neutral limit $\lambda \rightarrow 0$ dismisses the implicit fulfillment of Gauss's law for electric field (\ref{equ:ex_4}) through Amper\`{e}'s law (\ref{equ:ex_2}). A crucial observation is that formally letting $\lambda \rightarrow 0$ makes (\ref{equ:ex_4}) degenerate, but the divergence-free condition of $\mathbf{D}$-field is always satisfied since the system is divergent as $\lambda \rightarrow 0$ [cite something].

The remedy is to \emph{explicitly} include the divergence-free constraint in the scheme for any value of $\lambda$:  
\begin{align}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:ex_5}\\ 
    \lambda^2 \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= 0,  \label{equ:ex_6}\\
    \nabla \cdot \mathbf{D} &= 0 \label{equ:ex_7}.
\end{align}

With the divergence-free constraint (\ref{equ:ex_7}), we have more equations than unknowns, which can be resolved by introducing a Lagrange multiplier $p$ as follows:
\begin{align}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:ex_8}\\ 
    \lambda^2 \partial_t \mathbf{D} - \nabla \times \mathbf{H} + \colorbox{orange!20}{$\nabla p$} &= 0,  \label{equ:ex_9}\\
    \nabla \cdot \mathbf{D} &= 0 \label{equ:ex_10},
\end{align}
supplemented with the boundary condition $p = 0$ on $\partial\Omega_I$. One can check that (\ref{equ:ex_8})-(\ref{equ:ex_10}) are equivalent to (\ref{equ:ex_5})-(\ref{equ:ex_7}) by verifying that $p = 0$ in $\Omega_I$. This is done by taking the divergence of (\ref{equ:ex_9}) such that the Laplace equation of $p$ with zero Dirichlet boundary condition gives vanishing $p$.

The discretization of the Maxwell system in the insulating domain then becomes
\begin{align*}
    \delta_m^{-1} (\mathbf{b}^{m+1} - \mathbf{b}^m) + \mathbb{C}\mathbf{e}^{m+1} &= 0, \\
    \lambda^2\delta_m^{-1} (\Tilde{\mathbf{d}}^{m+1} - \Tilde{\mathbf{d}}^m) - \Tilde{\mathbb{C}}\Tilde{\mathbf{h}}^{m+1} + \colorbox{orange!20}{$\mathbb{H} \mathbb{G} \mathbf{p}^{m+1}$} &= 0 \\
    \Tilde{\mathbb{D}} \Tilde{\mathbf{d}}^{m+1} &= 0.
\end{align*}
where $\mathbb{H}$ is the discrete Hodge operator (matrix\footnote{In our case where the orthogonal mesh pair is used, it is diagonal.}) responsible for transforming any primal-edge-integrated variables to dual-face-integrated ones; the vector $\mathbf{p}$ is the discrete representation of $p$ and is defined on primal vertices lying in $\Omega_I$.

\begin{figure}
    \centering
    \begin{minipage}{0.5\textwidth}
\resizebox{\textwidth}{!}{
    \begin{tikzpicture}
    \coordinate (O1) at (0,0);
    \draw[very thick] (O1) circle (1) node[blue] {Cathode};
    \fill[blue, opacity=0.2] (O1) circle (1);
    \draw[very thick] (O1) circle (1.5);
    \coordinate (O2) at (4.5,1) ;
    \draw[gray] (O2) circle (1);
    \node at (O2) {\textcolor{red}{Anode}};
    \node at (barycentric cs:O1=1,O2=1) {Plasma}; 
    \fill[red, opacity=0.2] (O2) circle (1);
    \coordinate (S1) at ([shift={(-0.196,0.98)}]O1);
    \coordinate (S2) at ([shift={(-0.196,0.98)}]O2);
    \coordinate (P1) at ([shift={(0.196,-0.98)}]O1);
    \coordinate (P2) at ([shift={(0.196,-0.98)}]O2);
    \draw[gray] (S1) -- (S2);
    \draw[gray] (P1) -- (P2);
    \coordinate (SS1) at ([shift={({-0.196*1.5},{0.98*1.5})}]O1);
    \coordinate (SS2) at ([shift={({-0.196*1.5},{0.98*1.5})}]O2);
    \coordinate (PP1) at ([shift={({0.196*1.5},{-0.98*1.5})}]O1);
    \coordinate (PP2) at ([shift={({0.196*1.5},{-0.98*1.5})}]O2);
    \draw[very thick] (SS1) -- (SS2);
    \draw[very thick] (PP1) -- (PP2); 
    \draw[gray] (SS2) arc (101.31:180+101.31:1.5);
    \draw[very thick] (PP2) arc (101.31-180:101.31:1.5);
    \draw[-to] (barycentric cs:SS1=1,SS2=1,S1=1,S2=1) to[out=90,in=0] ([shift={(-0.5,0.5)}]barycentric cs:SS1=1,SS2=1,S1=1,S2=1) node[left, gray] {Insulator};
    \begin{scope}[shift={(5.5,-1.4)}]
    \draw[blue, -to] (0,0) -- (0.65,0.12) node[right]{\small $z$};
    \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
    \draw[blue, -to] (0,0) -- (0.7,0) node[below]{\small $y$};
    \end{scope}
    \end{tikzpicture}}
\end{minipage}
\begin{minipage}{0.49\textwidth}
    \resizebox{1.1\textwidth}{!}{ \begin{tikzpicture}
        \coordinate (A1) at (0,1.5);
        \coordinate (A2) at (0,1);
        \coordinate (A3) at (0,-1);
        \coordinate (A4) at (0,-1.5);
        \coordinate (B1) at (6,1.5);
        \coordinate (B2) at (6,1);
        \coordinate (B3) at (6,-1);
        \coordinate (B4) at (6,-1.5);
        \draw[gray] (A2) -- node[above]{\textbf{Insulator $\Omega_I$}} node[black, below]{reflective wall} (B2);
        \draw[gray] (A3) -- node[below]{\textbf{Insulator $\Omega_I$}} node[black, above]{reflective wall} (B3);
        \draw[very thick] (A2) -- (A1) -- node[above]{$\mathbf{D} \cdot \mathbf{n} = 0, \nabla \times \mathbf{E} \cdot \mathbf{n} = 0$}  (B1) -- (B2);
        \draw[very thick] (A3) -- (A4) -- node[below]{$\mathbf{D} \cdot \mathbf{n} = 0, \nabla \times \mathbf{E} \cdot \mathbf{n} = 0$} (B4) -- (B3);
        \draw[very thick, dashed, blue] (A2) -- node[left, yshift=0.3cm] {$\varphi^-(t)$} node[left, yshift=-0.3cm] {\textcolor{black}{open}} (A3);
        \draw[very thick, dashed, red]  (B2) -- node[right, yshift=0.3cm]  {$\varphi^+(t)$} node[right, yshift=-0.3cm] {\textcolor{black}{open}}  (B3);
        \node at (3,0) {\textbf{Plasma $\Omega_p$}};
        \begin{scope}[shift={(6.5,-1.6)}]
        \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
        \draw[blue, -to] (0,0) -- (0.7,0) node[right]{\small $z$};
        \end{scope}
    \end{tikzpicture}}
\end{minipage}
    \caption{Caption}
    \label{fig:ex}
\end{figure}

The setting of the numerical test is sketched in Fig. \ref{fig:ex}. The initial conditions keep unchanged as Section \ref{chap:3d_problem}.

As predicted in the analytic case, the Lagrange multiplier $p$ is approximately zero (in the order of $\mathcal{O}(10^{-12})$) in the numerical test. The introduction of the surrounding insulator sleeve does not qualitatively alters the 3D structure of the resulting electromagnetic fields (see Fig. \ref{fig:3d_vec_field_E_B_ue}), which are therefore omitted here. In Fig. \ref{fig:time_history_extend} we demonstrate how quantities at the center of the cylinder evolve with time. Comparison with its counterpart Fig. \ref{fig:origin-data_vs_time} shows many similarities. An interesting point is that now the ions move towards the anode, which is not nonphysical since the frictional force could be stronger than the electric force. What matters is the capability of the scheme to handle the quasi-neutral limit.
\begin{figure}
    \centering
    \includegraphics[scale=0.9]{origin_data-vs-time_withInsulator.eps}
    \caption{Time histories of quantities at the origin for different value of $\lambda$. The simulations are done on a mesh with 3840 primal cells with 16 layers along $z$-axis. Compared to fig. \ref{fig:origin-data_vs_time}, an insulating domain is included in this case.}
    \label{fig:time_history_extend}
\end{figure}

\chapter{Conclusion}
We generalize the AP scheme proposed in \cite{degond_2012}, which is originally designed to handle the quasi-neutrality of the Euler-Maxwell system and applied to problems in 1D, to a 3D scenario. Such generalization has been partially done in \cite{fuchs_2021}, and yet an inconsistency in the limiting case remains unsolved. Based upon the framework built by \cite{fuchs_2021}, this thesis proposes several modifications to the algorithm and the targeting problems.

The generalized scheme incorporates FIT and FVM for spatial discretization of Maxwell's equations and the Euler equations. The time discretization is of critical significance in attaining AP property, and the choice of implicit terms conforms to the mentioned references. Additionally, the collision between species is included. Substantial efforts are put on issues related to the boundary. We enforce the BCs under the framework of FIT by introducing auxiliary mesh facets and quantities at the boundary. Furthermore, we identify the proper BCs that are essential for the well-posedness of the Euler-Maxwell system over different regimes. The detailed strategy to assemble the linear system due to the implicitness is presented. The 3D scheme is first validated on the subsystems and is compared to its corresponding 1D discrete model. Solutions performed on the fully-coupled system for $\lambda$ ranging in $[0,1]$ show a smooth transition from the non-neutral model to the quasi-neutral one, which demonstrates that our scheme is AP.

Apart from the implementation of the scheme in 3D, the definition and property of AP schemes are rephrased in a more definite way. Despite a large amount of literature discussing AP schemes, the definition differs from paper to paper and remains vague. In this thesis, we summarize AP properties by two features: asymptotic-stability and asymptotic-consistency, which refer to the unconditional stability on the asymptotic parameter, and convergence of the scheme in the limiting case. We formulate two propositions as an attempt to unveil the connection between these two aspects---the second one might be relaxed by only requiring consistency under certain assumptions.

Future works could be carried out in the following directions. As is discussed in Section \ref{sec:impact_insulating_domain}, the failure arising from the insulating solid domain could be remedied by enforcing $\nabla \cdot \mathbf{D}$ = 0, which is worth pursuing. In terms of implementation, the algorithm is not yet optimized. As the bottleneck, solving the large sparse linear systems consumes nearly all the computation time. The matrix assembly might be smarter such that the resulting linear system possesses certain desired properties, e.g. symmetric positive-definite, and hence a faster solver can be invoked. Besides, the present AP scheme is of first-order in accuracy. The combination of high-order schemes and the AP property is a potential challenge since several issues, e.g. the intra-mesh interpolation of the electromagnetic fields and the discrete material law, could undermine the accuracy. One can also contemplate incorporating the AP property into other numerical frameworks like FEM. Regarding the design of AP schemes, the approaches so far are mostly heuristic and specific to the given problem. A unified strategy of construction and verification is still to be explored.

\begin{appendices}
\chapter{Rusanov Flux in 3D} \label{app:flux}
Consider the Euler equations
\begin{align} \label{equ:euler}
    \partial_t
    \begin{bmatrix}
    \rho \\
    \rho \mathbf{u} \\
    E
    \end{bmatrix}
    + \nabla \cdot
    \begin{bmatrix}
    \rho \mathbf{u} \\
    \rho \mathbf{u} \otimes \mathbf{u} + p\mathbb{I} \\
    (E+p)\mathbf{u}
    \end{bmatrix}
    = 0.
\end{align}
In 3D Cartesian coordinate system, it reads 
\begin{align} \label{equ:euler_xyz}
    \partial_t \mathbf{U} + \partial_x \mathbf{F}^x(\mathbf{U}) + \partial_y \mathbf{F}^y(\mathbf{U}) + \partial_z \mathbf{F}^z(\mathbf{U}) = 0.
\end{align}
where
\begin{equation*}
    \mathbf{U} =
    \begin{bmatrix}
    \rho \\
    \rho u_x \\
    \rho u_y \\
    \rho u_z \\
    E
    \end{bmatrix}, \ \ \ 
    \mathbf{F}^x(\mathbf{U}) =
    \begin{bmatrix}
    \rho u_x \\
    \rho u_x^2 + p \\
    \rho u_y u_x  \\
    \rho u_z u_x \\
    (E + p)u_x
    \end{bmatrix}, \ \ \ 
    \mathbf{F}^y(\mathbf{U}) =
    \begin{bmatrix}
    \rho u_y \\
    \rho u_x u_y \\
    \rho u_y^2 + p \\
    \rho u_z u_y \\
    (E + p)u_y
    \end{bmatrix}, \ \ \ 
    \mathbf{F}^z(\mathbf{U}) =
    \begin{bmatrix}
    \rho u_z \\
    \rho u_x u_z  \\
    \rho u_y u_z  \\
    \rho u_z^2  + p\\
    (E + p)u_z
    \end{bmatrix}
\end{equation*}
\begin{figure}
    \centering
    \begin{tikzpicture}[scale=0.7]
        \coordinate (A1) at (0,0);
        \coordinate (A2) at (2,0);
        \coordinate (A3) at (3,1);
        \coordinate (A4) at (3,3);
        \coordinate (A5) at (1,3);
        \coordinate (A6) at (-1,3);
        \coordinate (A7) at (-2,2);
        \coordinate (A8) at (-2,0);
        \coordinate (A10) at (0,2);
        \coordinate (A11) at (2,2);
        \coordinate (A12) at (-1,1);
        \coordinate (A13) at (1,1);
        \draw[very thick] (A1) -- (A2) -- (A3) -- (A4) -- (A5) -- (A6) -- node[left, yshift=2mm]{$\delta_y$} (A7) -- node[left]{$\delta_z$} (A8) -- (A1);
        \draw[very thick] (A7) -- (A10) -- (A11) -- (A4);
        \draw[very thick] (A1) -- (A10) -- (A5);
        \draw[very thick] (A2) -- (A11);
        \draw[gray] (A6) -- (A12) -- (A8);
        \draw[gray] (A12) -- (A3);
        \draw[gray] (A5) -- (A13) -- (A1); 
        \fill[blue, opacity=0.2] (A1) -- (A10) -- (A5) -- (A13);
        \draw[blue, thick] (-0.75,1.5) node[below=0.5cm] {$\mathbf{U}_L$} -- (0,1.5); 
        \draw[blue, thick, dotted] (0,1.5) -- (0.5,1.5); 
        \draw[blue, thick, -to] (0.5,1.5) -- (1.25,1.5) node[right,xshift=-1mm] {$\overline{\mathbf{F}}$} node[below=0.5cm] {$\mathbf{U}_R$};
        \draw[fill=blue] (0.5,1.5) circle (0.5mm) ;
        \begin{scope}[shift={(4,0)}]
        \draw[blue, -to] (0,0) -- (1,0) node[right]{\small $x$};
        \draw[blue, -to] (0,0) -- (0,1) node[above]{\small $z$};
        \draw[blue, -to] (0,0) -- (0.7,0.7) node[above, xshift=2mm]{\small $y$};
        \end{scope}
        \begin{scope}[shift={(10,0)}]
        \coordinate (P1) at (0,0);
        \coordinate (P2) at (0,1.5);
        \coordinate (P3) at (-1,3);
        \coordinate (P4) at (-3,0);
        \coordinate (P5) at (2.5,2);
        \draw[very thick] (P1) -- (P3) -- (P5) -- (P1);
        \draw[very thick] (P1) -- (P4) -- (P3);
        \draw[gray] (P1) -- (P2) -- (P3);
        \draw[gray] (P4) -- (P2) -- (P5);
        \fill[blue, opacity=0.2] (P1) -- (P2) -- (P3);
        \coordinate (O) at (barycentric cs:P1=1,P2=1,P3=1);
        \coordinate (O1) at ([shift={(1,0.5)}]barycentric cs:P1=1,P2=1,P3=1);
        \draw[blue, thick, -to] (O) -- (O1) node[below=3mm] {$\mathbf{U}_R$} node[right,xshift=-1mm] {$\overline{\mathbf{F}}$};
        \coordinate (S)  at (intersection of O--O1 and P1--P3);
        \draw[blue, thick] (S)--([shift={(-1,-0.5)}]S) node[below=0.1cm, xshift=4mm] {$\mathbf{U}_L$} ;
        \draw[blue, thick, dotted] (S) -- (O);
        \draw[fill=blue] (O) circle (0.5mm);
        \begin{scope}[shift={(4,0)}]
        \draw[blue, -to] (0,0) -- (1,0.5) node[right]{\small $\xi$};
        \draw[blue, -to] (0,0) -- (-0.5,1) node[above]{\small $\zeta$};
        \draw[blue, -to] (0,0) -- (0.5,0.8) node[above, xshift=0mm]{\small $\eta$};
        \end{scope}
        \end{scope}
    \end{tikzpicture}
    \caption{Flux between two cells in 3D Cartesian coordinate.}
    \label{fig:flux_cartesian}
\end{figure}

For the flux through a face orthogonal to $x$-axis, as is shown in Fig. \ref{fig:flux_cartesian}, Rusanov flux reads
\begin{equation} \label{equ:rusanov_flux_original}
    \overline{\mathbf{F}}(\mathbf{U}_L, \mathbf{U}_R) = \frac{1}{2}\left[\mathbf{F}^x(\mathbf{U}_L) + \mathbf{F}^x(\mathbf{U}_R)\right] - \frac{1}{2}\overline{s}\left(\mathbf{U}_R - \mathbf{U}_L\right).
\end{equation}
where $\overline{s} = \text{max}(s(\mathbf{U}_L), s(\mathbf{U}_R))$, $s(\mathbf{U}) := |u_x| + \sqrt{\gamma p/\rho}$ represents the largest wave speed. The numerical flux is derived from the approximate Riemann solver.

For the flux outflowing through arbitrary face with outer normal vector $\bm{\xi}$, as is shown in Fig. \ref{fig:flux_cartesian}, the Euler equations (\ref{equ:euler_xyz}) under $(x,y,z)$ reference coordinate system should be reformulated under $(\xi, \eta, \zeta)$ reference coordinate system:
\begin{align} \label{equ:euler_xez}
    \partial_t \mathbf{U'} + \partial_\xi \mathbf{F}^\xi(\mathbf{U'}) + \partial_\eta \mathbf{F}^\eta(\mathbf{U'}) + \partial_\zeta \mathbf{F}^\zeta(\mathbf{U'}) = 0.
\end{align}
where
\begin{equation*}
    \mathbf{U'} =
    \begin{bmatrix}
    \rho \\
    \rho u_\xi \\
    \rho u_\eta \\
    \rho u_\zeta \\
    E
    \end{bmatrix}, \ \ \ 
    \mathbf{F}^\xi(\mathbf{U'}) =
    \begin{bmatrix}
    \rho u_\xi \\
    \rho u_\xi^2 + p \\
    \rho u_\eta u_\xi  \\
    \rho u_\zeta u_\xi \\
    (E + p)u_\xi
    \end{bmatrix}, \ \ \ 
    \mathbf{F}^\eta(\mathbf{U'}) =
    \begin{bmatrix}
    \rho u_\eta \\
    \rho u_\xi u_\eta \\
    \rho u_\eta^2 + p \\
    \rho u_\zeta u_\eta \\
    (E + p)u_\eta
    \end{bmatrix}, \ \ \ 
    \mathbf{F}^\zeta(\mathbf{U'}) =
    \begin{bmatrix}
    \rho u_\zeta \\
    \rho u_\xi u_\zeta  \\
    \rho u_\eta u_\zeta  \\
    \rho u_\zeta^2  + p\\
    (E + p)u_\zeta
    \end{bmatrix}
\end{equation*}
The density $\rho$, pressure $p$, and energy $E$ remain the same while the velocities satisfy the following transformation
\begin{equation} \label{equ:rotation_relation}
    \begin{bmatrix}
    u_\xi \\
    u_\eta \\
    u_\zeta
    \end{bmatrix}
    =
    \begin{bmatrix}
    \bm{\xi}^T \\
    \bm{\eta}^T \\
    \bm{\zeta}^T 
    \end{bmatrix}
    \begin{bmatrix}
    u_x \\
    u_y \\
    u_z
    \end{bmatrix}, \ \ \ 
    \begin{bmatrix}
    u_x \\
    u_y \\
    u_z
    \end{bmatrix}
    =
    \begin{bmatrix}
    \bm{\xi},\bm{\eta},\bm{\zeta} 
    \end{bmatrix}
    \begin{bmatrix}
    u_\xi \\
    u_\eta \\
    u_\zeta
    \end{bmatrix},
\end{equation}
where $\bm{\xi}, \bm{\eta}, \bm{\zeta}$ denote the unit column vectors of $\xi$-axis, $\eta$-axis, $\zeta$-axis \emph{under $(x,y,z)$ coordinate systems}.
Since now $\xi$-axis is parallel to the face normal, we can use the formula for Rusanov flux (\ref{equ:rusanov_flux_original}) to compute the flux through the face
\begin{equation} \label{equ:rusanov_flux_rotated}
    \overline{\mathbf{F'}}(\mathbf{U}'_L, \mathbf{U}'_R) = \frac{1}{2}\left[\mathbf{F}^\xi(\mathbf{U}'_L) + \mathbf{F}^\xi(\mathbf{U}'_R)\right] - \frac{1}{2}\overline{s}\left(\mathbf{U}'_R - \mathbf{U}'_L\right).
\end{equation}
Note that now everything is under the rotated coordinate system, and the flux (\ref{equ:rusanov_flux_rotated}) need to be transformed into the original coordinate system. To be concrete, the momentum flux, which corresponds to the second, third and fourth components of (\ref{equ:rusanov_flux_rotated}), need to be rotated through the relation (\ref{equ:rotation_relation}), while the density and energy flux remain the same since they are invariant under rotation. Take the term $\mathbf{F}^\xi(\mathbf{U}'_L)$ as an example, its expression under $(x,y,z)$-system reads
\begin{equation*}
    \begin{bmatrix}
    \rho u_\xi \\
    (\rho u_\xi^2 + p)\bm{\xi} + \rho u_\eta u_\xi \bm{\eta} + \rho u_\zeta u_\xi \bm{\zeta}\\
    (E + p)u_\xi
    \end{bmatrix}_L
    = 
    \begin{bmatrix}
    \rho u_\xi \\
    \rho u_\xi(u_\xi\bm{\xi} + u_\eta\bm{\eta} + u_\zeta\bm{\zeta}) + p\bm{\xi}\\
    (E + p)u_\xi
    \end{bmatrix}_L
    = 
    \begin{bmatrix}
    \rho u_\xi \\
    \rho u_\xi u_x + p\xi_1\\
    \rho u_\xi u_y + p\xi_2\\
    \rho u_\xi u_z + p\xi_3\\
    (E + p)u_\xi
    \end{bmatrix}_L
\end{equation*}
under the $(x,y,z)$ coordinate system.

Finally, we end up with Rusanov flux at the face with normal vector $\bm{\xi}$ under $(x,y,z)$-system:
\begin{equation} \label{equ:rusanov_flux_euler}
    \overline{\mathbf{F}}(\mathbf{U}_L, \mathbf{U}_R, \bm{\xi})
    = \frac{1}{2} \left( 
    \begin{bmatrix}
    \rho u_\xi \\
    \rho u_\xi u_x + p\xi_1\\
    \rho u_\xi u_y + p\xi_2\\
    \rho u_\xi u_z + p\xi_3\\
    (E + p)u_\xi
    \end{bmatrix}_L
    +
    \begin{bmatrix}
    \rho u_\xi \\
    \rho u_\xi u_x + p\xi_1\\
    \rho u_\xi u_y + p\xi_2\\
    \rho u_\xi u_z + p\xi_3\\
    (E + p)u_\xi
    \end{bmatrix}_R
    \right)
    - \frac{1}{2}\overline{s}
    \left(
    \begin{bmatrix}
    \rho \\
    \rho u_x \\
    \rho u_y \\
    \rho u_z \\
    E
    \end{bmatrix}_L
    -
    \begin{bmatrix}
    \rho \\
    \rho u_x \\
    \rho u_y \\
    \rho u_z \\
    E
    \end{bmatrix}_R
    \right),
\end{equation}
where $\overline{s} = \text{max}(s(\mathbf{U}_L), s(\mathbf{U}_R))$, $s(\mathbf{U}) := |u_\xi| + \sqrt{\gamma p/\rho}$. Recall that $u_\xi$ is defined in (\ref{equ:rotation_relation}) which is the velocity projection on $\bm{\xi}$. Obviously it is nothing but formula (\ref{equ:rusanov-flux-3d}).

\chapter{Implementation in \texttt{C++}}
On presenting the numerical scheme for the Euler-Maxwell system under the framework of FIT and FVM, in this section, we want to illustrate the skeleton of our implementation including the data structure, the fluid solver, and Maxwell solver. Due to the coupling of two systems and the specially designed time discretization scheme, the update of quantities follows a complex sequence, which we want to make clear here. The program is written in \texttt{C++}.

This chapter is aimed to convey concrete ideas on how such a complex system is tackled in a computer program. Although the program is intended for simulating the case presented in Chapter \ref{chap:numerical_experiments_in_3d}, we would like to provide sufficient generality for other problems and make it extensible for more advanced algorithms.

\section{Data structure}
We refer to the data structure as the way of defining how the information of meshes is organized in the program. To allow the ability to tackle problems with complex geometries, we treat meshes in an unstructured manner, that is, the topological relations between elements (facets, as is defined before) cannot be induced by the indexing and have to be stored.

We define a parent class \texttt{GeometryItem} that only manages the indexing. Four child classes are derived from it. They are \texttt{Vertex}, \texttt{Edge}, \texttt{Face} and \texttt{Cell}, representing facets of zero, one, two and three dimensions. A class \texttt{Mesh} is defined to collect all these facet objects that compose an mesh.

In terms of the topology of a mesh, a facet object, say a $k$-dim facet, is aware of all the $(k-1)$-dim facets that it contains as well as all the $(k+1)$-dim facets containing it. Meanwhile, each object has its internal orientation. Each class provides a function \texttt{getIncidence} to check whether the internal orientation of a $(k-1)$-dim facet coincides with its external orientation induced by the $k$-dim facet. This information already suffices to construct the incidence matrices mentioned in Section \ref{sec:fit}.

The geometry is determined by the coordinates of all the \texttt{Vertex} objects, based on which each facet class can define its geometric property, such as length for \texttt{Edge}, area for \texttt{Face} and volume for \texttt{Cell}.

These components consist of the basic data structure used in our program. Some code snippets for their definitions are given in the following.

\begin{lstlisting}[numbers=none]
class GeometryItem
{
public:
    ...
private:
    int index;
    ...
};
\end{lstlisting}

\begin{minipage}{0.465\textwidth}
\begin{lstlisting}[numbers=none]
class Vertex :
    public GeometryItem
{
public:
    ...
private:
    Eigen::Vector3d position;
    std::vector<Edge*> edgeList;
    ...

};
\end{lstlisting}
\end{minipage}
\hfill
\begin{minipage}{0.465\textwidth}
\begin{lstlisting}[numbers=none]
class Edge :
    public GeometryItem
{
public:
    double getLength();
    int getIncidence(const Vertex* v);
    ...
private:
    std::vector<Vertex*> vertexList;
    std::vector<Face*>   faceList;
    ...
};
\end{lstlisting}
\end{minipage}

\begin{minipage}{0.465\textwidth}
\begin{lstlisting}[numbers=none]
class Face :
    public GeometryItem
{
public:
    double getArea();
    int getIncidence(const Edge* e);
    ...
private:
    std::vector<Edge*> edgeList;
    std::vector<Cell*> cellList;
    ...
};
\end{lstlisting}
\end{minipage}
\hfill
\begin{minipage}{0.465\textwidth}
\begin{lstlisting}[numbers=none]
class Cell :
    public GeometryItem
{
public:
    double getVolume();
    int getIncidence(const Face* f);
    ...
private:
    std::vector<Vertex*> faceList;
    ...

};
\end{lstlisting}
\end{minipage}

\hfill
\begin{minipage}{0.97\textwidth}
\begin{lstlisting}[numbers=none]
class Mesh
{
public:
    ...
protected:
    std::vector<Vertex*> vertexList;
    std::vector<Edge*>   edgeList;
    std::vector<Face*>   faceList;
    std::vector<Cell*>   cellList;
    ...
};
\end{lstlisting}
\end{minipage}

Two child classes \texttt{PrimalMesh} and \texttt{DualMesh} are derived from the parent class \texttt{Mesh} with some functions for their construction.

\section{Class for the fluid solver}
A class \texttt{FluidSolver} is defined to handle the computation related to the Euler system, such as the equation of state, the transformation between primitive and conservative quantities, the numerical flux, the time-stepping scheme. A \texttt{FluidSolver} object has information about the \texttt{DualMesh} object on which the Euler equations are solved. It maintains an array of fluid quantities whose indexing conforms to the one defined by the \texttt{DualMesh} object and is responsible to evolve it over time. The functions for applying the source term, such as the Lorentz force and the friction term, are also provided. These basic components are shown in the following code block.
\begin{lstlisting}[numbers=none]
class FluidSolver
{
public:
    ...
    void updateFlux(); // compute the numerical flux at each face
    void timestepping(const double dt);
private:
    ...
    void applyLorentzForce(const Eigen::MatrixXd &E, const Eigen::MatrixXd &B);
    void applyFrictionTerm(const FluidSolver* anotherSpecies, const double alpha);
    Eigen::VectorXd Flux(const Eigen::VectorXd &q, const Eigen::Vector3d &fn) const;
    Eigen::VectorXd RusanovFlux(const Eigen::VectorXd & qL, 
                                const Eigen::VectorXd & qR,
                                const Eigen::Vector3d & fn) const;
    Eigen::VectorXd conservative2primitive(const Eigen::VectorXd &q_cons) const;
    Eigen::VectorXd primitive2conservative(const Eigen::VectorXd &q_prim) const;

    const DualMesh* mesh;
    Eigen::MatrixXd U;  // conservative variable at each fluid cell
    Eigen::MatrixXd F;  // flux at each fluid face
    Eigen::MatrixXd rhs;// rhs at each fluid cell
};
\end{lstlisting}

To deal with the multi-species model, multiple \texttt{FluidSolver} objects are built at the simulation, and each of them is responsible for just one species. Hence, a class that wraps them together is needed and it has full control of these objects. In another word, it is representative of the Euler system and interacts with the Maxwell system over the simulation. Recall that such interaction is realized through the generalized Ohm's law (\ref{equ:tmp5}), namely providing $\mathbf{M}_\sigma$ and $\mathbf{j}_{\text{aux}}$.

In the two-fluid model, for instance, we define a class \texttt{TwoFluidSolver} that owns two \texttt{FluidSolver} members for electrons and ions. Some of its essential members are shown below.
\begin{lstlisting}[numbers=none]
class TwoFluidSolver
{
public:
    ...
    void updateFlux(); // compute the numerical fluxes of each species 
    void timestepping(const double dt); // do time-stepping for each species
    Eigen::SparseMatrix<double> get_M_sigma(const double dt); 
    Eigen::VectorXd get_j_aux(const double dt, const Eigen::MatrixXd& B) const; 
private:
    ...
    const PrimalMesh* primal;
    const DualMesh* dual;
    FluidSolver electron_solver;
    FluidSolver ion_solver;
};
\end{lstlisting}

\section{Class for the Maxwell solver}
Under the framework of FIT, a Maxwell solver takes care of the integral quantities on mesh facets and evolves them according to Maxwell's Grid Equations described in Section \ref{sec:fit}. Due to the implicit scheme, a linear system has to be solved at each time step, and the assembling of such a linear system is accomplished by the Maxwell solver. Besides, the Maxwell system influences the Euler system by the Lorentz force which entails interpolation of electromagnetic fields based on the integral quantities defined on mesh facets. These missions are assigned to the class \texttt{MaxwellSolver}, whose definition is briefly given as follows.
\begin{lstlisting}[numbers=none]
class MaxwellSolver
{
public:
    ...
    void solveLinearSystem(const double time, const double dt,
                           Eigen::SparseMatrix<double>&& M_sigma, 
                           Eigen::VectorXd&& j_aux);
    void evolveMagneticFlux(const double dt);
    Eigen::MatrixXd getInterpolated_E() const;
    Eigen::MatrixXd getInterpolated_B() const; 
private:
    ...
    const PrimalMesh* primal;
    const DualMesh* dual;

    Eigen::VectorXd eo;  // E-field integral at interior primal edge
    Eigen::VectorXd phi; // electric potenial at boundary primal vertex
    Eigen::VectorXd hp;	 // H-field integral at boundary dual edge  
    Eigen::VectorXd dp;	 // D-field integral at boundary dual face
};
\end{lstlisting}

\section{Workflow for simulations}
To perform a simulation, the primal and dual meshes are first generated with the boundary facets assigned with their boundary type. The inherent property of each plasma species, such as mass, charge number, and thermodynamic properties, are specified in the corresponding \texttt{FluidSolver} object. On setting the initial conditions, the discrete system can evolve until $t_{\text{end}}$.

The implementation of the AP scheme (\ref{equ:maxwell_faraday_ap}) to (\ref{equ:euler_ap}) requires particular attention on the order of updating quantities. In principle, the time step d$t$ satisfying CFL conditions is first fixed by invoking \texttt{TwoFluidSolver}. With the generalized ohm's law (\ref{equ:tmp5}) being provided by \texttt{TwoFluidSolver}, the Maxwell system is updated, followed by the Euler system. The pseudo-code depicting the typical workflow is given as follows. The input and output procedures are omitted.

\vspace{0.5cm}
\begin{minipage}{0.9\textwidth}
\fbox{
\parbox{\textwidth}{
\begin{algorithmic}
\State Init \texttt{PrimalMesh} and \texttt{DualMesh};
\State Init \texttt{TwoFluidSolver} and \texttt{MaxwellSolver};
\While{$t < t_{\text{end}}$}
\State \texttt{TwoFluidSolver} updates the numerical fluxes and computes d$t$;
\State \texttt{TwoFluidSolver} computes $\mathbf{M}_\sigma$ and $\mathbf{j}_{\text{aux}}$ in (\ref{equ:tmp5});
\State \texttt{MaxwellSolver} assembles and solves the linear system (\ref{equ:linear_system});
\State \texttt{MaxwellSolver} interpolates $\mathbf{E}$-field and $\mathbf{B}$-field;
\State \texttt{TwoFluidSolver} updates the momenta (\ref{equ:tmp1}) or (\ref{equ:tmp13});
\State \texttt{TwoFluidSolver} updates the implicit mass fluxes (\ref{equ:flux_ap});
\State \texttt{TwoFluidSolver} evolves all the fluid quantities as (\ref{equ:euler_ap});
\State \texttt{MaxwellSolver} evolves magnetic fluxes as (\ref{equ:maxwell_faraday_ap}); 
\State $t = t + \text{d}t$;
\EndWhile
\end{algorithmic}
}}
\end{minipage}
\end{appendices}

\bibliography{bib}
\end{document}

### 2022-09-11 paper_version/main.tex
basic setup

--- 2022-09-11 master_thesis_version/main.tex
@@
 \usepackage{amsthm}
-\usepackage{nicematrix}
-\usepackage{subcaption}
-\usepackage{pdfpages}
-\usepackage{algpseudocode}
-\DeclareMathOperator*{\argmin}{arg\,min}
 
-\usepackage{listings}
-\lstset { %
-    language=C++,
-    backgroundcolor=\color{white}, % set backgroundcolor
-    numbers=none,
-    frame=shadowbox,
-    basicstyle=\footnotesize,% basic font setting
-}
-
-\NiceMatrixOptions{cell-space-top-limit = 4pt}
-\NiceMatrixOptions{cell-space-bottom-limit = 4pt}
-
-\usepackage{bm}
-\usepackage{appendix}
-
-\newtheorem{definition}{Definition}
-\newtheorem{proposition}{Proposition}
-\newtheorem*{remark}{Remark}
-
-\usepackage{amsmath}
-\usepackage{graphicx}
-\usepackage{xcolor}
-\usepackage{tcolorbox}
-\tcbuselibrary{theorems}
-\newtcbtheorem
-  []% init options
-  {tcb-def}% name
-  {Definition}% title
-  {%
-    colback=green!5,
-    colframe=green!35!black,
-    fonttitle=\bfseries,
-  }% options
-  {def}% prefix
-\newtcbtheorem
-  []% init options
-  {tcb-prop}% name
-  {Proposition}% title
-  {%
-    colback=blue!5,
-    colframe=blue!80!black,
-    fonttitle=\bfseries,
-  }% options
-  {prop}% prefix
-
-\usepackage{natbib}
-\usepackage[figurename=Fig.,tablename=Tab.,labelfont={bf}]{caption}
-\usepackage{listings}
-\usepackage{tikz}
-\usetikzlibrary{positioning, decorations.markings, arrows, intersections}
-\bibliographystyle{apalike}
-\setcitestyle{authoryear,open={(},close={)}} %Citation-related commands
-\usepackage[linkbordercolor=green]{hyperref}
-\usepackage{geometry}
-\geometry{a4paper,scale=0.8}
-
-\definecolor{codegreen}{rgb}{0,0.6,0}
-\definecolor{codegray}{rgb}{0.5,0.5,0.5}
-\definecolor{codepurple}{rgb}{0.58,0,0.82}
-\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
-
-\lstdefinestyle{mystyle}{
-    backgroundcolor=\color{backcolour},   
-    commentstyle=\color{codegreen},
-    keywordstyle=\color{magenta},
-    numberstyle=\tiny\color{codegray},
-    stringstyle=\color{codepurple},
-    basicstyle=\ttfamily\footnotesize,
-    breakatwhitespace=false,         
-    breaklines=true,                 
-    captionpos=b,                    
-    keepspaces=true,                 
-    numbers=left,                    
-    numbersep=5pt,                  
-    showspaces=false,                
-    showstringspaces=false,
-    showtabs=false,                  
-    tabsize=2
-}
-
-\lstset{style=mystyle}
-
-\newcommand{\mathcolorbox}[2]{\colorbox{#1}{$\displaystyle #2$}}
-\newcommand{\note}[1]{{\footnotesize \textcolor{blue}{[\textbf{#1}]}}}
-
-\title{\textbf{Asymptotic-preserving Plasma Model in 3D}}
-\author{Tianwei Yu}
-\date{\today}
+\title{APPM report - Draft}
+\author{T.W. Yu, R. Fuchs, R. Hiptmair}
 
 \begin{document}
+\maketitle
 
-\begin{titlepage}
-\noindent \includegraphics[]{ETHlogo.pdf}
+\chapter{Introduction}
 
-\centering
-\vspace*{7cm}
-
-\textbf{\LARGE Asymptotic-Preserving Plasma Model in 3D}
-
-\vspace{3cm}
-\large
-
-Master thesis
-
-\vspace{0.25cm}
-
-\textbf{Tianwei Yu}
-
-\vspace{0.25cm}
-
-\today
-
-\vspace{7cm}
-
-Supervisor: Prof. Dr. Ralf Hiptmair
-
-\vspace{0.25cm}
-
-Department of Mathematics, ETH Z\"{u}rich
-
-\end{titlepage}
-
-\chapter*{Abstract}
-Plasma physics involves complex phenomena characterized by multiple scales, for example, the propagation of electromagnetic fields, the interaction between charged particles and electromagnetic fields, and the drift of fluids.
-To numerically simulate plasmas, discretization schemes that can automatically adapt to the scale of interest and remain stable regardless of the system scales are desirable.
-In this thesis, we discuss asymptotic-preserving (AP) schemes for the Euler-Maxwell system parametrized by the dimensionless Debye length $\lambda$ in a 3D setting for multi-species plasma modeling.
-The key capability of the AP scheme is the uniform performance, in the sense of stability and convergence, for a series of problems that are parametrized by arbitrary $\lambda$ and constitute a singular perturbation as $\lambda \rightarrow 0$.
-As the first part of the thesis, the AP property, still being a vague concept throughout literature, is clarified by two aspects: asymptotic-stability and asymptotic-consistency, which respectively refer to the unconditional stability on the asymptotic parameter and the convergence of the limit scheme to the limit model.
-Two propositions discussing some sufficient conditions for general AP schemes are presented, hopefully providing deeper insights into the AP property and some guidance for devising AP schemes.
-In the sequel, we reproduce the results in \cite{degond_2012}, based on which we extend the 1D two-fluid discrete Euler-Maxwell model to a more general model in a 3D setting that involves multiple species, friction terms, and possibly other source terms.
-The 3D discrete model for the Euler-Maxwell system is implemented based on the frameworks of Finite Volume Method (FVM) and Finite Integration Technique (FIT) for the Euler system and the Maxwell system respectively.
-Details about the procedure of time-stepping and the assembly of the linear system due to implicitness are provided.
-An essential aspect lies in the choice of right boundary conditions that are compatible with both non-limit and limit models.
-The discrete model is tested on a case that is adapted from \cite{fuchs_2021} due to the difficulty arising from the insulating solid domain.
-As verification, the scheme is checked on the subsystems and is compared with the corresponding 1D discrete model.
-The numerical results on the fully-coupled system with $\lambda$ ranging in $[0,1]$ manifest a continuous transition from the non-neutral model ($\lambda = \mathcal{O}(1)$) to the quasi-neutral model ($\lambda = 0$), which, as well as the convergence of the solutions over time, implies that the scheme is AP.
-
-\chapter*{Acknowledgements}
-First, I would like to extend my deepest gratitude to my supervisor Prof.
-Ralf Hiptmair.
-His proposal for this thesis combines fluid dynamics, a topic that I am familiar with, and electromagnetism, a completely new world for me.
-With reasonable amounts of theoretical and implementation work, I had much fun in the process of freely exploring the knowledge and accomplishing the task step by step.
-His constant and insightful input was always inspiring at the moment when I was lost.
-In a word, it was a pleasant, adventurous, and memorable journey.
-
-My appreciation also goes to Dr.
-Roman Fuchs, who gave me a lot of guidance on familiarizing myself with the topic and the underlying C++ code.
-I would also like to acknowledge the help of my colleague Langwen Huang in the configuration of the running environment on the cluster, which potentially saved me considerable time.
-
-Meanwhile, I would like to thank my girlfriend, friends, and flatmates for their company and support during the thesis work as well as my Master's life. I wish them all a bright future.
-
-In the end, I would like to express my special gratitude to my parents for their financial support and emotional care. They are always my strongest back no matter what setbacks I encounter.
-
-\tableofcontents
-\chapter{Introduction}
-\section{Plasma}
-Often described as the fourth state of matter, plasma is an ionized gas phase substance that consists of positively-charged \emph{ions}, negatively-charged \emph{electrons} and neutrally-charged atoms.
-Although plasmas seem to be intangible in our daily life, most of the material in the universe is in the plasma state \citep{gurnett2005}.
-They are largely associated with various astrophysical phenomena like sunspots, solar flares, planetary radiation belts.
-Regarding terrestrial plasmas, they can be found or exploited in many situations, for instance, lightning, gas-discharge lamps, controlled thermonuclear fusion.
-
-A plasma is classically defined as \emph{a quasi-neutral gas of charged particles showing collective behavior} \citep{chen_1994}.
-The \emph{collective} behavior arises due to the long-range nature of $1/r$ Coulumb potential \citep{gibbon2020}.
-Besides, the dynamics of plasma particles are largely determined by an internally-driven electromagnetic field, in the sense that the charges generate an electric field, and carry an electric current that induces a magnetic field.
-In contrast, a gas in a neutral state is largely characterized by inter-particle collision.
-The second key feature, \emph{quasi-neutrality}, refers to the tendency to keep the overall charges neutral in the scale of the Debye length $\lambda_D$, which is an important plasma parameter and will be elucidated in the later section.
-
-In classical plasma theory, three criteria must be satisfied to distinguish plasmas from ionized gases \citep{chen2016}.
-First, the quasi-neutrality requires that the Debye length $\lambda_D$ is much smaller than the system scale $L$.
-Second, to make the quasi-neutrality a statistically valid concept, the number $N_D$ of particles in a ``Debye sphere ", namely $N_D := n4/3\pi\lambda_D^3$ with $n$ being the number density of particles, must be large enough.
-The third criterion states the dominance of the electromagnetic forces over the hydrodynamics forces in driving the motions of particles.
-
-\subsection{Fluid model}
-To describe the dynamics of plasmas, a natural and extremely precise way is to treat it as a collection of particles and to monitor the positions and velocities of each particle, namely \emph{N-body dynamics}.
-It has been proven powerful in analytically describing effects relevant to plasmas \citep{escande2015}.
-However, a typical plasma density might be $10^{18}$ particles per $m^3$ \citep{chen2016}, which is way far from affordable for today's computers if one attempts to numerically simulate it.
-Therefore, relatively crude models are necessary for plasma simulations.
-The \emph{kinetic model} is another successful tool to describe plasmas.
-It compiles the state of a collection of particles in the form of probabilistic distributions of velocity and usually consists of the Vlasov-Maxwell equations with velocity distribution functions as variables.
-See \cite{chaudhary2018} for details on the kinetic description of plasmas.
-
-An even simpler model, \emph{fluid model}, described by the Euler-Maxwell equations, can be derived by taking the moments of the Vlasov-Maxwell equations supplemented with some closure assumption.
-Specifically, we take the velocity distribution to be $Maxwellian$, by which the distribution can be characterized by its moments.
-In this way, the fluid model describes the evolution of the moments, e.g.
-number density, drift velocity, pressure, rather than the distribution.
-Such a treatment reduces the complexity of the system at the cost of some information.
-This bridging between the fluid model and the kinetic model applies reasonably for ordinary hydrodynamics where the Maxwellian velocity distribution results from frequent collisions.
-It seems problematic for a plasma since generally, the collision rate is very low in a plasma due to its dilute nature.
-However, the experimental work of \cite{langmuir1925} demonstrates the surprising validity of the Maxwellian assumption for plasmas.
-This phenomenon is known as \emph{Langmuir paradox} which remains unsolved.
-Readers are referred to \cite[][p.
-63]{chen2016} for some discussions.
-It is worth noting that the fluid model suffices for the majority of plasma phenomena, but certain situations exist where neither the fluid model is applicable, nor is the kinetic theory.
-
-In the fluid model of plasma, each species of particles is equipped with a full set of fluid equations into which the Lorentz force and other plasma effects are incorporated.
-Maxwell's equations govern how an electromagnetic field is generated by the charged fluids, their motions, and changes of the fields.
-For such a coupled system, various assumptions are usually made to reduce complexity according to specific scenarios.
-In the simplest case, one considers a fully-ionized plasma and treats the ions, which are about $10^4$ times heavier than electrons, to be immobilized.
-Such simplification makes sense when phenomena at the scale of electron motions are of particular interest, and thus leads to so-called \emph{one-fluid} model\footnote{In this report, we think of ions, electrons, and neutral atoms as `fluid', and each `fluid' is described by a set of fluid equations.
-Also, `species' and `fluid' are synonymous here.
-Notice that in some literature they have different meanings.} in the sense that only one set of fluid equations is sufficient.
-To study more realistic situations, motions of multiple species of particles ought to be simulated.
-Furthermore, other effects like viscosity, ionization, recombination, and collisions could play important roles in many applications.
-
-\subsection{Quasi-neutrality} \label{sec:quasi-neutrality}
-Let's imagine such a situation: in a neutral\footnote{It means the net charge vanishes everywhere.} plasma with temperature $T_0$ and electron number density $n_0$, the electrons contained in cube volume $d^3$ are, due to thermal motions, separated from ions.
-The non-zero charge thus gives rise to an induced electric field, and the energy required for this movement is of magnitude $n_0e^2d^2 / \varepsilon_0$ for a single particle.
-In the absence of external forces, this energy must come only at the expense of the thermal energy \citep{frank_1972}, which is of magnitude $k_BT_0$.
-Only when the energy required for the displacement is less than the thermal energy can this local unbalance of charges happen.
-By balancing these two energy magnitudes we get the length scale
-
-\begin{equation*}
-    d \sim \left(\frac{\varepsilon_0k_BT_0}{e^2n_0}\right)^{1/2} =: \lambda_D
-\end{equation*}
-which is termed \emph{Debye length}\footnote{The Debye length is usually defined for electrons.
-In fact, one can define different Debye lengths for other species.}.
-The Debye length is a fundamental property of nearly all plasmas of interest \citep{gibbon2020}.
-Being a crucial plasma parameter, it is a characteristic length scale over which the perturbation of electric charges is screened due to random thermal motions.
-With a small $\lambda_D$, the mismatch of positive and negative charges would be limited to a small area.
-Hence the plasma is approximately \emph{neutral}, namely canceling out in net charges, over a relatively large spatial scale.
-Such phenomenon of effectively shielding the electrostatic field within a distance of the order $\lambda_D$ is called \emph{Debye shielding}.
-
-Now comes the illustration of \emph{quasi-neutrality}, which is a common property of plasmas.
-Consider $L_0$ as the characteristic length scale of the system, upon which the dimensionless Debye length $\lambda$ is readily defined as
-\begin{equation*}
-    \lambda := \frac{\lambda_D}{L_0}.
-\end{equation*}
-When $\lambda_D$ is much smaller than $L_0$, any local charge unbalance is shielded out within distance of the order $L_0$.
-The quasi-neutrality refers to such a situation that the plasma is neutral enough such that one can take $\rho \approx 0$, but not so neutral that all the interesting electromagnetic forces vanish \citep{chen2016}.
-In other words, the quasi-neutrality does not render the plasma a neutral gas such that it has no interaction with the electromagnetic field.
-
-From a mathematical viewpoint, the quasi-neutrality assumption causes the degeneracy of Gauss's law for the electric field to the quasi-neutral condition $\rho = 0$.
-Despite the vanishing electric charge $\rho$, the electric field is \emph{not} divergence-free.
-Such degeneracy of the system poses challenges when one has to deal with the non-neutral and quasi-neutral models---two systems of different mathematical properties---at the same time.
-
-\section{Asymptotic-preserving schemes}
- Many important partial differential equations (PDEs) systems involve asymptotic parameters (denoted by $\lambda$ from now on), which might take value from $\lambda = \mathcal{O}(1)$ to $\lambda \ll 1$ at different regimes of the targeting problem, e.g.
-the relaxation of collision term (or Knudsen number \textbf{Kn}) in Boltzmann equations, Mach number \textbf{Ma} in the Navier-Stokes (N-S) equations, and the Debye length $\lambda_D$ in the Euler-Maxwell system.
-These parameters have close connections with the characteristic scale of the system, e.g.
-wave speed and relaxation time.
-As the asymptotic parameter $\lambda$ approaches zero, the limit solution (if exists) is described by a set of PDEs of a different type from the non-limit one.
-A \emph{singular perturbation} problem hence arises (See \cite{mark_1995} for related theories).
-For instance, the Boltzmann equation tends to the compressible N-S equations as \textbf{Kn} $\rightarrow 0$; the compressible N-S equations approach the incompressible case as \textbf{Ma} $\rightarrow 0$, and the fluid pressure switches its hyperbolic character to the elliptic one.
-To give an intuition about the singular perturbation, consider a toy model
- \begin{equation} \label{equ:toy-model}
-     \lambda u' + u = 0, u:[0,\infty]\rightarrow\mathbb{R},
- \end{equation}
- which is a first-order ordinary differential equation (ODE). Let $\lambda$ go to zero, the (pointwise) limit solution satisfies 
- \begin{equation*}
-     u = 0,
- \end{equation*}
- which is no longer a first-order ODE.
-
- Following \cite{jin_2010}, we refer to the original system ($\lambda = \mathcal{O}(1)$) as \emph{microscopic} model while the limiting system ($\lambda \rightarrow 0$) as \emph{macroscopic} model, denoting them by $P^\lambda$ and $P^0$ respectively.
-If either the macroscopic or the microscopic model is uniformly valid in the whole domain, one can devise schemes accordingly.
-In fluid dynamics, for example, different solvers are tailored for compressible and incompressible flows.
-Applying schemes for $\lambda = \mathcal{O}(1)$ to the problem with $\lambda \ll 1$ would be problematic because schemes for $P^\lambda$ are usually subject to CFL-like conditions dependent on $\lambda$.
-For instance, \textbf{Ma} is inversely proportional to the sound speed; Debye length is inversely proportional to the wave speed.
-Under-resolving these small scales usually lead to instability.
-Therefore, $\lambda \ll 1$ would pose very strict restriction on time-step size, leading to prohibitive computational cost.
-Look back to the toy model (\ref{equ:toy-model}).
-A reasonable scheme for $\lambda = \mathcal{O}(1)$ is the explicit Euler
- \begin{equation*}
-     \lambda\frac{u^{n+1}-u^{n}}{\delta} + u^n = 0.
- \end{equation*}
-Yet obviously if the time-step size $\delta$ is fixed, it does not apply to arbitrarily small $\lambda$ due to the stability condition $\delta < 2\lambda$.
-
- The standard strategy to handle problem $P^\lambda$ with $\lambda \ll 1$ is to solve $P^0$ instead of $P^\lambda$ under the assumption that $P^0$ is a good approximation of $P^\lambda$.
-For instance, the fluid limit of the Boltzmann equation removes the restrictive stability condition that is dependent on a small relaxation length; the incompressible N-S equations eliminate the need to resolve the sound speed whereas it is necessary in the compressible case.
-However, challenges occur when sub-domains with $\lambda = \mathcal{O}(1)$ and $\lambda \ll 1$ coexists in the computational domain.
-To mention some examples, the reentry problem of space shuttles involves both rarefied and dense gases; the plume of a convergence-divergence nozzle experiences \textbf{Kn} from small to very large value \citep{jenny2015}; the plasma sheath near the wall area violates the quasi-neutral assumption in contrast to the quasi-neutral bulk area.
-To handle such hybrid problems, the classical approach is to split the domain and apply schemes accordingly.
-However, the criterion for domain splitting is not straightforward and quite empirical.
-In addition, the projection of solutions from one model to another in the transitional area adds to complexity \citep{jin_2010, degond_2011}.
-In other words, the non-uniformity of numerical schemes on microscopic and macroscopic models poses a great challenge in handling problems in a transitive regime.
-
- This dilemma spurs tremendous interests in developing schemes that work \emph{uniformly} well for $\lambda \in [0,1]$ with fixed spatial/time step.
-Such a scheme is expected to produce satisfactory results without resolving the smallest scale and provide a more elegant and unified solution to problems in a transitive regime.
-At this point, we introduce the concept of \emph{asymptotic-preserving} (AP) schemes.
-We resort to the celebrated commuting diagram Fig.
-\ref{fig:illustration_ap} in \cite{jin_1999} which sketches the property that an AP scheme should possess.
-As is defined above, $P^\lambda$ and $P^0$ stand for the (solutions of) microscopic and macroscopic models respectively.
-We introduce the discrete model $P^\lambda_h$ based on some AP scheme, whose solution depends on both the asymptotic parameter $\lambda$ and the spatial (or temporal) step size $h$.
-We stress that each limit in Fig.
-\ref{fig:illustration_ap} is attained by letting one parameter go to zero while fixing the other.
-As a basic requirement, the discrete microscopic model $P^\lambda_h$ should at least converge to its analytic solution $P^\lambda$ as $h\rightarrow0$.
-The AP property additionally allows the convergence of $P^\lambda_h$ to the limit discrete model $P^0_h$ as $\lambda\rightarrow0$.
-To accomplish this aim, the stability restriction on $h$ must be independent of $\lambda$.
-We refer to such property as \emph{asymptotic stability}, following \cite{degond_2011}.
-Furthermore, the discrete macroscopic model $P^0_h$ must again converge to the macroscopic model $P^0$ as $h\rightarrow0$.
-Such property is termed \emph{asymptotic consistency}.
-In other words, a discrete model (scheme) $P^\lambda_h$ is AP if it satisfies the commuting diagram Fig.\ref{fig:illustration_ap}.
-To make it intuitive, AP schemes preserve the asymptotic limits from the microscopic to the macroscopic models, \emph{at the discrete level} \citep{jin_2010}.
-
-  \begin{figure}
-     \centering
-     \begin{tikzpicture}
-     \node (nw) {\Large $P^\lambda_h$};
-     \node (ne) [right=3cm of nw]{\Large $P^\lambda$};
-     \node (sw) [below=of nw]{\Large $P^0_h$};
-     \node (se) [right=3cm of sw]{\Large $P^0$};
-     \draw[->] (nw.east)  -- node [above,midway] {$h\rightarrow0$} (ne.west) ;
-     \draw[->] (nw.east)  --  (ne.west) ;
-     \draw[->] (nw.south) -- node [left,midway] {$\lambda\rightarrow0$} (sw.north);
-     \draw[->] (nw.south) -- node {} (sw.north);
-     \draw[->] (sw.east)  -- node [above,midway] {$h\rightarrow0$}(se.west);
-     \draw[->] (ne.south) -- node [left,midway] {$\lambda\rightarrow0$} (se.north);
-     \end{tikzpicture}
-     \caption{Illustration of AP schemes}
-     \label{fig:illustration_ap}
- \end{figure}
-
- We present the definition in a formal way: 
- \begin{definition} \label{def:ap}
- Consider the microscopic model $P^\lambda$ depending on an asymptotic parameter $\lambda$, and assume the macroscopic model $P^0$ exists as the asymptotic limit as $\lambda \rightarrow 0$.
-The discrete model $P^\lambda_h$, depending both on $\lambda$ and $h$, is \emph{asymptotic-preserving} if
- \begin{itemize}
-     \item $P^\lambda_h$ converges to $P^\lambda$ as $h\rightarrow0$ with stability conditions independent of $\lambda$ \emph{(asymptotic stability)};
-     \item the asymptotic limit model $P^0_h$ is consistent with $P^0$ \emph{(asymptotic consistency)}.
- \end{itemize}
- \end{definition}
- Looking back again to the model (\ref{equ:toy-model}), one can easily verify that the implicit Euler
- \begin{equation*}
-     \lambda\frac{u^{n+1}-u^{n}}{\delta} + u^{n+1} = 0
- \end{equation*}
- is AP.
-
- Extra properties are also desirable in some cases.
-In kinetic models with relaxations \citep{jin_2010}, for example, the scheme that can drive \emph{any} initial data into the local equilibrium \emph{in one step} is referred to as \emph{strongly AP}.
-Instead, if the local equilibrium is reached after long enough, it is referred to as \emph{relaxed AP}.
-If the initial data is well-prepared and the equilibrium remains for good, it is \emph{weakly AP}.
-Yet in this thesis, we are only concerned about the essential part of AP property that is specified in Definition \ref{def:ap}.
-
- Note that the existence of a macroscopic model $P^0$ as the asymptotic limit of microscopic model $P^\lambda$ is presumed.
-Rigorous proofs of some cases are available, for instance, in \cite{friedman_1968} for general linear PDEs, \cite{klainerman_1981} for the incompressible limit of the Euler equations, \cite{chen_1994, natalini_1996} for conservation laws with stiff relaxation term; \cite{remi_2014} for quasi-neutrality limit in the Euler-Maxwell system.
-This topic is beyond the scope of this thesis and we just take for granted the existence of such limit models.
-
- The concept of AP schemes can be traced back to \cite{jin_1995} in which the authors approximate a conservation law by a hyperbolic system with relaxation, and manage to construct a scheme that is stable for an arbitrarily small relaxation parameter.
-The term ``asymptotic-preserving" was formally introduced in \cite{jin_1999} for handling the diffusive regime of kinetic models.
-This concept stemmed from and remains very active in kinetic models with stiff relaxations, see \cite{jin_2010} and the references therein.
-Nonetheless, considerable effort has been put into developing AP schemes for many other problems that admit asymptotic behavior.
-For instance, in fluid dynamics, the so-called \emph{all-speed} schemes are advantageous when dealing with both compressible and incompressible regimes simultaneously.
-\cite{degond_2007, haack_2010} devise all-speed schemes for the isentropic Euler equations through fast-slow decomposition of velocity fields.
-Concerning plasma physics, a number of papers are available dealing with the quasi-neutral limit of the Euler-Poisson (or Euler-Maxwell) system \citep{crispel_2005, degond_2008, degond_2011, degond_2012} and Vlasov-Poisson (or Vlasov-Maxwell) system \citep{degond_2017, degond2017b, zhu_2017}.
-Besides, \cite{caflisch_1997, berthon2011} concern AP schemes for generic hyperbolic systems with relaxation source terms.
-For a comprehensive review on AP schemes, readers are referred to \cite{jin_2010} for kinetic and hyperbolic equations, and \cite{degond_2017} for multiscale plasma simulations.
-
- To devise an AP scheme, one mostly has to consider which terms need to be evaluated implicitly to meet the requirements of the AP property \citep{degond_2011} since stronger stability is usually achieved through implicit treatment in time discretization.
-We want to stress that unconditionally-stable (with respect to $\lambda$) schemes are not necessarily AP \citep{degond_2011,caflisch_1997}\footnote{It means the asymptotic stability does not necessarily lead to asymptotic consistency as is defined in definition \ref{def:ap}.}.
-Furthermore, a fully-implicit scheme is very likely to possess AP property, but the computational difficulties arising from solving massive linear or possibly nonlinear equations is potentially a huge cost.
-As is summarized by \cite{degond_2017}, AP schemes aim to bridge several sets of equations describing the system in different regimes, rather than to alleviate the stability constraints of the numerical methods.
-In this sense, a fully-implicit scheme is likely to be overkill.
-We want to achieve the AP property without incurring too much extra cost, which necessitates a smart construction.
-
- A general methodology for devising AP schemes is suggested by \cite{degond_2012, degond_2017}.
-They summarize it into two steps.
-The first step is a ``reformulation" step, where an equivalent form $R^\lambda$ of $P^\lambda$ is to be found such that the $R^\lambda$ explicitly appears as a perturbation of $P^0$.
-Afterward, one discretizes $P^\lambda$ by a scheme $P^\lambda_h$ with a certain amount of implicitness in such a way that the reformulation procedure can be performed at the discrete level, and leads to a reformulated discrete model $R^\lambda_h$ that is consistent to $R^\lambda$.
-However, this procedure is somehow heuristic, and its applicability to other perturbation problems remains questionable.
-It is also infeasible to rigorously prove the AP property for a given scheme, which is largely owing to the fuzzy notations of ``convergence" of numerical schemes.
-Even the linearized stability, as a necessary condition, is difficult to analyze in a multi-dimensional framework.
-Therefore, for the time being, we can state the AP property and devise the AP scheme merely in a heuristic way, and mostly has to resort to numerical experiments for verification.
-
- To summarize, the advantage of AP schemes over classical ones is twofold: for problems involving different regimes, the macroscopic regime ($\lambda \ll 1$) does not suffer from the strict stability requirement whereas the microscopic regime ($\lambda \sim \mathcal{O}(1)$) can be resolved as usual; the scale of interest, namely the resolution that we desire, is free to choose regardless of the value of the asymptotic parameter that represents the scale of the system.
-
-\chapter{Discussion on Asymptotic-preserving Property}
-
-On portraying the AP property through the commuting diagram Fig.
-\ref{fig:illustration_ap} and Definition \ref{def:ap}, we convey the principle of how an AP scheme is supposed to behave.
-Yet these illustrations are somehow given in general terms and lack precise statements.
-Another concern lies in the potential entanglement between the two requirements of AP schemes, namely asymptotic stability and asymptotic consistency Since these two statements are very strong, decomposing them into weaker ones is likely to help identify essential components to yield AP property.
-Due to the shortage of theoretical analysis on AP schemes, we humbly make some attempts here.
-
-In this chapter, the AP property, as well as the related arguments, are rephrased in a relatively rigorous way.
-Specifically, we want to explore the connection of the four asymptotic relations depicted in the commuting diagram Fig.
-\ref{fig:illustration_ap}, relying on which we try to present an argument about a set of sufficient conditions that lead to an AP scheme.
-
-Based on the formulation the commuting diagram Fig. \ref{fig:illustration_ap}, we rephrase the AP property by a uniform convergence statement: a discrete model $P^\lambda_h$ is AP if and only if
-\begin{equation} \label{arg:ap}
-    \exists C, k > 0,\ \ \  \|P^\lambda_h - P^\lambda\| \leq Ch^k,\ \ \ \forall \lambda \in [0,1]  
-\end{equation}
-where $\|\cdot\|$ represents some suitable norm.
-We repeat the definitions: the asymptotic parameter $\lambda$; the discretization parameter $h$, e.g., time step size and cell size; the (solution of) discrete model $P^\lambda_h$; the (solution of)  continuous model $P^\lambda$.
-This amounts to stating a scheme that converges to the analytical solution uniformly well for arbitrary $\lambda$ and especially for the macroscopic model $P^0$, which is nothing but the philosophy of AP schemes.
-
-Next, we present an argument that relates the convergence relationships in the commuting diagram with the above uniform convergence statement.
-\begin{proposition} \label{prop:1}
-Assume $P^0_h$ is well-defined. If the following conditions are satisfied
-\begin{itemize}
-    \item[$(*)$] $P^\lambda_h \xrightarrow[]{h\rightarrow0}P^\lambda$ in the sense that $\exists \alpha, \Tilde{\alpha}, C_1$ being constant independent of $h, \lambda$ such that
-    \begin{equation*}
-        \|P^\lambda_h - P^\lambda\| \leq C_1\frac{h^\alpha}{\lambda^{\Tilde{\alpha}}},\ \ \ \forall \lambda \in (0,1],
-    \end{equation*}
-    \item[$(**)$] $P^\lambda_h \xrightarrow[]{\lambda\rightarrow0} P^0_h$ in the sense that $\exists \beta, C_2$ being constant independent of $h, \lambda$ such that
-    \begin{equation*}
-        \|P^\lambda_h - P^0_h\| \leq C_2\lambda^\beta,\ \ \ \forall h > 0,
-    \end{equation*}
-    \item[$(\$)$] $P^\lambda \xrightarrow[]{\lambda\rightarrow0}P^0$ in the sense that $\exists C_3, \gamma$ being constant independent of $h, \lambda$ such that
-    \begin{equation*}
-        \| P^\lambda - P^0\| \leq C_3\lambda^\gamma, \ \ \ \forall \lambda \in [0,1],
-    \end{equation*}
-\end{itemize}
-Then we have $P^\lambda_h \xrightarrow[]{h\rightarrow0} P^\lambda$ uniformly on $\lambda$, namely argument (\ref{arg:ap}).
-\end{proposition}
-\begin{proof}
-Let $\epsilon$ be a constant satisfying $\alpha - \epsilon > 0$. For any $\lambda \in [0,1]$, we have the following two situations.
-
-If $\lambda^{\Tilde{\alpha}} < h^{\alpha - \epsilon}$, we pick $\Tilde{\lambda} = h^\frac{\alpha - \epsilon}{\Tilde{\alpha}}$, and we have
-\begin{align*}
-    \|P^\lambda_h - P^\lambda\| &\leq \|P^\lambda_h - P^{\Tilde{\lambda}}_h\| + \|P^{\Tilde{\lambda}}_h - P^{\Tilde{\lambda}}\| + \|P^{\Tilde{\lambda}} - P^\lambda\| \\
-    & \leq C_2(\lambda^\beta + \Tilde{\lambda}^\beta) + C_1\frac{h^\alpha}{{\Tilde{\lambda}}^{\Tilde{\alpha}}} + C_3(\Tilde{\lambda}^\gamma + \lambda^\gamma) \\
-    & \leq 2C_2h^{\frac{\alpha - \epsilon}{\Tilde{\alpha}}\beta} + C_1h^\epsilon + 2C_3 h^{\frac{\alpha - \epsilon}{\Tilde{\alpha}}\gamma} \\
-    & \leq 5\text{max}\{C_1,C_2,C_3\}h^{\text{min}\{\frac{\alpha - \epsilon}{\Tilde{\alpha}}\beta, \epsilon, \frac{\alpha - \epsilon}{\Tilde{\alpha}}\gamma\}}.
-\end{align*}
-The triangle inequality is applied to the first and second inequalities.
-
-If $\lambda^{\Tilde{\alpha}} \geq h^{\alpha - \epsilon}$, we can directly apply condition $(*)$, which results in
-\begin{align*}
-    \|P^\lambda_h - P^\lambda\| \leq C_1\frac{h^\alpha}{\lambda^{\Tilde{\alpha}}} \leq C_1h^\epsilon.
-\end{align*}
-Combine these two situations, and we can conclude.
-\end{proof}
-Condition $(*)$ amounts to saying that the scheme converges to the right solution only when the discretization parameter $h$ resolves $\lambda$ in some way.
-Otherwise, the scheme diverges.
-This should be easily met by any classical scheme which is not necessarily AP.
-The asymptotic stability is enforced in Condition $(**)$ which implies that for a fixed $h$, no $\lambda$ should incur instability.
-Being the underlying assumption, the convergence of the microscopic model to the macroscopic model, as is depicted by Condition $(\$)$, is always taken for granted throughout the thesis.
-Therefore, Condition $(*)$ and $(\$)$ are usually satisfied by a suitable problem and a classical scheme.
-Proposition \ref{prop:1} hence provides some guidance on how to design an AP scheme, that is, to incorporate Condition $(**)$ into the scheme.
-
-In the sequel, we consider a single-step scheme in the form $u_{\lambda,h}^{m+1} = \Phi_{\lambda,h}^m u_{\lambda,h}^{m}$, where $\Phi_{\lambda,h}^m$ is the discrete evolving operator, and $u_{\lambda,h}^{m}$ is the numerical solution at $m$-th time step.
-Instead of directly arguing the convergence of solutions, as Proposition \ref{prop:1}, starting from such a scheme allows us to have finer control of their properties, especially the stability and consistency.
-The conclusion based on the scheme is more revealing in understanding AP properties and more instructive in the construction of AP schemes.
-
-\begin{proposition}{\emph{(A sufficient argument for AP schemes)}} \label{prop:2}
-
-Consider a suitable norm $\|\cdot\|$ and a normed space $\mathcal{V}$ as the solution space.
-For a singular perturbation problem $P^\lambda$, assume Condition $(\$)$ in Proposition \ref{prop:1} is satisfied, and the solutions are uniformly bounded, that is, $\|\Tilde{u}_\lambda\| \leq C_u,\ \forall \lambda \in [0,1].$
-For a single-step scheme $u_{\lambda,h}^{m+1} = \Phi_{\lambda,h}^m u_{\lambda,h}^{m}$, assume $\Phi_{0,h}^m$ is well-defined.
-We denote the exact solution by $\Tilde{u}_{\lambda,h}^m$.
-If the scheme satisfies the following conditions
-\begin{itemize}
-    \item[\emph{(AS)}]  $\Phi_{\lambda,h}(\cdot)$ is $(1+hC_\Phi)$-Lipschitz $\forall\lambda\in[0,1]$  where the constant $C_\Phi$ does not depend on $\lambda, h, m$;
-
-    \item[\emph{(C)}] the non-limit scheme is \emph{consistent} in the sense that 
-    \begin{equation*}
-        \| \Tilde{u}^{m+1}_{\lambda,h} - \Phi_{\lambda,h}^m\Tilde{u}^{m}_{\lambda,h}\| \leq C_c\frac{h^2}{\lambda}, \ \ \ \forall \lambda \in (0,1],
-    \end{equation*}
-    where the constant $C_c$ does not depend on $\lambda, h, m$;
-
-    \item[\emph{(AC)}] the limiting scheme is \emph{consistent} in the sense that 
-    \begin{equation*}
-        \| \Tilde{u}^{m+1}_{0,h} - \Phi_{0,h}^m\Tilde{u}^{m}_{0,h}\| \leq \Tilde{C_c}h^2, 
-    \end{equation*}
-    where the constant $\Tilde{C_c}$ does not depend on $h, m$;
-
-    \item[\emph{(L)}] $\Phi_{\lambda,h}^m$ is Lipschitz with respect to $\lambda$ in the sense that
-    \begin{equation*}
-        \| (\Phi_{\lambda,h}^m - \Phi_{0,h}^m)u \| \leq \Tilde{C}_\Phi\|u\|h\lambda,\ \ \ \forall u \in \mathcal{V}, 
-    \end{equation*}
-    where the constant $\Tilde{C}_\Phi$ does not depend on $h$,
-\end{itemize}
-then the scheme is AP in the sense of (\ref{arg:ap}).
-\end{proposition}
-\begin{proof}[Proof]
-Providing Proposition \ref{prop:1}, it suffices to check Condition $(*)$ and $(\$)$.
-
-For $\lambda > 0$, define the error $e^{m}_{\lambda,h} := \Tilde{u}_{\lambda,h}^{m} - u_{\lambda,h}^{m}$, and we have 
-\begin{align*}
-    e^{m+1}_{\lambda,h} = \Tilde{u}_{\lambda,h}^{m+1} - \Phi^m_{\lambda,h} \Tilde{u}_{\lambda,h}^{m} + \Phi^m_{\lambda,h} \Tilde{u}_{\lambda,h}^{m} - \Phi^m_{\lambda,h}u_{\lambda,h}^{m}.
-\end{align*}
-By triangle inequality,
-\begin{align*}
-    \|e^{m+1}_{\lambda,h}\| \leq \|\Tilde{u}_{\lambda,h}^{m+1} - \Phi^m_{\lambda,h} \Tilde{u}_{\lambda,h}^{m}\| + \|\Phi^m_{\lambda,h} \Tilde{u}_{\lambda,h}^{m} - \Phi^m_{\lambda,h}u_{\lambda,h}^{m}\|
-\end{align*}
-By (AS) and (C), 
-\begin{align*}
-    \|e^{m+1}_{\lambda,h}\| \leq (1+hC_\Phi)\|e^m_{\lambda,h}\|+ C_c\frac{h^2}{\lambda},
-\end{align*}
-and thus by induction,
-\begin{align*}
-    \|e^{m+1}_{\lambda,h}\| \leq (1+hC_\Phi)^{m+1}\|e^0_{\lambda,h}\| + \sum_{i=0}^{m}(1+hC_\Phi)^iC_c\frac{h^2}{\lambda}.
-\end{align*}
-Since it is reasonable to take $\|e^0_{\lambda,h}\|=0$ and
-\begin{align*}
-    \sum_{i=0}^{m}(1+hC_\Phi)^i = \frac{(1+hC_\Phi)^{m+1} - 1}{hC_\Phi} = \frac{(1+hC_\Phi)^{T/h} - 1}{hC_\Phi} \leq \frac{e^{C_\Phi T}-1}{hC_\Phi}, 
-\end{align*}
-we obtain
-\begin{align*}
-    \|e^{m+1}_{\lambda,h}\| \leq \frac{e^{C_\Phi T}-1}{C_\Phi}C_c\frac{h}{\lambda}, 
-\end{align*}
-namely Condition $(*)$ in Proposition \ref{prop:1}.
-By the same procedure and Condition (AC), we can draw the similar conclusion for the case $\lambda = 0$,
-\begin{align}\label{equ:prop2-arg1}
-    \|e^{m+1}_{0,h}\| \leq \frac{e^{C_\Phi T}-1}{C_\Phi}\Tilde{C}_ch, 
-\end{align}
-
-Secondly, we want to prove (\$) in Proposition \ref{prop:1}. Set $\lambda = 0$ in the scheme,
-\begin{align*}
-    u_{0,h}^{m+1} = \Phi^m_{0,h} u_{0,h}^{m}.
-\end{align*}
-Define $\varepsilon^{m}_{\lambda,h} := u_{\lambda,h}^{m} - u_{0,h}^{m}$, and we have
-\begin{align*}
-    \varepsilon^{m+1}_{\lambda,h} = \Phi^m_{\lambda,h} u_{\lambda,h}^{m} - \Phi^m_{0,h} u_{0,h}^{m}.
-\end{align*}
-By triangle inequality,
-\begin{align*}
-    \|\varepsilon^{m+1}_{\lambda,h}\| \leq \|\Phi^m_{\lambda,h} u_{\lambda,h}^{m} - \Phi^m_{\lambda,h} u_{0,h}^{m}\| + \|\Phi^m_{\lambda,h} u_{0,h}^{m} - \Phi^m_{0,h} u_{0,h}^{m}\|.
-\end{align*}
-By (AS) and (L),
-\begin{align*}
-    \|\varepsilon^{m+1}_{\lambda,h}\| \leq (1+hC_\Phi)\|\varepsilon^{m}_{\lambda,h}\| + \Tilde{C}_{\Phi}\|u_{0,h}^{m}\|h\lambda.
-\end{align*}
-From the definition $u_{0,h}^{m} = \Tilde{u}_{0,h}^{m} - e_{0,h}^{m}$, we deduce by (\ref{equ:prop2-arg1}) and boundedness on solutions that
-\begin{align} \label{equ:prop2-arg2}
-    \|\varepsilon^{m+1}_{\lambda,h}\| \leq (1+hC_\Phi)\|\varepsilon^{m}_{\lambda,h}\| + \Tilde{C}_{\Phi}\left[C_u + \frac{e^{C_\Phi T}-1}{C_\Phi}C_ch\right]h\lambda.
-\end{align}
-By induction as before, we end up getting
-\begin{align*}
-    \|\varepsilon^{m+1}_{\lambda,h}\| \leq \frac{e^{C_\Phi T}-1}{C_\Phi}\left[C_u + \frac{e^{C_\Phi T}-1}{C_\Phi}C_ch\right]\Tilde{C}_{\Phi}\lambda,
-\end{align*}
-Since we are concerned with the behavior of $h\rightarrow0$, one can assume $h < 1$ without loss of generality.
-
-On yielding (\ref{equ:prop2-arg1}) and (\ref{equ:prop2-arg2}), we can conclude by Proposition \ref{prop:1}.
-\end{proof}
-
-One can interpret Proposition \ref{prop:2} in this way: for a scheme that is already stable and consistent pointwise with respect to $\lambda > 0$, by requiring the asymptotic stability (AS), consistency in the limiting case (AS), as well as Condition (L), can one attain AP property.
-We would like to stress that Condition (AS) is weaker than the asymptotic consistency in Definition \ref{def:ap} which states the convergence of the limiting model.
-In exchange, we have to additionally enforce (L).
-
-To summarize, we try to dig in and present some concrete statements for the sake of unveiling the essential qualifications for an AP scheme.
-Proposition \ref{prop:1} serves to concretize the commuting diagram Fig.
-\ref{fig:illustration_ap}, and illuminates how these converging relations result in AP property.
-Further specification is manifested in Proposition \ref{prop:2} which proposes a sufficient condition and tries to give some definite clues about the properties worth paying attention to construct an AP scheme.
-\chapter{Discretization of the Euler-Maxwell System} \label{chap:discretization_euler_maxwell}
-Throughout the thesis, we are dealing with the numerical treatment of the \emph{Euler-Maxwell} system as a fluid description of multi-species plasmas.
-Hence, before specifying the schemes, we would like to give a preliminary introduction to the discretization of this system.
-This chapter is organized as follows: first, the governing equations of the Euler-Maxwell system are presented.
-In the sequel, two discretization framework, Finite Volume Method (FVM) and Finite Integration Technique (FIT), are briefly introduced, serving to discretize the Euler system and the Maxwell system respectively.
-Lastly, we discuss the interpolation of electromagnetic fields, which is dispensable in coupling the two subsystems.
-
-\section{Governing equations for multi-species plasma modeling}
-In plasma modeling, the system is composed of two subsystems.
-One governs the behavior of electric and magnetic fields while the other rules the motions of gas particles.
-We refer to the former one as \emph{Maxwell system} and the latter one as \emph{Euler system} under the framework of the fluid plasma model.
-
-The Maxwell system is described by Maxwell's equations whose expression in SI units read
-\begin{align}
-    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday} \\ 
-    \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= -\mathbf{J}, \label{equ:maxwell_ampere} \\
-    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B}\\
-    \nabla \cdot \mathbf{D} &= \rho, \label{equ:maxwell_gauss_D}
-\end{align}
-where the involved quantities are magnetic flux density $\mathbf{B}$, electric field intensity $\mathbf{E}$, electric induction $\mathbf{D}$, magnetic field intensity $\mathbf{H}$, electric current density $\mathbf{J}$ and electric charge density $\rho$.
-These equations are known as Faraday's law (\ref{equ:maxwell_faraday}), Amp\`{e}re's law (\ref{equ:maxwell_ampere}), Gauss's law for magnetism (\ref{equ:maxwell_gauss_B}) and Gauss's law for electric field (\ref{equ:maxwell_gauss_D}).
-For simplicity, we only consider isotropic and homogeneous mediums in vacuum.
-The quantities are thus related by the linear constitutive relations
-\begin{equation*}
-    \mathbf{D} = \varepsilon_0 \mathbf{E}, \ \ \ \mathbf{B} = \mu_0\mathbf{H}, 
-\end{equation*}
-where $\varepsilon_0$ and $\mu_0$ are the vacuum permittivity and permeability of the medium.
-By definition of the electric current density $\mathbf{J}$ and electric charge density $\rho$, they are supposed to satisfy the continuity equation
-\begin{equation} \label{equ:charge_continuity}
-    \partial_t\rho + \nabla \cdot \mathbf{J} = 0.
-\end{equation}
-Besides, on taking the divergence of equations (\ref{equ:maxwell_faraday}) and (\ref{equ:maxwell_ampere}) together with the relation (\ref{equ:charge_continuity}), it is possible to verify that Gauss's laws (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) are consequences of (\ref{equ:maxwell_faraday}) and (\ref{equ:maxwell_ampere}) provided that (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) are satisfied at the initial time.
-In other words, Gauss's laws (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) are redundant, and Faraday's law (\ref{equ:maxwell_faraday}) and Amp\`{e}re's law (\ref{equ:maxwell_ampere}) suffice.
-
-In the Euler system, the motions of gas particles are accounted for through the \emph{Euler equations}.
-Specifically, we equip each species with one set of (compressible) Euler equations, taking into account the effect of electromagnetic fields as well as other processes like collisions and recombination.
-The generic expressions read
-\begin{align} \label{equ:euler_}
-    \partial_t
-    \begin{bmatrix}
-    n_* \\
-    m_*n_* \mathbf{u}_* \\
-    m_*n_* e_*
-    \end{bmatrix}
-    + \nabla \cdot
-    \begin{bmatrix}
-    n_* \mathbf{u}_* \\
-    m_*n_* \mathbf{u}_* \otimes \mathbf{u}_* + p_*\mathbb{I} \\
-    m_*n_* h_* \mathbf{u}_*
-    \end{bmatrix}
-    =
-    \begin{bmatrix}
-    0 \\
-    q_*n_*(\mathbf{E} + \mathbf{u}_* \times \mathbf{B}) \\
-    \mathbf{J}_* \cdot \mathbf{E}
-    \end{bmatrix}
-    +
-    \begin{bmatrix}
-    \Gamma_* \\
-    \mathbf{R}_* \\
-    Q_*
-    \end{bmatrix}.
-\end{align}
-The subscript $*$ represents the indices for different species, and by convention we assign $* = e$ to electrons, $* = i$ to ions, and $* = n$ to neutral atoms.
-The involved fluid quantities are: number density $n_*$, particle mass $m_*$,  charge number $q_*$, velocity $\mathbf{u}_*$, pressure $p_*$, specific total energy $e_* := \frac{1}{2}|\mathbf{u}_*|^2 + \frac{p_*}{m_*n_*(\gamma - 1)}$, specific total enthalpy $h_* := e_* + \frac{p_*}{m_*n_*}$ and current density $\mathbf{J}_* := q_*n_*\mathbf{u}_*$.
-All the species are assumed ideal gases with heat capacity ratio $\gamma=5/3$ for monatomic gases.
-The left-hand side of the equations describes the convection of plasma fluids.
-The first term at the right-hand side denotes Lorentz force in the momentum equation and Joule heating in the energy equation.
-$\Gamma_*, \mathbf{R}_*, Q_*$ are generic terms that include effects of inter-species collision, ionization, recombination, etc.
-The three equations respectively describes how the mass, momentum and energy of plasma fluids change over time.
-
-It should be noted that by such a fluid model several assumptions are implicitly presumed.
-The intra-species collision rate is assumed to be high and isotropic so that the thermal equilibrium holds all the time, and one temperature is sufficient to characterize the thermal energy, which also explains the isotropic pressure.
-Actually, in some cases, a plasma species can exhibit two temperatures in different directions because of anisotropic thermal motions \citep{chen2016}.
-Additionally, the viscosity of plasma fluids, which gives rise to the off-diagonal elements of the stress tensor, is neglected in the Euler equations.
-
-Combination of the two sets of equations (\ref{equ:maxwell_faraday}) to (\ref{equ:maxwell_gauss_D}) and (\ref{equ:euler_}) leads to the governing equations for a multi-species plasma model.
-The coupling of the two subsystems takes effect through the following relations that connect the fluid and electromagnetic quantities
-\begin{equation*}
-    \rho = \sum_* q_*n_*, \ \ \  \mathbf{J} = \sum_* q_*n_*\mathbf{u}_*. 
-\end{equation*}
-\subsection{Collision term}
-The collisions within each species are accounted for by the pressure term which results from the Maxwellian assumption on the velocity distribution, while the intra-species collisions have to be included through source terms.
-If we consider a fully-ionized plasma that is composed of ions (with charge number $Z$) and electrons, their collisions are mostly \emph{Coulomb collision} \citep[][sec.
-5.6.2]{chen2016}.
-That is, different from the billiard-ball collision, an electron already feels a force from a distance when it approaches an ion and is deflected gradually.
-Such collisions are modeled by friction terms as follows, and we simply present the expressions without derivation (see \citep[][sec.
-5.6.2]{chen2016}):
-\begin{equation} \label{equ:collision}
-    \mathbf{R}_{e}^{\text{coll}} = \frac{\pi Ze^4m_e^{1/2}}{(4\pi\varepsilon_0)^2(k_BT_e)^{3/2}}\text{ln}\Lambda n_en_i(\mathbf{u}_i - \mathbf{u}_e) = - \mathbf{R}_{i}^{\text{coll}},  
-\end{equation}
-which models the collision force that is applied on the electrons.
-ln$\Lambda$ is called the \emph{Coulomb logarithm}, which typically takes a numerical value of order 10–20 .
-Because of the conservation of momentum, the collision term experienced by ions $\mathbf{R}_{i}^{\text{coll}}$ is just the negative of $\mathbf{R}_{e}^{\text{coll}}$.
-
-\section{Spatial discretization of Euler system: Finite Volume Method}
-We employ the finite volume method (FVM) to discretize the Euler system.
-As a classical framework for solving conservation laws and hyperbolic systems, FVM is derived from the integral form of the equations in each cell.
-It is the cell average of quantities that evolves at each time step, based on the \emph{numerical flux} through the cell boundary.
-The construction of the numerical flux, which serves to approximate the real flux, is the essence of constructing an FVM scheme.
-Due to the convection nature of fluid dynamics, the numerical fluxes are supposed to respect the convection direction, namely, the \emph{upwind scheme} is preferable.
-To this end, people resort to the approximated solution of \emph{Riemann problems}.
-The method is briefly illustrated in the following.
-For detailed information, see the textbook \cite{leveque_2002}.
-
-The Euler equations (\ref{equ:euler_}) can be generalized into the form of conservation law with source terms:
-\begin{equation} \label{equ:euler_conservation}
-    \partial_t \mathbf{U} + \nabla \cdot \mathbf{F}(\mathbf{U}) = \mathbf{RHS},
-\end{equation}
-where $\mathbf{U}$ stands for the conservative variable, $\mathbf{F}(\mathbf{U})$ is the flux density, and $\mathbf{RHS}$ is the source term.
-
-To obtain the semi-discretization, we first integrate (\ref{equ:euler_conservation}) over a cell $V_i$ 
-\begin{equation} \label{equ:euler_grid} 
-    \partial_t \overline{\mathbf{U}}_i + \frac{1}{|V_i|}\sum_{j:A_j\in\partial V_i} |A_j|\underbrace{\frac{1}{|A_j|}\iint_{A_j}\mathbf{F}(\mathbf{U})\cdot \mathbf{n}_j \text{d}A}_{\overline{\mathbf{F}}_j} = \underbrace{\frac{1}{|V_i|}\iiint_{V_i} \mathbf{RHS} \text{d}V}_{\overline{\mathbf{RHS}}_i}
-\end{equation}
-where $\overline{\mathbf{U}}_i := \iiint_{V_i} \mathbf{U} \text{d}V / |V_i|$ calculates the cell average, $\mathbf{n}_j$ is the outer normal vector of face $A_j$ with respect to the cell $V_i$.
-We approximate the analytic flux $\overline{\mathbf{F}}_j$ in (\ref{equ:euler_grid}) by the numerical flux $\overline{\mathbf{F}}\left(\overline{\mathbf{U}}_i, \overline{\mathbf{U}}_{k(i,j)}, \mathbf{n}_j\right)$, where $k(i,j)$ returns the index of the adjacent cell that shares $A_j$ with cell $V_i$.
-Classical numerical fluxes include Lax-Friedrich flux, Rusanov flux, Engquist-Osher flux, see \cite[][p.
-44-46]{mishra_2019}.
-Finally, we end up with the semi-discretized equation:
-\begin{equation*}
-    \partial_t \overline{\mathbf{U}}_i + \frac{1}{|V_i|}\sum_{j:A_j\in\partial V_i} |A_j| \overline{\mathbf{F}}\left(\overline{\mathbf{U}}_i, \overline{\mathbf{U}}_{k(i,j)}, \mathbf{n}_j\right) = \overline{\mathbf{RHS}}_i.
-\end{equation*}
-The Rusanov flux in multi-dimensions on face $A_j$ reads\footnote{See Appendix \ref{app:flux} for detailed derivation.}
-\begin{equation} \label{equ:rusanov-flux-3d}
-    \overline{\mathbf{F}}\left(\overline{\mathbf{U}}_L, \overline{\mathbf{U}}_R, \mathbf{n}\right) = \frac{1}{2}\left[\mathbf{F}(\overline{\mathbf{U}}_L)\cdot\mathbf{n} + \mathbf{F}(\overline{\mathbf{U}}_R)\cdot\mathbf{n}\right] - \frac{1}{2}\overline{s}\left(\overline{\mathbf{U}}_R - \overline{\mathbf{U}}_L\right),
-\end{equation}
-where $\overline{s} = \text{max}(s(\overline{\mathbf{U}}_L), s(\overline{\mathbf{U}}_R))$ with $s(\mathbf{U}) := |\mathbf{u}\cdot\mathbf{n}| + \sqrt{\gamma p/\rho}$ representing the largest wave speed.
-
-\section{Spatial discretization of Maxwell system: Finite Integration Technique}
-The Finite Integration Technique (FIT), originally proposed by \cite{weiland_1977}, is adopted as the discretized model for the Maxwell system in our work.
-Just like FVM, FIT starts from the integral form of Maxwell's equations \emph{on a mesh doublet} and yields the so-called \emph{Maxwell's Grid Equations}.
-The quantities to be evolved are global quantities like the electric voltage assigned to a line and the magnetic flux assigned to a surface, rather than the local quantities like a component-wise electric field.
-
-The FIT can be treated as a generalization of Yee's method \citep{yee_1966}, which is also known as Finite-Difference Time-Domain (FDTD).
-The FDTD method, in its standard formulation, is based on structured Cartesian grids, discretizing Maxwell's equations in a finite-difference manner.
-Coupled with the leap-frog time scheme, the FDTD method does not need to invoke an iterative solver at each time-step like the Finite Element Method (FEM), which makes it computationally efficient and easy-to-implement approach for solving a wide range of time-domain electromagnetic problems.
-The explicit time-domain FIT on Cartesian grids is computationally equivalent to the FDTD method.
-Inheriting the advantages of the FDTD method, FIT is furthermore able to handle complex geometry with unstructured mesh, and, thanks to the absence of approximation error in deriving the Maxwell's Grid Equations, provides powerful tools for the analysis of consistency, stability, and other issues \citep{weiland_2003}.
-Although originally developed for electromagnetism, FIT is also applicable in other types of wave-field problems, like acoustic and elastodynamic waves, as is summarized in \cite{marklein_2002}.
-
-\subsection{Mesh duality} \label{sec:mesh_duality}
-
-A mesh doublet $(\mathcal{M}, \Tilde{\mathcal{M}})$ is required for the formulation of FIT in the need of incorporating the material laws.
-The spatial domain is discretized by two meshes that interlace with each other.
-They are called \emph{primal} mesh $\mathcal{M}$ and \emph{dual} mesh $\Tilde{\mathcal{M}}$.
-The essential duality property requires that \emph{each edge of one mesh penetrates a face of the other mesh and that each vertex of one mesh lies at the center of a cell of the other mesh} \citep{weiland_2003}.
-We demonstrate such interlacing character by an example in Fig.
-\ref{fig:illustration_primal_dual}, where the primal mesh is composed of triangular prisms and the dual mesh is composed of hexagon prisms.
-The dual mesh can be generated as the Voronoi decomposition of the primal mesh \citep{fuchs_2021}.
-Compared to the constraint of FDTD to Cartesian meshes, FIT is compatible with a wide range of mesh types.
-An example of primal and dual meshes is given in Fig.
-\ref{fig:primal_dual_meshes}.
-
-To clarify the terminology, the \emph{vertices, edges, faces} and \emph{volumes} (denoted by $P,L,A$ and $V$ respectively) make up a mesh.
-Also, they are uniformly termed \emph{facets} with zero, one, two and three dimensions.
-
-\begin{figure}
-    \centering
-    \begin{tikzpicture}
-    \def\primalstyle{thick}
-    \def\dualstyle{thick}
-    \coordinate (P0) at (0cm, 0cm);
-    \foreach \i in {1,2,...,6}
-    {
-    \coordinate (P\i) at ({60*\i-30}:2cm);
-    \draw[\primalstyle] (P0) -- (P\i);
-    }
-    \draw[\primalstyle] (P1) -- (P2) node[left=5mm]{\Large $\mathcal{M}$} -- (P3) -- (P4) -- (P5) -- (P6) -- cycle;
-    \begin{scope}[shift={(3cm,0.5cm)}]
-        \coordinate (PP0) at (0cm, 0cm);
-        \foreach \i in {1,2,...,6}
-        {
-        \coordinate (PP\i) at ({60*\i-30}:2cm);
-        \draw[gray] (PP0) -- (PP\i);
-        }
-    \end{scope}
-
-    \draw[\primalstyle] (PP1) -- (PP2);
-    \draw[gray] (PP2) -- (PP3);
-    \draw[gray] (PP3) -- (PP4);
-    \draw[gray] (PP4) -- (PP5);
-    \draw[\primalstyle] (PP5) -- (PP6);
-    \draw[\primalstyle] (PP6) -- (PP1);
-
-    \draw[gray] (P0) -- (PP0);
-    \draw[\primalstyle] (P1) -- (PP1);
-    \draw[\primalstyle] (P2) -- (PP2);
-    \draw[gray] (P3) -- (PP3);
-    \draw[gray] (P4) -- (PP4);
-    \draw[\primalstyle] (P5) -- (PP5);
-    \draw[\primalstyle] (P6) -- (PP6);
-
-    \foreach \i in {1,2,...,6}
-    {
-    \coordinate (D\i) at ({60*\i-60}:{2./1.737});
-    }
-    \draw[dashed, blue] (D1) -- (D2) -- (D3) -- (D4) -- (D5) -- (D6) -- cycle;
-    \begin{scope}[shift={(1.5,0.25)}]
-        \foreach \i in {1,2,...,6}
-        {
-        \coordinate (DD\i) at ({60*\i-60}:{2./1.737});
-        }
-    \end{scope}
-    \draw[blue] (DD1) -- (DD2) -- (DD3) -- (DD4) -- (DD5) -- (DD6) -- cycle;
-    \draw[blue] (D1) -- (DD1);
-    \draw[blue] (D2) -- (DD2);
-    \draw[blue] (D3) -- (DD3);
-    \draw[blue] (D4) -- (DD4);
-    \draw[blue] (D5) -- (DD5);
-    \draw[blue] (D6) -- (DD6);
-
-    \begin{scope}[shift={(-1.5,-0.25)}]
-        \foreach \i in {1,2,...,6}
-        {
-        \coordinate (DDD\i) at ({60*\i-60}:{2./1.737});
-        }
-    \end{scope}
-    \draw[blue, ultra thick] (DDD1) -- (DDD2) -- (DDD3) node[left=3mm]{\textcolor{blue}{\Large $\Tilde{\mathcal{M}}$}} -- (DDD4) -- (DDD5) -- (DDD6) -- cycle;
-    \draw[blue, ultra thick] (D1) -- (DDD1);
-    \draw[blue, ultra thick] (D2) -- (DDD2);
-    \draw[blue, ultra thick] (D3) -- (DDD3);
-    \draw[blue] (D4) -- (DDD4);
-    \draw[blue] (D5) -- (DDD5);
-    \draw[blue, ultra thick] (D6) -- (DDD6);
-
-    \fill[blue!50, opacity=0.2] (D1) -- (D2) -- (D3) -- (D4) -- (D5) -- (D6);
-
-    \end{tikzpicture}
-    \caption{Illustration of primal and dual meshes.
-Six primal cells, which are triangle prisms, are depicted by black and gray edges.
-One dual cell, which is a hexagon prism, is depicted by blue edges.
-The dashed hexagon represents the intersection of the dual cell and primal cells.
-This particular type of mesh composed of prisms is picked as a demonstration since it is used in our numerical experiments.}
-    \label{fig:illustration_primal_dual}
-\end{figure}
-\subsection{Spatial semi-discretization} \label{sec:fit}
-The FIT is established based on the integral form of Maxwell's equations:
-\begin{align}
-    &\oint_{\partial A} \mathbf{E} \cdot d\mathbf{s} \ = - \iint_A \frac{\partial \mathbf{B}}{\partial t} \cdot d\mathbf{A}, \label{equ:maxwell_int_faraday}\\
-    &\oint_{\partial A} \mathbf{H} \cdot d\mathbf{s} \ = \iint_A \left(\frac{\partial \mathbf{D}}{\partial t} + \mathbf{J}\right) \cdot d\mathbf{A}, \label{equ:maxwell_int_ampere}\\
-    &\oint_{\partial V} \mathbf{B} \cdot d\mathbf{A} = 0, \label{equ:maxwell_int_gauss_B}\\
-    &\oint_{\partial V} \mathbf{D} \cdot d\mathbf{A} = \iiint_V \rho dV. \label{equ:maxwell_int_gauss_D}
-\end{align}
-where $A, V$ stand for any 2-D faces and 3-D cells in the spatial domain.
-These equations are consequence of curl theorem and divergence theorem, and correspond to the integral form of Faraday's law (\ref{equ:maxwell_int_faraday}), Ampere's law (\ref{equ:maxwell_int_ampere}) and Gauss's laws for magnetic flux (\ref{equ:maxwell_int_gauss_B}) and electric induction (\ref{equ:maxwell_int_gauss_D}).
-The fields are related by the material laws
-\begin{align} \label{equ:maxwell_material_laws}
-    \mathbf{B} = \mu_0 \mathbf{H},\ \ \ \mathbf{D} = \varepsilon_0 \mathbf{E}.
-\end{align}
-
-The discrete Maxwell system is obtained by applying and collecting the equations (\ref{equ:maxwell_int_faraday}) (\ref{equ:maxwell_int_gauss_B}) on each facet of the primal mesh $\mathcal{M}$ and the equations (\ref{equ:maxwell_int_ampere}) (\ref{equ:maxwell_int_gauss_D}) on each facet of the dual mesh $\Tilde{\mathcal{M}}$.
-We denote the vertices by $(P_i)_{i=1}^{N_P}$, $(\Tilde{P}_i)_{i=1}^{N_{\Tilde{P}}}$, edges by $(L_i)_{i=1}^{N_L}$, $(\Tilde{L}_i)_{i=1}^{N_{\Tilde{L}}}$, faces by $(A_i)_{i=1}^{N_A}$, $(\Tilde{A}_i)_{i=1}^{N_{\Tilde{A}}}$, and cells by $(V_i)_{i=1}^{N_V}$, $(\Tilde{V}_i)_{i=1}^{N_{\Tilde{V}}}$ where the ones with tilde belong to the dual mesh.
-Recall the duality property that $\mathcal{M}$ and $\mathcal{M}'$ interlaces with each other in the sense that each edge penetrates a face of the other mesh.
-This leads to $N_L = N_{\Tilde{A}}$ and $N_A = N_{\Tilde{L}}$\footnote{Note that here the influence of boundary is not considered.}.
-The equations (\ref{equ:maxwell_int_faraday}) to (\ref{equ:maxwell_int_gauss_D}) can be rewritten into
-
-\begin{align}
-    &\sum_{j:L_j\in\partial A_i} \underbrace{\int_{L_j} \mathbf{E} \cdot d\mathbf{s}}_{e_j} = - \frac{\partial}{\partial t} \underbrace{\iint_{A_i} \mathbf{B} \cdot d\mathbf{A}}_{b_i},\ \ \ i = 1,...,N_A, \label{equ:maxwell_grid_faraday} \\
-    &\sum_{j:\Tilde{L}_j\in\partial \Tilde{A}_i} \underbrace{\int_{\Tilde{L}_j} \mathbf{H} \cdot d\mathbf{s}}_{h_j} = \frac{\partial}{\partial t} \underbrace{\iint_{\Tilde{A}_i} \mathbf{D} \cdot d\mathbf{A}}_{d_i} + \underbrace{\iint_{\Tilde{A}_i} \mathbf{J} \cdot d\mathbf{A}}_{j_i}, \ \ \ i = 1,...,N_{\Tilde{A}}, \label{equ:maxwell_grid_ampere}\\
-    &\sum_{j:A_j\in \partial V_i} \iint_{A_j} \mathbf{B} \cdot d\mathbf{A} = 0,\ \ \ i = 1,..., N_V,\label{equ:maxwell_grid_gauss_B}\\
-    &\sum_{j:\Tilde{A}_j \in \partial\Tilde{V}_i}\iint_{\Tilde{A}_j} \mathbf{D} \cdot d\mathbf{A} = \underbrace{\iiint_{\Tilde{V}_i} \rho dV}_{q_i},\ \ \ i = 1,...,N_{\Tilde{V}}.
-\label{equ:maxwell_grid_gauss_D}
-\end{align}
-For the sake of neat illustration, we temporarily neglect the boundary conditions which will be discussed later.
-As is indicated in (\ref{equ:maxwell_grid_faraday})(\ref{equ:maxwell_grid_ampere}) by the underbraces, the discrete variables are chosen as the integral quantities of field vectors on edges or faces.
-Packing these scalar quantities into vectors, we define
-\begin{equation} \label{equ:fit_scale_vector}
-    \mathbf{e} := (e_i)_{i=1}^{N_L},\ \ \mathbf{b} := (b_i)_{i=1}^{N_A}, \ \ \mathbf{h} := (h_i)_{i=1}^{N_{\Tilde{L}}}, \ \ \mathbf{d} := (d_i)_{i=1}^{N_{\Tilde{A}}}, \ \ \mathbf{j} := (j_i)_{i=1}^{N_{\Tilde{A}}}, \ \ \mathbf{q} := (q_i)_{i=1}^{N_{\Tilde{V}}}.
-\end{equation}
-
-The next step is to transform the discrete Maxwell system (\ref{equ:maxwell_grid_faraday}) to (\ref{equ:maxwell_grid_gauss_D}) into a set of algebraic equations.
-One should note that the sign of each scalar depends on the orientation of the facet on which it is integrated.
-To uniquely determine the meaning of these quantities, an \emph{internal orientation} is assigned to every facet of the primal mesh $\mathcal{M}$.
-This attribute defines the orientations of edges and outer normals of faces.
-Besides, since the application of curl theorem and divergence theorem entails the orientation relations of edge-to-face and face-to-volume respectively, another orientation attribute, \emph{induced orientation}, is introduced to specify this topology.
-An induced orientation of a $k$-dim facet $f$ with respect to a $(k+1)$-dim facet $f'$ that contains $f$ is determined by the internal orientation of $f'$ according to some rule.
-An example is shown in Fig.
-\ref{fig:illustration_external_orientation}.
-These topological attributes are inherent for a mesh and can be set at will.
-
-\begin{figure}
-    \centering
-
-\begin{tikzpicture}
-\coordinate (P1) at (0,0);
-\coordinate (P2) at (2,2);
-\draw[decoration={markings, 
-    mark= at position 0.55 with {\arrow[scale=1.5]{to}}}
-    ,postaction={decorate}, very thick, blue] (P1) -- (P2);
-\node at (1,1.5) {\textcolor{blue}{$L$}};
-\draw[fill=black] (P1) circle (0.1) node[above=3mm] {$P_1$} node[below=2mm] {$(-)$};
-\draw[fill=black] (P2) circle (0.1) node[above=2mm] {$P_2$} node[below=2mm] {$(+)$};
-
-\begin{scope}[shift={(5, 0)}]
-\coordinate (Q1) at (0,0);
-\coordinate (Q2) at (2cm, -0.5cm);
-\coordinate (Q3) at (3cm, 1cm);
-\draw[decoration={markings, 
-    mark= at position 0.5 with {\arrow[scale=1]{to}}}
-    , postaction={decorate}, very thick] (Q1) -- node[below=1.5mm]{$L_1$} (Q2);
-    \draw[decoration={markings, 
-    mark= at position 0.5 with {\arrow[scale=1]{to}}}
-    , postaction={decorate}, very thick] (Q2) -- node[right,yshift=-1.5mm]{$L_2$} (Q3);
-    \draw[decoration={markings, 
-    mark= at position 0.5 with {\arrow[scale=1]{to}}}
-    , postaction={decorate}, very thick] (Q3) -- node[above,xshift=-3mm] {$L_3$}(Q1);
-
-\fill[blue, opacity=0.25] (Q1) -- (Q2) -- (Q3);
-\draw[decoration={markings, 
-    mark= at position 1 with {\arrow[scale=1.5]{to}}}
-    , postaction={decorate}, very thick, blue](barycentric cs:Q1=1,Q2=1,Q3=1) -- ([shift={(0,2cm)}] barycentric cs:Q1=1,Q2=1,Q3=1) node[right,xshift=1mm] {\textcolor{blue}{$A$}}; 
-\end{scope}
-
-\begin{scope}[shift={(12,0)}]
-\coordinate (S1) at (0,0);
-\coordinate (S2) at (-1,0.5);
-\coordinate (S3) at (1.5,1);
-\coordinate (S4) at (0.5,2.5);
-\draw[very thick, blue] (S1) -- (S2) -- (S4) -- cycle;
-\fill[gray, opacity=0.2] (S1) -- (S2) -- (S4);
-\draw[very thick, blue] (S1) -- (S3) -- (S4) -- cycle;
-\fill[gray, opacity=0.2] (S1) -- (S3) -- (S4);
-\draw[blue, thin] (S2) -- (S3);
-\draw[decoration={markings, 
-    mark= at position 1 with {\arrow[scale=1]{to}}}
-    , postaction={decorate}, very thick] (barycentric cs:S1=1,S2=1,S4=1) -- ([shift={(-1,0.5)}] barycentric cs:S1=1,S2=1,S4=1) node[above] {$A_1$};
-\coordinate (O1) at (barycentric cs:S1=1,S2=1,S3=1);
-\coordinate (O2) at ([shift={(0,-1)}] barycentric cs:S1=1,S2=1,S3=1);
-\coordinate (S)  at (intersection of O1--O2 and S1--S3);
-\draw[very thick, dotted] (O1) -- (S);
-\draw[decoration={markings, 
-    mark= at position 1 with {\arrow[scale=1]{to}}}
-    , postaction={decorate}, very thick] (S) -- (O2) node[right] {$A_2$};
-\draw[decoration={markings, 
-    mark= at position 1 with {\arrow[scale=1]{to}}}
-    , postaction={decorate}, very thick] (barycentric cs:S1=1,S3=1,S4=1) -- ([shift={(1,0.4)}] barycentric cs:S1=1,S3=1,S4=1) node[right] {$A_3$} ;
-\node at (S4) [left, xshift=-2mm] {\textcolor{blue}{$V$}};
-\end{scope}
-\end{tikzpicture}
-    \caption{Illustration of induced orientations.
-As per our rule, the ending vertex of an edge is positively oriented while the starting point is negatively oriented; the orientations of edges with respect to a face obey the right-hand rule; a face of a volume are oriented with its outer normal.
-Note that the rule can be freely set.}
-    \label{fig:illustration_external_orientation}
-\end{figure}
-
-With the aid of both internal and induced orientations, the facet-to-facet relations can be summarized by matrices containing only $\{-1,0,0\}$, which are called \emph{incidence matrices}.
-To describe the primal face-to-edge incidence relation, for instance, a sparse $N_A \times N_L$-matrix $\mathbb{C}$ is assembled whose $(i,j)$-entry is assigned $+1$ if the internal orientation of edge $L_j$ and its induced orientation with respect to face $A_i$ coincides; it is assigned $-1$ if two orientations are opposite; and assigned $0$ if $L_j$ is not a subset of the boundary of $A_i$.
-Discrete Faraday's law (\ref{equ:maxwell_grid_faraday}) is thus reformulated by:
-\begin{equation*}
-    \mathbb{C}\mathbf{e} = - \frac{\text{d}}{\text{d}t} \mathbf{b}.
-\end{equation*}
-As the incidence matrix $\mathbb{C}$ makes up the curl operator in a discrete manner, it is referred to as the \emph{discrete curl operator} for a certain primal mesh.
-
-Given $\mathcal{M}$, the generation of $\Tilde{\mathcal{M}}$ is usually affiliated to $\mathcal{M}$ in terms of geometry, indexing, and topology.
-Although the latter two attributes can be defined with no dependence on $\mathcal{M}$, conventionally one specifies them relying on those of $\mathcal{M}$ for the sake of convenience in both formulation and implementation.
-Recall that primal edges (resp.
-faces) and dual faces (resp.
-edges) intersect in a one-to-one manner.
-Therefore, one can equate the index of a dual edge (resp.
-face) to that of its intersecting primal face (resp.
-edge).
-Furthermore, the internal orientation of a dual facet can be linked to that of its associated primal facet.
-With these constraints, discrete Ampere's law (\ref{equ:maxwell_grid_ampere}) can be reformulated into:
-\begin{equation*}
-    \Tilde{\mathbb{C}}\mathbf{h} = \frac{\text{d}}{\text{d}t} \mathbf{d} + \mathbf{j},
-\end{equation*}
-where $\Tilde{\mathbb{C}}$ is the dual face-to-edge incidence matrix of size $N_{\Tilde{A}} \times N_{\Tilde{L}}$, satisfying $\Tilde{\mathbb{C}} = \mathbb{C}^T$.
-
-In a similar way, discrete Gauss's laws (\ref{equ:maxwell_grid_gauss_B})(\ref{equ:maxwell_grid_gauss_D}) is rewritten into:
-\begin{equation*}
-    \mathbb{D}\mathbf{b} = 0, \ \ \ \  \Tilde{\mathbb{D}}\mathbf{d} = \mathbf{q},
-\end{equation*}
-with $\mathbb{D}$ being the primal cell-to-face incidence matrix of size $N_{V} \times N_{A}$, and $\Tilde{\mathbb{D}}$ being the dual cell-to-face incidence matrix of size $N_{\Tilde{V}} \times N_{\Tilde{A}}$.
-Since they serve as the discrete version of the div operator, they are also referred to as \emph{discrete div operator}.
-It is readily to be checked the following relations
-\begin{equation*}
-    \mathbb{D}\mathbb{C} = 0, \ \ \ \ \Tilde{\mathbb{D}}\Tilde{\mathbb{C}} = 0,
-\end{equation*}
-which is the discrete version of the vector calculus $\nabla \cdot (\nabla \times u) = 0$.
-
-Additionally, the grad operator at the discrete level can be constructed by edge-to-vertex incidence matrices $\mathbb{G}$ of size $N_L \times N_P$ and $\Tilde{\mathbb{G}}$ of size $N_{\Tilde{L}} \times N_{\Tilde{P}}$.
-Given an electric potential vector $\bm{\varphi}$ whose components are defined at primal vertices, for example, the edge voltage vector $\mathbf{e}$ can thus be computed by
-\begin{equation*}
-    \mathbf{e} = \mathbb{G}\bm{\varphi}.
-\end{equation*}
-
-The material laws (\ref{equ:maxwell_material_laws}) need to be reformulated within this framework.
-The relations between scalar vectors, in the form of $\mathbf{b} = \mathbb{M}_\mu \mathbf{h}$ and $\mathbf{d} = \mathbb{M}_\varepsilon \mathbf{e}$, are to be derived.
-In the simplest case where permittivity $\mu$ and permeability $\varepsilon$ are homogeneous in the domain, and the orthogonality\footnote{The edges of one mesh penetrate the faces of the other mesh in an orthogonal manner.} of ($\mathcal{M}, \Tilde{\mathcal{M}}$) pair is ensured, the material matrices are diagonal with entries
-
-\begin{equation*}
-    \mathbb{M}_\mu[i,i] = \frac{\mu|A_i|}{|\Tilde{L}_i|}, \ \ \ \ \mathbb{M}_\varepsilon[i,i] = \frac{\varepsilon |\Tilde{A}_i|}{|L_i|},
-\end{equation*}
-where $|\cdot|$ means taking length or area.
-
-To summarize, the FIT framework enables us to transform Maxwell’s equations into algebraic equations given the mesh pair ($\mathcal{M}, \Tilde{\mathcal{M}}$).
-The resulting system of algebraic equations is called Maxwell's Grid Equations (MGE).
-Let's put together the original form of the Maxwell system as well as the MGE:
-
-\begin{minipage}{0.3\textwidth}
-\begin{align*}
-    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \\
-    \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= -\mathbf{J}, \\
-    \nabla \cdot \mathbf{B} &= 0,  \\
-    \nabla \cdot \mathbf{D} &= \rho, \\
-    \mathbf{H} &= \mu^{-1} \mathbf{B}, \\
-    \mathbf{D} &= \varepsilon \mathbf{E}. 
-\end{align*}
-\end{minipage}
-\begin{minipage}{0.1\textwidth}
-\centering
-\begin{tikzpicture}
-\draw[thick, -{to}] (0,0) -- node[above]{$(\mathcal{M}, \Tilde{\mathcal{M}})$} (1.5,0);
-\end{tikzpicture}
-\end{minipage}
-\begin{minipage}{0.3\textwidth}
-\begin{align*}
-    \dot{\mathbf{b}} + \mathbb{C}\mathbf{e} &= 0 , \\
-    \dot{\mathbf{d}} - \Tilde{\mathbb{C}}\mathbf{h} &= - \mathbf{j}, \\
-    \mathbb{D}\mathbf{b} &= 0,  \\
-    \Tilde{\mathbb{D}}\mathbf{d} &= \mathbf{q},  \\
-    \mathbf{h} &= \mathbb{M}_\mu^{-1} \mathbf{b}, \\
-    \mathbf{d} &= \mathbb{M}_{\varepsilon} \mathbf{e}. 
-\end{align*}
-\end{minipage}
-\begin{minipage}{0.2\textwidth}
-Topological relations:
-\begin{align*}
-    \Tilde{\mathbb{C}} = \mathbb{C}^T \\
-    \mathbb{D}\mathbb{C} = 0 \\
-    \Tilde{\mathbb{D}}\Tilde{\mathbb{C}} = 0
-\end{align*}
-\end{minipage}
-
-\hfill
-
-Note that this transformation does not introduce approximations \emph{except for} the discrete material laws.
-The essence of FIT lies in that the complexity of continuous electric and magnetic field quantities
-is reduced to a finite number of well-defined discrete unknowns \citep{weiland_2003}.
-
-\subsection{Boundary treatment} \label{sec:boundary_treatment}
-
-So far we have not discussed the boundary treatment.
-In fact, in the formulation of MGE, no boundary of the spatial domain is taken into account and all the scalar vectors should be treated of infinite length.
-Yet in a computer simulation, the computational domain has to be bounded, and the introduction of boundary complicates the situation.
-Under the framework of FIT, the issue is twofold: 1) The staggered mesh doublet ($\mathcal{M}, \Tilde{\mathcal{M}}$) entails cut-off cells at the boundary such that the boundaries of both meshes match up.
-To close the cut-off cells, we need auxiliary facets and quantities attached to them.
-2) The auxiliary edges might not be straight and the auxiliary faces might not be flat, which necessitates a versatile data structure to include such situations.
-The boundary effect is shown in Fig.
-\ref{fig:illustraion_dual_boundary}.
-How these auxiliary quantities are incorporated into the discrete system is explained in Chapter \ref{chap:numerical_experiments_in_3d} along with the specific case.
-
-\begin{figure}
-    \centering
-    \begin{tikzpicture}
-    \coordinate (A1) at (0,0);
-    \coordinate (A2) at (2,-0.7);
-    \coordinate (A3) at (1.2,1);
-    \coordinate (A4) at (-0.5,1.5);
-    \draw[thick] (A1) node[left] {$\mathcal{M}$} -- (A2) -- (A3) -- cycle;
-    \draw[thick] (A1) -- (A4) -- (A3);
-    \begin{scope}[shift={(2,0.5)}]
-        \coordinate (B1) at (0,0);
-        \coordinate (B2) at (2,-0.7);
-        \coordinate (B3) at (1.2,1);
-        \coordinate (B4) at (-0.5,1.5);
-        \draw[thick] (B2) -- (B3) -- (B4);
-        \draw[gray]  (B1) -- (B3);
-        \draw[gray]  (B1) -- (B2);
-        \draw[gray]  (B1) -- (B4);
-    \end{scope}
-    \begin{scope}[shift={(4,1)}]
-        \coordinate (C1) at (0,0);
-        \coordinate (C2) at (2,-0.7);
-        \coordinate (C3) at (1.2,1);
-        \coordinate (C4) at (-0.5,1.5);
-        \draw[thick] (C2) -- (C3) -- (C4);
-        \draw[gray]  (C1) -- (C3);
-        \draw[gray]  (C1) -- (C2);
-        \draw[gray]  (C1) -- (C4);
-    \end{scope}
-    \draw[thick] (A4) -- (B4) -- (C4);
-    \draw[thick] (A3) -- (B3) -- (C3);
-    \draw[thick] (A2) -- (B2) -- (C2);
-    \draw[gray]  (A1) -- (C1);
-    \coordinate (O1) at (barycentric cs:A3=1,B3=1);
-    \coordinate (O2) at (barycentric cs:A3=1,B3=1,A4=1,B4=1);
-    \coordinate (O5) at (barycentric cs:A3=1,B3=1,A2=1,B2=1);
-    \draw[blue, very thick] (O2) -- (O1) -- (O5);
-    \coordinate (O3) at (barycentric cs:A1=1,A3=1,A4=1,B1=1,B3=1,B4=1);
-    \coordinate (O4) at (barycentric cs:A1=1,A2=1,A3=1,B1=1,B2=1,B3=1);
-    \draw[blue] (O2) -- (O3) -- (O4) -- (O5);
-    \coordinate (OO1) at ([shift={(2,0.5)}]O1);
-    \coordinate (OO2) at ([shift={(2,0.5)}]O2);
-    \coordinate (OO3) at ([shift={(2,0.5)}]O3);
-    \coordinate (OO4) at ([shift={(2,0.5)}]O4);
-    \coordinate (OO5) at ([shift={(2,0.5)}]O5);
-    \draw[very thick, blue] (OO2) -- (OO1) -- (OO5) node[right] {\textcolor{blue}{$\Tilde{\mathcal{M}}$}};
-    \draw[blue] (OO2) -- (OO3) -- (OO4) -- (OO5);
-    \draw[very thick, blue] (O2) -- (OO2);
-    %\draw[very thick, blue] (O1) -- (OO1);
-    \draw[very thick, blue] (O5) -- (OO5);
-    \draw[blue] (O3) -- (OO3);
-    \draw[blue] (O4) -- (OO4);
-    \fill[gray,opacity=0.2] (A4) -- (A3) -- (C3) -- (C4);
-    \fill[gray,opacity=0.2] (A3) -- (A2) -- (C2) -- (C3);
-    \end{tikzpicture}
-    \caption{Illustration of a cut-off dual cell at the boundary.
-Compared to the interior case, the dual cells at boundary are cut off.
-Besides, an extra dual face (with thick blue edges) as well as their edges are supplemented to close the dual mesh.
-Note that this supplementary face is not necessarily flat, and its edges are not necessarily straight, as is shown here.}
-    \label{fig:illustraion_dual_boundary}
-\end{figure}
-
-\section{Interpolation of electromagnetic quantities} \label{sec:interpolation}
-The coupling of the two subsystems is bidirectional, in the sense that the Maxwell system impacts the Euler system through the Lorentz force while the latter provides information about charges and currents to the former.
-Since the currents, as is indicated by (\ref{equ:maxwell_grid_ampere}), are defined at dual faces and appear as mass fluxes in the fluid equations, the Euler system is discretized on the dual mesh.
-Therefore, an issue occurs because the component-wise electromagnetic fields are required to compute the Lorentz force inside the dual cells whereas the Maxwell system can only provide the integral form due to the nature of FIT.
-Hence the interpolation from the integral form on either edges or faces to the vector form at the cell center has to be tackled.
-
-The problem is summarized as:
-\begin{itemize}
-    \item[-] Given the flux at each face of a polyhedron, reconstruct the vector field at the cell center;
-    \item[-] Given the projection at each edge of a polyhedron, reconstruct the vector field at the cell center. 
-\end{itemize}
-We adopt the principle of least square fitting, and try to reconstruct the \emph{constant} vector field inside each cell.
-Specifically, assuming a polyhedral cell with $k$ faces with areas $\{A_i\}_{i=1}^k$, normal vectors $\{\mathbf{n}_i\}_{i=1}^k$ and fluxes $\{f_i\}_{i=1}^k$, one wants to find a vector $\mathbf{h}$ satisfying
-\begin{equation*}
-    \mathbf{h} = \argmin_{h\in \mathbb{R}^3} \sum_{i=1}^k(A_i\mathbf{h} \cdot \mathbf{n}_i - f_i)^2.   
-\end{equation*}
-The solution can be easily expressed as
-\begin{equation*}
-    \mathbf{h} = (\mathbb{K}^T\mathbb{K})^{-1}\mathbb{K}^T\mathbf{f},
-\end{equation*}
-where
-\begin{equation*}
-    \mathbb{K} = [A_1\mathbf{n}_1, A_2\mathbf{n}_2, \cdots, A_k\mathbf{n}_k]^T,\ \ \ \mathbf{f} = [f_1, f_2, \cdots, f_k]^T,
-\end{equation*}
-and each vector in $\mathbb{R}^3$ is treated as a column vector.
-
-The interpolation based on the integral quantities on edges can be done similarly, namely to find a constant vector field that minimizes the square error.
-This approach amounts to a first-order interpolation in the sense that a constant vector field can be precisely reconstructed.
-Assembling the local interpolation of each dual cell, we end up getting the global interpolation relation
-\begin{equation}
-    \mathbf{E} = \Tilde{\mathbb{R}}_E\mathbf{e},
-    \ \ \ \ 
-    \mathbf{B} = \Tilde{\mathbb{R}}_B\mathbf{b},
-\end{equation}
-where $\mathbf{e}, \mathbf{b}$ are electric voltage vector and magnetic flux vector defined in (\ref{equ:fit_scale_vector}); $\mathbf{E} := (\mathbf{E}_i)_{i=1}^{N_{\Tilde{V}}}$ and $\mathbf{B} := (\mathbf{B}_i)_{i=1}^{N_{\Tilde{V}}}$ are $N_{\Tilde{V}} \times 3$ matrices stacking the interpolated $\mathbf{E}$-field and $\mathbf{B}$-field at each dual cell center; $\Tilde{\mathbb{R}}_E$ and $\Tilde{\mathbb{R}}_B$ are thus rank-3 tensors that perform interpolation.
-
-The problem of the reconstruction of vector fields on unstructured meshes is a widely studied topic.
-Apart from the least-square method, other methods include Perot's method \citep{perot_2000}, finite-element-based methods, etc., which potentially can achieve higher-order accuracy.
-See \cite[][sec.
-3.4.4]{fuchs_2021} and the references therein.
-
-\chapter{Asymptotic-preserving Schemes for Euler-Maxwell System}
-The objective of AP schemes is to solve problems over different regimes, that is, problems with a huge gap in a certain characteristic scale $\lambda$.
-An AP scheme expects to provide a uniformly working discretization for arbitrary value of $\lambda$.
-To this end, two central issues must be solved: first, the dependence of a stability-induced constraint on $\lambda$ has to be alleviated; second, $\lambda \rightarrow 0$ usually poses a singular perturbation problem, and the limiting scheme is supposed to remain valid and consistent to the limiting model.
-
-A plasma is a multi-scale system that involves several scales, e.g.
-the wave speeds of electromagnetic fields and plasma fluids, and the plasma thermal speed that impacts its response to an external electromagnetic field.
-The identification of the impact of different characteristic scales is realized by rescaling the equations.
-The scale of interest in this work is the Debye length $\lambda_D$ that has a strong connection with the quasi-neutrality of plasma.
-
-This chapter is organized as follows.
-First, we define several typical quantities relying on which the Euler-Maxwell system is rescaled.
-By making assumptions on the magnitude relations between these typical quantities, the parametrization of the system is limited to the dimensionless Debye length $\lambda$ and the quasi-neutral behavior can thus be identified.
-Afterward comes the presentation of an AP scheme.
-The asymptotic stability and consistency, namely the two properties as are defined in definition \ref{def:ap}, are discussed for this scheme.
-At last, we talk about two issues, namely boundary conditions and the presence of an insulating domain, that hinders the construction of AP schemes in the way that they could undermine the well-posedness of the problem in the limiting case.
-
-\section{Rescaling of Euler-Maxwell system} \label{sec:rescaling}
-The multi-scale nature of the Euler-Maxwell system is revealed by defining different dimensionless parameters.
-In particular, the quasi-neutrality approximation is clarified.
-The rescaling procedure mostly sticks to that of \cite{degond_2017}.
-
-First, typical values for each quantity, as well as the characteristic length and time scale are specified.
-Rescaled by these values, the magnitude of each term of the equations can be compared according to the presumption on the magnitude of these typical values.
-We define $\overline{x}$ and $\overline{t}$ as space and time scale of interest, by which the reference velocity $\overline{v}$ is defined as $\overline{x}/\overline{t}$.
-The typical magnitudes of electromagnetic fields are $\overline{E}$ and $\overline{B}$.
-The typical magnitudes of fluid quantities are denoted by $\overline{u}$ for plasma drift velocity, $\overline{n}$ for plasma number density, $\overline{T}$ for plasma temperature.
-On top of that, the typical pressure is set $\overline{n}k_B\overline{T}$ with $k_B$ being the Boltzmann constant; the typical value for the specific total energy and enthalpy is set $\overline{u}^2$.
-Together with the physical parameters, namely, permittivity $\varepsilon_0$, permeability $\mu_0$, light speed $c^2 = (\varepsilon_0\mu_0)^{-1}$, Boltzmann constant $k_B$, the elementary charge $e$, and ion mass $m_i$, the following dimensionless parameters are induced,
-\begin{align*} 
-    \xi &:= \frac{\overline{v}}{c} \text{ the velocity of interest to the light speed}, &\\
-    \zeta &:= \frac{\overline{u}}{\overline{v}} \text{ the plasma velocity to the speed of interest}, &\\
-    M &:= \frac{\overline{u}}{v_{th,i}} \text{ the plasma drift velocity to the thermal speed of ions, where } v_{th,i} := \left(\frac{k_B \overline{T}}{m_i}\right)^{1/2}, &\\
-    \eta &:= \frac{e\overline{E}\overline{x}}{m_i\overline{u}^2} \text{ the electric energy to the kinetic energy of ions}, &\\
-    \beta &:= \frac{\overline{v}\overline{B}}{\overline{E}} \text{ the induced electric field to the total electric field}, &\\
-    \lambda &:= \frac{\lambda_D}{\overline{x}} \text{ the dimensionless Debye length, where }\lambda_D := \left(\frac{\varepsilon_0k_B\overline{T}}{e^2\overline{n}}\right)^{1/2}, &\\
-    \varepsilon_*^2 &:= \frac{m_*}{m_i} \text{ the species mass ratio to the ion mass},\ \  * \in \{i,e,n,\cdots\}, &\\
-    g &:= \frac{1}{\overline{n}\lambda_D^3} \text{ the plasma parameter\footnotemark}.&
-\end{align*}
-\footnotetext{It is basically the reciprocal of the number of particles per Debye sphere, see \cite[][sec. 1.1]{gibbon2020}. Classical plasma theory assumes $g \ll 1$.}
-
-The Euler-Maxwell system (\ref{equ:maxwell_faraday}) to (\ref{equ:euler_}) is readily to be rescaled by nondimensionalizing each quantity with respect to its typical value.
-By abuse of notation, the dimensionless quantities have the same symbol with their original ones without incurring any ambiguity.
-For simplicity, we only consider the collision terms, namely $\Gamma_* = 0, \mathbf{R}_* = \mathbf{R}_*^\text{coll}, Q_* = 0$ in (\ref{equ:euler_}), while neglecting other effects.
-The rescaled Euler-Maxwell system reads
-\begin{align}
-    \beta \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday_rescalling} \\ 
-    \lambda^2 \partial_t \mathbf{E} - \frac{\beta \lambda^2}{\xi^2}\nabla \times \mathbf{B} &= - \frac{\zeta}{\eta M^2}\mathbf{J}, \label{equ:maxwell_ampere_rescalling} \\
-    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B_rescalling}\\
-    \lambda^2 \eta M^2 \nabla \cdot \mathbf{E} &= \rho, \label{equ:maxwell_gauss_D_rescalling} \\
-    \partial_t
-    \begin{bmatrix}
-    n_* \\
-    n_* \mathbf{u}_* \\
-    n_* e_*
-    \end{bmatrix}
-    + \nabla \cdot
-    \begin{bmatrix}
-    \zeta n_* \mathbf{u}_* \\
-    \zeta n_* \mathbf{u}_* \otimes \mathbf{u}_* + \zeta M^{-2} \varepsilon_*^{-2} p_*\mathbb{I} \\
-    \zeta n_* h_* \mathbf{u}_*
-    \end{bmatrix}
-    &=
-    \begin{bmatrix}
-    0 \\
-    \eta \zea \varepsilon_*^{-2} q_* n_*\mathbf{E} + \eta \zeta^2 \beta \varepsilon_*^{-2} q_* n_* \mathbf{u}_* \times \mathbf{B} \\
-    \zeta \eta \varepsilon_*^{-2} \mathbf{J}_* \cdot \mathbf{E}
-    \end{bmatrix} +
-    \begin{bmatrix}
-    0 \\
-    \varepsilon_*^{-2}\mathbf{R}_*^{\text{coll}} \\
-    0 
-    \end{bmatrix}, \label{equ:euler_rescalling}
-\end{align}
-where the equation of state becomes $e_* = \frac{1}{2}|\mathbf{u_*}|^2 + M^{-2}\frac{p_*}{\epsilon^2_* n_* (\gamma - 1)}$ and $h_* = e_* + M^{-2}\frac{p_*}{\epsilon^2_* n_*}$.
-For a fully-ionized gas, we have the original expression of $\mathbf{R}_*^{\text{coll}}$ in (\ref{equ:collision}), and its rescaled expression becomes
-\begin{equation*}
-    \mathbf{R}_i^{\text{coll}} = \frac{Z\text{ln}\Lambda}{16\pi}g\lambda^{-1}M^{-1}\varepsilon_en_en_i(\mathbf{u}_i - \mathbf{u}_e). 
-\end{equation*}
-
-Following the assumption in \cite{degond_2017}, the reference speed $\overline{v}$ is of the same scale with the plasma speed $\overline{u}$ and the thermal speed $v_{th,i}$ whereas it is much smaller than the light speed $c$.
-To study the quasi-neutral regime, the dimensionless Debye length $\lambda$ is an asymptotic parameter ranging in $[0,1]$.
-It is assumed that $\alpha$ has the same magnitude as $\lambda$, and $\eta$ and $\beta$ are of order one.
-
-Special treatment is needed for the collision term.
-One would notice the inverse proportionality to $\lambda$, which would introduce a singular perturbation to the Euler system as $\lambda \rightarrow 0$.
-However, the validity of such a collision model is doubtful when $\lambda \rightarrow 0$.
-From the physical viewpoint, the shielding effect characterized by Debye length $\lambda$ makes the impact parameter no larger than $\lambda$.
-The $\lambda \rightarrow 0$ limit implies that the collisions happen in the atomic length scale, in which quantum-mechanical effects must be taken into effect \citep{frank_1972}.
-Therefore, for simplicity, we decide to assume $g \sim \lambda$ and keep the prefactor of collision term constant $\alpha^{\text{coll}}$ throughout the simulation\footnote{The reasonableness of this assumption is questionable.}.
-
-In summary, we make the following choices
-\begin{align*}
-    \xi \sim g \sim \lambda \in [0,1], \ \ \ \zeta \sim M \sim \eta \sim \beta \sim \mathcal{O}(1).
-\end{align*}
-
-Under such assumptions on these dimensionless parameters, the rescaled Euler-Maxwell system is simplified into a parametrized system with the dimensionless Debye length $\lambda$ being the asymptotic parameter
-\begin{align}
-    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday_rescaled} \\ 
-    \lambda^2 \partial_t \mathbf{E} - \nabla \times \mathbf{B} &= - \mathbf{J}, \label{equ:maxwell_ampere_rescaled} \\
-    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B_rescaled}\\
-    \lambda^2 \nabla \cdot \mathbf{E} &= \rho, \label{equ:maxwell_gauss_D_rescaled} \\
-    \partial_t
-    \begin{bmatrix}
-    n_* \\
-    n_* \mathbf{u}_* \\
-    n_* e_*
-    \end{bmatrix}
-    + \nabla \cdot
-    \begin{bmatrix}
-    n_* \mathbf{u}_* \\
-    n_* \mathbf{u}_* \otimes \mathbf{u}_* + \varepsilon_*^{-2} p_*\mathbb{I} \\
-    n_* h_* \mathbf{u}_*
-    \end{bmatrix}
-    &=
-    \begin{bmatrix}
-    0 \\
-    \varepsilon_*^{-2} q_* n_* (\mathbf{E} + \mathbf{u}_* \times \mathbf{B}) \\
-    \varepsilon_*^{-2} \mathbf{J}_* \cdot \mathbf{E}
-    \end{bmatrix}+
-    \begin{bmatrix}
-    0 \\
-    \varepsilon_*^{-2}\mathbf{R}_*^{\text{coll}} \\
-    0 
-    \end{bmatrix}, \label{equ:euler_rescaled}
-\end{align}
-with the equation of state $e_* = \frac{1}{2}|\mathbf{u_*}|^2 + \frac{p_*}{\varepsilon^2_* n_* (\gamma - 1)}$ and $h_* = e_* + \frac{p_*}{\varepsilon^2_* n_*}$.
-For a fully-ionized gas with only ions and electrons,
-\begin{equation} \label{equ:collision_rescaled} 
-    \mathbf{R}_i^{\text{coll}} = \alpha^{\text{coll}}n_en_i(\mathbf{u}_i - \mathbf{u}_e) = - \mathbf{R}_e^{\text{coll}}.
-\end{equation}
-
-Although the rescaling of the equations involves considerable physical intuitions on the decision of typical values and their magnitudes, which is crucial to reach a physically meaningful problem, we are now in a position to forget this reasoning, and focus on the singular perturbation problem parameterized by $\lambda$.
-The rescaling enables us to identify the magnitude of each term of the equations, which is revealed by the prefactor polynomial of $\lambda$.
-The consequence of vanishing $\lambda$, namely the quasi-neutrality, will be discussed in the next section.
-
-\section{Quasi-neutral limit} \label{sec:quasi-neutral_limit}
-As is already discussed in section \ref{sec:quasi-neutrality}, the quasi-neutrality, being an important character of plasmas, refers to the fact that the net charge of the free electrons and ions in plasmas cancel out over an area of the same order as the Deybe length $\lambda_D$.
-When the typical length scale $\overline{x}$ is of magnitudes larger than $\lambda_D$, the condition $\rho = 0$ can be approximately satisfied.
-
-Such behavior is clearly explained through the rescaled Euler-Maxwell system (\ref{equ:maxwell_faraday_rescaled}) to (\ref{equ:euler_rescaled}).
-By formally taking dimensionless Debye length $\lambda$ to zero\footnote{The convergence of the solutions as $\lambda$ tending to zero is discussed in \cite[][chap.
-2]{remi_2014}}, the Maxwell system becomes
-\begin{align}
-    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday_limit} \\ 
-    - \nabla \times \mathbf{B} &= - \mathbf{J}, \label{equ:maxwell_ampere_limit} \\
-    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B_limit}\\
-     0 &= \rho. \label{equ:maxwell_gauss_D_limit}
-\end{align}
-One can notice that the quasi-neutral condition (\ref{equ:maxwell_gauss_D_limit}) is the consequence of taking $\lambda = 0$ in Gauss's law for electric field (\ref{equ:maxwell_gauss_D_rescaled}).
-Like the non-neutral case, Gauss's laws (\ref{equ:maxwell_gauss_B_limit}) (\ref{equ:maxwell_gauss_D_limit}) are the consequence of (\ref{equ:maxwell_faraday_limit}) (\ref{equ:maxwell_ampere_limit}) provided (\ref{equ:maxwell_gauss_B_limit}) (\ref{equ:maxwell_gauss_D_limit}) are satisfied at the initial time.
-
-The vanishing time derivative of $\mathbf{E}$-field is an indicator of the singular perturbation nature of the quasi-neutral model.
-To be specific, in the non-neutral model the $\mathbf{E}$-field evolves with time whereas in the quasi-neutral model it responds instantaneously to other quantities according to the constraint (\ref{equ:maxwell_ampere_limit}).
-To make it clear, we replace the equation (\ref{equ:maxwell_ampere_rescaled}) by the sum of the curl of (\ref{equ:maxwell_faraday_rescaled}) and the time-derivative of (\ref{equ:maxwell_ampere_rescaled}).
-Meanwhile exploiting the momentum equation in (\ref{equ:euler_rescaled}) to express $\partial_t\mathbf{J}$, we end up getting the reformulated Maxwell's equations
-\begin{align}
-    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday_reform}\\
-    \lambda^2\partial_t^2 \mathbf{E} + \nabla \times \nabla \times \mathbf{E} &= - a\mathbf{E} - \mathbf{b}, \label{equ:maxwell_ampere_reform}\\
-    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B_reform}\\
-    \lambda^2\nabla \cdot \mathbf{E} &= \rho, \label{equ:maxwell_gauss_D_reform}
-\end{align}
-where
-\begin{equation*}
-    a = \sum_*\varepsilon_*^{-2}q_*^2n_*, \ \ \ \mathbf{b} = \sum_* \epsilon_*^{-2}q_*^2n_*\mathbf{u}_*\times\mathbf{B} - q_*\nabla\cdot(n_* \mathbf{u}_* \otimes \mathbf{u}_* + \varepsilon_*^{-2}p_*\mathbb{I}).
-\end{equation*}
-It is easy to check that (\ref{equ:maxwell_faraday_reform}) to (\ref{equ:maxwell_ampere_reform}) is equivalent to (\ref{equ:maxwell_faraday_rescaled}) to (\ref{equ:maxwell_gauss_D_rescaled}) as soon as (\ref{equ:maxwell_ampere_rescaled}) is satisfied at the initial time.
-The equation (\ref{equ:maxwell_ampere_reform}) implies the shift from the hyperbolic nature to the elliptic nature of the $\mathbf{E}$-field as $\lambda\rightarrow0$.
-One of the key aims of designing an AP scheme is to reproduce this shift at the discrete level.
-
-\section{AP schemes}
-In this section, we present the full discretization with AP property.
-The general approach for spatial discretizations of both the Euler and Maxwell's equations has been introduced in chapter \ref{chap:discretization_euler_maxwell}.
-As stability is a central issue for the AP property, this section is mostly devoted to the time discretization of the Euler-Maxwell system.
-
-We want to first recall the objective of AP schemes and make clear the direction to proceed towards.
-By definition \ref{def:ap}, the stability condition that does not depend on $\lambda$ and the consistency of the limit scheme with the quasi-neutral system have to be fulfilled.
-Furthermore, what is desired for the numerical treatment of Maxwell's equations is that Gauss's law is satisfied at the discrete level.
-To sum up, the following properties of the constructed scheme are to be realized:
-
-\begin{itemize}
-    \item[I] stable regardless of the value of $\lambda$;
-    \item[II] the limit scheme by taking $\lambda = 0$ is valid\footnote{By ``valid" we mean the scheme is a valid recursion such that the state at $t^{m+1}$ can be \emph{uniquely} computed by that at $t^m$.} and consistent to its continuous counterpart (\ref{equ:maxwell_faraday_limit}) to (\ref{equ:maxwell_gauss_D_limit});
-    \item[III] Gauss's law (\ref{equ:maxwell_gauss_D_rescaled}) is fulfilled at the discrete level for any $\lambda$. \label{condition3}
-\end{itemize}
-
-Given the mesh pair $(\mathcal{M}, \Tilde{\mathcal{M}})$, Maxwell's equations are handled by the FIT framework while FVM is applied to Euler equations on the dual mesh 
-$\Tilde{\mathcal{M}}$.
-Naturally extending the AP scheme for 1D two-fluid plasma proposed in \cite{degond_2012} to which the detailed constructing procedure should be referred, we straightforwardly present the full-discretization scheme for 3D multi-species plasma:
-
-\begin{align}
-    \delta_m^{-1} (\mathbf{b}^{m+1} - \mathbf{b}^{m}) \hspace{0.4cm}&\;+\; \hspace{1.5cm}\mathbb{C}\textcolor{blue}{\mathbf{e}^{m+1}}\hspace{1.25cm}=\; 0, \label{equ:maxwell_faraday_ap}\\
-    \lambda^2\delta_m^{-1}(\mathbf{d}^{m+1} - \mathbf{d}^m) \hspace{0.4cm}&\;-\; \hspace{1.5cm}\Tilde{\mathbb{C}}\textcolor{blue}{\mathbf{h}^{m+1}} \hspace{1.22cm}=\; - \textcolor{blue}{\mathbf{j}^{m+1}}, \label{equ:maxwell_ampere_ap}\\
-    \delta_m^{-1}(\mathbf{U}_{*,k}^{m+1} - \mathbf{U}_{*,k}^{m}) \hspace{0.10cm}&\;+\;  \frac{1}{|\Tilde{V}_k|}\sum_{j:\Tilde{A}_j\in\partial\Tilde{V}_k}|\Tilde{A}_j|\textcolor{blue}{\overline{\mathbf{F}}_{*,j}^{m+1/2}} \hspace{0.05cm}=\; \textcolor{blue}{\mathbf{RHS}_{*,k}^{m+1/2}}, \label{equ:euler_ap}
-\end{align}
-where 
-\begin{align}
-    \mathbf{U}_{*,k}^{m} &=
-    \begin{bmatrix}
-    n_* \\
-    n_* \mathbf{u}_* \\
-    n_* e_*
-    \end{bmatrix}^m_k, \\
-    \overline{\mathbf{F}}_{*,j}^{m+1/2} &=
-    \begin{bmatrix}
-    f^{m+1}_{n,*,j} \\
-    \bm{f}^m_{u,*,j} \\
-    f^m_{e,*,j} 
-    \end{bmatrix}
-    = 
-    \begin{bmatrix}
-    \frac{1}{2}\left[\textcolor{blue}{(nu_{\bot})_{*,k}^{m+1}} + \textcolor{blue}{(nu_{\bot})_{*,k+1}^{m+1}}\right] - \frac{1}{2}s^m_{*,k+1/2}(n_{*,k+1}^m - n_{*,k}^m) \\
-    \frac{1}{2}\left[(nu_{\bot}\mathbf{u})^m_{*,k} + (nu_{\bot}\mathbf{u})^m_{*,k+1} + p_{*,k}^m\mathbf{n}_j + p_{*,k+1}^m\mathbf{n}_j\right] - \frac{1}{2}s^m_{*,k+1/2}\left[(n\mathbf{u})^m_{*,k+1} - (n\mathbf{u})^m_{*,k}\right] \\
-    \frac{1}{2}\left[(nhu_\bot)^m_{*,k} + (nhu_\bot)^m_{*,k+1}\right] - \frac{1}{2}s^m_{*,k+1/2}\left[(ne)^m_{*,k+1} - (ne)^m_{*,k}\right]
-    \end{bmatrix}, \label{equ:flux_ap}\\
-    \mathbf{RHS}_{*,k}^{m+1/2} &=
-    \begin{bmatrix}
-    0 \\
-    \varepsilon_*^{-2}q_*\left[n_*^m\textcolor{blue}{\mathbf{E}^{m+1}} + (n\mathbf{u})^m_*\times\mathbf{B}^m\right] \\
-    \varepsilon_*^{-2}q_*(n\mathbf{u})^m_* \cdot \textcolor{blue}{\mathbf{E}^{m+1}}
-    \end{bmatrix}_k +
-    \begin{bmatrix}
-    0 \\
-    \varepsilon_*^{-2}\textcolor{blue}{\mathbf{R}_{*,k}^{\text{coll},m+1}} \\
-    0
-    \end{bmatrix}, \label{equ:rhs_ap}\\
-    \mathbf{R}_{*,k}^{\text{coll},m+1} &= 
-    \begin{cases}
-    \alpha^\text{coll}\left[n_{e,k}^m\textcolor{blue}{(n\mathbf{u})^{m+1}_{i,k}} - n_{i,k}^m\textcolor{blue}{(n\mathbf{u})^{m+1}_{e,k}}\right] \text{  if  } * = e \\
-    \alpha^\text{coll}\left[n_{i,k}^m\textcolor{blue}{(n\mathbf{u})^{m+1}_{e,k}} - n_{e,k}^m\textcolor{blue}{(n\mathbf{u})^{m+1}_{i,k}}\right] \text{  if  } * = i
-    \end{cases}  \\
-    \mathbf{j}^{m+1} &= \left(\sum_*\pm q_*\textcolor{blue}{f^{m+1}_{n,*,j}}|\Tilde{A}_j|\right)_{j=1}^{N_{\Tilde{A}}}, \label{equ:current_ap}\\
-    \mathbf{d}^m &= \mathbb{M}_\varepsilon \mathbf{e}^m, \ \ \ \mathbf{h}^m = \mathbb{M}_\mu^{-1} \mathbf{b}^m. \label{equ:material_law}
-\end{align}
-In the above scheme, the superscript $m$ indicates the number of iterations, and the quantities with superscript $m+1/2$ implies its dependency on the quantities at both $m$-th and $(m+1)$-th iterations; $\delta_m$ is the time step size for the $m$-th iteration.
-The numerical flux (\ref{equ:flux_ap}), where $u_\perp$ stands for the velocity component normal to the dual face $\Tilde{A}_j$, is just the application of the generic Rusanov flux (\ref{equ:rusanov-flux-3d}) on the Euler equations, see also the expression (\ref{equ:rusanov_flux_euler}) in the appendix.
-
-By abuse of notations, quantities with subscript $k+1$ are associated with the adjacent cell of $\Tilde{V}_k$ with respect to $\Tilde{A}_j$, which should not be confused with its real index.
-$\mathbf{n}_j$ is the outer normal of $\Tilde{A}_j$ as a face of $\Tilde{V}_k$.
-Since the equations have been rescaled into the dimensionless form, the material matrices $\mathbb{M}_\varepsilon = \text{diag}(\{|\Tilde{A}_i|/{|L_i|}\}_i)$, $\mathbb{M}_\varepsilon = \text{diag}(\{{|A_i|}/{|\Tilde{L}_i|}\}_i)$ now only depend on the meshes.
-
-Recall that the discrete Euler system (\ref{equ:euler_ap}) is defined on the dual mesh $\Tilde{\mathcal{M}}$, and hence $\mathbf{E}^{m+1}$ and $\mathbf{B}^m$ in (\ref{equ:rhs_ap}) are the interpolated vector fields at dual cell center as is illustrated in section \ref{sec:interpolation}.
-The $\pm$ in (\ref{equ:current_ap}) arises from the fact that the direction of numerical fluxes is determined by the outer normal of each cell whereas each component in $\mathbf{j}^{m+1}$ is defined to be aligned with the internal orientation of the dual face it associates with.
-Hence a flip of the sign may be necessary.
-
-First, we would like to discuss the necessity of the implicit terms (highlighted in blue color).
-The implicit treatment of electric field in (\ref{equ:rhs_ap}) is a must to ensure stability and is justified in \cite{fabre_1992} for the Euler-Poisson system.
-It is reasonable to infer that it applies equally to the Euler-Maxwell system.
-To guarantee Gauss's law at the discrete level, the current in (\ref{equ:maxwell_ampere_ap}), as well as the mass flux in (\ref{equ:flux_ap}), must be at the same implicit level.
-The reformulated Ampere's law (\ref{equ:maxwell_ampere_reform}) gives us some clue that in the quasi-neutral case the right-hand side, arising from the electric current, must be implicit to lead to a valid and unique time-stepping.
-Furthermore, we stress that the current (\ref{equ:current_ap}) is evaluated by the numerical mass flux rather than its original definition $\sum_*n_*q_*\mathbf{u}_*$ for the sake of consistency to the discrete Gauss's law.
-The implicitness of the electric field in (\ref{equ:maxwell_faraday_ap}) and the magnetic flux in (\ref{equ:maxwell_ampere_ap}) is necessary for unconditional stability with respect to $\lambda$, as is demonstrated by \cite{degond_2012} through a linearized analysis.
-The implicitness of the friction term is owing to the stiffness incurred from a potentially large value of $\varepsilon^{-2}_*\alpha^\text{coll}$.
-
-Now we deduce the limiting scheme and check its validity and consistency.
-By formally setting $\lambda = 0$ in the AP scheme (\ref{equ:maxwell_faraday_ap}) to (\ref{equ:euler_ap}), the equation for evolving the electric edge voltages (\ref{equ:maxwell_ampere_ap}) degenerates into a constraint that should be satisfied at each step, namely
-\begin{equation*}
-     \Tilde{\mathbb{C}}\mathbb{M}_\mu^{-1}\mathbf{b}^{m+1} = - \mathbf{j}^{m+1}.
-\end{equation*}
-We want to check the consistency of the limiting scheme with the quasi-neutral model, and especially to check if the constraint (\ref{equ:maxwell_ampere_reform}) when $\lambda = 0$ is correctly discretized.
-To that end, we mimic the procedure to derive (\ref{equ:maxwell_ampere_reform}) in a discrete way, which leads to
-\begin{equation*}
-    (\Tilde{\mathbb{C}}\mathbb{M}_\mu^{-1}\mathbb{C}\mathbf{e}^{m+1})_j / |\Tilde{A}_j| = - \frac{1}{2}(a_{j,k}^m\mathbf{E}^{m+1}_{j,k} + a_{j,k+1}^m\mathbf{E}^{m+1}_{j,k+1})\cdot \mathbf{n}_j - \frac{1}{2}(\mathbf{b}_{j,k}^m + \mathbf{b}_{j, k+1}^m) \cdot \mathbf{n}_j - \pi_j^m,
-\end{equation*}
-where
-\begin{align*}
-    a_{j,k}^m &= \sum_*\pm\varepsilon_*^{-2}q_*^2n^m_{*,k}, \\
-    \mathbf{b}_{j,k}^m &= \sum_*\pm\varepsilon_*^{-2}q_*\left[(n\mathbf{u})^m_{*,k}\times\mathbf{B}^m_k - \frac{1}{|\Tilde{V}_k|}\sum_{i:\Tilde{A}_i\in\partial\Tilde{V}_k}|\Tilde{A}_i|\bm{f}_{u,*,i}^m\right], \\
-    \pi^m_j &= - \frac{1}{2} \delta_m^{-1} \sum_* \pm q_* \left[s_{*,k+1/2}^m(n^m_{*,k+1} - n^m_{*,k}) - s^{m-1}_{*,k+1/2}(n^{m-1}_{*,k+1} - n^{m-1}_{*,k})\right].
-\end{align*}
-Comparison with (\ref{equ:maxwell_ampere_reform}) manifests the consistency when $\lambda = 0$, given the fact that $\pi^m_j = \mathcal{O}(h)$ where h is cell size.
-
-One should be aware that such a scheme merely meets the necessary conditions of AP property while we do not rigorously prove that it is AP.
-The difficulty to prove the nonlinear stability for such a complex system is notorious.
-Also as is mentioned throughout the thesis, the convergence of the continuous solutions as $\lambda \rightarrow 0$ is taken for granted.
-Therefore, instead of rigorously proving the scheme to be AP, the procedure shown here should be treated as a heuristic approach for constructing AP schemes, and one should always turn to numerical experiments for verification.
-
-\section{CFL condition}
-
-It has been shown in \cite{degond_2012} that the stability-induced constraint on the time-step size does not depend on the value of $\lambda$ thanks to the implicitness in the discrete Maxwell system.
-However, the Euler system is discretized by an explicit scheme and thus still subject to a CFL condition which we want to specify here.
-
-In standard conservation laws where no source term is present, the CFL condition is solely dependent on the numerical flux (recall Rusanov flux (\ref{equ:rusanov-flux-3d})) and mesh size $\delta_x$.
-Classically one restricts the time step size by $\delta_t < \delta_x/s$ where $s$ represents the maximum wave speed over all the cells.
-
-To be noticed is that the presence of source terms might poses more constraint. Let us consider the model equation
-\begin{equation*}
-    \partial_tu + c\partial_xu = \beta u, 
-\end{equation*}
-where $c>0$ and $\beta<0$ are constant. By a first-order upwind scheme
-\begin{equation*}
-    \delta_t^{-1}(u^{m+1}_k - u^m_k) + c\delta_x^{-1}(u^m_k - u^m_{k-1}) = \beta u^m_k,
-\end{equation*}
-we can perform Neumann analysis and deduce the CFL condition
-\begin{equation*}
-    \delta_t \leq \left[\frac{c}{\delta_x} + \frac{\beta}{2}\right]^{-1}.
-\end{equation*}
-On noticing the source term $\varepsilon_*^{-2}q_*(n\mathbf{u})^m_*\times\mathbf{B}^m$ in the momentum equation, we heuristically take the following restriction
-\begin{equation*}
-    \delta_t^m \leq \min_*\bigg\{\left[\frac{s^m_*}{\delta_x} + \frac{\varepsilon^{-2}_*|q_*||\mathbf{B}^m|}{2}\right]^{-1}\bigg\},
-\end{equation*}
-which is proven necessary by numerical experiments.
-
-A short remark goes to the factor $\varepsilon_*^{2}$, the mass ratio with respect to a reference mass.
-Because of the small mass of electrons, this factor can be very penalizing as it leads to a stiff time-stepping for heavy species.
-It is possible and interesting to devise a scheme that is AP with respect to the limit of vanishing $\varepsilon_e^{2}$ \citep{degond_2008}.
-
-\section{Impact of boundary conditions} \label{sec:impact_of_bc}
-We want to talk about the problems that may arise due to inappropriate BCs when taking $\lambda \rightarrow 0$.
-Since the scheme is supposed to work for both regimes, the BCs ought to be uniformly well-posed.
-An example is given to convey the idea.
-Let's look at the continuous non-neutral Amp\`{e}re's law (\ref{equ:maxwell_ampere_rescaled})
-\begin{equation*}
-    \lambda^2 \partial_t \mathbf{E} - \nabla \times \mathbf{B} = - \mathbf{J},
-\end{equation*}
-which loses its hyperbolic character and becomes a constraint when $\lambda \rightarrow 0$. Now consider two boundary conditions
-\begin{itemize}
-    \item[-]  $\mathbf{E}\cdot\mathbf{n} = 0$ on $\partial\Omega$;
-    \item[-] $\nabla \times \mathbf{B} \cdot\mathbf{n} = \mathbf{J}\cdot\mathbf{n}$ on $\partial\Omega$. 
-\end{itemize}
-They are equivalent when $\lambda$ is non-zero provided $\mathbf{E}\cdot\mathbf{n}|_{\partial\Omega}$ is zero at the initial time.
-However, setting $\lambda = 0$ destroys the equivalence.
-The second BC no longer implies the first one and becomes redundant since the quasi-neutral Amp\`{e}re's law already enforces such condition, which ruins the well-posedness of the quasi-neutral problem.
-Hence the first BC is the one that is supposed to be employed.
-
-From the viewpoint of the discrete model, the continuous equations are discretized into a set of algebraic equations according to the scheme, and they are assembled into a linear system that needs to be solved at each time step.
-The redundancy of the second BC at limiting case results in the singularity of the linear system since the BC can be derived by linear operations from the algebraic form of the PDEs.
-This issue and how BCs are incorporated in the numerical scheme will be elaborated in Chapter \ref{chap:numerical_experiments_in_3d}.
-
-\section{Impact of insulating domain} \label{sec:impact_insulating_domain}
-
-In many applications, plasmas might be confined by insulating solid walls in which the electromagnetic fields are of interest as well.
-An example is sketched in Fig.
-\ref{fig:sketch_domain_fusch} which is the test case in \cite{fuchs_2021}.
-The plasma is enclosed by an insulating solid sleeve where no charged particles exist.
-Such a setting implies that the plasma domain, where the Euler system is defined, does not make up the whole domain, where the Maxwell system is defined.
-\begin{figure}
-    \centering
-    \begin{tikzpicture}
-    \coordinate (O1) at (0,0);
-    \draw[very thick] (O1) circle (1) node {Cathode};
-    \fill[blue, opacity=0.2] (O1) circle (1);
-    \draw[very thick] (O1) circle (1.5);
-    \coordinate (O2) at (4.5,1) ;
-    \draw[gray] (O2) circle (1);
-    \node at (O2) {Anode};
-    \node at (barycentric cs:O1=1,O2=1) {Plasma}; 
-    \fill[red, opacity=0.2] (O2) circle (1);
-    \coordinate (S1) at ([shift={(-0.196,0.98)}]O1);
-    \coordinate (S2) at ([shift={(-0.196,0.98)}]O2);
-    \coordinate (P1) at ([shift={(0.196,-0.98)}]O1);
-    \coordinate (P2) at ([shift={(0.196,-0.98)}]O2);
-    \draw[gray] (S1) -- (S2);
-    \draw[gray] (P1) -- (P2);
-    \coordinate (SS1) at ([shift={({-0.196*1.5},{0.98*1.5})}]O1);
-    \coordinate (SS2) at ([shift={({-0.196*1.5},{0.98*1.5})}]O2);
-    \coordinate (PP1) at ([shift={({0.196*1.5},{-0.98*1.5})}]O1);
-    \coordinate (PP2) at ([shift={({0.196*1.5},{-0.98*1.5})}]O2);
-    \draw[very thick] (SS1) -- (SS2);
-    \draw[very thick] (PP1) -- (PP2); 
-    \draw[gray] (SS2) arc (101.31:180+101.31:1.5);
-    \draw[very thick] (PP2) arc (101.31-180:101.31:1.5);
-    \draw[-to] (barycentric cs:SS1=1,SS2=1,S1=1,S2=1) to[out=90,in=0] ([shift={(-0.5,0.5)}]barycentric cs:SS1=1,SS2=1,S1=1,S2=1) node[left] {Solid};
-    \begin{scope}[shift={(5.5,-1.4)}]
-    \draw[blue, -to] (0,0) -- (0.7,0.14) node[right]{\small $z$};
-    \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
-    \draw[blue, -to] (0,0) -- (0.7,0) node[below]{\small $y$};
-    \end{scope}
-    \end{tikzpicture}
-    \caption{Sketch of the computational domain of the case in \cite{fuchs_2021}.
-Different from the one in this thesis (see Fig.
-\ref{fig:sketch_domain}), there is a solid enclosing sleeve, and the plasma is confined at the inner area.}
-    \label{fig:sketch_domain_fusch}
-\end{figure}
-Consequently, the following Maxwell's equations to be solved in the insulating solid domain
-\begin{align}
-    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:tmp__1}\\ 
-    \lambda^2 \partial_t \mathbf{E} - \nabla \times \mathbf{B} &= 0,  \label{equ:tmp__3}\\
-    \nabla \cdot \mathbf{B} &= 0, \\
-    \lambda^2 \nabla \cdot \mathbf{E} &= 0 \label{equ:tmp__2}.
-\end{align}
-Supplemented by suitable BCs, the problem is well-posed for $\lambda > 0$.
-Nonetheless, the $\lambda \rightarrow 0$ limit would lose control of the irrotational part of $\mathbf{E}$-field since only the term curl$\mathbf{E}$ remains in the equations when $\lambda = 0$ (equation (\ref{equ:tmp__2}) becomes trivial) and the BCs are not sufficient to uniquely determine an irrotational vector field.
-
-To circumvent this problem, one can possibly, as \cite{fuchs_2021}, define a small electrical conductivity $\sigma$ for the insulating domain so that Amp\`{e}re's law becomes
-\begin{equation*}
-    \lambda^2 \partial_t \mathbf{E} - \nabla \times \mathbf{B} = \sigma\mathbf{E},
-\end{equation*}
-and the $\lambda \rightarrow 0$ limit model regains well-posedness.
-
-The quasi-neutral limit of the Maxwell system in insulating mediums shares much similarity with the eddy current approximation where the propagation speed, namely the light speed, is treated as infinite, and the displacement current $\partial_t\mathbf{D}$ is hence omitted.
-Recall that in Section \ref{sec:rescaling} we assume $\lambda$ has the same order as $\xi$, the ratio of the typical speed and light speed.
-Therefore, although the Debye length is not defined in the solid domain where no plasma exists, the $\lambda \rightarrow 0$ limit of the Maxwell system (\ref{equ:tmp__1}) to (\ref{equ:tmp__2}) is supposed to be interpreted as the eddy current approximation.
-Due to the disappearance of the divergence-free constraint (\ref{equ:tmp__2}) when $\lambda = 0$, the system is not well-posed.
-This failure might be resolved by enforcing vanishing divergence of the $\mathbf{E}$-field at the $\lambda \rightarrow 0$ limit, which is no longer a consequence of Amp\`{e}re's law (\ref{equ:tmp__3}).
-In this thesis, we do not pursue this way.
-One would later see that in the numerical experiments, for simplicity, we cancel the solid domain and extend the plasma domain to the whole domain.
-Similar to applying a small conductivity, this way recovers the connection between the current density and the $\mathbf{E}$-field.
-
-\chapter{Numerical Experiments in 1D}
-This chapter is devoted to reproducing the results in \cite{degond_2012} upon which our generalized scheme is built.
-In their work, 1D problems of one-fluid and two-fluid models are treated by FDTD, in the sense that quantities are defined on staggered structured meshes.
-As is mentioned before, the FDTD method is a subset of the FIT method, and they are equivalent under Cartesian meshes.
-One can interpret the FIT treatment of 1D problems through the projection of quantities defined on a 3D Cartesian mesh dual onto a 1D axis, as is depicted in Fig.
-\ref{fig:1d-frame}.
-
-Although Maxwell's equations are inherently 3D, their reduction in 1D can be derived based on some assumptions and, thanks to great simplification on notations and implementations, helps to test numerical schemes.
-In this chapter, three cases are tested: one-fluid and two-fluid models tested in \cite{degond_2012}, and additionally the two-fluid model with friction terms.
-The verification is meant to pave the way for testing in the 3D setting.
-
-\section{One-fluid model}
-In the one-fluid model, only the dynamics of electrons are to be simulated while the background ions are fixed with a uniform number density of unity.
-The ions are singly-charged throughout the thesis if not specifically stated.
-Since ions are much heavier than electrons, such a model is a reasonable approximation when only the short-term behavior is of interest so that ions have no time to respond.
-
-The rescaled one-fluid Euler-Maxwell system\footnote{In \cite{degond_2012}, the equation (2.11) is wrong since the mass ratio $\varepsilon^2$ is missing whereas it is necessary to reproduce their results.} is adapted from the general system (\ref{equ:maxwell_faraday_rescaled}) to (\ref{equ:euler_rescaled}) by only keeping one set of fluid equations to describe electrons and setting the number density of ions to be unity:
-\begin{align}
-    & \partial_t n + \nabla\cdot(n \mathbf{u}) = 0, \label{equ:EM_1f_n}\\
-    \varepsilon^2[& \partial_t (n \mathbf{u}) + \nabla \cdot (n \mathbf{u} \otimes \mathbf{u})] + \nabla p(n) = -n(\mathbf{E} + \mathbf{u} \times \mathbf{B}), \label{equ:EM_1f_nu}\\
-    & \partial_t \mathbf{B} + \nabla \times \mathbf{E} = 0 \label{equ:EM_1f_faraday}. \\
-    \lambda^2 & \partial_t \mathbf{E} - \nabla \times \mathbf{B} = n \mathbf{u}, \label{equ:EM_1f_ampere}\\
-    & \nabla\cdot \mathbf{B} = 0, \label{equ:EM_1f_gauss_B} \\
-    \lambda^2 & \nabla\cdot \mathbf{E} = 1 - n \label{equ:EM_1f_gauss_E}.
-\end{align}
-where $n$ and $\mathbf{u}$ stands for electron number density and velocity, $\varepsilon^2$ now stands for electron-ion mass ratio $m_e/m_i$ which is taken to be $10^{-4}$ here.
-Note that the energy equation is removed by assuming adiabatic process, and the equation of state $p(n) = n^\gamma$ with $\gamma = 5/3$ is supplemented.
-
-\subsection{Governing equations in 1D} \label{sec:1f-eqs-1d}
-The 3D problem is projected onto the 1D axis by assuming vanishing traverse derivatives (see Fig.
-\ref{fig:1d-frame} for the definition of reference frame).
-Besides, $u_y, E_y, B_x, B_z$ are set zero for simplicity, which amounts to considering the TE mode.
-The collision between particles is omitted for the time being.
-\begin{figure}
-    \centering
-    \includegraphics[scale=0.2]{1d_frame.png}
-    \caption{Projection of the 3D model onto $z$-axis.
-Let us consider a Cartesian mesh doublet.
-The reduction is accomplished by assigning the quantities defined on each cross-section, which is parallel to the $x$-$y$ plane, to its intersection point at $z$-axis.
-Since it is assumed that no variations occur in each cross-section, the quantities in 3D can be compressed by the ones that locate at each mesh point on the $z$-axis.}
-    \label{fig:1d-frame}
-\end{figure}
-
-Take all the traverse derivatives $\partial_x, \partial_y$ and $u_y, E_y, B_x, B_z$ to be zero, we get the one-fluid Euler-Maxwell system in 1D:
-\begin{align*}
-    \partial_t n + \partial_z(nu_z) &= 0, \\
-    \varepsilon^2[\partial_t(nu_x) + \partial_z(nu_zu_x)] &= - n(E_x - u_zB_y), \\
-    \varepsilon^2[\partial_t(nu_z) + \partial_z(nu_z^2)] + \partial_z(p(n)) &= -n(E_z + u_xB_y), \\
-    \partial_t B_y + \partial_z E_x &= 0, \\
-    \lambda^2 \partial_t E_x + \partial_z B_y &= nu_x, \\
-    \lambda^2 \partial_t E_z &= nu_z, \\
-    \lambda^2 \partial_z E_z &= 1 - n,
-\end{align*}
-as well as the quasi-neutral limit by taking $\lambda \rightarrow 0$:
-\begin{align*}
-    n &= 1\\
-    \varepsilon^2 \partial_t(u_x) &= - E_x, \\
-    E_z + u_xB_y &= 0, \\
-    u_z &= 0 \\
-    \partial_t B_y + \partial_z E_x &= 0, \\
-    \partial_z B_y &= nu_x
-\end{align*}
-
-\subsection{Full discretization} \label{sec:1f1d-discretization}
-Adapt the AP scheme (\ref{equ:maxwell_faraday_ap}) to (\ref{equ:euler_ap}) to this case, and we end up with
-\begin{align}
-    \frac{n^{m+1}_k - n^m_k}{\delta^m} + \frac{\textcolor{blue}{f^{m+1/2}_{n,k+1/2} - f^{m+1/2}_{n,k-1/2}}}{h} &= 0, \label{equ:1f1d-n}\\
-    \frac{(nu_x)^{m+1}_k - (nu_x)^m_k}{\delta^m} + \frac{f^{m}_{u_x,k+1/2} - f^{m}_{u_x,k-1/2}}{h} &= -\frac{n^m_k \textcolor{blue}{E^{m+1}_{x,k}}}{\varepsilon^2} + \frac{n^m_k u^m_{z,k}\Tilde{B}^m_{y,k}}{\varepsilon^2}, \label{equ:1f1d-nux}\\
-    \frac{(nu_z)^{m+1}_k - (nu_z)^m_k}{\delta^m} + \frac{f^{m}_{u_z,k+1/2} - f^{m}_{u_z,k-1/2}}{h} &= - \frac{n^m_k \textcolor{blue}{\Tilde{E}^{m+1}_{z,k}}}{\varepsilon^2} - \frac{n^m_k u^m_{x,k}\Tilde{B}^m_{y,k}}{\varepsilon^2}, \label{equ:1f1d-nuz}\\
-    \frac{B^{m+1}_{y,k+1/2} - B^{m}_{y,k+1/2}}{\delta^m} + \frac{\textcolor{blue}{E^{m+1}_{x,k+1} - E^{m+1}_{x,k}}}{h} &= 0, \label{equ:1f1d-By}\\
-    \lambda^2 \frac{E^{m+1}_{x,k} - E^{m}_{x,k}}{\delta^m} + \frac{\textcolor{blue}{B^{m+1}_{y,k+1/2} - B^{m+1}_{y,k-1/2}}}{h} &= \textcolor{blue}{(nu_x)^{m+1}_k}, \label{equ:1f1d-Ex}\\
-    \lambda^2 \frac{E^{m+1}_{z,k+1/2} - E^{m}_{z,k+1/2}}{\delta^m} &= \textcolor{blue}{f^{m+1}_{n,k+1/2}}, \label{equ:1f1d-Ez}
-\end{align}
-where 
-\begin{equation*}
-    \Tilde{E}^m_{z,k} = \frac{1}{2}(E^m_{z,k+1/2} + E^m_{z,k-1/2}), \ \ \ \Tilde{B}^m_{y,k} = \frac{1}{2}(B^m_{y,k+1/2} + B^m_{y,k-1/2}),
-\end{equation*}
-is the consequence of interpolation of electromagnetic field, 
-and the fluxes read
-\begin{align*}
-    f^{m+1/2}_{n,k+1/2} & = \frac{1}{2}[\textcolor{blue}{(nu_z)^{m+1}_k + (nu_z)^{m+1}_{k+1}} + \mu^m_{k+1/2}(n^m_k - n^m_{k+1})], \\
-    f^{m}_{u_x,k+1/2} & = \frac{1}{2}[(nu_zu_x)^{m}_k + (nu_zu_x)^{m}_{k+1} + \mu^m_{k+1/2}((nu_x)^m_k - (nu_x)^m_{k+1})], \\
-    f^{m}_{u_z,k+1/2} & = \frac{1}{2}[(nu_z^2 + p(n)/\varepsilon^2)^{m}_k + (nu_z^2 + p(n)/\varepsilon^2)^{m}_{k+1} + \mu^m_{k+1/2}((nu_z)^m_k - (nu_z)^m_{k+1})]. \\
-\end{align*}
-
-\subsection{Numerical results}
-A Riemann problem, namely a discontinuous initial condition with two states, is considered. The spatial domain is $[-0.1, 0.1]$. Initially, 
-\begin{align*}
-    & n(z,0) = 1,\ \ u_z(z,0) = \chi_{[-0.1,0]}(z) - \chi_{[0,0.1]}(z), \\
-    & u_x(z,0) = B_y(z,0) = E_x(z,0) = E_z(z,0) = 0.
-\end{align*}
-Homogeneous Neumann boundary condition is enforced for all the variables for simplicity whereas more sophisticate BC\footnote{In \cite{degond_2012}, Silver-M\"{u}ller condition is used.} is employed in \cite{degond_2012}.
-The experiments show that no distinct difference occurs.
-
-To verify the implementation, a grid convergence study is done, see Fig.
-\ref{fig:grid_study_1d1f}.
-Due to the discontinuity of solutions, the expected convergence rate for $L^1$-norm error is $1/2$.
-Since no analytic solution is available, the reference solution is obtained using very fine mesh ($N = 16385$).
-In addition, the convergence of the number density and the $z$-momentum as the underlying mesh being refined is displayed in Fig.
-\ref{fig:grid_study_field_1d1f} for $\lambda = 0.01$.
-Conformity with the results in \cite{degond_2012} is demonstrated by Fig.
-\ref{fig:lambdas_1d1f} and \ref{fig:lambdas_ref_1d1f}.
-For $\lambda = 1$, the coupling of fluid motions and electromagnetic fields is weak so that the solution behaves like a shock tube.
-With decreasing $\lambda$, the coupling effect becomes noticeable.
-For $\lambda \ll 1$, the solutions converge to quasi-neutral limit.
-The performance of the scheme when $\lambda = 0$ is also shown in Fig.
-\ref{fig:lambdas_1d1f}, which leads to a valid solution and nicely reproduces the theoretical solution ($n = 1$ and $u_z = 0$).
-Slight difference happens for the $z$-momentum when $\lambda = 10^{-4}$, which might result from the different treatment of BC.
-
-\begin{figure}
-    \centering
-    \includegraphics{grid_study_1d1f.eps}
-    \caption{Grid convergence study for solutions for $\lambda = 10^{-2}$ at $T = 0.0003$. The reference solution is generated by simulation with $N = 16385$. The rate of convergence is roughly 0.5.}
-    \label{fig:grid_study_1d1f}
-\end{figure}
-\begin{figure}
-    \centering
-    \includegraphics{grid_study_field_1d1f.eps}
-    \caption{Comparison of solutions generated by meshes of different sizes. The solutions are computed for $\lambda = 0.01$ at $t=0.0005$.}
-    \label{fig:grid_study_field_1d1f}
-\end{figure}
-\begin{figure}
-    \centering
-    \includegraphics[scale=1]{lambdas_1d1f.eps}
-    \caption{1D one-fluid case of $\lambda = 1, 10^{-2}, 10^{-4}, 0$ at $t = 0.0005$ with $N = 10^3$.}
-    \label{fig:lambdas_1d1f}
-\end{figure}
-\begin{figure}
-    \centering
-    \includegraphics[scale=0.4]{lambdas_ref_1d1f.png}
-    \caption{Results of \cite{degond_2012} at $T = 0.0005$ with $N = 10^3$. }
-    \label{fig:lambdas_ref_1d1f}
-\end{figure}
-
-\section{Two-fluid model} \label{sec:two_fluid_model}
-\subsection{Governing equations in 1D} \label{sec:1d_two_fluid_equations}
-Compared to one-fluid model, in two-fluid model the motion of ions is taken into account through one more set of fluid equations. The rescaled two-fluid Euler-Maxwell system reads
-\begin{align*}
-    \partial_t n_i + \nabla\cdot(n_i \mathbf{u}_i) &= 0, \\
-    \partial_t (n_i \mathbf{u}_i) + \nabla \cdot (n_i \mathbf{u}_i \otimes \mathbf{u}_i) + \nabla p(n_i) &= n_i(\mathbf{E} + \mathbf{u}_i \times \mathbf{B}),\\
-    \partial_t n_e + \nabla\cdot(n_e \mathbf{u}_e) &= 0, \\
-    \varepsilon^2[\partial_t (n_e \mathbf{u}_e) + \nabla \cdot (n_e \mathbf{u}_e \otimes \mathbf{u}_e)] + \nabla p(n_e) &= -n_e(\mathbf{E} + \mathbf{u}_e \times \mathbf{B}),\\
-    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0. \\
-    \lambda^2 \partial_t\mathbf{E} - \nabla \times \mathbf{B} &= -(n_i \mathbf{u}_i - n_e \mathbf{u}_e),\\
-    \nabla\cdot \mathbf{B} &= 0, \\
-    \lambda^2 \nabla\cdot \mathbf{E} &= n_i - n_e,
-\end{align*}
-
-Following the same assumption as Section \ref{sec:1f-eqs-1d} and supplementing the mass and momentum equations for ions, we obtain the two-fluid Euler-Maxwell system in 1D:
-\begin{align*}
-    \partial_t n_i + \partial_z(n_i u_{iz}) &= 0, \\
-    \partial_t(n_i u_{ix}) + \partial_z(n_i u_{iz} u_{ix}) &= n_i(E_x - u_{iz} B_y), \\
-    \partial_t(n_i u_{iz}) + \partial_z(n_i u_{iz}^2 + P(n_i)) &= n_i(E_z + u_{ix} B_y), \\
-    \partial_t n_e + \partial_z(n_e u_{ez}) &= 0, \\
-    \varepsilon^2 [ \partial_t(n_e u_{ex}) + \partial_z(n_e u_{ez} u_{ex}) ] &= - n_e(E_x - u_{ez} B_y), \\
-    \varepsilon^2 [ \partial_t(n_e u_{ez}) + \partial_z(n_e u_{ez}^2) ] + \partial_z(P(n_e)) &= -n_e(E_z + u_{ex} B_y), \\
-    \partial_t B_y + \partial_z E_x &= 0, \\
-    \lambda^2 \partial_t E_x + \partial_z B_y &= n_e u_{ex} - n_i u_{ix}, \\
-    \lambda^2 \partial_t E_z &= n_e u_{ez} - n_i u_{iz}, \\
-    \lambda^2 \partial_z E_z &= n_i - n_e,
-\end{align*}
-where the subscript $i$ and $e$ represent ion and electron variables respectively.
-
-The discretization follows the same principle as illustrated in Section \ref{sec:1f1d-discretization} and thus is omitted here.
-
-\subsection{Numerical results} \label{sec:1d_two_fluid_numerical_results}
-The same case as the previous one is tested here. The initial condition remains unchanged for electron variables and electromagnetic fields. Additionally, for ion variables, we set
-\begin{align*}
-    n_i(z,0) = 1, \ \ u_{ix}(z,0) = u_{iz}(z,0) = 0, 
-\end{align*}
-namely, the ion is uniform and at rest at the initial time.
-\begin{figure}
-    \centering
-    \includegraphics{grid_study_field_1d2f.eps}
-    \caption{Comparison of solutions generated by meshes of different sizes. The solutions are computed for $\lambda = 0.01$ at $t = 5 \times 10^{-4}$.}
-    \label{fig:grid_study_field_1d2f}
-\end{figure}
-\begin{figure}
-    \centering
-    \includegraphics[scale=1]{lambdas_1d2f.eps}
-    \caption{1D two-fluid case of $\lambda = 1, 10^{-2}, 10^{-4}, 0$ at $t = 5\times10^{-4}$ with $N = 10^3$.}
-    \label{fig:lambdas_1d2f}
-\end{figure}
-\begin{figure}
-    \centering
-    \includegraphics[scale=0.45]{lambdas_ref_1d2f_1.png}
-    \includegraphics[scale=0.45]{lambdas_ref_1d2f_2.png}
-    \caption{Results of \cite{degond_2012} at $t = 5\times10^{-4}$ with $N = 10^3$.}
-    \label{fig:lambdas_ref_1d2f}
-\end{figure}
-
-For the sake of verification, the convergence of certain quantities as the mesh being refined is demonstrated in Fig.
-\ref{fig:grid_study_field_1d2f} for $\lambda = 0.01$.
-Results of the same resolution ($N = 10^4$) with different $\lambda$ are shown in Fig.
-\ref{fig:lambdas_1d2f}.
-As reference, results in \cite{degond_2012} are shown in Fig.
-\ref{fig:lambdas_ref_1d2f}.
-They almost\footnote{Obviously, electron momentum when $\lambda = 10^{-4}$ in Fig.
-\ref{fig:lambdas_ref_1d2f} is incorrect since electron and ion momentum are supposed to be equal in quasi-neutral limit} coincide.
-Besides, the case corresponding to $\lambda = 0$ provided in Fig.
-\ref{fig:lambdas_1d2f} shows consistency with the quasi-neutral condition $n_i = n_e$ and $n_eu_{ez} = n_iu_{iz}$.
-
-\section{Two-fluid model with collision term} \label{sec:1d2f_coll}
-\subsection{Governing equations}
-As one step further towards a more realistic model, we take into account the collision between electrons and ions by including the friction term (\ref{equ:collision_rescaled}).
-The inclusion of collision term leads to the equations
-\begin{align*}
-    \partial_t n_i + \nabla\cdot(n_i \mathbf{u}_i) &= 0, \\
-    \partial_t (n_i \mathbf{u}_i) + \nabla \cdot (n_i \mathbf{u}_i \otimes \mathbf{u}_i) + \nabla p(n_i) &= n_i(\mathbf{E} + \mathbf{u}_i \times \mathbf{B}) + \colorbox{orange!20}{$\alpha^\text{coll} n_en_i(\mathbf{u}_i - \mathbf{u}_e)$},\\
-    \partial_t n_e + \nabla\cdot(n_e \mathbf{u}_e) &= 0, \\
-    \varepsilon^2[\partial_t (n_e \mathbf{u}_e) + \nabla \cdot (n_e \mathbf{u}_e \otimes \mathbf{u}_e)] + \nabla p(n_e) &= -n_e(\mathbf{E} + \mathbf{u}_e \times \mathbf{B}) + \colorbox{orange!20}{$\alpha^\text{coll}  n_en_i(\mathbf{u}_e - \mathbf{u}_i)$},\\
-    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0. \\
-    \lambda^2 \partial_t\mathbf{E} - \nabla \times \mathbf{B} &= -(n_i \mathbf{u}_i - n_e \mathbf{u}_e),\\
-    \nabla\cdot \mathbf{B} &= 0, \\
-    \lambda^2 \nabla\cdot \mathbf{E} &= n_i - n_e,
-\end{align*}
-where $\alpha^\text{coll}$ is the dimensionless prefactor and we treat it as a pre-defined parameter.
-
-In our 1D setting, the governing equations become
-\begin{align*}
-    \partial_t n_i + \partial_z(n_i u_{iz}) &= 0, \\
-    \partial_t(n_i u_{ix}) + \partial_z(n_i u_{iz} u_{ix}) &= n_i(E_x - u_{iz} B_y) + \colorbox{orange!20}{$\alpha^\text{coll} n_e n_i (u_{ex} - u_{ix})$}, \\
-    \partial_t(n_i u_{iz}) + \partial_z(n_i u_{iz}^2 + P(n_i)) &= n_i(E_z + u_{ix} B_y) + \colorbox{orange!20}{$\alpha^\text{coll} n_e n_i (u_{ez} - u_{iz})$}, \\
-    \partial_t n_e + \partial_z(n_e u_{ez}) &= 0, \\
-    \varepsilon^2 [ \partial_t(n_e u_{ex}) + \partial_z(n_e u_{ez} u_{ex}) ] &= - n_e(E_x - u_{ez} B_y) + \colorbox{orange!20}{$\alpha^\text{coll} n_e n_i (u_{ix} - u_{ex})$}, \\
-    \varepsilon^2 [ \partial_t(n_e u_{ez}) + \partial_z(n_e u_{ez}^2) ] + \partial_z(P(n_e)) &= -n_e(E_z + u_{ex} B_y) + \colorbox{orange!20}{$\alpha^\text{coll} n_e n_i (u_{iz} - u_{ez})$}, \\
-    \partial_t B_y + \partial_z E_x &= 0, \\
-    \lambda^2 \partial_t E_x + \partial_z B_y &= n_e u_{ex} - n_i u_{ix}, \\
-    \lambda^2 \partial_t E_z &= n_e u_{ez} - n_i u_{iz}, \\
-    \lambda^2 \partial_z E_z &= n_i - n_e.
-\end{align*}
-
-\subsection{Full discretization}
-The full discretization is merely the one used in the previous section plus implicit collision terms.
-The implicitness is owing to the stiffness incurred from the potentially large value of $\varepsilon^{-2}\alpha^\text{coll}$.
-\begin{align*}
-    \frac{n^{m+1}_{i,k} - n^m_{i,k}}{\delta^m} + \frac{\textcolor{blue}{f^{m+1/2}_{n_i,k+1/2} - f^{m+1/2}_{n_i,k-1/2}}}{h} &= 0, \\
-    \frac{(n_iu_{ix})^{m+1}_k - (n_iu_{ix})^m_k}{\delta^m} + \frac{f^{m}_{u_{ix},k+1/2} - f^{m}_{u_{ix},k-1/2}}{h} &= n^m_{i,k}( \textcolor{blue}{E^{m+1}_{x,k}} - u^m_{iz,k}\Tilde{B}^m_{y,k}) \\
-    & + \colorbox{orange!20}{$\alpha^\text{coll} \left[n^m_{i,k}\textcolor{blue}{(n_eu_{ex})^{m+1}_k} - n^m_{e,k}\textcolor{blue}{(n_iu_{ix})^{m+1}_k}\right]$},\\
-    \frac{(n_iu_{iz})^{m+1}_k - (n_iu_{iz})^m_k}{\delta^m} + \frac{f^{m}_{u_{iz},k+1/2} - f^{m}_{u_{iz},k-1/2}}{h} &= n^m_{i,k}(\textcolor{blue}{\Tilde{E}^{m+1}_{z,k}} + u^m_{ix,k}\Tilde{B}^m_{y,k}) \\
-    & + \colorbox{orange!20}{$\alpha^\text{coll} \left[n^m_{i,k}\textcolor{blue}{(n_eu_{ez})^{m+1}_k} - n^m_{e,k}\textcolor{blue}{(n_iu_{iz})^{m+1}_k}\right]$},\\
-    \frac{n^{m+1}_{e,k} - n^m_{e,k}}{\delta^m} + \frac{\textcolor{blue}{f^{m+1/2}_{n_e,k+1/2} - f^{m+1/2}_{n_e,k-1/2}}}{h} &= 0,  \\
-    \varepsilon^2\frac{(n_eu_{ex})^{m+1}_k - (n_eu_{ex})^m_k}{\delta^m} + \frac{f^{m}_{u_{ex},k+1/2} - f^{m}_{u_{ex},k-1/2}}{h} &= - n^m_{e,k}( \textcolor{blue}{E^{m+1}_{x,k}} - u^m_{ez,k}\Tilde{B}^m_{y,k}) \\
-    & - \colorbox{orange!20}{$\alpha^\text{coll} \left[n^m_{i,k}\textcolor{blue}{(n_eu_{ex})^{m+1}_k} - n^m_{e,k}\textcolor{blue}{(n_iu_{ix})^{m+1}_k}\right]$},\\
-    \varepsilon^2\frac{(n_eu_{ez})^{m+1}_k - (n_eu_{ez})^m_k}{\delta^m} + \frac{f^{m}_{u_{ez},k+1/2} - f^{m}_{u_{ez},k-1/2}}{h} &= - n^m_{e,k}(\textcolor{blue}{\Tilde{E}^{m+1}_{z,k}} + u^m_{ix,k}\Tilde{B}^m_{y,k}) \\
-    & - \colorbox{orange!20}{$\alpha^\text{coll} \left[n^m_{i,k}\textcolor{blue}{(n_eu_{ez})^{m+1}_k} - n^m_{e,k}\textcolor{blue}{(n_iu_{iz})^{m+1}_k}\right]$},\\    
-    \frac{B^{m+1}_{y,k+1/2} - B^{m}_{y,k+1/2}}{\delta^m} + \frac{\textcolor{blue}{E^{m+1}_{x,k+1} - E^{m+1}_{x,k}}}{h} &= 0, \\
-    \lambda^2 \frac{E^{m+1}_{x,k} - E^{m}_{x,k}}{\delta^m} + \frac{\textcolor{blue}{B^{m+1}_{y,k+1/2} - B^{m+1}_{y,k-1/2}}}{h} &= \textcolor{blue}{(n_eu_{ex})^{m+1}_k - (n_iu_{ix})^{m+1}_k}, \\
-    \lambda^2 \frac{E^{m+1}_{z,k+1/2} - E^{m}_{z,k+1/2}}{\delta^m} &= \textcolor{blue}{f^{m+1}_{n_e,k+1/2} - f^{m+1}_{n_i,k+1/2}}. \\
-\end{align*}
-
-\subsection{Numerical results}
-We set the friction coefficient $\alpha^\text{coll} = 644$, and stick to the previous initial condition
-\begin{align*}
-    & n_e(z,0) = n_i(z,0) = 1,\\
-    & u_{ez}(z,0) = u_{iz}(z,0) = \chi_{[-0.1,0]}(z) - \chi_{[0,0.1]}(z), \\
-    & u_{ex}(z,0) = u_{ix}(z,0) = B_y(z,0) = E_x(z,0) = E_z(z,0) = 0.
-\end{align*}
-The case with a cell number $N = 1000$ and terminal time $t_{\text{end}} = 0.02$ is tested for $\lambda = 1, 10^{-2}, 10^{-4}, 0$.
-The number densities and momenta of ions and electrons are shown in Fig.
-\ref{fig:lambdas_1d2fc}.
-\begin{figure}
-    \centering
-    \includegraphics{lambdas_1d2fc_const.eps}
-    \caption{1D two-fluid case with friction terms. Results for $\lambda = 1, 10^{-2}, 10^{-4}, 0$ at $t = 0.02$ with $N = 1000$.}
-    \label{fig:lambdas_1d2fc}
-\end{figure}
-\begin{figure}
-    \centering
-    \includegraphics{grid_study_field_1d2fc.eps}
-    \caption{Comparison of solutions generated by meshes of different sizes. The solutions are computed for $\lambda = 10^{-4}$ at $t = 0.02$.}
-    \label{fig:grid_study_field_1d2fc}
-\end{figure}
-With decreasing $\lambda$, as expected, the densities and $z$-momenta of ion and electron gradually approach each other.
-However, when $\lambda = 10^{-4}$, spurious spikes exist at the discontinuity of electron momentum field and can be diminished by refining the mesh, as is shown in Fig.
-\ref{fig:grid_study_field_1d2fc} which also manifests the convergence with respect to the mesh refinement.
-\section{Summary}
-We have verified the AP scheme proposed in \cite{degond_2012} by reproducing the numerical solutions of one-fluid and two-fluid Euler-Maxwell systems in 1D.
-Besides, it is also ensured that the inclusion of friction term does not undermine the AP property.
-To summarize, the scheme works uniformly for $\lambda \in [0,1]$ in the sense that no instability occurs and the transition of different regimes is smooth.
-Within expect, the quasi-neutral condition $n_i = n_e$ is observed for the limiting case.
-
-In the sequel, the performance of the AP scheme on problems in 3D is to be checked.
-It expects to pose more challenges due to the boundary treatment in FIT and the inherently more complex 3D structures of Maxwell's equations.
-
-\chapter{Numerical Experiments in 3D} \label{chap:numerical_experiments_in_3d}
-
-In the previous chapter, we have gone through problems in a 1D setting, and have conveyed the basic idea of simulating plasma by AP schemes.
-As Maxwell's equations are inherently 3D, doing simulations in 3D is essential to gain realistic results.
-
-We test the AP scheme on a case that is adapted\footnote{Keeping the geometry and BCs being unchanged, we remove the enclosing solid dielectric domain such that the plasma domain coincides with the electromagnetic domain.
-The reason is illustrated in Section \ref{sec:impact_insulating_domain}.} from the one used in \cite[][chap.
-1 sec.
-4]{fuchs_2021}---a cylindrical tube filled with plasmas and applied external potentials on both ends.
-
-In this chapter, a description of the problem is first given, including the domain geometry and boundary conditions.
-Considerable words are devoted to the enforcement of BCs as well as their well-posedness from an algebraic perspective.
-Afterward, we elaborate on the procedure of time-stepping, especially the assembling of the linear system.
-The validity of such a linear system over arbitrary $\lambda$ is critical for attaining the AP property.
-
-Instead of directly cutting to the fully-coupled system, we first test the behavior of the scheme on the subsystems of the Euler-Maxwell system as verification.
-Finally, we present the numerical results of the fully-coupled Euler-Maxwell system, on which the AP property is to be verified.
-
-\section{Problem description and mesh generation} \label{sec:problem_description}
-The problem setting is a cylindrical domain filled with plasma fluids, and with two electrodes on each end, as is sketched in Fig.
-\ref{fig:sketch_domain}.
-From the viewpoint of the Euler system, the cylinder is enclosed by a non-penetrating wall whereas the plasma fluids are allowed to inflow and outflow through the electrode surfaces.
-Regarding the Maxwell system, external electric potentials are applied on the electrodes, and the enclosing boundary is considered insulating.
-
-Under such a setting, the motions of charged particles of the plasma are driven by the external potential, giving rise to an electromagnetic field, which in turn exerts Lorentz force on the charged particles.
-This setting is intended for simulating electric arcs.
-
-We discretize the spatial domain by an unstructured mesh doublet ($\mathcal{M}, \Tilde{\mathcal{M}}$) which consists of prisms aligned with the axial direction.
-The mesh generation is realized by the code developed in \cite{fuchs_2021}.
-The detailed algorithm is omitted.
-In principle, a circle is first discretized with a 2D mesh which afterward is extended along the axial direction to form the 3D mesh.
-Based on the generated primal mesh, a dual mesh conforming to the duality requirements, as is illustrated in Section \ref{sec:mesh_duality}, can be constructed with additional attention on the cut-off boundary that is discussed in Section \ref{sec:boundary_treatment}.
-An example of the primal and dual meshes is shown in Fig.
-\ref{fig:primal_dual_meshes}.
-
-\begin{figure}
-    \centering
-    \begin{tikzpicture}
-    \coordinate (O1) at (0,0);
-    \draw[very thick] (O1) circle (1) node {Cathode};
-    \fill[blue, opacity=0.2] (O1) circle (1);
-    \draw[very thick] (O1) circle (1.5);
-    \coordinate (O2) at (4.5,1) ;
-    \draw[gray] (O2) circle (1);
-    \node at (O2) {Anode};
-    \node at (barycentric cs:O1=1,O2=1) {Plasma}; 
-    \fill[red, opacity=0.2] (O2) circle (1);
-    \coordinate (S1) at ([shift={(-0.196,0.98)}]O1);
-    \coordinate (S2) at ([shift={(-0.196,0.98)}]O2);
-    \coordinate (P1) at ([shift={(0.196,-0.98)}]O1);
-    \coordinate (P2) at ([shift={(0.196,-0.98)}]O2);
-    \coordinate (SS1) at ([shift={({-0.196*1.5},{0.98*1.5})}]O1);
-    \coordinate (SS2) at ([shift={({-0.196*1.5},{0.98*1.5})}]O2);
-    \coordinate (PP1) at ([shift={({0.196*1.5},{-0.98*1.5})}]O1);
-    \coordinate (PP2) at ([shift={({0.196*1.5},{-0.98*1.5})}]O2);
-    \draw[very thick] (SS1) -- (SS2);
-    \draw[very thick] (PP1) -- (PP2); 
-    \draw[gray] (SS2) arc (101.31:180+101.31:1.5);
-    \draw[very thick] (PP2) arc (101.31-180:101.31:1.5);
-    \begin{scope}[shift={(5.5,-1.4)}]
-    \draw[blue, -to] (0,0) -- (0.65,0.12) node[right]{\small $z$};
-    \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
-    \draw[blue, -to] (0,0) -- (0.7,0) node[below]{\small $y$};
-    \end{scope}
-    \end{tikzpicture}
-    \caption{Sketch of the computational domain: a cylinder filled with plasma and with two electrodes at the ends.}
-    \label{fig:sketch_domain}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[scale=0.4]{primal_mesh.png}
-    \hspace{2cm}
-    \includegraphics[scale=0.4]{dual_mesh.png}
-    \caption{Primal (left) and dual (right) meshes used for the 3D testing case. They are generated by the code developed in \cite{fuchs_2021}.}
-    \label{fig:primal_dual_meshes}
-\end{figure}
-
-\section{Boundary conditions} \label{sec:numerical_experiement_bc}
-
-\begin{figure}
-    \centering
-    \begin{tikzpicture}
-        \coordinate (A1) at (0,1.5);
-        \coordinate (A2) at (0,1);
-        \coordinate (A3) at (0,-1);
-        \coordinate (A4) at (0,-1.5);
-        \coordinate (B1) at (6,1.5);
-        \coordinate (B2) at (6,1);
-        \coordinate (B3) at (6,-1);
-        \coordinate (B4) at (6,-1.5);
-        \draw[very thick] (A2) -- (A1) -- node[above]{$\Gamma_I$} (B1) -- (B2);
-        \draw[very thick] (A3) -- (A4) -- node[below]{$\Gamma_I$} (B4) -- (B3);
-        \draw[very thick, blue] (A2) -- node[left]  {$\Gamma_-$}  (A3);
-        \draw[very thick, red]  (B2) -- node[right] {$\Gamma_+$}  (B3);
-        \node at (3,0) {$\Omega$};
-    \end{tikzpicture}
-    \begin{tikzpicture}
-        \coordinate (A1) at (0,1.5);
-        \coordinate (A2) at (0,1);
-        \coordinate (A3) at (0,-1);
-        \coordinate (A4) at (0,-1.5);
-        \coordinate (B1) at (6,1.5);
-        \coordinate (B2) at (6,1);
-        \coordinate (B3) at (6,-1);
-        \coordinate (B4) at (6,-1.5);
-        \draw[very thick] (A2) -- (A1) -- node[above]{$\nabla \times \mathbf{H}\cdot \mathbf{n} = 0$, reflective wall}  node[below, gray]{$\nabla \times \mathbf{E} \cdot \mathbf{n} = 0$ on the whole boundary} (B1) -- (B2);
-        \draw[very thick] (A3) -- (A4) -- node[below]{$\nabla \times \mathbf{H}\cdot \mathbf{n} = 0$, reflective wall} (B4) -- (B3);
-        \draw[very thick, dashed, blue] (A2) -- node[left, yshift=0.3cm] {$\varphi^-(t)$} node[left, yshift=-0.3cm] {\textcolor{black}{open}} (A3);
-        \draw[very thick, dashed, red]  (B2) -- node[right, yshift=0.3cm]  {$\varphi^+(t)$} node[right, yshift=-0.3cm] {\textcolor{black}{open}}  (B3);
-        \node at (3,0) {\textbf{Plasma}};
-        \begin{scope}[shift={(6.5,-1.6)}]
-        \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
-        \draw[blue, -to] (0,0) -- (0.7,0) node[right]{\small $z$};
-        \end{scope}
-    \end{tikzpicture}
-    \caption{Illustration of the boundary conditions: (left) notation of each part of the boundary; (right) boundary conditions at each part of the boundary.}
-    \label{fig:bc}
-\end{figure}
-
-Before presenting the BCs, we notate the different parts of the computational domain.
-The whole domain is $\Omega \subset \mathbb{R}^3$ consisting of the interior $\Omega^\circ$ and boundary $\partial \Omega := \Gamma$.
-The cathode and anode are modeled by a 2D surface without thickness and thus lie on the boundary.
-They are notated $\Gamma_-$ and $\Gamma_+$ respectively.
-The rest of the boundary $\Gamma_I := \Gamma \backslash (\Gamma_- \cup \Gamma_+)$ is the insulating boundary.
-These are visualized in Fig.
-\ref{fig:bc} (left).
-
-We would like to stress that the boundary of the plasmas domain, namely the domain where the Euler equations are defined, coincides with the artificial truncation for the electromagnetic field.
-
-For Maxwell's equations, we adopt the so-called \emph{ECE boundary conditions} in the sense that 1) at the electrodes electric potentials $\varphi^-(t)$ and $\varphi^+(t)$ are enforced externally
-; 2) the tangential $\mathbf{E}$-field is curl-free on $\Gamma$; 3) the tangential $\mathbf{H}$-field is curl-free at $\Gamma_I$.
-
-For the Euler system, the wall boundary is considered \emph{reflective} and requires vanishing normal velocity.
-At $\Gamma_+$ and $\Gamma_-$ where the electrodes lie, we stick to \cite{fuchs_2021}, and employ the \emph{open} BC, allowing the fluids to freely pass in the sense of zero gradients of the fluid quantities.
-
-Since the electrons and ions cannot penetrate the reflective wall, the orthogonal current vanishes on $\Gamma_I$.
-By Amp\`{e}re's law (\ref{equ:maxwell_ampere_rescaled}) the insulating BC $\text{curl}\mathbf{H} \cdot \mathbf{n} = 0$ is equivalent to $\mathbf{D}\cdot\mathbf{n} = 0$ provided $\mathbf{D}\cdot\mathbf{n} = 0$ is satisfied at the initial time.
-To study the asymptotic behavior of the system, the latter one is suitable and thus is actually adopted because of the reason discussed in Section \ref{sec:impact_of_bc}.
-
-To summarize, 
-\begin{align}
-    \varphi &= \varphi^-(t)\ \ \text{on} \ \ \Gamma_-, \label{equ:bc_1}\\
-    \varphi &= \varphi^+(t)\ \ \text{on} \ \ \Gamma_+, \label{equ:bc_2}\\
-    \text{curl} \mathbf{E} \cdot \mathbf{n} &= 0\ \ \text{on} \ \  \Gamma_I,  \label{equ:bc_3}\\
-    \text{curl} \mathbf{H} \cdot \mathbf{n} = 0 \Leftrightarrow \mathbf{D} \cdot \mathbf{n} &= 0\ \  \text{on} \ \  \Gamma_I, \label{equ:bc_4}\\
-    \mathbf{u_*}\cdot \mathbf{n} &= 0 \ \ \text{on} \ \ \Gamma_I, \label{equ:bc_5}\\
-    \text{grad}\mathbf{U_*} \cdot \mathbf{n} &= \mathbf{0} \ \ \text{on} \ \ \Gamma_+\cup\Gamma_-. \label{equ:bc_6}
-\end{align}
-where $\mathbf{n}$ denotes the outer normal vector. Recall that $\mathbf{u}_*$ and $\mathbf{U}_*$ denotes the velocity and conservative fluid quantities of species $*$.
-
-To verify that the BCs lead to a well-posed problem, especially for Maxwell's equations\footnote{The BCs for the Euler system are rather classical.
-See \cite[][Chap.
-7]{leveque_2002} for a general introduction, or \cite[][sec.
-2e]{mishra_2019b} for the specific implementation for the Euler equations.}, we want to check that these BCs in the discrete level lead to a solvable linear system.
-A \emph{necessary} condition is that \emph{the number of unknown variables and the number of (independent) algebraic equations coincide}.
-
-We would like to remark that the time-stepping for Euler equations (\ref{equ:euler_ap}) do not involve solving any linear system since the implicit mass term in (\ref{equ:flux_ap}) can be obtained through the momentum equations.
-As for the implicit term $\mathbf{E}^{m+1}$ in the source term (\ref{equ:rhs_ap}), it is obtained through updating the Maxwell system.
-Therefore, only the evolution of the Maxwell system entails solving a linear system, whose validity is discussed here.
-
-First, a meticulous classification and counting for facets of meshes are done as follows:
-\begin{align*}
-    \#\  \text{primal cell}\ \  &N_V \\
-    \#\  \text{primal edge}\ \  &N_L := \underbrace{N^+_L + N^-_L + N^I_L}_{N^\partial_L} + N^\circ_L  \\
-    \#\  \text{primal face}\ \  &N_A := \underbrace{N_A^+ + N_A^- + N^I_A}_{N^\partial_A} + N^\circ_A  \\
-    \#\  \text{primal vertex}\ \  &N_P := \underbrace{N_P^+ + N_P^- + N^I_P}_{N^\partial_P} + N^\circ_P \\
-    \#\  \text{dual cell}\ \  &N_{\Tilde{V}} := N_p \\
-    \#\  \text{dual edge}\ \  &N_{\Tilde{L}} := \underbrace{N^\partial_{\Tilde{L}}}_{=N^\partial_L} + \underbrace{N^\circ_{\Tilde{L}}}_{=N_A} \\
-    \#\  \text{dual face}\ \  &N_{\Tilde{A}} := \underbrace{N^\partial_{\Tilde{A}}}_{=N^\partial_P} + \underbrace{N^\circ_{\Tilde{A}}}_{=N_L}
-\end{align*}
-where the superscripts indicate the domains to which facets belong to, and $+,-,I,\circ,\partial$ represent $\Gamma_+, \Gamma_-, \Gamma_I, \Omega^\circ, \partial \Omega$ respectively.
-As is discussed in Section \ref{sec:boundary_treatment}, auxiliary dual facets are needed to trim $\Tilde{\mathcal{M}}$ such that $\mathcal{M}$ and $\Tilde{\mathcal{M}}$ share the same boundary.
-By inspecting Fig.
-\ref{fig:illustraion_dual_boundary}, one can realize that the auxiliary dual edges have the same number as the primal boundary edges since they intersect with each other; the auxiliary dual faces have the same number as the primal boundary vertices.
-These amount to $N^\partial_{\Tilde{L}} = N^\partial_L, N^\partial_{\Tilde{A}} = N^\partial_P$.
-Note that these number relationships are attained on the premise that non-straight edges and non-flat faces are admissible.
-
-Next, we count the number of unknowns.
-From the BCs (\ref{equ:bc_1})(\ref{equ:bc_3})  we know that the tangential $\mathbf{E}$-field is irrotational at the whole boundary $\partial\Omega$, which allows a scalar potential function $\varphi$ on $\partial \Omega$ with $\text{grad}_\tau \varphi = \mathbf{E}_\tau$.
-In the discrete case, $\bm{\varphi}$ is a scalar vector whose entries are defined on each primal vertex on $\partial \Omega$.
-The collection of boundary electric voltage $\mathbf{e}^\partial$ is retrieved by $\mathbf{e}^\partial = \mathbb{G}_\partial \bm{\varphi}$ where $\mathbb{G}_\partial$ stands for the discrete grad operator on the boundary.
-Besides, additional dual edges and faces at boundary, to which the integrals of the $\mathbf{H}$-field and the $\mathbf{D}$-field are assigned, give rise to unknown $\mathbf{h^\partial}$ and $\mathbf{d^\partial}$ vectors of sizes $N^\partial_{\Tilde{L}}$ and $N^\partial_{\Tilde{A}}$.
-The counting of unknown variables is as follows:
-\begin{equation*}
-    |\mathbf{e}| = N_L, \ \ \ |\mathbf{b}|=N_A, \ \ \ |\mathbf{h}^\partial|=N^\partial_{\Tilde{L}},\ \ \ |\mathbf{d}^\partial| = N^\partial_{\Tilde{A}}, \ \ \ |\bm{\varphi}| = N^\partial_P,
-\end{equation*}
-where $|\cdot|$ denotes the size of vector.
-
-Lastly, we collect all the algebraic equations derived from the Maxwell system.
-The coupling term $\mathbf{j}^{m+1}$ in discrete Ampere's law (\ref{equ:maxwell_ampere_ap}) can be rewritten by electric variables, which will be demonstrated in (\ref{equ:tmp5})(\ref{equ:tmp6}) at the next section.
-The discrete Faraday's law (\ref{equ:maxwell_faraday_ap}) updates the scalar vector $\mathbf{b}$ which is composed of integrals of $\mathbf{B}$-field on each primal face; the discrete Amp\`{e}re's law (\ref{equ:maxwell_ampere_ap}) updates $\mathbf{d}$ which is composed of integrals of $\mathbf{D}$-field on each dual face; the relation $\mathbf{e}^\partial = \mathbb{G}_\partial \bm{\varphi}$ entails $N^\partial_L$ equations each of which is defined on a boundary primal edge; the entries of $\bm{\varphi}$ that locate on the electrodes are assigned externally; the insulating BC (\ref{equ:bc_4}) needs to be satisfied at each dual face that lies in $\Gamma_I$.
-In summary, the counting of algebraic equations is as follows:
-\begin{align*}
-    \text{discrete Faraday law (\ref{equ:maxwell_faraday_ap})} \ \ &\longrightarrow\ \  N_A \ \ \text{equations} \\
-    \text{discrete Ampere law (\ref{equ:maxwell_ampere_ap})} \ \ &\longrightarrow\ \  N_{\Tilde{A}} \ \ \text{equations} \\
-     \mathbf{E}_\tau = \text{grad}_\tau \varphi \Rightarrow \mathbf{e}^\partial = \mathbb{G}_\partial \bm{\varphi} \ \ &\longrightarrow\ \  N^\partial_L \ \ \text{equations} \\
-    \text{enforced potentials}\ \ \varphi^+(t), \varphi^-(t) \ \ &\longrightarrow\ \  N_P^+ + N_P^- \ \ \text{equations} \\
-    \text{insulating BC (\ref{equ:bc_4})} \ \ &\longrightarrow\ \  N_{\Tilde{A}}^I = N_P^I \ \ \text{equations}.
-\end{align*}
-It is straightforward to check that the numbers of unknowns and the equations match. Specifically, 
-\begin{align*}
-    \#\text{ of unknowns} &= \colorbox{orange!20}{$N_L$} + \colorbox{blue!20}{$N_A$} + \colorbox{gray!20}{$N_{\Tilde{L}}^\partial$} + \colorbox{orange!20}{$N_{\Tilde{A}}^\partial$} + \colorbox{green!20}{$N_P^\partial$}, \\
-    \#\text{ of equations} &= \colorbox{blue!20}{$N_A$} + \colorbox{orange!20}{$N_{\Tilde{A}}$} + \colorbox{gray!20}{$N_L^\partial$} + \colorbox{green!20}{$N_P^+ + N_P^- + N_P^I$},
-\end{align*}
-where the terms with the same color can be equated by applying the counting relations listed above.
-
-However, the matching of numbers of unknowns and equations does not necessarily result in a valid linear system.
-Inappropriate BCs could cause the singularity of the linear system, as is discussed in Section \ref{sec:impact_of_bc}.
-
-\section{Procedure of time-stepping}
-In this section, we would like to present the concrete strategy to evolve the whole system, namely calculating variables at $t_{m+1}$ given their values at $t_m$.
-On one hand, the impact of BCs is not considered when presenting the AP scheme (\ref{equ:maxwell_faraday_ap}) to (\ref{equ:current_ap}).
-On the other hand, a clever and detailed strategy of establishing the linear system at every time step is necessary.
-
-To avoid any confusion, the definition of the quantities is repeated in Tab.
-\ref{tab:def_size_var}.
-For better illustration, matrices used in this section are supplemented with both superscript and subscript indicating the size.
-For instance, $\mathbb{C}^A_L$ indicates the discrete curl operator of size $N_A \times N_L$ with respect to primal faces and edges; $\Tilde{\mathbb{C}}^{A_I}_{\partial L}$ stands for the discrete curl operator of size $N_{\Tilde{A}}^{I} \times N_{\Tilde{L}}^\partial$ with respect to dual faces on $\Gamma_I$ and edges on $\partial \Gamma$.
-
-\begin{table}[]
-    \centering
-\begin{tabular}{c c c}
-     \hline
-     \textbf{Notation}  & \textbf{Meaning}  & \textbf{Size} \\
-     \hline
-     $\mathbf{e}$ & integral of $\mathbf{E}$-field at primal edges& $N_L$ \\
-     $\mathbf{e^\circ}$ & components of $\mathbf{e}$ lying in $\Omega^\circ$ & $N_L^\circ$ \\
-     $\mathbf{e^\partial}$ & components of $\mathbf{e}$ lying on $\partial \Omega$ & $N_L^\partial$ \\
-     $\mathbf{E}$ & cell average of $\mathbf{E}$-field for dual cells & $N_{\Tilde{V}}$ \\ 
-     $\bm{\varphi}$ & electric potentials at primal vertices & $N_P^\partial$ \\
-     $\bm{\varphi}^+$ & components of $\bm{\varphi}$ lying on $\Gamma^+$ & $N_P^+$ \\
-     $\bm{\varphi}^-$ & components of $\bm{\varphi}$ lying on $\Gamma^-$ & $N_P^-$ \\
-     $\mathbf{b}$ & integral of $\mathbf{B}$-field at primal faces & $N_A$ \\
-     $\mathbf{d}^\partial$ & integral of $\mathbf{D}$-field at boundary dual faces & $N_{\Tilde{A}}^\partial = N_P^\partial$ \\
-     $\mathbf{h}^\partial$ & integral of $\mathbf{H}$-field at boundary dual edges & $N_{\Tilde{L}}^\partial = N_L^\partial$ \\
-     $\mathbf{j}$ & current through dual faces & $N_{\Tilde{A}}$ \\
-     $\mathbf{j}^\circ$ & components of $\mathbf{j}$ lying in $\Omega^\circ$ & $N_{\Tilde{A}}^\circ$ \\
-     $\mathbf{j}^\partial$ & components of $\mathbf{j}$ lying on $\partial \Omega$ & $N_{\Tilde{A}}^\partial$ \\
-     \hline
-\end{tabular}
-    \caption{Definitions and sizes of scalar vectors for each quantity.}
-    \label{tab:def_size_var}
-\end{table}
-
-With extra quantities at boundary, the schemes (\ref{equ:maxwell_faraday_ap}) (\ref{equ:maxwell_ampere_ap}) turn into
-\begin{align}
-    \delta_m^{-1} (\mathbf{b}^{m+1} - \mathbf{b}^{m}) + \mathbb{C}_L^A\mathbf{e}^{m+1} \hspace{3.08cm}&= 0, \label{equ:tmp7}\\
-    \lambda^2\delta_m^{-1}\mathbb{M}_\varepsilon(\mathbf{e}^{m+1} - \mathbf{e}^m) - \Tilde{\mathbb{C}}_{L^\circ}^{A^\circ}\mathbb{M}_\mu^{-1}\mathbf{b}^{m+1} - \Tilde{C}^{A^\circ}_{\partial L} \mathbf{h}^{\partial, m+1} &= - \mathbf{j}^{\circ,m+1}, \label{equ:tmp8}\\
-     \lambda^2\delta_m^{-1}(\mathbf{d}^{\partial,m+1} - \mathbf{d}^{\partial, m}) - \Tilde{\mathbb{C}}^{\partial A}_{\partial L} \mathbf{h}^{\partial,m+1} \hspace{2.60cm}&= - \mathbf{j}^{\partial,m+1}.
-\label{equ:tmp9}
-\end{align}
-The equations (\ref{equ:tmp8}) (\ref{equ:tmp9}) arise due to the discrete Faraday law at $\Omega^\circ$ and on $\partial \Omega$.
-
-The discretized BCs (\ref{equ:bc_1}) to (\ref{equ:bc_4}) appear as
-\begin{align}
-    \mathbf{e}^{\partial,m} &= \mathbb{G}^{\partial L}_{\partial P} \bm{\varphi}^m, \label{equ:tmp10}\\
-    \begin{bmatrix}
-    \bm{\varphi}^+ \\
-    \bm{\varphi}^- 
-    \end{bmatrix}^m &= \mathbb{S}^{\pm}_{\partial P} \bm{\varphi}^m =
-    \begin{bmatrix}
-    \varphi^+(t_m) \\
-    \varphi^-(t_m) 
-    \end{bmatrix},\label{equ:tmp11}\\
-    \Tilde{\mathbb{S}}^{A_I}_{\partial A} \mathbf{d}^{\partial,m} &= 0, \label{equ:tmp12}
-\end{align}
-where $\mathbb{G}^{\partial L}_{\partial P}$ is the discrete gradient operator applied on $\partial \Omega$;
-$\mathbb{S}^{\pm}_{\partial P}$ is a matrix with entries $\in \{0,1\}$ responsible for selecting the potentials at $\Gamma^+$ and $\Gamma^-$; $\Tilde{\mathbb{S}}^{P_I}_{\partial P}$ is also a selecting matrix that picks dual faces on $\Gamma^I$ from those at $\partial\Omega$.
-
-With proper ordering of components in $\mathbf{e}$ and (\ref{equ:tmp10}), we derive all the edge voltages $\mathbf{e}$ from interior edge voltages $\mathbf{e}^\circ$ and boundary potentials $\bm{\varphi}$ through
-\begin{align*}
-    \mathbf{e}^m =
-    \begin{bmatrix}
-    \mathbf{e}^\circ \\ \mathbf{e}^\partial
-    \end{bmatrix}^m =
-    \underbrace{
-    \begin{bmatrix}
-    \mathbb{I} & 0 \\ 0 & \mathbb{G}^{\partial L}_{\partial P}
-    \end{bmatrix}}_{\mathbb{Q}_{L^\circ,\partial P}^{L}}
-    \begin{bmatrix}
-    \mathbf{e}^\circ \\ \bm{\varphi}
-    \end{bmatrix}^m.
-\end{align*}
-
-The last piece of the puzzle to be filled is the relation connecting $\mathbf{j}^{m+1}$ and the electrical quantities -- namely, a generalized Ohm's law\footnote{By ``generalized" we mean that it is merely a formula relating the current density and $\mathbf{E}$-field at the discrete model.
-There is no counterpart for the continuous model, and it is not the \emph{discretized} Ohm's law, either.} -- such that the linear system (\ref{equ:tmp7}) to (\ref{equ:tmp9}) can be closed and solved.
-The derivation of generalized Ohm's law resorts to the discrete Euler system (\ref{equ:euler_ap}).
-In the following, we provide the derivations for models with and without friction terms.
-
-\subsubsection{Model without friction}
-By the scheme (\ref{equ:euler_ap}) for the Euler equations, we get 
-\begin{equation} \label{equ:tmp1}
-    \left[(n\mathbf{u})_{*,k}\right]^{m+1} = \left[\delta_m \varepsilon^{-2}_* q_* n^m_{*,k}\mathbf{E}^{m+1}_k \right] + \underbrace{\left[(n\mathbf{u})_{*,k}\right]^{m} - \left[\frac{\delta_m}{|{\Tilde{V}}_k|}\sum_{j:\Tilde{A}_j\in\partial\Tilde{V}_k}|\Tilde{A}_j|\bm{f}^m_{u,*,j}\right] + \left[\delta_m \varepsilon^{-2}_* q_*(n\mathbf{u})^m_{*,k} \times \mathbf{B}^m_{k}\right]}_{\bm{\eta}^m_*}
-\end{equation}
-with $[\cdot]$ meaning packing the quantities into a vector. Recall the interpolation relation
-\begin{equation*}
-    \mathbf{E} = \Tilde{\mathbb{R}}^{V_f}_{A}
-    \begin{bmatrix}
-    \mathbf{e} \\
-    \mathbf{d}^\partial 
-    \end{bmatrix},
-    \ \ \ \ 
-    \mathbf{B} = \Tilde{\mathbb{R}}^{V_f}_{L}
-    \begin{bmatrix}
-    \mathbf{b} \\
-    \mathbf{h}^\partial 
-    \end{bmatrix},
-\end{equation*}
-with which (\ref{equ:tmp1}) is rewritten as
-\begin{equation} \label{equ:tmp2}
-    \left[(n\mathbf{u})_{*,k}\right]^{m+1} = \text{diag}(\delta_m \varepsilon^{-2}_* q_* n^m_{*,k}) \Tilde{\mathbb{R}}^{V_f}_{A} 
-    \begin{bmatrix}
-    \mathbf{e} \\
-    \mathbf{d}^\partial 
-    \end{bmatrix}^{m+1} + \bm{\eta}^m_*.
-\end{equation}
-Thanks to the linear nature of numerical flux (\ref{equ:flux_ap}), we can express the mass flux by linear operation 
-\begin{equation} \label{equ:tmp3}
-    \left[f_{n,*,j}\right]^{m+1} = \frac{1}{2} \Tilde{\mathbb{A}}_{V_f}^{A_f} :  \left[(n\mathbf{u})_{*,k}\right]^{m+1} - \frac{1}{2} [s_{*,j}]^m \odot \Tilde{\mathbb{D}}_{V_f}^{A_f} [n_{*,k}]^m,
-\end{equation}
-where $:$ represents two contraction, $\odot$ represents component-wise product.
-The meanings of 3-rank tensor $\Tilde{\mathbb{A}}_{V_f}^{A_f}$ and matrix $\Tilde{\mathbb{D}}_{V_f}^{A_f}$ should be self-explanatory by scrutinizing on its component-wise expression (\ref{equ:flux_ap}).
-We stress that the boundary conditions for the Euler equations are included in these two linear operators.
-
-Plug (\ref{equ:tmp2}) into (\ref{equ:tmp3}), and we get
-\begin{equation} \label{equ:tmp4}
-    \left[f_{n,*,j}\right]^{m+1} = \underbrace{\frac{1}{2} \Tilde{\mathbb{A}}_{V_f}^{A_f} : \text{diag}(\delta_m \varepsilon^{-2}_* q_* n^m_{*,k}) \Tilde{\mathbb{R}}^{V_f}_{A}}_{\Tilde{\mathbb{T}}_{A,*}^{A,m}}
-    \begin{bmatrix}
-    \mathbf{e} \\
-    \mathbf{d}^\partial 
-    \end{bmatrix}^{m+1} + \underbrace{\frac{1}{2}\Tilde{\mathbb{A}}_{V_f}^{A_f} :\bm{\eta}^m_* - \frac{1}{2} [s_{*,j}]^m \odot \Tilde{\mathbb{D}}_{V_f}^{A_f} [n_{*,k}]^m}_{\bm{\mu}^m_*}.
-\end{equation}
-
-\subsubsection{Two-fluid model with friction}
-We include the friction term (\ref{equ:collision_rescaled}).
-Adding friction terms would lead to extra complexity since they are discretized implicitly.
-For the sake of simplicity, only the two-fluid (electron-ion) model is tackled here.
-Following the same procedure as before, first, we need the discretized relation between momenta and $\mathbf{E}$-field.
-After lengthy calculation, we end up getting
-\begin{multline}\label{equ:tmp13}
-    [n\mathbf{u}_{i,k}]^{m+1} = \left[\frac{1 + \delta_m \alpha \varepsilon_e^{-2} n_{i,k}^m + \delta_m \alpha \varepsilon_e^{-2} \frac{q_e}{q_i}n_{e,k}^m }{1 + \delta_m \alpha (\varepsilon^{-2}_e n_{i,k}^m + \varepsilon_i^{-2} n_{e,k}^m)} \delta_m \varepsilon^{-2}_i q_i n_{i,k}^m \mathbf{E}^{m+1}_k\right] \\
-    + \left[\frac{\delta_m \alpha \varepsilon_i^{-2} n_{i,k}^m}{1 + \delta_m \alpha (\varepsilon^{-2}_e n_{i,k}^m + \varepsilon^{-2}_i n_{e,k}^m)}\right] \odot \bm{\eta}_e^m + \left[\frac{1 + \delta_m \alpha \varepsilon^{-2}_e n_{i,k}^m}{1 + \delta_m \alpha (\varepsilon^{-2}_e n_{i,k}^m + \varepsilon^{-2}_i n_{e,k}^m)}\right] \odot \bm{\eta}_i^m,
-\end{multline}
-where $\alpha$ is the friction coefficient, and $\bm{\eta}_e^m, \bm{\eta}_i^m$ are defined in (\ref{equ:tmp1}).
-Again by (\ref{equ:tmp3}) we derive the expression for mass fluxes in the same form as (\ref{equ:tmp4}).
-In this case,
-\begin{align}
-     \Tilde{\mathbb{T}}_{A, i}^{A, m} &= \frac{1}{2} \Tilde{\mathbb{A}}_{V_f}^{A_f} : \text{diag}\left(\frac{1 + \delta_m \alpha \varepsilon_e^{-2} n_{i,k}^m + \delta_m \alpha \varepsilon_e^{-2} \frac{q_e}{q_i}n_{e,k}^m }{1 + \delta_m \alpha (\varepsilon^{-2}_e n_{i,k}^m + \varepsilon_i^{-2} n_{e,k}^m)}\delta_m \varepsilon^{-2}_i q_i n^m_{i,k}\right) \Tilde{\mathbb{R}}^{V_f}_{A}, \label{equ:tmp14} \\
-     \bm{\mu}^m_i &= \frac{1}{2}\Tilde{\mathbb{A}}_{V_f}^{A_f} :\left(\left[\frac{\delta_m \alpha \varepsilon_i^{-2} n_{i,k}^m}{1 + \delta_m \alpha (\varepsilon^{-2}_e n_{i,k}^m + \varepsilon^{-2}_i n_{e,k}^m)}\right] \odot \bm{\eta}_e^m + \left[\frac{1 + \delta_m \alpha \varepsilon^{-2}_e n_{i,k}^m}{1 + \delta_m \alpha (\varepsilon^{-2}_e n_{i,k}^m + \varepsilon^{-2}_i n_{e,k}^m)}\right] \odot \bm{\eta}_i^m \right) \nonumber \\
-     &\hspace{10cm} - \frac{1}{2} [s_{i,j}]^m \odot \Tilde{\mathbb{D}}_{V_f}^{A_f} [n_{i,k}]^m. \label{equ:tmp15}
-\end{align}
-The counterpart of (\ref{equ:tmp14})(\ref{equ:tmp15}) for electron is straightforward by switching the subscript $e$ and $i$.
-Then the mass fluxes for different species remain the same as (\ref{equ:tmp4}), namely
-\begin{equation}
-    \left[f_{n,*,j}\right]^{m+1} = \Tilde{\mathbb{T}}_{A,*}^{A,m} 
-    \begin{bmatrix}
-    \mathbf{e} \\
-    \mathbf{d}^\partial 
-    \end{bmatrix}^{m+1} + \bm{\mu}^m_*.
-\end{equation}
-
-Now we have had the relation of the mass fluxes and the $\mathbf{E}$-field related quantities at $t_{m+1}$.
-By definition of the current density (\ref{equ:current_ap}) we end up with the expression for the generalized Ohm's law
-\begin{equation} \label{equ:tmp5}
-    \mathbf{j}^{m+1} = \sum_*q_*\text{diag}(|\Tilde{A}_j|)\left[f_{n,*,j}\right]^{m+1} = \underbrace{\sum_*q_*\text{diag}(|\Tilde{A}_j|) \Tilde{\mathbb{T}}_{A,*}^{A,m}}_{\mathbb{M}_\sigma^m} \begin{bmatrix}
-    \mathbf{e} \\
-    \mathbf{d}^\partial 
-    \end{bmatrix}^{m+1} + \underbrace{\sum_*q_*\text{diag}(|\Tilde{A}_j|) \bm{\mu}^m_*}_{\mathbf{j}^m_\text{aux}},
-\end{equation}
-The generalized Ohm's law (\ref{equ:tmp5}) is further split into
-\begin{equation} \label{equ:tmp6}
-    \mathbf{j}^{m+1} =
-    \begin{bmatrix}
-    \mathbf{j}^{\circ,m+1} \\
-    \mathbf{j}^{\partial, m+1}
-    \end{bmatrix} =
-    \begin{bmatrix}
-    \mathbb{M}_{\sigma,11}^m & \mathbb{M}_{\sigma,12}^m \\
-    \mathbb{M}_{\sigma,21}^m & \mathbb{M}_{\sigma,22}^m
-    \end{bmatrix}
-    \begin{bmatrix}
-    \mathbf{e} \\
-    \mathbf{d}^\partial 
-    \end{bmatrix}^{m+1} +
-    \begin{bmatrix}
-    \mathbf{j}^{\circ, m}_\text{aux} \\
-    \mathbf{j}^{\partial,m}_\text{aux}
-    \end{bmatrix}.
-\end{equation}
-Combine (\ref{equ:tmp7}) to (\ref{equ:tmp12}) and (\ref{equ:tmp6}), we end up with the assembled linear system
-\begin{multline} \label{equ:linear_system}
-    \begin{bNiceArray}{wc{4cm} wc{4cm} wc{2cm} c}[margin, hvlines,rules/color=blue]
-    \Block{1-2}{\left(\lambda^2\delta_m^{-1}\mathbb{M}_\varepsilon + \Tilde{\mathbb{C}}^{A^\circ}_{L^\circ}\mathbb{M}^{-1}_\mu \delta_m \mathbb{C}^A_L + \mathbb{M}^m_{\sigma,11}\right)\mathbb{Q}_{L^\circ,\partial P}^{L}} & & \Block{2-1}{-\Tilde{\mathbb{C}}^{A}_{\partial L}} & \mathbb{M}^m_{\sigma,12} \\
-    \Block{1-2}{\mathbb{M}^m_{\sigma,21}\mathbb{Q}_{L^\circ,\partial P}^{L}} & & & \lambda^2\delta_m^{-1}\mathbb{I} + \mathbb{M}^m_{\sigma,22} \\
-    0 & \mathbb{S}^{\pm}_{\partial P} & 0 & 0 \\
-    0 & 0 & 0 & \Tilde{\mathbb{S}}^{A_I}_{\partial A}
-    \end{bNiceArray}
-    \begin{bNiceArray}{c}
-    \mathbf{e}^\circ \\
-    \bm{\varphi}  \\
-    \mathbf{h}^\partial \\
-    \mathbf{d}^\partial 
-    \end{bNiceArray}^{m+1}  \\ =
-    \begin{bNiceArray}{c}
-    \lambda^2\delta_m^{-1}\mathbb{M}_\varepsilon\mathbf{e}^m + \Tilde{\mathbb{C}}^{A^\circ}_{L^\circ} \mathbb{M}^{-1}_\mu\mathbf{b}^m - \mathbf{j}^{\circ,m}_{\text{aux}} \\
-    \lambda^2\delta_m^{-1}\mathbf{d}^{\partial,m} - \mathbf{j}^{\partial,m}_\text{aux} \\
-    \bm{\varphi}^+(t_{m+1}) \\
-    \bm{\varphi}^-(t_{m+1}) \\
-    0 
-    \end{bNiceArray}
-\end{multline}
-As soon as $\mathbf{e}^{\circ,m+1}, \bm{\varphi}^{m+1}, \mathbf{h}^{\partial,m+1}, \mathbf{d}^{\partial,m+1}$ are available after solving the linear system, the fluid variables can be updated explicitly according to (\ref{equ:euler_ap}).
-To this point, the time-stepping is done.
-
-We would like to remark that the whole time-stepping procedure, although appears tedious, does not involve any tricky treatment.
-What is more important is that the formulation of the linear system helps us to identify problems incurring by the quasi-neutral limit.
-Upon setting $\lambda = 0$, we want to ensure that the square matrix at the left-hand side remains non-singular, which is indeed the case for our formulation.
-
-\section{Subsystem verification}
-Before running the fully-coupled Euler-Maxwell system, subsystems---the Euler solver and Maxwell solver---are separately tested such that we can take confidence in the correctness of the coupled system.
-The testing closely follows \cite{fuchs_2021}.
-
-\subsubsection{Sod shock tube}
-To begin with, we test the fluid solver on Sod shock tube, which is a commonly used case for benchmarking numerical schemes on the Euler equations.
-Although it is originally a 1D problem, we test it along the $z$-axis in our 3D setup.
-The result expects to be consistent with the reference solution because of the invariance at the spanwise directions.
-Fig.
-\ref{fig:sod_test} shows the results over different mesh sizes as well as the analytical solution \citep{isaac_2017} and indicates the right behavior.
-\begin{figure}
-    \centering
-    \includegraphics{sod_test.eps}
-    \caption{Comparison of results for Sod shock tube case over different mesh refinements and analytical solution. $N$ stands for the number of cells along $z$-axis.}
-    \label{fig:sod_test}
-\end{figure}
-\subsubsection{Uniform steady E-field}
-The electric field comes into play in this testing where we expose electrons and ions to the uniform steady E-field $(0,0,1)$, namely unit vector along $z$-axis.
-For simplicity, two species are assumed to be equal in mass.
-The magnetic field is set to zero.
-Collisions among the species are neglected.
-Initially being static, the electrons and ions expect to be accelerated along the $z$-axis in opposite directions while keeping the temperature unchanged.
-Fig.
-\ref{fig:uniform_e_test} shows the behavior we expect.
-To be noticed is that the temperature slightly decreases over time due to numerical error, and the error is mitigated with mesh refinement.
-\begin{figure}
-    \centering
-    \includegraphics{uniform_E_test.eps}
-    \caption{Result when a uniform background $\mathbf{E}$-field exists.
-The left figure shows the constant accelerations of electrons and ions.
-The right one indicates the slightly decreasing temperature due to numerical errors.}
-    \label{fig:uniform_e_test}
-\end{figure}
-
-\subsubsection{Step voltage on anode}
-In this case, we test the behavior of the Maxwell system when a step voltage is applied on the anode.
-Here we consider the domain to be dielectric and be devoid of plasma.
-In another word, we are dealing with the wave equation
-\begin{equation} \label{equ:wave_eq} 
-    \lambda^2\partial^2_t\mathbf{E} + \text{curl curl}\mathbf{E} = 0.
-\end{equation}
-The voltage on anode is given by
-\begin{equation*}
-    \varphi(t) = \frac{1}{2}\left(1+\text{tanh}\left( \frac{t - 1.0}{0.1}\right) \right).
-\end{equation*}
-We expect the electric field to produce oscillation with decaying magnitude.
-Besides, with Debye length $\lambda$ approaching zero, the damping becomes strong since the characteristic time scale is proportional to $\lambda$.
-Fig.
-\ref{fig:maxwell_test} (left) shows the $z$-component of $\mathbf{E}$-field at origin up to $t = 15$, and manifests such damping behavior.
-\begin{figure}
-    \centering
-    \includegraphics{maxwell_test.eps}
-    \includegraphics{maxwell_test2.eps}
-    \caption{Axial component of the $\mathbf{E}$-field at origin point with step-like voltage on anode.
-The results are computed under the mesh with 16 cells along axial direction.
-(left) The domain is an ideal dielectric; (right) the domain is of constant conductivity.}
-    \label{fig:maxwell_test}
-\end{figure}
-
-If we add to the conductivity of the material, and enforces the Ohm's law $\mathbf{J} = \sigma \mathbf{E}$, the problem to be solved becomes the wave equation with damping term
-\begin{equation*}
-    \lambda^2\partial^2_t\mathbf{E} + \sigma \partial_t \mathbf{E} - \nabla^2 \mathbf{E} = 0.
-\end{equation*}
-The introduction of conductivity causes dissipation and thus enhances the damping, as is shown in Fig. \ref{fig:maxwell_test} (right).
-
-\section{Fully-coupled system}
-We move on to test the performance of our fully-coupled Euler-Maxwell model (\ref{equ:maxwell_faraday_ap}) to (\ref{equ:current_ap}), and check its AP property.
-
-\subsection{Reduction to 1D}
-On noticing the radial symmetry of the domain as well as boundary conditions, the governing equations defined at the axis of symmetry, namely $z$-axis in this case, can be tremendously simplified thanks to vanishing radial components of vector variables and radial derivatives.
-The Euler-Maxwell system at the axis of symmetry is formulated as
-\begin{align}
-    &\partial_t n_* + \partial_z(n_*u_{*,z}) = 0, \\
-    &\partial_t (n_* u_{*,z}) + \partial_z(n_*u_{*,z}^2) + \varepsilon_*^{-2} \partial_z P_* = \varepsilon_*^{-2}q_*n_*E_z, \\
-    &\partial_t (n_*e_*) + \partial_z (n_* h_* u_{*,z}) = \varepsilon_*^{-2} q_* n_* u_{*,z} E_z, \\
-    \lambda^2 &\partial_t E_z = \sum_* - q_* n_* u_{*,z}.
-\end{align}
-Recall that in section \ref{sec:two_fluid_model} the two-fluid model in 1D setting is discussed and verified.
-We take the results as reference solutions for the 1D reduction on the $z$-axis of the 3D model.
-With the same setting as is described in section \ref{sec:1d_two_fluid_numerical_results} and the vanishing anode potentials, we expect the results produced by the purely 1D model and 1D reduction of the 3D model to behave in a similar way, which is shown in Fig.
-\ref{fig:z_axis_reduction}.
-\begin{figure}
-    \centering
-    \includegraphics{z_axis_reduction.eps}
-    \caption{Comparison of 1D two-fluid model and reduced 1D model on $z$-axis from 3D two-fluid model.
-The results are both generated on meshes with 64 cells along $z$-axis.
-No friction term exists.
-$t = 5 \times 10^{-4}.$}
-    \label{fig:z_axis_reduction}
-\end{figure}
-
-\subsection{Numerical results in 3D} \label{chap:3d_problem}
-Now comes the point to finally present the numerical results of the AP scheme on the Euler-Maxwell system in a 3D domain.
-To recap the problem setting and BCs, see Section \ref{sec:problem_description} and \ref{sec:numerical_experiement_bc}.
-We consider the two-fluid situation where the plasma is composed of electrons and ions.
-The mass ratio $m_i / m_e$ is equal to $10^4$.
-The friction term (\ref{equ:collision_rescaled}) is included with $\alpha^\text{coll} = 32$.
-Other effects like recombination or ionization are not considered yet.
-
-The initial state is
-\begin{equation*}
-    n_i(x,y,z,0) = n_e(x,y,z,0) = 1, \ \ \  p_i(x,y,z,0) = p_e(x,y,z,0) = 1.
-\end{equation*}
-All the other quantities are vanishing initially.
-The cathode is grounded, and the anode has potential 1.0 throughout the simulation, namely $\varphi^-(t) = 0, \varphi^+(t) = 1.0$.
-It is intended to see how a stationary system responds to an applied voltage.
-We would like to remark that such an initial state is conforming to the BCs as well as the quasi-neutral condition $\rho = 0$ so that the quasi-neutrality $\lambda  = 0$ would not incur any initial layer.
-
-In Fig.
-\ref{fig:3d_vec_field_E_B_ue} we present the vector fields of the numerical solutions for $\lambda = 1.0, 0.01, 0$ at $t = 0.1$, aiming to give an intuitive visualization.
-First of all, one \emph{a priori} expects the rotational symmetry in the solutions, which serves as a basic criterion to justify the results.
-In terms of the 3D structure of the electromagnetic fields, the electric field points from the anode to the cathode, and the magnetic field is spiral-shaped and orthogonal to the electric field.
-The electrons move in the inverse direction of the electric field.
-Regarding the asymptotic behavior of the AP scheme, the primary concern is its validity in the limiting case.
-For this case, the scheme manages to produce a meaningful numerical solution when $\lambda = 0$.
-Besides, by comparing the solutions for different $\lambda$, the smooth transition from the non-neutrality to quasi-neutrality is observed, which is an implication that the scheme reproduces the asymptotic behavior of the analytical solutions from the non-neutral model to the quasi-neutral one.
-\begin{figure}
-    \centering
-    \includegraphics[scale=0.35]{E_lambda_1.png}
-    \includegraphics[scale=0.35]{B_lambda_1.png}
-    \includegraphics[scale=0.35]{ue_lambda_1.png} \\
-    (a) $\lambda = 1.0$ \\
-    \includegraphics[scale=0.35]{E_lambda_1e-2.png}
-    \includegraphics[scale=0.35]{B_lambda_1e-2.png}
-    \includegraphics[scale=0.35]{ue_lambda_1e-2.png} \\
-    (b) $\lambda = 0.01$ \\
-    \includegraphics[scale=0.35]{E_lambda_0.png}
-    \includegraphics[scale=0.35]{B_lambda_0.png}
-    \includegraphics[scale=0.35]{ue_lambda_0.png} \\
-    (c) $\lambda = 0$
-    \caption{Snapshots of the $\mathbf{E}$-field, $\mathbf{B}$-field, and $\mathbf{u}_e$ for different $\lambda$ at $t = 10$ based on a primal mesh with 1920 cells (8 cells along $z$-axis). } 
-    \label{fig:3d_vec_field_E_B_ue}
-\end{figure}
-
-We perform the grid study and show the result in Fig.
-\ref{fig:grid_study_3d}.
-Meshes with different refinement levels are tested for $\lambda = 1$ and $0.1$ at $t = 1$, and the norms of the quantities are calculated.
-Due to the high computational cost incurred by the curse of dimensionality, only meshes with limited size are tested and the asymptotic regime of the grid study might be not reached.
-Nevertheless, it still helps to reveal the independence of solutions with respect to meshes --- the norms of electron density and the magnetic field do not deviate in a divergent manner.
-The exception of the norm of the electric field possibly results from the singularity caused by the interface of the contacting and insulating surfaces, as will be seen later.
-In Fig.
-\ref{fig:grid_study_3d_clip_lambda-1e-1} and \ref{fig:grid_study_3d_clip_lambda-0}, we plot the distribution of certain quantities at the cross-section based on different meshes for $\lambda = 0.1$ and $0$ at $t = 1$.
-Thanks to the rotational symmetry of the problem, the solution at the cross-section suffices to characterize the whole solution.
-The figures again demonstrate the stability of the numerical solutions with respect to mesh refinement in the sense that qualitatively the same solutions are produced by a series of meshes of different sizes.
-We would like to point out that singularity arises in the $\mathbf{E}$-field at the interface of contacting and insulating surfaces (two points at the left end and two at the right end).
-In numerical experiments, we observe an increasing magnitude of the $\mathbf{E}$-field at these points as the mesh is refined.
-Furthermore, it is noted from Fig.
-\ref{fig:grid_study_3d_clip_lambda-0} (last two rows) that when $\lambda = 0$, the charges carried by ions and electrons cancel out everywhere as indicated by the quasi-neutral condition $\rho = 0$.
-
-\begin{figure}
-    \centering
-    \includegraphics[scale=0.9]{norm_vs_nCell-T_1.eps}
-    \caption{1-norms of quantities with respect to different mesh size: The results are computed for $\lambda = 1$ and $0.1$ at $t = 1$.}.
-    \label{fig:grid_study_3d}
-\end{figure}
-
-\begin{figure}
-    \centering
-    Refinement 1\hspace{2.5cm}Refinement 2\hspace{2.5cm}Refinement 3\hspace{1cm}
-
-    \includegraphics[scale=0.27]{clip_E_T-1_lambda-1e-1_8-2-2.png}
-    \includegraphics[scale=0.27]{clip_E_T-1_lambda-1e-1_16-3-3.png}
-    \includegraphics[scale=0.27]{clip_E_T-1_lambda-1e-1_32-3-4.png}
-    \includegraphics[scale=0.27]{clip_B_T-1_lambda-1e-1_8-2-2.png}
-    \includegraphics[scale=0.27]{clip_B_T-1_lambda-1e-1_16-3-3.png}
-    \includegraphics[scale=0.27]{clip_B_T-1_lambda-1e-1_32-3-4.png}
-    \includegraphics[scale=0.27]{clip_ne_T-1_lambda-1e-1_8-2-2.png}
-    \includegraphics[scale=0.27]{clip_ne_T-1_lambda-1e-1_16-3-3.png}
-    \includegraphics[scale=0.27]{clip_ne_T-1_lambda-1e-1_32-3-4.png}
-    \includegraphics[scale=0.27]{clip_ni_T-1_lambda-1e-1_8-2-2.png}
-    \includegraphics[scale=0.27]{clip_ni_T-1_lambda-1e-1_16-3-3.png}
-    \includegraphics[scale=0.27]{clip_ni_T-1_lambda-1e-1_32-3-4.png}
-    \caption{Quantities at the cross-section generated by meshes with different refinement level.
-Refinement 1: 1920 primal cells; Refinement 2: 14592 primal cells; Refinement 3: 30720 primal cells.
-The snapshots are computed for $\lambda = 0.1$ at $t = 1$.}
-    \label{fig:grid_study_3d_clip_lambda-1e-1}
-\end{figure}
-
-\begin{figure}
-    \centering
-    Refinement 1\hspace{2.5cm}Refinement 2\hspace{2.5cm}Refinement 3\hspace{1cm}
-
-    \includegraphics[scale=0.27]{slice_E_T-1_lambda-0_8-2-2.png}
-    \includegraphics[scale=0.27]{slice_E_T-1_lambda-0_16-3-3.png}
-    \includegraphics[scale=0.27]{slice_E_T-1_lambda-0_32-3-4.png}
-    \includegraphics[scale=0.27]{slice_B_T-1_lambda-0_8-2-2.png}
-    \includegraphics[scale=0.27]{slice_B_T-1_lambda-0_16-3-3.png}
-    \includegraphics[scale=0.27]{slice_B_T-1_lambda-0_32-3-4.png}
-    \includegraphics[scale=0.27]{slice_ne_T-1_lambda-0_8-2-2.png}
-    \includegraphics[scale=0.27]{slice_ne_T-1_lambda-0_16-3-3.png}
-    \includegraphics[scale=0.27]{slice_ne_T-1_lambda-0_32-3-4.png}
-    \includegraphics[scale=0.27]{slice_ni_T-1_lambda-0_8-2-2.png}
-    \includegraphics[scale=0.27]{slice_ni_T-1_lambda-0_16-3-3.png}
-    \includegraphics[scale=0.27]{slice_ni_T-1_lambda-0_32-3-4.png}
-    \caption{Quantities at the cross-section generated by meshes with different refinement level.
-Refinement 1: 1920 primal cells; Refinement 2: 14592 primal cells; Refinement 3: 30720 primal cells.
-The snapshots are computed for $\lambda = 0$ at $t = 1$.}
-    \label{fig:grid_study_3d_clip_lambda-0}
-\end{figure}
-
-To inspect how the system evolves, we extract the time histories of certain quantities at the origin (the center of the tube) up to $t = 10$ and display them in Fig.
-\ref{fig:origin-data_vs_time}.
-Being originally at rest, the system is excited by the suddenly applied voltage and generates oscillations that dampen over time.
-In general, a large value of $\lambda$ leads to stronger oscillations with larger amplitude whereas smaller $\lambda$ incurs more damping and the system rapidly reaches a steady state.
-It is a reflection of the shielding effect of plasma which is characterized by the Debye length.
-It can also be noticed that the electron velocity becomes steady much sooner than ion velocity, which is a consequence of the huge difference in inertia.
-Besides, the convergence of the discrete model as $\lambda \rightarrow 0$ can be observed---the solution becomes steady over time.
-\begin{figure}
-    \centering
-    \includegraphics[scale=0.9]{origin-data_vs_time.eps}
-    \caption{Time histories of quantities at the origin for different $\lambda$. The simulation is done on a mesh with 1920 primal cells with 8 layers along $z$-axis.}
-    \label{fig:origin-data_vs_time}
-\end{figure}
-
-A critical sign of quasi-neutrality is the vanishing charge.
-In fact, in Section \ref{sec:quasi-neutral_limit} we discuss the limiting model where $\rho = 0$ is satisfied.
-To examine that, the quantities at the $z$-axis over different $\lambda$ are provided in Fig.
-\ref{fig:zaxis-data_vs_z-T_10}.
-The right figure demonstrates the approaching and eventual coincidence of electron and ion densities as $\lambda \rightarrow 0$.
-Furthermore, with relatively small but non-zero $\lambda$, the bulk of the plasma is approximately neutral while the area near the electrodes is not, which is known as a plasma sheath and within such an area the quasi-neutrality is usually inappropriate.
-\begin{figure}
-    \centering
-    \includegraphics{zaxis-data_vs_z-T_10.eps}
-    \caption{Quantities along $z$-axis for different $\lambda$: The results are computed at $t = 10$ on a mesh with 1920 primal cells with 8 layers along $z$-axis.}.
-    \label{fig:zaxis-data_vs_z-T_10}
-\end{figure}
-
-In Fig.
-\ref{fig:clip-ne-nue-T_10} the distribution of the electron number density and velocity at the cross-section is displayed.
-In the non-neutral case, the electrons accumulate near the anode, and the velocity is distributed rather uniformly.
-With the model approaching quasi-neutrality $\lambda = 0$, the electrons move slower in the bulk area while they are accelerated to high speed at the edge of electrodes, and they tend to accumulate in the middle pass.
-\begin{figure}
-    \centering
-    \begin{subfigure}[b]{0.4\textwidth}
-        \centering
-        \includegraphics[scale=0.4]{clip-ne-nue-T_10-lambda_1.png}
-        \caption{$\lambda = 1$}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.4\textwidth}
-        \centering
-        \includegraphics[scale=0.4]{clip-ne-nue-T_10-lambda_1e-1.png}
-        \caption{$\lambda = 0.1$}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.4\textwidth}
-        \centering
-        \includegraphics[scale=0.4]{clip-ne-nue-T_10-lambda_1e-2.png}
-        \caption{$\lambda = 0.01$}
-    \end{subfigure}
-    \hspace{0.2cm}
-    \begin{subfigure}[b]{0.4\textwidth}
-        \centering
-        \includegraphics[scale=0.38]{clip-ne-nue-T_10-lambda_0.png}
-        \caption{$\lambda = 0$}
-    \end{subfigure}
-    \caption{Electron number density and velocity vector at the cross-section.
-The results are computed at $t = 10$ on a mesh with 1920 primal cells with 8 layers along $z$-axis.
-The velocity vector lengths, which indicates the magnitude, are rescaled by the same factor.}
-    \label{fig:clip-ne-nue-T_10}
-\end{figure}
-
-\section{Summary}
-To evaluate the performance of the scheme (\ref{equ:maxwell_faraday_ap}) to (\ref{equ:euler_ap}), we need to examine the two criterion in Definition \ref{def:ap} which states the asymptotic stability and consistency.
-Both properties are \emph{experimentally} checked in a 3D setting.
-The former one, referring to the unconditional stability on $\lambda$, is confirmed as the program achieves meaningful solutions for arbitrary $\lambda$ without adjusting the time step size.
-The latter one requires the convergence of the limit scheme to the limit model, which is supported by two facts: the smooth transition of numerical solutions over $\lambda \in [0,1]$ and the conformity of the quasi-neutral condition $n_i = n_e$.
-
-\chapter{Extension to Insulating Domain}
-As is mentioned in Section \ref{sec:impact_insulating_domain}, the scheme so far could not directly handle the case with an insulating domain $\Omega_I$ where no plasma fluid is there.
-An example is shown in Fig.
-\ref{fig:sketch_domain_fusch}.
-Now the plasma domain is enclosed by a insulating sleeve.
-
-We repeat the dilemma again: the scheme fails for $\lambda \rightarrow 0$. The Maxwell system in $\Omega_I$ is    
-\begin{align}
-    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:ex_1}\\ 
-    \lambda^2 \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= 0,  \label{equ:ex_2}\\
-    \nabla \cdot \mathbf{B} &= 0, \label{equ:ex_3}\\
-    \lambda^2 \nabla \cdot \mathbf{D} &= 0 \label{equ:ex_4}.
-\end{align}
-In non-neutral regime, namely $\lambda = \mathcal{O}(1)$, the Maxwell system in $\Omega_I$ is well-posed and Gauss's laws (\ref{equ:ex_3}) (\ref{equ:ex_4}) are redundant.
-Therefore, they are \emph{implicitly} satisfied (up to numerical errors) in the scheme.
-Nonetheless, the quasi-neutral limit $\lambda \rightarrow 0$ dismisses the implicit fulfillment of Gauss's law for electric field (\ref{equ:ex_4}) through Amper\`{e}'s law (\ref{equ:ex_2}).
-A crucial observation is that formally letting $\lambda \rightarrow 0$ makes (\ref{equ:ex_4}) degenerate, but the divergence-free condition of $\mathbf{D}$-field is always satisfied since the system is divergent as $\lambda \rightarrow 0$ [cite something].
-
-The remedy is to \emph{explicitly} include the divergence-free constraint in the scheme for any value of $\lambda$:  
-\begin{align}
-    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:ex_5}\\ 
-    \lambda^2 \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= 0,  \label{equ:ex_6}\\
-    \nabla \cdot \mathbf{D} &= 0 \label{equ:ex_7}.
-\end{align}
-
-With the divergence-free constraint (\ref{equ:ex_7}), we have more equations than unknowns, which can be resolved by introducing a Lagrange multiplier $p$ as follows:
-\begin{align}
-    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:ex_8}\\ 
-    \lambda^2 \partial_t \mathbf{D} - \nabla \times \mathbf{H} + \colorbox{orange!20}{$\nabla p$} &= 0,  \label{equ:ex_9}\\
-    \nabla \cdot \mathbf{D} &= 0 \label{equ:ex_10},
-\end{align}
-supplemented with the boundary condition $p = 0$ on $\partial\Omega_I$.
-One can check that (\ref{equ:ex_8})-(\ref{equ:ex_10}) are equivalent to (\ref{equ:ex_5})-(\ref{equ:ex_7}) by verifying that $p = 0$ in $\Omega_I$.
-This is done by taking the divergence of (\ref{equ:ex_9}) such that the Laplace equation of $p$ with zero Dirichlet boundary condition gives vanishing $p$.
-
-The discretization of the Maxwell system in the insulating domain then becomes
-\begin{align*}
-    \delta_m^{-1} (\mathbf{b}^{m+1} - \mathbf{b}^m) + \mathbb{C}\mathbf{e}^{m+1} &= 0, \\
-    \lambda^2\delta_m^{-1} (\Tilde{\mathbf{d}}^{m+1} - \Tilde{\mathbf{d}}^m) - \Tilde{\mathbb{C}}\Tilde{\mathbf{h}}^{m+1} + \colorbox{orange!20}{$\mathbb{H} \mathbb{G} \mathbf{p}^{m+1}$} &= 0 \\
-    \Tilde{\mathbb{D}} \Tilde{\mathbf{d}}^{m+1} &= 0.
-\end{align*}
-where $\mathbb{H}$ is the discrete Hodge operator (matrix\footnote{In our case where the orthogonal mesh pair is used, it is diagonal.}) responsible for transforming any primal-edge-integrated variables to dual-face-integrated ones; the vector $\mathbf{p}$ is the discrete representation of $p$ and is defined on primal vertices lying in $\Omega_I$.
-
-\begin{figure}
-    \centering
-    \begin{minipage}{0.5\textwidth}
-\resizebox{\textwidth}{!}{
-    \begin{tikzpicture}
-    \coordinate (O1) at (0,0);
-    \draw[very thick] (O1) circle (1) node[blue] {Cathode};
-    \fill[blue, opacity=0.2] (O1) circle (1);
-    \draw[very thick] (O1) circle (1.5);
-    \coordinate (O2) at (4.5,1) ;
-    \draw[gray] (O2) circle (1);
-    \node at (O2) {\textcolor{red}{Anode}};
-    \node at (barycentric cs:O1=1,O2=1) {Plasma}; 
-    \fill[red, opacity=0.2] (O2) circle (1);
-    \coordinate (S1) at ([shift={(-0.196,0.98)}]O1);
-    \coordinate (S2) at ([shift={(-0.196,0.98)}]O2);
-    \coordinate (P1) at ([shift={(0.196,-0.98)}]O1);
-    \coordinate (P2) at ([shift={(0.196,-0.98)}]O2);
-    \draw[gray] (S1) -- (S2);
-    \draw[gray] (P1) -- (P2);
-    \coordinate (SS1) at ([shift={({-0.196*1.5},{0.98*1.5})}]O1);
-    \coordinate (SS2) at ([shift={({-0.196*1.5},{0.98*1.5})}]O2);
-    \coordinate (PP1) at ([shift={({0.196*1.5},{-0.98*1.5})}]O1);
-    \coordinate (PP2) at ([shift={({0.196*1.5},{-0.98*1.5})}]O2);
-    \draw[very thick] (SS1) -- (SS2);
-    \draw[very thick] (PP1) -- (PP2); 
-    \draw[gray] (SS2) arc (101.31:180+101.31:1.5);
-    \draw[very thick] (PP2) arc (101.31-180:101.31:1.5);
-    \draw[-to] (barycentric cs:SS1=1,SS2=1,S1=1,S2=1) to[out=90,in=0] ([shift={(-0.5,0.5)}]barycentric cs:SS1=1,SS2=1,S1=1,S2=1) node[left, gray] {Insulator};
-    \begin{scope}[shift={(5.5,-1.4)}]
-    \draw[blue, -to] (0,0) -- (0.65,0.12) node[right]{\small $z$};
-    \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
-    \draw[blue, -to] (0,0) -- (0.7,0) node[below]{\small $y$};
-    \end{scope}
-    \end{tikzpicture}}
-\end{minipage}
-\begin{minipage}{0.49\textwidth}
-    \resizebox{1.1\textwidth}{!}{ \begin{tikzpicture}
-        \coordinate (A1) at (0,1.5);
-        \coordinate (A2) at (0,1);
-        \coordinate (A3) at (0,-1);
-        \coordinate (A4) at (0,-1.5);
-        \coordinate (B1) at (6,1.5);
-        \coordinate (B2) at (6,1);
-        \coordinate (B3) at (6,-1);
-        \coordinate (B4) at (6,-1.5);
-        \draw[gray] (A2) -- node[above]{\textbf{Insulator $\Omega_I$}} node[black, below]{reflective wall} (B2);
-        \draw[gray] (A3) -- node[below]{\textbf{Insulator $\Omega_I$}} node[black, above]{reflective wall} (B3);
-        \draw[very thick] (A2) -- (A1) -- node[above]{$\mathbf{D} \cdot \mathbf{n} = 0, \nabla \times \mathbf{E} \cdot \mathbf{n} = 0$}  (B1) -- (B2);
-        \draw[very thick] (A3) -- (A4) -- node[below]{$\mathbf{D} \cdot \mathbf{n} = 0, \nabla \times \mathbf{E} \cdot \mathbf{n} = 0$} (B4) -- (B3);
-        \draw[very thick, dashed, blue] (A2) -- node[left, yshift=0.3cm] {$\varphi^-(t)$} node[left, yshift=-0.3cm] {\textcolor{black}{open}} (A3);
-        \draw[very thick, dashed, red]  (B2) -- node[right, yshift=0.3cm]  {$\varphi^+(t)$} node[right, yshift=-0.3cm] {\textcolor{black}{open}}  (B3);
-        \node at (3,0) {\textbf{Plasma $\Omega_p$}};
-        \begin{scope}[shift={(6.5,-1.6)}]
-        \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
-        \draw[blue, -to] (0,0) -- (0.7,0) node[right]{\small $z$};
-        \end{scope}
-    \end{tikzpicture}}
-\end{minipage}
-    \caption{Caption}
-    \label{fig:ex}
-\end{figure}
-
-The setting of the numerical test is sketched in Fig. \ref{fig:ex}. The initial conditions keep unchanged as Section \ref{chap:3d_problem}.
-
-As predicted in the analytic case, the Lagrange multiplier $p$ is approximately zero (in the order of $\mathcal{O}(10^{-12})$) in the numerical test.
-The introduction of the surrounding insulator sleeve does not qualitatively alters the 3D structure of the resulting electromagnetic fields (see Fig.
-\ref{fig:3d_vec_field_E_B_ue}), which are therefore omitted here.
-In Fig.
-\ref{fig:time_history_extend} we demonstrate how quantities at the center of the cylinder evolve with time.
-Comparison with its counterpart Fig.
-\ref{fig:origin-data_vs_time} shows many similarities.
-An interesting point is that now the ions move towards the anode, which is not nonphysical since the frictional force could be stronger than the electric force.
-What matters is the capability of the scheme to handle the quasi-neutral limit.
-\begin{figure}
-    \centering
-    \includegraphics[scale=0.9]{origin_data-vs-time_withInsulator.eps}
-    \caption{Time histories of quantities at the origin for different value of $\lambda$.
-The simulations are done on a mesh with 3840 primal cells with 16 layers along $z$-axis.
-Compared to fig.
-\ref{fig:origin-data_vs_time}, an insulating domain is included in this case.}
-    \label{fig:time_history_extend}
-\end{figure}
-
-\chapter{Conclusion}
-We generalize the AP scheme proposed in \cite{degond_2012}, which is originally designed to handle the quasi-neutrality of the Euler-Maxwell system and applied to problems in 1D, to a 3D scenario.
-Such generalization has been partially done in \cite{fuchs_2021}, and yet an inconsistency in the limiting case remains unsolved.
-Based upon the framework built by \cite{fuchs_2021}, this thesis proposes several modifications to the algorithm and the targeting problems.
-
-The generalized scheme incorporates FIT and FVM for spatial discretization of Maxwell's equations and the Euler equations.
-The time discretization is of critical significance in attaining AP property, and the choice of implicit terms conforms to the mentioned references.
-Additionally, the collision between species is included.
-Substantial efforts are put on issues related to the boundary.
-We enforce the BCs under the framework of FIT by introducing auxiliary mesh facets and quantities at the boundary.
-Furthermore, we identify the proper BCs that are essential for the well-posedness of the Euler-Maxwell system over different regimes.
-The detailed strategy to assemble the linear system due to the implicitness is presented.
-The 3D scheme is first validated on the subsystems and is compared to its corresponding 1D discrete model.
-Solutions performed on the fully-coupled system for $\lambda$ ranging in $[0,1]$ show a smooth transition from the non-neutral model to the quasi-neutral one, which demonstrates that our scheme is AP.
-
-Apart from the implementation of the scheme in 3D, the definition and property of AP schemes are rephrased in a more definite way.
-Despite a large amount of literature discussing AP schemes, the definition differs from paper to paper and remains vague.
-In this thesis, we summarize AP properties by two features: asymptotic-stability and asymptotic-consistency, which refer to the unconditional stability on the asymptotic parameter, and convergence of the scheme in the limiting case.
-We formulate two propositions as an attempt to unveil the connection between these two aspects---the second one might be relaxed by only requiring consistency under certain assumptions.
-
-Future works could be carried out in the following directions.
-As is discussed in Section \ref{sec:impact_insulating_domain}, the failure arising from the insulating solid domain could be remedied by enforcing $\nabla \cdot \mathbf{D}$ = 0, which is worth pursuing.
-In terms of implementation, the algorithm is not yet optimized.
-As the bottleneck, solving the large sparse linear systems consumes nearly all the computation time.
-The matrix assembly might be smarter such that the resulting linear system possesses certain desired properties, e.g.
-symmetric positive-definite, and hence a faster solver can be invoked.
-Besides, the present AP scheme is of first-order in accuracy.
-The combination of high-order schemes and the AP property is a potential challenge since several issues, e.g.
-the intra-mesh interpolation of the electromagnetic fields and the discrete material law, could undermine the accuracy.
-One can also contemplate incorporating the AP property into other numerical frameworks like FEM.
-Regarding the design of AP schemes, the approaches so far are mostly heuristic and specific to the given problem.
-A unified strategy of construction and verification is still to be explored.
-
-\begin{appendices}
-\chapter{Rusanov Flux in 3D} \label{app:flux}
-Consider the Euler equations
-\begin{align} \label{equ:euler}
-    \partial_t
-    \begin{bmatrix}
-    \rho \\
-    \rho \mathbf{u} \\
-    E
-    \end{bmatrix}
-    + \nabla \cdot
-    \begin{bmatrix}
-    \rho \mathbf{u} \\
-    \rho \mathbf{u} \otimes \mathbf{u} + p\mathbb{I} \\
-    (E+p)\mathbf{u}
-    \end{bmatrix}
-    = 0.
-\end{align}
-In 3D Cartesian coordinate system, it reads 
-\begin{align} \label{equ:euler_xyz}
-    \partial_t \mathbf{U} + \partial_x \mathbf{F}^x(\mathbf{U}) + \partial_y \mathbf{F}^y(\mathbf{U}) + \partial_z \mathbf{F}^z(\mathbf{U}) = 0.
-\end{align}
-where
-\begin{equation*}
-    \mathbf{U} =
-    \begin{bmatrix}
-    \rho \\
-    \rho u_x \\
-    \rho u_y \\
-    \rho u_z \\
-    E
-    \end{bmatrix}, \ \ \ 
-    \mathbf{F}^x(\mathbf{U}) =
-    \begin{bmatrix}
-    \rho u_x \\
-    \rho u_x^2 + p \\
-    \rho u_y u_x  \\
-    \rho u_z u_x \\
-    (E + p)u_x
-    \end{bmatrix}, \ \ \ 
-    \mathbf{F}^y(\mathbf{U}) =
-    \begin{bmatrix}
-    \rho u_y \\
-    \rho u_x u_y \\
-    \rho u_y^2 + p \\
-    \rho u_z u_y \\
-    (E + p)u_y
-    \end{bmatrix}, \ \ \ 
-    \mathbf{F}^z(\mathbf{U}) =
-    \begin{bmatrix}
-    \rho u_z \\
-    \rho u_x u_z  \\
-    \rho u_y u_z  \\
-    \rho u_z^2  + p\\
-    (E + p)u_z
-    \end{bmatrix}
-\end{equation*}
-\begin{figure}
-    \centering
-    \begin{tikzpicture}[scale=0.7]
-        \coordinate (A1) at (0,0);
-        \coordinate (A2) at (2,0);
-        \coordinate (A3) at (3,1);
-        \coordinate (A4) at (3,3);
-        \coordinate (A5) at (1,3);
-        \coordinate (A6) at (-1,3);
-        \coordinate (A7) at (-2,2);
-        \coordinate (A8) at (-2,0);
-        \coordinate (A10) at (0,2);
-        \coordinate (A11) at (2,2);
-        \coordinate (A12) at (-1,1);
-        \coordinate (A13) at (1,1);
-        \draw[very thick] (A1) -- (A2) -- (A3) -- (A4) -- (A5) -- (A6) -- node[left, yshift=2mm]{$\delta_y$} (A7) -- node[left]{$\delta_z$} (A8) -- (A1);
-        \draw[very thick] (A7) -- (A10) -- (A11) -- (A4);
-        \draw[very thick] (A1) -- (A10) -- (A5);
-        \draw[very thick] (A2) -- (A11);
-        \draw[gray] (A6) -- (A12) -- (A8);
-        \draw[gray] (A12) -- (A3);
-        \draw[gray] (A5) -- (A13) -- (A1); 
-        \fill[blue, opacity=0.2] (A1) -- (A10) -- (A5) -- (A13);
-        \draw[blue, thick] (-0.75,1.5) node[below=0.5cm] {$\mathbf{U}_L$} -- (0,1.5); 
-        \draw[blue, thick, dotted] (0,1.5) -- (0.5,1.5); 
-        \draw[blue, thick, -to] (0.5,1.5) -- (1.25,1.5) node[right,xshift=-1mm] {$\overline{\mathbf{F}}$} node[below=0.5cm] {$\mathbf{U}_R$};
-        \draw[fill=blue] (0.5,1.5) circle (0.5mm) ;
-        \begin{scope}[shift={(4,0)}]
-        \draw[blue, -to] (0,0) -- (1,0) node[right]{\small $x$};
-        \draw[blue, -to] (0,0) -- (0,1) node[above]{\small $z$};
-        \draw[blue, -to] (0,0) -- (0.7,0.7) node[above, xshift=2mm]{\small $y$};
-        \end{scope}
-        \begin{scope}[shift={(10,0)}]
-        \coordinate (P1) at (0,0);
-        \coordinate (P2) at (0,1.5);
-        \coordinate (P3) at (-1,3);
-        \coordinate (P4) at (-3,0);
-        \coordinate (P5) at (2.5,2);
-        \draw[very thick] (P1) -- (P3) -- (P5) -- (P1);
-        \draw[very thick] (P1) -- (P4) -- (P3);
-        \draw[gray] (P1) -- (P2) -- (P3);
-        \draw[gray] (P4) -- (P2) -- (P5);
-        \fill[blue, opacity=0.2] (P1) -- (P2) -- (P3);
-        \coordinate (O) at (barycentric cs:P1=1,P2=1,P3=1);
-        \coordinate (O1) at ([shift={(1,0.5)}]barycentric cs:P1=1,P2=1,P3=1);
-        \draw[blue, thick, -to] (O) -- (O1) node[below=3mm] {$\mathbf{U}_R$} node[right,xshift=-1mm] {$\overline{\mathbf{F}}$};
-        \coordinate (S)  at (intersection of O--O1 and P1--P3);
-        \draw[blue, thick] (S)--([shift={(-1,-0.5)}]S) node[below=0.1cm, xshift=4mm] {$\mathbf{U}_L$} ;
-        \draw[blue, thick, dotted] (S) -- (O);
-        \draw[fill=blue] (O) circle (0.5mm);
-        \begin{scope}[shift={(4,0)}]
-        \draw[blue, -to] (0,0) -- (1,0.5) node[right]{\small $\xi$};
-        \draw[blue, -to] (0,0) -- (-0.5,1) node[above]{\small $\zeta$};
-        \draw[blue, -to] (0,0) -- (0.5,0.8) node[above, xshift=0mm]{\small $\eta$};
-        \end{scope}
-        \end{scope}
-    \end{tikzpicture}
-    \caption{Flux between two cells in 3D Cartesian coordinate.}
-    \label{fig:flux_cartesian}
-\end{figure}
-
-For the flux through a face orthogonal to $x$-axis, as is shown in Fig. \ref{fig:flux_cartesian}, Rusanov flux reads
-\begin{equation} \label{equ:rusanov_flux_original}
-    \overline{\mathbf{F}}(\mathbf{U}_L, \mathbf{U}_R) = \frac{1}{2}\left[\mathbf{F}^x(\mathbf{U}_L) + \mathbf{F}^x(\mathbf{U}_R)\right] - \frac{1}{2}\overline{s}\left(\mathbf{U}_R - \mathbf{U}_L\right).
-\end{equation}
-where $\overline{s} = \text{max}(s(\mathbf{U}_L), s(\mathbf{U}_R))$, $s(\mathbf{U}) := |u_x| + \sqrt{\gamma p/\rho}$ represents the largest wave speed.
-The numerical flux is derived from the approximate Riemann solver.
-
-For the flux outflowing through arbitrary face with outer normal vector $\bm{\xi}$, as is shown in Fig.
-\ref{fig:flux_cartesian}, the Euler equations (\ref{equ:euler_xyz}) under $(x,y,z)$ reference coordinate system should be reformulated under $(\xi, \eta, \zeta)$ reference coordinate system:
-\begin{align} \label{equ:euler_xez}
-    \partial_t \mathbf{U'} + \partial_\xi \mathbf{F}^\xi(\mathbf{U'}) + \partial_\eta \mathbf{F}^\eta(\mathbf{U'}) + \partial_\zeta \mathbf{F}^\zeta(\mathbf{U'}) = 0.
-\end{align}
-where
-\begin{equation*}
-    \mathbf{U'} =
-    \begin{bmatrix}
-    \rho \\
-    \rho u_\xi \\
-    \rho u_\eta \\
-    \rho u_\zeta \\
-    E
-    \end{bmatrix}, \ \ \ 
-    \mathbf{F}^\xi(\mathbf{U'}) =
-    \begin{bmatrix}
-    \rho u_\xi \\
-    \rho u_\xi^2 + p \\
-    \rho u_\eta u_\xi  \\
-    \rho u_\zeta u_\xi \\
-    (E + p)u_\xi
-    \end{bmatrix}, \ \ \ 
-    \mathbf{F}^\eta(\mathbf{U'}) =
-    \begin{bmatrix}
-    \rho u_\eta \\
-    \rho u_\xi u_\eta \\
-    \rho u_\eta^2 + p \\
-    \rho u_\zeta u_\eta \\
-    (E + p)u_\eta
-    \end{bmatrix}, \ \ \ 
-    \mathbf{F}^\zeta(\mathbf{U'}) =
-    \begin{bmatrix}
-    \rho u_\zeta \\
-    \rho u_\xi u_\zeta  \\
-    \rho u_\eta u_\zeta  \\
-    \rho u_\zeta^2  + p\\
-    (E + p)u_\zeta
-    \end{bmatrix}
-\end{equation*}
-The density $\rho$, pressure $p$, and energy $E$ remain the same while the velocities satisfy the following transformation
-\begin{equation} \label{equ:rotation_relation}
-    \begin{bmatrix}
-    u_\xi \\
-    u_\eta \\
-    u_\zeta
-    \end{bmatrix}
-    =
-    \begin{bmatrix}
-    \bm{\xi}^T \\
-    \bm{\eta}^T \\
-    \bm{\zeta}^T 
-    \end{bmatrix}
-    \begin{bmatrix}
-    u_x \\
-    u_y \\
-    u_z
-    \end{bmatrix}, \ \ \ 
-    \begin{bmatrix}
-    u_x \\
-    u_y \\
-    u_z
-    \end{bmatrix}
-    =
-    \begin{bmatrix}
-    \bm{\xi},\bm{\eta},\bm{\zeta} 
-    \end{bmatrix}
-    \begin{bmatrix}
-    u_\xi \\
-    u_\eta \\
-    u_\zeta
-    \end{bmatrix},
-\end{equation}
-where $\bm{\xi}, \bm{\eta}, \bm{\zeta}$ denote the unit column vectors of $\xi$-axis, $\eta$-axis, $\zeta$-axis \emph{under $(x,y,z)$ coordinate systems}.
-Since now $\xi$-axis is parallel to the face normal, we can use the formula for Rusanov flux (\ref{equ:rusanov_flux_original}) to compute the flux through the face
-\begin{equation} \label{equ:rusanov_flux_rotated}
-    \overline{\mathbf{F'}}(\mathbf{U}'_L, \mathbf{U}'_R) = \frac{1}{2}\left[\mathbf{F}^\xi(\mathbf{U}'_L) + \mathbf{F}^\xi(\mathbf{U}'_R)\right] - \frac{1}{2}\overline{s}\left(\mathbf{U}'_R - \mathbf{U}'_L\right).
-\end{equation}
-Note that now everything is under the rotated coordinate system, and the flux (\ref{equ:rusanov_flux_rotated}) need to be transformed into the original coordinate system.
-To be concrete, the momentum flux, which corresponds to the second, third and fourth components of (\ref{equ:rusanov_flux_rotated}), need to be rotated through the relation (\ref{equ:rotation_relation}), while the density and energy flux remain the same since they are invariant under rotation.
-Take the term $\mathbf{F}^\xi(\mathbf{U}'_L)$ as an example, its expression under $(x,y,z)$-system reads
-\begin{equation*}
-    \begin{bmatrix}
-    \rho u_\xi \\
-    (\rho u_\xi^2 + p)\bm{\xi} + \rho u_\eta u_\xi \bm{\eta} + \rho u_\zeta u_\xi \bm{\zeta}\\
-    (E + p)u_\xi
-    \end{bmatrix}_L
-    = 
-    \begin{bmatrix}
-    \rho u_\xi \\
-    \rho u_\xi(u_\xi\bm{\xi} + u_\eta\bm{\eta} + u_\zeta\bm{\zeta}) + p\bm{\xi}\\
-    (E + p)u_\xi
-    \end{bmatrix}_L
-    = 
-    \begin{bmatrix}
-    \rho u_\xi \\
-    \rho u_\xi u_x + p\xi_1\\
-    \rho u_\xi u_y + p\xi_2\\
-    \rho u_\xi u_z + p\xi_3\\
-    (E + p)u_\xi
-    \end{bmatrix}_L
-\end{equation*}
-under the $(x,y,z)$ coordinate system.
-
-Finally, we end up with Rusanov flux at the face with normal vector $\bm{\xi}$ under $(x,y,z)$-system:
-\begin{equation} \label{equ:rusanov_flux_euler}
-    \overline{\mathbf{F}}(\mathbf{U}_L, \mathbf{U}_R, \bm{\xi})
-    = \frac{1}{2} \left( 
-    \begin{bmatrix}
-    \rho u_\xi \\
-    \rho u_\xi u_x + p\xi_1\\
-    \rho u_\xi u_y + p\xi_2\\
-    \rho u_\xi u_z + p\xi_3\\
-    (E + p)u_\xi
-    \end{bmatrix}_L
-    +
-    \begin{bmatrix}
-    \rho u_\xi \\
-    \rho u_\xi u_x + p\xi_1\\
-    \rho u_\xi u_y + p\xi_2\\
-    \rho u_\xi u_z + p\xi_3\\
-    (E + p)u_\xi
-    \end{bmatrix}_R
-    \right)
-    - \frac{1}{2}\overline{s}
-    \left(
-    \begin{bmatrix}
-    \rho \\
-    \rho u_x \\
-    \rho u_y \\
-    \rho u_z \\
-    E
-    \end{bmatrix}_L
-    -
-    \begin{bmatrix}
-    \rho \\
-    \rho u_x \\
-    \rho u_y \\
-    \rho u_z \\
-    E
-    \end{bmatrix}_R
-    \right),
-\end{equation}
-where $\overline{s} = \text{max}(s(\mathbf{U}_L), s(\mathbf{U}_R))$, $s(\mathbf{U}) := |u_\xi| + \sqrt{\gamma p/\rho}$.
-Recall that $u_\xi$ is defined in (\ref{equ:rotation_relation}) which is the velocity projection on $\bm{\xi}$.
-Obviously it is nothing but formula (\ref{equ:rusanov-flux-3d}).
-
-\chapter{Implementation in \texttt{C++}}
-On presenting the numerical scheme for the Euler-Maxwell system under the framework of FIT and FVM, in this section, we want to illustrate the skeleton of our implementation including the data structure, the fluid solver, and Maxwell solver.
-Due to the coupling of two systems and the specially designed time discretization scheme, the update of quantities follows a complex sequence, which we want to make clear here.
-The program is written in \texttt{C++}.
-
-This chapter is aimed to convey concrete ideas on how such a complex system is tackled in a computer program.
-Although the program is intended for simulating the case presented in Chapter \ref{chap:numerical_experiments_in_3d}, we would like to provide sufficient generality for other problems and make it extensible for more advanced algorithms.
-
-\section{Data structure}
-We refer to the data structure as the way of defining how the information of meshes is organized in the program.
-To allow the ability to tackle problems with complex geometries, we treat meshes in an unstructured manner, that is, the topological relations between elements (facets, as is defined before) cannot be induced by the indexing and have to be stored.
-
-We define a parent class \texttt{GeometryItem} that only manages the indexing.
-Four child classes are derived from it.
-They are \texttt{Vertex}, \texttt{Edge}, \texttt{Face} and \texttt{Cell}, representing facets of zero, one, two and three dimensions.
-A class \texttt{Mesh} is defined to collect all these facet objects that compose an mesh.
-
-In terms of the topology of a mesh, a facet object, say a $k$-dim facet, is aware of all the $(k-1)$-dim facets that it contains as well as all the $(k+1)$-dim facets containing it.
-Meanwhile, each object has its internal orientation.
-Each class provides a function \texttt{getIncidence} to check whether the internal orientation of a $(k-1)$-dim facet coincides with its external orientation induced by the $k$-dim facet.
-This information already suffices to construct the incidence matrices mentioned in Section \ref{sec:fit}.
-
-The geometry is determined by the coordinates of all the \texttt{Vertex} objects, based on which each facet class can define its geometric property, such as length for \texttt{Edge}, area for \texttt{Face} and volume for \texttt{Cell}.
-
-These components consist of the basic data structure used in our program. Some code snippets for their definitions are given in the following.
-
-\begin{lstlisting}[numbers=none]
-class GeometryItem
-{
-public:
-    ...
-private:
-    int index;
-    ...
-};
-\end{lstlisting}
-
-\begin{minipage}{0.465\textwidth}
-\begin{lstlisting}[numbers=none]
-class Vertex :
-    public GeometryItem
-{
-public:
-    ...
-private:
-    Eigen::Vector3d position;
-    std::vector<Edge*> edgeList;
-    ...
-
-};
-\end{lstlisting}
-\end{minipage}
-\hfill
-\begin{minipage}{0.465\textwidth}
-\begin{lstlisting}[numbers=none]
-class Edge :
-    public GeometryItem
-{
-public:
-    double getLength();
-    int getIncidence(const Vertex* v);
-    ...
-private:
-    std::vector<Vertex*> vertexList;
-    std::vector<Face*>   faceList;
-    ...
-};
-\end{lstlisting}
-\end{minipage}
-
-\begin{minipage}{0.465\textwidth}
-\begin{lstlisting}[numbers=none]
-class Face :
-    public GeometryItem
-{
-public:
-    double getArea();
-    int getIncidence(const Edge* e);
-    ...
-private:
-    std::vector<Edge*> edgeList;
-    std::vector<Cell*> cellList;
-    ...
-};
-\end{lstlisting}
-\end{minipage}
-\hfill
-\begin{minipage}{0.465\textwidth}
-\begin{lstlisting}[numbers=none]
-class Cell :
-    public GeometryItem
-{
-public:
-    double getVolume();
-    int getIncidence(const Face* f);
-    ...
-private:
-    std::vector<Vertex*> faceList;
-    ...
-
-};
-\end{lstlisting}
-\end{minipage}
-
-\hfill
-\begin{minipage}{0.97\textwidth}
-\begin{lstlisting}[numbers=none]
-class Mesh
-{
-public:
-    ...
-protected:
-    std::vector<Vertex*> vertexList;
-    std::vector<Edge*>   edgeList;
-    std::vector<Face*>   faceList;
-    std::vector<Cell*>   cellList;
-    ...
-};
-\end{lstlisting}
-\end{minipage}
-
-Two child classes \texttt{PrimalMesh} and \texttt{DualMesh} are derived from the parent class \texttt{Mesh} with some functions for their construction.
-
-\section{Class for the fluid solver}
-A class \texttt{FluidSolver} is defined to handle the computation related to the Euler system, such as the equation of state, the transformation between primitive and conservative quantities, the numerical flux, the time-stepping scheme.
-A \texttt{FluidSolver} object has information about the \texttt{DualMesh} object on which the Euler equations are solved.
-It maintains an array of fluid quantities whose indexing conforms to the one defined by the \texttt{DualMesh} object and is responsible to evolve it over time.
-The functions for applying the source term, such as the Lorentz force and the friction term, are also provided.
-These basic components are shown in the following code block.
-\begin{lstlisting}[numbers=none]
-class FluidSolver
-{
-public:
-    ...
-    void updateFlux(); // compute the numerical flux at each face
-    void timestepping(const double dt);
-private:
-    ...
-    void applyLorentzForce(const Eigen::MatrixXd &E, const Eigen::MatrixXd &B);
-    void applyFrictionTerm(const FluidSolver* anotherSpecies, const double alpha);
-    Eigen::VectorXd Flux(const Eigen::VectorXd &q, const Eigen::Vector3d &fn) const;
-    Eigen::VectorXd RusanovFlux(const Eigen::VectorXd & qL, 
-                                const Eigen::VectorXd & qR,
-                                const Eigen::Vector3d & fn) const;
-    Eigen::VectorXd conservative2primitive(const Eigen::VectorXd &q_cons) const;
-    Eigen::VectorXd primitive2conservative(const Eigen::VectorXd &q_prim) const;
-
-    const DualMesh* mesh;
-    Eigen::MatrixXd U;  // conservative variable at each fluid cell
-    Eigen::MatrixXd F;  // flux at each fluid face
-    Eigen::MatrixXd rhs;// rhs at each fluid cell
-};
-\end{lstlisting}
-
-To deal with the multi-species model, multiple \texttt{FluidSolver} objects are built at the simulation, and each of them is responsible for just one species.
-Hence, a class that wraps them together is needed and it has full control of these objects.
-In another word, it is representative of the Euler system and interacts with the Maxwell system over the simulation.
-Recall that such interaction is realized through the generalized Ohm's law (\ref{equ:tmp5}), namely providing $\mathbf{M}_\sigma$ and $\mathbf{j}_{\text{aux}}$.
-
-In the two-fluid model, for instance, we define a class \texttt{TwoFluidSolver} that owns two \texttt{FluidSolver} members for electrons and ions. Some of its essential members are shown below.
-\begin{lstlisting}[numbers=none]
-class TwoFluidSolver
-{
-public:
-    ...
-    void updateFlux(); // compute the numerical fluxes of each species 
-    void timestepping(const double dt); // do time-stepping for each species
-    Eigen::SparseMatrix<double> get_M_sigma(const double dt); 
-    Eigen::VectorXd get_j_aux(const double dt, const Eigen::MatrixXd& B) const; 
-private:
-    ...
-    const PrimalMesh* primal;
-    const DualMesh* dual;
-    FluidSolver electron_solver;
-    FluidSolver ion_solver;
-};
-\end{lstlisting}
-
-\section{Class for the Maxwell solver}
-Under the framework of FIT, a Maxwell solver takes care of the integral quantities on mesh facets and evolves them according to Maxwell's Grid Equations described in Section \ref{sec:fit}.
-Due to the implicit scheme, a linear system has to be solved at each time step, and the assembling of such a linear system is accomplished by the Maxwell solver.
-Besides, the Maxwell system influences the Euler system by the Lorentz force which entails interpolation of electromagnetic fields based on the integral quantities defined on mesh facets.
-These missions are assigned to the class \texttt{MaxwellSolver}, whose definition is briefly given as follows.
-\begin{lstlisting}[numbers=none]
-class MaxwellSolver
-{
-public:
-    ...
-    void solveLinearSystem(const double time, const double dt,
-                           Eigen::SparseMatrix<double>&& M_sigma, 
-                           Eigen::VectorXd&& j_aux);
-    void evolveMagneticFlux(const double dt);
-    Eigen::MatrixXd getInterpolated_E() const;
-    Eigen::MatrixXd getInterpolated_B() const; 
-private:
-    ...
-    const PrimalMesh* primal;
-    const DualMesh* dual;
-
-    Eigen::VectorXd eo;  // E-field integral at interior primal edge
-    Eigen::VectorXd phi; // electric potenial at boundary primal vertex
-    Eigen::VectorXd hp;	 // H-field integral at boundary dual edge  
-    Eigen::VectorXd dp;	 // D-field integral at boundary dual face
-};
-\end{lstlisting}
-
-\section{Workflow for simulations}
-To perform a simulation, the primal and dual meshes are first generated with the boundary facets assigned with their boundary type.
-The inherent property of each plasma species, such as mass, charge number, and thermodynamic properties, are specified in the corresponding \texttt{FluidSolver} object.
-On setting the initial conditions, the discrete system can evolve until $t_{\text{end}}$.
-
-The implementation of the AP scheme (\ref{equ:maxwell_faraday_ap}) to (\ref{equ:euler_ap}) requires particular attention on the order of updating quantities.
-In principle, the time step d$t$ satisfying CFL conditions is first fixed by invoking \texttt{TwoFluidSolver}.
-With the generalized ohm's law (\ref{equ:tmp5}) being provided by \texttt{TwoFluidSolver}, the Maxwell system is updated, followed by the Euler system.
-The pseudo-code depicting the typical workflow is given as follows.
-The input and output procedures are omitted.
-
-\vspace{0.5cm}
-\begin{minipage}{0.9\textwidth}
-\fbox{
-\parbox{\textwidth}{
-\begin{algorithmic}
-\State Init \texttt{PrimalMesh} and \texttt{DualMesh};
-\State Init \texttt{TwoFluidSolver} and \texttt{MaxwellSolver};
-\While{$t < t_{\text{end}}$}
-\State \texttt{TwoFluidSolver} updates the numerical fluxes and computes d$t$;
-\State \texttt{TwoFluidSolver} computes $\mathbf{M}_\sigma$ and $\mathbf{j}_{\text{aux}}$ in (\ref{equ:tmp5});
-\State \texttt{MaxwellSolver} assembles and solves the linear system (\ref{equ:linear_system});
-\State \texttt{MaxwellSolver} interpolates $\mathbf{E}$-field and $\mathbf{B}$-field;
-\State \texttt{TwoFluidSolver} updates the momenta (\ref{equ:tmp1}) or (\ref{equ:tmp13});
-\State \texttt{TwoFluidSolver} updates the implicit mass fluxes (\ref{equ:flux_ap});
-\State \texttt{TwoFluidSolver} evolves all the fluid quantities as (\ref{equ:euler_ap});
-\State \texttt{MaxwellSolver} evolves magnetic fluxes as (\ref{equ:maxwell_faraday_ap}); 
-\State $t = t + \text{d}t$;
-\EndWhile
-\end{algorithmic}
-}}
-\end{minipage}
-\end{appendices}
-
-\bibliography{bib}
 \end{document}

### 2022-09-15 paper_version/main.tex
test
Copy-paste from master thesis. The main skeleton is done.

@@
-\documentclass{report}
+\documentclass{article}
 \usepackage[utf8]{inputenc}
 \usepackage{amssymb}
+\usepackage{amsmath}
 \usepackage{amsthm}
+\usepackage{hyperref}
+\usepackage{geometry}
+\geometry{a4paper,scale=0.8}
+\usepackage{natbib}
+\bibliographystyle{apalike}
+\usepackage{tikz}
+\usetikzlibrary{positioning, decorations.markings, arrows, intersections}
+\usepackage{nicematrix}
+\NiceMatrixOptions{cell-space-top-limit = 4pt}
+\NiceMatrixOptions{cell-space-bottom-limit = 4pt}
+\usepackage{tcolorbox}
+
+\newcommand{\todo}[1]{\textcolor{blue}{\fbox{\textbf{TODO: #1}}}}
+\newcommand{\todobox}[1]{
+    \begin{tcolorbox}[title=TODO list, colback=blue!10, colframe=blue]
+        #1
+    \end{tcolorbox}
+}
 
@@
 
-\chapter{Introduction}
+\todobox{
+    \begin{itemize}
+        \item For the time being, the contents are just clipped from master thesis. They could be very chaotic.
+        \item The figures are not added yet.
+        \item For sure some parts need rewriting.
+    \end{itemize}
+}
 
+\section*{Abstract}
+A key coefficient characterizing plasmas is the so-called Debye length $\lambda_D$, whose size indicates to what extent electric charges can deviate from the neutral case: If $\lambda_D = \mathcal{O}(1)$ we face the non-neutral regime, while for $\lambda_D\to 0$ the plasma becomes quasi-neutral.
+Plasma models have rather different properties in these two regimes due to the singular perturbation arising from the $\lambda_D\to 0$ limit.
+Since both regimes may coexist in some plasma phenomena, it is desired to design numerical schemes that are \emph{robust} for arbitrary $\lambda_D$.
+More precisely, they should be \emph{asymptotic-preserving} (AP), in the sense that the limit $\lambda_D\to 0$ of the scheme yields a viable discretization for the continuous limit model.
+
+An asymptotic preserving scheme for single- and multi-fluid Euler-Maxwell system was proposed by \cite{degond_2012} for one spatial dimension.
+We start from their dimensionless model and extend the scheme to three dimensions.
+The key ingredients are (i) a discretization of Maxwell's equations based on primal and dual meshes in the spirit of discrete exterior calculus (DEC)/the finite integration technique (FIT), (ii) finite volume method (FVM) for the fluid equations on the dual mesh, and (iii) mixed implicit-explicit timestepping.
+This scheme turns out to be AP for $\lambda_D\to 0$ both in terms of structure and empirically in numerical test.
+Special care is necessary for the boundary conditions which must be valid in both regimes.
+Additionally, if the electromagnetic fields have to be modeled in an insulating region beyond the plasma domain, additional stabilization is necessary to accommodate Gauss's law.
+
+\section{Introduction}
+Under moderate assumptions, plasmas, which are mixed gases of charged particles, can be treated as fluid and described by hydrodynamic equations.
+The Maxwell equations are involved to describe their induction of and interaction with electromagnetic fields.
+In this work, we discuss and implement this so-called \emph{Euler-Maxwell} system with a focus on its limiting behavior of quasi-neutrality, namely when the \emph{Debye length} goes to zero.
+The dimensionless form of the Euler-Maxwell equations is parameterized by the rescaled Debye length $\lambda$ whose vanishing limit alters the mathematical nature of the equations.
+To be more concrete, the non-limit model ($\lambda = \mathcal{O}(1)$) is hyperbolic where information spreads with a finite speed whereas the limit model ($\lambda \rightarrow 0$) becomes elliptic, and any changes immediately influence the whole domain.
+In other words, the perturbation of $\lambda$ in the Maxwell-Euler system poses a singular perturbation problem.
+Such switching makes it difficult to handle both models in a single implementation framework, which, however, is desired in many cases where both models coexist in the computational domain.
+Now comes the concept of \emph{asymptotic-preserving}(AP) scheme.
+We turn to the celebrated commuting diagram Fig.
+\ref{fig:commuting_diagram_ap} for illustration.\todo{add illustration of AP schemes}.
+
+The other emphasis of this work is the development of a 3D discretization framework for the Maxwell-Euler system.
+The key ingredient is the combination of the Finite Volume Method (FVM) for the Euler equations and the Finite Integration Technique (FIT) for the Maxwell equations.
+The latter one is usually treated as a generalization to Yee's scheme \citep{yee_1966} or FDTD.
+The advantage of the FVM-FIT framework lie in the \emph{discrete exterior calculus} (DEC) nature of FIT and straightforward coupling of both systems through the primal-dual mesh pair.
+These would be made clear in the corresponding sections.
+
+\todo{add previous work on AP schemes, FIT, plasma simulation}.
+
+The content of this paper is organized as follows.
+In Section 2 we introduce the full Maxwell-Euler model for plasmas, followed by the rescaling procedure which is crucial to define the rescaled Debye length $\lambda$ and to identify its limiting behavior.
+In the meantime, it is essential to discuss what boundary conditions are appropriate for this singular perturbation problem.
+Section 3 is then dedicated to a brief introduction about \cite{degond_2012} based on which our work is extended.
+In Section 4, we first discuss our FVM-FIT framework in details, especially how the unknowns are assigned on the staggered meshes and the boundary treatment in 3D case.
+Afterwards, the full discretization scheme is presented.
+Special care shall be taken to the treatment of boundary conditions and insulator part of the domain as $\lambda \rightarrow 0$, which is crucial to make the scheme AP.
+A numerical experiment for a 3D cylindrical domain is presented in Section 5 where we want to demonstrate the capability of our scheme in dealing with both non-neutral and quasi-neutral regimes of plasmas.
+
+\begin{figure}
+    \centering
+    \begin{tikzpicture}
+    \node (nw) {\Large $P^\lambda_h$};
+    \node (ne) [right=3cm of nw]{\Large $P^\lambda$};
+    \node (sw) [below=of nw]{\Large $P^0_h$};
+    \node (se) [right=3cm of sw]{\Large $P^0$};
+    \draw[->] (nw.east)  -- node [above,midway] {$h\rightarrow0$} (ne.west) ;
+    \draw[->] (nw.east)  --  (ne.west) ;
+    \draw[->] (nw.south) -- node [left,midway] {$\lambda\rightarrow0$} (sw.north);
+    \draw[->] (nw.south) -- node {} (sw.north);
+    \draw[->] (sw.east)  -- node [above,midway] {$h\rightarrow0$}(se.west);
+    \draw[->] (ne.south) -- node [left,midway] {$\lambda\rightarrow0$} (se.north);
+    \end{tikzpicture}
+    \caption{Commuting diagram of AP schemes}
+    \label{fig:commuting_diagram_ap}
+\end{figure}
+
+\section{The Maxwell-Euler System and its Rescalling}
+\subsection{Full plasma fluid model}
+The Maxwell system is described by Maxwell's equations whose expression in SI units read
+\begin{align}
+    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday} \\ 
+    \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= -\mathbf{J}, \label{equ:maxwell_ampere} \\
+    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B}\\
+    \nabla \cdot \mathbf{D} &= \rho, \label{equ:maxwell_gauss_D}
+\end{align}
+where the involved quantities are magnetic flux density $\mathbf{B}$, electric field intensity $\mathbf{E}$, electric induction $\mathbf{D}$, magnetic field intensity $\mathbf{H}$, electric current density $\mathbf{J}$ and electric charge density $\rho$.
+These equations are known as Faraday's law (\ref{equ:maxwell_faraday}), Amp\`{e}re's law (\ref{equ:maxwell_ampere}), Gauss's law for magnetism (\ref{equ:maxwell_gauss_B}) and Gauss's law for electric field (\ref{equ:maxwell_gauss_D}).
+For simplicity, we only consider isotropic and homogeneous mediums in vacuum.
+The quantities are thus related by the linear constitutive relations
+\begin{equation*}
+    \mathbf{D} = \varepsilon_0 \mathbf{E}, \ \ \ \mathbf{B} = \mu_0\mathbf{H}, 
+\end{equation*}
+where $\varepsilon_0$ and $\mu_0$ are the vacuum permittivity and permeability of the medium.
+By definition of the electric current density $\mathbf{J}$ and electric charge density $\rho$, they are supposed to satisfy the continuity equation
+\begin{equation} \label{equ:charge_continuity}
+    \partial_t\rho + \nabla \cdot \mathbf{J} = 0.
+\end{equation}
+Besides, on taking the divergence of equations (\ref{equ:maxwell_faraday}) and (\ref{equ:maxwell_ampere}) together with the relation (\ref{equ:charge_continuity}), it is possible to verify that Gauss's laws (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) are consequences of (\ref{equ:maxwell_faraday}) and (\ref{equ:maxwell_ampere}) provided that (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) are satisfied at the initial time.
+In other words, Gauss's laws (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) are redundant, and Faraday's law (\ref{equ:maxwell_faraday}) and Amp\`{e}re's law (\ref{equ:maxwell_ampere}) suffice.
+
+In the Euler system, the motions of gas particles are accounted for through the \emph{Euler equations}.
+Specifically, we equip each species with one set of (compressible) Euler equations, taking into account the effect of electromagnetic fields as well as other processes like collisions and recombination.
+The generic expressions read
+\begin{align} \label{equ:euler_}
+    \partial_t
+    \begin{bmatrix}
+    n_* \\
+    m_*n_* \mathbf{u}_* \\
+    m_*n_* e_*
+    \end{bmatrix}
+    + \nabla \cdot
+    \begin{bmatrix}
+    n_* \mathbf{u}_* \\
+    m_*n_* \mathbf{u}_* \otimes \mathbf{u}_* + p_*\mathbb{I} \\
+    m_*n_* h_* \mathbf{u}_*
+    \end{bmatrix}
+    =
+    \begin{bmatrix}
+    0 \\
+    q_*n_*(\mathbf{E} + \mathbf{u}_* \times \mathbf{B}) \\
+    \mathbf{J}_* \cdot \mathbf{E}
+    \end{bmatrix}
+    +
+    \begin{bmatrix}
+    \Gamma_* \\
+    \mathbf{R}_* \\
+    Q_*
+    \end{bmatrix}.
+\end{align}
+The subscript $*$ represents the indices for different species, and by convention we assign $* = e$ to electrons, $* = i$ to ions, and $* = n$ to neutral atoms.
+The involved fluid quantities are: number density $n_*$, particle mass $m_*$,  charge number $q_*$, velocity $\mathbf{u}_*$, pressure $p_*$, specific total energy $e_* := \frac{1}{2}|\mathbf{u}_*|^2 + \frac{p_*}{m_*n_*(\gamma - 1)}$, specific total enthalpy $h_* := e_* + \frac{p_*}{m_*n_*}$ and current density $\mathbf{J}_* := q_*n_*\mathbf{u}_*$.
+All the species are assumed ideal gases with heat capacity ratio $\gamma=5/3$ for monatomic gases.
+The left-hand side of the equations describes the convection of plasma fluids.
+The first term at the right-hand side denotes Lorentz force in the momentum equation and Joule heating in the energy equation.
+$\Gamma_*, \mathbf{R}_*, Q_*$ are generic terms that include effects of inter-species collision, ionization, recombination, etc.
+
+For the sake of simplicity, we would only consider ion-electron collision in this work.
+Such collisions are modeled by friction terms as follows, and we simply present the expressions without derivation (see \citep[][sec.
+5.6.2]{chen2016}):
+\begin{equation} \label{equ:collision}
+    \mathbf{R}_{e}^{\text{coll}} = \frac{\pi Ze^4m_e^{1/2}}{(4\pi\varepsilon_0)^2(k_BT_e)^{3/2}}\text{ln}\Lambda n_en_i(\mathbf{u}_i - \mathbf{u}_e) = - \mathbf{R}_{i}^{\text{coll}},  
+\end{equation}
+which models the collision force that is applied on the electrons.
+ln$\Lambda$ is called the \emph{Coulomb logarithm}, which typically takes a numerical value of order 10–20 .
+Because of the conservation of momentum, the collision term experienced by ions $\mathbf{R}_{i}^{\text{coll}}$ is just the negative of $\mathbf{R}_{e}^{\text{coll}}$.
+For full details about the ionization and recombination, readers are referred to \cite{fuchs_2021}.
+
+Combination of the two sets of equations (\ref{equ:maxwell_faraday}) to (\ref{equ:maxwell_gauss_D}) and (\ref{equ:euler_}) leads to the governing equations for a multi-species plasma model.
+The coupling of the two subsystems takes effect through the following relations that connect the fluid and electromagnetic quantities
+\begin{equation*}
+    \rho = \sum_* q_*n_*, \ \ \  \mathbf{J} = \sum_* q_*n_*\mathbf{u}_*. 
+\end{equation*}
+
+\subsection{Rescaled Maxwell-Euler system}
+The multi-scale nature of the Euler-Maxwell system is revealed by defining different dimensionless parameters.
+In particular, the quasi-neutrality approximation is clarified.
+The rescaling procedure mostly sticks to that of \cite{degond_2017}.
+
+First, typical values for each quantity, as well as the characteristic length and time scale are specified.
+Rescaled by these values, the magnitude of each term of the equations can be compared according to the presumption on the magnitude of these typical values.
+We define $\overline{x}$ and $\overline{t}$ as space and time scale of interest, by which the reference velocity $\overline{v}$ is defined as $\overline{x}/\overline{t}$.
+The typical magnitudes of electromagnetic fields are $\overline{E}$ and $\overline{B}$.
+The typical magnitudes of fluid quantities are denoted by $\overline{u}$ for plasma drift velocity, $\overline{n}$ for plasma number density, $\overline{T}$ for plasma temperature.
+On top of that, the typical pressure is set $\overline{n}k_B\overline{T}$ with $k_B$ being the Boltzmann constant; the typical value for the specific total energy and enthalpy is set $\overline{u}^2$.
+Together with the physical parameters, namely, permittivity $\varepsilon_0$, permeability $\mu_0$, light speed $c^2 = (\varepsilon_0\mu_0)^{-1}$, Boltzmann constant $k_B$, the elementary charge $e$, and ion mass $m_i$, the following dimensionless parameters are induced,
+\begin{align*} 
+    \xi &:= \frac{\overline{v}}{c} \text{ the velocity of interest to the light speed}, &\\
+    \zeta &:= \frac{\overline{u}}{\overline{v}} \text{ the plasma velocity to the speed of interest}, &\\
+    M &:= \frac{\overline{u}}{v_{th,i}} \text{ the plasma drift velocity to the thermal speed of ions, where } v_{th,i} := \left(\frac{k_B \overline{T}}{m_i}\right)^{1/2}, &\\
+    \eta &:= \frac{e\overline{E}\overline{x}}{m_i\overline{u}^2} \text{ the electric energy to the kinetic energy of ions}, &\\
+    \beta &:= \frac{\overline{v}\overline{B}}{\overline{E}} \text{ the induced electric field to the total electric field}, &\\
+    \lambda &:= \frac{\lambda_D}{\overline{x}} \text{ the dimensionless Debye length, where }\lambda_D := \left(\frac{\varepsilon_0k_B\overline{T}}{e^2\overline{n}}\right)^{1/2}, &\\
+    \varepsilon_*^2 &:= \frac{m_*}{m_i} \text{ the species mass ratio to the ion mass},\ \  * \in \{i,e,n,\cdots\}, &\\
+    g &:= \frac{1}{\overline{n}\lambda_D^3} \text{ the plasma parameter\footnotemark}.&
+\end{align*}
+\footnotetext{It is basically the reciprocal of the number of particles per Debye sphere, see \cite[][sec. 1.1]{gibbon2020}. Classical plasma theory assumes $g \ll 1$.}
+
+The Euler-Maxwell system (\ref{equ:maxwell_faraday}) to (\ref{equ:euler_}) is readily to be rescaled by nondimensionalizing each quantity with respect to its typical value.
+By abuse of notation, the dimensionless quantities have the same symbol with their original ones without incurring any ambiguity.
+For simplicity, we only consider the collision terms, namely $\Gamma_* = 0, \mathbf{R}_* = \mathbf{R}_*^\text{coll}, Q_* = 0$ in (\ref{equ:euler_}), while neglecting other effects.
+The rescaled Euler-Maxwell system reads
+\begin{align}
+    \beta \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday_rescalling} \\ 
+    \lambda^2 \partial_t \mathbf{E} - \frac{\beta \lambda^2}{\xi^2}\nabla \times \mathbf{B} &= - \frac{\zeta}{\eta M^2}\mathbf{J}, \label{equ:maxwell_ampere_rescalling} \\
+    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B_rescalling}\\
+    \lambda^2 \eta M^2 \nabla \cdot \mathbf{E} &= \rho, \label{equ:maxwell_gauss_D_rescalling} \\
+    \partial_t
+    \begin{bmatrix}
+    n_* \\
+    n_* \mathbf{u}_* \\
+    n_* e_*
+    \end{bmatrix}
+    + \nabla \cdot
+    \begin{bmatrix}
+    \zeta n_* \mathbf{u}_* \\
+    \zeta n_* \mathbf{u}_* \otimes \mathbf{u}_* + \zeta M^{-2} \varepsilon_*^{-2} p_*\mathbb{I} \\
+    \zeta n_* h_* \mathbf{u}_*
+    \end{bmatrix}
+    &=
+    \begin{bmatrix}
+    0 \\
+    \eta \zea \varepsilon_*^{-2} q_* n_*\mathbf{E} + \eta \zeta^2 \beta \varepsilon_*^{-2} q_* n_* \mathbf{u}_* \times \mathbf{B} \\
+    \zeta \eta \varepsilon_*^{-2} \mathbf{J}_* \cdot \mathbf{E}
+    \end{bmatrix} +
+    \begin{bmatrix}
+    0 \\
+    \varepsilon_*^{-2}\mathbf{R}_*^{\text{coll}} \\
+    0 
+    \end{bmatrix}, \label{equ:euler_rescalling}
+\end{align}
+where the equation of state becomes $e_* = \frac{1}{2}|\mathbf{u_*}|^2 + M^{-2}\frac{p_*}{\epsilon^2_* n_* (\gamma - 1)}$ and $h_* = e_* + M^{-2}\frac{p_*}{\epsilon^2_* n_*}$.
+For a fully-ionized gas, we have the original expression of $\mathbf{R}_*^{\text{coll}}$ in (\ref{equ:collision}), and its rescaled expression becomes
+\begin{equation*}
+    \mathbf{R}_i^{\text{coll}} = \frac{Z\text{ln}\Lambda}{16\pi}g\lambda^{-1}M^{-1}\varepsilon_en_en_i(\mathbf{u}_i - \mathbf{u}_e). 
+\end{equation*}
+
+Following the assumption in \cite{degond_2017}, the reference speed $\overline{v}$ is of the same scale with the plasma speed $\overline{u}$ and the thermal speed $v_{th,i}$ whereas it is much smaller than the light speed $c$.
+To study the quasi-neutral regime, the dimensionless Debye length $\lambda$ is an asymptotic parameter ranging in $[0,1]$.
+It is assumed that $\alpha$ has the same magnitude as $\lambda$, and $\eta$ and $\beta$ are of order one.
+
+Special treatment is needed for the collision term.
+One would notice the inverse proportionality to $\lambda$, which would introduce a singular perturbation to the Euler system as $\lambda \rightarrow 0$.
+However, the validity of such a collision model is doubtful when $\lambda \rightarrow 0$.
+From the physical viewpoint, the shielding effect characterized by Debye length $\lambda$ makes the impact parameter no larger than $\lambda$.
+The $\lambda \rightarrow 0$ limit implies that the collisions happen in the atomic length scale, in which quantum-mechanical effects must be taken into effect \citep{frank_1972}.
+Therefore, for the sake of simplicity, we decide to assume $g \sim \lambda$ and keep the prefactor of collision term constant $\alpha^{\text{coll}}$ throughout the simulation\footnote{The reasonableness of this assumption is questionable.}.
+
+In summary, we make the following choices
+\begin{align*}
+    \xi \sim g \sim \lambda \in [0,1], \ \ \ \zeta \sim M \sim \eta \sim \beta \sim \mathcal{O}(1).
+\end{align*}
+
+Under such assumptions on these dimensionless parameters, the rescaled Euler-Maxwell system is simplified into a parametrized system with the dimensionless Debye length $\lambda$ being the asymptotic parameter
+\begin{align}
+    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday_rescaled} \\ 
+    \lambda^2 \partial_t \mathbf{E} - \nabla \times \mathbf{B} &= - \mathbf{J}, \label{equ:maxwell_ampere_rescaled} \\
+    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B_rescaled}\\
+    \lambda^2 \nabla \cdot \mathbf{E} &= \rho, \label{equ:maxwell_gauss_D_rescaled} \\
+    \partial_t
+    \begin{bmatrix}
+    n_* \\
+    n_* \mathbf{u}_* \\
+    n_* e_*
+    \end{bmatrix}
+    + \nabla \cdot
+    \begin{bmatrix}
+    n_* \mathbf{u}_* \\
+    n_* \mathbf{u}_* \otimes \mathbf{u}_* + \varepsilon_*^{-2} p_*\mathbb{I} \\
+    n_* h_* \mathbf{u}_*
+    \end{bmatrix}
+    &=
+    \begin{bmatrix}
+    0 \\
+    \varepsilon_*^{-2} q_* n_* (\mathbf{E} + \mathbf{u}_* \times \mathbf{B}) \\
+    \varepsilon_*^{-2} \mathbf{J}_* \cdot \mathbf{E}
+    \end{bmatrix}+
+    \begin{bmatrix}
+    0 \\
+    \varepsilon_*^{-2}\mathbf{R}_*^{\text{coll}} \\
+    0 
+    \end{bmatrix}, \label{equ:euler_rescaled}
+\end{align}
+with the equation of state $e_* = \frac{1}{2}|\mathbf{u_*}|^2 + \frac{p_*}{\varepsilon^2_* n_* (\gamma - 1)}$ and $h_* = e_* + \frac{p_*}{\varepsilon^2_* n_*}$.
+For a fully-ionized gas with only ions and electrons,
+\begin{equation} \label{equ:collision_rescaled} 
+    \mathbf{R}_i^{\text{coll}} = \alpha^{\text{coll}}n_en_i(\mathbf{u}_i - \mathbf{u}_e) = - \mathbf{R}_e^{\text{coll}}.
+\end{equation}
+
+Although the rescaling of the equations involves considerable physical intuitions on the decision of typical values and their magnitudes, which is crucial to reach a physically meaningful problem, we are now in a position to forget this reasoning, and focus on the singular perturbation problem parameterized by $\lambda$.
+The rescaling enables us to identify the magnitude of each term of the equations, which is revealed by the prefactor polynomial of $\lambda$.
+
+\subsection{Quasi-neutral limit} \label{sec:quasi-neutral_limit}
+As is already discussed in section \ref{sec:quasi-neutrality}, the quasi-neutrality, being an important character of plasmas, refers to the fact that the net charge of the free electrons and ions in plasmas cancel out over an area of the same order as the Deybe length $\lambda_D$.
+When the typical length scale $\overline{x}$ is of magnitudes larger than $\lambda_D$, the condition $\rho = 0$ can be approximately satisfied.
+
+Such behavior is clearly explained through the rescaled Euler-Maxwell system (\ref{equ:maxwell_faraday_rescaled}) to (\ref{equ:euler_rescaled}).
+By formally taking dimensionless Debye length $\lambda$ to zero\footnote{The convergence of the solutions as $\lambda$ tending to zero is discussed in \cite[][chap.
+2]{remi_2014}}, the Maxwell system becomes
+\begin{align}
+    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday_limit} \\ 
+    - \nabla \times \mathbf{B} &= - \mathbf{J}, \label{equ:maxwell_ampere_limit} \\
+    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B_limit}\\
+     0 &= \rho. \label{equ:maxwell_gauss_D_limit}
+\end{align}
+One can notice that the quasi-neutral condition (\ref{equ:maxwell_gauss_D_limit}) is the consequence of taking $\lambda = 0$ in Gauss's law for electric field (\ref{equ:maxwell_gauss_D_rescaled}).
+Like the non-neutral case, Gauss's laws (\ref{equ:maxwell_gauss_B_limit}) (\ref{equ:maxwell_gauss_D_limit}) are the consequence of (\ref{equ:maxwell_faraday_limit}) (\ref{equ:maxwell_ampere_limit}) provided (\ref{equ:maxwell_gauss_B_limit}) (\ref{equ:maxwell_gauss_D_limit}) are satisfied at the initial time.
+
+The vanishing time derivative of $\mathbf{E}$-field is an indicator of the singular perturbation nature of the quasi-neutral model.
+To be specific, in the non-neutral model the $\mathbf{E}$-field evolves with time whereas in the quasi-neutral model it responds instantaneously to other quantities according to the constraint (\ref{equ:maxwell_ampere_limit}).
+To make it clear, we replace the equation (\ref{equ:maxwell_ampere_rescaled}) by the sum of the curl of (\ref{equ:maxwell_faraday_rescaled}) and the time-derivative of (\ref{equ:maxwell_ampere_rescaled}).
+Meanwhile exploiting the momentum equation in (\ref{equ:euler_rescaled}) to express $\partial_t\mathbf{J}$, we end up getting the reformulated Maxwell's equations
+\begin{align}
+    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday_reform}\\
+    \lambda^2\partial_t^2 \mathbf{E} + \nabla \times \nabla \times \mathbf{E} &= - a\mathbf{E} - \mathbf{b}, \label{equ:maxwell_ampere_reform}\\
+    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B_reform}\\
+    \lambda^2\nabla \cdot \mathbf{E} &= \rho, \label{equ:maxwell_gauss_D_reform}
+\end{align}
+where
+\begin{equation*}
+    a = \sum_*\varepsilon_*^{-2}q_*^2n_*, \ \ \ \mathbf{b} = \sum_* \epsilon_*^{-2}q_*^2n_*\mathbf{u}_*\times\mathbf{B} - q_*\nabla\cdot(n_* \mathbf{u}_* \otimes \mathbf{u}_* + \varepsilon_*^{-2}p_*\mathbb{I}).
+\end{equation*}
+It is easy to check that (\ref{equ:maxwell_faraday_reform}) to (\ref{equ:maxwell_ampere_reform}) is equivalent to (\ref{equ:maxwell_faraday_rescaled}) to (\ref{equ:maxwell_gauss_D_rescaled}) as soon as (\ref{equ:maxwell_ampere_rescaled}) is satisfied at the initial time.
+The equation (\ref{equ:maxwell_ampere_reform}) implies the shift from the hyperbolic nature to the elliptic nature of the $\mathbf{E}$-field as $\lambda\rightarrow0$.
+One of the key aims of designing an AP scheme is to reproduce this shift at the discrete level.
+
+\subsection{Boundary conditions}
+On yielding the rescaled system (?) - (?), we would like to discuss about the boundary conditions here.
+One cannot directly impose any BC suitable for the non-limit model since it could possibly be ill-posed for the limiting model.
+In our case, we dealing with the shifting between the full Maxwell equations and the eddy-current model.
+
+Since the scheme is supposed to work for both regimes, the BCs ought to be uniformly well-posed.
+An example is given to convey the idea.
+Let's look at the continuous non-neutral Amp\`{e}re's law (\ref{equ:maxwell_ampere_rescaled})
+\begin{equation*}
+    \lambda^2 \partial_t \mathbf{E} - \nabla \times \mathbf{B} = - \mathbf{J},
+\end{equation*}
+which loses its hyperbolic character and becomes a constraint when $\lambda \rightarrow 0$. Now consider two boundary conditions
+\begin{itemize}
+    \item[-]  $\mathbf{E}\cdot\mathbf{n} = 0$ on $\partial\Omega$;
+    \item[-] $\nabla \times \mathbf{B} \cdot\mathbf{n} = \mathbf{J}\cdot\mathbf{n}$ on $\partial\Omega$. 
+\end{itemize}
+They are equivalent when $\lambda$ is non-zero provided $\mathbf{E}\cdot\mathbf{n}|_{\partial\Omega}$ is zero at the initial time.
+However, setting $\lambda = 0$ destroys the equivalence.
+The second BC no longer implies the first one and becomes redundant since the quasi-neutral Amp\`{e}re's law already enforces such condition, which ruins the well-posedness of the quasi-neutral problem.
+Hence the first BC is the one that is supposed to be employed.
+
+From the viewpoint of the discrete model, the continuous equations are discretized into a set of algebraic equations according to the scheme, and they are assembled into a linear system that needs to be solved at each time step.
+The redundancy of the second BC at limiting case results in the singularity of the linear system since the BC can be derived by linear operations from the algebraic form of the PDEs.
+
+\todo{Give a sketch of an abstract domain, and assign BCs to each boundary for both Euler and Maxwell.}
+
+\section{Previous Work: 1D Discretization}
+In this section we briefly discuss the underlying work \cite{degond_2012} on which our work is built.
+Meanwhile, this section also serves as a preliminary case study such that readers can better understand the 3D scheme that we present.
+\subsection{1D plasma model}
+The 3D problem is projected onto the 1D axis by assuming vanishing traverse derivatives (see Fig.
+\ref{fig:1d-frame} for the definition of reference frame).
+Besides, $u_y, E_y, B_x, B_z$ are set zero for simplicity, which amounts to considering the TE mode.
+The collision between particles is omitted for the time being.
+\begin{figure}
+    \centering
+    \includegraphics[scale=0.2]{1d_frame.png}
+    \caption{Projection of the 3D model onto $z$-axis.
+Let us consider a Cartesian mesh doublet.
+The reduction is accomplished by assigning the quantities defined on each cross-section, which is parallel to the $x$-$y$ plane, to its intersection point at $z$-axis.
+Since it is assumed that no variations occur in each cross-section, the quantities in 3D can be compressed by the ones that locate at each mesh point on the $z$-axis.}
+    \label{fig:1d-frame}
+\end{figure}
+
+Take all the traverse derivatives $\partial_x, \partial_y$ and $u_y, E_y, B_x, B_z$ to be zero, we get the one-fluid Euler-Maxwell system in 1D:
+\begin{align*}
+    \partial_t n + \partial_z(nu_z) &= 0, \\
+    \varepsilon^2[\partial_t(nu_x) + \partial_z(nu_zu_x)] &= - n(E_x - u_zB_y), \\
+    \varepsilon^2[\partial_t(nu_z) + \partial_z(nu_z^2)] + \partial_z(p(n)) &= -n(E_z + u_xB_y), \\
+    \partial_t B_y + \partial_z E_x &= 0, \\
+    \lambda^2 \partial_t E_x + \partial_z B_y &= nu_x, \\
+    \lambda^2 \partial_t E_z &= nu_z, \\
+    \lambda^2 \partial_z E_z &= 1 - n,
+\end{align*}
+as well as the quasi-neutral limit by taking $\lambda \rightarrow 0$:
+\begin{align*}
+    n &= 1\\
+    \varepsilon^2 \partial_t(u_x) &= - E_x, \\
+    E_z + u_xB_y &= 0, \\
+    u_z &= 0 \\
+    \partial_t B_y + \partial_z E_x &= 0, \\
+    \partial_z B_y &= nu_x
+\end{align*}
+\subsection{Finite difference on staggered grid}
+\todo{Add illustration about 1D FDTD}
+\subsection{Semi-implicit AP time-stepping}
+Adapt the AP scheme (\ref{equ:maxwell_faraday_ap}) to (\ref{equ:euler_ap}) to this case, and we end up with
+\begin{align}
+    \frac{n^{m+1}_k - n^m_k}{\delta^m} + \frac{\textcolor{blue}{f^{m+1/2}_{n,k+1/2} - f^{m+1/2}_{n,k-1/2}}}{h} &= 0, \label{equ:1f1d-n}\\
+    \frac{(nu_x)^{m+1}_k - (nu_x)^m_k}{\delta^m} + \frac{f^{m}_{u_x,k+1/2} - f^{m}_{u_x,k-1/2}}{h} &= -\frac{n^m_k \textcolor{blue}{E^{m+1}_{x,k}}}{\varepsilon^2} + \frac{n^m_k u^m_{z,k}\Tilde{B}^m_{y,k}}{\varepsilon^2}, \label{equ:1f1d-nux}\\
+    \frac{(nu_z)^{m+1}_k - (nu_z)^m_k}{\delta^m} + \frac{f^{m}_{u_z,k+1/2} - f^{m}_{u_z,k-1/2}}{h} &= - \frac{n^m_k \textcolor{blue}{\Tilde{E}^{m+1}_{z,k}}}{\varepsilon^2} - \frac{n^m_k u^m_{x,k}\Tilde{B}^m_{y,k}}{\varepsilon^2}, \label{equ:1f1d-nuz}\\
+    \frac{B^{m+1}_{y,k+1/2} - B^{m}_{y,k+1/2}}{\delta^m} + \frac{\textcolor{blue}{E^{m+1}_{x,k+1} - E^{m+1}_{x,k}}}{h} &= 0, \label{equ:1f1d-By}\\
+    \lambda^2 \frac{E^{m+1}_{x,k} - E^{m}_{x,k}}{\delta^m} + \frac{\textcolor{blue}{B^{m+1}_{y,k+1/2} - B^{m+1}_{y,k-1/2}}}{h} &= \textcolor{blue}{(nu_x)^{m+1}_k}, \label{equ:1f1d-Ex}\\
+    \lambda^2 \frac{E^{m+1}_{z,k+1/2} - E^{m}_{z,k+1/2}}{\delta^m} &= \textcolor{blue}{f^{m+1}_{n,k+1/2}}, \label{equ:1f1d-Ez}
+\end{align}
+where 
+\begin{equation*}
+    \Tilde{E}^m_{z,k} = \frac{1}{2}(E^m_{z,k+1/2} + E^m_{z,k-1/2}), \ \ \ \Tilde{B}^m_{y,k} = \frac{1}{2}(B^m_{y,k+1/2} + B^m_{y,k-1/2}),
+\end{equation*}
+is the consequence of interpolation of electromagnetic field, 
+and the fluxes read
+\begin{align*}
+    f^{m+1/2}_{n,k+1/2} & = \frac{1}{2}[\textcolor{blue}{(nu_z)^{m+1}_k + (nu_z)^{m+1}_{k+1}} + \mu^m_{k+1/2}(n^m_k - n^m_{k+1})], \\
+    f^{m}_{u_x,k+1/2} & = \frac{1}{2}[(nu_zu_x)^{m}_k + (nu_zu_x)^{m}_{k+1} + \mu^m_{k+1/2}((nu_x)^m_k - (nu_x)^m_{k+1})], \\
+    f^{m}_{u_z,k+1/2} & = \frac{1}{2}[(nu_z^2 + p(n)/\varepsilon^2)^{m}_k + (nu_z^2 + p(n)/\varepsilon^2)^{m}_{k+1} + \mu^m_{k+1/2}((nu_z)^m_k - (nu_z)^m_{k+1})]. \\
+\end{align*}
+
+\section{Discretization in 3D}
+\subsection{Primal-dual staggered mesh}
+A mesh doublet $(\mathcal{M}, \Tilde{\mathcal{M}})$ is required for the formulation of FIT in the need of incorporating the material laws.
+The spatial domain is discretized by two meshes that interlace with each other.
+They are called \emph{primal} mesh $\mathcal{M}$ and \emph{dual} mesh $\Tilde{\mathcal{M}}$.
+The essential duality property requires that \emph{each edge of one mesh penetrates a face of the other mesh and that each vertex of one mesh lies at the center of a cell of the other mesh} \citep{weiland_2003}.
+We demonstrate such interlacing character by an example in Fig.
+\ref{fig:illustration_primal_dual}, where the primal mesh is composed of triangular prisms and the dual mesh is composed of hexagon prisms.
+The dual mesh can be generated as the Voronoi decomposition of the primal mesh \citep{fuchs_2021}.
+Compared to the constraint of FDTD to Cartesian meshes, FIT is compatible with a wide range of mesh types.
+An example of primal and dual meshes is given in Fig.
+\ref{fig:primal_dual_meshes}.
+
+To clarify the terminology, the \emph{vertices, edges, faces} and \emph{volumes} (denoted by $P,L,A$ and $V$ respectively) make up a mesh.
+Also, they are uniformly termed \emph{facets} with zero, one, two and three dimensions.
+
+\begin{figure}
+    \centering
+    \begin{tikzpicture}
+    \def\primalstyle{thick}
+    \def\dualstyle{thick}
+    \coordinate (P0) at (0cm, 0cm);
+    \foreach \i in {1,2,...,6}
+    {
+    \coordinate (P\i) at ({60*\i-30}:2cm);
+    \draw[\primalstyle] (P0) -- (P\i);
+    }
+    \draw[\primalstyle] (P1) -- (P2) node[left=5mm]{\Large $\mathcal{M}$} -- (P3) -- (P4) -- (P5) -- (P6) -- cycle;
+    \begin{scope}[shift={(3cm,0.5cm)}]
+        \coordinate (PP0) at (0cm, 0cm);
+        \foreach \i in {1,2,...,6}
+        {
+        \coordinate (PP\i) at ({60*\i-30}:2cm);
+        \draw[gray] (PP0) -- (PP\i);
+        }
+    \end{scope}
+
+    \draw[\primalstyle] (PP1) -- (PP2);
+    \draw[gray] (PP2) -- (PP3);
+    \draw[gray] (PP3) -- (PP4);
+    \draw[gray] (PP4) -- (PP5);
+    \draw[\primalstyle] (PP5) -- (PP6);
+    \draw[\primalstyle] (PP6) -- (PP1);
+
+    \draw[gray] (P0) -- (PP0);
+    \draw[\primalstyle] (P1) -- (PP1);
+    \draw[\primalstyle] (P2) -- (PP2);
+    \draw[gray] (P3) -- (PP3);
+    \draw[gray] (P4) -- (PP4);
+    \draw[\primalstyle] (P5) -- (PP5);
+    \draw[\primalstyle] (P6) -- (PP6);
+
+    \foreach \i in {1,2,...,6}
+    {
+    \coordinate (D\i) at ({60*\i-60}:{2./1.737});
+    }
+    \draw[dashed, blue] (D1) -- (D2) -- (D3) -- (D4) -- (D5) -- (D6) -- cycle;
+    \begin{scope}[shift={(1.5,0.25)}]
+        \foreach \i in {1,2,...,6}
+        {
+        \coordinate (DD\i) at ({60*\i-60}:{2./1.737});
+        }
+    \end{scope}
+    \draw[blue] (DD1) -- (DD2) -- (DD3) -- (DD4) -- (DD5) -- (DD6) -- cycle;
+    \draw[blue] (D1) -- (DD1);
+    \draw[blue] (D2) -- (DD2);
+    \draw[blue] (D3) -- (DD3);
+    \draw[blue] (D4) -- (DD4);
+    \draw[blue] (D5) -- (DD5);
+    \draw[blue] (D6) -- (DD6);
+
+    \begin{scope}[shift={(-1.5,-0.25)}]
+        \foreach \i in {1,2,...,6}
+        {
+        \coordinate (DDD\i) at ({60*\i-60}:{2./1.737});
+        }
+    \end{scope}
+    \draw[blue, ultra thick] (DDD1) -- (DDD2) -- (DDD3) node[left=3mm]{\textcolor{blue}{\Large $\Tilde{\mathcal{M}}$}} -- (DDD4) -- (DDD5) -- (DDD6) -- cycle;
+    \draw[blue, ultra thick] (D1) -- (DDD1);
+    \draw[blue, ultra thick] (D2) -- (DDD2);
+    \draw[blue, ultra thick] (D3) -- (DDD3);
+    \draw[blue] (D4) -- (DDD4);
+    \draw[blue] (D5) -- (DDD5);
+    \draw[blue, ultra thick] (D6) -- (DDD6);
+
+    \fill[blue!50, opacity=0.2] (D1) -- (D2) -- (D3) -- (D4) -- (D5) -- (D6);
+
+    \end{tikzpicture}
+    \caption{Illustration of primal and dual meshes.
+Six primal cells, which are triangle prisms, are depicted by black and gray edges.
+One dual cell, which is a hexagon prism, is depicted by blue edges.
+The dashed hexagon represents the intersection of the dual cell and primal cells.
+This particular type of mesh composed of prisms is picked as a demonstration since it is used in our numerical experiments.}
+    \label{fig:illustration_primal_dual}
+\end{figure}
+\subsection{Discrete Maxwell equations: DEC}
+\todo{Reformulate this section in the spirit of DEC. Now it is a bit tedious.}
+
+The FIT is established based on the integral form of Maxwell's equations:
+\begin{align}
+    &\oint_{\partial A} \mathbf{E} \cdot d\mathbf{s} \ = - \iint_A \frac{\partial \mathbf{B}}{\partial t} \cdot d\mathbf{A}, \label{equ:maxwell_int_faraday}\\
+    &\oint_{\partial A} \mathbf{H} \cdot d\mathbf{s} \ = \iint_A \left(\frac{\partial \mathbf{D}}{\partial t} + \mathbf{J}\right) \cdot d\mathbf{A}, \label{equ:maxwell_int_ampere}\\
+    &\oint_{\partial V} \mathbf{B} \cdot d\mathbf{A} = 0, \label{equ:maxwell_int_gauss_B}\\
+    &\oint_{\partial V} \mathbf{D} \cdot d\mathbf{A} = \iiint_V \rho dV. \label{equ:maxwell_int_gauss_D}
+\end{align}
+where $A, V$ stand for any 2-D faces and 3-D cells in the spatial domain.
+These equations are consequence of curl theorem and divergence theorem, and correspond to the integral form of Faraday's law (\ref{equ:maxwell_int_faraday}), Ampere's law (\ref{equ:maxwell_int_ampere}) and Gauss's laws for magnetic flux (\ref{equ:maxwell_int_gauss_B}) and electric induction (\ref{equ:maxwell_int_gauss_D}).
+The fields are related by the material laws
+\begin{align} \label{equ:maxwell_material_laws}
+    \mathbf{B} = \mu_0 \mathbf{H},\ \ \ \mathbf{D} = \varepsilon_0 \mathbf{E}.
+\end{align}
+
+The discrete Maxwell system is obtained by applying and collecting the equations (\ref{equ:maxwell_int_faraday}) (\ref{equ:maxwell_int_gauss_B}) on each facet of the primal mesh $\mathcal{M}$ and the equations (\ref{equ:maxwell_int_ampere}) (\ref{equ:maxwell_int_gauss_D}) on each facet of the dual mesh $\Tilde{\mathcal{M}}$.
+We denote the vertices by $(P_i)_{i=1}^{N_P}$, $(\Tilde{P}_i)_{i=1}^{N_{\Tilde{P}}}$, edges by $(L_i)_{i=1}^{N_L}$, $(\Tilde{L}_i)_{i=1}^{N_{\Tilde{L}}}$, faces by $(A_i)_{i=1}^{N_A}$, $(\Tilde{A}_i)_{i=1}^{N_{\Tilde{A}}}$, and cells by $(V_i)_{i=1}^{N_V}$, $(\Tilde{V}_i)_{i=1}^{N_{\Tilde{V}}}$ where the ones with tilde belong to the dual mesh.
+Recall the duality property that $\mathcal{M}$ and $\mathcal{M}'$ interlaces with each other in the sense that each edge penetrates a face of the other mesh.
+This leads to $N_L = N_{\Tilde{A}}$ and $N_A = N_{\Tilde{L}}$\footnote{Note that here the influence of boundary is not considered.}.
+The equations (\ref{equ:maxwell_int_faraday}) to (\ref{equ:maxwell_int_gauss_D}) can be rewritten into
+
+\begin{align}
+    &\sum_{j:L_j\in\partial A_i} \underbrace{\int_{L_j} \mathbf{E} \cdot d\mathbf{s}}_{e_j} = - \frac{\partial}{\partial t} \underbrace{\iint_{A_i} \mathbf{B} \cdot d\mathbf{A}}_{b_i},\ \ \ i = 1,...,N_A, \label{equ:maxwell_grid_faraday} \\
+    &\sum_{j:\Tilde{L}_j\in\partial \Tilde{A}_i} \underbrace{\int_{\Tilde{L}_j} \mathbf{H} \cdot d\mathbf{s}}_{h_j} = \frac{\partial}{\partial t} \underbrace{\iint_{\Tilde{A}_i} \mathbf{D} \cdot d\mathbf{A}}_{d_i} + \underbrace{\iint_{\Tilde{A}_i} \mathbf{J} \cdot d\mathbf{A}}_{j_i}, \ \ \ i = 1,...,N_{\Tilde{A}}, \label{equ:maxwell_grid_ampere}\\
+    &\sum_{j:A_j\in \partial V_i} \iint_{A_j} \mathbf{B} \cdot d\mathbf{A} = 0,\ \ \ i = 1,..., N_V,\label{equ:maxwell_grid_gauss_B}\\
+    &\sum_{j:\Tilde{A}_j \in \partial\Tilde{V}_i}\iint_{\Tilde{A}_j} \mathbf{D} \cdot d\mathbf{A} = \underbrace{\iiint_{\Tilde{V}_i} \rho dV}_{q_i},\ \ \ i = 1,...,N_{\Tilde{V}}.
+\label{equ:maxwell_grid_gauss_D}
+\end{align}
+For the sake of neat illustration, we temporarily neglect the boundary conditions which will be discussed later.
+As is indicated in (\ref{equ:maxwell_grid_faraday})(\ref{equ:maxwell_grid_ampere}) by the underbraces, the discrete variables are chosen as the integral quantities of field vectors on edges or faces.
+Packing these scalar quantities into vectors, we define
+\begin{equation} \label{equ:fit_scale_vector}
+    \mathbf{e} := (e_i)_{i=1}^{N_L},\ \ \mathbf{b} := (b_i)_{i=1}^{N_A}, \ \ \mathbf{h} := (h_i)_{i=1}^{N_{\Tilde{L}}}, \ \ \mathbf{d} := (d_i)_{i=1}^{N_{\Tilde{A}}}, \ \ \mathbf{j} := (j_i)_{i=1}^{N_{\Tilde{A}}}, \ \ \mathbf{q} := (q_i)_{i=1}^{N_{\Tilde{V}}}.
+\end{equation}
+
+The next step is to transform the discrete Maxwell system (\ref{equ:maxwell_grid_faraday}) to (\ref{equ:maxwell_grid_gauss_D}) into a set of algebraic equations.
+One should note that the sign of each scalar depends on the orientation of the facet on which it is integrated.
+To uniquely determine the meaning of these quantities, an \emph{internal orientation} is assigned to every facet of the primal mesh $\mathcal{M}$.
+This attribute defines the orientations of edges and outer normals of faces.
+Besides, since the application of curl theorem and divergence theorem entails the orientation relations of edge-to-face and face-to-volume respectively, another orientation attribute, \emph{induced orientation}, is introduced to specify this topology.
+An induced orientation of a $k$-dim facet $f$ with respect to a $(k+1)$-dim facet $f'$ that contains $f$ is determined by the internal orientation of $f'$ according to some rule.
+An example is shown in Fig.
+\ref{fig:illustration_external_orientation}.
+These topological attributes are inherent for a mesh and can be set at will.
+
+\begin{figure}
+    \centering
+
+\begin{tikzpicture}
+\coordinate (P1) at (0,0);
+\coordinate (P2) at (2,2);
+\draw[decoration={markings, 
+    mark= at position 0.55 with {\arrow[scale=1.5]{to}}}
+    ,postaction={decorate}, very thick, blue] (P1) -- (P2);
+\node at (1,1.5) {\textcolor{blue}{$L$}};
+\draw[fill=black] (P1) circle (0.1) node[above=3mm] {$P_1$} node[below=2mm] {$(-)$};
+\draw[fill=black] (P2) circle (0.1) node[above=2mm] {$P_2$} node[below=2mm] {$(+)$};
+
+\begin{scope}[shift={(5, 0)}]
+\coordinate (Q1) at (0,0);
+\coordinate (Q2) at (2cm, -0.5cm);
+\coordinate (Q3) at (3cm, 1cm);
+\draw[decoration={markings, 
+    mark= at position 0.5 with {\arrow[scale=1]{to}}}
+    , postaction={decorate}, very thick] (Q1) -- node[below=1.5mm]{$L_1$} (Q2);
+    \draw[decoration={markings, 
+    mark= at position 0.5 with {\arrow[scale=1]{to}}}
+    , postaction={decorate}, very thick] (Q2) -- node[right,yshift=-1.5mm]{$L_2$} (Q3);
+    \draw[decoration={markings, 
+    mark= at position 0.5 with {\arrow[scale=1]{to}}}
+    , postaction={decorate}, very thick] (Q3) -- node[above,xshift=-3mm] {$L_3$}(Q1);
+
+\fill[blue, opacity=0.25] (Q1) -- (Q2) -- (Q3);
+\draw[decoration={markings, 
+    mark= at position 1 with {\arrow[scale=1.5]{to}}}
+    , postaction={decorate}, very thick, blue](barycentric cs:Q1=1,Q2=1,Q3=1) -- ([shift={(0,2cm)}] barycentric cs:Q1=1,Q2=1,Q3=1) node[right,xshift=1mm] {\textcolor{blue}{$A$}}; 
+\end{scope}
+
+\begin{scope}[shift={(12,0)}]
+\coordinate (S1) at (0,0);
+\coordinate (S2) at (-1,0.5);
+\coordinate (S3) at (1.5,1);
+\coordinate (S4) at (0.5,2.5);
+\draw[very thick, blue] (S1) -- (S2) -- (S4) -- cycle;
+\fill[gray, opacity=0.2] (S1) -- (S2) -- (S4);
+\draw[very thick, blue] (S1) -- (S3) -- (S4) -- cycle;
+\fill[gray, opacity=0.2] (S1) -- (S3) -- (S4);
+\draw[blue, thin] (S2) -- (S3);
+\draw[decoration={markings, 
+    mark= at position 1 with {\arrow[scale=1]{to}}}
+    , postaction={decorate}, very thick] (barycentric cs:S1=1,S2=1,S4=1) -- ([shift={(-1,0.5)}] barycentric cs:S1=1,S2=1,S4=1) node[above] {$A_1$};
+\coordinate (O1) at (barycentric cs:S1=1,S2=1,S3=1);
+\coordinate (O2) at ([shift={(0,-1)}] barycentric cs:S1=1,S2=1,S3=1);
+\coordinate (S)  at (intersection of O1--O2 and S1--S3);
+\draw[very thick, dotted] (O1) -- (S);
+\draw[decoration={markings, 
+    mark= at position 1 with {\arrow[scale=1]{to}}}
+    , postaction={decorate}, very thick] (S) -- (O2) node[right] {$A_2$};
+\draw[decoration={markings, 
+    mark= at position 1 with {\arrow[scale=1]{to}}}
+    , postaction={decorate}, very thick] (barycentric cs:S1=1,S3=1,S4=1) -- ([shift={(1,0.4)}] barycentric cs:S1=1,S3=1,S4=1) node[right] {$A_3$} ;
+\node at (S4) [left, xshift=-2mm] {\textcolor{blue}{$V$}};
+\end{scope}
+\end{tikzpicture}
+    \caption{Illustration of induced orientations.
+As per our rule, the ending vertex of an edge is positively oriented while the starting point is negatively oriented; the orientations of edges with respect to a face obey the right-hand rule; a face of a volume are oriented with its outer normal.
+Note that the rule can be freely set.}
+    \label{fig:illustration_external_orientation}
+\end{figure}
+
+With the aid of both internal and induced orientations, the facet-to-facet relations can be summarized by matrices containing only $\{-1,0,0\}$, which are called \emph{incidence matrices}.
+To describe the primal face-to-edge incidence relation, for instance, a sparse $N_A \times N_L$-matrix $\mathbb{C}$ is assembled whose $(i,j)$-entry is assigned $+1$ if the internal orientation of edge $L_j$ and its induced orientation with respect to face $A_i$ coincides; it is assigned $-1$ if two orientations are opposite; and assigned $0$ if $L_j$ is not a subset of the boundary of $A_i$.
+Discrete Faraday's law (\ref{equ:maxwell_grid_faraday}) is thus reformulated by:
+\begin{equation*}
+    \mathbb{C}\mathbf{e} = - \frac{\text{d}}{\text{d}t} \mathbf{b}.
+\end{equation*}
+As the incidence matrix $\mathbb{C}$ makes up the curl operator in a discrete manner, it is referred to as the \emph{discrete curl operator} for a certain primal mesh.
+
+Given $\mathcal{M}$, the generation of $\Tilde{\mathcal{M}}$ is usually affiliated to $\mathcal{M}$ in terms of geometry, indexing, and topology.
+Although the latter two attributes can be defined with no dependence on $\mathcal{M}$, conventionally one specifies them relying on those of $\mathcal{M}$ for the sake of convenience in both formulation and implementation.
+Recall that primal edges (resp.
+faces) and dual faces (resp.
+edges) intersect in a one-to-one manner.
+Therefore, one can equate the index of a dual edge (resp.
+face) to that of its intersecting primal face (resp.
+edge).
+Furthermore, the internal orientation of a dual facet can be linked to that of its associated primal facet.
+With these constraints, discrete Ampere's law (\ref{equ:maxwell_grid_ampere}) can be reformulated into:
+\begin{equation*}
+    \Tilde{\mathbb{C}}\mathbf{h} = \frac{\text{d}}{\text{d}t} \mathbf{d} + \mathbf{j},
+\end{equation*}
+where $\Tilde{\mathbb{C}}$ is the dual face-to-edge incidence matrix of size $N_{\Tilde{A}} \times N_{\Tilde{L}}$, satisfying $\Tilde{\mathbb{C}} = \mathbb{C}^T$.
+
+In a similar way, discrete Gauss's laws (\ref{equ:maxwell_grid_gauss_B})(\ref{equ:maxwell_grid_gauss_D}) is rewritten into:
+\begin{equation*}
+    \mathbb{D}\mathbf{b} = 0, \ \ \ \  \Tilde{\mathbb{D}}\mathbf{d} = \mathbf{q},
+\end{equation*}
+with $\mathbb{D}$ being the primal cell-to-face incidence matrix of size $N_{V} \times N_{A}$, and $\Tilde{\mathbb{D}}$ being the dual cell-to-face incidence matrix of size $N_{\Tilde{V}} \times N_{\Tilde{A}}$.
+Since they serve as the discrete version of the div operator, they are also referred to as \emph{discrete div operator}.
+It is readily to be checked the following relations
+\begin{equation*}
+    \mathbb{D}\mathbb{C} = 0, \ \ \ \ \Tilde{\mathbb{D}}\Tilde{\mathbb{C}} = 0,
+\end{equation*}
+which is the discrete version of the vector calculus $\nabla \cdot (\nabla \times u) = 0$.
+
+Additionally, the grad operator at the discrete level can be constructed by edge-to-vertex incidence matrices $\mathbb{G}$ of size $N_L \times N_P$ and $\Tilde{\mathbb{G}}$ of size $N_{\Tilde{L}} \times N_{\Tilde{P}}$.
+Given an electric potential vector $\bm{\varphi}$ whose components are defined at primal vertices, for example, the edge voltage vector $\mathbf{e}$ can thus be computed by
+\begin{equation*}
+    \mathbf{e} = \mathbb{G}\bm{\varphi}.
+\end{equation*}
+
+The material laws (\ref{equ:maxwell_material_laws}) need to be reformulated within this framework.
+The relations between scalar vectors, in the form of $\mathbf{b} = \mathbb{M}_\mu \mathbf{h}$ and $\mathbf{d} = \mathbb{M}_\varepsilon \mathbf{e}$, are to be derived.
+In the simplest case where permittivity $\mu$ and permeability $\varepsilon$ are homogeneous in the domain, and the orthogonality\footnote{The edges of one mesh penetrate the faces of the other mesh in an orthogonal manner.} of ($\mathcal{M}, \Tilde{\mathcal{M}}$) pair is ensured, the material matrices are diagonal with entries
+
+\begin{equation*}
+    \mathbb{M}_\mu[i,i] = \frac{\mu|A_i|}{|\Tilde{L}_i|}, \ \ \ \ \mathbb{M}_\varepsilon[i,i] = \frac{\varepsilon |\Tilde{A}_i|}{|L_i|},
+\end{equation*}
+where $|\cdot|$ means taking length or area.
+
+To summarize, the FIT framework enables us to transform Maxwell’s equations into algebraic equations given the mesh pair ($\mathcal{M}, \Tilde{\mathcal{M}}$).
+The resulting system of algebraic equations is called Maxwell's Grid Equations (MGE).
+Let's put together the original form of the Maxwell system as well as the MGE:
+
+\begin{minipage}{0.3\textwidth}
+\begin{align*}
+    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \\
+    \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= -\mathbf{J}, \\
+    \nabla \cdot \mathbf{B} &= 0,  \\
+    \nabla \cdot \mathbf{D} &= \rho, \\
+    \mathbf{H} &= \mu^{-1} \mathbf{B}, \\
+    \mathbf{D} &= \varepsilon \mathbf{E}. 
+\end{align*}
+\end{minipage}
+\begin{minipage}{0.1\textwidth}
+\centering
+\begin{tikzpicture}
+\draw[thick, -{to}] (0,0) -- node[above]{$(\mathcal{M}, \Tilde{\mathcal{M}})$} (1.5,0);
+\end{tikzpicture}
+\end{minipage}
+\begin{minipage}{0.3\textwidth}
+\begin{align*}
+    \dot{\mathbf{b}} + \mathbb{C}\mathbf{e} &= 0 , \\
+    \dot{\mathbf{d}} - \Tilde{\mathbb{C}}\mathbf{h} &= - \mathbf{j}, \\
+    \mathbb{D}\mathbf{b} &= 0,  \\
+    \Tilde{\mathbb{D}}\mathbf{d} &= \mathbf{q},  \\
+    \mathbf{h} &= \mathbb{M}_\mu^{-1} \mathbf{b}, \\
+    \mathbf{d} &= \mathbb{M}_{\varepsilon} \mathbf{e}. 
+\end{align*}
+\end{minipage}
+\begin{minipage}{0.2\textwidth}
+Topological relations:
+\begin{align*}
+    \Tilde{\mathbb{C}} = \mathbb{C}^T \\
+    \mathbb{D}\mathbb{C} = 0 \\
+    \Tilde{\mathbb{D}}\Tilde{\mathbb{C}} = 0
+\end{align*}
+\end{minipage}
+
+\hfill
+
+Note that this transformation does not introduce approximations \emph{except for} the discrete material laws.
+The essence of FIT lies in that the complexity of continuous electric and magnetic field quantities
+is reduced to a finite number of well-defined discrete unknowns \citep{weiland_2003}.
+\subsection{Finite volume discretization of the Euler equations}
+We employ the finite volume method (FVM) to discretize the Euler system.
+As a classical framework for solving conservation laws and hyperbolic systems, FVM is derived from the integral form of the equations in each cell.
+It is the cell average of quantities that evolves at each time step, based on the \emph{numerical flux} through the cell boundary.
+The construction of the numerical flux, which serves to approximate the real flux, is the essence of constructing an FVM scheme.
+Due to the convection nature of fluid dynamics, the numerical fluxes are supposed to respect the convection direction, namely, the \emph{upwind scheme} is preferable.
+To this end, people resort to the approximated solution of \emph{Riemann problems}.
+The method is briefly illustrated in the following.
+For detailed information, see the textbook \cite{leveque_2002}.
+
+The Euler equations (\ref{equ:euler_}) can be generalized into the form of conservation law with source terms:
+\begin{equation} \label{equ:euler_conservation}
+    \partial_t \mathbf{U} + \nabla \cdot \mathbf{F}(\mathbf{U}) = \mathbf{RHS},
+\end{equation}
+where $\mathbf{U}$ stands for the conservative variable, $\mathbf{F}(\mathbf{U})$ is the flux density, and $\mathbf{RHS}$ is the source term.
+
+To obtain the semi-discretization, we first integrate (\ref{equ:euler_conservation}) over a cell $V_i$ 
+\begin{equation} \label{equ:euler_grid} 
+    \partial_t \overline{\mathbf{U}}_i + \frac{1}{|V_i|}\sum_{j:A_j\in\partial V_i} |A_j|\underbrace{\frac{1}{|A_j|}\iint_{A_j}\mathbf{F}(\mathbf{U})\cdot \mathbf{n}_j \text{d}A}_{\overline{\mathbf{F}}_j} = \underbrace{\frac{1}{|V_i|}\iiint_{V_i} \mathbf{RHS} \text{d}V}_{\overline{\mathbf{RHS}}_i}
+\end{equation}
+where $\overline{\mathbf{U}}_i := \iiint_{V_i} \mathbf{U} \text{d}V / |V_i|$ calculates the cell average, $\mathbf{n}_j$ is the outer normal vector of face $A_j$ with respect to the cell $V_i$.
+We approximate the analytic flux $\overline{\mathbf{F}}_j$ in (\ref{equ:euler_grid}) by the numerical flux $\overline{\mathbf{F}}\left(\overline{\mathbf{U}}_i, \overline{\mathbf{U}}_{k(i,j)}, \mathbf{n}_j\right)$, where $k(i,j)$ returns the index of the adjacent cell that shares $A_j$ with cell $V_i$.
+Classical numerical fluxes include Lax-Friedrich flux, Rusanov flux, Engquist-Osher flux, see \cite[][p.
+44-46]{mishra_2019}.
+Finally, we end up with the semi-discretized equation:
+\begin{equation*}
+    \partial_t \overline{\mathbf{U}}_i + \frac{1}{|V_i|}\sum_{j:A_j\in\partial V_i} |A_j| \overline{\mathbf{F}}\left(\overline{\mathbf{U}}_i, \overline{\mathbf{U}}_{k(i,j)}, \mathbf{n}_j\right) = \overline{\mathbf{RHS}}_i.
+\end{equation*}
+The Rusanov flux in multi-dimensions on face $A_j$ reads\footnote{See Appendix \ref{app:flux} for detailed derivation.}
+\begin{equation} \label{equ:rusanov-flux-3d}
+    \overline{\mathbf{F}}\left(\overline{\mathbf{U}}_L, \overline{\mathbf{U}}_R, \mathbf{n}\right) = \frac{1}{2}\left[\mathbf{F}(\overline{\mathbf{U}}_L)\cdot\mathbf{n} + \mathbf{F}(\overline{\mathbf{U}}_R)\cdot\mathbf{n}\right] - \frac{1}{2}\overline{s}\left(\overline{\mathbf{U}}_R - \overline{\mathbf{U}}_L\right),
+\end{equation}
+where $\overline{s} = \text{max}(s(\overline{\mathbf{U}}_L), s(\overline{\mathbf{U}}_R))$ with $s(\mathbf{U}) := |\mathbf{u}\cdot\mathbf{n}| + \sqrt{\gamma p/\rho}$ representing the largest wave speed.
+\subsection{Discrete boundary conditions}
+Dirichlet BCs lead to setting corresponding DoFs at boundary to zero. Vanishing tangential curl is treated by introducing a boundary potential. 
+\todo{More details.}
+\subsection{Stabilization in insulating domain}
+We repeat the dilemma again: the scheme fails for $\lambda \rightarrow 0$. The Maxwell system in $\Omega_I$ is    
+\begin{align}
+    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:ex_1}\\ 
+    \lambda^2 \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= 0,  \label{equ:ex_2}\\
+    \nabla \cdot \mathbf{B} &= 0, \label{equ:ex_3}\\
+    \lambda^2 \nabla \cdot \mathbf{D} &= 0 \label{equ:ex_4}.
+\end{align}
+In non-neutral regime, namely $\lambda = \mathcal{O}(1)$, the Maxwell system in $\Omega_I$ is well-posed and Gauss's laws (\ref{equ:ex_3}) (\ref{equ:ex_4}) are redundant.
+Therefore, they are \emph{implicitly} satisfied (up to numerical errors) in the scheme.
+Nonetheless, the quasi-neutral limit $\lambda \rightarrow 0$ dismisses the implicit fulfillment of Gauss's law for electric field (\ref{equ:ex_4}) through Amper\`{e}'s law (\ref{equ:ex_2}).
+A crucial observation is that formally letting $\lambda \rightarrow 0$ makes (\ref{equ:ex_4}) degenerate, but the divergence-free condition of $\mathbf{D}$-field is always satisfied since the system is divergent as $\lambda \rightarrow 0$ [cite something].
+
+The remedy is to \emph{explicitly} include the divergence-free constraint in the scheme for any value of $\lambda$:  
+\begin{align}
+    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:ex_5}\\ 
+    \lambda^2 \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= 0,  \label{equ:ex_6}\\
+    \nabla \cdot \mathbf{D} &= 0 \label{equ:ex_7}.
+\end{align}
+
+With the divergence-free constraint (\ref{equ:ex_7}), we have more equations than unknowns, which can be resolved by introducing a Lagrange multiplier $p$ as follows:
+\begin{align}
+    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:ex_8}\\ 
+    \lambda^2 \partial_t \mathbf{D} - \nabla \times \mathbf{H} + \colorbox{orange!20}{$\nabla p$} &= 0,  \label{equ:ex_9}\\
+    \nabla \cdot \mathbf{D} &= 0 \label{equ:ex_10},
+\end{align}
+supplemented with the boundary condition $p = 0$ on $\partial\Omega_I$.
+One can check that (\ref{equ:ex_8})-(\ref{equ:ex_10}) are equivalent to (\ref{equ:ex_5})-(\ref{equ:ex_7}) by verifying that $p = 0$ in $\Omega_I$.
+This is done by taking the divergence of (\ref{equ:ex_9}) such that the Laplace equation of $p$ with zero Dirichlet boundary condition gives vanishing $p$.
+
+\todo{The following part should be put after the full discretization is presented.}
+
+The discretization of the Maxwell system in the insulating domain then becomes
+\begin{align*}
+    \delta_m^{-1} (\mathbf{b}^{m+1} - \mathbf{b}^m) + \mathbb{C}\mathbf{e}^{m+1} &= 0, \\
+    \lambda^2\delta_m^{-1} (\Tilde{\mathbf{d}}^{m+1} - \Tilde{\mathbf{d}}^m) - \Tilde{\mathbb{C}}\Tilde{\mathbf{h}}^{m+1} + \colorbox{orange!20}{$\mathbb{H} \mathbb{G} \mathbf{p}^{m+1}$} &= 0 \\
+    \Tilde{\mathbb{D}} \Tilde{\mathbf{d}}^{m+1} &= 0.
+\end{align*}
+where $\mathbb{H}$ is the discrete Hodge operator (matrix\footnote{In our case where the orthogonal mesh pair is used, it is diagonal.}) responsible for transforming any primal-edge-integrated variables to dual-face-integrated ones; the vector $\mathbf{p}$ is the discrete representation of $p$ and is defined on primal vertices lying in $\Omega_I$.
+
+\subsection{Semi-implicit AP schemes}
+In this section, we present the full discretization with AP property.
+The general approach for spatial discretizations of both the Euler and Maxwell's equations has been introduced in chapter \ref{chap:discretization_euler_maxwell}.
+As stability is a central issue for the AP property, this section is mostly devoted to the time discretization of the Euler-Maxwell system.
+
+We want to first recall the objective of AP schemes and make clear the direction to proceed towards.
+By definition \ref{def:ap}, the stability condition that does not depend on $\lambda$ and the consistency of the limit scheme with the quasi-neutral system have to be fulfilled.
+Furthermore, what is desired for the numerical treatment of Maxwell's equations is that Gauss's law is satisfied at the discrete level.
+To sum up, the following properties of the constructed scheme are to be realized:
+
+\begin{itemize}
+    \item[I] stable regardless of the value of $\lambda$;
+    \item[II] the limit scheme by taking $\lambda = 0$ is valid\footnote{By ``valid" we mean the scheme is a valid recursion such that the state at $t^{m+1}$ can be \emph{uniquely} computed by that at $t^m$.} and consistent to its continuous counterpart (\ref{equ:maxwell_faraday_limit}) to (\ref{equ:maxwell_gauss_D_limit});
+    \item[III] Gauss's law (\ref{equ:maxwell_gauss_D_rescaled}) is fulfilled at the discrete level for any $\lambda$. \label{condition3}
+\end{itemize}
+
+Given the mesh pair $(\mathcal{M}, \Tilde{\mathcal{M}})$, Maxwell's equations are handled by the FIT framework while FVM is applied to Euler equations on the dual mesh 
+$\Tilde{\mathcal{M}}$.
+Naturally extending the AP scheme for 1D two-fluid plasma proposed in \cite{degond_2012} to which the detailed constructing procedure should be referred, we straightforwardly present the full-discretization scheme for 3D multi-species plasma:
+
+\begin{align}
+    \delta_m^{-1} (\mathbf{b}^{m+1} - \mathbf{b}^{m}) \hspace{0.4cm}&\;+\; \hspace{1.5cm}\mathbb{C}\textcolor{blue}{\mathbf{e}^{m+1}}\hspace{1.25cm}=\; 0, \label{equ:maxwell_faraday_ap}\\
+    \lambda^2\delta_m^{-1}(\mathbf{d}^{m+1} - \mathbf{d}^m) \hspace{0.4cm}&\;-\; \hspace{1.5cm}\Tilde{\mathbb{C}}\textcolor{blue}{\mathbf{h}^{m+1}} \hspace{1.22cm}=\; - \textcolor{blue}{\mathbf{j}^{m+1}}, \label{equ:maxwell_ampere_ap}\\
+    \delta_m^{-1}(\mathbf{U}_{*,k}^{m+1} - \mathbf{U}_{*,k}^{m}) \hspace{0.10cm}&\;+\;  \frac{1}{|\Tilde{V}_k|}\sum_{j:\Tilde{A}_j\in\partial\Tilde{V}_k}|\Tilde{A}_j|\textcolor{blue}{\overline{\mathbf{F}}_{*,j}^{m+1/2}} \hspace{0.05cm}=\; \textcolor{blue}{\mathbf{RHS}_{*,k}^{m+1/2}}, \label{equ:euler_ap}
+\end{align}
+where 
+\begin{align}
+    \mathbf{U}_{*,k}^{m} &=
+    \begin{bmatrix}
+    n_* \\
+    n_* \mathbf{u}_* \\
+    n_* e_*
+    \end{bmatrix}^m_k, \\
+    \overline{\mathbf{F}}_{*,j}^{m+1/2} &=
+    \begin{bmatrix}
+    f^{m+1}_{n,*,j} \\
+    \bm{f}^m_{u,*,j} \\
+    f^m_{e,*,j} 
+    \end{bmatrix}
+    = 
+    \begin{bmatrix}
+    \frac{1}{2}\left[\textcolor{blue}{(nu_{\bot})_{*,k}^{m+1}} + \textcolor{blue}{(nu_{\bot})_{*,k+1}^{m+1}}\right] - \frac{1}{2}s^m_{*,k+1/2}(n_{*,k+1}^m - n_{*,k}^m) \\
+    \frac{1}{2}\left[(nu_{\bot}\mathbf{u})^m_{*,k} + (nu_{\bot}\mathbf{u})^m_{*,k+1} + p_{*,k}^m\mathbf{n}_j + p_{*,k+1}^m\mathbf{n}_j\right] - \frac{1}{2}s^m_{*,k+1/2}\left[(n\mathbf{u})^m_{*,k+1} - (n\mathbf{u})^m_{*,k}\right] \\
+    \frac{1}{2}\left[(nhu_\bot)^m_{*,k} + (nhu_\bot)^m_{*,k+1}\right] - \frac{1}{2}s^m_{*,k+1/2}\left[(ne)^m_{*,k+1} - (ne)^m_{*,k}\right]
+    \end{bmatrix}, \label{equ:flux_ap}\\
+    \mathbf{RHS}_{*,k}^{m+1/2} &=
+    \begin{bmatrix}
+    0 \\
+    \varepsilon_*^{-2}q_*\left[n_*^m\textcolor{blue}{\mathbf{E}^{m+1}} + (n\mathbf{u})^m_*\times\mathbf{B}^m\right] \\
+    \varepsilon_*^{-2}q_*(n\mathbf{u})^m_* \cdot \textcolor{blue}{\mathbf{E}^{m+1}}
+    \end{bmatrix}_k +
+    \begin{bmatrix}
+    0 \\
+    \varepsilon_*^{-2}\textcolor{blue}{\mathbf{R}_{*,k}^{\text{coll},m+1}} \\
+    0
+    \end{bmatrix}, \label{equ:rhs_ap}\\
+    \mathbf{R}_{*,k}^{\text{coll},m+1} &= 
+    \begin{cases}
+    \alpha^\text{coll}\left[n_{e,k}^m\textcolor{blue}{(n\mathbf{u})^{m+1}_{i,k}} - n_{i,k}^m\textcolor{blue}{(n\mathbf{u})^{m+1}_{e,k}}\right] \text{  if  } * = e \\
+    \alpha^\text{coll}\left[n_{i,k}^m\textcolor{blue}{(n\mathbf{u})^{m+1}_{e,k}} - n_{e,k}^m\textcolor{blue}{(n\mathbf{u})^{m+1}_{i,k}}\right] \text{  if  } * = i
+    \end{cases}  \\
+    \mathbf{j}^{m+1} &= \left(\sum_*\pm q_*\textcolor{blue}{f^{m+1}_{n,*,j}}|\Tilde{A}_j|\right)_{j=1}^{N_{\Tilde{A}}}, \label{equ:current_ap}\\
+    \mathbf{d}^m &= \mathbb{M}_\varepsilon \mathbf{e}^m, \ \ \ \mathbf{h}^m = \mathbb{M}_\mu^{-1} \mathbf{b}^m. \label{equ:material_law}
+\end{align}
+In the above scheme, the superscript $m$ indicates the number of iterations, and the quantities with superscript $m+1/2$ implies its dependency on the quantities at both $m$-th and $(m+1)$-th iterations; $\delta_m$ is the time step size for the $m$-th iteration.
+The numerical flux (\ref{equ:flux_ap}), where $u_\perp$ stands for the velocity component normal to the dual face $\Tilde{A}_j$, is just the application of the generic Rusanov flux (\ref{equ:rusanov-flux-3d}) on the Euler equations, see also the expression (\ref{equ:rusanov_flux_euler}) in the appendix.
+
+By abuse of notations, quantities with subscript $k+1$ are associated with the adjacent cell of $\Tilde{V}_k$ with respect to $\Tilde{A}_j$, which should not be confused with its real index.
+$\mathbf{n}_j$ is the outer normal of $\Tilde{A}_j$ as a face of $\Tilde{V}_k$.
+Since the equations have been rescaled into the dimensionless form, the material matrices $\mathbb{M}_\varepsilon = \text{diag}(\{|\Tilde{A}_i|/{|L_i|}\}_i)$, $\mathbb{M}_\varepsilon = \text{diag}(\{{|A_i|}/{|\Tilde{L}_i|}\}_i)$ now only depend on the meshes.
+
+Recall that the discrete Euler system (\ref{equ:euler_ap}) is defined on the dual mesh $\Tilde{\mathcal{M}}$, and hence $\mathbf{E}^{m+1}$ and $\mathbf{B}^m$ in (\ref{equ:rhs_ap}) are the interpolated vector fields at dual cell center as is illustrated in section \ref{sec:interpolation}.
+The $\pm$ in (\ref{equ:current_ap}) arises from the fact that the direction of numerical fluxes is determined by the outer normal of each cell whereas each component in $\mathbf{j}^{m+1}$ is defined to be aligned with the internal orientation of the dual face it associates with.
+Hence a flip of the sign may be necessary.
+
+First, we would like to discuss the necessity of the implicit terms (highlighted in blue color).
+The implicit treatment of electric field in (\ref{equ:rhs_ap}) is a must to ensure stability and is justified in \cite{fabre_1992} for the Euler-Poisson system.
+It is reasonable to infer that it applies equally to the Euler-Maxwell system.
+To guarantee Gauss's law at the discrete level, the current in (\ref{equ:maxwell_ampere_ap}), as well as the mass flux in (\ref{equ:flux_ap}), must be at the same implicit level.
+The reformulated Ampere's law (\ref{equ:maxwell_ampere_reform}) gives us some clue that in the quasi-neutral case the right-hand side, arising from the electric current, must be implicit to lead to a valid and unique time-stepping.
+Furthermore, we stress that the current (\ref{equ:current_ap}) is evaluated by the numerical mass flux rather than its original definition $\sum_*n_*q_*\mathbf{u}_*$ for the sake of consistency to the discrete Gauss's law.
+The implicitness of the electric field in (\ref{equ:maxwell_faraday_ap}) and the magnetic flux in (\ref{equ:maxwell_ampere_ap}) is necessary for unconditional stability with respect to $\lambda$, as is demonstrated by \cite{degond_2012} through a linearized analysis.
+The implicitness of the friction term is owing to the stiffness incurred from a potentially large value of $\varepsilon^{-2}_*\alpha^\text{coll}$.
+
+Now we deduce the limiting scheme and check its validity and consistency.
+By formally setting $\lambda = 0$ in the AP scheme (\ref{equ:maxwell_faraday_ap}) to (\ref{equ:euler_ap}), the equation for evolving the electric edge voltages (\ref{equ:maxwell_ampere_ap}) degenerates into a constraint that should be satisfied at each step, namely
+\begin{equation*}
+     \Tilde{\mathbb{C}}\mathbb{M}_\mu^{-1}\mathbf{b}^{m+1} = - \mathbf{j}^{m+1}.
+\end{equation*}
+We want to check the consistency of the limiting scheme with the quasi-neutral model, and especially to check if the constraint (\ref{equ:maxwell_ampere_reform}) when $\lambda = 0$ is correctly discretized.
+To that end, we mimic the procedure to derive (\ref{equ:maxwell_ampere_reform}) in a discrete way, which leads to
+\begin{equation*}
+    (\Tilde{\mathbb{C}}\mathbb{M}_\mu^{-1}\mathbb{C}\mathbf{e}^{m+1})_j / |\Tilde{A}_j| = - \frac{1}{2}(a_{j,k}^m\mathbf{E}^{m+1}_{j,k} + a_{j,k+1}^m\mathbf{E}^{m+1}_{j,k+1})\cdot \mathbf{n}_j - \frac{1}{2}(\mathbf{b}_{j,k}^m + \mathbf{b}_{j, k+1}^m) \cdot \mathbf{n}_j - \pi_j^m,
+\end{equation*}
+where
+\begin{align*}
+    a_{j,k}^m &= \sum_*\pm\varepsilon_*^{-2}q_*^2n^m_{*,k}, \\
+    \mathbf{b}_{j,k}^m &= \sum_*\pm\varepsilon_*^{-2}q_*\left[(n\mathbf{u})^m_{*,k}\times\mathbf{B}^m_k - \frac{1}{|\Tilde{V}_k|}\sum_{i:\Tilde{A}_i\in\partial\Tilde{V}_k}|\Tilde{A}_i|\bm{f}_{u,*,i}^m\right], \\
+    \pi^m_j &= - \frac{1}{2} \delta_m^{-1} \sum_* \pm q_* \left[s_{*,k+1/2}^m(n^m_{*,k+1} - n^m_{*,k}) - s^{m-1}_{*,k+1/2}(n^{m-1}_{*,k+1} - n^{m-1}_{*,k})\right].
+\end{align*}
+Comparison with (\ref{equ:maxwell_ampere_reform}) manifests the consistency when $\lambda = 0$, given the fact that $\pi^m_j = \mathcal{O}(h)$ where h is cell size.
+
+One should be aware that such a scheme merely meets the necessary conditions of AP property while we do not rigorously prove that it is AP.
+The difficulty to prove the nonlinear stability for such a complex system is notorious.
+Also as is mentioned throughout the thesis, the convergence of the continuous solutions as $\lambda \rightarrow 0$ is taken for granted.
+Therefore, instead of rigorously proving the scheme to be AP, the procedure shown here should be treated as a heuristic approach for constructing AP schemes, and one should always turn to numerical experiments for verification.
+
+\todo{CFL condition should be mentioned.}
+
+\todo{Not sure if a bit analysis about the scheme is needed (and possible).}
+
+\subsection{An algebraic check on the well-posedness}
+
+\todo{Not sure if this section is necessary}
+
+To verify that the BCs lead to a well-posed problem, especially for Maxwell's equations\footnote{The BCs for the Euler system are rather classical.
+See \cite[][Chap.
+7]{leveque_2002} for a general introduction, or \cite[][sec.
+2e]{mishra_2019b} for the specific implementation for the Euler equations.}, we want to check that these BCs in the discrete level lead to a solvable linear system.
+A \emph{necessary} condition is that \emph{the number of unknown variables and the number of (independent) algebraic equations coincide}.
+
+We would like to remark that the time-stepping for Euler equations (\ref{equ:euler_ap}) do not involve solving any linear system since the implicit mass term in (\ref{equ:flux_ap}) can be obtained through the momentum equations.
+As for the implicit term $\mathbf{E}^{m+1}$ in the source term (\ref{equ:rhs_ap}), it is obtained through updating the Maxwell system.
+Therefore, only the evolution of the Maxwell system entails solving a linear system, whose validity is discussed here.
+
+First, a meticulous classification and counting for facets of meshes are done as follows:
+\begin{align*}
+    \#\  \text{primal cell}\ \  &N_V \\
+    \#\  \text{primal edge}\ \  &N_L := \underbrace{N^+_L + N^-_L + N^I_L}_{N^\partial_L} + N^\circ_L  \\
+    \#\  \text{primal face}\ \  &N_A := \underbrace{N_A^+ + N_A^- + N^I_A}_{N^\partial_A} + N^\circ_A  \\
+    \#\  \text{primal vertex}\ \  &N_P := \underbrace{N_P^+ + N_P^- + N^I_P}_{N^\partial_P} + N^\circ_P \\
+    \#\  \text{dual cell}\ \  &N_{\Tilde{V}} := N_p \\
+    \#\  \text{dual edge}\ \  &N_{\Tilde{L}} := \underbrace{N^\partial_{\Tilde{L}}}_{=N^\partial_L} + \underbrace{N^\circ_{\Tilde{L}}}_{=N_A} \\
+    \#\  \text{dual face}\ \  &N_{\Tilde{A}} := \underbrace{N^\partial_{\Tilde{A}}}_{=N^\partial_P} + \underbrace{N^\circ_{\Tilde{A}}}_{=N_L}
+\end{align*}
+where the superscripts indicate the domains to which facets belong to, and $+,-,I,\circ,\partial$ represent $\Gamma_+, \Gamma_-, \Gamma_I, \Omega^\circ, \partial \Omega$ respectively.
+As is discussed in Section \ref{sec:boundary_treatment}, auxiliary dual facets are needed to trim $\Tilde{\mathcal{M}}$ such that $\mathcal{M}$ and $\Tilde{\mathcal{M}}$ share the same boundary.
+By inspecting Fig.
+\ref{fig:illustraion_dual_boundary}, one can realize that the auxiliary dual edges have the same number as the primal boundary edges since they intersect with each other; the auxiliary dual faces have the same number as the primal boundary vertices.
+These amount to $N^\partial_{\Tilde{L}} = N^\partial_L, N^\partial_{\Tilde{A}} = N^\partial_P$.
+Note that these number relationships are attained on the premise that non-straight edges and non-flat faces are admissible.
+
+Next, we count the number of unknowns.
+From the BCs (\ref{equ:bc_1})(\ref{equ:bc_3})  we know that the tangential $\mathbf{E}$-field is irrotational at the whole boundary $\partial\Omega$, which allows a scalar potential function $\varphi$ on $\partial \Omega$ with $\text{grad}_\tau \varphi = \mathbf{E}_\tau$.
+In the discrete case, $\bm{\varphi}$ is a scalar vector whose entries are defined on each primal vertex on $\partial \Omega$.
+The collection of boundary electric voltage $\mathbf{e}^\partial$ is retrieved by $\mathbf{e}^\partial = \mathbb{G}_\partial \bm{\varphi}$ where $\mathbb{G}_\partial$ stands for the discrete grad operator on the boundary.
+Besides, additional dual edges and faces at boundary, to which the integrals of the $\mathbf{H}$-field and the $\mathbf{D}$-field are assigned, give rise to unknown $\mathbf{h^\partial}$ and $\mathbf{d^\partial}$ vectors of sizes $N^\partial_{\Tilde{L}}$ and $N^\partial_{\Tilde{A}}$.
+The counting of unknown variables is as follows:
+\begin{equation*}
+    |\mathbf{e}| = N_L, \ \ \ |\mathbf{b}|=N_A, \ \ \ |\mathbf{h}^\partial|=N^\partial_{\Tilde{L}},\ \ \ |\mathbf{d}^\partial| = N^\partial_{\Tilde{A}}, \ \ \ |\bm{\varphi}| = N^\partial_P,
+\end{equation*}
+where $|\cdot|$ denotes the size of vector.
+
+Lastly, we collect all the algebraic equations derived from the Maxwell system.
+The coupling term $\mathbf{j}^{m+1}$ in discrete Ampere's law (\ref{equ:maxwell_ampere_ap}) can be rewritten by electric variables, which will be demonstrated in (\ref{equ:tmp5})(\ref{equ:tmp6}) at the next section.
+The discrete Faraday's law (\ref{equ:maxwell_faraday_ap}) updates the scalar vector $\mathbf{b}$ which is composed of integrals of $\mathbf{B}$-field on each primal face; the discrete Amp\`{e}re's law (\ref{equ:maxwell_ampere_ap}) updates $\mathbf{d}$ which is composed of integrals of $\mathbf{D}$-field on each dual face; the relation $\mathbf{e}^\partial = \mathbb{G}_\partial \bm{\varphi}$ entails $N^\partial_L$ equations each of which is defined on a boundary primal edge; the entries of $\bm{\varphi}$ that locate on the electrodes are assigned externally; the insulating BC (\ref{equ:bc_4}) needs to be satisfied at each dual face that lies in $\Gamma_I$.
+In summary, the counting of algebraic equations is as follows:
+\begin{align*}
+    \text{discrete Faraday law (\ref{equ:maxwell_faraday_ap})} \ \ &\longrightarrow\ \  N_A \ \ \text{equations} \\
+    \text{discrete Ampere law (\ref{equ:maxwell_ampere_ap})} \ \ &\longrightarrow\ \  N_{\Tilde{A}} \ \ \text{equations} \\
+     \mathbf{E}_\tau = \text{grad}_\tau \varphi \Rightarrow \mathbf{e}^\partial = \mathbb{G}_\partial \bm{\varphi} \ \ &\longrightarrow\ \  N^\partial_L \ \ \text{equations} \\
+    \text{enforced potentials}\ \ \varphi^+(t), \varphi^-(t) \ \ &\longrightarrow\ \  N_P^+ + N_P^- \ \ \text{equations} \\
+    \text{insulating BC (\ref{equ:bc_4})} \ \ &\longrightarrow\ \  N_{\Tilde{A}}^I = N_P^I \ \ \text{equations}.
+\end{align*}
+It is straightforward to check that the numbers of unknowns and the equations match. Specifically, 
+\begin{align*}
+    \#\text{ of unknowns} &= \colorbox{orange!20}{$N_L$} + \colorbox{blue!20}{$N_A$} + \colorbox{gray!20}{$N_{\Tilde{L}}^\partial$} + \colorbox{orange!20}{$N_{\Tilde{A}}^\partial$} + \colorbox{green!20}{$N_P^\partial$}, \\
+    \#\text{ of equations} &= \colorbox{blue!20}{$N_A$} + \colorbox{orange!20}{$N_{\Tilde{A}}$} + \colorbox{gray!20}{$N_L^\partial$} + \colorbox{green!20}{$N_P^+ + N_P^- + N_P^I$},
+\end{align*}
+where the terms with the same color can be equated by applying the counting relations listed above.
+
+However, the matching of numbers of unknowns and equations does not necessarily result in a valid linear system.
+Inappropriate BCs could cause the singularity of the linear system, as is discussed in Section \ref{sec:impact_of_bc}.
+
+\subsection{Procedure of time-stepping}
+In this section we provide full details on the procedure of the semi-implicit time-stepping.
+
+\todo{The notation to be simplified. The content to be reduced.}
+
+In this section, we would like to present the concrete strategy to evolve the whole system, namely calculating variables at $t_{m+1}$ given their values at $t_m$.
+On one hand, the impact of BCs is not considered when presenting the AP scheme (\ref{equ:maxwell_faraday_ap}) to (\ref{equ:current_ap}).
+On the other hand, a clever and detailed strategy of establishing the linear system at every time step is necessary.
+
+To avoid any confusion, the definition of the quantities is repeated in Tab.
+\ref{tab:def_size_var}.
+For better illustration, matrices used in this section are supplemented with both superscript and subscript indicating the size.
+For instance, $\mathbb{C}^A_L$ indicates the discrete curl operator of size $N_A \times N_L$ with respect to primal faces and edges; $\Tilde{\mathbb{C}}^{A_I}_{\partial L}$ stands for the discrete curl operator of size $N_{\Tilde{A}}^{I} \times N_{\Tilde{L}}^\partial$ with respect to dual faces on $\Gamma_I$ and edges on $\partial \Gamma$.
+
+\begin{table}[]
+    \centering
+\begin{tabular}{c c c}
+     \hline
+     \textbf{Notation}  & \textbf{Meaning}  & \textbf{Size} \\
+     \hline
+     $\mathbf{e}$ & integral of $\mathbf{E}$-field at primal edges& $N_L$ \\
+     $\mathbf{e^\circ}$ & components of $\mathbf{e}$ lying in $\Omega^\circ$ & $N_L^\circ$ \\
+     $\mathbf{e^\partial}$ & components of $\mathbf{e}$ lying on $\partial \Omega$ & $N_L^\partial$ \\
+     $\mathbf{E}$ & cell average of $\mathbf{E}$-field for dual cells & $N_{\Tilde{V}}$ \\ 
+     $\bm{\varphi}$ & electric potentials at primal vertices & $N_P^\partial$ \\
+     $\bm{\varphi}^+$ & components of $\bm{\varphi}$ lying on $\Gamma^+$ & $N_P^+$ \\
+     $\bm{\varphi}^-$ & components of $\bm{\varphi}$ lying on $\Gamma^-$ & $N_P^-$ \\
+     $\mathbf{b}$ & integral of $\mathbf{B}$-field at primal faces & $N_A$ \\
+     $\mathbf{d}^\partial$ & integral of $\mathbf{D}$-field at boundary dual faces & $N_{\Tilde{A}}^\partial = N_P^\partial$ \\
+     $\mathbf{h}^\partial$ & integral of $\mathbf{H}$-field at boundary dual edges & $N_{\Tilde{L}}^\partial = N_L^\partial$ \\
+     $\mathbf{j}$ & current through dual faces & $N_{\Tilde{A}}$ \\
+     $\mathbf{j}^\circ$ & components of $\mathbf{j}$ lying in $\Omega^\circ$ & $N_{\Tilde{A}}^\circ$ \\
+     $\mathbf{j}^\partial$ & components of $\mathbf{j}$ lying on $\partial \Omega$ & $N_{\Tilde{A}}^\partial$ \\
+     \hline
+\end{tabular}
+    \caption{Definitions and sizes of scalar vectors for each quantity.}
+    \label{tab:def_size_var}
+\end{table}
+
+With extra quantities at boundary, the schemes (\ref{equ:maxwell_faraday_ap}) (\ref{equ:maxwell_ampere_ap}) turn into
+\begin{align}
+    \delta_m^{-1} (\mathbf{b}^{m+1} - \mathbf{b}^{m}) + \mathbb{C}_L^A\mathbf{e}^{m+1} \hspace{3.08cm}&= 0, \label{equ:tmp7}\\
+    \lambda^2\delta_m^{-1}\mathbb{M}_\varepsilon(\mathbf{e}^{m+1} - \mathbf{e}^m) - \Tilde{\mathbb{C}}_{L^\circ}^{A^\circ}\mathbb{M}_\mu^{-1}\mathbf{b}^{m+1} - \Tilde{C}^{A^\circ}_{\partial L} \mathbf{h}^{\partial, m+1} &= - \mathbf{j}^{\circ,m+1}, \label{equ:tmp8}\\
+     \lambda^2\delta_m^{-1}(\mathbf{d}^{\partial,m+1} - \mathbf{d}^{\partial, m}) - \Tilde{\mathbb{C}}^{\partial A}_{\partial L} \mathbf{h}^{\partial,m+1} \hspace{2.60cm}&= - \mathbf{j}^{\partial,m+1}.
+\label{equ:tmp9}
+\end{align}
+The equations (\ref{equ:tmp8}) (\ref{equ:tmp9}) arise due to the discrete Faraday law at $\Omega^\circ$ and on $\partial \Omega$.
+
+The discretized BCs (\ref{equ:bc_1}) to (\ref{equ:bc_4}) appear as
+\begin{align}
+    \mathbf{e}^{\partial,m} &= \mathbb{G}^{\partial L}_{\partial P} \bm{\varphi}^m, \label{equ:tmp10}\\
+    \begin{bmatrix}
+    \bm{\varphi}^+ \\
+    \bm{\varphi}^- 
+    \end{bmatrix}^m &= \mathbb{S}^{\pm}_{\partial P} \bm{\varphi}^m =
+    \begin{bmatrix}
+    \varphi^+(t_m) \\
+    \varphi^-(t_m) 
+    \end{bmatrix},\label{equ:tmp11}\\
+    \Tilde{\mathbb{S}}^{A_I}_{\partial A} \mathbf{d}^{\partial,m} &= 0, \label{equ:tmp12}
+\end{align}
+where $\mathbb{G}^{\partial L}_{\partial P}$ is the discrete gradient operator applied on $\partial \Omega$;
+$\mathbb{S}^{\pm}_{\partial P}$ is a matrix with entries $\in \{0,1\}$ responsible for selecting the potentials at $\Gamma^+$ and $\Gamma^-$; $\Tilde{\mathbb{S}}^{P_I}_{\partial P}$ is also a selecting matrix that picks dual faces on $\Gamma^I$ from those at $\partial\Omega$.
+
+With proper ordering of components in $\mathbf{e}$ and (\ref{equ:tmp10}), we derive all the edge voltages $\mathbf{e}$ from interior edge voltages $\mathbf{e}^\circ$ and boundary potentials $\bm{\varphi}$ through
+\begin{align*}
+    \mathbf{e}^m =
+    \begin{bmatrix}
+    \mathbf{e}^\circ \\ \mathbf{e}^\partial
+    \end{bmatrix}^m =
+    \underbrace{
+    \begin{bmatrix}
+    \mathbb{I} & 0 \\ 0 & \mathbb{G}^{\partial L}_{\partial P}
+    \end{bmatrix}}_{\mathbb{Q}_{L^\circ,\partial P}^{L}}
+    \begin{bmatrix}
+    \mathbf{e}^\circ \\ \bm{\varphi}
+    \end{bmatrix}^m.
+\end{align*}
+
+The last piece of the puzzle to be filled is the relation connecting $\mathbf{j}^{m+1}$ and the electrical quantities -- namely, a generalized Ohm's law\footnote{By ``generalized" we mean that it is merely a formula relating the current density and $\mathbf{E}$-field at the discrete model.
+There is no counterpart for the continuous model, and it is not the \emph{discretized} Ohm's law, either.} -- such that the linear system (\ref{equ:tmp7}) to (\ref{equ:tmp9}) can be closed and solved.
+The derivation of generalized Ohm's law resorts to the discrete Euler system (\ref{equ:euler_ap}).
+In the following, we provide the derivations for models with and without friction terms.
+
+\subsubsection{Model without friction}
+By the scheme (\ref{equ:euler_ap}) for the Euler equations, we get 
+\begin{equation} \label{equ:tmp1}
+    \left[(n\mathbf{u})_{*,k}\right]^{m+1} = \left[\delta_m \varepsilon^{-2}_* q_* n^m_{*,k}\mathbf{E}^{m+1}_k \right] + \underbrace{\left[(n\mathbf{u})_{*,k}\right]^{m} - \left[\frac{\delta_m}{|{\Tilde{V}}_k|}\sum_{j:\Tilde{A}_j\in\partial\Tilde{V}_k}|\Tilde{A}_j|\bm{f}^m_{u,*,j}\right] + \left[\delta_m \varepsilon^{-2}_* q_*(n\mathbf{u})^m_{*,k} \times \mathbf{B}^m_{k}\right]}_{\bm{\eta}^m_*}
+\end{equation}
+with $[\cdot]$ meaning packing the quantities into a vector. Recall the interpolation relation
+\begin{equation*}
+    \mathbf{E} = \Tilde{\mathbb{R}}^{V_f}_{A}
+    \begin{bmatrix}
+    \mathbf{e} \\
+    \mathbf{d}^\partial 
+    \end{bmatrix},
+    \ \ \ \ 
+    \mathbf{B} = \Tilde{\mathbb{R}}^{V_f}_{L}
+    \begin{bmatrix}
+    \mathbf{b} \\
+    \mathbf{h}^\partial 
+    \end{bmatrix},
+\end{equation*}
+with which (\ref{equ:tmp1}) is rewritten as
+\begin{equation} \label{equ:tmp2}
+    \left[(n\mathbf{u})_{*,k}\right]^{m+1} = \text{diag}(\delta_m \varepsilon^{-2}_* q_* n^m_{*,k}) \Tilde{\mathbb{R}}^{V_f}_{A} 
+    \begin{bmatrix}
+    \mathbf{e} \\
+    \mathbf{d}^\partial 
+    \end{bmatrix}^{m+1} + \bm{\eta}^m_*.
+\end{equation}
+Thanks to the linear nature of numerical flux (\ref{equ:flux_ap}), we can express the mass flux by linear operation 
+\begin{equation} \label{equ:tmp3}
+    \left[f_{n,*,j}\right]^{m+1} = \frac{1}{2} \Tilde{\mathbb{A}}_{V_f}^{A_f} :  \left[(n\mathbf{u})_{*,k}\right]^{m+1} - \frac{1}{2} [s_{*,j}]^m \odot \Tilde{\mathbb{D}}_{V_f}^{A_f} [n_{*,k}]^m,
+\end{equation}
+where $:$ represents two contraction, $\odot$ represents component-wise product.
+The meanings of 3-rank tensor $\Tilde{\mathbb{A}}_{V_f}^{A_f}$ and matrix $\Tilde{\mathbb{D}}_{V_f}^{A_f}$ should be self-explanatory by scrutinizing on its component-wise expression (\ref{equ:flux_ap}).
+We stress that the boundary conditions for the Euler equations are included in these two linear operators.
+
+Plug (\ref{equ:tmp2}) into (\ref{equ:tmp3}), and we get
+\begin{equation} \label{equ:tmp4}
+    \left[f_{n,*,j}\right]^{m+1} = \underbrace{\frac{1}{2} \Tilde{\mathbb{A}}_{V_f}^{A_f} : \text{diag}(\delta_m \varepsilon^{-2}_* q_* n^m_{*,k}) \Tilde{\mathbb{R}}^{V_f}_{A}}_{\Tilde{\mathbb{T}}_{A,*}^{A,m}}
+    \begin{bmatrix}
+    \mathbf{e} \\
+    \mathbf{d}^\partial 
+    \end{bmatrix}^{m+1} + \underbrace{\frac{1}{2}\Tilde{\mathbb{A}}_{V_f}^{A_f} :\bm{\eta}^m_* - \frac{1}{2} [s_{*,j}]^m \odot \Tilde{\mathbb{D}}_{V_f}^{A_f} [n_{*,k}]^m}_{\bm{\mu}^m_*}.
+\end{equation}
+
+\subsubsection{Two-fluid model with friction}
+We include the friction term (\ref{equ:collision_rescaled}).
+Adding friction terms would lead to extra complexity since they are discretized implicitly.
+For the sake of simplicity, only the two-fluid (electron-ion) model is tackled here.
+Following the same procedure as before, first, we need the discretized relation between momenta and $\mathbf{E}$-field.
+After lengthy calculation, we end up getting
+\begin{multline}\label{equ:tmp13}
+    [n\mathbf{u}_{i,k}]^{m+1} = \left[\frac{1 + \delta_m \alpha \varepsilon_e^{-2} n_{i,k}^m + \delta_m \alpha \varepsilon_e^{-2} \frac{q_e}{q_i}n_{e,k}^m }{1 + \delta_m \alpha (\varepsilon^{-2}_e n_{i,k}^m + \varepsilon_i^{-2} n_{e,k}^m)} \delta_m \varepsilon^{-2}_i q_i n_{i,k}^m \mathbf{E}^{m+1}_k\right] \\
+    + \left[\frac{\delta_m \alpha \varepsilon_i^{-2} n_{i,k}^m}{1 + \delta_m \alpha (\varepsilon^{-2}_e n_{i,k}^m + \varepsilon^{-2}_i n_{e,k}^m)}\right] \odot \bm{\eta}_e^m + \left[\frac{1 + \delta_m \alpha \varepsilon^{-2}_e n_{i,k}^m}{1 + \delta_m \alpha (\varepsilon^{-2}_e n_{i,k}^m + \varepsilon^{-2}_i n_{e,k}^m)}\right] \odot \bm{\eta}_i^m,
+\end{multline}
+where $\alpha$ is the friction coefficient, and $\bm{\eta}_e^m, \bm{\eta}_i^m$ are defined in (\ref{equ:tmp1}).
+Again by (\ref{equ:tmp3}) we derive the expression for mass fluxes in the same form as (\ref{equ:tmp4}).
+In this case,
+\begin{align}
+     \Tilde{\mathbb{T}}_{A, i}^{A, m} &= \frac{1}{2} \Tilde{\mathbb{A}}_{V_f}^{A_f} : \text{diag}\left(\frac{1 + \delta_m \alpha \varepsilon_e^{-2} n_{i,k}^m + \delta_m \alpha \varepsilon_e^{-2} \frac{q_e}{q_i}n_{e,k}^m }{1 + \delta_m \alpha (\varepsilon^{-2}_e n_{i,k}^m + \varepsilon_i^{-2} n_{e,k}^m)}\delta_m \varepsilon^{-2}_i q_i n^m_{i,k}\right) \Tilde{\mathbb{R}}^{V_f}_{A}, \label{equ:tmp14} \\
+     \bm{\mu}^m_i &= \frac{1}{2}\Tilde{\mathbb{A}}_{V_f}^{A_f} :\left(\left[\frac{\delta_m \alpha \varepsilon_i^{-2} n_{i,k}^m}{1 + \delta_m \alpha (\varepsilon^{-2}_e n_{i,k}^m + \varepsilon^{-2}_i n_{e,k}^m)}\right] \odot \bm{\eta}_e^m + \left[\frac{1 + \delta_m \alpha \varepsilon^{-2}_e n_{i,k}^m}{1 + \delta_m \alpha (\varepsilon^{-2}_e n_{i,k}^m + \varepsilon^{-2}_i n_{e,k}^m)}\right] \odot \bm{\eta}_i^m \right) \nonumber \\
+     &\hspace{10cm} - \frac{1}{2} [s_{i,j}]^m \odot \Tilde{\mathbb{D}}_{V_f}^{A_f} [n_{i,k}]^m. \label{equ:tmp15}
+\end{align}
+The counterpart of (\ref{equ:tmp14})(\ref{equ:tmp15}) for electron is straightforward by switching the subscript $e$ and $i$.
+Then the mass fluxes for different species remain the same as (\ref{equ:tmp4}), namely
+\begin{equation}
+    \left[f_{n,*,j}\right]^{m+1} = \Tilde{\mathbb{T}}_{A,*}^{A,m} 
+    \begin{bmatrix}
+    \mathbf{e} \\
+    \mathbf{d}^\partial 
+    \end{bmatrix}^{m+1} + \bm{\mu}^m_*.
+\end{equation}
+
+Now we have had the relation of the mass fluxes and the $\mathbf{E}$-field related quantities at $t_{m+1}$.
+By definition of the current density (\ref{equ:current_ap}) we end up with the expression for the generalized Ohm's law
+\begin{equation} \label{equ:tmp5}
+    \mathbf{j}^{m+1} = \sum_*q_*\text{diag}(|\Tilde{A}_j|)\left[f_{n,*,j}\right]^{m+1} = \underbrace{\sum_*q_*\text{diag}(|\Tilde{A}_j|) \Tilde{\mathbb{T}}_{A,*}^{A,m}}_{\mathbb{M}_\sigma^m} \begin{bmatrix}
+    \mathbf{e} \\
+    \mathbf{d}^\partial 
+    \end{bmatrix}^{m+1} + \underbrace{\sum_*q_*\text{diag}(|\Tilde{A}_j|) \bm{\mu}^m_*}_{\mathbf{j}^m_\text{aux}},
+\end{equation}
+The generalized Ohm's law (\ref{equ:tmp5}) is further split into
+\begin{equation} \label{equ:tmp6}
+    \mathbf{j}^{m+1} =
+    \begin{bmatrix}
+    \mathbf{j}^{\circ,m+1} \\
+    \mathbf{j}^{\partial, m+1}
+    \end{bmatrix} =
+    \begin{bmatrix}
+    \mathbb{M}_{\sigma,11}^m & \mathbb{M}_{\sigma,12}^m \\
+    \mathbb{M}_{\sigma,21}^m & \mathbb{M}_{\sigma,22}^m
+    \end{bmatrix}
+    \begin{bmatrix}
+    \mathbf{e} \\
+    \mathbf{d}^\partial 
+    \end{bmatrix}^{m+1} +
+    \begin{bmatrix}
+    \mathbf{j}^{\circ, m}_\text{aux} \\
+    \mathbf{j}^{\partial,m}_\text{aux}
+    \end{bmatrix}.
+\end{equation}
+Combine (\ref{equ:tmp7}) to (\ref{equ:tmp12}) and (\ref{equ:tmp6}), we end up with the assembled linear system
+\begin{multline} \label{equ:linear_system}
+    \begin{bNiceArray}{wc{4cm} wc{4cm} wc{2cm} c}[margin, hvlines,rules/color=blue]
+    \Block{1-2}{\left(\lambda^2\delta_m^{-1}\mathbb{M}_\varepsilon + \Tilde{\mathbb{C}}^{A^\circ}_{L^\circ}\mathbb{M}^{-1}_\mu \delta_m \mathbb{C}^A_L + \mathbb{M}^m_{\sigma,11}\right)\mathbb{Q}_{L^\circ,\partial P}^{L}} & & \Block{2-1}{-\Tilde{\mathbb{C}}^{A}_{\partial L}} & \mathbb{M}^m_{\sigma,12} \\
+    \Block{1-2}{\mathbb{M}^m_{\sigma,21}\mathbb{Q}_{L^\circ,\partial P}^{L}} & & & \lambda^2\delta_m^{-1}\mathbb{I} + \mathbb{M}^m_{\sigma,22} \\
+    0 & \mathbb{S}^{\pm}_{\partial P} & 0 & 0 \\
+    0 & 0 & 0 & \Tilde{\mathbb{S}}^{A_I}_{\partial A}
+    \end{bNiceArray}
+    \begin{bNiceArray}{c}
+    \mathbf{e}^\circ \\
+    \bm{\varphi}  \\
+    \mathbf{h}^\partial \\
+    \mathbf{d}^\partial 
+    \end{bNiceArray}^{m+1}  \\ =
+    \begin{bNiceArray}{c}
+    \lambda^2\delta_m^{-1}\mathbb{M}_\varepsilon\mathbf{e}^m + \Tilde{\mathbb{C}}^{A^\circ}_{L^\circ} \mathbb{M}^{-1}_\mu\mathbf{b}^m - \mathbf{j}^{\circ,m}_{\text{aux}} \\
+    \lambda^2\delta_m^{-1}\mathbf{d}^{\partial,m} - \mathbf{j}^{\partial,m}_\text{aux} \\
+    \bm{\varphi}^+(t_{m+1}) \\
+    \bm{\varphi}^-(t_{m+1}) \\
+    0 
+    \end{bNiceArray}
+\end{multline}
+As soon as $\mathbf{e}^{\circ,m+1}, \bm{\varphi}^{m+1}, \mathbf{h}^{\partial,m+1}, \mathbf{d}^{\partial,m+1}$ are available after solving the linear system, the fluid variables can be updated explicitly according to (\ref{equ:euler_ap}).
+To this point, the time-stepping is done.
+
+We would like to remark that the whole time-stepping procedure, although appears tedious, does not involve any tricky treatment.
+What is more important is that the formulation of the linear system helps us to identify problems incurring by the quasi-neutral limit.
+Upon setting $\lambda = 0$, we want to ensure that the square matrix at the left-hand side remains non-singular, which is indeed the case for our formulation.
+
+\section{Numerical Experiment}
+
+\subsection{Reduction to 1D case}
+On enforcing the traverse invariance, the 3D discretization boils down to the 1D case, which provides a justification of our implementation.
+The Euler-Maxwell system at the axis of symmetry is formulated as 
+\begin{align}
+    &\partial_t n_* + \partial_z(n_*u_{*,z}) = 0, \\
+    &\partial_t (n_* u_{*,z}) + \partial_z(n_*u_{*,z}^2) + \varepsilon_*^{-2} \partial_z P_* = \varepsilon_*^{-2}q_*n_*E_z, \\
+    &\partial_t (n_*e_*) + \partial_z (n_* h_* u_{*,z}) = \varepsilon_*^{-2} q_* n_* u_{*,z} E_z, \\
+    \lambda^2 &\partial_t E_z = \sum_* - q_* n_* u_{*,z}.
+\end{align}
+Recall that in section \ref{sec:two_fluid_model} the two-fluid model in 1D setting is discussed and verified.
+We take the results as reference solutions for the 1D reduction on the $z$-axis of the 3D model.
+With the same setting as is described in section \ref{sec:1d_two_fluid_numerical_results} and the vanishing anode potentials, we expect the results produced by the purely 1D model and 1D reduction of the 3D model to behave in a similar way, which is shown in Fig.
+\ref{fig:z_axis_reduction}.
+\begin{figure}
+    \centering
+    \includegraphics{z_axis_reduction.eps}
+    \caption{Comparison of 1D two-fluid model and reduced 1D model on $z$-axis from 3D two-fluid model.
+The results are both generated on meshes with 64 cells along $z$-axis.
+No friction term exists.
+$t = 5 \times 10^{-4}.$}
+    \label{fig:z_axis_reduction}
+\end{figure}
+
+\todo{Do more thorough tests}
+
+\subsection{A real problem setup}
+The problem setting is a cylindrical domain filled with plasma fluids, and with two electrodes on each end, as is sketched in Fig.
+\ref{fig:sketch_domain}.
+From the viewpoint of the Euler system, the cylinder is enclosed by a non-penetrating wall whereas the plasma fluids are allowed to inflow and outflow through the electrode surfaces.
+Regarding the Maxwell system, external electric potentials are applied on the electrodes, and the enclosing boundary is considered insulating.
+
+Under such a setting, the motions of charged particles of the plasma are driven by the external potential, giving rise to an electromagnetic field, which in turn exerts Lorentz force on the charged particles.
+This setting is intended for simulating electric arcs.
+
+We discretize the spatial domain by an unstructured mesh doublet ($\mathcal{M}, \Tilde{\mathcal{M}}$) which consists of prisms aligned with the axial direction.
+The mesh generation is realized by the code developed in \cite{fuchs_2021}.
+The detailed algorithm is omitted.
+In principle, a circle is first discretized with a 2D mesh which afterward is extended along the axial direction to form the 3D mesh.
+Based on the generated primal mesh, a dual mesh conforming to the duality requirements, as is illustrated in Section \ref{sec:mesh_duality}, can be constructed with additional attention on the cut-off boundary that is discussed in Section \ref{sec:boundary_treatment}.
+An example of the primal and dual meshes is shown in Fig.
+\ref{fig:primal_dual_meshes}.
+
+\begin{figure}
+    \centering
+    \begin{tikzpicture}
+    \coordinate (O1) at (0,0);
+    \draw[very thick] (O1) circle (1) node {Cathode};
+    \fill[blue, opacity=0.2] (O1) circle (1);
+    \draw[very thick] (O1) circle (1.5);
+    \coordinate (O2) at (4.5,1) ;
+    \draw[gray] (O2) circle (1);
+    \node at (O2) {Anode};
+    \node at (barycentric cs:O1=1,O2=1) {Plasma}; 
+    \fill[red, opacity=0.2] (O2) circle (1);
+    \coordinate (S1) at ([shift={(-0.196,0.98)}]O1);
+    \coordinate (S2) at ([shift={(-0.196,0.98)}]O2);
+    \coordinate (P1) at ([shift={(0.196,-0.98)}]O1);
+    \coordinate (P2) at ([shift={(0.196,-0.98)}]O2);
+    \coordinate (SS1) at ([shift={({-0.196*1.5},{0.98*1.5})}]O1);
+    \coordinate (SS2) at ([shift={({-0.196*1.5},{0.98*1.5})}]O2);
+    \coordinate (PP1) at ([shift={({0.196*1.5},{-0.98*1.5})}]O1);
+    \coordinate (PP2) at ([shift={({0.196*1.5},{-0.98*1.5})}]O2);
+    \draw[very thick] (SS1) -- (SS2);
+    \draw[very thick] (PP1) -- (PP2); 
+    \draw[gray] (SS2) arc (101.31:180+101.31:1.5);
+    \draw[very thick] (PP2) arc (101.31-180:101.31:1.5);
+    \begin{scope}[shift={(5.5,-1.4)}]
+    \draw[blue, -to] (0,0) -- (0.65,0.12) node[right]{\small $z$};
+    \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
+    \draw[blue, -to] (0,0) -- (0.7,0) node[below]{\small $y$};
+    \end{scope}
+    \end{tikzpicture}
+    \caption{Sketch of the computational domain: a cylinder filled with plasma and with two electrodes at the ends.\todo{Change the figure}}
+    \label{fig:sketch_domain}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[scale=0.4]{primal_mesh.png}
+    \hspace{2cm}
+    \includegraphics[scale=0.4]{dual_mesh.png}
+    \caption{Primal (left) and dual (right) meshes used for the 3D testing case. They are generated by the code developed in \cite{fuchs_2021}.}
+    \label{fig:primal_dual_meshes}
+\end{figure}
+
+\subsection{Numerical results}
+Now comes the point to finally present the numerical results of the AP scheme on the Euler-Maxwell system in a 3D domain.
+To recap the problem setting and BCs, see Section \ref{sec:problem_description} and \ref{sec:numerical_experiement_bc}.
+We consider the two-fluid situation where the plasma is composed of electrons and ions.
+The mass ratio $m_i / m_e$ is equal to $10^4$.
+The friction term (\ref{equ:collision_rescaled}) is included with $\alpha^\text{coll} = 32$.
+Other effects like recombination or ionization are not considered yet.
+
+The initial state is
+\begin{equation*}
+    n_i(x,y,z,0) = n_e(x,y,z,0) = 1, \ \ \  p_i(x,y,z,0) = p_e(x,y,z,0) = 1.
+\end{equation*}
+All the other quantities are vanishing initially.
+The cathode is grounded, and the anode has potential 1.0 throughout the simulation, namely $\varphi^-(t) = 0, \varphi^+(t) = 1.0$.
+It is intended to see how a stationary system responds to an applied voltage.
+We would like to remark that such an initial state is conforming to the BCs as well as the quasi-neutral condition $\rho = 0$ so that the quasi-neutrality $\lambda  = 0$ would not incur any initial layer.
+
+In Fig.
+\ref{fig:3d_vec_field_E_B_ue} we present the vector fields of the numerical solutions for $\lambda = 1.0, 0.01, 0$ at $t = 0.1$, aiming to give an intuitive visualization.
+First of all, one \emph{a priori} expects the rotational symmetry in the solutions, which serves as a basic criterion to justify the results.
+In terms of the 3D structure of the electromagnetic fields, the electric field points from the anode to the cathode, and the magnetic field is spiral-shaped and orthogonal to the electric field.
+The electrons move in the inverse direction of the electric field.
+Regarding the asymptotic behavior of the AP scheme, the primary concern is its validity in the limiting case.
+For this case, the scheme manages to produce a meaningful numerical solution when $\lambda = 0$.
+Besides, by comparing the solutions for different $\lambda$, the smooth transition from the non-neutrality to quasi-neutrality is observed, which is an implication that the scheme reproduces the asymptotic behavior of the analytical solutions from the non-neutral model to the quasi-neutral one.
+\begin{figure}
+    \centering
+    \includegraphics[scale=0.35]{E_lambda_1.png}
+    \includegraphics[scale=0.35]{B_lambda_1.png}
+    \includegraphics[scale=0.35]{ue_lambda_1.png} \\
+    (a) $\lambda = 1.0$ \\
+    \includegraphics[scale=0.35]{E_lambda_1e-2.png}
+    \includegraphics[scale=0.35]{B_lambda_1e-2.png}
+    \includegraphics[scale=0.35]{ue_lambda_1e-2.png} \\
+    (b) $\lambda = 0.01$ \\
+    \includegraphics[scale=0.35]{E_lambda_0.png}
+    \includegraphics[scale=0.35]{B_lambda_0.png}
+    \includegraphics[scale=0.35]{ue_lambda_0.png} \\
+    (c) $\lambda = 0$
+    \caption{Snapshots of the $\mathbf{E}$-field, $\mathbf{B}$-field, and $\mathbf{u}_e$ for different $\lambda$ at $t = 10$ based on a primal mesh with 1920 cells (8 cells along $z$-axis). } 
+    \label{fig:3d_vec_field_E_B_ue}
+\end{figure}
+
+We perform the grid study and show the result in Fig.
+\ref{fig:grid_study_3d}.
+Meshes with different refinement levels are tested for $\lambda = 1$ and $0.1$ at $t = 1$, and the norms of the quantities are calculated.
+Due to the high computational cost incurred by the curse of dimensionality, only meshes with limited size are tested and the asymptotic regime of the grid study might be not reached.
+Nevertheless, it still helps to reveal the independence of solutions with respect to meshes --- the norms of electron density and the magnetic field do not deviate in a divergent manner.
+The exception of the norm of the electric field possibly results from the singularity caused by the interface of the contacting and insulating surfaces, as will be seen later.
+In Fig.
+\ref{fig:grid_study_3d_clip_lambda-1e-1} and \ref{fig:grid_study_3d_clip_lambda-0}, we plot the distribution of certain quantities at the cross-section based on different meshes for $\lambda = 0.1$ and $0$ at $t = 1$.
+Thanks to the rotational symmetry of the problem, the solution at the cross-section suffices to characterize the whole solution.
+The figures again demonstrate the stability of the numerical solutions with respect to mesh refinement in the sense that qualitatively the same solutions are produced by a series of meshes of different sizes.
+We would like to point out that singularity arises in the $\mathbf{E}$-field at the interface of contacting and insulating surfaces (two points at the left end and two at the right end).
+In numerical experiments, we observe an increasing magnitude of the $\mathbf{E}$-field at these points as the mesh is refined.
+Furthermore, it is noted from Fig.
+\ref{fig:grid_study_3d_clip_lambda-0} (last two rows) that when $\lambda = 0$, the charges carried by ions and electrons cancel out everywhere as indicated by the quasi-neutral condition $\rho = 0$.
+
+\begin{figure}
+    \centering
+    \includegraphics[scale=0.9]{norm_vs_nCell-T_1.eps}
+    \caption{1-norms of quantities with respect to different mesh size: The results are computed for $\lambda = 1$ and $0.1$ at $t = 1$.}.
+    \label{fig:grid_study_3d}
+\end{figure}
+
+\begin{figure}
+    \centering
+    Refinement 1\hspace{2.5cm}Refinement 2\hspace{2.5cm}Refinement 3\hspace{1cm}
+
+    \includegraphics[scale=0.27]{clip_E_T-1_lambda-1e-1_8-2-2.png}
+    \includegraphics[scale=0.27]{clip_E_T-1_lambda-1e-1_16-3-3.png}
+    \includegraphics[scale=0.27]{clip_E_T-1_lambda-1e-1_32-3-4.png}
+    \includegraphics[scale=0.27]{clip_B_T-1_lambda-1e-1_8-2-2.png}
+    \includegraphics[scale=0.27]{clip_B_T-1_lambda-1e-1_16-3-3.png}
+    \includegraphics[scale=0.27]{clip_B_T-1_lambda-1e-1_32-3-4.png}
+    \includegraphics[scale=0.27]{clip_ne_T-1_lambda-1e-1_8-2-2.png}
+    \includegraphics[scale=0.27]{clip_ne_T-1_lambda-1e-1_16-3-3.png}
+    \includegraphics[scale=0.27]{clip_ne_T-1_lambda-1e-1_32-3-4.png}
+    \includegraphics[scale=0.27]{clip_ni_T-1_lambda-1e-1_8-2-2.png}
+    \includegraphics[scale=0.27]{clip_ni_T-1_lambda-1e-1_16-3-3.png}
+    \includegraphics[scale=0.27]{clip_ni_T-1_lambda-1e-1_32-3-4.png}
+    \caption{Quantities at the cross-section generated by meshes with different refinement level.
+Refinement 1: 1920 primal cells; Refinement 2: 14592 primal cells; Refinement 3: 30720 primal cells.
+The snapshots are computed for $\lambda = 0.1$ at $t = 1$.}
+    \label{fig:grid_study_3d_clip_lambda-1e-1}
+\end{figure}
+
+\begin{figure}
+    \centering
+    Refinement 1\hspace{2.5cm}Refinement 2\hspace{2.5cm}Refinement 3\hspace{1cm}
+
+    \includegraphics[scale=0.27]{slice_E_T-1_lambda-0_8-2-2.png}
+    \includegraphics[scale=0.27]{slice_E_T-1_lambda-0_16-3-3.png}
+    \includegraphics[scale=0.27]{slice_E_T-1_lambda-0_32-3-4.png}
+    \includegraphics[scale=0.27]{slice_B_T-1_lambda-0_8-2-2.png}
+    \includegraphics[scale=0.27]{slice_B_T-1_lambda-0_16-3-3.png}
+    \includegraphics[scale=0.27]{slice_B_T-1_lambda-0_32-3-4.png}
+    \includegraphics[scale=0.27]{slice_ne_T-1_lambda-0_8-2-2.png}
+    \includegraphics[scale=0.27]{slice_ne_T-1_lambda-0_16-3-3.png}
+    \includegraphics[scale=0.27]{slice_ne_T-1_lambda-0_32-3-4.png}
+    \includegraphics[scale=0.27]{slice_ni_T-1_lambda-0_8-2-2.png}
+    \includegraphics[scale=0.27]{slice_ni_T-1_lambda-0_16-3-3.png}
+    \includegraphics[scale=0.27]{slice_ni_T-1_lambda-0_32-3-4.png}
+    \caption{Quantities at the cross-section generated by meshes with different refinement level.
+Refinement 1: 1920 primal cells; Refinement 2: 14592 primal cells; Refinement 3: 30720 primal cells.
+The snapshots are computed for $\lambda = 0$ at $t = 1$.}
+    \label{fig:grid_study_3d_clip_lambda-0}
+\end{figure}
+
+To inspect how the system evolves, we extract the time histories of certain quantities at the origin (the center of the tube) up to $t = 10$ and display them in Fig.
+\ref{fig:origin-data_vs_time}.
+Being originally at rest, the system is excited by the suddenly applied voltage and generates oscillations that dampen over time.
+In general, a large value of $\lambda$ leads to stronger oscillations with larger amplitude whereas smaller $\lambda$ incurs more damping and the system rapidly reaches a steady state.
+It is a reflection of the shielding effect of plasma which is characterized by the Debye length.
+It can also be noticed that the electron velocity becomes steady much sooner than ion velocity, which is a consequence of the huge difference in inertia.
+Besides, the convergence of the discrete model as $\lambda \rightarrow 0$ can be observed---the solution becomes steady over time.
+\begin{figure}
+    \centering
+    \includegraphics[scale=0.9]{origin-data_vs_time.eps}
+    \caption{Time histories of quantities at the origin for different $\lambda$. The simulation is done on a mesh with 1920 primal cells with 8 layers along $z$-axis.}
+    \label{fig:origin-data_vs_time}
+\end{figure}
+
+A critical sign of quasi-neutrality is the vanishing charge.
+In fact, in Section \ref{sec:quasi-neutral_limit} we discuss the limiting model where $\rho = 0$ is satisfied.
+To examine that, the quantities at the $z$-axis over different $\lambda$ are provided in Fig.
+\ref{fig:zaxis-data_vs_z-T_10}.
+The right figure demonstrates the approaching and eventual coincidence of electron and ion densities as $\lambda \rightarrow 0$.
+Furthermore, with relatively small but non-zero $\lambda$, the bulk of the plasma is approximately neutral while the area near the electrodes is not, which is known as a plasma sheath and within such an area the quasi-neutrality is usually inappropriate.
+\begin{figure}
+    \centering
+    \includegraphics{zaxis-data_vs_z-T_10.eps}
+    \caption{Quantities along $z$-axis for different $\lambda$: The results are computed at $t = 10$ on a mesh with 1920 primal cells with 8 layers along $z$-axis.}.
+    \label{fig:zaxis-data_vs_z-T_10}
+\end{figure}
+
+In Fig.
+\ref{fig:clip-ne-nue-T_10} the distribution of the electron number density and velocity at the cross-section is displayed.
+In the non-neutral case, the electrons accumulate near the anode, and the velocity is distributed rather uniformly.
+With the model approaching quasi-neutrality $\lambda = 0$, the electrons move slower in the bulk area while they are accelerated to high speed at the edge of electrodes, and they tend to accumulate in the middle pass.
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.4\textwidth}
+        \centering
+        \includegraphics[scale=0.4]{clip-ne-nue-T_10-lambda_1.png}
+        \caption{$\lambda = 1$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.4\textwidth}
+        \centering
+        \includegraphics[scale=0.4]{clip-ne-nue-T_10-lambda_1e-1.png}
+        \caption{$\lambda = 0.1$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.4\textwidth}
+        \centering
+        \includegraphics[scale=0.4]{clip-ne-nue-T_10-lambda_1e-2.png}
+        \caption{$\lambda = 0.01$}
+    \end{subfigure}
+    \hspace{0.2cm}
+    \begin{subfigure}[b]{0.4\textwidth}
+        \centering
+        \includegraphics[scale=0.38]{clip-ne-nue-T_10-lambda_0.png}
+        \caption{$\lambda = 0$}
+    \end{subfigure}
+    \caption{Electron number density and velocity vector at the cross-section.
+The results are computed at $t = 10$ on a mesh with 1920 primal cells with 8 layers along $z$-axis.
+The velocity vector lengths, which indicates the magnitude, are rescaled by the same factor.}
+    \label{fig:clip-ne-nue-T_10}
+\end{figure}
+
+\section{Conclusion}
+\todo{}
+
+\begin{figure}
+    \centering
+    \begin{tikzpicture}
+        \coordinate (A1) at (0,1.5);
+        \coordinate (A2) at (0,1);
+        \coordinate (A3) at (0,-1);
+        \coordinate (A4) at (0,-1.5);
+        \coordinate (B1) at (6,1.5);
+        \coordinate (B2) at (6,1);
+        \coordinate (B3) at (6,-1);
+        \coordinate (B4) at (6,-1.5);
+        \draw[very thick] (A2) -- (A1) -- node[above]{$\Gamma_I$} (B1) -- (B2);
+        \draw[very thick] (A3) -- (A4) -- node[below]{$\Gamma_I$} (B4) -- (B3);
+        \draw[very thick, blue] (A2) -- node[left]  {$\Gamma_-$}  (A3);
+        \draw[very thick, red]  (B2) -- node[right] {$\Gamma_+$}  (B3);
+        \node at (3,0) {$\Omega$};
+    \end{tikzpicture}
+    \begin{tikzpicture}
+        \coordinate (A1) at (0,1.5);
+        \coordinate (A2) at (0,1);
+        \coordinate (A3) at (0,-1);
+        \coordinate (A4) at (0,-1.5);
+        \coordinate (B1) at (6,1.5);
+        \coordinate (B2) at (6,1);
+        \coordinate (B3) at (6,-1);
+        \coordinate (B4) at (6,-1.5);
+        \draw[very thick] (A2) -- (A1) -- node[above]{$\nabla \times \mathbf{H}\cdot \mathbf{n} = 0$, reflective wall}  node[below, gray]{$\nabla \times \mathbf{E} \cdot \mathbf{n} = 0$ on the whole boundary} (B1) -- (B2);
+        \draw[very thick] (A3) -- (A4) -- node[below]{$\nabla \times \mathbf{H}\cdot \mathbf{n} = 0$, reflective wall} (B4) -- (B3);
+        \draw[very thick, dashed, blue] (A2) -- node[left, yshift=0.3cm] {$\varphi^-(t)$} node[left, yshift=-0.3cm] {\textcolor{black}{open}} (A3);
+        \draw[very thick, dashed, red]  (B2) -- node[right, yshift=0.3cm]  {$\varphi^+(t)$} node[right, yshift=-0.3cm] {\textcolor{black}{open}}  (B3);
+        \node at (3,0) {\textbf{Plasma}};
+        \begin{scope}[shift={(6.5,-1.6)}]
+        \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
+        \draw[blue, -to] (0,0) -- (0.7,0) node[right]{\small $z$};
+        \end{scope}
+    \end{tikzpicture}
+    \caption{Illustration of the boundary conditions: (left) notation of each part of the boundary; (right) boundary conditions at each part of the boundary.\todo{Change the figure}}
+    \label{fig:bc}
+\end{figure}
+
+\bibliography{ref}
 \end{document}

### 2022-09-30 paper_version/main.tex
Polish the first part: plasma model

@@
 
-\section{Introduction}
-Under moderate assumptions, plasmas, which are mixed gases of charged particles, can be treated as fluid and described by hydrodynamic equations.
+\section{Plasma model}
+Under moderate assumptions, plasmas, which are gases composed of charged particles (and possibly neutral particles), can be treated as fluid and described by hydrodynamic equations.
 The Maxwell equations are involved to describe their induction of and interaction with electromagnetic fields.
-In this work, we discuss and implement this so-called \emph{Euler-Maxwell} system with a focus on its limiting behavior of quasi-neutrality, namely when the \emph{Debye length} goes to zero.
+
+\todo{A bit more on the physical background}.
+
+After rescalling all the variables with respect to the prescribed reference units, the Debye length $\lambda_D$, characterizing the charge screening ability of the plasma, would pop up and its zero limit, which is what we called \emph{quasineutral limit}, is of great interest, since the limit model largely simplifies the system and in many cases the accuracy of the assumption is satisfactory enough.
+
+In this section, the multi-species Maxwell-Euler equations with collision term is introduced first, followed by detailed rescalling procedure.
+The quasi-neutral model will be make clear by letting the rescalled Debye length $\lambda$ go to zero.
+Afterwards, a set of boundary conditions are presented and its validity to both non-limit and limit model is discussed.
+Finally, we would like to present a reformulation of the system which would be crucial to the stability of the numerical scheme.
+
+\begin{comment}
+In this work, we discuss and implement the so-called \emph{Euler-Maxwell} system with a focus on its limiting behavior of quasi-neutrality, namely when the \emph{Debye length} goes to zero.
 The dimensionless form of the Euler-Maxwell equations is parameterized by the rescaled Debye length $\lambda$ whose vanishing limit alters the mathematical nature of the equations.
@@
 \end{figure}
-
-\section{The Maxwell-Euler System and its Rescalling}
-\subsection{Full plasma fluid model}
+\end{comment}
+
+\subsection{The Maxwell-Euler System}
 The Maxwell system is described by Maxwell's equations whose expression in SI units read
@@
 For simplicity, we only consider isotropic and homogeneous mediums in vacuum.
-The quantities are thus related by the linear constitutive relations
+We consider the linear constitutive relations
 \begin{equation*}
@@
 Besides, on taking the divergence of equations (\ref{equ:maxwell_faraday}) and (\ref{equ:maxwell_ampere}) together with the relation (\ref{equ:charge_continuity}), it is possible to verify that Gauss's laws (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) are consequences of (\ref{equ:maxwell_faraday}) and (\ref{equ:maxwell_ampere}) provided that (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) are satisfied at the initial time.
-In other words, Gauss's laws (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) are redundant, and Faraday's law (\ref{equ:maxwell_faraday}) and Amp\`{e}re's law (\ref{equ:maxwell_ampere}) suffice.
+In other words, Gauss's laws (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) serve as initial conditions.
+Faraday's law (\ref{equ:maxwell_faraday}) and Amp\`{e}re's law (\ref{equ:maxwell_ampere}) suffice.
 
@@
 The left-hand side of the equations describes the convection of plasma fluids.
+Note that the heat conduction is omitted in the energy equation.
 The first term at the right-hand side denotes Lorentz force in the momentum equation and Joule heating in the energy equation.
@@
 For the sake of simplicity, we would only consider ion-electron collision in this work.
-Such collisions are modeled by friction terms as follows, and we simply present the expressions without derivation (see \citep[][sec.
+Under moderate assumptions, such collisions can be well modelled by friction terms, and we simply present the expressions without derivation (see \citep[][sec.
 5.6.2]{chen2016}):
@@
 ln$\Lambda$ is called the \emph{Coulomb logarithm}, which typically takes a numerical value of order 10–20 .
-Because of the conservation of momentum, the collision term experienced by ions $\mathbf{R}_{i}^{\text{coll}}$ is just the negative of $\mathbf{R}_{e}^{\text{coll}}$.
+Because of the conservation of momentum, the collision term experienced by ions $\mathbf{R}_{i}^{\text{coll}}$ is nothing but the negation of $\mathbf{R}_{e}^{\text{coll}}$.
 For full details about the ionization and recombination, readers are referred to \cite{fuchs_2021}.
@@
 
-\subsection{Rescaled Maxwell-Euler system}
-The multi-scale nature of the Euler-Maxwell system is revealed by defining different dimensionless parameters.
-In particular, the quasi-neutrality approximation is clarified.
-The rescaling procedure mostly sticks to that of \cite{degond_2017}.
-
-First, typical values for each quantity, as well as the characteristic length and time scale are specified.
-Rescaled by these values, the magnitude of each term of the equations can be compared according to the presumption on the magnitude of these typical values.
+\subsection{Rescalling}
+In the rescalling, the variables in the equations are taken as the ratio of their original quantities and reference units, which transforms the system into a dimensionless form.
+The magnitudes of the dimensionless numbers are indications of the magnitude of corresponding terms.
+In this part, the rescalling procedure mostly sticks to that of \cite{degond_2017}.
+
+First, reference units for each quantity, e.g.
+the characteristic length and time scale, are prescribed.
 We define $\overline{x}$ and $\overline{t}$ as space and time scale of interest, by which the reference velocity $\overline{v}$ is defined as $\overline{x}/\overline{t}$.
@@
 
-The Euler-Maxwell system (\ref{equ:maxwell_faraday}) to (\ref{equ:euler_}) is readily to be rescaled by nondimensionalizing each quantity with respect to its typical value.
 By abuse of notation, the dimensionless quantities have the same symbol with their original ones without incurring any ambiguity.
-For simplicity, we only consider the collision terms, namely $\Gamma_* = 0, \mathbf{R}_* = \mathbf{R}_*^\text{coll}, Q_* = 0$ in (\ref{equ:euler_}), while neglecting other effects.
+For the sake of simplicity, we only consider the collision terms, namely $\Gamma_* = 0, \mathbf{R}_* = \mathbf{R}_*^\text{coll}, Q_* = Q_*^\text{coll}$ in (\ref{equ:euler_}), while neglecting other effects.
 The rescaled Euler-Maxwell system reads
@@
     \varepsilon_*^{-2}\mathbf{R}_*^{\text{coll}} \\
-    0 
+    \varepsilon_*^{-2}Q_*^{\text{coll}} 
     \end{bmatrix}, \label{equ:euler_rescalling}
@@
     \varepsilon_*^{-2}\mathbf{R}_*^{\text{coll}} \\
-    0 
+    \varepsilon_*^{-2}Q_*^{\text{coll}} 
     \end{bmatrix}, \label{equ:euler_rescaled}
@@
 \begin{equation} \label{equ:collision_rescaled} 
-    \mathbf{R}_i^{\text{coll}} = \alpha^{\text{coll}}n_en_i(\mathbf{u}_i - \mathbf{u}_e) = - \mathbf{R}_e^{\text{coll}}.
+    \mathbf{R}_i^{\text{coll}} = \alpha^{\text{coll}}n_en_i(\mathbf{u}_i - \mathbf{u}_e) = - \mathbf{R}_e^{\text{coll}},
 \end{equation}
-
-Although the rescaling of the equations involves considerable physical intuitions on the decision of typical values and their magnitudes, which is crucial to reach a physically meaningful problem, we are now in a position to forget this reasoning, and focus on the singular perturbation problem parameterized by $\lambda$.
-The rescaling enables us to identify the magnitude of each term of the equations, which is revealed by the prefactor polynomial of $\lambda$.
+and consequently, the rescaled friction heat for ions and electrons takes the expression
+\begin{align*} 
+    Q_i^{\text{coll}} &= \alpha^{\text{coll}}n_en_i \mathbf{u}_i (\mathbf{u}_i - \mathbf{u}_e), \\
+    Q_e^{\text{coll}} &= \alpha^{\text{coll}}n_en_i \mathbf{u}_e (\mathbf{u}_e - \mathbf{u}_i).
+\end{align*}
+
+We end up getting the rescaled Maxwell-Euler system parameterized by $\lambda$.
+The rescaling enables us to identify the magnitude of each term in the equations, which is revealed by the prefactor polynomial of $\lambda$.
 
 \subsection{Quasi-neutral limit} \label{sec:quasi-neutral_limit}
-As is already discussed in section \ref{sec:quasi-neutrality}, the quasi-neutrality, being an important character of plasmas, refers to the fact that the net charge of the free electrons and ions in plasmas cancel out over an area of the same order as the Deybe length $\lambda_D$.
-When the typical length scale $\overline{x}$ is of magnitudes larger than $\lambda_D$, the condition $\rho = 0$ can be approximately satisfied.
-
-Such behavior is clearly explained through the rescaled Euler-Maxwell system (\ref{equ:maxwell_faraday_rescaled}) to (\ref{equ:euler_rescaled}).
+The Debye length $\lambda_D$ (see its definition at the proceeding section) is an characteristic length over which any net charge is screened due to the thermal diffusion of the particles.
+In many situations, it has a rather low value.\todo{Examples and typical values}.
+That justifies the quasi-neutral assumptions of vanishing $\lambda_D$ with respect to the interested length scale.
+Under this limit, the plasma keeps locally neutral in net charge, namely $\rho = \sum_* q_*n_* = 0$.
+Such behavior is explained through the rescaled Euler-Maxwell system (\ref{equ:maxwell_faraday_rescaled}) to (\ref{equ:euler_rescaled}).
 By formally taking dimensionless Debye length $\lambda$ to zero\footnote{The convergence of the solutions as $\lambda$ tending to zero is discussed in \cite[][chap.
@@
 
-The vanishing time derivative of $\mathbf{E}$-field is an indicator of the singular perturbation nature of the quasi-neutral model.
-To be specific, in the non-neutral model the $\mathbf{E}$-field evolves with time whereas in the quasi-neutral model it responds instantaneously to other quantities according to the constraint (\ref{equ:maxwell_ampere_limit}).
+This limit poses a \emph{singular perturbation problem} in the sense that vanishing $\lambda$ changes the character of the PDE system.
+To be more specific, in the non-limit model the $\mathbf{E}$-field evolves with time whereas in the quasi-neutral model it responds instantaneously to other quantities according to the constraint (\ref{equ:maxwell_ampere_limit}).
 To make it clear, we replace the equation (\ref{equ:maxwell_ampere_rescaled}) by the sum of the curl of (\ref{equ:maxwell_faraday_rescaled}) and the time-derivative of (\ref{equ:maxwell_ampere_rescaled}).
-Meanwhile exploiting the momentum equation in (\ref{equ:euler_rescaled}) to express $\partial_t\mathbf{J}$, we end up getting the reformulated Maxwell's equations
-\begin{align}
-    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday_reform}\\
-    \lambda^2\partial_t^2 \mathbf{E} + \nabla \times \nabla \times \mathbf{E} &= - a\mathbf{E} - \mathbf{b}, \label{equ:maxwell_ampere_reform}\\
-    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B_reform}\\
-    \lambda^2\nabla \cdot \mathbf{E} &= \rho, \label{equ:maxwell_gauss_D_reform}
+Meanwhile exploiting the momentum equation in (\ref{equ:euler_rescaled}) to express $\partial_t\mathbf{J}$, we end up getting the equation that the $\mathbf{E}$-field satisfies
+\begin{align}
+    \lambda^2\partial_t^2 \mathbf{E} + \nabla \times \nabla \times \mathbf{E} &= - a\mathbf{E} - \mathbf{b}, \label{equ:E}
 \end{align}
@@
 \end{equation*}
-It is easy to check that (\ref{equ:maxwell_faraday_reform}) to (\ref{equ:maxwell_ampere_reform}) is equivalent to (\ref{equ:maxwell_faraday_rescaled}) to (\ref{equ:maxwell_gauss_D_rescaled}) as soon as (\ref{equ:maxwell_ampere_rescaled}) is satisfied at the initial time.
-The equation (\ref{equ:maxwell_ampere_reform}) implies the shift from the hyperbolic nature to the elliptic nature of the $\mathbf{E}$-field as $\lambda\rightarrow0$.
-One of the key aims of designing an AP scheme is to reproduce this shift at the discrete level.
+ The equation (\ref{equ:E}) implies the shift from the hyperbolic nature to the elliptic nature of the $\mathbf{E}$-field as $\lambda\rightarrow0$.
+
+We would like to point out the proceeding argument about the derivation of limit model is merely formal and heuristic without mentioning the proof and to which sense the convergence holds.
+Deep mathematical tools from the perturbation theory is needed to rigorously prove the convergence of the limiting sequence.
+This topic is beyond this paper and thus omitted.
+Readers are referred to \cite{remi_2014} for the quasi-neutral limit of the Maxwell-Euler system, and \cite{mark_1995} for the general theory.
 
 \subsection{Boundary conditions}
-On yielding the rescaled system (?) - (?), we would like to discuss about the boundary conditions here.
-One cannot directly impose any BC suitable for the non-limit model since it could possibly be ill-posed for the limiting model.
-In our case, we dealing with the shifting between the full Maxwell equations and the eddy-current model.
-
-Since the scheme is supposed to work for both regimes, the BCs ought to be uniformly well-posed.
-An example is given to convey the idea.
-Let's look at the continuous non-neutral Amp\`{e}re's law (\ref{equ:maxwell_ampere_rescaled})
-\begin{equation*}
-    \lambda^2 \partial_t \mathbf{E} - \nabla \times \mathbf{B} = - \mathbf{J},
-\end{equation*}
-which loses its hyperbolic character and becomes a constraint when $\lambda \rightarrow 0$. Now consider two boundary conditions
-\begin{itemize}
-    \item[-]  $\mathbf{E}\cdot\mathbf{n} = 0$ on $\partial\Omega$;
-    \item[-] $\nabla \times \mathbf{B} \cdot\mathbf{n} = \mathbf{J}\cdot\mathbf{n}$ on $\partial\Omega$. 
-\end{itemize}
-They are equivalent when $\lambda$ is non-zero provided $\mathbf{E}\cdot\mathbf{n}|_{\partial\Omega}$ is zero at the initial time.
-However, setting $\lambda = 0$ destroys the equivalence.
-The second BC no longer implies the first one and becomes redundant since the quasi-neutral Amp\`{e}re's law already enforces such condition, which ruins the well-posedness of the quasi-neutral problem.
-Hence the first BC is the one that is supposed to be employed.
-
-From the viewpoint of the discrete model, the continuous equations are discretized into a set of algebraic equations according to the scheme, and they are assembled into a linear system that needs to be solved at each time step.
-The redundancy of the second BC at limiting case results in the singularity of the linear system since the BC can be derived by linear operations from the algebraic form of the PDEs.
 
@@
 
-\section{Previous Work: 1D Discretization}
+\subsection{Reformulation}
+In the insulating domain, no charges and currents are present and thus the Maxwell system in $\Omega_I$ is described by    
+\begin{align}
+    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:faraday_ins}\\ 
+    \lambda^2 \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= 0,  \label{equ:ampere_ins}\\
+    \nabla \cdot \mathbf{B} &= 0, \label{equ:gauss_B_ins}\\
+    \lambda^2 \nabla \cdot \mathbf{D} &= 0 \label{equ:gauss_D_ins}.
+\end{align}
+In non-neutral regime, namely $\lambda = \mathcal{O}(1)$, the Maxwell system in $\Omega_I$ is well-posed and Gauss's laws (\ref{equ:gauss_B_ins}) (\ref{equ:gauss_D_ins}) are redundant as long as they are satisfied at initial moment.
+Nonetheless, as the system approaches the quasi-neutral limit as $\lambda \rightarrow 0$, Gauss's law for $\mathbf{D}$-field (\ref{equ:gauss_D_ins}) becomes degenerate.
+Due to limited precision of computers, schemes based on this set of PDEs would run into instability because the vanishing divergence would be broken down as $\nabla \cdot \mathbf{D} = 0/\lambda^2 = 0$ would not hold numerically when $\lambda^2$ becomes extremely small.
+
+To see this issue from another perspective, we observe the limit Maxwell system in $\Omega_I$
+\begin{align}
+    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:faraday_ins_limit}\\ 
+    - \nabla \times \mathbf{H} &= 0,  \label{equ:ampere_ins_limit}\\
+    \nabla \cdot \mathbf{B} &= 0, \label{equ:gauss_B_ins_limit}\\
+    \nabla \cdot \mathbf{D} &= 0 \label{equ:gaus_D_ins_limit}.
+\end{align}
+Again, Gauss's law for $\mathbf{B}$-field (\ref{equ:gauss_B_ins_limit}) is redundant while Gauss's law for $\mathbf{D}$-field (\ref{equ:gaus_D_ins_limit}) is no longer the consequence of the Amper\`{e}'s law and essential for the well-posedness of the problem \citep{ana_2010}.
+From this perspective, the degeneracy of Gauss's law for $\mathbf{D}$-field of the system (\ref{equ:faraday_ins_limit}) to (\ref{equ:gaus_D_ins_limit}) as $\lambda \rightarrow 0$ potentially poses some problem.
+
+In one word, the set of equations (\ref{equ:faraday_ins_limit}) to (\ref{equ:gaus_D_ins_limit}) ``approaches" an ill-posed situation as $\lambda \rightarrow 0$.
+This is totally fine in the continuous level while it could be problematic in the discrete level due to a limited precision.
+
+We propose the following reformulation as a remedy, which introduces a Lagrange multiplier $p$ and removes the $\lambda^2$ prefactor in Gauss's law for $\mathbf{D}$-field:
+\begin{align}
+    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:faraday_ins_reform}\\ 
+    \lambda^2 \partial_t \mathbf{D} - \nabla \times \mathbf{H} + \colorbox{orange!20}{$\nabla p$} &= 0,  \label{equ:ampere_ins_reform}\\
+    \nabla \cdot \mathbf{B} &= 0, \label{equ:gauss_B_ins_reform}\\
+    \nabla \cdot \mathbf{D} &= 0 \label{equ:gauss_D_ins_reform}.
+\end{align}
+Supplemented with the boundary condition $p = 0$ on $\partial\Omega_I$, one can check that (\ref{equ:faraday_ins_reform}) to (\ref{equ:gauss_D_ins_reform}) are equivalent to the original formulation (\ref{equ:faraday_ins})-(\ref{equ:gauss_D_ins}) by verifying that $p = 0$ in $\Omega_I$.
+This is done by taking the divergence of (\ref{equ:ampere_ins_reform}) such that the Laplace equation of $p$ with zero Dirichlet boundary condition gives vanishing $p$.
+The importance of this reformulation will be make clear in the numerical experiment.
+
+\section{Discretization}
+
+\subsection{1D Discretization}
 In this section we briefly discuss the underlying work \cite{degond_2012} on which our work is built.
 Meanwhile, this section also serves as a preliminary case study such that readers can better understand the 3D scheme that we present.
-\subsection{1D plasma model}
+\subsubsection{1D plasma model}
 The 3D problem is projected onto the 1D axis by assuming vanishing traverse derivatives (see Fig.
@@
 \end{align*}
-\subsection{Finite difference on staggered grid}
+\subsubsection{Finite difference on staggered grid}
 \todo{Add illustration about 1D FDTD}
-\subsection{Semi-implicit AP time-stepping}
+\subsubsection{Semi-implicit AP time-stepping}
 Adapt the AP scheme (\ref{equ:maxwell_faraday_ap}) to (\ref{equ:euler_ap}) to this case, and we end up with
@@
 
-\section{Discretization in 3D}
-\subsection{Primal-dual staggered mesh}
+\subsection{Discretization in 3D}
+\subsubsection{Primal-dual staggered mesh}
 A mesh doublet $(\mathcal{M}, \Tilde{\mathcal{M}})$ is required for the formulation of FIT in the need of incorporating the material laws.
@@
 \end{figure}
-\subsection{Discrete Maxwell equations: DEC}
+\subsubsection{Discrete Maxwell equations: DEC}
 \todo{Reformulate this section in the spirit of DEC. Now it is a bit tedious.}
@@
 is reduced to a finite number of well-defined discrete unknowns \citep{weiland_2003}.
-\subsection{Finite volume discretization of the Euler equations}
+\subsubsection{Finite volume discretization of the Euler equations}
 We employ the finite volume method (FVM) to discretize the Euler system.
@@
 where $\overline{s} = \text{max}(s(\overline{\mathbf{U}}_L), s(\overline{\mathbf{U}}_R))$ with $s(\mathbf{U}) := |\mathbf{u}\cdot\mathbf{n}| + \sqrt{\gamma p/\rho}$ representing the largest wave speed.
-\subsection{Discrete boundary conditions}
+\subsubsection{Discrete boundary conditions}
 Dirichlet BCs lead to setting corresponding DoFs at boundary to zero. Vanishing tangential curl is treated by introducing a boundary potential. 
 \todo{More details.}
-\subsection{Stabilization in insulating domain}
+\subsubsection{Stabilization in insulating domain}
 We repeat the dilemma again: the scheme fails for $\lambda \rightarrow 0$. The Maxwell system in $\Omega_I$ is    
@@
 
-\subsection{Semi-implicit AP schemes}
+\subsubsection{Semi-implicit AP schemes}
 In this section, we present the full discretization with AP property.
@@
 
-\subsection{An algebraic check on the well-posedness}
+\subsubsection{An algebraic check on the well-posedness}
 
@@
 
-\subsection{Procedure of time-stepping}
+\subsubsection{Procedure of time-stepping}
 In this section we provide full details on the procedure of the semi-implicit time-stepping.

### 2022-10-03 paper_version/main.tex
polish first section: Plasma model

@@
 Deep mathematical tools from the perturbation theory is needed to rigorously prove the convergence of the limiting sequence.
-This topic is beyond this paper and thus omitted.
+This topic is beyond the scope of this paper and thus omitted.
 Readers are referred to \cite{remi_2014} for the quasi-neutral limit of the Maxwell-Euler system, and \cite{mark_1995} for the general theory.
@@
 
-\todo{Give a sketch of an abstract domain, and assign BCs to each boundary for both Euler and Maxwell.}
+We consider a simply connected domain $\Omega$ that is decomposed into two sub-domains $\Omega_P$ and $\Omega_I$ representing plasma domain and insulating domain respectively.
+We use the notation $\Gamma_C := \partial\Omega \cap \partial\Omega_P$, denoting the contact boundary, and $\Gamma_I := \partial\Omega \cap \partial\Omega_I$ for the insulating boundary.
+The interface between the two domains is denoted by $\Gamma_W = \partial\Gamma_I \cap \partial\Gamma_P$.
+This setting is visualized in Fig.
+.
+
+The plasma fills $\Omega_I$ where the Euler system lies and thus the boundary of plasmas lies on $\partial\Omega_P$.
+We consider the physical scenario where plasmas are confined with the solid insulator.
+Therefore, the interface $\Gamma_W$ is treated as reflective walls where fluid particles are bounced back while keeping the tangential velocity and energy unchanged.
+The contact boundary $\Gamma_C$ is where the plasma and energy flow across, modelled by, for the sake of simplicity, open boundaries, namely they are free to flow through.
+\todo{Discussion the more realistic electrode model}
+
+The Maxwell system is defined on the whole domain $\Omega$.
+External voltages are enforced on the contact boundary $\Gamma_C$ to model electrodes.
+More specifically, $\Gamma_C$ is usually composed of disjoint connecting components $\Gamma_C^i$, $i \leq N$ where $N$ is total number of these boundary components.
+Constant potentials are enforced on each component in the sense that $\varphi|_{\Gamma_C^i} = \varphi_i$.
+The insulating boundary blocks the energy interchange and therefore only admits zero electric and magnetic flux, in the sense that $\text{curl}\mathbf{E}\cdot \mathbf{n} = 0$ and $\text{curl}\mathbf{H}\cdot \mathbf{n} = 0$ where $\mathbf{n}$ is the outer normal vector.
+\begin{figure}
+\begin{minipage}{0.45\textwidth}
+    \resizebox{\textwidth}{!}{
+    \begin{tikzpicture}
+    \coordinate (O1) at (0,0);
+    \draw[very thick] (O1) circle (1) node[blue] {Electrode};
+    \fill[blue, opacity=0.2] (O1) circle (1);
+    \draw[very thick] (O1) circle (1.5);
+    \coordinate (O2) at (4.5,1);
+    \draw[gray] (O2) circle (1);
+    \node at (O2) {\textcolor{red}{Electrode}};
+    \node at (barycentric cs:O1=1,O2=1) {Plasma}; 
+    \fill[red, opacity=0.2] (O2) circle (1);
+    \coordinate (S1) at ([shift={(-0.196,0.98)}]O1);
+    \coordinate (S2) at ([shift={(-0.196,0.98)}]O2);
+    \coordinate (P1) at ([shift={(0.196,-0.98)}]O1);
+    \coordinate (P2) at ([shift={(0.196,-0.98)}]O2);
+    \draw[gray] (S1) -- (S2);
+    \draw[gray] (P1) -- (P2);
+    \coordinate (SS1) at ([shift={({-0.196*1.5},{0.98*1.5})}]O1);
+    \coordinate (SS2) at ([shift={({-0.196*1.5},{0.98*1.5})}]O2);
+    \coordinate (PP1) at ([shift={({0.196*1.5},{-0.98*1.5})}]O1);
+    \coordinate (PP2) at ([shift={({0.196*1.5},{-0.98*1.5})}]O2);
+    \draw[very thick] (SS1) -- (SS2);
+    \draw[very thick] (PP1) -- (PP2); 
+    \draw[gray] (SS2) arc (101.31:180+101.31:1.5);
+    \draw[very thick] (PP2) arc (101.31-180:101.31:1.5);
+    \draw[-to] (barycentric cs:SS1=1,SS2=1,S1=1,S2=1) to[out=90,in=0] ([shift={(-0.5,0.5)}]barycentric cs:SS1=1,SS2=1,S1=1,S2=1) node[left, gray] {Insulator};
+    \begin{scope}[shift={(5.5,-1.4)}]
+    \draw[blue, -to] (0,0) -- (0.65,0.12) node[right]{\small $z$};
+    \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
+    \draw[blue, -to] (0,0) -- (0.7,0) node[below]{\small $y$};
+    \end{scope}
+    \end{tikzpicture}}
+\end{minipage}
+\begin{minipage}{0.49\textwidth}
+    \resizebox{1.1\textwidth}{!}{ \begin{tikzpicture}
+        \coordinate (A1) at (0,1.5);
+        \coordinate (A2) at (0,1);
+        \coordinate (A3) at (0,-1);
+        \coordinate (A4) at (0,-1.5);
+        \coordinate (B1) at (6,1.5);
+        \coordinate (B2) at (6,1);
+        \coordinate (B3) at (6,-1);
+        \coordinate (B4) at (6,-1.5);
+        \draw[gray] (A2) -- node[above]{\textbf{Insulator $\Omega_I$}} node[black, below]{$\Gamma_W$} (B2);
+        \draw[gray] (A3) -- node[below]{\textbf{Insulator $\Omega_I$}} node[black, above]{$\Gamma_W$} (B3);
+        \draw[very thick] (A2) -- (A1) -- node[above]{$\Gamma_I$}  (B1) -- (B2);
+        \draw[very thick] (A3) -- (A4) -- node[below]{$\Gamma_I$} (B4) -- (B3);
+        \draw[very thick, dashed, blue] (A2) -- node[left] {$\Gamma_C^1$} (A3);
+        \draw[very thick, dashed, red]  (B2) -- node[right] {$\Gamma_C^2$}  (B3);
+        \node at (3,0) {\textbf{Plasma $\Omega_P$}};
+        \begin{scope}[shift={(6.5,-1.6)}]
+        \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
+        \draw[blue, -to] (0,0) -- (0.7,0) node[right]{\small $z$};
+        \end{scope}
+    \end{tikzpicture}}
+\end{minipage}
+\caption{Sketch of the domain. The right figure shows the cross section on the $x$-$z$ plane.}
+\end{figure}
+
+    To summarize the boundary conditions for both systems:
+
+\vspace{10pt}
+\begin{minipage}[t]{0.49\textwidth}
+    \textbf{For the Euler equations:}
+    \begin{align*}
+    \mathbf{u_*}\cdot \mathbf{n} &= 0 \ \ \text{on} \ \ \Gamma_W, \\
+    \text{grad}\mathbf{n_*} \cdot \mathbf{n} &= 0 \ \ \text{on} \ \ \Gamma_W. \\
+    \text{grad}\mathbf{e_*} \cdot \mathbf{n} &= 0 \ \ \text{on} \ \ \Gamma_W. \\
+    \text{grad}\mathbf{U_*} \cdot \mathbf{n} &= \mathbf{0} \ \ \text{on} \ \ \Gamma_C.
+\end{align*}
+\end{minipage}
+\begin{minipage}[t]{0.49\textwidth}
+    \textbf{For the Maxwell equations:}
+    \begin{align*}
+    \varphi &= \varphi^i(t)\ \ \text{on} \ \ \Gamma_C^i, \\
+    \text{curl} \mathbf{E} \cdot \mathbf{n} &= 0\ \ \text{on} \ \  \Gamma_I,  \\
+    \text{curl} \mathbf{H} \cdot \mathbf{n} &= 0\ \  \text{on} \ \  \Gamma_I.\
+    \end{align*}
+\end{minipage}
+
+\vspace{10pt}
+A small remark goes to the validity of assignment of electric potentials on $\Gamma_c^i$.
+Since the surface curl $\text{curl}_\gamma\mathbf{E} = \text{curl} \mathbf{E} \cdot \mathbf{n} = 0$, there exists a surface potential $\varphi$ such that the surface gradient $\nabla_\Gamma \varphi = \gamma_\tau \mathbf{E}$ where $\gamma_\tau $ is the tangential trace operator.
 
 \subsection{Reformulation}
-In the insulating domain, no charges and currents are present and thus the Maxwell system in $\Omega_I$ is described by    
+In the insulating domain, the Euler system is not defined there and no charges or currents are present. Consequently, the Maxwell system in $\Omega_I$ is described by    
 \begin{align}
@@
 \end{align}
+
 In non-neutral regime, namely $\lambda = \mathcal{O}(1)$, the Maxwell system in $\Omega_I$ is well-posed and Gauss's laws (\ref{equ:gauss_B_ins}) (\ref{equ:gauss_D_ins}) are redundant as long as they are satisfied at initial moment.
 Nonetheless, as the system approaches the quasi-neutral limit as $\lambda \rightarrow 0$, Gauss's law for $\mathbf{D}$-field (\ref{equ:gauss_D_ins}) becomes degenerate.
-Due to limited precision of computers, schemes based on this set of PDEs would run into instability because the vanishing divergence would be broken down as $\nabla \cdot \mathbf{D} = 0/\lambda^2 = 0$ would not hold numerically when $\lambda^2$ becomes extremely small.
+Due to limited precision of computers, schemes based on this set of PDEs would run into instability.
+The vanishing divergence would be broken down as $\nabla \cdot \mathbf{D} = 0/\lambda^2 = 0$ would not hold numerically when $\lambda^2$ becomes extremely small.
 
@@
 In one word, the set of equations (\ref{equ:faraday_ins_limit}) to (\ref{equ:gaus_D_ins_limit}) ``approaches" an ill-posed situation as $\lambda \rightarrow 0$.
-This is totally fine in the continuous level while it could be problematic in the discrete level due to a limited precision.
+This is totally fine in the continuous level while it could be problematic in the discrete level due to a limited floating-point precision.
 

### 2022-10-10 paper_version/main.tex
remove insertion of missing figures
fix errors
minor change
polish 2.1 introduction on AP

@@
 \usepackage{amsthm}
+\usepackage{bm}
 \usepackage{hyperref}
@@
 \usepackage{tcolorbox}
+\usepackage{subcaption}
 
@@
     0 \\
-    \eta \zea \varepsilon_*^{-2} q_* n_*\mathbf{E} + \eta \zeta^2 \beta \varepsilon_*^{-2} q_* n_* \mathbf{u}_* \times \mathbf{B} \\
+    \eta \zeta \varepsilon_*^{-2} q_* n_*\mathbf{E} + \eta \zeta^2 \beta \varepsilon_*^{-2} q_* n_* \mathbf{u}_* \times \mathbf{B} \\
     \zeta \eta \varepsilon_*^{-2} \mathbf{J}_* \cdot \mathbf{E}
@@
     \varepsilon_*^{-2}\mathbf{R}_*^{\text{coll}} \\
-    \varepsilon_*^{-2}Q_*^{\text{coll}} 
+    \varepsilon_*^{-2}Q_*^{\text{coll}} \\
     \end{bmatrix}, \label{equ:euler_rescalling}
@@
     \mathbf{u_*}\cdot \mathbf{n} &= 0 \ \ \text{on} \ \ \Gamma_W, \\
-    \text{grad}\mathbf{n_*} \cdot \mathbf{n} &= 0 \ \ \text{on} \ \ \Gamma_W. \\
-    \text{grad}\mathbf{e_*} \cdot \mathbf{n} &= 0 \ \ \text{on} \ \ \Gamma_W. \\
+    \text{grad}n_* \cdot \mathbf{n} &= 0 \ \ \text{on} \ \ \Gamma_W. \\
+    \text{grad}e_* \cdot \mathbf{n} &= 0 \ \ \text{on} \ \ \Gamma_W. \\
     \text{grad}\mathbf{U_*} \cdot \mathbf{n} &= \mathbf{0} \ \ \text{on} \ \ \Gamma_C.
@@
 
+\subsection{Asymptotic-Preserving schemes}
+As is mentioned in the proceeding chapter, the zero-Debye-length limit poses a singularly perturbed problem in the sense that the Maxwell-Euler equations changes its type from a hyperbolic to hyperbolic-elliptic one.
+To simulate a plasma, one usually first identifies which regime it lies in and designs the scheme according to its type.
+Nonetheless, there exist cases that covers both regimes and cannot be approximated by either of them.
+Due to the difference on their mathematical characters, naively applying classical schemes for $\lambda = \mathcal{O}(1)$ to problems with $\lambda \rightarrow 0$ would fail and vice versa.
+\emph{Asymptotic-preserving} (AP) schemes are such a class of schemes that provide a unified approach for both limit and non-limit problems.
+
+To illustrate the general concept of AP schemes, we quote the celebrated commutative diagram Fig.
+\ref{fig:commutative_diagram_ap} in \cite{jin_1999} which sketches the property that an AP scheme should possess.
+We consider a parametrized problem $P^\lambda$ that converges to its limit $P^0$ as the perturbed parameter $\lambda \rightarrow 0$.
+To discretize $P^\lambda$, the scheme $P^\lambda_h$ is constructed whose numerical results depend on some discretization parameter $h$, e.g.
+mesh size.
+Beside the convergence of the scheme $P^\lambda_h$ to its analytic solution $P^\lambda$ as $h\rightarrow0$, the AP property additionally requires that the convergence of $P^\lambda_h$ to the limit discrete model $P^0_h$ as $\lambda\rightarrow0$.
+Such a limit scheme $P^0_h$ should in turn converge to the continuous solution $P^0$ as $h \rightarrow 0$.
+In short, an AP scheme $P^\lambda_h$ makes the diagram Fig.
+\ref{fig:commutative_diagram_ap} commutative.
+
+The concept of AP schemes can be traced back to \cite{jin_1995} in which the authors approximate a conservation law by a hyperbolic system with relaxation, and manage to construct a scheme that is stable for an arbitrarily small relaxation parameter.
+The term ``asymptotic-preserving" was formally introduced in \cite{jin_1999} for handling the diffusive regime of kinetic models.
+This concept stemmed from and remains very active in kinetic models with stiff relaxations, see \cite{jin_2010} and the references therein.
+Nonetheless, considerable effort has been put into developing AP schemes for many other problems that admit asymptotic behavior.
+For instance, in fluid dynamics, the so-called \emph{all-speed} schemes are advantageous when dealing with both compressible and incompressible regimes simultaneously.
+\cite{degond_2007, haack_2010} devise all-speed schemes for the isentropic Euler equations through fast-slow decomposition of velocity fields.
+Concerning plasma physics, a number of papers are available dealing with the quasi-neutral limit of the Euler-Poisson (or Euler-Maxwell) system \citep{crispel_2005, degond_2008, degond_2011, degond_2012} and Vlasov-Poisson (or Vlasov-Maxwell) system \citep{degond_2017, degond2017b, zhu_2017}.
+Besides, \cite{caflisch_1997, berthon2011} concern AP schemes for generic hyperbolic systems with relaxation source terms.
+For a comprehensive review on AP schemes, readers are referred to \cite{jin_2010} for kinetic and hyperbolic equations, and \cite{degond_2017} for multiscale plasma simulations.
+
+To devise an AP scheme, the dependence of the stability constraints of $h$ on $\lambda$ has to be removed.
+This is mainly achieved by utilizing implicit time-stepping for certain terms.
+As is summarized by \cite{degond_2017}, AP schemes aim to bridge several sets of equations describing the system in different regimes, rather than to alleviate the stability constraints of the numerical methods.
+In this sense, a fully-implicit scheme is likely to be overkill and thus a smart construction is necessary.
+The second consideration goes to the identification of a compatible boundary conditions for both regimes, which would be shown to be essential for the numerical stability.
+
+In the following sections, we first briefly discuss the 1D scheme for the Maxwell-Euler system devised by \cite{degond_2012} on which our work us built.
+this section also serves as a preliminary case study such that readers can better understand the 3D scheme.
+
+\begin{figure}
+    \centering
+    \begin{tikzpicture}
+    \node (nw) {\Large $P^\lambda_h$};
+    \node (ne) [right=3cm of nw]{\Large $P^\lambda$};
+    \node (sw) [below=of nw]{\Large $P^0_h$};
+    \node (se) [right=3cm of sw]{\Large $P^0$};
+    \draw[->] (nw.east)  -- node [above,midway] {$h\rightarrow0$} (ne.west) ;
+    \draw[->] (nw.east)  --  (ne.west) ;
+    \draw[->] (nw.south) -- node [left,midway] {$\lambda\rightarrow0$} (sw.north);
+    \draw[->] (nw.south) -- node {} (sw.north);
+    \draw[->] (sw.east)  -- node [above,midway] {$h\rightarrow0$}(se.west);
+    \draw[->] (ne.south) -- node [left,midway] {$\lambda\rightarrow0$} (se.north);
+    \end{tikzpicture}
+    \caption{Commuting diagram of AP schemes}
+    \label{fig:commutative_diagram_ap}
+\end{figure}
+
+\colorbox{red}{Polish until here.}
+
 \subsection{1D Discretization}
-In this section we briefly discuss the underlying work \cite{degond_2012} on which our work is built.
-Meanwhile, this section also serves as a preliminary case study such that readers can better understand the 3D scheme that we present.
 \subsubsection{1D plasma model}
@@
     \centering
-    \includegraphics[scale=0.2]{1d_frame.png}
+    %\includegraphics[scale=0.2]{1d_frame.png}
     \caption{Projection of the 3D model onto $z$-axis.
@@
     \centering
-    \includegraphics{z_axis_reduction.eps}
+    %\includegraphics{z_axis_reduction.eps}
     \caption{Comparison of 1D two-fluid model and reduced 1D model on $z$-axis from 3D two-fluid model.
@@
     \centering
-    \includegraphics[scale=0.4]{primal_mesh.png}
+    %\includegraphics[scale=0.4]{primal_mesh.png}
     \hspace{2cm}
-    \includegraphics[scale=0.4]{dual_mesh.png}
+    %\includegraphics[scale=0.4]{dual_mesh.png}
     \caption{Primal (left) and dual (right) meshes used for the 3D testing case. They are generated by the code developed in \cite{fuchs_2021}.}
@@
     \centering
-    \includegraphics[scale=0.35]{E_lambda_1.png}
-    \includegraphics[scale=0.35]{B_lambda_1.png}
-    \includegraphics[scale=0.35]{ue_lambda_1.png} \\
+    %\includegraphics[scale=0.35]{E_lambda_1.png}
+    %\includegraphics[scale=0.35]{B_lambda_1.png}
+    %\includegraphics[scale=0.35]{ue_lambda_1.png} \\
     (a) $\lambda = 1.0$ \\
-    \includegraphics[scale=0.35]{E_lambda_1e-2.png}
-    \includegraphics[scale=0.35]{B_lambda_1e-2.png}
-    \includegraphics[scale=0.35]{ue_lambda_1e-2.png} \\
+    %\includegraphics[scale=0.35]{E_lambda_1e-2.png}
+    %\includegraphics[scale=0.35]{B_lambda_1e-2.png}
+    %\includegraphics[scale=0.35]{ue_lambda_1e-2.png} \\
     (b) $\lambda = 0.01$ \\
-    \includegraphics[scale=0.35]{E_lambda_0.png}
-    \includegraphics[scale=0.35]{B_lambda_0.png}
-    \includegraphics[scale=0.35]{ue_lambda_0.png} \\
+    %\includegraphics[scale=0.35]{E_lambda_0.png}
+    %\includegraphics[scale=0.35]{B_lambda_0.png}
+    %\includegraphics[scale=0.35]{ue_lambda_0.png} \\
     (c) $\lambda = 0$
@@
     \centering
-    \includegraphics[scale=0.9]{norm_vs_nCell-T_1.eps}
+    %\includegraphics[scale=0.9]{norm_vs_nCell-T_1.eps}
     \caption{1-norms of quantities with respect to different mesh size: The results are computed for $\lambda = 1$ and $0.1$ at $t = 1$.}.
@@
 
-    \includegraphics[scale=0.27]{clip_E_T-1_lambda-1e-1_8-2-2.png}
-    \includegraphics[scale=0.27]{clip_E_T-1_lambda-1e-1_16-3-3.png}
-    \includegraphics[scale=0.27]{clip_E_T-1_lambda-1e-1_32-3-4.png}
-    \includegraphics[scale=0.27]{clip_B_T-1_lambda-1e-1_8-2-2.png}
-    \includegraphics[scale=0.27]{clip_B_T-1_lambda-1e-1_16-3-3.png}
-    \includegraphics[scale=0.27]{clip_B_T-1_lambda-1e-1_32-3-4.png}
-    \includegraphics[scale=0.27]{clip_ne_T-1_lambda-1e-1_8-2-2.png}
-    \includegraphics[scale=0.27]{clip_ne_T-1_lambda-1e-1_16-3-3.png}
-    \includegraphics[scale=0.27]{clip_ne_T-1_lambda-1e-1_32-3-4.png}
-    \includegraphics[scale=0.27]{clip_ni_T-1_lambda-1e-1_8-2-2.png}
-    \includegraphics[scale=0.27]{clip_ni_T-1_lambda-1e-1_16-3-3.png}
-    \includegraphics[scale=0.27]{clip_ni_T-1_lambda-1e-1_32-3-4.png}
+    %\includegraphics[scale=0.27]{clip_E_T-1_lambda-1e-1_8-2-2.png}
+    %\includegraphics[scale=0.27]{clip_E_T-1_lambda-1e-1_16-3-3.png}
+    %\includegraphics[scale=0.27]{clip_E_T-1_lambda-1e-1_32-3-4.png}
+    %\includegraphics[scale=0.27]{clip_B_T-1_lambda-1e-1_8-2-2.png}
+    %\includegraphics[scale=0.27]{clip_B_T-1_lambda-1e-1_16-3-3.png}
+    %\includegraphics[scale=0.27]{clip_B_T-1_lambda-1e-1_32-3-4.png}
+    %\includegraphics[scale=0.27]{clip_ne_T-1_lambda-1e-1_8-2-2.png}
+    %\includegraphics[scale=0.27]{clip_ne_T-1_lambda-1e-1_16-3-3.png}
+    %\includegraphics[scale=0.27]{clip_ne_T-1_lambda-1e-1_32-3-4.png}
+    %\includegraphics[scale=0.27]{clip_ni_T-1_lambda-1e-1_8-2-2.png}
+    %\includegraphics[scale=0.27]{clip_ni_T-1_lambda-1e-1_16-3-3.png}
+    %\includegraphics[scale=0.27]{clip_ni_T-1_lambda-1e-1_32-3-4.png}
     \caption{Quantities at the cross-section generated by meshes with different refinement level.
@@
 
-    \includegraphics[scale=0.27]{slice_E_T-1_lambda-0_8-2-2.png}
-    \includegraphics[scale=0.27]{slice_E_T-1_lambda-0_16-3-3.png}
-    \includegraphics[scale=0.27]{slice_E_T-1_lambda-0_32-3-4.png}
-    \includegraphics[scale=0.27]{slice_B_T-1_lambda-0_8-2-2.png}
-    \includegraphics[scale=0.27]{slice_B_T-1_lambda-0_16-3-3.png}
-    \includegraphics[scale=0.27]{slice_B_T-1_lambda-0_32-3-4.png}
-    \includegraphics[scale=0.27]{slice_ne_T-1_lambda-0_8-2-2.png}
-    \includegraphics[scale=0.27]{slice_ne_T-1_lambda-0_16-3-3.png}
-    \includegraphics[scale=0.27]{slice_ne_T-1_lambda-0_32-3-4.png}
-    \includegraphics[scale=0.27]{slice_ni_T-1_lambda-0_8-2-2.png}
-    \includegraphics[scale=0.27]{slice_ni_T-1_lambda-0_16-3-3.png}
-    \includegraphics[scale=0.27]{slice_ni_T-1_lambda-0_32-3-4.png}
+    %\includegraphics[scale=0.27]{slice_E_T-1_lambda-0_8-2-2.png}
+    %\includegraphics[scale=0.27]{slice_E_T-1_lambda-0_16-3-3.png}
+    %\includegraphics[scale=0.27]{slice_E_T-1_lambda-0_32-3-4.png}
+    %\includegraphics[scale=0.27]{slice_B_T-1_lambda-0_8-2-2.png}
+    %\includegraphics[scale=0.27]{slice_B_T-1_lambda-0_16-3-3.png}
+    %\includegraphics[scale=0.27]{slice_B_T-1_lambda-0_32-3-4.png}
+    %\includegraphics[scale=0.27]{slice_ne_T-1_lambda-0_8-2-2.png}
+    %\includegraphics[scale=0.27]{slice_ne_T-1_lambda-0_16-3-3.png}
+    %\includegraphics[scale=0.27]{slice_ne_T-1_lambda-0_32-3-4.png}
+    %\includegraphics[scale=0.27]{slice_ni_T-1_lambda-0_8-2-2.png}
+    %\includegraphics[scale=0.27]{slice_ni_T-1_lambda-0_16-3-3.png}
+    %\includegraphics[scale=0.27]{slice_ni_T-1_lambda-0_32-3-4.png}
     \caption{Quantities at the cross-section generated by meshes with different refinement level.
@@
     \centering
-    \includegraphics[scale=0.9]{origin-data_vs_time.eps}
+    %\includegraphics[scale=0.9]{origin-data_vs_time.eps}
     \caption{Time histories of quantities at the origin for different $\lambda$. The simulation is done on a mesh with 1920 primal cells with 8 layers along $z$-axis.}
@@
     \centering
-    \includegraphics{zaxis-data_vs_z-T_10.eps}
+    %\includegraphics{zaxis-data_vs_z-T_10.eps}
     \caption{Quantities along $z$-axis for different $\lambda$: The results are computed at $t = 10$ on a mesh with 1920 primal cells with 8 layers along $z$-axis.}.
@@
         \centering
-        \includegraphics[scale=0.4]{clip-ne-nue-T_10-lambda_1.png}
+        %\includegraphics[scale=0.4]{clip-ne-nue-T_10-lambda_1.png}
         \caption{$\lambda = 1$}
@@
         \centering
-        \includegraphics[scale=0.4]{clip-ne-nue-T_10-lambda_1e-1.png}
+        %\includegraphics[scale=0.4]{clip-ne-nue-T_10-lambda_1e-1.png}
         \caption{$\lambda = 0.1$}
@@
         \centering
-        \includegraphics[scale=0.4]{clip-ne-nue-T_10-lambda_1e-2.png}
+        %\includegraphics[scale=0.4]{clip-ne-nue-T_10-lambda_1e-2.png}
         \caption{$\lambda = 0.01$}
@@
         \centering
-        \includegraphics[scale=0.38]{clip-ne-nue-T_10-lambda_0.png}
+        %\includegraphics[scale=0.38]{clip-ne-nue-T_10-lambda_0.png}
         \caption{$\lambda = 0$}

### 2022-10-13 paper_version/main.tex
polish until BCs

@@
 \geometry{a4paper,scale=0.8}
-\usepackage{natbib}
-\bibliographystyle{apalike}
+\usepackage[square,numbers]{natbib}
+\bibliographystyle{abbrvnat}
 \usepackage{tikz}
@@
 
+\newtheorem*{remark}{Remark}
+
 \newcommand{\todo}[1]{\textcolor{blue}{\fbox{\textbf{TODO: #1}}}}
@@
 \title{APPM report - Draft}
-\author{T.W. Yu, R. Fuchs, R. Hiptmair}
+\author{T.W. Yu\footnote{SAM, ETH Z\"{u}rich}, R. Hiptmair\footnote{SAM, ETH Z\"{u}rich}, R. Fuchs\footnote{IET Institut für Energietechnik, OST}}
 
@@
 \maketitle
-
-\todobox{
-    \begin{itemize}
-        \item For the time being, the contents are just clipped from master thesis. They could be very chaotic.
-        \item The figures are not added yet.
-        \item For sure some parts need rewriting.
-    \end{itemize}
-}
 
@@
 Special care is necessary for the boundary conditions which must be valid in both regimes.
-Additionally, if the electromagnetic fields have to be modeled in an insulating region beyond the plasma domain, additional stabilization is necessary to accommodate Gauss's law.
+Additionally, if the electromagnetic fields have to be modelled in an insulating region beyond the plasma domain, additional stabilization is necessary to accommodate Gauss's law.
+
+\section{Introduction}
+We consider a hydrodynamic multi-species plasma model, which boils down to the Maxwell-Euler system.
+As in \cite{degond_2012}, our focus is an \emph{asymptotic-preserving} (AP) discretization in the quasi-neutral limit $\lambda_D \rightarrow 0$, where $\lambda_D$ is the rescaled Debye length, see Section \ref{sec:rescaling} for the underlying scaling arguments and \cite{degond_2012,degond_2017} for a discussion of the importance of the AP property in plasma codes.
+
+Our approach is inspired by \cite{degond_2012}, but goes beyond that work in various directions:
+\begin{itemize}
+    \item we supplement the Maxwell-Euler system by inter-species friction, see Section ?;
+    \item we extend the spatially 1D scheme to three spatial dimensions;
+    \item we propose an essential stabilization in non-conducting regions;
+    \item we introduce suitable boundary conditions for the electromagnetic fields at a spatial truncateion boundary.
+\end{itemize}
+
+We stay close to \cite{degond_2012} in terms of discretization in time by semi-implicit time-stepping and by restricting to a cylindrical geometry shown in Fig.
+\ref{fig:domain_geometry}.
+We would like to remark that the mesh-based numerical scheme proposed in this paper can in principle be adapted to geometric situations much more general than that of Fig.
+\ref{fig:domain_geometry}.
+However, one may then encounter subtle problems in defining proper mesh duality as we do in Section ?.
+Thus, for the sake of simplicity of presentation we forgo geometric generality.
+
+The content of this paper is organized as follows.
+In Section 2, we first give full details on the underlying equations of the Maxwell-Euler system and its rescaling procedure.
+Afterwards we introduce the ECE-type boundary conditions for our problem.
+A reformulation of the Maxwell equations in the insulating region is then presented.
+Section 3 is devoted to the discretization.
+\todo{outline}
+
+\begin{figure}
+    \centering
+    \begin{tikzpicture}
+    \coordinate (O1) at (0,0);
+    \draw[violet] (O1) circle (1) node[blue] {Electrode};
+    \fill[blue, opacity=0.2] (O1) circle (1);
+    \draw[very thick] (O1) circle (1.5);
+    \coordinate (O2) at (4.5,1);
+    \draw[violet] (O2) circle (1);
+    \node at (O2) {\textcolor{red}{Electrode}};
+    \node at (barycentric cs:O1=1,O2=1) {Plasma}; 
+    \fill[red, opacity=0.2] (O2) circle (1);
+    \coordinate (S1) at ([shift={(-0.196,0.98)}]O1);
+    \coordinate (S2) at ([shift={(-0.196,0.98)}]O2);
+    \coordinate (P1) at ([shift={(0.196,-0.98)}]O1);
+    \coordinate (P2) at ([shift={(0.196,-0.98)}]O2);
+    \draw[violet] (S1) -- (S2);
+    \draw[violet] (P1) -- (P2);
+    \coordinate (SS1) at ([shift={({-0.196*1.5},{0.98*1.5})}]O1);
+    \coordinate (SS2) at ([shift={({-0.196*1.5},{0.98*1.5})}]O2);
+    \coordinate (PP1) at ([shift={({0.196*1.5},{-0.98*1.5})}]O1);
+    \coordinate (PP2) at ([shift={({0.196*1.5},{-0.98*1.5})}]O2);
+    \draw[very thick] (SS1) -- (SS2);
+    \draw[very thick] (PP1) -- (PP2); 
+    \draw[black, very thick] (SS2) arc (101.31:180+101.31:1.5);
+    \draw[very thick] (PP2) arc (101.31-180:101.31:1.5);
+    \draw[-to] (barycentric cs:SS1=1,SS2=1,S1=1,S2=1) to[out=90,in=0] ([shift={(-0.5,0.5)}]barycentric cs:SS1=1,SS2=1,S1=1,S2=1) node[left, gray] {Insulator};
+    \begin{scope}[shift={(5.5,-1.4)}]
+    \draw[blue, -to] (0,0) -- (0.65,0.12) node[right]{\small $z$};
+    \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
+    \draw[blue, -to] (0,0) -- (0.7,0) node[below]{\small $y$};
+    \end{scope}
+    \end{tikzpicture}
+\caption{The domain geometry}
+\label{fig:domain_geometry}
+\end{figure}
 
 \section{Plasma model}
+\begin{comment}
 Under moderate assumptions, plasmas, which are gases composed of charged particles (and possibly neutral particles), can be treated as fluid and described by hydrodynamic equations.
@@
 
-\todo{A bit more on the physical background}.
-
-After rescalling all the variables with respect to the prescribed reference units, the Debye length $\lambda_D$, characterizing the charge screening ability of the plasma, would pop up and its zero limit, which is what we called \emph{quasineutral limit}, is of great interest, since the limit model largely simplifies the system and in many cases the accuracy of the assumption is satisfactory enough.
+After rescalling all the variables with respect to the prescribed reference units, the Debye length $\lambda_D$, characterizing the charge screening ability of the plasma, would pop up and its zero limit, which is what we called \emph{quasi-neutral limit}, is of great interest, since the limit model largely simplifies the system and in many cases the accuracy of the assumption is satisfactory enough.
 
 In this section, the multi-species Maxwell-Euler equations with collision term is introduced first, followed by detailed rescalling procedure.
-The quasi-neutral model will be make clear by letting the rescalled Debye length $\lambda$ go to zero.
+The quasi-neutral model will be make clear by letting the rescaled Debye length $\lambda$ go to zero.
 Afterwards, a set of boundary conditions are presented and its validity to both non-limit and limit model is discussed.
 Finally, we would like to present a reformulation of the system which would be crucial to the stability of the numerical scheme.
+\end{comment}
 
@@
 \subsection{The Maxwell-Euler System}
-The Maxwell system is described by Maxwell's equations whose expression in SI units read
+Under moderate assumptions, plasmas, which are gases composed of charged particles (and possibly neutral particles), can be treated as fluids governed by hydrodynamic equations.
+The Maxwell equations take charge of their interaction with electromagnetic fields.
+For more details on the fluid model of plasma, see \cite{chen2016, remi_2014}.
+
+The Maxwell's equations in SI units read
+\begin{subequations}
 \begin{align}
@@
 \end{align}
+\end{subequations}
 where the involved quantities are magnetic flux density $\mathbf{B}$, electric field intensity $\mathbf{E}$, electric induction $\mathbf{D}$, magnetic field intensity $\mathbf{H}$, electric current density $\mathbf{J}$ and electric charge density $\rho$.
 These equations are known as Faraday's law (\ref{equ:maxwell_faraday}), Amp\`{e}re's law (\ref{equ:maxwell_ampere}), Gauss's law for magnetism (\ref{equ:maxwell_gauss_B}) and Gauss's law for electric field (\ref{equ:maxwell_gauss_D}).
-For simplicity, we only consider isotropic and homogeneous mediums in vacuum.
+For simplicity, we only consider isotropic and homogeneous media in vacuum.
 We consider the linear constitutive relations
@@
 Besides, on taking the divergence of equations (\ref{equ:maxwell_faraday}) and (\ref{equ:maxwell_ampere}) together with the relation (\ref{equ:charge_continuity}), it is possible to verify that Gauss's laws (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) are consequences of (\ref{equ:maxwell_faraday}) and (\ref{equ:maxwell_ampere}) provided that (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) are satisfied at the initial time.
-In other words, Gauss's laws (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) serve as initial conditions.
-Faraday's law (\ref{equ:maxwell_faraday}) and Amp\`{e}re's law (\ref{equ:maxwell_ampere}) suffice.
-
-In the Euler system, the motions of gas particles are accounted for through the \emph{Euler equations}.
-Specifically, we equip each species with one set of (compressible) Euler equations, taking into account the effect of electromagnetic fields as well as other processes like collisions and recombination.
-The generic expressions read
+In other words, Gauss's laws (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) can be thought of as initial conditions.
+
+Each species in plasmas are treated as a compressible flow and assocated to one set of Euler equations that includes electromagnetic forces as well as other processes, e.g.
+collisions and recombination.
+The generic expressions are
 \begin{align} \label{equ:euler_}
@@
 The left-hand side of the equations describes the convection of plasma fluids.
-Note that the heat conduction is omitted in the energy equation.
 The first term at the right-hand side denotes Lorentz force in the momentum equation and Joule heating in the energy equation.
-$\Gamma_*, \mathbf{R}_*, Q_*$ are generic terms that include effects of inter-species collision, ionization, recombination, etc.
-
-For the sake of simplicity, we would only consider ion-electron collision in this work.
-Under moderate assumptions, such collisions can be well modelled by friction terms, and we simply present the expressions without derivation (see \citep[][sec.
+$\Gamma_*, \mathbf{R}_*, Q_*$ are generic terms due to effects of inter-species collision, ionization, recombination, etc.
+
+For the sake of simplicity for presentation, we only consider ion-electron collision in this work, but extension to more species is straightforward.
+Under moderate assumptions, such collisions can be well modelled by frictions, and we simply present the expressions without derivation (see \citep[][sec.
 5.6.2]{chen2016}):
@@
 ln$\Lambda$ is called the \emph{Coulomb logarithm}, which typically takes a numerical value of order 10–20 .
-Because of the conservation of momentum, the collision term experienced by ions $\mathbf{R}_{i}^{\text{coll}}$ is nothing but the negation of $\mathbf{R}_{e}^{\text{coll}}$.
-For full details about the ionization and recombination, readers are referred to \cite{fuchs_2021}.
+Because of the conservation of momentum, the collision term for ions $\mathbf{R}_{i}^{\text{coll}}$ is nothing but the negation of $\mathbf{R}_{e}^{\text{coll}}$.
+In this work, the other effects, e.g.
+ionization and recombination, are not considered.
+For full details about the modeling of these physical processes, readers are referred to \cite{fuchs_2021}.
 
 Combination of the two sets of equations (\ref{equ:maxwell_faraday}) to (\ref{equ:maxwell_gauss_D}) and (\ref{equ:euler_}) leads to the governing equations for a multi-species plasma model.
-The coupling of the two subsystems takes effect through the following relations that connect the fluid and electromagnetic quantities
+The coupling of the two subsystems is due to the following relations that connect the fluid and electromagnetic quantities
 \begin{equation*}
@@
 
-\subsection{Rescalling}
-In the rescalling, the variables in the equations are taken as the ratio of their original quantities and reference units, which transforms the system into a dimensionless form.
-The magnitudes of the dimensionless numbers are indications of the magnitude of corresponding terms.
-In this part, the rescalling procedure mostly sticks to that of \cite{degond_2017}.
+\subsection{Rescaling} \label{sec:rescaling}
+In the rescaling, the variables in the equations are taken as the ratio of their original quantities and reference units, which transforms the system into dimensionless form.
+In this part, the rescaling procedure mostly follows that of \cite{degond_2017}.
 
@@
 \begin{align*} 
-    \xi &:= \frac{\overline{v}}{c} \text{ the velocity of interest to the light speed}, &\\
-    \zeta &:= \frac{\overline{u}}{\overline{v}} \text{ the plasma velocity to the speed of interest}, &\\
-    M &:= \frac{\overline{u}}{v_{th,i}} \text{ the plasma drift velocity to the thermal speed of ions, where } v_{th,i} := \left(\frac{k_B \overline{T}}{m_i}\right)^{1/2}, &\\
-    \eta &:= \frac{e\overline{E}\overline{x}}{m_i\overline{u}^2} \text{ the electric energy to the kinetic energy of ions}, &\\
-    \beta &:= \frac{\overline{v}\overline{B}}{\overline{E}} \text{ the induced electric field to the total electric field}, &\\
+    \xi &:= \frac{\overline{v}}{c} \text{ the velocity of interest \emph{w.r.t.}\footnotemark[1] the light speed}, &\\
+    \zeta &:= \frac{\overline{u}}{\overline{v}} \text{ the plasma velocity \emph{w.r.t.} the speed of interest}, &\\
+    M &:= \frac{\overline{u}}{v_{th,i}} \text{ the plasma drift velocity \emph{w.r.t.} the thermal speed of ions, where } v_{th,i} := \left(\frac{k_B \overline{T}}{m_i}\right)^{1/2}, &\\
+    \eta &:= \frac{e\overline{E}\overline{x}}{m_i\overline{u}^2} \text{ the electric energy \emph{w.r.t.} the kinetic energy of ions}, &\\
+    \beta &:= \frac{\overline{v}\overline{B}}{\overline{E}} \text{ the induced electric field \emph{w.r.t.} the total electric field}, &\\
     \lambda &:= \frac{\lambda_D}{\overline{x}} \text{ the dimensionless Debye length, where }\lambda_D := \left(\frac{\varepsilon_0k_B\overline{T}}{e^2\overline{n}}\right)^{1/2}, &\\
-    \varepsilon_*^2 &:= \frac{m_*}{m_i} \text{ the species mass ratio to the ion mass},\ \  * \in \{i,e,n,\cdots\}, &\\
-    g &:= \frac{1}{\overline{n}\lambda_D^3} \text{ the plasma parameter\footnotemark}.&
+    \varepsilon_*^2 &:= \frac{m_*}{m_i} \text{ the species mass \emph{w.r.t.} the ion mass},\ \  * \in \{i,e,n,\cdots\}, &\\
+    g &:= \frac{1}{\overline{n}\lambda_D^3} \text{ the plasma parameter\footnotemark[2]}.&
 \end{align*}
-\footnotetext{It is basically the reciprocal of the number of particles per Debye sphere, see \cite[][sec. 1.1]{gibbon2020}. Classical plasma theory assumes $g \ll 1$.}
+\footnotetext[1]{Abbreviation of \emph{with respect to}.}
+\footnotetext[2]{It is basically the reciprocal of the number of particles per Debye sphere, see \cite[][sec. 1.1]{gibbon2020}. Classical plasma theory assumes $g \ll 1$.}
 
@@
 The rescaled Euler-Maxwell system reads
+\begin{subequations}
 \begin{align}
@@
 \end{align}
+\end{subequations}
 where the equation of state becomes $e_* = \frac{1}{2}|\mathbf{u_*}|^2 + M^{-2}\frac{p_*}{\epsilon^2_* n_* (\gamma - 1)}$ and $h_* = e_* + M^{-2}\frac{p_*}{\epsilon^2_* n_*}$.
@@
 The $\lambda \rightarrow 0$ limit implies that the collisions happen in the atomic length scale, in which quantum-mechanical effects must be taken into effect \citep{frank_1972}.
-Therefore, for the sake of simplicity, we decide to assume $g \sim \lambda$ and keep the prefactor of collision term constant $\alpha^{\text{coll}}$ throughout the simulation\footnote{The reasonableness of this assumption is questionable.}.
+Therefore, for the sake of simplicity, we eliminate the perturbation parameter in the friction term by assuming $g \sim \lambda$ and keep the prefactor of collision term constant $\alpha^{\text{coll}}$ throughout the simulation.
+
+\begin{remark}
+    It is also of research interest when there is an asymptotic parameter at the denominator of the friction term.
+Such problem is called relaxation limit, see \cite{peng_2011, wasiolek_2016, Li_2021, Chen_2000}.
+\end{remark}
 
@@
 Under such assumptions on these dimensionless parameters, the rescaled Euler-Maxwell system is simplified into a parametrized system with the dimensionless Debye length $\lambda$ being the asymptotic parameter
+\begin{subequations}
 \begin{align}
@@
 \end{align}
+\end{subequations}
 with the equation of state $e_* = \frac{1}{2}|\mathbf{u_*}|^2 + \frac{p_*}{\varepsilon^2_* n_* (\gamma - 1)}$ and $h_* = e_* + \frac{p_*}{\varepsilon^2_* n_*}$.
@@
 \subsection{Quasi-neutral limit} \label{sec:quasi-neutral_limit}
-The Debye length $\lambda_D$ (see its definition at the proceeding section) is an characteristic length over which any net charge is screened due to the thermal diffusion of the particles.
-In many situations, it has a rather low value.\todo{Examples and typical values}.
-That justifies the quasi-neutral assumptions of vanishing $\lambda_D$ with respect to the interested length scale.
-Under this limit, the plasma keeps locally neutral in net charge, namely $\rho = \sum_* q_*n_* = 0$.
-Such behavior is explained through the rescaled Euler-Maxwell system (\ref{equ:maxwell_faraday_rescaled}) to (\ref{equ:euler_rescaled}).
-By formally taking dimensionless Debye length $\lambda$ to zero\footnote{The convergence of the solutions as $\lambda$ tending to zero is discussed in \cite[][chap.
-2]{remi_2014}}, the Maxwell system becomes
+The Debye length $\lambda_D$ (see its definition at the preceding section) is an characteristic length over which local concentrations of charge are shielded out.
+For the underlying physics, see \cite[Sec.
+1.4]{chen2016}.
+In many situations, it has a rather low value compared to the interested length scale: the typical $\lambda_D$ for gas discharge and Tokamak is $10^{-4}$ m; for interstellar medium, the magnitude is about $1$ m \cite[ch.
+20]{Blandford_2013}.
+That justifies the quasi-neutrality assumption that the plasma is locally neutral, namely $\rho = \sum_* q_*n_* = 0$.
+The limit model is obtained by formally taking the rescaled Debye length $\lambda$ to zero:
+\vspace{-\baselineskip}
+\begin{center}
+    \begin{minipage}{0.3\textwidth}
+\begin{subequations}
+\begin{align*}
+    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0,\\ 
+    \lambda^2 \partial_t \mathbf{E} - \nabla \times \mathbf{B} &= - \mathbf{J}, \\
+    \nabla \cdot \mathbf{B} &= 0, \\
+    \lambda^2 \nabla \cdot \mathbf{E} &= \rho.
+\end{align*}
+\end{subequations}
+
+\end{minipage}
+$\xrightarrow[]{\lambda \rightarrow 0}$
+\begin{minipage}{0.3\textwidth}
+\begin{subequations}
 \begin{align}
@@
 \end{align}
-One can notice that the quasi-neutral condition (\ref{equ:maxwell_gauss_D_limit}) is the consequence of taking $\lambda = 0$ in Gauss's law for electric field (\ref{equ:maxwell_gauss_D_rescaled}).
-Like the non-neutral case, Gauss's laws (\ref{equ:maxwell_gauss_B_limit}) (\ref{equ:maxwell_gauss_D_limit}) are the consequence of (\ref{equ:maxwell_faraday_limit}) (\ref{equ:maxwell_ampere_limit}) provided (\ref{equ:maxwell_gauss_B_limit}) (\ref{equ:maxwell_gauss_D_limit}) are satisfied at the initial time.
+\end{subequations}
+\end{minipage}
+\end{center}
+The quasi-neutral condition (\ref{equ:maxwell_gauss_D_limit}) is the consequence of taking $\lambda = 0$ in Gauss's law for electric field (\ref{equ:maxwell_gauss_D_rescaled}).
+Like the non-neutral case, Gauss's laws (\ref{equ:maxwell_gauss_B_limit}) (\ref{equ:maxwell_gauss_D_limit}) are the consequence of (\ref{equ:maxwell_faraday_limit}) (\ref{equ:maxwell_ampere_limit}) provided (\ref{equ:maxwell_gauss_B_limit}) (\ref{equ:maxwell_gauss_D_limit}) are satisfied at initial time.
 
@@
 
-We would like to point out the proceeding argument about the derivation of limit model is merely formal and heuristic without mentioning the proof and to which sense the convergence holds.
-Deep mathematical tools from the perturbation theory is needed to rigorously prove the convergence of the limiting sequence.
+\begin{remark}
+    The preceeding formal limit argument is rather heuristic.
+Deep mathematical tools from perturbation theory is needed to rigorously prove the convergence of the limiting sequence.
 This topic is beyond the scope of this paper and thus omitted.
-Readers are referred to \cite{remi_2014} for the quasi-neutral limit of the Maxwell-Euler system, and \cite{mark_1995} for the general theory.
+Readers are referred to \cite[ch.
+2]{remi_2014} \cite{Peng_2008} for the quasi-neutral limit of the Maxwell-Euler system, and \cite{mark_1995, Eckhaus_1980} for the general theory.
+\end{remark}
 
@@
 We consider a simply connected domain $\Omega$ that is decomposed into two sub-domains $\Omega_P$ and $\Omega_I$ representing plasma domain and insulating domain respectively.
-We use the notation $\Gamma_C := \partial\Omega \cap \partial\Omega_P$, denoting the contact boundary, and $\Gamma_I := \partial\Omega \cap \partial\Omega_I$ for the insulating boundary.
+We use the notation $\Gamma_C := \partial\Omega \cap \partial\Omega_P$, denoting the contact boundary, and $\Gamma_I := \partial\Omega \cap \partial\Omega_I$ for the insulating boundary which an artificial cut-off boundary.
 The interface between the two domains is denoted by $\Gamma_W = \partial\Gamma_I \cap \partial\Gamma_P$.
-This setting is visualized in Fig.
-.
-
-The plasma fills $\Omega_I$ where the Euler system lies and thus the boundary of plasmas lies on $\partial\Omega_P$.
+A geometric arrangement corresponding to his setting is visualized in Fig.
+\ref{fig:domain_sketch}.
+
+The plasma fills $\Omega_P$ where the Euler system is defined and the boundary of plasmas lies on $\partial\Omega_P$.
 We consider the physical scenario where plasmas are confined with the solid insulator.
 Therefore, the interface $\Gamma_W$ is treated as reflective walls where fluid particles are bounced back while keeping the tangential velocity and energy unchanged.
-The contact boundary $\Gamma_C$ is where the plasma and energy flow across, modelled by, for the sake of simplicity, open boundaries, namely they are free to flow through.
-\todo{Discussion the more realistic electrode model}
+The contact boundary $\Gamma_C$ is where the plasma and energy flow across, modelled by open boundaries in the sense that they are free to flow through, namely, ions and electrons are emitted and absorbed by the electron.
+
+\begin{remark}
+    The treatment of electrodes as open boundary is a rather simplified approach. \todo{a realistic BC for electrodes.}
+\end{remark}
 
@@
 The insulating boundary blocks the energy interchange and therefore only admits zero electric and magnetic flux, in the sense that $\text{curl}\mathbf{E}\cdot \mathbf{n} = 0$ and $\text{curl}\mathbf{H}\cdot \mathbf{n} = 0$ where $\mathbf{n}$ is the outer normal vector.
+\todo{A few works on ECE BC?}
 \begin{figure}
@@
     \coordinate (O1) at (0,0);
-    \draw[very thick] (O1) circle (1) node[blue] {Electrode};
+    \draw[violet] (O1) circle (1) node[blue] {Electrode};
     \fill[blue, opacity=0.2] (O1) circle (1);
@@
     \coordinate (O2) at (4.5,1);
-    \draw[gray] (O2) circle (1);
+    \draw[violet] (O2) circle (1);
     \node at (O2) {\textcolor{red}{Electrode}};
@@
     \coordinate (P2) at ([shift={(0.196,-0.98)}]O2);
-    \draw[gray] (S1) -- (S2);
-    \draw[gray] (P1) -- (P2);
+    \draw[violet] (S1) -- (S2);
+    \draw[violet] (P1) -- (P2);
     \coordinate (SS1) at ([shift={({-0.196*1.5},{0.98*1.5})}]O1);
@@
     \draw[very thick] (PP1) -- (PP2); 
-    \draw[gray] (SS2) arc (101.31:180+101.31:1.5);
+    \draw[black, very thick] (SS2) arc (101.31:180+101.31:1.5);
     \draw[very thick] (PP2) arc (101.31-180:101.31:1.5);
@@
         \coordinate (B4) at (6,-1.5);
-        \draw[gray] (A2) -- node[above]{\textbf{Insulator $\Omega_I$}} node[black, below]{$\Gamma_W$} (B2);
-        \draw[gray] (A3) -- node[below]{\textbf{Insulator $\Omega_I$}} node[black, above]{$\Gamma_W$} (B3);
+        \draw[violet] (A2) -- node[above]{\color{gray}Insulating domain $\Omega_I$} node[black, below]{\textcolor{violet}{$\Gamma_W$}} (B2);
+        \draw[violet] (A3) -- node[below]{\color{gray}Insulating domain $\Omega_I$} node[black, above]{\textcolor{violet}{$\Gamma_W$}} (B3);
         \draw[very thick] (A2) -- (A1) -- node[above]{$\Gamma_I$}  (B1) -- (B2);
@@
         \draw[very thick, dashed, red]  (B2) -- node[right] {$\Gamma_C^2$}  (B3);
-        \node at (3,0) {\textbf{Plasma $\Omega_P$}};
+        \node at (3,0) {Plasma domain $\Omega_P$};
         \begin{scope}[shift={(6.5,-1.6)}]
@@
 \caption{Sketch of the domain. The right figure shows the cross section on the $x$-$z$ plane.}
+\label{fig:domain_sketch}
 \end{figure}
@@
 \vspace{10pt}
+
+\begin{remark}
     A small remark goes to the validity of assignment of electric potentials on $\Gamma_c^i$.
 Since the surface curl $\text{curl}_\gamma\mathbf{E} = \text{curl} \mathbf{E} \cdot \mathbf{n} = 0$, there exists a surface potential $\varphi$ such that the surface gradient $\nabla_\Gamma \varphi = \gamma_\tau \mathbf{E}$ where $\gamma_\tau $ is the tangential trace operator.
+However, for a geometric setting with non-trivial geometry, one needs to consider cohomology vector fields\cite{Hiptmair_2021}.
+\end{remark}
 
@@
 \subsection{Asymptotic-Preserving schemes}
-As is mentioned in the proceeding chapter, the zero-Debye-length limit poses a singularly perturbed problem in the sense that the Maxwell-Euler equations changes its type from a hyperbolic to hyperbolic-elliptic one.
+As is mentioned in the preceeding chapter, the zero-Debye-length limit poses a singularly perturbed problem in the sense that the Maxwell-Euler equations changes its type from a hyperbolic to hyperbolic-elliptic one.
 To simulate a plasma, one usually first identifies which regime it lies in and designs the scheme according to its type.
@@
 In the following sections, we first briefly discuss the 1D scheme for the Maxwell-Euler system devised by \cite{degond_2012} on which our work us built.
-this section also serves as a preliminary case study such that readers can better understand the 3D scheme.
+This section also serves as a preliminary case study such that readers can better understand the 3D scheme.
 

### 2022-10-14 paper_version/main.tex
Polish until discretization

@@
 \usepackage{subcaption}
+\usepackage{authblk}
 
@@
 \title{APPM report - Draft}
-\author{T.W. Yu\footnote{SAM, ETH Z\"{u}rich}, R. Hiptmair\footnote{SAM, ETH Z\"{u}rich}, R. Fuchs\footnote{IET Institut für Energietechnik, OST}}
-
+\author[1]{R. Hiptmair}
+\author[1]{T.W. Yu}
+\author[2]{R. Fuchs}
+\affil[1]{Seminar for Applied Mathematics , ETH Z\"{u}rich}
+\affil[2]{IET Institut für Energietechnik, OST}
+\date{}
 \begin{document}
@@
 Thus, for the sake of simplicity of presentation we forgo geometric generality.
+
+The quasi-neutral limit of the Maxwell system leads to a singularly perturbed problem in the sense that the system changes its type from hyperbolic to a mixture of hyperbolic, parabolic and elliptic, which poses challenge for simulations over different regimes.
+Such phenomena occur in many problems, e.g.
+vanishing viscosity in the Navier-Stokes equations\cite{Kato_1984}, zero-relaxation-limit of kinetic equations\cite{jin_2010} and zero-Mach-limit of compressible flows\cite{degond_2007, haack_2010}.
+Asymptotic-preserving schemes are the ones that perform uniformly well in such asymptotic limit.
+To briefly illustrate the concept, see the commutative diagram Fig.
+\ref{fig:commutative_diagram_ap} in \cite{jin_1999}.
+The parametrized problem $P^\lambda$, which converges to its limit $P^0$ as the perturbed parameter $\lambda \rightarrow 0$, is discretized by the scheme $P^\lambda_h$ where $h$ denotes some discretization parameter, e.g.
+mesh size.
+The AP property requires the uniform convergence of $P^\lambda_h$ to the $P^\lambda$ as $\lambda\rightarrow0$.
+In the other word, an AP scheme $P^\lambda_h$ makes the diagram Fig.
+\ref{fig:commutative_diagram_ap} commutative.
+For more details about AP schemes, see \cite{jin_2010, degond_2017} for comprehensive reviews.
+
+\begin{figure}
+    \centering
+    \begin{tikzpicture}
+    \node (nw) {\Large $P^\lambda_h$};
+    \node (ne) [right=3cm of nw]{\Large $P^\lambda$};
+    \node (sw) [below=of nw]{\Large $P^0_h$};
+    \node (se) [right=3cm of sw]{\Large $P^0$};
+    \draw[->] (nw.east)  -- node [above,midway] {$h\rightarrow0$} (ne.west) ;
+    \draw[->] (nw.east)  --  (ne.west) ;
+    \draw[->] (nw.south) -- node [left,midway] {$\lambda\rightarrow0$} (sw.north);
+    \draw[->] (nw.south) -- node {} (sw.north);
+    \draw[->] (sw.east)  -- node [above,midway] {$h\rightarrow0$}(se.west);
+    \draw[->] (ne.south) -- node [left,midway] {$\lambda\rightarrow0$} (se.north);
+    \end{tikzpicture}
+    \caption{Commuting diagram of AP schemes}
+    \label{fig:commutative_diagram_ap}
+\end{figure}
 
@@
     \beta \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday_rescalling} \\ 
-    \lambda^2 \partial_t \mathbf{E} - \frac{\beta \lambda^2}{\xi^2}\nabla \times \mathbf{B} &= - \frac{\zeta}{\eta M^2}\mathbf{J}, \label{equ:maxwell_ampere_rescalling} \\
+    \lambda^2 \partial_t \mathbf{D} - \frac{\beta \lambda^2}{\xi^2}\nabla \times \mathbf{H} &= - \frac{\zeta}{\eta M^2}\mathbf{J}, \label{equ:maxwell_ampere_rescalling} \\
     \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B_rescalling}\\
-    \lambda^2 \eta M^2 \nabla \cdot \mathbf{E} &= \rho, \label{equ:maxwell_gauss_D_rescalling} \\
+    \lambda^2 \eta M^2 \nabla \cdot \mathbf{D} &= \rho, \label{equ:maxwell_gauss_D_rescalling} \\
     \partial_t
@@
     \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday_rescaled} \\ 
-    \lambda^2 \partial_t \mathbf{E} - \nabla \times \mathbf{B} &= - \mathbf{J}, \label{equ:maxwell_ampere_rescaled} \\
+    \lambda^2 \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= - \mathbf{J}, \label{equ:maxwell_ampere_rescaled} \\
     \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B_rescaled}\\
-    \lambda^2 \nabla \cdot \mathbf{E} &= \rho, \label{equ:maxwell_gauss_D_rescaled} \\
+    \lambda^2 \nabla \cdot \mathbf{D} &= \rho, \label{equ:maxwell_gauss_D_rescaled} \\
     \partial_t
@@
     \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0,\\ 
-    \lambda^2 \partial_t \mathbf{E} - \nabla \times \mathbf{B} &= - \mathbf{J}, \\
+    \lambda^2 \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= - \mathbf{J}, \\
     \nabla \cdot \mathbf{B} &= 0, \\
-    \lambda^2 \nabla \cdot \mathbf{E} &= \rho.
+    \lambda^2 \nabla \cdot \mathbf{D} &= \rho.
 \end{align*}
@@
     \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday_limit} \\ 
-    - \nabla \times \mathbf{B} &= - \mathbf{J}, \label{equ:maxwell_ampere_limit} \\
+    - \nabla \times \mathbf{H} &= - \mathbf{J}, \label{equ:maxwell_ampere_limit} \\
     \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B_limit}\\
@@
 Since the surface curl $\text{curl}_\gamma\mathbf{E} = \text{curl} \mathbf{E} \cdot \mathbf{n} = 0$, there exists a surface potential $\varphi$ such that the surface gradient $\nabla_\Gamma \varphi = \gamma_\tau \mathbf{E}$ where $\gamma_\tau $ is the tangential trace operator.
-However, for a geometric setting with non-trivial geometry, one needs to consider cohomology vector fields\cite{Hiptmair_2021}.
+However, for a geometric setting with non-trivial geometry, one needs to consider co-homology vector fields\cite{Hiptmair_2021}.
 \end{remark}
@@
 \subsection{Reformulation}
-In the insulating domain, the Euler system is not defined there and no charges or currents are present. Consequently, the Maxwell system in $\Omega_I$ is described by    
+In the insulating domain $\Omega_I$ (see Fig.
+\ref{fig:sketch_domain}), the Euler system is not defined there due to the absence of plasmas.
+Consequently, the Maxwell system in $\Omega_I$ is described by
+\begin{subequations}
 \begin{align}
@@
 \end{align}
-
-In non-neutral regime, namely $\lambda = \mathcal{O}(1)$, the Maxwell system in $\Omega_I$ is well-posed and Gauss's laws (\ref{equ:gauss_B_ins}) (\ref{equ:gauss_D_ins}) are redundant as long as they are satisfied at initial moment.
+\end{subequations}
+
+In non-neutral regime where $\lambda = \mathcal{O}(1)$, the Maxwell system in $\Omega_I$ is well-posed and Gauss's laws (\ref{equ:gauss_B_ins}) (\ref{equ:gauss_D_ins}) are redundant as long as they are satisfied at initial moment.
 Nonetheless, as the system approaches the quasi-neutral limit as $\lambda \rightarrow 0$, Gauss's law for $\mathbf{D}$-field (\ref{equ:gauss_D_ins}) becomes degenerate.
@@
 To see this issue from another perspective, we observe the limit Maxwell system in $\Omega_I$
+\begin{subequations}
 \begin{align}
@@
 \end{align}
+\end{subequations}
+
 Again, Gauss's law for $\mathbf{B}$-field (\ref{equ:gauss_B_ins_limit}) is redundant while Gauss's law for $\mathbf{D}$-field (\ref{equ:gaus_D_ins_limit}) is no longer the consequence of the Amper\`{e}'s law and essential for the well-posedness of the problem \citep{ana_2010}.
@@
 We propose the following reformulation as a remedy, which introduces a Lagrange multiplier $p$ and removes the $\lambda^2$ prefactor in Gauss's law for $\mathbf{D}$-field:
+\begin{subequations}
 \begin{align}
@@
 \end{align}
+\end{subequations}
+
 Supplemented with the boundary condition $p = 0$ on $\partial\Omega_I$, one can check that (\ref{equ:faraday_ins_reform}) to (\ref{equ:gauss_D_ins_reform}) are equivalent to the original formulation (\ref{equ:faraday_ins})-(\ref{equ:gauss_D_ins}) by verifying that $p = 0$ in $\Omega_I$.
@@
 
+We would like to point out that this reformulation is not needed in the plasma domain $\Omega_P$ since the Maxwell system is uniformly well-posed for $\lambda \in [0,1]$ thanks to the existence of electric current and its dependence on the $\mathbf{E}$-field.
+
 \section{Discretization}
 
-\subsection{Asymptotic-Preserving schemes}
-As is mentioned in the preceeding chapter, the zero-Debye-length limit poses a singularly perturbed problem in the sense that the Maxwell-Euler equations changes its type from a hyperbolic to hyperbolic-elliptic one.
-To simulate a plasma, one usually first identifies which regime it lies in and designs the scheme according to its type.
-Nonetheless, there exist cases that covers both regimes and cannot be approximated by either of them.
-Due to the difference on their mathematical characters, naively applying classical schemes for $\lambda = \mathcal{O}(1)$ to problems with $\lambda \rightarrow 0$ would fail and vice versa.
-\emph{Asymptotic-preserving} (AP) schemes are such a class of schemes that provide a unified approach for both limit and non-limit problems.
-
-To illustrate the general concept of AP schemes, we quote the celebrated commutative diagram Fig.
-\ref{fig:commutative_diagram_ap} in \cite{jin_1999} which sketches the property that an AP scheme should possess.
-We consider a parametrized problem $P^\lambda$ that converges to its limit $P^0$ as the perturbed parameter $\lambda \rightarrow 0$.
-To discretize $P^\lambda$, the scheme $P^\lambda_h$ is constructed whose numerical results depend on some discretization parameter $h$, e.g.
-mesh size.
-Beside the convergence of the scheme $P^\lambda_h$ to its analytic solution $P^\lambda$ as $h\rightarrow0$, the AP property additionally requires that the convergence of $P^\lambda_h$ to the limit discrete model $P^0_h$ as $\lambda\rightarrow0$.
-Such a limit scheme $P^0_h$ should in turn converge to the continuous solution $P^0$ as $h \rightarrow 0$.
-In short, an AP scheme $P^\lambda_h$ makes the diagram Fig.
-\ref{fig:commutative_diagram_ap} commutative.
-
-The concept of AP schemes can be traced back to \cite{jin_1995} in which the authors approximate a conservation law by a hyperbolic system with relaxation, and manage to construct a scheme that is stable for an arbitrarily small relaxation parameter.
-The term ``asymptotic-preserving" was formally introduced in \cite{jin_1999} for handling the diffusive regime of kinetic models.
-This concept stemmed from and remains very active in kinetic models with stiff relaxations, see \cite{jin_2010} and the references therein.
-Nonetheless, considerable effort has been put into developing AP schemes for many other problems that admit asymptotic behavior.
-For instance, in fluid dynamics, the so-called \emph{all-speed} schemes are advantageous when dealing with both compressible and incompressible regimes simultaneously.
-\cite{degond_2007, haack_2010} devise all-speed schemes for the isentropic Euler equations through fast-slow decomposition of velocity fields.
-Concerning plasma physics, a number of papers are available dealing with the quasi-neutral limit of the Euler-Poisson (or Euler-Maxwell) system \citep{crispel_2005, degond_2008, degond_2011, degond_2012} and Vlasov-Poisson (or Vlasov-Maxwell) system \citep{degond_2017, degond2017b, zhu_2017}.
-Besides, \cite{caflisch_1997, berthon2011} concern AP schemes for generic hyperbolic systems with relaxation source terms.
-For a comprehensive review on AP schemes, readers are referred to \cite{jin_2010} for kinetic and hyperbolic equations, and \cite{degond_2017} for multiscale plasma simulations.
-
+\begin{comment}
 To devise an AP scheme, the dependence of the stability constraints of $h$ on $\lambda$ has to be removed.
@@
 This section also serves as a preliminary case study such that readers can better understand the 3D scheme.
-
-\begin{figure}
-    \centering
-    \begin{tikzpicture}
-    \node (nw) {\Large $P^\lambda_h$};
-    \node (ne) [right=3cm of nw]{\Large $P^\lambda$};
-    \node (sw) [below=of nw]{\Large $P^0_h$};
-    \node (se) [right=3cm of sw]{\Large $P^0$};
-    \draw[->] (nw.east)  -- node [above,midway] {$h\rightarrow0$} (ne.west) ;
-    \draw[->] (nw.east)  --  (ne.west) ;
-    \draw[->] (nw.south) -- node [left,midway] {$\lambda\rightarrow0$} (sw.north);
-    \draw[->] (nw.south) -- node {} (sw.north);
-    \draw[->] (sw.east)  -- node [above,midway] {$h\rightarrow0$}(se.west);
-    \draw[->] (ne.south) -- node [left,midway] {$\lambda\rightarrow0$} (se.north);
-    \end{tikzpicture}
-    \caption{Commuting diagram of AP schemes}
-    \label{fig:commutative_diagram_ap}
-\end{figure}
+\end{comment}
 

### 2022-10-21 paper_version/main.tex
Polish spatial semi-discretization

@@
 \usepackage{tikz}
+\usepackage{tkz-euclide}
 \usetikzlibrary{positioning, decorations.markings, arrows, intersections}
@@
 \usepackage{tcolorbox}
-\usepackage{subcaption}
+\usepackage{caption, subcaption}
 \usepackage{authblk}
@@
 The quasi-neutral limit of the Maxwell system leads to a singularly perturbed problem in the sense that the system changes its type from hyperbolic to a mixture of hyperbolic, parabolic and elliptic, which poses challenge for simulations over different regimes.
-Such phenomena occur in many problems, e.g.
+Such phenomena occur in many physical models, e.g.
 vanishing viscosity in the Navier-Stokes equations\cite{Kato_1984}, zero-relaxation-limit of kinetic equations\cite{jin_2010} and zero-Mach-limit of compressible flows\cite{degond_2007, haack_2010}.
-Asymptotic-preserving schemes are the ones that perform uniformly well in such asymptotic limit.
-To briefly illustrate the concept, see the commutative diagram Fig.
+It is desirable that numerical schemes are valid for all ranges of scaled parameters, and especially when they goes to zero.
+These schemes are said to be \emph{asymptotic-preserving}.
+The concept is sketched by the commutative diagram Fig.
 \ref{fig:commutative_diagram_ap} in \cite{jin_1999}.
-The parametrized problem $P^\lambda$, which converges to its limit $P^0$ as the perturbed parameter $\lambda \rightarrow 0$, is discretized by the scheme $P^\lambda_h$ where $h$ denotes some discretization parameter, e.g.
+The parametric problem $P^\lambda$, which converges to its limit $P^0$ as the perturbed parameter $\lambda \rightarrow 0$, is discretized by the scheme $P^\lambda_h$ where $h$ denotes some discretization parameter, e.g.
 mesh size.
@@
 Afterwards we introduce the ECE-type boundary conditions for our problem.
-A reformulation of the Maxwell equations in the insulating region is then presented.
+A reformulation of Maxwell's equations in the insulating region is then presented.
 Section 3 is devoted to the discretization.
@@
 Under moderate assumptions, plasmas, which are gases composed of charged particles (and possibly neutral particles), can be treated as fluid and described by hydrodynamic equations.
-The Maxwell equations are involved to describe their induction of and interaction with electromagnetic fields.
+Maxwell's equations are involved to describe their induction of and interaction with electromagnetic fields.
 
@@
 The other emphasis of this work is the development of a 3D discretization framework for the Maxwell-Euler system.
-The key ingredient is the combination of the Finite Volume Method (FVM) for the Euler equations and the Finite Integration Technique (FIT) for the Maxwell equations.
+The key ingredient is the combination of the Finite Volume Method (FVM) for the Euler equations and the Finite Integration Technique (FIT) for Maxwell's equations.
 The latter one is usually treated as a generalization to Yee's scheme \citep{yee_1966} or FDTD.
@@
 Under moderate assumptions, plasmas, which are gases composed of charged particles (and possibly neutral particles), can be treated as fluids governed by hydrodynamic equations.
-The Maxwell equations take charge of their interaction with electromagnetic fields.
+Maxwell's equations take charge of their interaction with electromagnetic fields.
 For more details on the fluid model of plasma, see \cite{chen2016, remi_2014}.
@@
 We consider the linear constitutive relations
-\begin{equation*}
+\begin{equation} \label{equ:material_law}
     \mathbf{D} = \varepsilon_0 \mathbf{E}, \ \ \ \mathbf{B} = \mu_0\mathbf{H}, 
-\end{equation*}
+\end{equation}
 where $\varepsilon_0$ and $\mu_0$ are the vacuum permittivity and permeability of the medium.
@@
 The coupling of the two subsystems is due to the following relations that connect the fluid and electromagnetic quantities
-\begin{equation*}
+\begin{equation} \label{equ:maxwell_euler_coupling}
     \rho = \sum_* q_*n_*, \ \ \  \mathbf{J} = \sum_* q_*n_*\mathbf{u}_*. 
-\end{equation*}
+\end{equation}
 
@@
 
-Under such assumptions on these dimensionless parameters, the rescaled Euler-Maxwell system is simplified into a parametrized system with the dimensionless Debye length $\lambda$ being the asymptotic parameter
+Under such assumptions on these dimensionless parameters, the rescaled Euler-Maxwell system is simplified into a parametric system with the dimensionless Debye length $\lambda$ being the asymptotic parameter
 \begin{subequations}
@@
 
-\subsection{Quasi-neutral limit} \label{sec:quasi-neutral_limit}
+\subsection{Quasi-neutral Limit} \label{sec:quasi-neutral_limit}
 The Debye length $\lambda_D$ (see its definition at the preceding section) is an characteristic length over which local concentrations of charge are shielded out.
@@
 
-\subsection{Boundary conditions}
+\subsection{Boundary Conditions} \label{sec:BC}
 
@@
 \begin{remark}
-    The treatment of electrodes as open boundary is a rather simplified approach. \todo{a realistic BC for electrodes.}
+    The treatment of electrodes as open boundary is a rather simplified approach. For more realistic electrode modelling, see \cite{godyak_1990, parker_1993}.
 \end{remark}
@@
 External voltages are enforced on the contact boundary $\Gamma_C$ to model electrodes.
-More specifically, $\Gamma_C$ is usually composed of disjoint connecting components $\Gamma_C^i$, $i \leq N$ where $N$ is total number of these boundary components.
-Constant potentials are enforced on each component in the sense that $\varphi|_{\Gamma_C^i} = \varphi_i$.
+More specifically, $\Gamma_C$ is composed of two disjoint connecting components $\Gamma_C^\pm$.
+Constant potentials are enforced on each component in the sense that $\Phi|_{\Gamma_C^\pm} = \Phi_\pm$.
 The insulating boundary blocks the energy interchange and therefore only admits zero electric and magnetic flux, in the sense that $\text{curl}\mathbf{E}\cdot \mathbf{n} = 0$ and $\text{curl}\mathbf{H}\cdot \mathbf{n} = 0$ where $\mathbf{n}$ is the outer normal vector.
@@
 \begin{minipage}[t]{0.49\textwidth}
-    \textbf{For the Maxwell equations:}
+    \textbf{For Maxwell's equations:}
     \begin{align*}
-    \varphi &= \varphi^i(t)\ \ \text{on} \ \ \Gamma_C^i, \\
-    \text{curl} \mathbf{E} \cdot \mathbf{n} &= 0\ \ \text{on} \ \  \Gamma_I,  \\
-    \text{curl} \mathbf{H} \cdot \mathbf{n} &= 0\ \  \text{on} \ \  \Gamma_I.\
+    \Phi = \Phi^\pm(t)\ \ &\text{on} \ \ \Gamma_C^\pm, \\
+    \text{curl} \mathbf{E} \cdot \mathbf{n} = 0\ \ &\text{on} \ \  \Gamma_I,  \\
+    \text{curl} \mathbf{H} \cdot \mathbf{n} = 0\ \ &\text{on} \ \  \Gamma_I.\
     \end{align*}
@@
 \begin{remark}
-    A small remark goes to the validity of assignment of electric potentials on $\Gamma_c^i$.
-Since the surface curl $\text{curl}_\gamma\mathbf{E} = \text{curl} \mathbf{E} \cdot \mathbf{n} = 0$, there exists a surface potential $\varphi$ such that the surface gradient $\nabla_\Gamma \varphi = \gamma_\tau \mathbf{E}$ where $\gamma_\tau $ is the tangential trace operator.
-However, for a geometric setting with non-trivial geometry, one needs to consider co-homology vector fields\cite{Hiptmair_2021}.
+    A small remark goes to the validity of assignment of electric potentials on $\Gamma_c^\pm$.
+Since the surface curl $\text{\emph{curl}}_\gamma\mathbf{E} = \text{\emph{curl}} \mathbf{E} \cdot \mathbf{n} = 0$, there exists a surface potential $\varphi$ such that the surface gradient $\nabla_\Gamma \varphi = \gamma_\tau \mathbf{E}$ where $\gamma_\tau $ is the tangential trace operator.
+However, for a geometric setting with non-trivial geometry, one needs to consider co-homology vector fields \cite{Hiptmair_2021}.
 \end{remark}
 
-\subsection{Reformulation}
+\subsection{Reformulation} \label{sec:reform_continuous}
 In the insulating domain $\Omega_I$ (see Fig.
@@
 We would like to point out that this reformulation is not needed in the plasma domain $\Omega_P$ since the Maxwell system is uniformly well-posed for $\lambda \in [0,1]$ thanks to the existence of electric current and its dependence on the $\mathbf{E}$-field.
-
-\section{Discretization}
 
@@
 
-\colorbox{red}{Polish until here.}
-
-\subsection{1D Discretization}
+\section{Spatial Discretization}
+\subsection{Primal-dual Staggered Meshes}
+\subsubsection{Geometric Property}
+Prior to the spatial discretization of the Maxwell-Euler system, we introduce primal-dual staggered meshes that are necessary in the discretization framework we use.
+The spatial domain is discretized by two meshes that interlace with each other, denoted by a mesh doublet $(\mathcal{M}, \Tilde{\mathcal{M}})$ for primal mesh and dual mesh respectively.
+The fundamental duality property requires that \emph{each edge of one mesh penetrates a face of the other mesh and that each vertex of one mesh lies at the center of a cell of the other mesh} \citep{weiland_2003}, which makes $(\mathcal{M}, \Tilde{\mathcal{M}})$ staggered.
+
+To clarify the notation, in three dimensions the primal mesh $\mathcal{M}$ is a cell complex defined by the set of elements $\{P, L, A, V\}$\footnote{The notation here is a bit floppy.
+$P, L, A, V$ can refer to a single element or a set of elements.} denoting \emph{vertices, edges, faces} and \emph{volume} respectively.
+In the same way, the dual mesh $\Tilde{\mathcal{M}}$ is defined by $\{\Tilde{P}, \Tilde{L}, \Tilde{A}, \Tilde{V}\}$.
+Elements of two meshes are associated with bijective mappings $P \leftrightarrow \Tilde{V}$, $L \leftrightarrow \Tilde{A}$, $A \leftrightarrow \Tilde{L}$ and $V \leftrightarrow \Tilde{P}$ which arise in a very natural way: $P(\Tilde{P} \text{ resp.})$ corresponds to $\Tilde{V}(V \text{ resp.})$ where it lies and $L(\Tilde{L} \text{ resp.})$ penetrates its corresponding $\Tilde{A}(A \text{ resp.})$.
+According to their dimensions, vertices, edges, faces and volumes are also termed 0-dim, 1-dim, 2-dim and 3-dim elements respectively.
+Meanwhile, we denote by $N_\ast, \ast \in \{P, \Tilde{P}, L, \Tilde{L},A, \Tilde{A},V, \Tilde{V}\}$ the total number of elements in $\mathcal{M}, \Tilde{\mathcal{M}}$.
+
+First, we illustrate the 2D case and construct the meshes based on the Delaunay-Voronoi approach: we start with a Delaunay triangulation $\mathcal{M}$ of the domain and construct $\Tilde{\mathcal{M}}$ by connecting \emph{circumcenters} of any two adjacent triangles, see Fig.
+\ref{fig:2d-mesh}.
+
+In three dimensions, the meshes are constructed by extruding the 2D meshes vertically along one axis in a staggered manner \cite{Marrone_2001}.
+See an example in Fig.
+\ref{fig:2d-extrusion}.
+In this way, the meshes are composed of prisms.
+This particular choice is compatible with the cylindrical geometric setting that we are in, see Fig.
+\ref{fig:sketch_domain}.
+For a general setting, one directly decomposes the domain into tetrahedrons and constructs the Voronoi grid in the same manner as before, but the procedure is more complicated and time-consuming.
+The full discretization of the cylindrical domain is given in Fig.
+\ref{fig:primal_dual_meshes}.
+
+The orthogonality between $L \leftrightarrow \Tilde{A}$ and $A \leftrightarrow \Tilde{L}$ is satisfied and would be a crucial property for approximating the material laws shown in the following section.
+
+\begin{remark}
+    The use of the Delaunay-Voronoi based primal-dual meshes may lead to bad performance in simulations if there are obtuse-angle triangles in $\mathcal{M}$.
+In this case their circumcenters lie outside the triangles and the intersection between edges and faces is violated.
+An alternative approach is barycenter-based dual mesh, which is not constraint to an acute-angle triangulation \cite{Marrone_2001}.
+\end{remark}
+
+\begin{figure}
+    \begin{subfigure}[b]{0.45\textwidth}
+    \centering
+    \resizebox{0.45\textwidth}{!}{\begin{tikzpicture}
+    \def\primalstyle{thick}
+    \def\dualstyle{ultra thick}
+    \coordinate (P0) at (0cm, 0cm);
+    \foreach \i in {1,2,...,6}
+    {
+    \coordinate (P\i) at ({60*\i-30}:2cm);
+    \draw[\primalstyle] (P0) -- (P\i);
+    }
+    \draw[\primalstyle] (P1) -- (P2) node[above=3mm]{\Large $\mathcal{M}$} node[left=11mm]{\Large \color{blue} $\Tilde{\mathcal{M}}$} -- (P3) -- (P4) -- (P5) -- (P6) -- cycle;
+    \foreach \i in {1,2,...,6}
+    {
+    \coordinate (D\i) at ({60*\i-60}:{2./1.737});
+    \coordinate (DD\i) at ({60*\i-60}:{4./1.737});
+    }
+    \draw[blue,\dualstyle] (D1) -- (D2) -- (D3) -- (D4) -- (D5) -- (D6) -- cycle;
+    \foreach \i in {1,2,...,6}
+    {
+    \draw[blue,\dualstyle] (D\i) -- (DD\i);
+    }
+    \fill[blue!50, opacity=0.2] (D1) -- (D2) -- (D3) -- (D4) -- (D5) -- (D6) -- cycle;
+    \end{tikzpicture}}
+    \caption{2D case}
+    \label{fig:2d-mesh}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.45\textwidth}
+    \centering
+    \resizebox{0.8\textwidth}{!}{\begin{tikzpicture}
+    \def\primalstyle{thick}
+    \def\dualstyle{thick}
+    \coordinate (P0) at (0cm, 0cm);
+    \foreach \i in {1,2,...,6}
+    {
+    \coordinate (P\i) at ({60*\i-30}:2cm);
+    \draw[\primalstyle] (P0) -- (P\i);
+    }
+    \draw[\primalstyle] (P1) -- (P2) node[left=5mm]{\Large $\mathcal{M}$} -- (P3) -- (P4) -- (P5) -- (P6) -- cycle;
+    \begin{scope}[shift={(3cm,0.5cm)}]
+        \coordinate (PP0) at (0cm, 0cm);
+        \foreach \i in {1,2,...,6}
+        {
+        \coordinate (PP\i) at ({60*\i-30}:2cm);
+        \draw[gray] (PP0) -- (PP\i);
+        }
+    \end{scope}
+
+    \draw[\primalstyle] (PP1) -- (PP2);
+    \draw[gray] (PP2) -- (PP3);
+    \draw[gray] (PP3) -- (PP4);
+    \draw[gray] (PP4) -- (PP5);
+    \draw[\primalstyle] (PP5) -- (PP6);
+    \draw[\primalstyle] (PP6) -- (PP1);
+
+    \draw[gray] (P0) -- (PP0);
+    \draw[\primalstyle] (P1) -- (PP1);
+    \draw[\primalstyle] (P2) -- (PP2);
+    \draw[gray] (P3) -- (PP3);
+    \draw[gray] (P4) -- (PP4);
+    \draw[\primalstyle] (P5) -- (PP5);
+    \draw[\primalstyle] (P6) -- (PP6);
+
+    \foreach \i in {1,2,...,6}
+    {
+    \coordinate (D\i) at ({60*\i-60}:{2./1.737});
+    }
+    \draw[dashed, blue] (D1) -- (D2) -- (D3) -- (D4) -- (D5) -- (D6) -- cycle;
+    \begin{scope}[shift={(1.5,0.25)}]
+        \foreach \i in {1,2,...,6}
+        {
+        \coordinate (DD\i) at ({60*\i-60}:{2./1.737});
+        }
+    \end{scope}
+    \draw[blue] (DD1) -- (DD2) -- (DD3) -- (DD4) -- (DD5) -- (DD6) -- cycle;
+    \draw[blue] (D1) -- (DD1);
+    \draw[blue] (D2) -- (DD2);
+    \draw[blue] (D3) -- (DD3);
+    \draw[blue] (D4) -- (DD4);
+    \draw[blue] (D5) -- (DD5);
+    \draw[blue] (D6) -- (DD6);
+
+    \begin{scope}[shift={(-1.5,-0.25)}]
+        \foreach \i in {1,2,...,6}
+        {
+        \coordinate (DDD\i) at ({60*\i-60}:{2./1.737});
+        }
+    \end{scope}
+    \draw[blue, ultra thick] (DDD1) -- (DDD2) -- (DDD3) node[left=3mm]{\textcolor{blue}{\Large $\Tilde{\mathcal{M}}$}} -- (DDD4) -- (DDD5) -- (DDD6) -- cycle;
+    \draw[blue, ultra thick] (D1) -- (DDD1);
+    \draw[blue, ultra thick] (D2) -- (DDD2);
+    \draw[blue, ultra thick] (D3) -- (DDD3);
+    \draw[blue] (D4) -- (DDD4);
+    \draw[blue] (D5) -- (DDD5);
+    \draw[blue, ultra thick] (D6) -- (DDD6);
+
+    \fill[blue!50, opacity=0.2] (D1) -- (D2) -- (D3) -- (D4) -- (D5) -- (D6);
+
+    \end{tikzpicture}}
+    \caption{3D case (2D extrusion)}
+    \label{fig:2d-extrusion}
+    \end{subfigure}
+    \hfill
+    \caption{Illustration of primal and dual meshes.
+(a) A Delaunay-Voronoi grid in 2D (b) The extrusion of 2D mesh.
+Six triangle prisms are primal cells (depicted by black and gray edges).
+One dual cell, which is a hexagon prism, is depicted by blue edges.
+The dashed hexagon represents the intersection of the dual cell and primal cells.}
+    \label{fig:illustration_primal_dual}
+\end{figure}
+
+\subsubsection{Orientation and Incidence Matrices}
+Each geometrical element in the primal mesh $\mathcal{M}$ is (arbitrarily) endowed of an \emph{internal orientation} \footnote{This notion should not be aliased with \emph{inner orientation}, which has a slightly different definition, see \cite{tonti_2002}.}.
+The notion is sketched in Fig.
+\ref{fig:orientation}.
+For the elements of the dual mesh $\Tilde{\mathcal{M}}$, we set their internal orientations to be aligned with their corresponding primal elements according to the bijective mappings.
+
+Another orientation attribute, \emph{induced orientation}, is defined as follows: an induced orientation of a k-dim element $f$ with respect to a (k+1)-dim element $f'$, satisfying $f \subset \partial f' $, is determined by the internal orientation of $f'$ according to the rule shown in Fig.
+\ref{fig:orientation}.
+
+These information can be formulated into matrices with entries in $\{0,-1,+1\}$, called \emph{incidence matrices}.
+To describe the primal face-to-edge relation, for instance, a sparse matrix $\mathbb{C} \in \mathbb{R}^{N_A \times N_L}$ is assembled whose $(i,j)$-entry is assigned $+1$ if the internal orientation of edge $L_j$ and its induced orientation with respect to face $A_i$ coincides; it is assigned $-1$ if two orientations are opposite; and assigned $0$ if $L_j$ is not a subset of the boundary of $A_i$.
+One would see in the later section that $\mathbb{C}$ functions as a discrete version of curl operator.
+The other incidence matrices are constructed in the same manner, see Tab.
+\ref{tab:incidence_mat} for a summary.
+Given the link of orientations of $\mathcal{M}$ and $\Tilde{\mathcal{M}}$, we can derive the relations listed in Tab.
+\ref{tab:incidence_relation}.
+
+\begin{table}[h!]
+    \centering
+    \begin{tabular}{c c c c}
+    \hline
+         Matrix & Size & Incidence relation & Intuition  \\
+    \hline
+         $\mathbb{D}\ (\Tilde{\mathbb{D}})$ & $N_V \times N_A\ (N_{\Tilde{V}} \times N_{\Tilde{A}})$ & volume $\rightarrow$ face & discrete div \\
+         $\mathbb{C}\ (\Tilde{\mathbb{C}})$ & $N_A \times N_L\ (N_{\Tilde{A}} \times N_{\Tilde{L}})$ & face $\rightarrow$ edge & discrete curl \\
+         $\mathbb{G}\ (\Tilde{\mathbb{G}})$ & $N_L \times N_P\ (N_{\Tilde{L}} \times N_{\Tilde{P}})$ & edge $\rightarrow$ vertex & discrete grad \\
+    \hline
+    \end{tabular}
+    \caption{Summary of incidence matrices}
+    \label{tab:incidence_mat}
+\end{table}
+
+\begin{table}[h!]
+    \centering
+    \begin{tabular}{l c}
+    \hline
+         Relation & Intuition \\
+    \hline
+         $\mathbb{G}^T = -\Tilde{\mathbb{D}}$  &  $\text{grad}^* = - \text{div}$\\
+         $\mathbb{C}^T = \Tilde{\mathbb{C}}$   &  $\text{curl}^* = - \text{curl}$\\
+         $\mathbb{D}^T = -\Tilde{\mathbb{G}}$  &  $\text{div}^* = - \text{grad}$\\
+         $\mathbb{C}\mathbb{G} = \mathbf{0}, \Tilde{\mathbb{C}}\Tilde{\mathbb{G}} = \mathbf{0}$  &  curl $\circ$ grad = 0 \\
+         $\mathbb{D}\mathbb{C} = \mathbf{0}, \Tilde{\mathbb{D}}\Tilde{\mathbb{C}} = \mathbf{0}$   &  div $\circ$ curl = 0 \\
+    \hline
+        \small $\ast$ denotes adjoint operator.
+    \end{tabular}
+    \caption{Relations between incidence matrices}
+    \label{tab:incidence_relation}
+\end{table}
+
+These matrices are topological and thus invariant under smooth deformation of the domain.
+In the next section, we will show that they play a crucial role in constructing the topological relations of the unknowns.
+
+\begin{figure}
+    \centering
+    \begin{minipage}{0.2\textwidth}
+    \centering
+    \begin{tikzpicture}
+        \coordinate (P0) at (0,0);
+        \coordinate (P1) at (10:1); 
+        \coordinate (P2) at (90:1);
+        \coordinate (P3) at (190:1);
+        \coordinate (P4) at (270:1);
+        \coordinate (P5) at (135:0.6);
+        \coordinate (P6) at (-45:0.6);
+        \foreach \i in {1,2,...,6} 
+        {
+            \draw[decoration={markings, mark= at position 0.5 with {\arrow[scale=1.5]{stealth}}},postaction={decorate}] (P\i) -- (P0);
+        }
+        \draw[fill=black] (P0) circle (0.07) node[yshift=15pt, xshift=12pt]{P}; 
+    \end{tikzpicture}
+    \end{minipage}
+    \begin{minipage}{0.2\textwidth}
+    \begin{tikzpicture}
+        \coordinate (P1) at (0,0);
+        \coordinate (P2) at (10:1.8);
+        \draw[decoration={markings, mark= at position 0.55 with {\arrow[scale=1.5]{stealth}}},postaction={decorate}, thick] (P1) -- node[above=2mm]{$L$} (P2);
+        \draw[blue, fill=blue] (P1) circle (0.07) node[above=2mm] {\color{blue}$P_1$} node[below=2mm] {\color{blue}$(-)$};
+        \draw[blue, fill=blue] (P2) circle (0.07) node[above=2mm] {\color{blue}$P_2$} node[below=2mm] {\color{blue}$(+)$};
+    \end{tikzpicture}
+    \end{minipage}
+    \begin{minipage}{0.2\textwidth}
+    \begin{tikzpicture}
+        \coordinate (Q1) at (0,0);
+        \coordinate (Q2) at (1.3cm, -0.46cm);
+        \coordinate (Q3) at (2.0cm, 0.7cm);
+        \draw[decoration={markings, mark= at position 0.5 with {\arrow[scale=1]{stealth}}}, postaction={decorate}, thick, blue] (Q1) -- node[below=1.5mm]{$L_1$} (Q2);
+        \draw[decoration={markings, mark= at position 0.5 with {\arrow[scale=1]{stealth}}}, postaction={decorate},  thick, blue] (Q2) -- node[right,yshift=-1.5mm]{$L_2$} (Q3);
+        \draw[decoration={markings, mark= at position 0.5 with {\arrow[scale=1]{stealth}}}, postaction={decorate},  thick, blue] (Q3) -- node[above,xshift=-3mm] {$L_3$}(Q1);
+        \fill[black!50, opacity=0.25] (Q1) -- (Q2) -- (Q3);
+        \draw[-stealth](barycentric cs:Q1=1,Q2=1,Q3=1) -- ([shift={(0,1cm)}] barycentric cs:Q1=1,Q2=1,Q3=1) node[right,xshift=1mm] {$A$}; 
+    \end{tikzpicture}
+    \end{minipage}
+    \begin{minipage}{0.2\textwidth}
+    \begin{tikzpicture}
+        \coordinate (S1) at (0,0);
+        \coordinate (S2) at (-0.7,0.3);
+        \coordinate (S3) at (1.1,0.7);
+        \coordinate (S4) at (0.3,1.7);
+        \draw[thick] (S1) -- (S2) -- (S4) -- cycle;
+        \fill[blue!50, opacity=0.2] (S1) -- (S2) -- (S4);
+        \draw[thick] (S1) -- (S3) -- (S4) -- cycle;
+        \fill[blue!50, opacity=0.2] (S1) -- (S3) -- (S4);
+        \draw[thin] (S2) -- (S3);
+        \draw[-stealth, blue] (barycentric cs:S1=1,S2=1,S4=1) -- ([shift={(-0.7,0.3)}] barycentric cs:S1=1,S2=1,S4=1) node[above] {$A_1$};
+        \coordinate (O1) at (barycentric cs:S1=1,S2=1,S3=1);
+        \coordinate (O2) at ([shift={(0,-0.7)}] barycentric cs:S1=1,S2=1,S3=1);
+        \coordinate (S)  at (intersection of O1--O2 and S1--S3);
+        \draw[dashed] (O1) -- (S);
+        \draw[-stealth, blue] (S) -- (O2) node[right] {$A_2$};
+        \draw[-stealth, blue] (barycentric cs:S1=1,S3=1,S4=1) -- ([shift={(0.7,0.3)}] barycentric cs:S1=1,S3=1,S4=1) node[right] {$A_3$} ;
+        \coordinate (OO1) at (barycentric cs:S2=1,S3=1,S4=1);
+        \coordinate (OO2) at ([shift={(-0.3,0.9)}] barycentric cs:S2=1,S3=1,S4=1);
+        \coordinate (SS)  at (intersection of OO1--OO2 and S2--S4);
+        \draw[dashed, blue] (OO1) -- (SS);
+        \draw[-stealth, blue] (SS) -- (OO2) node[left] {$A_4$};
+        \node at (S4) [right, xshift=2mm] {$V$};
+    \end{tikzpicture}
+    \end{minipage}
+    \caption{Illustration of internal and induced orientations.
+The internal orientation of each element is depicted in black color: vertices are oriented as \emph{sink} by default; edges are oriented by their pointing direction; faces are oriented by their normal vector; volumes are oriented as positive default.
+The induced orientations are depicted in blue color: the ending vertex of an edge is negatively oriented while the starting point is positively oriented; the orientations of edges with respect to a face obey the right-hand rule; a face of a volume are oriented by its outer normal vector.
+}
+    \label{fig:orientation}
+\end{figure}
+
+\subsubsection{Cut-off Boundary}
+In simulations, the meshes are confined by a definite boundary.
+To make them aligned at boundary, we have to cut off the \emph{dual} elements near the boundary due to the staggered character.
+In the meantime, extra elements are needed to close $\Tilde{\mathcal{M}}$.
+These issues are illustrated in Fig.
+\ref{fig:illustraion_dual_boundary}.
+
+Note that the auxiliary edges might not be straight and the auxiliary faces might not be flat, which necessitates a versatile data structure to include such situations.
+In the following, the auxiliary elements would be treated as dual elements, which limits the validity of the relations in Tab.
+\ref{tab:incidence_relation} only for interior part of $\Tilde{\mathcal{M}}$.
+
+\begin{figure}
+    \begin{subfigure}[b]{0.3\textwidth}
+        \centering
+        \begin{tikzpicture}
+            \colorlet{dual}{blue}
+            \tkzDefPoint(0,0){P1} 
+            \tkzDefPoint(1,1){P1}
+            \tkzDefPoint(1.1,-0.8){P2} 
+            \tkzDefPoint(0.4,-1.4){P3} 
+            \tkzDefPoint(2,0.9){P4} 
+            \tkzDefPoint(1.4, 0){P5}
+            \tkzDefPoint(2.3, 0){P6}
+            \tkzDefPoint(2.1,-1){P7} 
+            \tkzDefPoint(1.6,-1.7){P8} 
+            \foreach \i in {0,...,8} {\tkzDrawPoints(P\i)}
+            %\foreach \i in {0,...,8} {\tkzLabelPoints(P\i)}
+            \tkzDrawSegments(P1,P0 P1,P4 P1,P5 P5,P0 P5,P4 P5,P2 P5,P6 P4,P6 P0,P2 P2,P7 P5,P7 P6,P7 P3,P0 P3,P2 P3,P8 P2,P8 P8,P7)
+            \tkzDefTriangleCenter[circum](P1,P0,P5) \tkzGetPoint{O1} 
+            \tkzDefTriangleCenter[circum](P1,P4,P5) \tkzGetPoint{O2}
+            \tkzDefTriangleCenter[circum](P4,P6,P5) \tkzGetPoint{O3}
+            \tkzDefTriangleCenter[circum](P2,P0,P5) \tkzGetPoint{O4} 
+            \tkzDefTriangleCenter[circum](P2,P7,P5) \tkzGetPoint{O5}
+            \tkzDefTriangleCenter[circum](P2,P0,P3) \tkzGetPoint{O6}
+            \tkzDefTriangleCenter[circum](P2,P3,P8) \tkzGetPoint{O7}
+            \tkzDefTriangleCenter[circum](P2,P7,P8) \tkzGetPoint{O8}
+            \tkzDefTriangleCenter[circum](P5,P6,P7) \tkzGetPoint{O9}
+            \foreach \i in {1,...,9} {\tkzDrawPoints[dual](O\i)}
+            %\foreach \i in {1,...,9} {\tkzLabelPoints(O\i)}
+            \tkzDrawSegments[dual](O1,O2 O2,O3 O3,O9 O9,O5 O5,O4 O1,O4 O4,O6 O6,O7 O7,O8 O8,O5 O5,O9)
+            \tkzDefMidPoint(P0,P1) \tkzGetPoint{M0} \tkzDrawSegment[dual, add= 0 and 1](O1, M0)
+            \tkzDefMidPoint(P1,P4) \tkzGetPoint{M1} \tkzDrawSegment[dual, add= 0 and 1](O2, M1)
+            \tkzDefMidPoint(P4,P6) \tkzGetPoint{M2} \tkzDrawSegment[dual, add= 0 and 1](O3, M2)
+            \tkzDefMidPoint(P6,P7) \tkzGetPoint{M3} \tkzDrawSegment[dual, add= 0 and 1](O9, M3)
+            \tkzDefMidPoint(P7,P8) \tkzGetPoint{M4} \tkzDrawSegment[dual, add= 0 and 1](O8, M4)
+            \tkzDefMidPoint(P3,P8) \tkzGetPoint{M5} \tkzDrawSegment[dual, add= 0 and 1](O7, M5)
+            \tkzDefMidPoint(P0,P3) \tkzGetPoint{M6} \tkzDrawSegment[dual, add= 0 and 1](O6, M6)
+        \end{tikzpicture}
+        \caption{Before cut-off}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.3\textwidth}
+        \centering
+        \begin{tikzpicture}
+            \colorlet{dual}{blue}
+            \colorlet{aux}{orange}
+            \tkzDefPoint(0,0){P1} 
+            \tkzDefPoint(1,1){P1}
+            \tkzDefPoint(1.1,-0.8){P2} 
+            \tkzDefPoint(0.4,-1.4){P3} 
+            \tkzDefPoint(2,0.9){P4} 
+            \tkzDefPoint(1.4, 0){P5}
+            \tkzDefPoint(2.3, 0){P6}
+            \tkzDefPoint(2.1,-1){P7} 
+            \tkzDefPoint(1.6,-1.7){P8} 
+            \foreach \i in {0,...,8} {\tkzDrawPoints(P\i)}
+            %\foreach \i in {0,...,8} {\tkzLabelPoints(P\i)}
+            \tkzDrawSegments(P1,P0 P1,P4 P1,P5 P5,P0 P5,P4 P5,P2 P5,P6 P4,P6 P0,P2 P2,P7 P5,P7 P6,P7 P3,P0 P3,P2 P3,P8 P2,P8 P8,P7)
+            \tkzDefTriangleCenter[circum](P1,P0,P5) \tkzGetPoint{O1} 
+            \tkzDefTriangleCenter[circum](P1,P4,P5) \tkzGetPoint{O2}
+            \tkzDefTriangleCenter[circum](P4,P6,P5) \tkzGetPoint{O3}
+            \tkzDefTriangleCenter[circum](P2,P0,P5) \tkzGetPoint{O4} 
+            \tkzDefTriangleCenter[circum](P2,P7,P5) \tkzGetPoint{O5}
+            \tkzDefTriangleCenter[circum](P2,P0,P3) \tkzGetPoint{O6}
+            \tkzDefTriangleCenter[circum](P2,P3,P8) \tkzGetPoint{O7}
+            \tkzDefTriangleCenter[circum](P2,P7,P8) \tkzGetPoint{O8}
+            \tkzDefTriangleCenter[circum](P5,P6,P7) \tkzGetPoint{O9}
+            \foreach \i in {1,...,9} {\tkzDrawPoints[dual](O\i)}
+            %\foreach \i in {1,...,9} {\tkzLabelPoints(O\i)}
+            \tkzDrawSegments[dual](O1,O2 O2,O3 O3,O9 O9,O5 O5,O4 O1,O4 O4,O6 O6,O7 O7,O8 O8,O5 O5,O9)
+            \tkzDefMidPoint(P0,P1) \tkzGetPoint{M0} \tkzDrawSegment[dual](O1, M0)
+            \tkzDefMidPoint(P1,P4) \tkzGetPoint{M1} \tkzDrawSegment[dual](O2, M1)
+            \tkzDefMidPoint(P4,P6) \tkzGetPoint{M2} \tkzDrawSegment[dual](O3, M2)
+            \tkzDefMidPoint(P6,P7) \tkzGetPoint{M3} \tkzDrawSegment[dual](O9, M3)
+            \tkzDefMidPoint(P7,P8) \tkzGetPoint{M4} \tkzDrawSegment[dual](O8, M4)
+            \tkzDefMidPoint(P3,P8) \tkzGetPoint{M5} \tkzDrawSegment[dual](O7, M5)
+            \tkzDefMidPoint(P0,P3) \tkzGetPoint{M6} \tkzDrawSegment[dual](O6, M6)
+            %\foreach \i in {0,...,6} {\tkzLabelPoints(M\i)}
+
+            \tkzDefPointWith[K=1.2, linear](O1,M0) \tkzGetPoint{N0} 
+            \tkzDefPointWith[K=1.2, linear](O2,M1) \tkzGetPoint{N1}
+            \tkzDefPointWith[K=1.2, linear](O3,M2) \tkzGetPoint{N2}
+            \tkzDefPointWith[K=1.2, linear](O9,M3) \tkzGetPoint{N3}
+            \tkzDefPointWith[K=1.2, linear](O8,M4) \tkzGetPoint{N4}
+            \tkzDefPointWith[K=1.5, linear](O7,M5) \tkzGetPoint{N5}
+            \tkzDefPointWith[K=1.4, linear](O6,M6) \tkzGetPoint{N6}
+            \foreach \i in {0,...,6} {\tkzDrawPoints[aux](N\i)}
+
+            \tkzDefPointWith[K=1.07, linear](P5,P1) \tkzGetPoint{PP1}
+            \tkzDefPointWith[K=1.07, linear](P5,P4) \tkzGetPoint{PP4}
+            \tkzDefPointWith[K=1.08, linear](P5,P6) \tkzGetPoint{PP6}
+            \tkzDefPointWith[K=1.07, linear](P2,P7) \tkzGetPoint{PP7}
+            \tkzDefPointWith[K=1.07, linear](P2,P8) \tkzGetPoint{PP8}
+            \tkzDefPointWith[K=1.07, linear](P2,P3) \tkzGetPoint{PP3}
+            \tkzDefPointWith[K=1.03, linear](M3,P0) \tkzGetPoint{PP0}
+
+            \tkzDrawSegments[aux](N0,PP1 PP1,N1 N1,PP4 PP4,N2 N2,PP6 PP6,N3 N3,PP7 PP7,N4 N4,PP8 PP8,N5 N5,PP3 PP3,N6 N6,PP0 PP0,N0)
+
+        \end{tikzpicture}
+    \caption{After cut-off}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.35\textwidth}
+        \centering
+        \begin{tikzpicture}[scale=0.8]
+            \coordinate (A1) at (0,0);
+            \coordinate (A2) at (2,-0.7);
+            \coordinate (A3) at (1.2,1);
+            \coordinate (A4) at (-0.5,1.5);
+            \draw[thick] (A1) node[left] {$\mathcal{M}$} -- (A2) -- (A3) -- cycle;
+            \draw[thick] (A1) -- (A4) -- (A3);
+            \begin{scope}[shift={(2,0.5)}]
+                \coordinate (B1) at (0,0);
+                \coordinate (B2) at (2,-0.7);
+                \coordinate (B3) at (1.2,1);
+                \coordinate (B4) at (-0.5,1.5);
+                \draw[thick] (B2) -- (B3) -- (B4);
+                \draw[gray]  (B1) -- (B3);
+                \draw[gray]  (B1) -- (B2);
+                \draw[gray]  (B1) -- (B4);
+            \end{scope}
+            \begin{scope}[shift={(4,1)}]
+                \coordinate (C1) at (0,0);
+                \coordinate (C2) at (2,-0.7);
+                \coordinate (C3) at (1.2,1);
+                \coordinate (C4) at (-0.5,1.5);
+                \draw[thick] (C2) -- (C3) -- (C4);
+                \draw[gray]  (C1) -- (C3);
+                \draw[gray]  (C1) -- (C2);
+                \draw[gray]  (C1) -- (C4);
+            \end{scope}
+            \draw[thick] (A4) -- (B4) -- (C4);
+            \draw[thick] (A3) -- (B3) -- (C3);
+            \draw[thick] (A2) -- (B2) -- (C2);
+            \draw[gray]  (A1) -- (C1);
+            \coordinate (O1) at (barycentric cs:A3=1,B3=1);
+            \coordinate (O2) at (barycentric cs:A3=1,B3=1,A4=1,B4=1);
+            \coordinate (O5) at (barycentric cs:A3=1,B3=1,A2=1,B2=1);
+            \draw[orange, very thick] (O2) -- (O1) -- (O5);
+            \coordinate (O3) at (barycentric cs:A1=1,A3=1,A4=1,B1=1,B3=1,B4=1);
+            \coordinate (O4) at (barycentric cs:A1=1,A2=1,A3=1,B1=1,B2=1,B3=1);
+            \draw[blue] (O2) -- (O3) -- (O4) -- (O5);
+            \coordinate (OO1) at ([shift={(2,0.5)}]O1);
+            \coordinate (OO2) at ([shift={(2,0.5)}]O2);
+            \coordinate (OO3) at ([shift={(2,0.5)}]O3);
+            \coordinate (OO4) at ([shift={(2,0.5)}]O4);
+            \coordinate (OO5) at ([shift={(2,0.5)}]O5);
+            \draw[very thick, orange] (OO2) -- (OO1) -- (OO5) node[right] {\textcolor{blue}{$\Tilde{\mathcal{M}}$}};
+            \draw[blue] (OO2) -- (OO3) -- (OO4) -- (OO5);
+            \draw[very thick, orange] (O2) -- (OO2);
+            %\draw[very thick, blue] (O1) -- (OO1);
+            \draw[very thick, orange] (O5) -- (OO5);
+            \draw[blue] (O3) -- (OO3);
+            \draw[blue] (O4) -- (OO4);
+            \fill[gray,opacity=0.2] (A4) -- (A3) -- (C3) -- (C4);
+            \fill[gray,opacity=0.2] (A3) -- (A2) -- (C2) -- (C3);
+            \fill[orange,opacity=0.3] (OO2)--(O2)--(O1)--(O5)--(OO5)--(OO1);
+        \end{tikzpicture}
+        \caption{3D case}
+    \end{subfigure}
+    \caption{Illustration of cut-off boundary.
+Before the cut-off, the boundary of $\Tilde{\mathcal{M}}$ is not well-defined.
+To resolve the same boundary as $\mathcal{M}$, boundary dual volumes are truncated and auxiliary elements are supplemented (shown in orange color).
+To be specific, in subfigure (c) four edges and one face are added in order to close this dual volume.
+Notice that these auxiliary edges and faces can be non-straight and non-flat.}
+    \label{fig:illustraion_dual_boundary}
+\end{figure}
+
+\subsection{Discrete Maxwell Equations}
+\subsubsection{The Finite Integration Technique (FIT)}
+We utilize the FIT to discretize Maxwell's equations.
+This framework was originally proposed in \cite{weiland_1977} and can be treated as a generalization of Yee's FDTD method \cite{yee_1966}.
+FIT is established based on the integral form of Maxwell's equations:
+\begin{subequations}
+\begin{align}
+    &\oint_{\partial A} \mathbf{E} \cdot d\mathbf{s} \ = - \iint_A \frac{\partial \mathbf{B}}{\partial t} \cdot d\mathbf{A}, \label{equ:maxwell_int_faraday}\\
+    &\oint_{\partial A} \mathbf{H} \cdot d\mathbf{s} \ = \iint_A \left(\frac{\partial \mathbf{D}}{\partial t} + \mathbf{J}\right) \cdot d\mathbf{A}, \label{equ:maxwell_int_ampere}\\
+    &\oint_{\partial V} \mathbf{B} \cdot d\mathbf{A} = 0, \label{equ:maxwell_int_gauss_B}\\
+    &\oint_{\partial V} \mathbf{D} \cdot d\mathbf{A} = \iiint_V \rho dV. \label{equ:maxwell_int_gauss_D}
+\end{align}
+\end{subequations}
+where $A, V$ stand for arbitrary surfaces and volumes in the spatial domain.
+
+Given the mesh pair $(\mathcal{M}, \Tilde{\mathcal{M}})$, the discrete Maxwell system is described by applying the integral equations (\ref{equ:maxwell_int_faraday})-(\ref{equ:maxwell_int_gauss_D}) to the elements in $(\mathcal{M}, \Tilde{\mathcal{M}})$.
+We end up with
+\begin{subequations}
+\begin{align}
+    &\sum_{j:L_j\in\partial A_i} \underbrace{\int_{L_j} \mathbf{E} \cdot d\mathbf{s}}_{e_j} = - \frac{\partial}{\partial t} \underbrace{\iint_{A_i} \mathbf{B} \cdot d\mathbf{A}}_{b_i},\ \ \ i = 1,...,N_A, \label{equ:maxwell_grid_faraday} \\
+    &\sum_{j:\Tilde{L}_j\in\partial \Tilde{A}_i} \underbrace{\int_{\Tilde{L}_j} \mathbf{H} \cdot d\mathbf{s}}_{h_j} = \frac{\partial}{\partial t} \underbrace{\iint_{\Tilde{A}_i} \mathbf{D} \cdot d\mathbf{A}}_{d_i} + \underbrace{\iint_{\Tilde{A}_i} \mathbf{J} \cdot d\mathbf{A}}_{j_i}, \ \ \ i = 1,...,N_{\Tilde{A}}, \label{equ:maxwell_grid_ampere}\\
+    &\sum_{j:A_j\in \partial V_i} \iint_{A_j} \mathbf{B} \cdot d\mathbf{A} = 0,\ \ \ i = 1,..., N_V,\label{equ:maxwell_grid_gauss_B}\\
+    &\sum_{j:\Tilde{A}_j \in \partial\Tilde{V}_i}\iint_{\Tilde{A}_j} \mathbf{D} \cdot d\mathbf{A} = \underbrace{\iiint_{\Tilde{V}_i} \rho dV}_{q_i},\ \ \ i = 1,...,N_{\Tilde{V}}.
+\label{equ:maxwell_grid_gauss_D}
+\end{align}
+\end{subequations}
+where $i, j$ are indices for elements in the meshes.
+
+The integral quantities are the unknowns to be solved.
+As is defined in (\ref{equ:maxwell_grid_faraday})-(\ref{equ:maxwell_grid_gauss_D}) by the underbraces, these scalar quantities are stacked into vectors:
+\begin{equation} \label{equ:fit_scale_vector}
+    \mathbf{e} := (e_i)_{i=1}^{N_L},\ \ \mathbf{b} := (b_i)_{i=1}^{N_A}, \ \ \mathbf{h} := (h_i)_{i=1}^{N_{\Tilde{L}}}, \ \ \mathbf{d} := (d_i)_{i=1}^{N_{\Tilde{A}}}, \ \ \mathbf{j} := (j_i)_{i=1}^{N_{\Tilde{A}}}, \ \ \mathbf{q} := (q_i)_{i=1}^{N_{\Tilde{V}}}.
+\end{equation}
+
+The material laws (\ref{equ:material_law}) need to be reformulated within this framework.
+The relations between scalar vectors, in the form of $\mathbf{b} = \mathbb{M}_\mu \mathbf{h}$ and $\mathbf{d} = \mathbb{M}_\varepsilon \mathbf{e}$, are to be derived.
+In the simplest case where permittivity $\mu$ and permeability $\varepsilon$ are homogeneous in the domain, and the orthogonality of ($\mathcal{M}, \Tilde{\mathcal{M}}$) pair is ensured, the material matrices are diagonal with entries
+
+\begin{equation*}
+    (\mathbb{M}_\mu)_{i,i} = \frac{\mu|A_i|}{|\Tilde{L}_i|}, \ \ \ \ \ (\mathbb{M}_\varepsilon)_{i,i} = \frac{\varepsilon |\Tilde{A}_i|}{|L_i|},
+\end{equation*}
+where $|\cdot|$ denotes taking length or area.
+We would like to remark that the approximation error is introduced due to the implicit assumption that vector fields are piecewise constant, see analysis in \cite{Marrone_2001}.
+
+With the aid of incidence matrices defined in the preceding section and given the discrete material law, (\ref{equ:maxwell_grid_faraday})-(\ref{equ:maxwell_grid_gauss_D}) can be reformulated by a set of algebraic equations:
+\begin{center}
+\vspace{-0.5cm}
+\begin{minipage}{0.3\textwidth}
+\begin{align*}
+    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \\
+    \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= -\mathbf{J}, \\
+    \nabla \cdot \mathbf{B} &= 0,  \\
+    \nabla \cdot \mathbf{D} &= \rho, \\
+    \mathbf{H} &= \mu^{-1} \mathbf{B}, \\
+    \mathbf{D} &= \varepsilon \mathbf{E}. 
+\end{align*}
+\end{minipage}
+\begin{minipage}{0.1\textwidth}
+\centering
+\begin{tikzpicture}
+\draw[thick, -{to}] (0,0) -- node[above]{$(\mathcal{M}, \Tilde{\mathcal{M}})$} (1.5,0);
+\end{tikzpicture}
+\end{minipage}
+\begin{minipage}{0.3\textwidth}
+\begin{subequations}
+\begin{align}
+    \dot{\mathbf{b}} + \mathbb{C}\mathbf{e} &= \mathbf{0} , \label{equ:alg_faraday}\\
+    \dot{\mathbf{d}} - \Tilde{\mathbb{C}}\mathbf{h} &= - \mathbf{j}, \label{equ:alg_empere}\\
+    \mathbb{D}\mathbf{b} &= \mathbf{0},  \label{equ:alg_gauss_b}\\
+    \Tilde{\mathbb{D}}\mathbf{d} &= \mathbf{q},  \label{equ:alg_gauss_d}\\
+    \mathbf{h} &= \mathbb{M}_\mu^{-1} \mathbf{b}, \label{equ:alg_material_magnetic}\\
+    \mathbf{d} &= \mathbb{M}_{\varepsilon} \mathbf{e}, \label{equ:alg_material_electric} 
+\end{align}
+\end{subequations}
+\end{minipage}
+\end{center}
+where the topping dot $\cdot$ stands for time derivative.
+
+At this point, we would like to emphasis the importance of the primal-dual staggered meshes: the material laws can be included in a rather simple way.
+For magnetic Gauss's law $\mathbf{D} = \varepsilon \mathbf{E}$, for instance, the $\mathbf{D}$-field is represented by a collection of face integrals $ (d_i)_{i}$ while $\mathbf{E}$-field is represented by a collection of edge integrals $ (e_i)_{i}$.
+The primal-dual meshes allow us to arrange them in a staggered way -- edges penetrate faces -- such that $\mathbf{D} = \varepsilon \mathbf{E}$ can be approximated by $\mathbf{d} = \mathbb{M}_{\varepsilon}\mathbf{e}$ in a local fashion, namely $\mathbb{M}_{\varepsilon}$ is diagonal.
+A more schematic illustration involves the language of differential forms and discrete Hodge operator, see \cite{bossavit1999, teixeira_1999, hip_1999}.
+
+This transformation does not introduce approximations \emph{except for} the discrete material laws. The essence of FIT lies in that the complexity of continuous electric and magnetic field quantities
+is reduced to a finite number of well-defined discrete unknowns \citep{weiland_2003}.
+Also, this discrete version of Maxwell's equations are topological in the sense that they are invariant under different coordinate systems.
+
+\subsubsection{Discrete Boundary Conditions}
+The electromagnetic boundary $\Gamma_C, \Gamma_I$ is resolved by the primal mesh $\mathcal{M}$.
+As is mentioned in Section \ref{sec:BC}, a boundary scalar potential $\Phi$ can be introduced due to the vanishing surface curl of $\mathbf{E}$-field.
+It holds in the discrete level as well.
+We assign each primal vertex $P_i \in \partial\Omega$ a scalar value $\varphi_i$.
+Therefore, the boundary conditions (see Section \ref{sec:BC}) are discretized in the following way:
+\begin{center}
+    \vspace{-0.5cm}
+    \begin{minipage}{0.3\textwidth}
+    \begin{align*}
+    \varphi = \varphi^\pm(t)\ \ &\text{on} \ \ \Gamma_C^\pm, \\
+    \text{curl} \mathbf{E} \cdot \mathbf{n} = 0\ \ &\text{on} \ \  \Gamma_I,  \\
+    \text{curl} \mathbf{H} \cdot \mathbf{n} = 0\ \  &\text{on} \ \  \Gamma_I.\
+    \end{align*}
+    \end{minipage}
+    \begin{minipage}{0.1\textwidth}
+    \centering
+    \begin{tikzpicture}
+    \draw[thick, -{to}] (0,0) -- node[above]{$(\mathcal{M}, \Tilde{\mathcal{M}})$} (1.5,0);
+    \end{tikzpicture}
+    \end{minipage}
+    \begin{minipage}{0.4\textwidth}
+        \begin{subequations}
+            \begin{align}
+            \varphi_i = \Phi^\pm(t), \ \ &\forall i : P_i \subset \Gamma_C^\pm, \label{equ:bc_1}\\
+            e_i = (\mathbb{G}\bm{\varphi})_i,\ \ &\forall i : L_i \subset \partial\Omega, \label{equ:bc_2}\\
+            (\Tilde{\mathbb{C}} \bm{h})_i = 0\ \ &\forall i : \Tilde{A}_i \subset \Gamma_I.\label{equ:bc_3}\
+            \end{align}
+        \end{subequations}
+    \end{minipage}
+\end{center}
+
+\subsubsection{Reformulation} \label{sec:reform_discrete}
+In Section \ref{sec:reform_continuous}, we propose the stabilization of the Maxwell system in the insulating domain $\Omega_I$ by introducing a Lagrange multiplier.
+In the semi-discrete level, the equations to be solved in $\Omega_I$ are
+\begin{subequations}
+    \begin{align}
+        \dot{\mathbf{b}} + \mathbb{C}\mathbf{e} &= \mathbf{0} ,\\
+        \dot{\mathbf{d}} - \Tilde{\mathbb{C}}\mathbf{h} + \colorbox{orange!20}{$\mathbb{H} \mathbb{G} \mathbf{p}$}&= \mathbf{0},\\
+        \Tilde{\mathbb{D}}\mathbf{d} &= \mathbf{0} \label{equ:discrete_zero_div}, 
+    \end{align} 
+\end{subequations}
+
+where $\mathbf{p} = (p_i)_i$ denotes the scalar $p$ assigned to each primal vertex in $\Omega_I$ and the matrix $(\mathbb{H})_{i,i} = \frac{|\Tilde{A}_i|}{|L_i|}$ transforms primal edge integrals to dual face fluxes\footnote{$\mathbb{H}$ functions as a discrete Hodge operator.}.
+To incorporate the zero Dirichlet BC, we limit the unknowns $(p_i)_{i=1}^{N^{\Omega^\circ_I}_P}$ to primal vertices in the interior of $\Omega_I$.
+
+\subsubsection{An algebraic check on the well-posedness}
+
+We can heuristically examine the well-posedness of the (semi-)discrete Maxwell system by checking whether the numbers of unknowns (also called degrees of freedom (D.o.F.)) and equations coincide.
+Before counting, we make a meticulous classification for mesh elements according to their locations and summarize the notation for the sake of clarification (see Tab.
+\ref{tab:def_size_var}).
+\begin{align*}
+    \#\  \text{primal cell}\ \  &N_V \\
+    \#\  \text{primal edge}\ \  &N_L := \underbrace{N^+_L + N^-_L + N^I_L}_{N^\partial_L} + N^\circ_L  \\
+    \#\  \text{primal face}\ \  &N_A := \underbrace{N_A^+ + N_A^- + N^I_A}_{N^\partial_A} + N^\circ_A  \\
+    \#\  \text{primal vertex}\ \  &N_P := \underbrace{N_P^+ + N_P^- + N^I_P}_{N^\partial_P} + N^\circ_P \\
+    \#\  \text{dual cell}\ \  &N_{\Tilde{V}} := N_P \\
+    \#\  \text{dual edge}\ \  &N_{\Tilde{L}} := \underbrace{N^\partial_{\Tilde{L}}}_{=N^\partial_L} + \underbrace{N^\circ_{\Tilde{L}}}_{=N_A} \\
+    \#\  \text{dual face}\ \  &N_{\Tilde{A}} := \underbrace{N^\partial_{\Tilde{A}}}_{=N^\partial_P} + \underbrace{N^\circ_{\Tilde{A}}}_{=N_L}
+\end{align*}
+where the superscripts $\pm, I, \partial, \circ$ indicate that the elements lying in $\gamma^\pm, \gamma^I, \partial\Omega, \Omega^\circ$ respectively .
+The equations $N^\partial_{\Tilde{L}} = N^\partial_L, N^\partial_{\Tilde{A}} = N^\partial_P$, revealing the bijective relation between the boundary primal elements and auxiliary elements, can be check easily by inspecting Fig.
+\ref{fig:illustraion_dual_boundary}.
+
+\begin{table}[]
+    \centering
+\begin{tabular}{c c c}
+     \hline
+     \textbf{D.o.F.}  & \textbf{Meaning}  & \textbf{Size} \\
+     \hline\hline
+     $\mathbf{e}$ & line integrals of $\mathbf{E}$-field at primal edges $L$& $N_L$ \\
+     $\bm{\varphi}$ & electric potentials at primal vertices $P$ on $\partial\Omega$ & $N_P^\partial$ \\
+     $\mathbf{b}$ & surface integrals of $\mathbf{B}$-field at primal faces $A$ & $N_A$ \\
+     $\mathbf{h}$ & line integrals of $\mathbf{H}$-field at dual edges $\Tilde{L}$ & $N_{\Tilde{L}}$ \\
+     $\mathbf{d}$ & surface integrals of $\mathbf{D}$-field at dual faces $\Tilde{A}$ & $N_{\Tilde{A}}$ \\
+     $\mathbf{p}$ & Lagrange multiplier at primal vertices $P$ in $\Omega_I^\circ$ & $N^{\Omega_I^\circ}_P$\\ 
+     \hline
+\end{tabular}
+    \caption{Definitions and sizes of all the degrees of freedom.}
+    \label{tab:def_size_var}
+\end{table}
+
+Next, we collect all the algebraic equations derived from the Maxwell system and the boundary conditions: 
+\begin{align*}
+    \text{discrete Faraday law (\ref{equ:alg_faraday})} \ \ &\longrightarrow\ \  N_A \ \ \text{equations} \\
+    \text{discrete Ampere law (\ref{equ:alg_empere})} \ \ &\longrightarrow\ \  N_{\Tilde{A}} \ \ \text{equations} \\
+    \text{discrete material laws (\ref{equ:alg_material_magnetic})(\ref{equ:alg_material_electric})} \ \ &\longrightarrow\ \  N_A + N_L \ \ \text{equations} \\
+    \text{boundary condition (\ref{equ:bc_1})} \ \ &\longrightarrow\ \  N_P^+ + N_P^- \ \ \text{equations} \\
+    \text{boundary condition (\ref{equ:bc_2})} \ \ &\longrightarrow\ \  N_L^\partial \ \ \text{equations} \\
+    \text{boundary condition (\ref{equ:bc_3})} \ \ &\longrightarrow\ \  N_{\Tilde{A}}^I \ \ \text{equations}. \\
+    \text{vanishing divergence constraint (\ref{equ:discrete_zero_div})} \ \ &\longrightarrow\ \  N_P^{\Omega^\circ_I} \ \ \text{equations}. \\
+\end{align*}
+Comparing the numbers of D.o.F in Tab. \ref{tab:def_size_var} and of the equations we collect, we show that they are equal:
+\begin{align*}
+    \#\text{ of unknowns} &= \colorbox{violet!20}{$N_L$} + \colorbox{blue!20}{$N_A$} + \colorbox{gray!40}{$N_{\Tilde{L}}$} + \colorbox{orange!20}{$N_{\Tilde{A}}$} + \colorbox{green!20}{$N_P^\partial$} + \colorbox{yellow!40}{$N_P^{\Omega^\circ_I}$}, \\
+    \#\text{ of equations} &= \colorbox{blue!20}{$N_A$} + \colorbox{orange!20}{$N_{\Tilde{A}}$} + \colorbox{gray!40}{$N_A$} + \colorbox{violet!20}{$N_L$} + \colorbox{gray!40}{$N_L^\partial$} + \colorbox{green!20}{$N_P^+ + N_P^- + N_P^I$}+ \colorbox{yellow!40}{$N_P^{\Omega^\circ_I}$},
+\end{align*}
+where the terms with the same color are equal.
+
+However, the matching of numbers of unknowns and equations does not necessarily result in a valid linear system.
+Inappropriate BCs could cause the singularity of the linear system as $\lambda \rightarrow 0$, which will be discussed later.
+
+\subsection{Discrete Euler Equations}
+We employ the finite volume method (FVM) to discretize the Euler system.
+As a classical framework for solving conservation laws and hyperbolic systems, FVM is derived from the integral form of the equations in each cell.
+It is the cell average of quantities that evolves at each time step, based on the \emph{numerical flux} through the cell boundary.
+The construction of the numerical flux, which serves to approximate the real flux, is the essence of constructing an FVM scheme.
+Due to the convection nature of fluid dynamics, the numerical fluxes are supposed to respect the convection direction, namely, the \emph{upwind scheme} is preferable.
+To this end, people resort to the approximated solution of \emph{Riemann problems}.
+The method is briefly illustrated in the following.
+For detailed information, see the textbook \cite{leveque_2002}.
+
+The Euler equations (\ref{equ:euler_}) can be generalized into the form of conservation law with source terms:
+\begin{equation} \label{equ:euler_conservation}
+    \partial_t \mathbf{U} + \nabla \cdot \mathbf{F}(\mathbf{U}) = \mathbf{RHS},
+\end{equation}
+where $\mathbf{U} \in L^2(\Omega \times [0,T], \mathbb{R}^m)$ stands for $m$ conservative variable, $\mathbf{F}(\mathbf{U}) \in L^2(\Omega \times  [0,T], \mathbb{R}^m)$ is the flux density, and $\mathbf{RHS} \in L^2(\Omega \times  [0,T], \mathbb{R}^m)$ is the source term.
+
+To obtain the semi-discretization, we first integrate (\ref{equ:euler_conservation}) over a cell $V_i$ 
+\begin{equation} \label{equ:euler_grid} 
+    \dot{\overline{\mathbf{U}}}_i + \frac{1}{|V_i|}\sum_{j:A_j\in\partial V_i} |A_j|\underbrace{\frac{1}{|A_j|}\iint_{A_j}\mathbf{F}(\mathbf{U})\cdot \mathbf{n}_j \text{d}A}_{\overline{\mathbf{F}}_j} = \underbrace{\frac{1}{|V_i|}\iiint_{V_i} \mathbf{RHS} \text{d}V}_{\overline{\mathbf{RHS}}_i}
+\end{equation}
+where $\overline{\mathbf{U}}_i := \iiint_{V_i} \mathbf{U} \text{d}V / |V_i| \in L^2([0,T],\mathbb{R}^m)$ calculates the cell average, $\mathbf{n}_j$ is the outer normal vector of face $A_j$ with respect to the cell $V_i$.
+We approximate the analytic flux $\overline{\mathbf{F}}_j$ in (\ref{equ:euler_grid}) by the numerical flux $\overline{\mathbf{F}}\left(\overline{\mathbf{U}}_i, \overline{\mathbf{U}}_{k(i,j)}, \mathbf{n}_j\right)$, where $k(i,j)$ returns the index of the adjacent cell that shares $A_j$ with cell $V_i$.
+Classical numerical fluxes include Lax-Friedrich flux, Rusanov flux, Engquist-Osher flux, see \cite[][p.
+44-46]{mishra_2019}.
+Finally, we end up with the semi-discretized equation:
+\begin{equation}
+    \dot{\overline{\mathbf{U}}}_i + \frac{1}{|V_i|}\sum_{j:A_j\in\partial V_i} |A_j| \overline{\mathbf{F}}\left(\overline{\mathbf{U}}_i, \overline{\mathbf{U}}_{k(i,j)}, \mathbf{n}_j\right) = \overline{\mathbf{RHS}}_i.
+    \label{equ:fvm}
+\end{equation}
+The Rusanov flux in multi-dimensions on face $A_j$ writes
+\begin{equation} \label{equ:rusanov-flux-3d}
+    \overline{\mathbf{F}}\left(\overline{\mathbf{U}}_L, \overline{\mathbf{U}}_R, \mathbf{n}\right) = \frac{1}{2}\left[\mathbf{F}(\overline{\mathbf{U}}_L)\cdot\mathbf{n} + \mathbf{F}(\overline{\mathbf{U}}_R)\cdot\mathbf{n}\right] - \frac{1}{2}\overline{s}\left(\overline{\mathbf{U}}_R - \overline{\mathbf{U}}_L\right),
+\end{equation}
+where $\overline{s} = \text{max}(s(\overline{\mathbf{U}}_L), s(\overline{\mathbf{U}}_R))$ with $s(\mathbf{U}) := |\mathbf{u}\cdot\mathbf{n}| + \sqrt{\gamma p/\rho}$ representing the largest wave speed.
+
+We would like to emphasis that the Euler system is discretized on $\mathcal{M}'$ due to the fact that 1) the electric current is strongly connected to the momenta of charged particles by (\ref{equ:maxwell_euler_coupling}); 2) the electric current is discretized on dual faces by (\ref{equ:maxwell_grid_ampere}).
+
+To rewrite (\ref{equ:fvm}) into a matrix form, by abuse of notation we stack all the cell average $(\overline{\mathbf{U}}_i)_i$ into a matrix $\mathbf{U} \in \mathbb{R}^{N_{\Tilde{V}}^P \times m}$ with $\mathbf{U}_{i,:} = \overline{\mathbf{U}}_i$.
+Meanwhile, we denote by $\mathbf{F} \in \mathbb{R}^{N_{\Tilde{A}}^P \times m}$ the collection of the (total) numerical fluxes $|A_i|\overline{\mathbf{F}}_i$, namely $\mathbf{f}_{i,:} = |A_i|\overline{\mathbf{F}}_i$, whose directions are determined by the internal direction of faces where they are defined.
+In the same way, we denote by $\mathbf{RHS}\in \mathbb{R}^{N_{\Tilde{V}}^P \times m}$ the collection of $\overline{\mathbf{RHS}}_i$.
+Besides, we define the diagonal matrix $\mathbb{\Tilde{V}} \in \mathbb{R}^{N_{\Tilde{V}}^P}$ with $\mathbb{\Tilde{V}}_{i,i} = |\Tilde{V}_i|$.
+Making use of the incidence matrices, we end up with
+\begin{equation*}
+    \dot{\mathbf{U}} + \mathbb{\Tilde{V}}^{-1}\mathbb{\Tilde{D}}\mathbf{F}(\mathbf{U})  = \mathbf{RHS}(\mathbf{U},\mathbf{b},\mathbf{e}),
+\end{equation*}
+where the dependence of $\mathbf{RHS}$ on $\mathbf{U}, \mathbf{b}, \mathbf{e}$ is implied by (\ref{equ:euler_rescaled}) and will be elaborated below.
+\subsubsection{Reconstruction of Lorentz Force}
+
+\subsubsection{Discrete Boundary Conditions}
+
+\subsection{Summary: Spatially Semi-discrete Model}
+We collect all the equations and BCs presented above and make a summary for the spatially semi-discrete Maxwell-Euler system:
+\begin{subequations}
+    \begin{align*}
+        [\dot{\mathbf{b}} + \mathbb{C}\mathbf{e} = \mathbf{0}]_i, \ \ &\forall i: A_i \subset \Omega, \\
+        [\dot{\mathbf{d}} - \Tilde{\mathbb{C}}\mathbf{h} = - \mathbf{j}]_i, \ \ &\forall i: \Tilde{A}_i \subset \Omega_P,\\
+        [\dot{\mathbf{d}} - \Tilde{\mathbb{C}}\mathbf{h} + \mathbb{H} \mathbb{G} \mathbf{p} = - \mathbf{j}]_i, \ \ &\forall i: A_i \subset \Omega_I,\\
+        [\Tilde{\mathbb{D}}\mathbf{d} = \mathbf{0}]_i,\ \ &\forall i: \Tilde{V}_i \subset \Omega_I, \\
+        [\dot{\mathbf{U}} + \mathbb{\Tilde{V}}^{-1}\mathbb{\Tilde{D}}\mathbf{F} = \mathbf{RHS}]_i,\ \ &\forall i: \Tilde{V}_i \subset \Omega_P,
+    \end{align*}
+with boundary conditions:
+    \begin{align*}
+    \varphi_i = \Phi^\pm(t), \ \ &\forall i : P_i \subset \Gamma_C^\pm, \\
+    e_i = (\mathbb{G}\bm{\varphi})_i,\ \ &\forall i : L_i \subset \partial\Omega, \\
+    (\Tilde{\mathbb{C}} \bm{h})_i = 0,\ \ &\forall i : \Tilde{A}_i \subset \Gamma_I,\\
+    \mathbf{F}_i = |\Tilde{A}_i|\overline{\mathbf{F}}(\mathbf{U}_j, \mathbf{U}_j, \mathbf{n}_i), \ \ &\forall i: \Tilde{A}_i \subset \Gamma_C, \\
+    \mathbf{F}_i = |\Tilde{A}_i|\overline{\mathbf{F}}(\mathbf{U}_j, \hat{\mathbf{U}}_j, \mathbf{n}_i), \ \ &\forall i: \Tilde{A}_i \subset \Gamma_W.
+    \end{align*}
+\end{subequations}
+
+\section{Discretization in time}
+\subsection{Motivation: 1D Discretization}
 \subsubsection{1D plasma model}
@@
 The collision between particles is omitted for the time being.
-\begin{figure}
-    \centering
-    %\includegraphics[scale=0.2]{1d_frame.png}
-    \caption{Projection of the 3D model onto $z$-axis.
-Let us consider a Cartesian mesh doublet.
-The reduction is accomplished by assigning the quantities defined on each cross-section, which is parallel to the $x$-$y$ plane, to its intersection point at $z$-axis.
-Since it is assumed that no variations occur in each cross-section, the quantities in 3D can be compressed by the ones that locate at each mesh point on the $z$-axis.}
-    \label{fig:1d-frame}
-\end{figure}
 
@@
 \subsubsection{Primal-dual staggered mesh}
-A mesh doublet $(\mathcal{M}, \Tilde{\mathcal{M}})$ is required for the formulation of FIT in the need of incorporating the material laws.
-The spatial domain is discretized by two meshes that interlace with each other.
-They are called \emph{primal} mesh $\mathcal{M}$ and \emph{dual} mesh $\Tilde{\mathcal{M}}$.
-The essential duality property requires that \emph{each edge of one mesh penetrates a face of the other mesh and that each vertex of one mesh lies at the center of a cell of the other mesh} \citep{weiland_2003}.
-We demonstrate such interlacing character by an example in Fig.
-\ref{fig:illustration_primal_dual}, where the primal mesh is composed of triangular prisms and the dual mesh is composed of hexagon prisms.
-The dual mesh can be generated as the Voronoi decomposition of the primal mesh \citep{fuchs_2021}.
-Compared to the constraint of FDTD to Cartesian meshes, FIT is compatible with a wide range of mesh types.
-An example of primal and dual meshes is given in Fig.
-\ref{fig:primal_dual_meshes}.
-
-To clarify the terminology, the \emph{vertices, edges, faces} and \emph{volumes} (denoted by $P,L,A$ and $V$ respectively) make up a mesh.
-Also, they are uniformly termed \emph{facets} with zero, one, two and three dimensions.
-
-\begin{figure}
-    \centering
-    \begin{tikzpicture}
-    \def\primalstyle{thick}
-    \def\dualstyle{thick}
-    \coordinate (P0) at (0cm, 0cm);
-    \foreach \i in {1,2,...,6}
-    {
-    \coordinate (P\i) at ({60*\i-30}:2cm);
-    \draw[\primalstyle] (P0) -- (P\i);
-    }
-    \draw[\primalstyle] (P1) -- (P2) node[left=5mm]{\Large $\mathcal{M}$} -- (P3) -- (P4) -- (P5) -- (P6) -- cycle;
-    \begin{scope}[shift={(3cm,0.5cm)}]
-        \coordinate (PP0) at (0cm, 0cm);
-        \foreach \i in {1,2,...,6}
-        {
-        \coordinate (PP\i) at ({60*\i-30}:2cm);
-        \draw[gray] (PP0) -- (PP\i);
-        }
-    \end{scope}
-
-    \draw[\primalstyle] (PP1) -- (PP2);
-    \draw[gray] (PP2) -- (PP3);
-    \draw[gray] (PP3) -- (PP4);
-    \draw[gray] (PP4) -- (PP5);
-    \draw[\primalstyle] (PP5) -- (PP6);
-    \draw[\primalstyle] (PP6) -- (PP1);
-
-    \draw[gray] (P0) -- (PP0);
-    \draw[\primalstyle] (P1) -- (PP1);
-    \draw[\primalstyle] (P2) -- (PP2);
-    \draw[gray] (P3) -- (PP3);
-    \draw[gray] (P4) -- (PP4);
-    \draw[\primalstyle] (P5) -- (PP5);
-    \draw[\primalstyle] (P6) -- (PP6);
-
-    \foreach \i in {1,2,...,6}
-    {
-    \coordinate (D\i) at ({60*\i-60}:{2./1.737});
-    }
-    \draw[dashed, blue] (D1) -- (D2) -- (D3) -- (D4) -- (D5) -- (D6) -- cycle;
-    \begin{scope}[shift={(1.5,0.25)}]
-        \foreach \i in {1,2,...,6}
-        {
-        \coordinate (DD\i) at ({60*\i-60}:{2./1.737});
-        }
-    \end{scope}
-    \draw[blue] (DD1) -- (DD2) -- (DD3) -- (DD4) -- (DD5) -- (DD6) -- cycle;
-    \draw[blue] (D1) -- (DD1);
-    \draw[blue] (D2) -- (DD2);
-    \draw[blue] (D3) -- (DD3);
-    \draw[blue] (D4) -- (DD4);
-    \draw[blue] (D5) -- (DD5);
-    \draw[blue] (D6) -- (DD6);
-
-    \begin{scope}[shift={(-1.5,-0.25)}]
-        \foreach \i in {1,2,...,6}
-        {
-        \coordinate (DDD\i) at ({60*\i-60}:{2./1.737});
-        }
-    \end{scope}
-    \draw[blue, ultra thick] (DDD1) -- (DDD2) -- (DDD3) node[left=3mm]{\textcolor{blue}{\Large $\Tilde{\mathcal{M}}$}} -- (DDD4) -- (DDD5) -- (DDD6) -- cycle;
-    \draw[blue, ultra thick] (D1) -- (DDD1);
-    \draw[blue, ultra thick] (D2) -- (DDD2);
-    \draw[blue, ultra thick] (D3) -- (DDD3);
-    \draw[blue] (D4) -- (DDD4);
-    \draw[blue] (D5) -- (DDD5);
-    \draw[blue, ultra thick] (D6) -- (DDD6);
-
-    \fill[blue!50, opacity=0.2] (D1) -- (D2) -- (D3) -- (D4) -- (D5) -- (D6);
-
-    \end{tikzpicture}
-    \caption{Illustration of primal and dual meshes.
-Six primal cells, which are triangle prisms, are depicted by black and gray edges.
-One dual cell, which is a hexagon prism, is depicted by blue edges.
-The dashed hexagon represents the intersection of the dual cell and primal cells.
-This particular type of mesh composed of prisms is picked as a demonstration since it is used in our numerical experiments.}
-    \label{fig:illustration_primal_dual}
-\end{figure}
+
 \subsubsection{Discrete Maxwell equations: DEC}
@@
 
-The FIT is established based on the integral form of Maxwell's equations:
-\begin{align}
-    &\oint_{\partial A} \mathbf{E} \cdot d\mathbf{s} \ = - \iint_A \frac{\partial \mathbf{B}}{\partial t} \cdot d\mathbf{A}, \label{equ:maxwell_int_faraday}\\
-    &\oint_{\partial A} \mathbf{H} \cdot d\mathbf{s} \ = \iint_A \left(\frac{\partial \mathbf{D}}{\partial t} + \mathbf{J}\right) \cdot d\mathbf{A}, \label{equ:maxwell_int_ampere}\\
-    &\oint_{\partial V} \mathbf{B} \cdot d\mathbf{A} = 0, \label{equ:maxwell_int_gauss_B}\\
-    &\oint_{\partial V} \mathbf{D} \cdot d\mathbf{A} = \iiint_V \rho dV. \label{equ:maxwell_int_gauss_D}
-\end{align}
-where $A, V$ stand for any 2-D faces and 3-D cells in the spatial domain.
-These equations are consequence of curl theorem and divergence theorem, and correspond to the integral form of Faraday's law (\ref{equ:maxwell_int_faraday}), Ampere's law (\ref{equ:maxwell_int_ampere}) and Gauss's laws for magnetic flux (\ref{equ:maxwell_int_gauss_B}) and electric induction (\ref{equ:maxwell_int_gauss_D}).
-The fields are related by the material laws
-\begin{align} \label{equ:maxwell_material_laws}
-    \mathbf{B} = \mu_0 \mathbf{H},\ \ \ \mathbf{D} = \varepsilon_0 \mathbf{E}.
-\end{align}
-
-The discrete Maxwell system is obtained by applying and collecting the equations (\ref{equ:maxwell_int_faraday}) (\ref{equ:maxwell_int_gauss_B}) on each facet of the primal mesh $\mathcal{M}$ and the equations (\ref{equ:maxwell_int_ampere}) (\ref{equ:maxwell_int_gauss_D}) on each facet of the dual mesh $\Tilde{\mathcal{M}}$.
-We denote the vertices by $(P_i)_{i=1}^{N_P}$, $(\Tilde{P}_i)_{i=1}^{N_{\Tilde{P}}}$, edges by $(L_i)_{i=1}^{N_L}$, $(\Tilde{L}_i)_{i=1}^{N_{\Tilde{L}}}$, faces by $(A_i)_{i=1}^{N_A}$, $(\Tilde{A}_i)_{i=1}^{N_{\Tilde{A}}}$, and cells by $(V_i)_{i=1}^{N_V}$, $(\Tilde{V}_i)_{i=1}^{N_{\Tilde{V}}}$ where the ones with tilde belong to the dual mesh.
-Recall the duality property that $\mathcal{M}$ and $\mathcal{M}'$ interlaces with each other in the sense that each edge penetrates a face of the other mesh.
-This leads to $N_L = N_{\Tilde{A}}$ and $N_A = N_{\Tilde{L}}$\footnote{Note that here the influence of boundary is not considered.}.
-The equations (\ref{equ:maxwell_int_faraday}) to (\ref{equ:maxwell_int_gauss_D}) can be rewritten into
-
-\begin{align}
-    &\sum_{j:L_j\in\partial A_i} \underbrace{\int_{L_j} \mathbf{E} \cdot d\mathbf{s}}_{e_j} = - \frac{\partial}{\partial t} \underbrace{\iint_{A_i} \mathbf{B} \cdot d\mathbf{A}}_{b_i},\ \ \ i = 1,...,N_A, \label{equ:maxwell_grid_faraday} \\
-    &\sum_{j:\Tilde{L}_j\in\partial \Tilde{A}_i} \underbrace{\int_{\Tilde{L}_j} \mathbf{H} \cdot d\mathbf{s}}_{h_j} = \frac{\partial}{\partial t} \underbrace{\iint_{\Tilde{A}_i} \mathbf{D} \cdot d\mathbf{A}}_{d_i} + \underbrace{\iint_{\Tilde{A}_i} \mathbf{J} \cdot d\mathbf{A}}_{j_i}, \ \ \ i = 1,...,N_{\Tilde{A}}, \label{equ:maxwell_grid_ampere}\\
-    &\sum_{j:A_j\in \partial V_i} \iint_{A_j} \mathbf{B} \cdot d\mathbf{A} = 0,\ \ \ i = 1,..., N_V,\label{equ:maxwell_grid_gauss_B}\\
-    &\sum_{j:\Tilde{A}_j \in \partial\Tilde{V}_i}\iint_{\Tilde{A}_j} \mathbf{D} \cdot d\mathbf{A} = \underbrace{\iiint_{\Tilde{V}_i} \rho dV}_{q_i},\ \ \ i = 1,...,N_{\Tilde{V}}.
-\label{equ:maxwell_grid_gauss_D}
-\end{align}
-For the sake of neat illustration, we temporarily neglect the boundary conditions which will be discussed later.
-As is indicated in (\ref{equ:maxwell_grid_faraday})(\ref{equ:maxwell_grid_ampere}) by the underbraces, the discrete variables are chosen as the integral quantities of field vectors on edges or faces.
-Packing these scalar quantities into vectors, we define
-\begin{equation} \label{equ:fit_scale_vector}
-    \mathbf{e} := (e_i)_{i=1}^{N_L},\ \ \mathbf{b} := (b_i)_{i=1}^{N_A}, \ \ \mathbf{h} := (h_i)_{i=1}^{N_{\Tilde{L}}}, \ \ \mathbf{d} := (d_i)_{i=1}^{N_{\Tilde{A}}}, \ \ \mathbf{j} := (j_i)_{i=1}^{N_{\Tilde{A}}}, \ \ \mathbf{q} := (q_i)_{i=1}^{N_{\Tilde{V}}}.
-\end{equation}
-
-The next step is to transform the discrete Maxwell system (\ref{equ:maxwell_grid_faraday}) to (\ref{equ:maxwell_grid_gauss_D}) into a set of algebraic equations.
-One should note that the sign of each scalar depends on the orientation of the facet on which it is integrated.
-To uniquely determine the meaning of these quantities, an \emph{internal orientation} is assigned to every facet of the primal mesh $\mathcal{M}$.
-This attribute defines the orientations of edges and outer normals of faces.
-Besides, since the application of curl theorem and divergence theorem entails the orientation relations of edge-to-face and face-to-volume respectively, another orientation attribute, \emph{induced orientation}, is introduced to specify this topology.
-An induced orientation of a $k$-dim facet $f$ with respect to a $(k+1)$-dim facet $f'$ that contains $f$ is determined by the internal orientation of $f'$ according to some rule.
-An example is shown in Fig.
-\ref{fig:illustration_external_orientation}.
-These topological attributes are inherent for a mesh and can be set at will.
-
-\begin{figure}
-    \centering
-
-\begin{tikzpicture}
-\coordinate (P1) at (0,0);
-\coordinate (P2) at (2,2);
-\draw[decoration={markings, 
-    mark= at position 0.55 with {\arrow[scale=1.5]{to}}}
-    ,postaction={decorate}, very thick, blue] (P1) -- (P2);
-\node at (1,1.5) {\textcolor{blue}{$L$}};
-\draw[fill=black] (P1) circle (0.1) node[above=3mm] {$P_1$} node[below=2mm] {$(-)$};
-\draw[fill=black] (P2) circle (0.1) node[above=2mm] {$P_2$} node[below=2mm] {$(+)$};
-
-\begin{scope}[shift={(5, 0)}]
-\coordinate (Q1) at (0,0);
-\coordinate (Q2) at (2cm, -0.5cm);
-\coordinate (Q3) at (3cm, 1cm);
-\draw[decoration={markings, 
-    mark= at position 0.5 with {\arrow[scale=1]{to}}}
-    , postaction={decorate}, very thick] (Q1) -- node[below=1.5mm]{$L_1$} (Q2);
-    \draw[decoration={markings, 
-    mark= at position 0.5 with {\arrow[scale=1]{to}}}
-    , postaction={decorate}, very thick] (Q2) -- node[right,yshift=-1.5mm]{$L_2$} (Q3);
-    \draw[decoration={markings, 
-    mark= at position 0.5 with {\arrow[scale=1]{to}}}
-    , postaction={decorate}, very thick] (Q3) -- node[above,xshift=-3mm] {$L_3$}(Q1);
-
-\fill[blue, opacity=0.25] (Q1) -- (Q2) -- (Q3);
-\draw[decoration={markings, 
-    mark= at position 1 with {\arrow[scale=1.5]{to}}}
-    , postaction={decorate}, very thick, blue](barycentric cs:Q1=1,Q2=1,Q3=1) -- ([shift={(0,2cm)}] barycentric cs:Q1=1,Q2=1,Q3=1) node[right,xshift=1mm] {\textcolor{blue}{$A$}}; 
-\end{scope}
-
-\begin{scope}[shift={(12,0)}]
-\coordinate (S1) at (0,0);
-\coordinate (S2) at (-1,0.5);
-\coordinate (S3) at (1.5,1);
-\coordinate (S4) at (0.5,2.5);
-\draw[very thick, blue] (S1) -- (S2) -- (S4) -- cycle;
-\fill[gray, opacity=0.2] (S1) -- (S2) -- (S4);
-\draw[very thick, blue] (S1) -- (S3) -- (S4) -- cycle;
-\fill[gray, opacity=0.2] (S1) -- (S3) -- (S4);
-\draw[blue, thin] (S2) -- (S3);
-\draw[decoration={markings, 
-    mark= at position 1 with {\arrow[scale=1]{to}}}
-    , postaction={decorate}, very thick] (barycentric cs:S1=1,S2=1,S4=1) -- ([shift={(-1,0.5)}] barycentric cs:S1=1,S2=1,S4=1) node[above] {$A_1$};
-\coordinate (O1) at (barycentric cs:S1=1,S2=1,S3=1);
-\coordinate (O2) at ([shift={(0,-1)}] barycentric cs:S1=1,S2=1,S3=1);
-\coordinate (S)  at (intersection of O1--O2 and S1--S3);
-\draw[very thick, dotted] (O1) -- (S);
-\draw[decoration={markings, 
-    mark= at position 1 with {\arrow[scale=1]{to}}}
-    , postaction={decorate}, very thick] (S) -- (O2) node[right] {$A_2$};
-\draw[decoration={markings, 
-    mark= at position 1 with {\arrow[scale=1]{to}}}
-    , postaction={decorate}, very thick] (barycentric cs:S1=1,S3=1,S4=1) -- ([shift={(1,0.4)}] barycentric cs:S1=1,S3=1,S4=1) node[right] {$A_3$} ;
-\node at (S4) [left, xshift=-2mm] {\textcolor{blue}{$V$}};
-\end{scope}
-\end{tikzpicture}
-    \caption{Illustration of induced orientations.
-As per our rule, the ending vertex of an edge is positively oriented while the starting point is negatively oriented; the orientations of edges with respect to a face obey the right-hand rule; a face of a volume are oriented with its outer normal.
-Note that the rule can be freely set.}
-    \label{fig:illustration_external_orientation}
-\end{figure}
-
-With the aid of both internal and induced orientations, the facet-to-facet relations can be summarized by matrices containing only $\{-1,0,0\}$, which are called \emph{incidence matrices}.
-To describe the primal face-to-edge incidence relation, for instance, a sparse $N_A \times N_L$-matrix $\mathbb{C}$ is assembled whose $(i,j)$-entry is assigned $+1$ if the internal orientation of edge $L_j$ and its induced orientation with respect to face $A_i$ coincides; it is assigned $-1$ if two orientations are opposite; and assigned $0$ if $L_j$ is not a subset of the boundary of $A_i$.
-Discrete Faraday's law (\ref{equ:maxwell_grid_faraday}) is thus reformulated by:
-\begin{equation*}
-    \mathbb{C}\mathbf{e} = - \frac{\text{d}}{\text{d}t} \mathbf{b}.
-\end{equation*}
-As the incidence matrix $\mathbb{C}$ makes up the curl operator in a discrete manner, it is referred to as the \emph{discrete curl operator} for a certain primal mesh.
-
-Given $\mathcal{M}$, the generation of $\Tilde{\mathcal{M}}$ is usually affiliated to $\mathcal{M}$ in terms of geometry, indexing, and topology.
-Although the latter two attributes can be defined with no dependence on $\mathcal{M}$, conventionally one specifies them relying on those of $\mathcal{M}$ for the sake of convenience in both formulation and implementation.
-Recall that primal edges (resp.
-faces) and dual faces (resp.
-edges) intersect in a one-to-one manner.
-Therefore, one can equate the index of a dual edge (resp.
-face) to that of its intersecting primal face (resp.
-edge).
-Furthermore, the internal orientation of a dual facet can be linked to that of its associated primal facet.
-With these constraints, discrete Ampere's law (\ref{equ:maxwell_grid_ampere}) can be reformulated into:
-\begin{equation*}
-    \Tilde{\mathbb{C}}\mathbf{h} = \frac{\text{d}}{\text{d}t} \mathbf{d} + \mathbf{j},
-\end{equation*}
-where $\Tilde{\mathbb{C}}$ is the dual face-to-edge incidence matrix of size $N_{\Tilde{A}} \times N_{\Tilde{L}}$, satisfying $\Tilde{\mathbb{C}} = \mathbb{C}^T$.
-
-In a similar way, discrete Gauss's laws (\ref{equ:maxwell_grid_gauss_B})(\ref{equ:maxwell_grid_gauss_D}) is rewritten into:
-\begin{equation*}
-    \mathbb{D}\mathbf{b} = 0, \ \ \ \  \Tilde{\mathbb{D}}\mathbf{d} = \mathbf{q},
-\end{equation*}
-with $\mathbb{D}$ being the primal cell-to-face incidence matrix of size $N_{V} \times N_{A}$, and $\Tilde{\mathbb{D}}$ being the dual cell-to-face incidence matrix of size $N_{\Tilde{V}} \times N_{\Tilde{A}}$.
-Since they serve as the discrete version of the div operator, they are also referred to as \emph{discrete div operator}.
-It is readily to be checked the following relations
-\begin{equation*}
-    \mathbb{D}\mathbb{C} = 0, \ \ \ \ \Tilde{\mathbb{D}}\Tilde{\mathbb{C}} = 0,
-\end{equation*}
-which is the discrete version of the vector calculus $\nabla \cdot (\nabla \times u) = 0$.
-
-Additionally, the grad operator at the discrete level can be constructed by edge-to-vertex incidence matrices $\mathbb{G}$ of size $N_L \times N_P$ and $\Tilde{\mathbb{G}}$ of size $N_{\Tilde{L}} \times N_{\Tilde{P}}$.
-Given an electric potential vector $\bm{\varphi}$ whose components are defined at primal vertices, for example, the edge voltage vector $\mathbf{e}$ can thus be computed by
-\begin{equation*}
-    \mathbf{e} = \mathbb{G}\bm{\varphi}.
-\end{equation*}
-
-The material laws (\ref{equ:maxwell_material_laws}) need to be reformulated within this framework.
-The relations between scalar vectors, in the form of $\mathbf{b} = \mathbb{M}_\mu \mathbf{h}$ and $\mathbf{d} = \mathbb{M}_\varepsilon \mathbf{e}$, are to be derived.
-In the simplest case where permittivity $\mu$ and permeability $\varepsilon$ are homogeneous in the domain, and the orthogonality\footnote{The edges of one mesh penetrate the faces of the other mesh in an orthogonal manner.} of ($\mathcal{M}, \Tilde{\mathcal{M}}$) pair is ensured, the material matrices are diagonal with entries
-
-\begin{equation*}
-    \mathbb{M}_\mu[i,i] = \frac{\mu|A_i|}{|\Tilde{L}_i|}, \ \ \ \ \mathbb{M}_\varepsilon[i,i] = \frac{\varepsilon |\Tilde{A}_i|}{|L_i|},
-\end{equation*}
-where $|\cdot|$ means taking length or area.
-
-To summarize, the FIT framework enables us to transform Maxwell’s equations into algebraic equations given the mesh pair ($\mathcal{M}, \Tilde{\mathcal{M}}$).
-The resulting system of algebraic equations is called Maxwell's Grid Equations (MGE).
-Let's put together the original form of the Maxwell system as well as the MGE:
-
-\begin{minipage}{0.3\textwidth}
-\begin{align*}
-    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \\
-    \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= -\mathbf{J}, \\
-    \nabla \cdot \mathbf{B} &= 0,  \\
-    \nabla \cdot \mathbf{D} &= \rho, \\
-    \mathbf{H} &= \mu^{-1} \mathbf{B}, \\
-    \mathbf{D} &= \varepsilon \mathbf{E}. 
-\end{align*}
-\end{minipage}
-\begin{minipage}{0.1\textwidth}
-\centering
-\begin{tikzpicture}
-\draw[thick, -{to}] (0,0) -- node[above]{$(\mathcal{M}, \Tilde{\mathcal{M}})$} (1.5,0);
-\end{tikzpicture}
-\end{minipage}
-\begin{minipage}{0.3\textwidth}
-\begin{align*}
-    \dot{\mathbf{b}} + \mathbb{C}\mathbf{e} &= 0 , \\
-    \dot{\mathbf{d}} - \Tilde{\mathbb{C}}\mathbf{h} &= - \mathbf{j}, \\
-    \mathbb{D}\mathbf{b} &= 0,  \\
-    \Tilde{\mathbb{D}}\mathbf{d} &= \mathbf{q},  \\
-    \mathbf{h} &= \mathbb{M}_\mu^{-1} \mathbf{b}, \\
-    \mathbf{d} &= \mathbb{M}_{\varepsilon} \mathbf{e}. 
-\end{align*}
-\end{minipage}
-\begin{minipage}{0.2\textwidth}
-Topological relations:
-\begin{align*}
-    \Tilde{\mathbb{C}} = \mathbb{C}^T \\
-    \mathbb{D}\mathbb{C} = 0 \\
-    \Tilde{\mathbb{D}}\Tilde{\mathbb{C}} = 0
-\end{align*}
-\end{minipage}
-
-\hfill
-
-Note that this transformation does not introduce approximations \emph{except for} the discrete material laws.
-The essence of FIT lies in that the complexity of continuous electric and magnetic field quantities
-is reduced to a finite number of well-defined discrete unknowns \citep{weiland_2003}.
-\subsubsection{Finite volume discretization of the Euler equations}
-We employ the finite volume method (FVM) to discretize the Euler system.
-As a classical framework for solving conservation laws and hyperbolic systems, FVM is derived from the integral form of the equations in each cell.
-It is the cell average of quantities that evolves at each time step, based on the \emph{numerical flux} through the cell boundary.
-The construction of the numerical flux, which serves to approximate the real flux, is the essence of constructing an FVM scheme.
-Due to the convection nature of fluid dynamics, the numerical fluxes are supposed to respect the convection direction, namely, the \emph{upwind scheme} is preferable.
-To this end, people resort to the approximated solution of \emph{Riemann problems}.
-The method is briefly illustrated in the following.
-For detailed information, see the textbook \cite{leveque_2002}.
-
-The Euler equations (\ref{equ:euler_}) can be generalized into the form of conservation law with source terms:
-\begin{equation} \label{equ:euler_conservation}
-    \partial_t \mathbf{U} + \nabla \cdot \mathbf{F}(\mathbf{U}) = \mathbf{RHS},
-\end{equation}
-where $\mathbf{U}$ stands for the conservative variable, $\mathbf{F}(\mathbf{U})$ is the flux density, and $\mathbf{RHS}$ is the source term.
-
-To obtain the semi-discretization, we first integrate (\ref{equ:euler_conservation}) over a cell $V_i$ 
-\begin{equation} \label{equ:euler_grid} 
-    \partial_t \overline{\mathbf{U}}_i + \frac{1}{|V_i|}\sum_{j:A_j\in\partial V_i} |A_j|\underbrace{\frac{1}{|A_j|}\iint_{A_j}\mathbf{F}(\mathbf{U})\cdot \mathbf{n}_j \text{d}A}_{\overline{\mathbf{F}}_j} = \underbrace{\frac{1}{|V_i|}\iiint_{V_i} \mathbf{RHS} \text{d}V}_{\overline{\mathbf{RHS}}_i}
-\end{equation}
-where $\overline{\mathbf{U}}_i := \iiint_{V_i} \mathbf{U} \text{d}V / |V_i|$ calculates the cell average, $\mathbf{n}_j$ is the outer normal vector of face $A_j$ with respect to the cell $V_i$.
-We approximate the analytic flux $\overline{\mathbf{F}}_j$ in (\ref{equ:euler_grid}) by the numerical flux $\overline{\mathbf{F}}\left(\overline{\mathbf{U}}_i, \overline{\mathbf{U}}_{k(i,j)}, \mathbf{n}_j\right)$, where $k(i,j)$ returns the index of the adjacent cell that shares $A_j$ with cell $V_i$.
-Classical numerical fluxes include Lax-Friedrich flux, Rusanov flux, Engquist-Osher flux, see \cite[][p.
-44-46]{mishra_2019}.
-Finally, we end up with the semi-discretized equation:
-\begin{equation*}
-    \partial_t \overline{\mathbf{U}}_i + \frac{1}{|V_i|}\sum_{j:A_j\in\partial V_i} |A_j| \overline{\mathbf{F}}\left(\overline{\mathbf{U}}_i, \overline{\mathbf{U}}_{k(i,j)}, \mathbf{n}_j\right) = \overline{\mathbf{RHS}}_i.
-\end{equation*}
-The Rusanov flux in multi-dimensions on face $A_j$ reads\footnote{See Appendix \ref{app:flux} for detailed derivation.}
-\begin{equation} \label{equ:rusanov-flux-3d}
-    \overline{\mathbf{F}}\left(\overline{\mathbf{U}}_L, \overline{\mathbf{U}}_R, \mathbf{n}\right) = \frac{1}{2}\left[\mathbf{F}(\overline{\mathbf{U}}_L)\cdot\mathbf{n} + \mathbf{F}(\overline{\mathbf{U}}_R)\cdot\mathbf{n}\right] - \frac{1}{2}\overline{s}\left(\overline{\mathbf{U}}_R - \overline{\mathbf{U}}_L\right),
-\end{equation}
-where $\overline{s} = \text{max}(s(\overline{\mathbf{U}}_L), s(\overline{\mathbf{U}}_R))$ with $s(\mathbf{U}) := |\mathbf{u}\cdot\mathbf{n}| + \sqrt{\gamma p/\rho}$ representing the largest wave speed.
 \subsubsection{Discrete boundary conditions}
@@
 \todo{Not sure if a bit analysis about the scheme is needed (and possible).}
-
-\subsubsection{An algebraic check on the well-posedness}
-
-\todo{Not sure if this section is necessary}
-
-To verify that the BCs lead to a well-posed problem, especially for Maxwell's equations\footnote{The BCs for the Euler system are rather classical.
-See \cite[][Chap.
-7]{leveque_2002} for a general introduction, or \cite[][sec.
-2e]{mishra_2019b} for the specific implementation for the Euler equations.}, we want to check that these BCs in the discrete level lead to a solvable linear system.
-A \emph{necessary} condition is that \emph{the number of unknown variables and the number of (independent) algebraic equations coincide}.
-
-We would like to remark that the time-stepping for Euler equations (\ref{equ:euler_ap}) do not involve solving any linear system since the implicit mass term in (\ref{equ:flux_ap}) can be obtained through the momentum equations.
-As for the implicit term $\mathbf{E}^{m+1}$ in the source term (\ref{equ:rhs_ap}), it is obtained through updating the Maxwell system.
-Therefore, only the evolution of the Maxwell system entails solving a linear system, whose validity is discussed here.
-
-First, a meticulous classification and counting for facets of meshes are done as follows:
-\begin{align*}
-    \#\  \text{primal cell}\ \  &N_V \\
-    \#\  \text{primal edge}\ \  &N_L := \underbrace{N^+_L + N^-_L + N^I_L}_{N^\partial_L} + N^\circ_L  \\
-    \#\  \text{primal face}\ \  &N_A := \underbrace{N_A^+ + N_A^- + N^I_A}_{N^\partial_A} + N^\circ_A  \\
-    \#\  \text{primal vertex}\ \  &N_P := \underbrace{N_P^+ + N_P^- + N^I_P}_{N^\partial_P} + N^\circ_P \\
-    \#\  \text{dual cell}\ \  &N_{\Tilde{V}} := N_p \\
-    \#\  \text{dual edge}\ \  &N_{\Tilde{L}} := \underbrace{N^\partial_{\Tilde{L}}}_{=N^\partial_L} + \underbrace{N^\circ_{\Tilde{L}}}_{=N_A} \\
-    \#\  \text{dual face}\ \  &N_{\Tilde{A}} := \underbrace{N^\partial_{\Tilde{A}}}_{=N^\partial_P} + \underbrace{N^\circ_{\Tilde{A}}}_{=N_L}
-\end{align*}
-where the superscripts indicate the domains to which facets belong to, and $+,-,I,\circ,\partial$ represent $\Gamma_+, \Gamma_-, \Gamma_I, \Omega^\circ, \partial \Omega$ respectively.
-As is discussed in Section \ref{sec:boundary_treatment}, auxiliary dual facets are needed to trim $\Tilde{\mathcal{M}}$ such that $\mathcal{M}$ and $\Tilde{\mathcal{M}}$ share the same boundary.
-By inspecting Fig.
-\ref{fig:illustraion_dual_boundary}, one can realize that the auxiliary dual edges have the same number as the primal boundary edges since they intersect with each other; the auxiliary dual faces have the same number as the primal boundary vertices.
-These amount to $N^\partial_{\Tilde{L}} = N^\partial_L, N^\partial_{\Tilde{A}} = N^\partial_P$.
-Note that these number relationships are attained on the premise that non-straight edges and non-flat faces are admissible.
-
-Next, we count the number of unknowns.
-From the BCs (\ref{equ:bc_1})(\ref{equ:bc_3})  we know that the tangential $\mathbf{E}$-field is irrotational at the whole boundary $\partial\Omega$, which allows a scalar potential function $\varphi$ on $\partial \Omega$ with $\text{grad}_\tau \varphi = \mathbf{E}_\tau$.
-In the discrete case, $\bm{\varphi}$ is a scalar vector whose entries are defined on each primal vertex on $\partial \Omega$.
-The collection of boundary electric voltage $\mathbf{e}^\partial$ is retrieved by $\mathbf{e}^\partial = \mathbb{G}_\partial \bm{\varphi}$ where $\mathbb{G}_\partial$ stands for the discrete grad operator on the boundary.
-Besides, additional dual edges and faces at boundary, to which the integrals of the $\mathbf{H}$-field and the $\mathbf{D}$-field are assigned, give rise to unknown $\mathbf{h^\partial}$ and $\mathbf{d^\partial}$ vectors of sizes $N^\partial_{\Tilde{L}}$ and $N^\partial_{\Tilde{A}}$.
-The counting of unknown variables is as follows:
-\begin{equation*}
-    |\mathbf{e}| = N_L, \ \ \ |\mathbf{b}|=N_A, \ \ \ |\mathbf{h}^\partial|=N^\partial_{\Tilde{L}},\ \ \ |\mathbf{d}^\partial| = N^\partial_{\Tilde{A}}, \ \ \ |\bm{\varphi}| = N^\partial_P,
-\end{equation*}
-where $|\cdot|$ denotes the size of vector.
-
-Lastly, we collect all the algebraic equations derived from the Maxwell system.
-The coupling term $\mathbf{j}^{m+1}$ in discrete Ampere's law (\ref{equ:maxwell_ampere_ap}) can be rewritten by electric variables, which will be demonstrated in (\ref{equ:tmp5})(\ref{equ:tmp6}) at the next section.
-The discrete Faraday's law (\ref{equ:maxwell_faraday_ap}) updates the scalar vector $\mathbf{b}$ which is composed of integrals of $\mathbf{B}$-field on each primal face; the discrete Amp\`{e}re's law (\ref{equ:maxwell_ampere_ap}) updates $\mathbf{d}$ which is composed of integrals of $\mathbf{D}$-field on each dual face; the relation $\mathbf{e}^\partial = \mathbb{G}_\partial \bm{\varphi}$ entails $N^\partial_L$ equations each of which is defined on a boundary primal edge; the entries of $\bm{\varphi}$ that locate on the electrodes are assigned externally; the insulating BC (\ref{equ:bc_4}) needs to be satisfied at each dual face that lies in $\Gamma_I$.
-In summary, the counting of algebraic equations is as follows:
-\begin{align*}
-    \text{discrete Faraday law (\ref{equ:maxwell_faraday_ap})} \ \ &\longrightarrow\ \  N_A \ \ \text{equations} \\
-    \text{discrete Ampere law (\ref{equ:maxwell_ampere_ap})} \ \ &\longrightarrow\ \  N_{\Tilde{A}} \ \ \text{equations} \\
-     \mathbf{E}_\tau = \text{grad}_\tau \varphi \Rightarrow \mathbf{e}^\partial = \mathbb{G}_\partial \bm{\varphi} \ \ &\longrightarrow\ \  N^\partial_L \ \ \text{equations} \\
-    \text{enforced potentials}\ \ \varphi^+(t), \varphi^-(t) \ \ &\longrightarrow\ \  N_P^+ + N_P^- \ \ \text{equations} \\
-    \text{insulating BC (\ref{equ:bc_4})} \ \ &\longrightarrow\ \  N_{\Tilde{A}}^I = N_P^I \ \ \text{equations}.
-\end{align*}
-It is straightforward to check that the numbers of unknowns and the equations match. Specifically, 
-\begin{align*}
-    \#\text{ of unknowns} &= \colorbox{orange!20}{$N_L$} + \colorbox{blue!20}{$N_A$} + \colorbox{gray!20}{$N_{\Tilde{L}}^\partial$} + \colorbox{orange!20}{$N_{\Tilde{A}}^\partial$} + \colorbox{green!20}{$N_P^\partial$}, \\
-    \#\text{ of equations} &= \colorbox{blue!20}{$N_A$} + \colorbox{orange!20}{$N_{\Tilde{A}}$} + \colorbox{gray!20}{$N_L^\partial$} + \colorbox{green!20}{$N_P^+ + N_P^- + N_P^I$},
-\end{align*}
-where the terms with the same color can be equated by applying the counting relations listed above.
-
-However, the matching of numbers of unknowns and equations does not necessarily result in a valid linear system.
-Inappropriate BCs could cause the singularity of the linear system, as is discussed in Section \ref{sec:impact_of_bc}.
 

### 2022-10-24 paper_version/main.tex
polish until 3d full scheme

@@
 \newtheorem*{remark}{Remark}
+\DeclareMathOperator*{\argmin}{arg\,min}
 
@@
 \date{}
+
 \begin{document}
@@
 The fundamental duality property requires that \emph{each edge of one mesh penetrates a face of the other mesh and that each vertex of one mesh lies at the center of a cell of the other mesh} \citep{weiland_2003}, which makes $(\mathcal{M}, \Tilde{\mathcal{M}})$ staggered.
+A simple example for Cartesian meshes is shown in Fig.
+\ref{fig:cartesian}.
 
@@
 
-The orthogonality between $L \leftrightarrow \Tilde{A}$ and $A \leftrightarrow \Tilde{L}$ is satisfied and would be a crucial property for approximating the material laws shown in the following section.
+The geometrical orthogonality between $L \leftrightarrow \Tilde{A}$ and $A \leftrightarrow \Tilde{L}$ is satisfied and would be a crucial property for approximating the material laws shown in the following section.
 
@@
 \begin{figure}
-    \begin{subfigure}[b]{0.45\textwidth}
+    \begin{subfigure}[b]{0.3\textwidth}
     \centering
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.45\textwidth}
+    \begin{subfigure}[b]{0.35\textwidth}
     \centering
@@
     \draw[blue, ultra thick] (D6) -- (DDD6);
-
     \fill[blue!50, opacity=0.2] (D1) -- (D2) -- (D3) -- (D4) -- (D5) -- (D6);
-
     \end{tikzpicture}}
@@
     \label{fig:2d-extrusion}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.35\textwidth}
+    \centering
+    \begin{tikzpicture}[scale = 0.2]
+            \def\style{thick}
+            \draw[\style] (0,0) -- (1.5,0);
+            \draw[\style] (0,0) -- (0,5) -- (5,5) -- (5,2.5);
+            \draw[\style] (0,5) -- (2,7) node[left]{$\mathcal{M}$} -- (7,7) -- (5,5);
+            \draw[\style] (7,7) -- (7,3.5);
+            \draw[dashed, very thin] (1.5, 0) -- (5,0);
+            \draw[dashed, very thin] (5,0) -- (5,2.5);
+            \draw[dashed, very thin] (5,0) -- (7,2);
+            \draw[dashed, very thin] (7,2) -- (7,3.5);
+
+            \draw[fill = gray!60,\style] (5,2.5) -- (6,3.5) -- (7,3.5) -- (7,7) -- (5,5) -- cycle;
+            \draw[fill = gray!10,\style] (0,5) -- (5,5) -- (7,7) -- (2,7) -- cycle;
+            \draw[dashed, very thin] (5,0) -- (6.5,1.5) -- (5,1.5) -- cycle;
+
+            \begin{scope}[shift={(1.5,-3.5)}]
+            \draw[blue,\style] (0,0) -- (5,0)  node[right]{$\Tilde{\mathcal{M}}$};
+            \draw[blue,\style] (5,0) -- (5,5);
+            \draw[blue,\style] (5,5) -- (0,5);
+            \draw[blue,\style] (0,5) -- (0,0);
+            \draw[blue,\style] (0,5) -- (1,6);
+            \draw[blue,\style] (4.5,7) -- (7,7);
+            \draw[blue,\style] (7,7) -- (5,5);
+            \draw[blue,\style] (7,7) -- (7,2);
+            \draw[blue,\style] (7,2) -- (5,0);
+            \draw[dashed, very thin] (1,6) -- (2,7);
+            \draw[dashed, very thin] (2,7) -- (4.5,7);
+            \draw[fill = blue!10,\style] (0,5) -- (5,5) -- (7,7) -- (4.5,7) -- (3.5, 6) -- (1,6) -- cycle;
+            \draw[fill = blue!40,\style] (5,0) -- (7,2) -- (7,7) -- (5,5) -- cycle;
+            \draw[dashed, very thin] (1,6) -- (2,7) -- (3.5,7) -- (3.5,6) -- cycle;
+            \end{scope}
+        \end{tikzpicture}
+        \caption{3D case (Cartesian)}
+        \label{fig:cartesian}
     \end{subfigure}
@@
 One dual cell, which is a hexagon prism, is depicted by blue edges.
-The dashed hexagon represents the intersection of the dual cell and primal cells.}
+The dashed hexagon represents the intersection of the dual cell and primal cells.
+(c) A Cartesian case.}
     \label{fig:illustration_primal_dual}
@@
 \subsubsection{Cut-off Boundary}
-In simulations, the meshes are confined by a definite boundary.
+We can only solve problems on a bounded domain and thus the meshes are confined by a definite boundary.
 To make them aligned at boundary, we have to cut off the \emph{dual} elements near the boundary due to the staggered character.
@@
 \end{center}
-where the topping dot $\cdot$ stands for time derivative.
+where the topping dot $\cdot$ stands for taking time derivative.
 
@@
 
-where $\mathbf{p} = (p_i)_i$ denotes the scalar $p$ assigned to each primal vertex in $\Omega_I$ and the matrix $(\mathbb{H})_{i,i} = \frac{|\Tilde{A}_i|}{|L_i|}$ transforms primal edge integrals to dual face fluxes\footnote{$\mathbb{H}$ functions as a discrete Hodge operator.}.
+where $\mathbf{p} = (p_i)_i$ denotes the scalar $p$ assigned to each primal vertex in $\Omega_I$ and the matrix $\mathbb{H}_{i,i} = \frac{|\Tilde{A}_i|}{|L_i|}$ transforms primal edge integrals to dual face fluxes\footnote{$\mathbb{H}$ functions as a discrete Hodge operator.}.
 To incorporate the zero Dirichlet BC, we limit the unknowns $(p_i)_{i=1}^{N^{\Omega^\circ_I}_P}$ to primal vertices in the interior of $\Omega_I$.
@@
 \begin{equation} \label{equ:euler_conservation}
-    \partial_t \mathbf{U} + \nabla \cdot \mathbf{F}(\mathbf{U}) = \mathbf{RHS},
+    \partial_t \mathbf{U} + \nabla \cdot \mathbf{f}(\mathbf{U}) = \mathbf{RHS},
 \end{equation}
-where $\mathbf{U} \in L^2(\Omega \times [0,T], \mathbb{R}^m)$ stands for $m$ conservative variable, $\mathbf{F}(\mathbf{U}) \in L^2(\Omega \times  [0,T], \mathbb{R}^m)$ is the flux density, and $\mathbf{RHS} \in L^2(\Omega \times  [0,T], \mathbb{R}^m)$ is the source term.
+where $\mathbf{U} \in L^2(\Omega \times [0,T], \mathbb{R}^m)$ stands for $m$ conservative variable, $\mathbf{f}(\mathbf{U}) \in L^2(\Omega \times  [0,T], \mathbb{R}^m)$ is the flux density, and $\mathbf{RHS} \in L^2(\Omega \times  [0,T], \mathbb{R}^m)$ is the source term.
 
@@
 \begin{equation} \label{equ:euler_grid} 
-    \dot{\overline{\mathbf{U}}}_i + \frac{1}{|V_i|}\sum_{j:A_j\in\partial V_i} |A_j|\underbrace{\frac{1}{|A_j|}\iint_{A_j}\mathbf{F}(\mathbf{U})\cdot \mathbf{n}_j \text{d}A}_{\overline{\mathbf{F}}_j} = \underbrace{\frac{1}{|V_i|}\iiint_{V_i} \mathbf{RHS} \text{d}V}_{\overline{\mathbf{RHS}}_i}
+    \dot{\overline{\mathbf{U}}}_i + \frac{1}{|V_i|}\sum_{j:A_j\in\partial V_i} |A_j|\underbrace{\frac{1}{|A_j|}\iint_{A_j}\mathbf{f}(\mathbf{U})\cdot \mathbf{n}_j \text{d}A}_{\overline{\mathbf{f}}_j \approx \mathbf{f}^\text{num}_j} = \underbrace{\frac{1}{|V_i|}\iiint_{V_i} \mathbf{RHS} \text{d}V}_{\overline{\mathbf{RHS}}_i}
 \end{equation}
 where $\overline{\mathbf{U}}_i := \iiint_{V_i} \mathbf{U} \text{d}V / |V_i| \in L^2([0,T],\mathbb{R}^m)$ calculates the cell average, $\mathbf{n}_j$ is the outer normal vector of face $A_j$ with respect to the cell $V_i$.
-We approximate the analytic flux $\overline{\mathbf{F}}_j$ in (\ref{equ:euler_grid}) by the numerical flux $\overline{\mathbf{F}}\left(\overline{\mathbf{U}}_i, \overline{\mathbf{U}}_{k(i,j)}, \mathbf{n}_j\right)$, where $k(i,j)$ returns the index of the adjacent cell that shares $A_j$ with cell $V_i$.
+We approximate the flux $\overline{\mathbf{f}}_j$ in (\ref{equ:euler_grid}) by a numerical flux $\mathbf{f}^\text{num}_j := \mathbf{f}^\text{num}\left(\overline{\mathbf{U}}_i, \overline{\mathbf{U}}_{k(i,j)}, \mathbf{n}_j\right)$, where $k(i,j)$ returns the index of the adjacent cell that shares $A_j$ with cell $V_i$.
 Classical numerical fluxes include Lax-Friedrich flux, Rusanov flux, Engquist-Osher flux, see \cite[][p.
@@
 \begin{equation}
-    \dot{\overline{\mathbf{U}}}_i + \frac{1}{|V_i|}\sum_{j:A_j\in\partial V_i} |A_j| \overline{\mathbf{F}}\left(\overline{\mathbf{U}}_i, \overline{\mathbf{U}}_{k(i,j)}, \mathbf{n}_j\right) = \overline{\mathbf{RHS}}_i.
+    \dot{\overline{\mathbf{U}}}_i + \frac{1}{|V_i|}\sum_{j:A_j\in\partial V_i} |A_j| \mathbf{f}^\text{num}\left(\overline{\mathbf{U}}_i, \overline{\mathbf{U}}_{k(i,j)}, \mathbf{n}_j\right) = \overline{\mathbf{RHS}}_i.
     \label{equ:fvm}
@@
 \begin{equation} \label{equ:rusanov-flux-3d}
-    \overline{\mathbf{F}}\left(\overline{\mathbf{U}}_L, \overline{\mathbf{U}}_R, \mathbf{n}\right) = \frac{1}{2}\left[\mathbf{F}(\overline{\mathbf{U}}_L)\cdot\mathbf{n} + \mathbf{F}(\overline{\mathbf{U}}_R)\cdot\mathbf{n}\right] - \frac{1}{2}\overline{s}\left(\overline{\mathbf{U}}_R - \overline{\mathbf{U}}_L\right),
+    \mathbf{f}^\text{num}\left(\overline{\mathbf{U}}_L, \overline{\mathbf{U}}_R, \mathbf{n}\right) = \frac{1}{2}\left[\mathbf{f}(\overline{\mathbf{U}}_L)\cdot\mathbf{n} + \mathbf{f}(\overline{\mathbf{U}}_R)\cdot\mathbf{n}\right] - \frac{1}{2}\overline{s}\left(\overline{\mathbf{U}}_R - \overline{\mathbf{U}}_L\right),
 \end{equation}
@@
 
-We would like to emphasis that the Euler system is discretized on $\mathcal{M}'$ due to the fact that 1) the electric current is strongly connected to the momenta of charged particles by (\ref{equ:maxwell_euler_coupling}); 2) the electric current is discretized on dual faces by (\ref{equ:maxwell_grid_ampere}).
+We would like to emphasis that the Euler system is discretized on $\mathcal{M}'$ due to the fact that 1) the electric current is connected to the momenta of charged particles by (\ref{equ:maxwell_euler_coupling}); 2) the electric current is discretized on dual faces by (\ref{equ:maxwell_grid_ampere}).
 
 To rewrite (\ref{equ:fvm}) into a matrix form, by abuse of notation we stack all the cell average $(\overline{\mathbf{U}}_i)_i$ into a matrix $\mathbf{U} \in \mathbb{R}^{N_{\Tilde{V}}^P \times m}$ with $\mathbf{U}_{i,:} = \overline{\mathbf{U}}_i$.
-Meanwhile, we denote by $\mathbf{F} \in \mathbb{R}^{N_{\Tilde{A}}^P \times m}$ the collection of the (total) numerical fluxes $|A_i|\overline{\mathbf{F}}_i$, namely $\mathbf{f}_{i,:} = |A_i|\overline{\mathbf{F}}_i$, whose directions are determined by the internal direction of faces where they are defined.
+Meanwhile, we denote by $\mathbf{F} \in \mathbb{R}^{N_{\Tilde{A}}^P \times m}$ the collection of the (total) numerical fluxes, namely $\mathbf{F}_{i,:} = |A_i|\mathbf{f}^\text{num}_i$.
 In the same way, we denote by $\mathbf{RHS}\in \mathbb{R}^{N_{\Tilde{V}}^P \times m}$ the collection of $\overline{\mathbf{RHS}}_i$.
@@
 \begin{equation*}
-    \dot{\mathbf{U}} + \mathbb{\Tilde{V}}^{-1}\mathbb{\Tilde{D}}\mathbf{F}(\mathbf{U})  = \mathbf{RHS}(\mathbf{U},\mathbf{b},\mathbf{e}),
+    \dot{\mathbf{U}} + \mathbb{\Tilde{V}}^{-1}\mathbb{\Tilde{D}}\mathbf{F}(\mathbf{U})  = \mathbf{RHS}(\mathbf{U},\mathbf{d},\mathbf{b}),
 \end{equation*}
-where the dependence of $\mathbf{RHS}$ on $\mathbf{U}, \mathbf{b}, \mathbf{e}$ is implied by (\ref{equ:euler_rescaled}) and will be elaborated below.
+where the dependence of $\mathbf{RHS}$ on $\mathbf{U}, \mathbf{d}, \mathbf{b}$ is implied by (\ref{equ:euler_rescaled}) and will be elaborated below.
+
 \subsubsection{Reconstruction of Lorentz Force}
+Since the electromagnetic fields are represented by integrals on edges and faces, we need to reconstruct their vector components for the computation of Lorentz force (and Joule heating) inside each dual volume.
+
+The problem is twofold:
+\begin{itemize}
+    \item[-] given the fluxes at faces of a volume, reconstruct the vector field inside the volume;
+    \item[-] given the integrals along edges of a volume, reconstruct the vector field inside the volume. 
+\end{itemize}
+We adopt the principle of least square fitting, and reconstruct a \emph{constant} vector field inside each volume.
+For a volume $\Tilde{V}$ with $k$ faces with areas $\{A_i\}_{i=1}^k$, normal vectors $\{\mathbf{n}_i\}_{i=1}^k$ and fluxes $\{f_i\}_{i=1}^k$, a constant vector field $\mathbf{v}$ satisfying
+\begin{equation*}
+    \mathbf{v} = \argmin_{v\in \mathbb{R}^3} \sum_{i=1}^k(A_i\mathbf{v} \cdot \mathbf{n}_i - f_i)^2.   
+\end{equation*} can be computed through
+\begin{equation*}
+    \mathbf{v} = (\mathbb{K}^T\mathbb{K})^{-1}\mathbb{K}^T\mathbf{f},
+\end{equation*}
+where
+\begin{equation*}
+    \mathbb{K} = [A_1\mathbf{n}_1, A_2\mathbf{n}_2, \cdots, A_k\mathbf{n}_k]^T,\ \ \ \mathbf{f} = [f_1, f_2, \cdots, f_k]^T,
+\end{equation*}
+and each vector in $\mathbb{R}^3$ is treated as a column vector.
+The construction based on the integral quantities on edges can be done similarly.
+Assembling the local constructions for each dual volume, the global construction can be written as
+\begin{equation}
+    \mathbf{E} = \Tilde{\mathbb{R}}_E\mathbf{d},
+    \ \ \ \ 
+    \mathbf{B} = \Tilde{\mathbb{R}}_B\mathbf{b},
+\end{equation}
+where $\mathbf{d}, \mathbf{b}$ are stacked unknowns, see Tab.
+\ref{tab:def_size_var}; $\mathbf{E} := (\mathbf{E}_i)_{i=1}^{N_{\Tilde{V}}}$ and $\mathbf{B} := (\mathbf{B}_i)_{i=1}^{N_{\Tilde{V}}}$ are $N_{\Tilde{V}} \times 3$ matrices stacking the reconstructed $\mathbf{E}$-fields and $\mathbf{B}$-fields at each $\Tilde{V}$; $\Tilde{\mathbb{R}}_E$ and $\Tilde{\mathbb{R}}_B$ are thus rank-3 tensors.
+
+The problem of the reconstruction of vector fields on unstructured meshes is a widely studied topic.
+Apart from the least-square method, other methods include Perot's method \citep{perot_2000}, finite-element-based methods, etc., which potentially can achieve higher-order accuracy.
+See \cite[][sec.
+3.4.4]{fuchs_2021} and the references therein.
 
 \subsubsection{Discrete Boundary Conditions}
+The BCs for the Euler system (see Section \ref{sec:BC}) are implemented by the approach of ghost cells \cite[][Chapt.
+7]{leveque_2007}, namely thinking of extending the domain by a few additional cells and prescribing the variables.
+In our case, the ghost cells at the open boundary at $\Gamma_C$ are set to have the equal values as the interior ones that are adjacent.
+It is equivalent to enforce the numerical fluxes
+\begin{equation*}
+    \mathbf{F}_i = |\Tilde{A}_i|{\mathbf{f}^\text{num}}(\mathbf{U}_j, \mathbf{U}_j, \mathbf{n}_i), \ \ \forall i: \Tilde{A}_i \subset \Gamma_C,
+\end{equation*}
+where $j$ refers to the index of the volume adjacent to the boundary face $\Tilde{A}_i$ and is unique.
+For the reflective wall $\Gamma_W$, the momentum of a ghost cell are reversed with respect to its adjacent one while keeping the other quantities unchanged.
+Therefore, the numerical fluxes are
+\begin{equation*}
+    \mathbf{F}_i = |\Tilde{A}_i|\mathbf{f}^\text{num}(\mathbf{U}_j, \hat{\mathbf{U}}_j, \mathbf{n}_i), \ \ \forall i: \Tilde{A}_i \subset \Gamma_W,
+\end{equation*}
+where the value of the ghost cell $\hat{\mathbf{U}} = [n, n\mathbf{u} - 2(\mathbf{n}\cdot\mathbf{u})\mathbf{n}, ne]^T$ for $\mathbf{U} = [n, n\mathbf{u}, ne]^T$.
 
@@
 \begin{subequations}
-    \begin{align*}
+    \begin{align}
         [\dot{\mathbf{b}} + \mathbb{C}\mathbf{e} = \mathbf{0}]_i, \ \ &\forall i: A_i \subset \Omega, \\
         [\dot{\mathbf{d}} - \Tilde{\mathbb{C}}\mathbf{h} = - \mathbf{j}]_i, \ \ &\forall i: \Tilde{A}_i \subset \Omega_P,\\
-        [\dot{\mathbf{d}} - \Tilde{\mathbb{C}}\mathbf{h} + \mathbb{H} \mathbb{G} \mathbf{p} = - \mathbf{j}]_i, \ \ &\forall i: A_i \subset \Omega_I,\\
+        [\dot{\mathbf{d}} - \Tilde{\mathbb{C}}\mathbf{h} + \mathbb{H} \mathbb{G} \mathbf{p} = - \mathbf{j}]_i, \ \ &\forall i: \Tilde{A}_i \subset \Omega_I,\\
         [\Tilde{\mathbb{D}}\mathbf{d} = \mathbf{0}]_i,\ \ &\forall i: \Tilde{V}_i \subset \Omega_I, \\
-        [\dot{\mathbf{U}} + \mathbb{\Tilde{V}}^{-1}\mathbb{\Tilde{D}}\mathbf{F} = \mathbf{RHS}]_i,\ \ &\forall i: \Tilde{V}_i \subset \Omega_P,
-    \end{align*}
-with boundary conditions:
-    \begin{align*}
+        [\dot{\mathbf{U}}_\ast + \mathbb{\Tilde{V}}^{-1}\mathbb{\Tilde{D}}\mathbf{F}_\ast = \mathbf{RHS}_\ast]_i,\ \ &\forall i: \Tilde{V}_i \subset \Omega_P, 
+    \end{align}
+    \vspace{-1cm}
+    \begin{align}
+        \hspace{1.6cm}\mathbf{j}_i =
+        \begin{cases}
+         \Sigma_{\ast} q_*\mathbf{F}_{\ast,i}^\text{n},&\forall i: \Tilde{A}_i \subset \Omega_P, \\
+        0,&\forall i: \Tilde{A}_i \subset \Omega_I,
+        \end{cases}
+    \end{align}
+where $\ast$ stands for indices for multiple species and $\mathbf{F}^\text{n}$ denotes the mass flux. We have the following BCs:
+    \begin{align}
     \varphi_i = \Phi^\pm(t), \ \ &\forall i : P_i \subset \Gamma_C^\pm, \\
@@
     (\Tilde{\mathbb{C}} \bm{h})_i = 0,\ \ &\forall i : \Tilde{A}_i \subset \Gamma_I,\\
-    \mathbf{F}_i = |\Tilde{A}_i|\overline{\mathbf{F}}(\mathbf{U}_j, \mathbf{U}_j, \mathbf{n}_i), \ \ &\forall i: \Tilde{A}_i \subset \Gamma_C, \\
-    \mathbf{F}_i = |\Tilde{A}_i|\overline{\mathbf{F}}(\mathbf{U}_j, \hat{\mathbf{U}}_j, \mathbf{n}_i), \ \ &\forall i: \Tilde{A}_i \subset \Gamma_W.
-    \end{align*}
+    \mathbf{F}_{\ast,i} = |\Tilde{A}_i|\mathbf{f}^\text{num}(\mathbf{U}_{\ast,j}, \mathbf{U}_{\ast,j}, \mathbf{n}_i), \ \ &\forall i: \Tilde{A}_i \subset \Gamma_C, \\
+    \mathbf{F}_{\ast,i} = |\Tilde{A}_i|\mathbf{f}^\text{num}(\mathbf{U}_{\ast,j}, \hat{\mathbf{U}}_{\ast,j}, \mathbf{n}_i), \ \ &\forall i: \Tilde{A}_i \subset \Gamma_W.
+    \end{align}
 \end{subequations}
-
-\section{Discretization in time}
-\subsection{Motivation: 1D Discretization}
-\subsubsection{1D plasma model}
-The 3D problem is projected onto the 1D axis by assuming vanishing traverse derivatives (see Fig.
-\ref{fig:1d-frame} for the definition of reference frame).
+We would like to stress again that in our FIT-FVM framework Faraday's law is discretized on $\mathcal{M}$ while Amp\`{e}re's law is discretized on $\mathcal{M}'$ for a simple approximation of material laws.
+By arranging the Euler system on $\mathcal{M}'$, the connection between electric currents and fluid momenta is naturally established in the discrete level since they are defined on the same locations.
+
+\section{Full Discretization}
+On discussing the discretization in space, inthis section we discuss the time-stepping which is strongly related to the AP property since it directly influences the stability of the scheme. 
+\subsection{Motivation: Reduction to 1D Discretization}
+Our work is an extension of the 1D scheme proposed in \cite{degond_2012} towards a scheme in three dimensions.
+Therefore, it is compatible with the original 1D scheme when one considers its reduction to one dimension.
+This mental experiment aims to help readers understand how the new 3D scheme originates from the 1D one.
+\subsubsection{Projection to one dimension}
+Consider a mesh pair $(\mathcal{M}, \mathcal{M}')$ that are constructed by 2D extrusion along $z$-axis and are unbounded along transverse directions on $x$-$y$ plane.
+On assuming the transverse invariance and rotational symmetry, one can reduce the 3D problem to a 1D one along $z$-axis.
+All the D.o.F.
+are now defined at the locations that are the projections of their original locations.
+For instance, an edge that is orthogonal to $z$-axis projects to a vertex while an edge parallel to $z$-axis projects to an edge.
+The procedure is sketched in Fig.
+\ref{}.
+
+\begin{remark}
+    The 1D reduction of the FVM-FIT discretization can be interpreted in the sense of finite difference. 
+\end{remark}
+
+In \cite{degond_2012}, the authors consider a 1D Maxwell-Euler system by assuming vanishing traverse derivatives.
 Besides, $u_y, E_y, B_x, B_z$ are set zero for simplicity, which amounts to considering the TE mode.
-The collision between particles is omitted for the time being.
-
-Take all the traverse derivatives $\partial_x, \partial_y$ and $u_y, E_y, B_x, B_z$ to be zero, we get the one-fluid Euler-Maxwell system in 1D:
+The 1D reduced Maxwell-Euler system and its quasi-neutral limit are
+
+\vspace{-0.3cm}
+\begin{minipage}{0.6\textwidth}
     \begin{align*}
@@
         \lambda^2 \partial_t E_z &= nu_z, \\
-    \lambda^2 \partial_z E_z &= 1 - n,
+        \lambda^2 \partial_z E_z &= 1 - n.
     \end{align*}
-as well as the quasi-neutral limit by taking $\lambda \rightarrow 0$:
+\end{minipage}
+$\xrightarrow[]{\lambda \rightarrow 0}$
+\begin{minipage}{0.3\textwidth}
     \begin{align*}
-    n &= 1\\
+        n &= 1,\\
         \varepsilon^2 \partial_t(u_x) &= - E_x, \\
         E_z + u_xB_y &= 0, \\
-    u_z &= 0 \\
+        u_z &= 0, \\
         \partial_t B_y + \partial_z E_x &= 0, \\
-    \partial_z B_y &= nu_x
+        \partial_z B_y &= nu_x.
     \end{align*}
-\subsubsection{Finite difference on staggered grid}
-\todo{Add illustration about 1D FDTD}
-\subsubsection{Semi-implicit AP time-stepping}
-Adapt the AP scheme (\ref{equ:maxwell_faraday_ap}) to (\ref{equ:euler_ap}) to this case, and we end up with
-\begin{align}
-    \frac{n^{m+1}_k - n^m_k}{\delta^m} + \frac{\textcolor{blue}{f^{m+1/2}_{n,k+1/2} - f^{m+1/2}_{n,k-1/2}}}{h} &= 0, \label{equ:1f1d-n}\\
-    \frac{(nu_x)^{m+1}_k - (nu_x)^m_k}{\delta^m} + \frac{f^{m}_{u_x,k+1/2} - f^{m}_{u_x,k-1/2}}{h} &= -\frac{n^m_k \textcolor{blue}{E^{m+1}_{x,k}}}{\varepsilon^2} + \frac{n^m_k u^m_{z,k}\Tilde{B}^m_{y,k}}{\varepsilon^2}, \label{equ:1f1d-nux}\\
-    \frac{(nu_z)^{m+1}_k - (nu_z)^m_k}{\delta^m} + \frac{f^{m}_{u_z,k+1/2} - f^{m}_{u_z,k-1/2}}{h} &= - \frac{n^m_k \textcolor{blue}{\Tilde{E}^{m+1}_{z,k}}}{\varepsilon^2} - \frac{n^m_k u^m_{x,k}\Tilde{B}^m_{y,k}}{\varepsilon^2}, \label{equ:1f1d-nuz}\\
-    \frac{B^{m+1}_{y,k+1/2} - B^{m}_{y,k+1/2}}{\delta^m} + \frac{\textcolor{blue}{E^{m+1}_{x,k+1} - E^{m+1}_{x,k}}}{h} &= 0, \label{equ:1f1d-By}\\
-    \lambda^2 \frac{E^{m+1}_{x,k} - E^{m}_{x,k}}{\delta^m} + \frac{\textcolor{blue}{B^{m+1}_{y,k+1/2} - B^{m+1}_{y,k-1/2}}}{h} &= \textcolor{blue}{(nu_x)^{m+1}_k}, \label{equ:1f1d-Ex}\\
-    \lambda^2 \frac{E^{m+1}_{z,k+1/2} - E^{m}_{z,k+1/2}}{\delta^m} &= \textcolor{blue}{f^{m+1}_{n,k+1/2}}, \label{equ:1f1d-Ez}
-\end{align}
+\end{minipage}
+where the subscript indicates the direction of the component.
+
+\subsubsection{1D plasma fully-discrete model}
+The following fully-discrete scheme is proposed in \cite{degond_2012}.
+The spatial discretization can be interpreted by the 1D projection procedure illustrated above.
+Here we want to discuss the time discretization with a focus on its semi-implicitness.
+The scheme is built on a uniform 1D mesh with cell size $h$ and evolves the system with time step $\delta^m$:
+\begin{align*}
+    \frac{n^{m+1}_k - n^m_k}{\delta^m} + \frac{\textcolor{blue}{f^{m+1/2}_{n,k+1/2} - f^{m+1/2}_{n,k-1/2}}}{h} &= 0, \\
+    \frac{(nu_x)^{m+1}_k - (nu_x)^m_k}{\delta^m} + \frac{f^{m}_{u_x,k+1/2} - f^{m}_{u_x,k-1/2}}{h} &= -\frac{n^m_k \textcolor{blue}{E^{m+1}_{x,k}}}{\varepsilon^2} + \frac{n^m_k u^m_{z,k}\Tilde{B}^m_{y,k}}{\varepsilon^2},\\
+    \frac{(nu_z)^{m+1}_k - (nu_z)^m_k}{\delta^m} + \frac{f^{m}_{u_z,k+1/2} - f^{m}_{u_z,k-1/2}}{h} &= - \frac{n^m_k \textcolor{blue}{\Tilde{E}^{m+1}_{z,k}}}{\varepsilon^2} - \frac{n^m_k u^m_{x,k}\Tilde{B}^m_{y,k}}{\varepsilon^2}, \\
+    \frac{B^{m+1}_{y,k+1/2} - B^{m}_{y,k+1/2}}{\delta^m} + \frac{\textcolor{blue}{E^{m+1}_{x,k+1} - E^{m+1}_{x,k}}}{h} &= 0, \\
+    \lambda^2 \frac{E^{m+1}_{x,k} - E^{m}_{x,k}}{\delta^m} + \frac{\textcolor{blue}{B^{m+1}_{y,k+1/2} - B^{m+1}_{y,k-1/2}}}{h} &= \textcolor{blue}{(nu_x)^{m+1}_k}, \\
+    \lambda^2 \frac{E^{m+1}_{z,k+1/2} - E^{m}_{z,k+1/2}}{\delta^m} &= \textcolor{blue}{f^{m+1}_{n,k+1/2}}, 
+\end{align*}
 where 
@@
 \end{equation*}
-is the consequence of interpolation of electromagnetic field, 
-and the fluxes read
+are the averaged electromagnetic fields, and the fluxes read
 \begin{align*}
@@
 \end{align*}
-
-\subsection{Discretization in 3D}
-\subsubsection{Primal-dual staggered mesh}
-
-\subsubsection{Discrete Maxwell equations: DEC}
-\todo{Reformulate this section in the spirit of DEC. Now it is a bit tedious.}
-
-\subsubsection{Discrete boundary conditions}
-Dirichlet BCs lead to setting corresponding DoFs at boundary to zero. Vanishing tangential curl is treated by introducing a boundary potential. 
-\todo{More details.}
-\subsubsection{Stabilization in insulating domain}
-We repeat the dilemma again: the scheme fails for $\lambda \rightarrow 0$. The Maxwell system in $\Omega_I$ is    
+According to the linearized stability analysis in \cite{degond_2012}, the implicitness of the Lorentz force and the Maxwell equations is essential to the stability in the quasi-neutral limit.
+Besides, the mass flux in the mass conservation equation and the current in Amp\`{e}re's law have the same degree of implicitness in order to guarantee the consistency with the Gauss law.
+The implicit terms are highlighted in blue color.
+
+\subsection{Semi-implicit Fully-discrete AP Scheme in 3D}
+
 \begin{align}
-    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:ex_1}\\ 
-    \lambda^2 \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= 0,  \label{equ:ex_2}\\
-    \nabla \cdot \mathbf{B} &= 0, \label{equ:ex_3}\\
-    \lambda^2 \nabla \cdot \mathbf{D} &= 0 \label{equ:ex_4}.
-\end{align}
-In non-neutral regime, namely $\lambda = \mathcal{O}(1)$, the Maxwell system in $\Omega_I$ is well-posed and Gauss's laws (\ref{equ:ex_3}) (\ref{equ:ex_4}) are redundant.
-Therefore, they are \emph{implicitly} satisfied (up to numerical errors) in the scheme.
-Nonetheless, the quasi-neutral limit $\lambda \rightarrow 0$ dismisses the implicit fulfillment of Gauss's law for electric field (\ref{equ:ex_4}) through Amper\`{e}'s law (\ref{equ:ex_2}).
-A crucial observation is that formally letting $\lambda \rightarrow 0$ makes (\ref{equ:ex_4}) degenerate, but the divergence-free condition of $\mathbf{D}$-field is always satisfied since the system is divergent as $\lambda \rightarrow 0$ [cite something].
-
-The remedy is to \emph{explicitly} include the divergence-free constraint in the scheme for any value of $\lambda$:  
-\begin{align}
-    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:ex_5}\\ 
-    \lambda^2 \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= 0,  \label{equ:ex_6}\\
-    \nabla \cdot \mathbf{D} &= 0 \label{equ:ex_7}.
-\end{align}
-
-With the divergence-free constraint (\ref{equ:ex_7}), we have more equations than unknowns, which can be resolved by introducing a Lagrange multiplier $p$ as follows:
-\begin{align}
-    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:ex_8}\\ 
-    \lambda^2 \partial_t \mathbf{D} - \nabla \times \mathbf{H} + \colorbox{orange!20}{$\nabla p$} &= 0,  \label{equ:ex_9}\\
-    \nabla \cdot \mathbf{D} &= 0 \label{equ:ex_10},
-\end{align}
-supplemented with the boundary condition $p = 0$ on $\partial\Omega_I$.
-One can check that (\ref{equ:ex_8})-(\ref{equ:ex_10}) are equivalent to (\ref{equ:ex_5})-(\ref{equ:ex_7}) by verifying that $p = 0$ in $\Omega_I$.
-This is done by taking the divergence of (\ref{equ:ex_9}) such that the Laplace equation of $p$ with zero Dirichlet boundary condition gives vanishing $p$.
-
-\todo{The following part should be put after the full discretization is presented.}
-
-The discretization of the Maxwell system in the insulating domain then becomes
-\begin{align*}
-    \delta_m^{-1} (\mathbf{b}^{m+1} - \mathbf{b}^m) + \mathbb{C}\mathbf{e}^{m+1} &= 0, \\
-    \lambda^2\delta_m^{-1} (\Tilde{\mathbf{d}}^{m+1} - \Tilde{\mathbf{d}}^m) - \Tilde{\mathbb{C}}\Tilde{\mathbf{h}}^{m+1} + \colorbox{orange!20}{$\mathbb{H} \mathbb{G} \mathbf{p}^{m+1}$} &= 0 \\
-    \Tilde{\mathbb{D}} \Tilde{\mathbf{d}}^{m+1} &= 0.
-\end{align*}
-where $\mathbb{H}$ is the discrete Hodge operator (matrix\footnote{In our case where the orthogonal mesh pair is used, it is diagonal.}) responsible for transforming any primal-edge-integrated variables to dual-face-integrated ones; the vector $\mathbf{p}$ is the discrete representation of $p$ and is defined on primal vertices lying in $\Omega_I$.
-
-\subsubsection{Semi-implicit AP schemes}
-In this section, we present the full discretization with AP property.
-The general approach for spatial discretizations of both the Euler and Maxwell's equations has been introduced in chapter \ref{chap:discretization_euler_maxwell}.
-As stability is a central issue for the AP property, this section is mostly devoted to the time discretization of the Euler-Maxwell system.
-
-We want to first recall the objective of AP schemes and make clear the direction to proceed towards.
-By definition \ref{def:ap}, the stability condition that does not depend on $\lambda$ and the consistency of the limit scheme with the quasi-neutral system have to be fulfilled.
-Furthermore, what is desired for the numerical treatment of Maxwell's equations is that Gauss's law is satisfied at the discrete level.
-To sum up, the following properties of the constructed scheme are to be realized:
-
-\begin{itemize}
-    \item[I] stable regardless of the value of $\lambda$;
-    \item[II] the limit scheme by taking $\lambda = 0$ is valid\footnote{By ``valid" we mean the scheme is a valid recursion such that the state at $t^{m+1}$ can be \emph{uniquely} computed by that at $t^m$.} and consistent to its continuous counterpart (\ref{equ:maxwell_faraday_limit}) to (\ref{equ:maxwell_gauss_D_limit});
-    \item[III] Gauss's law (\ref{equ:maxwell_gauss_D_rescaled}) is fulfilled at the discrete level for any $\lambda$. \label{condition3}
-\end{itemize}
-
-Given the mesh pair $(\mathcal{M}, \Tilde{\mathcal{M}})$, Maxwell's equations are handled by the FIT framework while FVM is applied to Euler equations on the dual mesh 
-$\Tilde{\mathcal{M}}$.
-Naturally extending the AP scheme for 1D two-fluid plasma proposed in \cite{degond_2012} to which the detailed constructing procedure should be referred, we straightforwardly present the full-discretization scheme for 3D multi-species plasma:
-
-\begin{align}
-    \delta_m^{-1} (\mathbf{b}^{m+1} - \mathbf{b}^{m}) \hspace{0.4cm}&\;+\; \hspace{1.5cm}\mathbb{C}\textcolor{blue}{\mathbf{e}^{m+1}}\hspace{1.25cm}=\; 0, \label{equ:maxwell_faraday_ap}\\
-    \lambda^2\delta_m^{-1}(\mathbf{d}^{m+1} - \mathbf{d}^m) \hspace{0.4cm}&\;-\; \hspace{1.5cm}\Tilde{\mathbb{C}}\textcolor{blue}{\mathbf{h}^{m+1}} \hspace{1.22cm}=\; - \textcolor{blue}{\mathbf{j}^{m+1}}, \label{equ:maxwell_ampere_ap}\\
-    \delta_m^{-1}(\mathbf{U}_{*,k}^{m+1} - \mathbf{U}_{*,k}^{m}) \hspace{0.10cm}&\;+\;  \frac{1}{|\Tilde{V}_k|}\sum_{j:\Tilde{A}_j\in\partial\Tilde{V}_k}|\Tilde{A}_j|\textcolor{blue}{\overline{\mathbf{F}}_{*,j}^{m+1/2}} \hspace{0.05cm}=\; \textcolor{blue}{\mathbf{RHS}_{*,k}^{m+1/2}}, \label{equ:euler_ap}
+    \left[\delta_m^{-1} (\mathbf{b}^{m+1} - \mathbf{b}^{m}) + \mathbb{C}\textcolor{blue}{\mathbf{e}^{m+1}} = \mathbf{0} \right]_i,\ \ &\forall i:A_i \subset \Omega, \label{equ:maxwell_faraday_ap}\\
+    \left[\lambda^2\delta_m^{-1}(\mathbf{d}^{m+1} - \mathbf{d}^m)- \Tilde{\mathbb{C}}\textcolor{blue}{\mathbf{h}^{m+1}} = - \textcolor{blue}{\Sigma_\ast q_\ast \mathbf{F}^{n,m+1}_{\ast}}\right]_i,\ \ &\forall i:\Tilde{A}\subset\Omega_P, \\
+    \left[\lambda^2\delta_m^{-1}(\mathbf{d}^{m+1} - \mathbf{d}^m)- \Tilde{\mathbb{C}}\textcolor{blue}{\mathbf{h}^{m+1}} + \mathbb{H}\mathbb{G}\textcolor{blue}{\mathbf{p}^{m+1}} = \mathbf{0} \right]_i,\ \ &\forall i:\Tilde{A}\subset\Omega_I, \label{equ:maxwell_ampere_ap}\\
+    \left[\mathbb{D}\textcolor{blue}{\mathbf{d}^{m+1}} = \mathbf{0}\right]_i, \ \ &\forall i : \Tilde{V}_i \subset \Omega_I, \\
+    \left[\delta_m^{-1}(\mathbf{U}_{*}^{m+1} - \mathbf{U}_{*}^{m}) + \mathbb{\Tilde{V}}^{-1}\mathbb{\Tilde{D}}\textcolor{blue}{\mathbf{F}_\ast^{m+1/2}} = \textcolor{blue}{\mathbf{RHS}_\ast^{m+1/2}} \right]_i,\ \ &\forall i : \Tilde{V}_i \subset \Omega_P, \label{equ:euler_ap}
 \end{align}

### 2022-10-25 paper_version/main.tex
Polish until the end. First version of the draft.

@@
 \usepackage{authblk}
+\usepackage{soul}
 
@@
 
+\newcommand{\mycolorbox}[2]{\colorbox{#1}{$\displaystyle#2$}}
 \newcommand{\todo}[1]{\textcolor{blue}{\fbox{\textbf{TODO: #1}}}}
@@
     \partial_t
-    \begin{bmatrix}
+    \begin{pmatrix}
     n_* \\
@@
     m_*n_* e_*
-    \end{bmatrix}
+    \end{pmatrix}
     + \nabla \cdot
-    \begin{bmatrix}
+    \begin{pmatrix}
     n_* \mathbf{u}_* \\
@@
     m_*n_* h_* \mathbf{u}_*
-    \end{bmatrix}
+    \end{pmatrix}
     =
-    \begin{bmatrix}
+    \begin{pmatrix}
     0 \\
@@
     \mathbf{J}_* \cdot \mathbf{E}
-    \end{bmatrix}
+    \end{pmatrix}
     +
-    \begin{bmatrix}
+    \begin{pmatrix}
     \Gamma_* \\
@@
     Q_*
-    \end{bmatrix}.
+    \end{pmatrix}.
 \end{align}
@@
     n_* e_*
-    \end{bmatrix}
+    \end{pmatrix}
     + \nabla \cdot
-    \begin{bmatrix}
+    \begin{pmatrix}
     \zeta n_* \mathbf{u}_* \\
@@
     \zeta n_* h_* \mathbf{u}_*
-    \end{bmatrix}
+    \end{pmatrix}
     &=
-    \begin{bmatrix}
+    \begin{pmatrix}
     0 \\
@@
     \zeta \eta \varepsilon_*^{-2} \mathbf{J}_* \cdot \mathbf{E}
-    \end{bmatrix} +
-    \begin{bmatrix}
+    \end{pmatrix} +
+    \begin{pmatrix}
     0 \\
@@
     \varepsilon_*^{-2}Q_*^{\text{coll}} \\
-    \end{bmatrix}, \label{equ:euler_rescalling}
+    \end{pmatrix}, \label{equ:euler_rescalling}
 \end{align}
@@
     n_* e_*
-    \end{bmatrix}
+    \end{pmatrix}
     + \nabla \cdot
-    \begin{bmatrix}
+    \begin{pmatrix}
     n_* \mathbf{u}_* \\
@@
     n_* h_* \mathbf{u}_*
-    \end{bmatrix}
+    \end{pmatrix}
     &=
-    \begin{bmatrix}
+    \begin{pmatrix}
     0 \\
@@
     \varepsilon_*^{-2} \mathbf{J}_* \cdot \mathbf{E}
-    \end{bmatrix}+
-    \begin{bmatrix}
+    \end{pmatrix}+
+    \begin{pmatrix}
     0 \\
@@
     \varepsilon_*^{-2}Q_*^{\text{coll}} 
-    \end{bmatrix}, \label{equ:euler_rescaled}
+    \end{pmatrix}, \label{equ:euler_rescaled}
 \end{align}
@@
 
-We consider a simply connected domain $\Omega$ that is decomposed into two sub-domains $\Omega_P$ and $\Omega_I$ representing plasma domain and insulating domain respectively.
-We use the notation $\Gamma_C := \partial\Omega \cap \partial\Omega_P$, denoting the contact boundary, and $\Gamma_I := \partial\Omega \cap \partial\Omega_I$ for the insulating boundary which an artificial cut-off boundary.
-The interface between the two domains is denoted by $\Gamma_W = \partial\Gamma_I \cap \partial\Gamma_P$.
-A geometric arrangement corresponding to his setting is visualized in Fig.
-\ref{fig:domain_sketch}.
+We consider a simply connected domain $\Omega$ that is decomposed into two sub-domains $\Omega_P$ and $\Omega_N$ representing plasma domain and non-conducting domain respectively.
+We use the notation $\Gamma_C := \partial\Omega \cap \partial\Omega_P$, denoting the contact boundary, and $\Gamma_I := \partial\Omega \cap \partial\Omega_N$ for the insulating boundary which an artificial cut-off boundary.
+The interface between the two domains is denoted by $\Gamma_W = \partial\Omega_I \cap \partial\Omega_P$.
+A geometric arrangement corresponding to this setting is visualized in Fig.
+\ref{fig:domain_sketch} and is the one used in \cite[][ch.
+1, sec.
+4]{fuchs_2021}.
 
@@
 The insulating boundary blocks the energy interchange and therefore only admits zero electric and magnetic flux, in the sense that $\text{curl}\mathbf{E}\cdot \mathbf{n} = 0$ and $\text{curl}\mathbf{H}\cdot \mathbf{n} = 0$ where $\mathbf{n}$ is the outer normal vector.
-\todo{A few works on ECE BC?}
+\todo{ECE BC}
 \begin{figure}
@@
         \coordinate (B4) at (6,-1.5);
-        \draw[violet] (A2) -- node[above]{\color{gray}Insulating domain $\Omega_I$} node[black, below]{\textcolor{violet}{$\Gamma_W$}} (B2);
-        \draw[violet] (A3) -- node[below]{\color{gray}Insulating domain $\Omega_I$} node[black, above]{\textcolor{violet}{$\Gamma_W$}} (B3);
+        \draw[violet] (A2) -- node[above]{\color{gray}Non-conducting domain $\Omega_N$} node[black, below]{\textcolor{violet}{$\Gamma_W$}} (B2);
+        \draw[violet] (A3) -- node[below]{\color{gray}Non-conducting domain $\Omega_N$} node[black, above]{\textcolor{violet}{$\Gamma_W$}} (B3);
         \draw[very thick] (A2) -- (A1) -- node[above]{$\Gamma_I$}  (B1) -- (B2);
@@
     \begin{align*}
-    \Phi = \Phi^\pm(t)\ \ &\text{on} \ \ \Gamma_C^\pm, \\
+    \Phi = \Phi(t)\ \ &\text{on} \ \ \Gamma_C, \\
     \text{curl} \mathbf{E} \cdot \mathbf{n} = 0\ \ &\text{on} \ \  \Gamma_I,  \\
@@
 \subsection{Reformulation} \label{sec:reform_continuous}
-In the insulating domain $\Omega_I$ (see Fig.
-\ref{fig:sketch_domain}), the Euler system is not defined there due to the absence of plasmas.
-Consequently, the Maxwell system in $\Omega_I$ is described by
+In the non-conducting domain $\Omega_N$ (see Fig.
+\ref{fig:domain_sketch}), the Euler system is not defined there due to the absence of plasmas.
+Consequently, the Maxwell system in $\Omega_N$ is described by
 \begin{subequations}
@@
 
-In non-neutral regime where $\lambda = \mathcal{O}(1)$, the Maxwell system in $\Omega_I$ is well-posed and Gauss's laws (\ref{equ:gauss_B_ins}) (\ref{equ:gauss_D_ins}) are redundant as long as they are satisfied at initial moment.
+In non-neutral regime where $\lambda = \mathcal{O}(1)$, the Maxwell system in $\Omega_N$ is well-posed and Gauss's laws (\ref{equ:gauss_B_ins}) (\ref{equ:gauss_D_ins}) are redundant as long as they are satisfied at initial moment.
 Nonetheless, as the system approaches the quasi-neutral limit as $\lambda \rightarrow 0$, Gauss's law for $\mathbf{D}$-field (\ref{equ:gauss_D_ins}) becomes degenerate.
@@
 
-To see this issue from another perspective, we observe the limit Maxwell system in $\Omega_I$
+To see this issue from another perspective, we observe the limit Maxwell system in $\Omega_N$
 \begin{subequations}
@@
 
-We propose the following reformulation as a remedy, which introduces a Lagrange multiplier $p$ and removes the $\lambda^2$ prefactor in Gauss's law for $\mathbf{D}$-field:
+We propose the following reformulation as a remedy, which introduces a Lagrange multiplier $\psi$ and removes the $\lambda^2$ prefactor in Gauss's law for $\mathbf{D}$-field:
 \begin{subequations}
@@
     \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:faraday_ins_reform}\\ 
-    \lambda^2 \partial_t \mathbf{D} - \nabla \times \mathbf{H} + \colorbox{orange!20}{$\nabla p$} &= 0,  \label{equ:ampere_ins_reform}\\
+    \lambda^2 \partial_t \mathbf{D} - \nabla \times \mathbf{H} + \colorbox{orange!20}{$\nabla \psi$} &= 0,  \label{equ:ampere_ins_reform}\\
     \nabla \cdot \mathbf{B} &= 0, \label{equ:gauss_B_ins_reform}\\
@@
 
-Supplemented with the boundary condition $p = 0$ on $\partial\Omega_I$, one can check that (\ref{equ:faraday_ins_reform}) to (\ref{equ:gauss_D_ins_reform}) are equivalent to the original formulation (\ref{equ:faraday_ins})-(\ref{equ:gauss_D_ins}) by verifying that $p = 0$ in $\Omega_I$.
-This is done by taking the divergence of (\ref{equ:ampere_ins_reform}) such that the Laplace equation of $p$ with zero Dirichlet boundary condition gives vanishing $p$.
+Supplemented with the boundary condition $\psi = 0$ on $\partial\Omega_N$, one can check that (\ref{equ:faraday_ins_reform}) to (\ref{equ:gauss_D_ins_reform}) are equivalent to the original formulation (\ref{equ:faraday_ins})-(\ref{equ:gauss_D_ins}) by verifying that $\psi = 0$ in $\Omega_N$.
+This is done by taking the divergence of (\ref{equ:ampere_ins_reform}) such that the Laplace equation of $\psi$ with zero Dirichlet boundary condition gives vanishing $\psi$.
 The importance of this reformulation will be make clear in the numerical experiment.
@@
 
-\section{Spatial Discretization}
+\section{Spatial Discretization} \label{sec:spatial_discretization}
 \subsection{Primal-dual Staggered Meshes}
@@
 
+\begin{remark}
+    In the implementation, it always provides convenience to index a pair of corresponding primal and dual elements with the same number.
+For instance, a primal face $A_k$ is penetrated by the dual edge $\Tilde{L}_k$.
+In the following discussion, we stick to this convention, which would simplify our notation.
+\end{remark}
+
 The material laws (\ref{equ:material_law}) need to be reformulated within this framework.
@@
     \begin{align*}
-    \varphi = \varphi^\pm(t)\ \ &\text{on} \ \ \Gamma_C^\pm, \\
+    \varphi = \Phi(\mathbf{x}, t)\ \ &\text{on} \ \ \Gamma_C, \\
     \text{curl} \mathbf{E} \cdot \mathbf{n} = 0\ \ &\text{on} \ \  \Gamma_I,  \\
@@
             \begin{align}
-            \varphi_i = \Phi^\pm(t), \ \ &\forall i : P_i \subset \Gamma_C^\pm, \label{equ:bc_1}\\
+            \varphi_i = \Phi(P_i, t), \ \ &\forall i : P_i \subset \Gamma_C, \label{equ:bc_1}\\
             e_i = (\mathbb{G}\bm{\varphi})_i,\ \ &\forall i : L_i \subset \partial\Omega, \label{equ:bc_2}\\
@@
 \subsubsection{Reformulation} \label{sec:reform_discrete}
-In Section \ref{sec:reform_continuous}, we propose the stabilization of the Maxwell system in the insulating domain $\Omega_I$ by introducing a Lagrange multiplier.
-In the semi-discrete level, the equations to be solved in $\Omega_I$ are
+In Section \ref{sec:reform_continuous}, we propose the stabilization of the Maxwell system in the non-conducting domain $\Omega_N$ by introducing a Lagrange multiplier.
+In the semi-discrete level, the equations to be solved in $\Omega_N$ are
 \begin{subequations}
@@
         \dot{\mathbf{b}} + \mathbb{C}\mathbf{e} &= \mathbf{0} ,\\
-        \dot{\mathbf{d}} - \Tilde{\mathbb{C}}\mathbf{h} + \colorbox{orange!20}{$\mathbb{H} \mathbb{G} \mathbf{p}$}&= \mathbf{0},\\
+        \dot{\mathbf{d}} - \Tilde{\mathbb{C}}\mathbf{h} + \colorbox{orange!20}{$\mathbb{H} \mathbb{G} \bm{\psi}$}&= \mathbf{0},\\
         \Tilde{\mathbb{D}}\mathbf{d} &= \mathbf{0} \label{equ:discrete_zero_div}, 
@@
 
-where $\mathbf{p} = (p_i)_i$ denotes the scalar $p$ assigned to each primal vertex in $\Omega_I$ and the matrix $\mathbb{H}_{i,i} = \frac{|\Tilde{A}_i|}{|L_i|}$ transforms primal edge integrals to dual face fluxes\footnote{$\mathbb{H}$ functions as a discrete Hodge operator.}.
-To incorporate the zero Dirichlet BC, we limit the unknowns $(p_i)_{i=1}^{N^{\Omega^\circ_I}_P}$ to primal vertices in the interior of $\Omega_I$.
+where $\bm{\psi} = (\psi_i)_i$ denotes unknowns assigned to each primal vertex in $\Omega_N$ and the matrix $\mathbb{H}_{i,i} = \frac{|\Tilde{A}_i|}{|L_i|}$ transforms primal edge integrals to dual face fluxes\footnote{$\mathbb{H}$ functions as a discrete Hodge operator.}.
+To incorporate the zero Dirichlet BC, we limit the unknowns $(\psi_i)_{i=1}^{N^{N,\circ}_P}$ to primal vertices in $\Omega_N^\circ$.
 
@@
     \#\  \text{primal cell}\ \  &N_V \\
-    \#\  \text{primal edge}\ \  &N_L := \underbrace{N^+_L + N^-_L + N^I_L}_{N^\partial_L} + N^\circ_L  \\
-    \#\  \text{primal face}\ \  &N_A := \underbrace{N_A^+ + N_A^- + N^I_A}_{N^\partial_A} + N^\circ_A  \\
-    \#\  \text{primal vertex}\ \  &N_P := \underbrace{N_P^+ + N_P^- + N^I_P}_{N^\partial_P} + N^\circ_P \\
+    \#\  \text{primal edge}\ \  &N_L := \underbrace{N^C_L + N^I_L}_{N^\partial_L} + N^\circ_L  \\
+    \#\  \text{primal face}\ \  &N_A := \underbrace{N_A^C + N^I_A}_{N^\partial_A} + N^\circ_A  \\
+    \#\  \text{primal vertex}\ \  &N_P := \underbrace{N_P^C + N^I_P}_{N^\partial_P} + N^\circ_P \\
     \#\  \text{dual cell}\ \  &N_{\Tilde{V}} := N_P \\
@@
 \end{align*}
-where the superscripts $\pm, I, \partial, \circ$ indicate that the elements lying in $\gamma^\pm, \gamma^I, \partial\Omega, \Omega^\circ$ respectively .
+where the superscript indicates the locations where the elements lie.
 The equations $N^\partial_{\Tilde{L}} = N^\partial_L, N^\partial_{\Tilde{A}} = N^\partial_P$, revealing the bijective relation between the boundary primal elements and auxiliary elements, can be check easily by inspecting Fig.
@@
      \hline
-     \textbf{D.o.F.}  & \textbf{Meaning}  & \textbf{Size} \\
-     \hline\hline
+     D.o.F.  & Meaning  & Size \\
+     \hline
      $\mathbf{e}$ & line integrals of $\mathbf{E}$-field at primal edges $L$& $N_L$ \\
@@
      $\mathbf{d}$ & surface integrals of $\mathbf{D}$-field at dual faces $\Tilde{A}$ & $N_{\Tilde{A}}$ \\
-     $\mathbf{p}$ & Lagrange multiplier at primal vertices $P$ in $\Omega_I^\circ$ & $N^{\Omega_I^\circ}_P$\\ 
+     $\bm{\psi}$ & Lagrange multiplier at primal vertices $P$ in $\Omega_N^\circ$ & $N^{N,\circ}_P$\\ 
      \hline
@@
     \text{discrete material laws (\ref{equ:alg_material_magnetic})(\ref{equ:alg_material_electric})} \ \ &\longrightarrow\ \  N_A + N_L \ \ \text{equations} \\
-    \text{boundary condition (\ref{equ:bc_1})} \ \ &\longrightarrow\ \  N_P^+ + N_P^- \ \ \text{equations} \\
+    \text{boundary condition (\ref{equ:bc_1})} \ \ &\longrightarrow\ \  N_P^C \ \ \text{equations} \\
     \text{boundary condition (\ref{equ:bc_2})} \ \ &\longrightarrow\ \  N_L^\partial \ \ \text{equations} \\
     \text{boundary condition (\ref{equ:bc_3})} \ \ &\longrightarrow\ \  N_{\Tilde{A}}^I \ \ \text{equations}. \\
-    \text{vanishing divergence constraint (\ref{equ:discrete_zero_div})} \ \ &\longrightarrow\ \  N_P^{\Omega^\circ_I} \ \ \text{equations}. \\
+    \text{vanishing divergence constraint (\ref{equ:discrete_zero_div})} \ \ &\longrightarrow\ \  N_P^{N,\circ} \ \ \text{equations}. \\
 \end{align*}
@@
 \begin{align*}
-    \#\text{ of unknowns} &= \colorbox{violet!20}{$N_L$} + \colorbox{blue!20}{$N_A$} + \colorbox{gray!40}{$N_{\Tilde{L}}$} + \colorbox{orange!20}{$N_{\Tilde{A}}$} + \colorbox{green!20}{$N_P^\partial$} + \colorbox{yellow!40}{$N_P^{\Omega^\circ_I}$}, \\
-    \#\text{ of equations} &= \colorbox{blue!20}{$N_A$} + \colorbox{orange!20}{$N_{\Tilde{A}}$} + \colorbox{gray!40}{$N_A$} + \colorbox{violet!20}{$N_L$} + \colorbox{gray!40}{$N_L^\partial$} + \colorbox{green!20}{$N_P^+ + N_P^- + N_P^I$}+ \colorbox{yellow!40}{$N_P^{\Omega^\circ_I}$},
+    \#\text{ of unknowns} &= \colorbox{violet!20}{$N_L$} + \colorbox{blue!20}{$N_A$} + \colorbox{gray!40}{$N_{\Tilde{L}}$} + \colorbox{orange!20}{$N_{\Tilde{A}}$} + \colorbox{green!20}{$N_P^\partial$} + \colorbox{yellow!40}{$N_P^{N,\circ}$}, \\
+    \#\text{ of equations} &= \colorbox{blue!20}{$N_A$} + \colorbox{orange!20}{$N_{\Tilde{A}}$} + \colorbox{gray!40}{$N_A$} + \colorbox{violet!20}{$N_L$} + \colorbox{gray!40}{$N_L^\partial$} + \colorbox{green!20}{$N_P^C + N_P^I$}+ \colorbox{yellow!40}{$N_P^{N,\circ}$},
 \end{align*}
@@
 To rewrite (\ref{equ:fvm}) into a matrix form, by abuse of notation we stack all the cell average $(\overline{\mathbf{U}}_i)_i$ into a matrix $\mathbf{U} \in \mathbb{R}^{N_{\Tilde{V}}^P \times m}$ with $\mathbf{U}_{i,:} = \overline{\mathbf{U}}_i$.
-Meanwhile, we denote by $\mathbf{F} \in \mathbb{R}^{N_{\Tilde{A}}^P \times m}$ the collection of the (total) numerical fluxes, namely $\mathbf{F}_{i,:} = |A_i|\mathbf{f}^\text{num}_i$.
+Meanwhile, we denote by $\mathbf{F} \in \mathbb{R}^{N_{\Tilde{A}}^P \times m}$ the collection of the (total) numerical fluxes, namely $\mathbf{F}_{i,:} = \mathbf{f}^\text{num}_i$.
 In the same way, we denote by $\mathbf{RHS}\in \mathbb{R}^{N_{\Tilde{V}}^P \times m}$ the collection of $\overline{\mathbf{RHS}}_i$.
-Besides, we define the diagonal matrix $\mathbb{\Tilde{V}} \in \mathbb{R}^{N_{\Tilde{V}}^P}$ with $\mathbb{\Tilde{V}}_{i,i} = |\Tilde{V}_i|$.
+Besides, we define the diagonal matrix $\mathbb{\Tilde{V}} \in \mathbb{R}^{N_{\Tilde{V}}^P \times N_{\Tilde{V}}^P}$ and $\mathbb{\Tilde{A}}\in \mathbb{R}^{N_{\Tilde{A}}^P \times N_{\Tilde{A}}^P}$ with $\mathbb{\Tilde{A}}_{i,i} = |\Tilde{A}_i|$.
 Making use of the incidence matrices, we end up with
 \begin{equation*}
-    \dot{\mathbf{U}} + \mathbb{\Tilde{V}}^{-1}\mathbb{\Tilde{D}}\mathbf{F}(\mathbf{U})  = \mathbf{RHS}(\mathbf{U},\mathbf{d},\mathbf{b}),
+    \dot{\mathbf{U}} + \mathbb{\Tilde{V}}^{-1}\mathbb{\Tilde{D}}\mathbb{\Tilde{A}}\mathbf{F}(\mathbf{U})  = \mathbf{RHS}(\mathbf{U},\mathbf{d},\mathbf{b}),
 \end{equation*}
-where the dependence of $\mathbf{RHS}$ on $\mathbf{U}, \mathbf{d}, \mathbf{b}$ is implied by (\ref{equ:euler_rescaled}) and will be elaborated below.
+where the dependence of $\mathbf{RHS}$ on $\mathbf{d}, \mathbf{b}$ is implied by (\ref{equ:euler_rescaled}) and will be elaborated below.
 
@@
     \ \ \ \ 
-    \mathbf{B} = \Tilde{\mathbb{R}}_B\mathbf{b},
+    \mathbf{B} = \Tilde{\mathbb{R}}_B\mathbf{b}, \label{equ:reconstruction}
 \end{equation}
@@
 \subsubsection{Discrete Boundary Conditions}
-The BCs for the Euler system (see Section \ref{sec:BC}) are implemented by the approach of ghost cells \cite[][Chapt.
+The BCs for the Euler system (see Section \ref{sec:BC}) are implemented by the approach of ghost cells \cite[][ch.
 7]{leveque_2007}, namely thinking of extending the domain by a few additional cells and prescribing the variables.
@@
 \begin{equation*}
-    \mathbf{F}_i = |\Tilde{A}_i|{\mathbf{f}^\text{num}}(\mathbf{U}_j, \mathbf{U}_j, \mathbf{n}_i), \ \ \forall i: \Tilde{A}_i \subset \Gamma_C,
+    \mathbf{F}_i = {\mathbf{f}^\text{num}}(\mathbf{U}_j, \mathbf{U}_j, \mathbf{n}_i), \ \ \forall i: \Tilde{A}_i \subset \Gamma_C,
 \end{equation*}
@@
 \begin{equation*}
-    \mathbf{F}_i = |\Tilde{A}_i|\mathbf{f}^\text{num}(\mathbf{U}_j, \hat{\mathbf{U}}_j, \mathbf{n}_i), \ \ \forall i: \Tilde{A}_i \subset \Gamma_W,
+    \mathbf{F}_i = \mathbf{f}^\text{num}(\mathbf{U}_j, \hat{\mathbf{U}}_j, \mathbf{n}_i), \ \ \forall i: \Tilde{A}_i \subset \Gamma_W,
 \end{equation*}
-where the value of the ghost cell $\hat{\mathbf{U}} = [n, n\mathbf{u} - 2(\mathbf{n}\cdot\mathbf{u})\mathbf{n}, ne]^T$ for $\mathbf{U} = [n, n\mathbf{u}, ne]^T$.
+where the value of the ghost cell $\hat{\mathbf{U}} = [n, n\mathbf{u} - 2(\mathbf{n}\cdot\mathbf{u})\mathbf{n}, ne]^T$ reverses the normal velocity of $\mathbf{U} = [n, n\mathbf{u}, ne]^T$.
 
 \subsection{Summary: Spatially Semi-discrete Model}
-We collect all the equations and BCs presented above and make a summary for the spatially semi-discrete Maxwell-Euler system:
+We collect all the equations and BCs presented above and make a summary for the spatially semi-discrete Maxwell-Euler system based on the FIT-FVM framework:
 \begin{subequations}
@@
         [\dot{\mathbf{b}} + \mathbb{C}\mathbf{e} = \mathbf{0}]_i, \ \ &\forall i: A_i \subset \Omega, \\
-        [\dot{\mathbf{d}} - \Tilde{\mathbb{C}}\mathbf{h} = - \mathbf{j}]_i, \ \ &\forall i: \Tilde{A}_i \subset \Omega_P,\\
-        [\dot{\mathbf{d}} - \Tilde{\mathbb{C}}\mathbf{h} + \mathbb{H} \mathbb{G} \mathbf{p} = - \mathbf{j}]_i, \ \ &\forall i: \Tilde{A}_i \subset \Omega_I,\\
-        [\Tilde{\mathbb{D}}\mathbf{d} = \mathbf{0}]_i,\ \ &\forall i: \Tilde{V}_i \subset \Omega_I, \\
-        [\dot{\mathbf{U}}_\ast + \mathbb{\Tilde{V}}^{-1}\mathbb{\Tilde{D}}\mathbf{F}_\ast = \mathbf{RHS}_\ast]_i,\ \ &\forall i: \Tilde{V}_i \subset \Omega_P, 
+        [\dot{\mathbf{d}} - \Tilde{\mathbb{C}}\mathbf{h} = - \Sigma_{\ast} q_*\bm{f}_{\ast}^{n}]_i, \ \ &\forall i: \Tilde{A}_i \subset \Omega_P,\\
+        [\dot{\mathbf{d}} - \Tilde{\mathbb{C}}\mathbf{h} + \mathbb{H} \mathbb{G} \bm{\psi} = \mathbf{0}]_i, \ \ &\forall i: \Tilde{A}_i \subset \Omega_N,\\
+        [\Tilde{\mathbb{D}}\mathbf{d} = \mathbf{0}]_i,\ \ &\forall i: \Tilde{V}_i \subset \Omega_N, \\
+        [\dot{\mathbf{U}}_\ast + \mathbb{\Tilde{V}}^{-1}\mathbb{\Tilde{D}}\mathbb{\Tilde{A}}\mathbf{F}_\ast = \mathbf{RHS}_\ast]_i,\ \ &\forall i: \Tilde{V}_i \subset \Omega_P, \\
+        [\mathbf{d} = \mathbb{M}_\varepsilon\mathbf{e}]_i,\ \ &\forall i:L_i \subset \Omega,\\
+        [\mathbf{h} = \mathbb{M}_\mu^{-1}\mathbf{b}]_i, \ \ &\forall i:A_i \subset \Omega,
     \end{align}
+    \begin{comment}
         \vspace{-1cm}
@@
             \begin{cases}
-         \Sigma_{\ast} q_*\mathbf{F}_{\ast,i}^\text{n},&\forall i: \Tilde{A}_i \subset \Omega_P, \\
-        0,&\forall i: \Tilde{A}_i \subset \Omega_I,
+             \Sigma_{\ast} q_*\bm{f}_{\ast,i}^{n},&\forall i: \Tilde{A}_i \subset \Omega_P, \\
+            0,&\forall i: \Tilde{A}_i \subset \Omega_N,
             \end{cases}
         \end{align}
-where $\ast$ stands for indices for multiple species and $\mathbf{F}^\text{n}$ denotes the mass flux. We have the following BCs:
+    \end{comment}
+where $\ast \in \{\text{electron}, \text{ion}, \dots\}$ and $\bm{f}^n$ denotes the mass flux.
+By $[\dots]_i$ we mean taking the $i$-th component of both sides of the equation.
+We have the following BCs:
     \begin{align}
-    \varphi_i = \Phi^\pm(t), \ \ &\forall i : P_i \subset \Gamma_C^\pm, \\
+    \varphi_i = \Phi(P_i, t), \ \ &\forall i : P_i \subset \Gamma_C, \\
     e_i = (\mathbb{G}\bm{\varphi})_i,\ \ &\forall i : L_i \subset \partial\Omega, \\
-    (\Tilde{\mathbb{C}} \bm{h})_i = 0,\ \ &\forall i : \Tilde{A}_i \subset \Gamma_I,\\
-    \mathbf{F}_{\ast,i} = |\Tilde{A}_i|\mathbf{f}^\text{num}(\mathbf{U}_{\ast,j}, \mathbf{U}_{\ast,j}, \mathbf{n}_i), \ \ &\forall i: \Tilde{A}_i \subset \Gamma_C, \\
-    \mathbf{F}_{\ast,i} = |\Tilde{A}_i|\mathbf{f}^\text{num}(\mathbf{U}_{\ast,j}, \hat{\mathbf{U}}_{\ast,j}, \mathbf{n}_i), \ \ &\forall i: \Tilde{A}_i \subset \Gamma_W.
+    (\Tilde{\mathbb{C}} \bm{h})_i = 0,\ \ &\forall i : \Tilde{A}_i \subset \Gamma_I, \label{equ:bc_zero_curl_h} \\
+    \mathbf{F}_{\ast,i} = \mathbf{f}^\text{num}(\mathbf{U}_{\ast,j}, \mathbf{U}_{\ast,j}, \mathbf{n}_i), \ \ &\forall i: \Tilde{A}_i \subset \Gamma_C, \\
+    \mathbf{F}_{\ast,i} = \mathbf{f}^\text{num}(\mathbf{U}_{\ast,j}, \hat{\mathbf{U}}_{\ast,j}, \mathbf{n}_i), \ \ &\forall i: \Tilde{A}_i \subset \Gamma_W.
     \end{align}
@@
 \section{Full Discretization}
-On discussing the discretization in space, inthis section we discuss the time-stepping which is strongly related to the AP property since it directly influences the stability of the scheme. 
 \subsection{Motivation: Reduction to 1D Discretization}
@@
 This mental experiment aims to help readers understand how the new 3D scheme originates from the 1D one.
-\subsubsection{Projection to one dimension}
+\subsubsection{Projection to one dimension} \label{sec:projection_to_1d}
 Consider a mesh pair $(\mathcal{M}, \mathcal{M}')$ that are constructed by 2D extrusion along $z$-axis and are unbounded along transverse directions on $x$-$y$ plane.
@@
 The procedure is sketched in Fig.
-\ref{}.
+\ref{fig:1d_reduction}.
+
+\begin{figure}
+    \centering
+    \begin{tikzpicture}[scale=0.4]
+        \def\primalstyle{thick}
+        \def\dualstyle{thick}
+        \coordinate (P0) at (0cm, 0cm);
+        \foreach \i in {1,2,...,6}
+        {
+        \coordinate (P\i) at ({60*\i-30}:2cm);
+        \draw[\primalstyle] (P0) -- (P\i);
+        }
+        \draw[\primalstyle] (P1) -- (P2) node[left=5mm]{\Large $\mathcal{M}$} -- (P3) -- (P4) -- (P5) -- (P6) -- cycle;
+
+        \draw[very thick, -stealth] (-7.5,-1.05) -- (10,1.4) node[right] {$z$-axis};
+        \begin{scope}[shift={(5cm,0.7
+        cm)}]
+            \coordinate (PP0) at (0cm, 0cm);
+            \foreach \i in {1,2,...,6}
+            {
+            \coordinate (PP\i) at ({60*\i-30}:2cm);
+            \draw[gray] (PP0) -- (PP\i);
+            }
+        \end{scope}
+
+        \draw[\primalstyle] (PP1) -- (PP2);
+        \draw[gray] (PP2) -- (PP3);
+        \draw[gray] (PP3) -- (PP4);
+        \draw[gray] (PP4) -- (PP5);
+        \draw[\primalstyle] (PP5) -- (PP6);
+        \draw[\primalstyle] (PP6) -- (PP1);
+
+        \draw[gray] (P0) -- (PP0);
+        \draw[\primalstyle] (P1) -- (PP1);
+        \draw[\primalstyle] (P2) -- (PP2);
+        \draw[gray] (P3) -- (PP3);
+        \draw[gray] (P4) -- (PP4);
+        \draw[\primalstyle] (P5) -- (PP5);
+        \draw[\primalstyle] (P6) -- (PP6);
+
+        \foreach \i in {1,2,...,6}
+        {
+        \coordinate (D\i) at ({60*\i-60}:{2./1.737});
+        }
+        \draw[dashed, blue] (D1) -- (D2) -- (D3) -- (D4) -- (D5) -- (D6) -- cycle;
+        \begin{scope}[shift={(2.5,0.35)}]
+            \foreach \i in {1,2,...,6}
+            {
+            \coordinate (DD\i) at ({60*\i-60}:{2./1.737});
+            }
+        \end{scope}
+        \draw[blue] (DD1) -- (DD2) -- (DD3) -- (DD4) -- (DD5) -- (DD6) -- cycle;
+        \draw[blue] (D1) -- (DD1);
+        \draw[blue] (D2) -- (DD2);
+        \draw[blue] (D3) -- (DD3);
+        \draw[blue] (D4) -- (DD4);
+        \draw[blue] (D5) -- (DD5);
+        \draw[blue] (D6) -- (DD6);
+
+        \begin{scope}[shift={(-2.5,-0.35)}]
+            \foreach \i in {1,2,...,6}
+            {
+            \coordinate (DDD\i) at ({60*\i-60}:{2./1.737});
+            }
+        \end{scope}
+
+        \begin{scope}[shift={(5cm,0.7cm)}]
+            \draw[fill = gray!60, opacity=0.4] (-3,5) -- (3,2) -- (3,-5)  -- (-3,-2) -- cycle; 
+            \draw[thick, violet] (-3,5) -- (3,2) -- (3,-5) -- (-3,-2) -- cycle; 
+            \draw[fill=violet] (0,0) circle (0.2) ;
+            \node[below] (n) at (3,-5) {\textcolor{black}{$z_{k+1}$}};
+        \end{scope}
+        \begin{scope}[shift={(2.5,0.35)}]
+            \draw[fill = gray!40, opacity=0.4] (-3,5) -- (3,2) -- (3,-5) -- (-3,-2) -- cycle; 
+            \draw[thick, red] (-3,5) -- (3,2) -- (3,-5) -- (-3,-2) -- cycle;
+            \draw[fill=red] (0,0) circle (0.2) ;
+            \node[below] (n) at (3,-5) {\textcolor{black}{$z_{k+1/2}$}};
+        \end{scope}
+        \draw[fill = gray!20, opacity=0.4] (-3,5) -- (3,2) -- (3,-5) -- (-3,-2) -- cycle; 
+        \node[below] (n) at (3,-5) {\textcolor{black}{$z_{k}$}};
+        \draw[thick, brown] (-3,5) -- (3,2) -- (3,-5) -- (-3,-2) -- cycle;
+        \draw[fill=brown] (0,0) circle (0.2) ;
+        \draw[blue, ultra thick] (DDD1) -- (DDD2) -- (DDD3) node[left=3mm]{\textcolor{blue}{\Large $\Tilde{\mathcal{M}}$}} -- (DDD4) -- (DDD5) -- (DDD6) -- cycle;
+        \draw[blue, ultra thick] (D1) -- (DDD1);
+        \draw[blue, ultra thick] (D2) -- (DDD2);
+        \draw[blue, ultra thick] (D3) -- (DDD3);
+        \draw[blue] (D4) -- (DDD4);
+        \draw[blue] (D5) -- (DDD5);
+        \draw[blue, ultra thick] (D6) -- (DDD6);
+        \fill[blue!50, opacity=0.2] (D1) -- (D2) -- (D3) -- (D4) -- (D5) -- (D6);
+         \begin{scope}[shift={(-2.5cm,-0.35
+        cm)}]
+            \draw[fill = gray!10, opacity=0.4] (-3,5) -- (3,2) -- (3,-5) -- (-3,-2) -- cycle; 
+            \draw[thick, orange!50] (-3,5) -- (3,2) -- (3,-5) -- (-3,-2) -- cycle; 
+            \draw[fill=orange!50] (0,0) circle (0.2) ;
+            \node[below] (n) at (3,-5) {\textcolor{black}{$z_{k-1/2}$}};
+        \end{scope}
+    \end{tikzpicture}
+    \caption{3D discretization to 1D. On the assumption of transverse invariance, we can reduce all the D.o.F. lying in the plane $z=z_k$ to the vertex at $z=z_k$. }
+    \label{fig:1d_reduction}
+\end{figure}
 
 \begin{remark}
-    The 1D reduction of the FVM-FIT discretization can be interpreted in the sense of finite difference. 
+    The 1D reduction of the FIT-FVM discretization can be interpreted in the sense of finite difference. 
 \end{remark}
@@
         \lambda^2 \partial_t E_z &= nu_z, \\
-        \lambda^2 \partial_z E_z &= 1 - n.
+        \lambda^2 \partial_z E_z &= 1 - n,
     \end{align*}
@@
         \partial_t B_y + \partial_z E_x &= 0, \\
-        \partial_z B_y &= nu_x.
+        \partial_z B_y &= nu_x,
     \end{align*}
 \end{minipage}
-where the subscript indicates the direction of the component.
-
-\subsubsection{1D plasma fully-discrete model}
+where the subscript indicates the direction of the component. Here they consider a isentropic process with the equation of state $p(n) = n^\gamma$.
+
+\subsubsection{1D plasma fully-discrete model} \label{sec:1d_fully_discrete_model}
 The following fully-discrete scheme is proposed in \cite{degond_2012}.
@@
 Here we want to discuss the time discretization with a focus on its semi-implicitness.
-The scheme is built on a uniform 1D mesh with cell size $h$ and evolves the system with time step $\delta^m$:
+From now on, we attach to variables a superscript involving $m$ to indicate the time step.
+The scheme is built on a uniform 1D mesh with cell size $h$ and evolves the system with time step $\delta^m := t^{m+1} - t^m$:
 \begin{align*}
-    \frac{n^{m+1}_k - n^m_k}{\delta^m} + \frac{\textcolor{blue}{f^{m+1/2}_{n,k+1/2} - f^{m+1/2}_{n,k-1/2}}}{h} &= 0, \\
-    \frac{(nu_x)^{m+1}_k - (nu_x)^m_k}{\delta^m} + \frac{f^{m}_{u_x,k+1/2} - f^{m}_{u_x,k-1/2}}{h} &= -\frac{n^m_k \textcolor{blue}{E^{m+1}_{x,k}}}{\varepsilon^2} + \frac{n^m_k u^m_{z,k}\Tilde{B}^m_{y,k}}{\varepsilon^2},\\
-    \frac{(nu_z)^{m+1}_k - (nu_z)^m_k}{\delta^m} + \frac{f^{m}_{u_z,k+1/2} - f^{m}_{u_z,k-1/2}}{h} &= - \frac{n^m_k \textcolor{blue}{\Tilde{E}^{m+1}_{z,k}}}{\varepsilon^2} - \frac{n^m_k u^m_{x,k}\Tilde{B}^m_{y,k}}{\varepsilon^2}, \\
-    \frac{B^{m+1}_{y,k+1/2} - B^{m}_{y,k+1/2}}{\delta^m} + \frac{\textcolor{blue}{E^{m+1}_{x,k+1} - E^{m+1}_{x,k}}}{h} &= 0, \\
-    \lambda^2 \frac{E^{m+1}_{x,k} - E^{m}_{x,k}}{\delta^m} + \frac{\textcolor{blue}{B^{m+1}_{y,k+1/2} - B^{m+1}_{y,k-1/2}}}{h} &= \textcolor{blue}{(nu_x)^{m+1}_k}, \\
-    \lambda^2 \frac{E^{m+1}_{z,k+1/2} - E^{m}_{z,k+1/2}}{\delta^m} &= \textcolor{blue}{f^{m+1}_{n,k+1/2}}, 
+    \frac{n^{m+1}_k - n^m_k}{\delta^m} + \frac{\mycolorbox{orange!30}{f^{n,m+1/2}_{k+1/2} - f^{n,m+1/2}_{k-1/2}}}{h} &= 0, \\
+    \frac{(nu_x)^{m+1}_k - (nu_x)^m_k}{\delta^m} + \frac{f^{u_x,m}_{k+1/2} - f^{u_x,m}_{k-1/2}}{h} &= -\frac{n^m_k \mycolorbox{orange!30}{E^{m+1}_{x,k}}}{\varepsilon^2} + \frac{n^m_k u^m_{z,k}\Tilde{B}^m_{y,k}}{\varepsilon^2},\\
+    \frac{(nu_z)^{m+1}_k - (nu_z)^m_k}{\delta^m} + \frac{f^{u_z,m}_{k+1/2} - f^{u_z,m}_{k-1/2}}{h} &= - \frac{n^m_k \mycolorbox{orange!30}{\Tilde{E}^{m+1}_{z,k}}}{\varepsilon^2} - \frac{n^m_k u^m_{x,k}\Tilde{B}^m_{y,k}}{\varepsilon^2}, \\
+    \frac{B^{m+1}_{y,k+1/2} - B^{m}_{y,k+1/2}}{\delta^m} + \frac{\mycolorbox{orange!30}{E^{m+1}_{x,k+1} - E^{m+1}_{x,k}}}{h} &= 0, \\
+    \lambda^2 \frac{E^{m+1}_{x,k} - E^{m}_{x,k}}{\delta^m} + \frac{\mycolorbox{orange!30}{B^{m+1}_{y,k+1/2} - B^{m+1}_{y,k-1/2}}}{h} &= \mycolorbox{orange!30}{(nu_x)^{m+1}_k}, \\
+    \lambda^2 \frac{E^{m+1}_{z,k+1/2} - E^{m}_{z,k+1/2}}{\delta^m} &= \mycolorbox{orange!30}{f^{m+1}_{n,k+1/2}}, 
 \end{align*}
@@
 \begin{align*}
-    f^{m+1/2}_{n,k+1/2} & = \frac{1}{2}[\textcolor{blue}{(nu_z)^{m+1}_k + (nu_z)^{m+1}_{k+1}} + \mu^m_{k+1/2}(n^m_k - n^m_{k+1})], \\
-    f^{m}_{u_x,k+1/2} & = \frac{1}{2}[(nu_zu_x)^{m}_k + (nu_zu_x)^{m}_{k+1} + \mu^m_{k+1/2}((nu_x)^m_k - (nu_x)^m_{k+1})], \\
-    f^{m}_{u_z,k+1/2} & = \frac{1}{2}[(nu_z^2 + p(n)/\varepsilon^2)^{m}_k + (nu_z^2 + p(n)/\varepsilon^2)^{m}_{k+1} + \mu^m_{k+1/2}((nu_z)^m_k - (nu_z)^m_{k+1})]. \\
+    f^{n,m+1/2}_{k+1/2} & = \frac{1}{2}[\mycolorbox{orange!30}{(nu_z)^{m+1}_k + (nu_z)^{m+1}_{k+1}} + \mu^m_{k+1/2}(n^m_k - n^m_{k+1})], \\
+    f^{u_x,m}_{k+1/2} & = \frac{1}{2}[(nu_zu_x)^{m}_k + (nu_zu_x)^{m}_{k+1} + \mu^m_{k+1/2}((nu_x)^m_k - (nu_x)^m_{k+1})], \\
+    f^{u_z,m}_{k+1/2} & = \frac{1}{2}[(nu_z^2 + p(n)/\varepsilon^2)^{m}_k + (nu_z^2 + p(n)/\varepsilon^2)^{m}_{k+1} + \mu^m_{k+1/2}((nu_z)^m_k - (nu_z)^m_{k+1})].
 \end{align*}
-According to the linearized stability analysis in \cite{degond_2012}, the implicitness of the Lorentz force and the Maxwell equations is essential to the stability in the quasi-neutral limit.
-Besides, the mass flux in the mass conservation equation and the current in Amp\`{e}re's law have the same degree of implicitness in order to guarantee the consistency with the Gauss law.
-The implicit terms are highlighted in blue color.
-
-\subsection{Semi-implicit Fully-discrete AP Scheme in 3D}
-
+The implicit terms are highlighted.
+The implicitness of the electric field in the Lorentz force is shown to be necessary in \cite{fabre_1992} for the Euler-Poisson system.
+In \cite{degond_2012}, based on the linearized stability analysis, the author shows that the full-implicit treatment of the Maxwell equations is essential to the stability in the quasi-neutral limit.
+Besides, the mass flux in the mass conservation equation and the current in Amp\`{e}re's law have the same degree of implicitness in order to guarantee the consistency with Gauss's law.
+
+\subsection{Semi-implicit Fully-discrete AP Scheme in 3D} \label{sec:3d_ap_scheme}
+Combining the 3D FIT-FVM framework presented in Section \ref{sec:spatial_discretization} and the time-stepping scheme shown below, we end up getting the following semi-implicit fully-discrete AP scheme in 3D:
+\begin{subequations}
 \begin{align}
-    \left[\delta_m^{-1} (\mathbf{b}^{m+1} - \mathbf{b}^{m}) + \mathbb{C}\textcolor{blue}{\mathbf{e}^{m+1}} = \mathbf{0} \right]_i,\ \ &\forall i:A_i \subset \Omega, \label{equ:maxwell_faraday_ap}\\
-    \left[\lambda^2\delta_m^{-1}(\mathbf{d}^{m+1} - \mathbf{d}^m)- \Tilde{\mathbb{C}}\textcolor{blue}{\mathbf{h}^{m+1}} = - \textcolor{blue}{\Sigma_\ast q_\ast \mathbf{F}^{n,m+1}_{\ast}}\right]_i,\ \ &\forall i:\Tilde{A}\subset\Omega_P, \\
-    \left[\lambda^2\delta_m^{-1}(\mathbf{d}^{m+1} - \mathbf{d}^m)- \Tilde{\mathbb{C}}\textcolor{blue}{\mathbf{h}^{m+1}} + \mathbb{H}\mathbb{G}\textcolor{blue}{\mathbf{p}^{m+1}} = \mathbf{0} \right]_i,\ \ &\forall i:\Tilde{A}\subset\Omega_I, \label{equ:maxwell_ampere_ap}\\
-    \left[\mathbb{D}\textcolor{blue}{\mathbf{d}^{m+1}} = \mathbf{0}\right]_i, \ \ &\forall i : \Tilde{V}_i \subset \Omega_I, \\
-    \left[\delta_m^{-1}(\mathbf{U}_{*}^{m+1} - \mathbf{U}_{*}^{m}) + \mathbb{\Tilde{V}}^{-1}\mathbb{\Tilde{D}}\textcolor{blue}{\mathbf{F}_\ast^{m+1/2}} = \textcolor{blue}{\mathbf{RHS}_\ast^{m+1/2}} \right]_i,\ \ &\forall i : \Tilde{V}_i \subset \Omega_P, \label{equ:euler_ap}
+    \left[\delta_m^{-1} (\mathbf{b}^{m+1} - \mathbf{b}^{m}) + \mathbb{C}\mycolorbox{orange!30}{\mathbf{e}^{m+1}} = \mathbf{0} \right]_i,\ \ &\forall i:A_i \subset \Omega, \label{equ:maxwell_faraday_ap}\\
+    \left[\lambda^2\delta_m^{-1}(\mathbf{d}^{m+1} - \mathbf{d}^m)- \Tilde{\mathbb{C}}\mycolorbox{orange!30}{\mathbf{h}^{m+1}} = - \Sigma_\ast q_\ast \mycolorbox{orange!30}{\bm{f}^{n,m+1}_{\ast}}\right]_i,\ \ &\forall i:\Tilde{A}_i\subset\Omega_P, \label{equ:maxwell_ampere_plasma_ap}\\
+    \left[\lambda^2\delta_m^{-1}(\mathbf{d}^{m+1} - \mathbf{d}^m)- \Tilde{\mathbb{C}}\mycolorbox{orange!30}{\mathbf{h}^{m+1}} + \mathbb{H}\mathbb{G}\mycolorbox{orange!30}{\bm{\psi}^{m+1}} = \mathbf{0} \right]_i,\ \ &\forall i:\Tilde{A}_i\subset\Omega_N, \label{equ:maxwell_ampere_nonconducting_ap}\\
+    \left[\mathbb{D}\mycolorbox{orange!30}{\mathbf{d}^{m+1}} = \mathbf{0}\right]_i, \ \ &\forall i : \Tilde{V}_i \subset \Omega_N, \label{equ:gauss_nonconducting_ap} \\
+    \left[\delta_m^{-1}(\mathbf{U}_{*}^{m+1} - \mathbf{U}_{*}^{m}) + \mathbb{\Tilde{V}}^{-1}\mathbb{\Tilde{D}}\mathbb{\Tilde{A}}\mycolorbox{orange!30}{\mathbf{F}_\ast^{m+1/2}} = \mycolorbox{orange!30}{\mathbf{RHS}_\ast^{m+1/2}} \right]_i,\ \ &\forall i : \Tilde{V}_i \subset \Omega_P, \label{equ:euler_ap}
 \end{align}
@@
 \begin{align}
-    \mathbf{U}_{*,k}^{m} &=
-    \begin{bmatrix}
-    n_* \\
-    n_* \mathbf{u}_* \\
-    n_* e_*
-    \end{bmatrix}^m_k, \\
-    \overline{\mathbf{F}}_{*,j}^{m+1/2} &=
-    \begin{bmatrix}
-    f^{m+1}_{n,*,j} \\
-    \bm{f}^m_{u,*,j} \\
-    f^m_{e,*,j} 
-    \end{bmatrix}
+    \mathbf{U}_{*,i}^{m} &=
+    \begin{pmatrix}
+    n \\
+    n \mathbf{u} \\
+    n e
+    \end{pmatrix}^m_{\ast,i}, \\
+    \mathbf{F}_{*,i}^{m+1/2} &=
+    \begin{pmatrix}
+    f^{n,m+1} \\
+    \bm{f}^{u,m} \\
+    f^{e,m}
+    \end{pmatrix}_{\ast,i}
     = 
-    \begin{bmatrix}
-    \frac{1}{2}\left[\textcolor{blue}{(nu_{\bot})_{*,k}^{m+1}} + \textcolor{blue}{(nu_{\bot})_{*,k+1}^{m+1}}\right] - \frac{1}{2}s^m_{*,k+1/2}(n_{*,k+1}^m - n_{*,k}^m) \\
-    \frac{1}{2}\left[(nu_{\bot}\mathbf{u})^m_{*,k} + (nu_{\bot}\mathbf{u})^m_{*,k+1} + p_{*,k}^m\mathbf{n}_j + p_{*,k+1}^m\mathbf{n}_j\right] - \frac{1}{2}s^m_{*,k+1/2}\left[(n\mathbf{u})^m_{*,k+1} - (n\mathbf{u})^m_{*,k}\right] \\
-    \frac{1}{2}\left[(nhu_\bot)^m_{*,k} + (nhu_\bot)^m_{*,k+1}\right] - \frac{1}{2}s^m_{*,k+1/2}\left[(ne)^m_{*,k+1} - (ne)^m_{*,k}\right]
-    \end{bmatrix}, \label{equ:flux_ap}\\
-    \mathbf{RHS}_{*,k}^{m+1/2} &=
-    \begin{bmatrix}
+    \begin{pmatrix}
+    \frac{1}{2}\left[\mycolorbox{orange!30}{(nu_{\bot})_{L}^{m+1}} + \mycolorbox{orange!30}{(nu_{\bot})_{R}^{m+1}}\right] - \frac{1}{2}s^m(n_{R}^m - n_{L}^m) \\
+    \frac{1}{2}\left[(nu_{\bot}\mathbf{u})^m_{L} + (nu_{\bot}\mathbf{u})^m_{R} + p_{L}^m\mathbf{n}_j + p_{R}^m\mathbf{n}_j\right] - \frac{1}{2}s^m\left[(n\mathbf{u})^m_{R} - (n\mathbf{u})^m_{L}\right] \\
+    \frac{1}{2}\left[(nhu_\bot)^m_{L} + (nhu_\bot)^m_{R}\right] - \frac{1}{2}s^m\left[(ne)^m_{R} - (ne)^m_{L}\right]
+    \end{pmatrix}_{\ast,i}, \label{equ:flux_ap}\\
+    \mathbf{RHS}_{*,i}^{m+1/2} &=
+    \begin{pmatrix}
     0 \\
-    \varepsilon_*^{-2}q_*\left[n_*^m\textcolor{blue}{\mathbf{E}^{m+1}} + (n\mathbf{u})^m_*\times\mathbf{B}^m\right] \\
-    \varepsilon_*^{-2}q_*(n\mathbf{u})^m_* \cdot \textcolor{blue}{\mathbf{E}^{m+1}}
-    \end{bmatrix}_k +
-    \begin{bmatrix}
+    \varepsilon_*^{-2}q_*\left[n_*^m\mycolorbox{orange!30}{\mathbf{E}^{m+1}} + (n\mathbf{u})^m_*\times\mathbf{B}^m\right] \\
+    \varepsilon_*^{-2}q_*(n\mathbf{u})^m_* \cdot \mycolorbox{orange!30}{\mathbf{E}^{m+1}}
+    \end{pmatrix}_i +
+    \begin{pmatrix}
     0 \\
-    \varepsilon_*^{-2}\textcolor{blue}{\mathbf{R}_{*,k}^{\text{coll},m+1}} \\
-    0
-    \end{bmatrix}, \label{equ:rhs_ap}\\
-    \mathbf{R}_{*,k}^{\text{coll},m+1} &= 
+    \varepsilon_*^{-2}\mycolorbox{orange!30}{\mathbf{R}_{*}^{\text{coll},m+1}} \\
+    \varepsilon_*^{-2}\mycolorbox{orange!30}{Q_*^{\text{coll}, m+1}} 
+    \end{pmatrix}_i, \label{equ:rhs_ap}\\
+    \mathbf{E}^{m+1} &= \Tilde{\mathbb{R}}_E\mathbf{d}^{m+1},
+    \ \ \ \ 
+    \mathbf{B}^{m} = \Tilde{\mathbb{R}}_B\mathbf{b}^{m}, \\
+    \mathbf{R}_{*,i}^{\text{coll},m+1} &= 
     \begin{cases}
-    \alpha^\text{coll}\left[n_{e,k}^m\textcolor{blue}{(n\mathbf{u})^{m+1}_{i,k}} - n_{i,k}^m\textcolor{blue}{(n\mathbf{u})^{m+1}_{e,k}}\right] \text{  if  } * = e \\
-    \alpha^\text{coll}\left[n_{i,k}^m\textcolor{blue}{(n\mathbf{u})^{m+1}_{e,k}} - n_{e,k}^m\textcolor{blue}{(n\mathbf{u})^{m+1}_{i,k}}\right] \text{  if  } * = i
-    \end{cases}  \\
-    \mathbf{j}^{m+1} &= \left(\sum_*\pm q_*\textcolor{blue}{f^{m+1}_{n,*,j}}|\Tilde{A}_j|\right)_{j=1}^{N_{\Tilde{A}}}, \label{equ:current_ap}\\
-    \mathbf{d}^m &= \mathbb{M}_\varepsilon \mathbf{e}^m, \ \ \ \mathbf{h}^m = \mathbb{M}_\mu^{-1} \mathbf{b}^m. \label{equ:material_law}
-\end{align}
-In the above scheme, the superscript $m$ indicates the number of iterations, and the quantities with superscript $m+1/2$ implies its dependency on the quantities at both $m$-th and $(m+1)$-th iterations; $\delta_m$ is the time step size for the $m$-th iteration.
-The numerical flux (\ref{equ:flux_ap}), where $u_\perp$ stands for the velocity component normal to the dual face $\Tilde{A}_j$, is just the application of the generic Rusanov flux (\ref{equ:rusanov-flux-3d}) on the Euler equations, see also the expression (\ref{equ:rusanov_flux_euler}) in the appendix.
-
-By abuse of notations, quantities with subscript $k+1$ are associated with the adjacent cell of $\Tilde{V}_k$ with respect to $\Tilde{A}_j$, which should not be confused with its real index.
-$\mathbf{n}_j$ is the outer normal of $\Tilde{A}_j$ as a face of $\Tilde{V}_k$.
-Since the equations have been rescaled into the dimensionless form, the material matrices $\mathbb{M}_\varepsilon = \text{diag}(\{|\Tilde{A}_i|/{|L_i|}\}_i)$, $\mathbb{M}_\varepsilon = \text{diag}(\{{|A_i|}/{|\Tilde{L}_i|}\}_i)$ now only depend on the meshes.
-
-Recall that the discrete Euler system (\ref{equ:euler_ap}) is defined on the dual mesh $\Tilde{\mathcal{M}}$, and hence $\mathbf{E}^{m+1}$ and $\mathbf{B}^m$ in (\ref{equ:rhs_ap}) are the interpolated vector fields at dual cell center as is illustrated in section \ref{sec:interpolation}.
-The $\pm$ in (\ref{equ:current_ap}) arises from the fact that the direction of numerical fluxes is determined by the outer normal of each cell whereas each component in $\mathbf{j}^{m+1}$ is defined to be aligned with the internal orientation of the dual face it associates with.
-Hence a flip of the sign may be necessary.
-
-First, we would like to discuss the necessity of the implicit terms (highlighted in blue color).
-The implicit treatment of electric field in (\ref{equ:rhs_ap}) is a must to ensure stability and is justified in \cite{fabre_1992} for the Euler-Poisson system.
-It is reasonable to infer that it applies equally to the Euler-Maxwell system.
-To guarantee Gauss's law at the discrete level, the current in (\ref{equ:maxwell_ampere_ap}), as well as the mass flux in (\ref{equ:flux_ap}), must be at the same implicit level.
-The reformulated Ampere's law (\ref{equ:maxwell_ampere_reform}) gives us some clue that in the quasi-neutral case the right-hand side, arising from the electric current, must be implicit to lead to a valid and unique time-stepping.
-Furthermore, we stress that the current (\ref{equ:current_ap}) is evaluated by the numerical mass flux rather than its original definition $\sum_*n_*q_*\mathbf{u}_*$ for the sake of consistency to the discrete Gauss's law.
-The implicitness of the electric field in (\ref{equ:maxwell_faraday_ap}) and the magnetic flux in (\ref{equ:maxwell_ampere_ap}) is necessary for unconditional stability with respect to $\lambda$, as is demonstrated by \cite{degond_2012} through a linearized analysis.
-The implicitness of the friction term is owing to the stiffness incurred from a potentially large value of $\varepsilon^{-2}_*\alpha^\text{coll}$.
-
-Now we deduce the limiting scheme and check its validity and consistency.
-By formally setting $\lambda = 0$ in the AP scheme (\ref{equ:maxwell_faraday_ap}) to (\ref{equ:euler_ap}), the equation for evolving the electric edge voltages (\ref{equ:maxwell_ampere_ap}) degenerates into a constraint that should be satisfied at each step, namely
+    \alpha^\text{coll}\left[n_{\text{electron}}^m\mycolorbox{orange!30}{(n\mathbf{u})^{m+1}_{\text{ion}}} - n_{\text{ion}}^m\mycolorbox{orange!30}{(n\mathbf{u})^{m+1}_{\text{electron}}}\right]_i, \text{   if   } * = \text{electron} \\
+    \alpha^\text{coll}\left[n_{\text{ion}}^m\mycolorbox{orange!30}{(n\mathbf{u})^{m+1}_{\text{electron}}} - n_{\text{electron}}^m\mycolorbox{orange!30}{(n\mathbf{u})^{m+1}_{\text{ion}}}\right]_i, \text{   if   } * = \text{ion}
+    \end{cases}  \label{equ:R_coll_ap}\\
+    Q_{*,i}^{\text{coll},m+1} &= \mycolorbox{orange!30}{\mathbf{R}_{*,i}^{\text{coll},m+1} \cdot \mathbf{u}_{\ast,i}^{m+1}} \label{equ:Q_coll_ap}
+.\end{align}
+\end{subequations}
+The quantities with superscript $m+1/2$ implies its dependency on the quantities at both $m$-th and $(m+1)$-th iterations.
+In the Rusanov flux (\ref{equ:flux_ap}), we denote by $u_\perp$ the normal component velocity with respect to the dual face $\Tilde{A}_j$.
+We refrain the illustration of the collision term (\ref{equ:R_coll_ap}) (\ref{equ:Q_coll_ap}) to the two-species case for the sake of simplicity.
+
+The time-stepping scheme mimics the 1D scheme shown in the previous section.
+The implicitness of the friction term is owing to the stiffness incurred from a potentially large value of the prefactor $\varepsilon^{-2}_*\alpha^\text{coll}$.
+
+\subsubsection{Inappropriate Boundary Condition}
+We notice that the boundary condition (\ref{equ:bc_zero_curl_h}) is not valid in the quasi-neutral limit, which is revealed by taking the limit of Amp\`{e}re's law in the non-conducting region (\ref{equ:maxwell_ampere_nonconducting_ap}).
+Since $\bm{\psi}^{m+1}$ can be shown to be zero by multiplying (\ref{equ:gauss_nonconducting_ap}) by $\mathbb{D}$, we obtain that
 \begin{equation*}
-     \Tilde{\mathbb{C}}\mathbb{M}_\mu^{-1}\mathbf{b}^{m+1} = - \mathbf{j}^{m+1}.
+    [\Tilde{\mathbb{C}}\mathbf{h}^{m+1} = 0]_i, \ \ \forall i : \Tilde{A}_i \subset \Omega_N,
 \end{equation*}
-We want to check the consistency of the limiting scheme with the quasi-neutral model, and especially to check if the constraint (\ref{equ:maxwell_ampere_reform}) when $\lambda = 0$ is correctly discretized.
-To that end, we mimic the procedure to derive (\ref{equ:maxwell_ampere_reform}) in a discrete way, which leads to
+which makes the boundary condition (\ref{equ:bc_zero_curl_h}) an over-determined condition. We propose to replace (\ref{equ:bc_zero_curl_h}) by 
 \begin{equation*}
-    (\Tilde{\mathbb{C}}\mathbb{M}_\mu^{-1}\mathbb{C}\mathbf{e}^{m+1})_j / |\Tilde{A}_j| = - \frac{1}{2}(a_{j,k}^m\mathbf{E}^{m+1}_{j,k} + a_{j,k+1}^m\mathbf{E}^{m+1}_{j,k+1})\cdot \mathbf{n}_j - \frac{1}{2}(\mathbf{b}_{j,k}^m + \mathbf{b}_{j, k+1}^m) \cdot \mathbf{n}_j - \pi_j^m,
+    [\mathbf{d}^{m+1} = 0]_i, \ \ \forall i : \Tilde{A}_i \subset \Omega_N,
 \end{equation*}
-where
+since one can easily check that it is equivalent to (\ref{equ:bc_zero_curl_h}) for $\lambda = \mathcal{O}(1)$.
+In the meantime, it makes the Maxwell system in the non-conducting region well-posed in the quasi-neutral limit, which amounts to the eddy current model \cite{alfredo_2003}.
+
+\subsubsection{CFL condition}
+It has been shown in \cite{degond_2012} that the stability-induced constraint on the time-step size does not depend on the value of $\lambda$ thanks to the implicitness in the discrete Maxwell system.
+However, the Euler system is discretized by an explicit scheme and thus still subject to a CFL condition.
+
+In our case we have an conservation law with source terms. Let us consider the model equation
+\begin{equation*}
+    \partial_tu + c\partial_xu = \beta u, 
+\end{equation*}
+where $c>0$ and $\beta<0$ are constant. By a first-order upwind scheme
+\begin{equation*}
+    \delta_t^{-1}(u^{m+1}_k - u^m_k) + c\delta_x^{-1}(u^m_k - u^m_{k-1}) = \beta u^m_k,
+\end{equation*}
+we can perform Neumann analysis and deduce the CFL condition
+\begin{equation*}
+    \delta_t \leq \left[\frac{c}{\delta_x} + \frac{\beta}{2}\right]^{-1}.
+\end{equation*}
+On noticing the source term $\varepsilon_*^{-2}q_*(n\mathbf{u})^m_*\times\mathbf{B}^m$ in the momentum equation, we heuristically take the following restriction
+\begin{equation*}
+    \delta_t^m \leq \min_*\bigg\{\left[\frac{s^m_*}{\delta_x} + \frac{\varepsilon^{-2}_*|q_*||\mathbf{B}^m|}{2}\right]^{-1}\bigg\},
+\end{equation*}
+which is proven necessary by numerical experiments.
+
+\subsubsection{Procedure of time-stepping}
+The semi-implicit scheme (\ref{equ:maxwell_faraday_ap})-(\ref{equ:Q_coll_ap}) entails solving a linear system for each time step.
+We would like to provide a brief guide on how to build such a linear system and evolve the system.
+
+The main step is to establish the connection between the mass fluxes $\mathbf{f}^{n,m+1}_*$ and discrete electric induction $\mathbf{d}$.
+From the momentum conservative equation, one can get the relation between the momenta $n\mathbf{u}^{m+1}_*$ and the reconstructed electric field $\mathbf{E}^{m+1}$.
+Given the reconstruction relation (\ref{equ:reconstruction}), we can get the following relation
+\begin{equation*}
+    (n\mathbf{u})_*^{m+1} = \hat{\mathbb{M}}^m_* \mathbf{d}^{m+1} + \bm{\eta}_*^m. 
+\end{equation*}
+Next, by the formula for the mass fluxes in (\ref{equ:flux_ap}), the expression for the currents in $\Omega_P$ (see (\ref{equ:maxwell_ampere_plasma_ap})) is written  
+\begin{equation} \label{equ:discrete_ohm}
+    \mathbf{j}^{m+1} := \Sigma_\ast q_\ast \bm{f}^{n,m+1}_\ast = \mathbb{M}_\sigma^{m} \mathbf{d}^{m+1} + \mathbf{j}^m_{\text{aux}}.
+\end{equation}
+The calculation of $\hat{\mathbb{M}}_*^m, \bm{\eta}_*^m, \mathbb{M}_\sigma^m, \mathbf{j}^m_{\text{aux}}$ is slightly lengthy but straightforward, so we omit the details.
+
+The discrete Maxwell system (\ref{equ:maxwell_faraday_ap})-(\ref{equ:gauss_nonconducting_ap}) is closed provided (\ref{equ:discrete_ohm}) and can be evolved by solving a linear system.
+The Euler system (\ref{equ:euler_ap}) can afterwards be evolved explicitly.
+
+\begin{remark}
+    The formula (\ref{equ:discrete_ohm}) functions as Ohm's law in the discrete level and $\mathbb{M}_\sigma^m$ can be treated as a "conductivity" matrix.
+Since in the quasi-neutral limit $\lambda \rightarrow 0$ we lose control of the $\mathbf{E}$-field through its time derivative, $\mathbb{M}_\sigma^m$ is crucial to the stability of the scheme.
+Due to the fact that $\mathbf{j}$ and $\mathbf{d}$ are both defined on dual faces, it is reasonable to adopt a local relation between them.
+Therefore, we perform the \emph{diagonal lumping} trick on (\ref{equ:discrete_ohm}), namely rendering it diagonal by accumulating the row sum.
+We observe enhanced stability in the numerical experiments with very minor changes in the results.
+\end{remark}
+\section{Numerical Experiment}
+We conduct numerical experiments based on the geometrical setting and boundary conditions presented in Section \ref{sec:BC}.
+The primal-dual mesh pair $(\mathcal{M}, \mathcal{M}')$ is generated based on the code developed in \cite[][ch.
+1]{fuchs_2021}.
+An instance is shown in Fig.
+\ref{fig:primal_dual_meshes}.
+We consider a two-fluid plasma model which is composed of electrons and ions.
+We set the mass ratio $\varepsilon_e := m_e / m_i = 10^4$ and the collision parameter $\alpha^\text{coll} = 32$.
+\begin{figure}
+    \centering
+    \includegraphics[scale=0.3]{primal_mesh.png}
+    \hspace{1cm}
+    \includegraphics[scale=0.3]{dual_mesh.png}
+    \caption{Primal mesh (left) and dual mesh(right).}
+    \label{fig:primal_dual_meshes}
+\end{figure}
+\subsection{Quasi-1D Problem}
+On noticing the radial symmetry of the domain as well as boundary conditions, the governing equations defined at the axis of symmetry, namely $z$-axis in this case, can be tremendously simplified thanks to vanishing radial components of vector variables and radial derivatives.
+The Euler-Maxwell system at the axis of symmetry is formulated as
 \begin{align*}
-    a_{j,k}^m &= \sum_*\pm\varepsilon_*^{-2}q_*^2n^m_{*,k}, \\
-    \mathbf{b}_{j,k}^m &= \sum_*\pm\varepsilon_*^{-2}q_*\left[(n\mathbf{u})^m_{*,k}\times\mathbf{B}^m_k - \frac{1}{|\Tilde{V}_k|}\sum_{i:\Tilde{A}_i\in\partial\Tilde{V}_k}|\Tilde{A}_i|\bm{f}_{u,*,i}^m\right], \\
-    \pi^m_j &= - \frac{1}{2} \delta_m^{-1} \sum_* \pm q_* \left[s_{*,k+1/2}^m(n^m_{*,k+1} - n^m_{*,k}) - s^{m-1}_{*,k+1/2}(n^{m-1}_{*,k+1} - n^{m-1}_{*,k})\right].
-\end{align*}
-Comparison with (\ref{equ:maxwell_ampere_reform}) manifests the consistency when $\lambda = 0$, given the fact that $\pi^m_j = \mathcal{O}(h)$ where h is cell size.
-
-One should be aware that such a scheme merely meets the necessary conditions of AP property while we do not rigorously prove that it is AP.
-The difficulty to prove the nonlinear stability for such a complex system is notorious.
-Also as is mentioned throughout the thesis, the convergence of the continuous solutions as $\lambda \rightarrow 0$ is taken for granted.
-Therefore, instead of rigorously proving the scheme to be AP, the procedure shown here should be treated as a heuristic approach for constructing AP schemes, and one should always turn to numerical experiments for verification.
-
-\todo{CFL condition should be mentioned.}
-
-\todo{Not sure if a bit analysis about the scheme is needed (and possible).}
-
-\subsubsection{Procedure of time-stepping}
-In this section we provide full details on the procedure of the semi-implicit time-stepping.
-
-\todo{The notation to be simplified. The content to be reduced.}
-
-In this section, we would like to present the concrete strategy to evolve the whole system, namely calculating variables at $t_{m+1}$ given their values at $t_m$.
-On one hand, the impact of BCs is not considered when presenting the AP scheme (\ref{equ:maxwell_faraday_ap}) to (\ref{equ:current_ap}).
-On the other hand, a clever and detailed strategy of establishing the linear system at every time step is necessary.
-
-To avoid any confusion, the definition of the quantities is repeated in Tab.
-\ref{tab:def_size_var}.
-For better illustration, matrices used in this section are supplemented with both superscript and subscript indicating the size.
-For instance, $\mathbb{C}^A_L$ indicates the discrete curl operator of size $N_A \times N_L$ with respect to primal faces and edges; $\Tilde{\mathbb{C}}^{A_I}_{\partial L}$ stands for the discrete curl operator of size $N_{\Tilde{A}}^{I} \times N_{\Tilde{L}}^\partial$ with respect to dual faces on $\Gamma_I$ and edges on $\partial \Gamma$.
-
-\begin{table}[]
-    \centering
-\begin{tabular}{c c c}
-     \hline
-     \textbf{Notation}  & \textbf{Meaning}  & \textbf{Size} \\
-     \hline
-     $\mathbf{e}$ & integral of $\mathbf{E}$-field at primal edges& $N_L$ \\
-     $\mathbf{e^\circ}$ & components of $\mathbf{e}$ lying in $\Omega^\circ$ & $N_L^\circ$ \\
-     $\mathbf{e^\partial}$ & components of $\mathbf{e}$ lying on $\partial \Omega$ & $N_L^\partial$ \\
-     $\mathbf{E}$ & cell average of $\mathbf{E}$-field for dual cells & $N_{\Tilde{V}}$ \\ 
-     $\bm{\varphi}$ & electric potentials at primal vertices & $N_P^\partial$ \\
-     $\bm{\varphi}^+$ & components of $\bm{\varphi}$ lying on $\Gamma^+$ & $N_P^+$ \\
-     $\bm{\varphi}^-$ & components of $\bm{\varphi}$ lying on $\Gamma^-$ & $N_P^-$ \\
-     $\mathbf{b}$ & integral of $\mathbf{B}$-field at primal faces & $N_A$ \\
-     $\mathbf{d}^\partial$ & integral of $\mathbf{D}$-field at boundary dual faces & $N_{\Tilde{A}}^\partial = N_P^\partial$ \\
-     $\mathbf{h}^\partial$ & integral of $\mathbf{H}$-field at boundary dual edges & $N_{\Tilde{L}}^\partial = N_L^\partial$ \\
-     $\mathbf{j}$ & current through dual faces & $N_{\Tilde{A}}$ \\
-     $\mathbf{j}^\circ$ & components of $\mathbf{j}$ lying in $\Omega^\circ$ & $N_{\Tilde{A}}^\circ$ \\
-     $\mathbf{j}^\partial$ & components of $\mathbf{j}$ lying on $\partial \Omega$ & $N_{\Tilde{A}}^\partial$ \\
-     \hline
-\end{tabular}
-    \caption{Definitions and sizes of scalar vectors for each quantity.}
-    \label{tab:def_size_var}
-\end{table}
-
-With extra quantities at boundary, the schemes (\ref{equ:maxwell_faraday_ap}) (\ref{equ:maxwell_ampere_ap}) turn into
-\begin{align}
-    \delta_m^{-1} (\mathbf{b}^{m+1} - \mathbf{b}^{m}) + \mathbb{C}_L^A\mathbf{e}^{m+1} \hspace{3.08cm}&= 0, \label{equ:tmp7}\\
-    \lambda^2\delta_m^{-1}\mathbb{M}_\varepsilon(\mathbf{e}^{m+1} - \mathbf{e}^m) - \Tilde{\mathbb{C}}_{L^\circ}^{A^\circ}\mathbb{M}_\mu^{-1}\mathbf{b}^{m+1} - \Tilde{C}^{A^\circ}_{\partial L} \mathbf{h}^{\partial, m+1} &= - \mathbf{j}^{\circ,m+1}, \label{equ:tmp8}\\
-     \lambda^2\delta_m^{-1}(\mathbf{d}^{\partial,m+1} - \mathbf{d}^{\partial, m}) - \Tilde{\mathbb{C}}^{\partial A}_{\partial L} \mathbf{h}^{\partial,m+1} \hspace{2.60cm}&= - \mathbf{j}^{\partial,m+1}.
-\label{equ:tmp9}
-\end{align}
-The equations (\ref{equ:tmp8}) (\ref{equ:tmp9}) arise due to the discrete Faraday law at $\Omega^\circ$ and on $\partial \Omega$.
-
-The discretized BCs (\ref{equ:bc_1}) to (\ref{equ:bc_4}) appear as
-\begin{align}
-    \mathbf{e}^{\partial,m} &= \mathbb{G}^{\partial L}_{\partial P} \bm{\varphi}^m, \label{equ:tmp10}\\
-    \begin{bmatrix}
-    \bm{\varphi}^+ \\
-    \bm{\varphi}^- 
-    \end{bmatrix}^m &= \mathbb{S}^{\pm}_{\partial P} \bm{\varphi}^m =
-    \begin{bmatrix}
-    \varphi^+(t_m) \\
-    \varphi^-(t_m) 
-    \end{bmatrix},\label{equ:tmp11}\\
-    \Tilde{\mathbb{S}}^{A_I}_{\partial A} \mathbf{d}^{\partial,m} &= 0, \label{equ:tmp12}
-\end{align}
-where $\mathbb{G}^{\partial L}_{\partial P}$ is the discrete gradient operator applied on $\partial \Omega$;
-$\mathbb{S}^{\pm}_{\partial P}$ is a matrix with entries $\in \{0,1\}$ responsible for selecting the potentials at $\Gamma^+$ and $\Gamma^-$; $\Tilde{\mathbb{S}}^{P_I}_{\partial P}$ is also a selecting matrix that picks dual faces on $\Gamma^I$ from those at $\partial\Omega$.
-
-With proper ordering of components in $\mathbf{e}$ and (\ref{equ:tmp10}), we derive all the edge voltages $\mathbf{e}$ from interior edge voltages $\mathbf{e}^\circ$ and boundary potentials $\bm{\varphi}$ through
-\begin{align*}
-    \mathbf{e}^m =
-    \begin{bmatrix}
-    \mathbf{e}^\circ \\ \mathbf{e}^\partial
-    \end{bmatrix}^m =
-    \underbrace{
-    \begin{bmatrix}
-    \mathbb{I} & 0 \\ 0 & \mathbb{G}^{\partial L}_{\partial P}
-    \end{bmatrix}}_{\mathbb{Q}_{L^\circ,\partial P}^{L}}
-    \begin{bmatrix}
-    \mathbf{e}^\circ \\ \bm{\varphi}
-    \end{bmatrix}^m.
-\end{align*}
-
-The last piece of the puzzle to be filled is the relation connecting $\mathbf{j}^{m+1}$ and the electrical quantities -- namely, a generalized Ohm's law\footnote{By ``generalized" we mean that it is merely a formula relating the current density and $\mathbf{E}$-field at the discrete model.
-There is no counterpart for the continuous model, and it is not the \emph{discretized} Ohm's law, either.} -- such that the linear system (\ref{equ:tmp7}) to (\ref{equ:tmp9}) can be closed and solved.
-The derivation of generalized Ohm's law resorts to the discrete Euler system (\ref{equ:euler_ap}).
-In the following, we provide the derivations for models with and without friction terms.
-
-\subsubsection{Model without friction}
-By the scheme (\ref{equ:euler_ap}) for the Euler equations, we get 
-\begin{equation} \label{equ:tmp1}
-    \left[(n\mathbf{u})_{*,k}\right]^{m+1} = \left[\delta_m \varepsilon^{-2}_* q_* n^m_{*,k}\mathbf{E}^{m+1}_k \right] + \underbrace{\left[(n\mathbf{u})_{*,k}\right]^{m} - \left[\frac{\delta_m}{|{\Tilde{V}}_k|}\sum_{j:\Tilde{A}_j\in\partial\Tilde{V}_k}|\Tilde{A}_j|\bm{f}^m_{u,*,j}\right] + \left[\delta_m \varepsilon^{-2}_* q_*(n\mathbf{u})^m_{*,k} \times \mathbf{B}^m_{k}\right]}_{\bm{\eta}^m_*}
-\end{equation}
-with $[\cdot]$ meaning packing the quantities into a vector. Recall the interpolation relation
-\begin{equation*}
-    \mathbf{E} = \Tilde{\mathbb{R}}^{V_f}_{A}
-    \begin{bmatrix}
-    \mathbf{e} \\
-    \mathbf{d}^\partial 
-    \end{bmatrix},
-    \ \ \ \ 
-    \mathbf{B} = \Tilde{\mathbb{R}}^{V_f}_{L}
-    \begin{bmatrix}
-    \mathbf{b} \\
-    \mathbf{h}^\partial 
-    \end{bmatrix},
-\end{equation*}
-with which (\ref{equ:tmp1}) is rewritten as
-\begin{equation} \label{equ:tmp2}
-    \left[(n\mathbf{u})_{*,k}\right]^{m+1} = \text{diag}(\delta_m \varepsilon^{-2}_* q_* n^m_{*,k}) \Tilde{\mathbb{R}}^{V_f}_{A} 
-    \begin{bmatrix}
-    \mathbf{e} \\
-    \mathbf{d}^\partial 
-    \end{bmatrix}^{m+1} + \bm{\eta}^m_*.
-\end{equation}
-Thanks to the linear nature of numerical flux (\ref{equ:flux_ap}), we can express the mass flux by linear operation 
-\begin{equation} \label{equ:tmp3}
-    \left[f_{n,*,j}\right]^{m+1} = \frac{1}{2} \Tilde{\mathbb{A}}_{V_f}^{A_f} :  \left[(n\mathbf{u})_{*,k}\right]^{m+1} - \frac{1}{2} [s_{*,j}]^m \odot \Tilde{\mathbb{D}}_{V_f}^{A_f} [n_{*,k}]^m,
-\end{equation}
-where $:$ represents two contraction, $\odot$ represents component-wise product.
-The meanings of 3-rank tensor $\Tilde{\mathbb{A}}_{V_f}^{A_f}$ and matrix $\Tilde{\mathbb{D}}_{V_f}^{A_f}$ should be self-explanatory by scrutinizing on its component-wise expression (\ref{equ:flux_ap}).
-We stress that the boundary conditions for the Euler equations are included in these two linear operators.
-
-Plug (\ref{equ:tmp2}) into (\ref{equ:tmp3}), and we get
-\begin{equation} \label{equ:tmp4}
-    \left[f_{n,*,j}\right]^{m+1} = \underbrace{\frac{1}{2} \Tilde{\mathbb{A}}_{V_f}^{A_f} : \text{diag}(\delta_m \varepsilon^{-2}_* q_* n^m_{*,k}) \Tilde{\mathbb{R}}^{V_f}_{A}}_{\Tilde{\mathbb{T}}_{A,*}^{A,m}}
-    \begin{bmatrix}
-    \mathbf{e} \\
-    \mathbf{d}^\partial 
-    \end{bmatrix}^{m+1} + \underbrace{\frac{1}{2}\Tilde{\mathbb{A}}_{V_f}^{A_f} :\bm{\eta}^m_* - \frac{1}{2} [s_{*,j}]^m \odot \Tilde{\mathbb{D}}_{V_f}^{A_f} [n_{*,k}]^m}_{\bm{\mu}^m_*}.
-\end{equation}
-
-\subsubsection{Two-fluid model with friction}
-We include the friction term (\ref{equ:collision_rescaled}).
-Adding friction terms would lead to extra complexity since they are discretized implicitly.
-For the sake of simplicity, only the two-fluid (electron-ion) model is tackled here.
-Following the same procedure as before, first, we need the discretized relation between momenta and $\mathbf{E}$-field.
-After lengthy calculation, we end up getting
-\begin{multline}\label{equ:tmp13}
-    [n\mathbf{u}_{i,k}]^{m+1} = \left[\frac{1 + \delta_m \alpha \varepsilon_e^{-2} n_{i,k}^m + \delta_m \alpha \varepsilon_e^{-2} \frac{q_e}{q_i}n_{e,k}^m }{1 + \delta_m \alpha (\varepsilon^{-2}_e n_{i,k}^m + \varepsilon_i^{-2} n_{e,k}^m)} \delta_m \varepsilon^{-2}_i q_i n_{i,k}^m \mathbf{E}^{m+1}_k\right] \\
-    + \left[\frac{\delta_m \alpha \varepsilon_i^{-2} n_{i,k}^m}{1 + \delta_m \alpha (\varepsilon^{-2}_e n_{i,k}^m + \varepsilon^{-2}_i n_{e,k}^m)}\right] \odot \bm{\eta}_e^m + \left[\frac{1 + \delta_m \alpha \varepsilon^{-2}_e n_{i,k}^m}{1 + \delta_m \alpha (\varepsilon^{-2}_e n_{i,k}^m + \varepsilon^{-2}_i n_{e,k}^m)}\right] \odot \bm{\eta}_i^m,
-\end{multline}
-where $\alpha$ is the friction coefficient, and $\bm{\eta}_e^m, \bm{\eta}_i^m$ are defined in (\ref{equ:tmp1}).
-Again by (\ref{equ:tmp3}) we derive the expression for mass fluxes in the same form as (\ref{equ:tmp4}).
-In this case,
-\begin{align}
-     \Tilde{\mathbb{T}}_{A, i}^{A, m} &= \frac{1}{2} \Tilde{\mathbb{A}}_{V_f}^{A_f} : \text{diag}\left(\frac{1 + \delta_m \alpha \varepsilon_e^{-2} n_{i,k}^m + \delta_m \alpha \varepsilon_e^{-2} \frac{q_e}{q_i}n_{e,k}^m }{1 + \delta_m \alpha (\varepsilon^{-2}_e n_{i,k}^m + \varepsilon_i^{-2} n_{e,k}^m)}\delta_m \varepsilon^{-2}_i q_i n^m_{i,k}\right) \Tilde{\mathbb{R}}^{V_f}_{A}, \label{equ:tmp14} \\
-     \bm{\mu}^m_i &= \frac{1}{2}\Tilde{\mathbb{A}}_{V_f}^{A_f} :\left(\left[\frac{\delta_m \alpha \varepsilon_i^{-2} n_{i,k}^m}{1 + \delta_m \alpha (\varepsilon^{-2}_e n_{i,k}^m + \varepsilon^{-2}_i n_{e,k}^m)}\right] \odot \bm{\eta}_e^m + \left[\frac{1 + \delta_m \alpha \varepsilon^{-2}_e n_{i,k}^m}{1 + \delta_m \alpha (\varepsilon^{-2}_e n_{i,k}^m + \varepsilon^{-2}_i n_{e,k}^m)}\right] \odot \bm{\eta}_i^m \right) \nonumber \\
-     &\hspace{10cm} - \frac{1}{2} [s_{i,j}]^m \odot \Tilde{\mathbb{D}}_{V_f}^{A_f} [n_{i,k}]^m. \label{equ:tmp15}
-\end{align}
-The counterpart of (\ref{equ:tmp14})(\ref{equ:tmp15}) for electron is straightforward by switching the subscript $e$ and $i$.
-Then the mass fluxes for different species remain the same as (\ref{equ:tmp4}), namely
-\begin{equation}
-    \left[f_{n,*,j}\right]^{m+1} = \Tilde{\mathbb{T}}_{A,*}^{A,m} 
-    \begin{bmatrix}
-    \mathbf{e} \\
-    \mathbf{d}^\partial 
-    \end{bmatrix}^{m+1} + \bm{\mu}^m_*.
-\end{equation}
-
-Now we have had the relation of the mass fluxes and the $\mathbf{E}$-field related quantities at $t_{m+1}$.
-By definition of the current density (\ref{equ:current_ap}) we end up with the expression for the generalized Ohm's law
-\begin{equation} \label{equ:tmp5}
-    \mathbf{j}^{m+1} = \sum_*q_*\text{diag}(|\Tilde{A}_j|)\left[f_{n,*,j}\right]^{m+1} = \underbrace{\sum_*q_*\text{diag}(|\Tilde{A}_j|) \Tilde{\mathbb{T}}_{A,*}^{A,m}}_{\mathbb{M}_\sigma^m} \begin{bmatrix}
-    \mathbf{e} \\
-    \mathbf{d}^\partial 
-    \end{bmatrix}^{m+1} + \underbrace{\sum_*q_*\text{diag}(|\Tilde{A}_j|) \bm{\mu}^m_*}_{\mathbf{j}^m_\text{aux}},
-\end{equation}
-The generalized Ohm's law (\ref{equ:tmp5}) is further split into
-\begin{equation} \label{equ:tmp6}
-    \mathbf{j}^{m+1} =
-    \begin{bmatrix}
-    \mathbf{j}^{\circ,m+1} \\
-    \mathbf{j}^{\partial, m+1}
-    \end{bmatrix} =
-    \begin{bmatrix}
-    \mathbb{M}_{\sigma,11}^m & \mathbb{M}_{\sigma,12}^m \\
-    \mathbb{M}_{\sigma,21}^m & \mathbb{M}_{\sigma,22}^m
-    \end{bmatrix}
-    \begin{bmatrix}
-    \mathbf{e} \\
-    \mathbf{d}^\partial 
-    \end{bmatrix}^{m+1} +
-    \begin{bmatrix}
-    \mathbf{j}^{\circ, m}_\text{aux} \\
-    \mathbf{j}^{\partial,m}_\text{aux}
-    \end{bmatrix}.
-\end{equation}
-Combine (\ref{equ:tmp7}) to (\ref{equ:tmp12}) and (\ref{equ:tmp6}), we end up with the assembled linear system
-\begin{multline} \label{equ:linear_system}
-    \begin{bNiceArray}{wc{4cm} wc{4cm} wc{2cm} c}[margin, hvlines,rules/color=blue]
-    \Block{1-2}{\left(\lambda^2\delta_m^{-1}\mathbb{M}_\varepsilon + \Tilde{\mathbb{C}}^{A^\circ}_{L^\circ}\mathbb{M}^{-1}_\mu \delta_m \mathbb{C}^A_L + \mathbb{M}^m_{\sigma,11}\right)\mathbb{Q}_{L^\circ,\partial P}^{L}} & & \Block{2-1}{-\Tilde{\mathbb{C}}^{A}_{\partial L}} & \mathbb{M}^m_{\sigma,12} \\
-    \Block{1-2}{\mathbb{M}^m_{\sigma,21}\mathbb{Q}_{L^\circ,\partial P}^{L}} & & & \lambda^2\delta_m^{-1}\mathbb{I} + \mathbb{M}^m_{\sigma,22} \\
-    0 & \mathbb{S}^{\pm}_{\partial P} & 0 & 0 \\
-    0 & 0 & 0 & \Tilde{\mathbb{S}}^{A_I}_{\partial A}
-    \end{bNiceArray}
-    \begin{bNiceArray}{c}
-    \mathbf{e}^\circ \\
-    \bm{\varphi}  \\
-    \mathbf{h}^\partial \\
-    \mathbf{d}^\partial 
-    \end{bNiceArray}^{m+1}  \\ =
-    \begin{bNiceArray}{c}
-    \lambda^2\delta_m^{-1}\mathbb{M}_\varepsilon\mathbf{e}^m + \Tilde{\mathbb{C}}^{A^\circ}_{L^\circ} \mathbb{M}^{-1}_\mu\mathbf{b}^m - \mathbf{j}^{\circ,m}_{\text{aux}} \\
-    \lambda^2\delta_m^{-1}\mathbf{d}^{\partial,m} - \mathbf{j}^{\partial,m}_\text{aux} \\
-    \bm{\varphi}^+(t_{m+1}) \\
-    \bm{\varphi}^-(t_{m+1}) \\
-    0 
-    \end{bNiceArray}
-\end{multline}
-As soon as $\mathbf{e}^{\circ,m+1}, \bm{\varphi}^{m+1}, \mathbf{h}^{\partial,m+1}, \mathbf{d}^{\partial,m+1}$ are available after solving the linear system, the fluid variables can be updated explicitly according to (\ref{equ:euler_ap}).
-To this point, the time-stepping is done.
-
-We would like to remark that the whole time-stepping procedure, although appears tedious, does not involve any tricky treatment.
-What is more important is that the formulation of the linear system helps us to identify problems incurring by the quasi-neutral limit.
-Upon setting $\lambda = 0$, we want to ensure that the square matrix at the left-hand side remains non-singular, which is indeed the case for our formulation.
-
-\section{Numerical Experiment}
-
-\subsection{Reduction to 1D case}
-On enforcing the traverse invariance, the 3D discretization boils down to the 1D case, which provides a justification of our implementation.
-The Euler-Maxwell system at the axis of symmetry is formulated as 
-\begin{align}
     &\partial_t n_* + \partial_z(n_*u_{*,z}) = 0, \\
-    &\partial_t (n_* u_{*,z}) + \partial_z(n_*u_{*,z}^2) + \varepsilon_*^{-2} \partial_z P_* = \varepsilon_*^{-2}q_*n_*E_z, \\
+    &\partial_t (n_* u_{*,z}) + \partial_z(n_*u_{*,z}^2) + \varepsilon_*^{-2} \partial_z p_* = \varepsilon_*^{-2}q_*n_*E_z, \\
     &\partial_t (n_*e_*) + \partial_z (n_* h_* u_{*,z}) = \varepsilon_*^{-2} q_* n_* u_{*,z} E_z, \\
     \lambda^2 &\partial_t E_z = \sum_* - q_* n_* u_{*,z}.
-\end{align}
-Recall that in section \ref{sec:two_fluid_model} the two-fluid model in 1D setting is discussed and verified.
-We take the results as reference solutions for the 1D reduction on the $z$-axis of the 3D model.
-With the same setting as is described in section \ref{sec:1d_two_fluid_numerical_results} and the vanishing anode potentials, we expect the results produced by the purely 1D model and 1D reduction of the 3D model to behave in a similar way, which is shown in Fig.
-\ref{fig:z_axis_reduction}.
+\end{align*}
+which shares a similar structure as the 1D model in Section \ref{sec:projection_to_1d}.
+Therefore, it is reasonable to compare the results produced by the 1D scheme in Section \ref{sec:1d_fully_discrete_model} and the one on $z$-axis produced by the 3D scheme proposed in Section \ref{sec:3d_ap_scheme}.
+Fig.
+\ref{fig:z_axis_reduction} demonstrates good matching.
 \begin{figure}
     \centering
-    %\includegraphics{z_axis_reduction.eps}
+    \includegraphics{z_axis_reduction.eps}
     \caption{Comparison of 1D two-fluid model and reduced 1D model on $z$-axis from 3D two-fluid model.
@@
 
-\todo{Do more thorough tests}
-
-\subsection{A real problem setup}
-The problem setting is a cylindrical domain filled with plasma fluids, and with two electrodes on each end, as is sketched in Fig.
-\ref{fig:sketch_domain}.
-From the viewpoint of the Euler system, the cylinder is enclosed by a non-penetrating wall whereas the plasma fluids are allowed to inflow and outflow through the electrode surfaces.
-Regarding the Maxwell system, external electric potentials are applied on the electrodes, and the enclosing boundary is considered insulating.
-
-Under such a setting, the motions of charged particles of the plasma are driven by the external potential, giving rise to an electromagnetic field, which in turn exerts Lorentz force on the charged particles.
-This setting is intended for simulating electric arcs.
-
-We discretize the spatial domain by an unstructured mesh doublet ($\mathcal{M}, \Tilde{\mathcal{M}}$) which consists of prisms aligned with the axial direction.
-The mesh generation is realized by the code developed in \cite{fuchs_2021}.
-The detailed algorithm is omitted.
-In principle, a circle is first discretized with a 2D mesh which afterward is extended along the axial direction to form the 3D mesh.
-Based on the generated primal mesh, a dual mesh conforming to the duality requirements, as is illustrated in Section \ref{sec:mesh_duality}, can be constructed with additional attention on the cut-off boundary that is discussed in Section \ref{sec:boundary_treatment}.
-An example of the primal and dual meshes is shown in Fig.
-\ref{fig:primal_dual_meshes}.
-
-\begin{figure}
-    \centering
-    \begin{tikzpicture}
-    \coordinate (O1) at (0,0);
-    \draw[very thick] (O1) circle (1) node {Cathode};
-    \fill[blue, opacity=0.2] (O1) circle (1);
-    \draw[very thick] (O1) circle (1.5);
-    \coordinate (O2) at (4.5,1) ;
-    \draw[gray] (O2) circle (1);
-    \node at (O2) {Anode};
-    \node at (barycentric cs:O1=1,O2=1) {Plasma}; 
-    \fill[red, opacity=0.2] (O2) circle (1);
-    \coordinate (S1) at ([shift={(-0.196,0.98)}]O1);
-    \coordinate (S2) at ([shift={(-0.196,0.98)}]O2);
-    \coordinate (P1) at ([shift={(0.196,-0.98)}]O1);
-    \coordinate (P2) at ([shift={(0.196,-0.98)}]O2);
-    \coordinate (SS1) at ([shift={({-0.196*1.5},{0.98*1.5})}]O1);
-    \coordinate (SS2) at ([shift={({-0.196*1.5},{0.98*1.5})}]O2);
-    \coordinate (PP1) at ([shift={({0.196*1.5},{-0.98*1.5})}]O1);
-    \coordinate (PP2) at ([shift={({0.196*1.5},{-0.98*1.5})}]O2);
-    \draw[very thick] (SS1) -- (SS2);
-    \draw[very thick] (PP1) -- (PP2); 
-    \draw[gray] (SS2) arc (101.31:180+101.31:1.5);
-    \draw[very thick] (PP2) arc (101.31-180:101.31:1.5);
-    \begin{scope}[shift={(5.5,-1.4)}]
-    \draw[blue, -to] (0,0) -- (0.65,0.12) node[right]{\small $z$};
-    \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
-    \draw[blue, -to] (0,0) -- (0.7,0) node[below]{\small $y$};
-    \end{scope}
-    \end{tikzpicture}
-    \caption{Sketch of the computational domain: a cylinder filled with plasma and with two electrodes at the ends.\todo{Change the figure}}
-    \label{fig:sketch_domain}
-\end{figure}
-
-\begin{figure}
-    \centering
-    %\includegraphics[scale=0.4]{primal_mesh.png}
-    \hspace{2cm}
-    %\includegraphics[scale=0.4]{dual_mesh.png}
-    \caption{Primal (left) and dual (right) meshes used for the 3D testing case. They are generated by the code developed in \cite{fuchs_2021}.}
-    \label{fig:primal_dual_meshes}
-\end{figure}
-
-\subsection{Numerical results}
-Now comes the point to finally present the numerical results of the AP scheme on the Euler-Maxwell system in a 3D domain.
-To recap the problem setting and BCs, see Section \ref{sec:problem_description} and \ref{sec:numerical_experiement_bc}.
-We consider the two-fluid situation where the plasma is composed of electrons and ions.
-The mass ratio $m_i / m_e$ is equal to $10^4$.
-The friction term (\ref{equ:collision_rescaled}) is included with $\alpha^\text{coll} = 32$.
-Other effects like recombination or ionization are not considered yet.
-
-The initial state is
+\subsection{3D Cylindrical Problem}
+Sticking to the setting in Section \ref{sec:BC}, we set initial conditions
 \begin{equation*}
-    n_i(x,y,z,0) = n_e(x,y,z,0) = 1, \ \ \  p_i(x,y,z,0) = p_e(x,y,z,0) = 1.
+    n_i(\mathbf{x}, 0) = n_e(\mathbf{x},0) = 1, \ \ \  p_i(\mathbf{x},0) = p_e(\mathbf{x},0) = 1.
 \end{equation*}
 All the other quantities are vanishing initially.
-The cathode is grounded, and the anode has potential 1.0 throughout the simulation, namely $\varphi^-(t) = 0, \varphi^+(t) = 1.0$.
-It is intended to see how a stationary system responds to an applied voltage.
-We would like to remark that such an initial state is conforming to the BCs as well as the quasi-neutral condition $\rho = 0$ so that the quasi-neutrality $\lambda  = 0$ would not incur any initial layer.
+The electrode at $\Gamma_C^1$(cathode) is grounded, and the one at $\Gamma_C^2$ (anode) has potential 1.0 throughout the simulation, namely $\Phi(\mathbf{x}, t)|_{\Gamma_C^1} = 0, \Phi(\mathbf{x}, t)|_{\Gamma_C^2} = 1$.
+The experiment is intended to study how a stationary system responds to an applied voltage.
+
+\begin{remark}
+    Such an initial state is compatible with the BCs and the quasi-neutral condition $\rho = 0$. 
+\end{remark}
 
@@
     \centering
-    %\includegraphics[scale=0.35]{E_lambda_1.png}
-    %\includegraphics[scale=0.35]{B_lambda_1.png}
-    %\includegraphics[scale=0.35]{ue_lambda_1.png} \\
+    \includegraphics[scale=0.35]{E_lambda_1.png}
+    \includegraphics[scale=0.35]{B_lambda_1.png}
+    \includegraphics[scale=0.35]{ue_lambda_1.png} \\
     (a) $\lambda = 1.0$ \\
-    %\includegraphics[scale=0.35]{E_lambda_1e-2.png}
-    %\includegraphics[scale=0.35]{B_lambda_1e-2.png}
-    %\includegraphics[scale=0.35]{ue_lambda_1e-2.png} \\
+    \includegraphics[scale=0.35]{E_lambda_1e-2.png}
+    \includegraphics[scale=0.35]{B_lambda_1e-2.png}
+    \includegraphics[scale=0.35]{ue_lambda_1e-2.png} \\
     (b) $\lambda = 0.01$ \\
-    %\includegraphics[scale=0.35]{E_lambda_0.png}
-    %\includegraphics[scale=0.35]{B_lambda_0.png}
-    %\includegraphics[scale=0.35]{ue_lambda_0.png} \\
+    \includegraphics[scale=0.35]{E_lambda_0.png}
+    \includegraphics[scale=0.35]{B_lambda_0.png}
+    \includegraphics[scale=0.35]{ue_lambda_0.png} \\
     (c) $\lambda = 0$
@@
     \centering
-    %\includegraphics[scale=0.9]{norm_vs_nCell-T_1.eps}
+    \includegraphics[scale=0.9]{norm_vs_nCell-T_1.eps}
     \caption{1-norms of quantities with respect to different mesh size: The results are computed for $\lambda = 1$ and $0.1$ at $t = 1$.}.
@@
 
-    %\includegraphics[scale=0.27]{clip_E_T-1_lambda-1e-1_8-2-2.png}
-    %\includegraphics[scale=0.27]{clip_E_T-1_lambda-1e-1_16-3-3.png}
-    %\includegraphics[scale=0.27]{clip_E_T-1_lambda-1e-1_32-3-4.png}
-    %\includegraphics[scale=0.27]{clip_B_T-1_lambda-1e-1_8-2-2.png}
-    %\includegraphics[scale=0.27]{clip_B_T-1_lambda-1e-1_16-3-3.png}
-    %\includegraphics[scale=0.27]{clip_B_T-1_lambda-1e-1_32-3-4.png}
-    %\includegraphics[scale=0.27]{clip_ne_T-1_lambda-1e-1_8-2-2.png}
-    %\includegraphics[scale=0.27]{clip_ne_T-1_lambda-1e-1_16-3-3.png}
-    %\includegraphics[scale=0.27]{clip_ne_T-1_lambda-1e-1_32-3-4.png}
-    %\includegraphics[scale=0.27]{clip_ni_T-1_lambda-1e-1_8-2-2.png}
-    %\includegraphics[scale=0.27]{clip_ni_T-1_lambda-1e-1_16-3-3.png}
-    %\includegraphics[scale=0.27]{clip_ni_T-1_lambda-1e-1_32-3-4.png}
+    \includegraphics[scale=0.27]{clip_E_T-1_lambda-1e-1_8-2-2.png}
+    \includegraphics[scale=0.27]{clip_E_T-1_lambda-1e-1_16-3-3.png}
+    \includegraphics[scale=0.27]{clip_E_T-1_lambda-1e-1_32-3-4.png}
+    \includegraphics[scale=0.27]{clip_B_T-1_lambda-1e-1_8-2-2.png}
+    \includegraphics[scale=0.27]{clip_B_T-1_lambda-1e-1_16-3-3.png}
+    \includegraphics[scale=0.27]{clip_B_T-1_lambda-1e-1_32-3-4.png}
+    \includegraphics[scale=0.27]{clip_ne_T-1_lambda-1e-1_8-2-2.png}
+    \includegraphics[scale=0.27]{clip_ne_T-1_lambda-1e-1_16-3-3.png}
+    \includegraphics[scale=0.27]{clip_ne_T-1_lambda-1e-1_32-3-4.png}
+    \includegraphics[scale=0.27]{clip_ni_T-1_lambda-1e-1_8-2-2.png}
+    \includegraphics[scale=0.27]{clip_ni_T-1_lambda-1e-1_16-3-3.png}
+    \includegraphics[scale=0.27]{clip_ni_T-1_lambda-1e-1_32-3-4.png}
     \caption{Quantities at the cross-section generated by meshes with different refinement level.
@@
 
-    %\includegraphics[scale=0.27]{slice_E_T-1_lambda-0_8-2-2.png}
-    %\includegraphics[scale=0.27]{slice_E_T-1_lambda-0_16-3-3.png}
-    %\includegraphics[scale=0.27]{slice_E_T-1_lambda-0_32-3-4.png}
-    %\includegraphics[scale=0.27]{slice_B_T-1_lambda-0_8-2-2.png}
-    %\includegraphics[scale=0.27]{slice_B_T-1_lambda-0_16-3-3.png}
-    %\includegraphics[scale=0.27]{slice_B_T-1_lambda-0_32-3-4.png}
-    %\includegraphics[scale=0.27]{slice_ne_T-1_lambda-0_8-2-2.png}
-    %\includegraphics[scale=0.27]{slice_ne_T-1_lambda-0_16-3-3.png}
-    %\includegraphics[scale=0.27]{slice_ne_T-1_lambda-0_32-3-4.png}
-    %\includegraphics[scale=0.27]{slice_ni_T-1_lambda-0_8-2-2.png}
-    %\includegraphics[scale=0.27]{slice_ni_T-1_lambda-0_16-3-3.png}
-    %\includegraphics[scale=0.27]{slice_ni_T-1_lambda-0_32-3-4.png}
+    \includegraphics[scale=0.27]{slice_E_T-1_lambda-0_8-2-2.png}
+    \includegraphics[scale=0.27]{slice_E_T-1_lambda-0_16-3-3.png}
+    \includegraphics[scale=0.27]{slice_E_T-1_lambda-0_32-3-4.png}
+    \includegraphics[scale=0.27]{slice_B_T-1_lambda-0_8-2-2.png}
+    \includegraphics[scale=0.27]{slice_B_T-1_lambda-0_16-3-3.png}
+    \includegraphics[scale=0.27]{slice_B_T-1_lambda-0_32-3-4.png}
+    \includegraphics[scale=0.27]{slice_ne_T-1_lambda-0_8-2-2.png}
+    \includegraphics[scale=0.27]{slice_ne_T-1_lambda-0_16-3-3.png}
+    \includegraphics[scale=0.27]{slice_ne_T-1_lambda-0_32-3-4.png}
+    \includegraphics[scale=0.27]{slice_ni_T-1_lambda-0_8-2-2.png}
+    \includegraphics[scale=0.27]{slice_ni_T-1_lambda-0_16-3-3.png}
+    \includegraphics[scale=0.27]{slice_ni_T-1_lambda-0_32-3-4.png}
     \caption{Quantities at the cross-section generated by meshes with different refinement level.
@@
     \centering
-    %\includegraphics[scale=0.9]{origin-data_vs_time.eps}
+    \includegraphics[scale=0.9]{origin_data-vs-time_withInsulator.eps}
     \caption{Time histories of quantities at the origin for different $\lambda$. The simulation is done on a mesh with 1920 primal cells with 8 layers along $z$-axis.}
@@
     \centering
-    %\includegraphics{zaxis-data_vs_z-T_10.eps}
+    \includegraphics{zaxis-data_vs_z-T_10.eps}
     \caption{Quantities along $z$-axis for different $\lambda$: The results are computed at $t = 10$ on a mesh with 1920 primal cells with 8 layers along $z$-axis.}.
@@
 
-In Fig.
-\ref{fig:clip-ne-nue-T_10} the distribution of the electron number density and velocity at the cross-section is displayed.
-In the non-neutral case, the electrons accumulate near the anode, and the velocity is distributed rather uniformly.
-With the model approaching quasi-neutrality $\lambda = 0$, the electrons move slower in the bulk area while they are accelerated to high speed at the edge of electrodes, and they tend to accumulate in the middle pass.
-\begin{figure}
-    \centering
-    \begin{subfigure}[b]{0.4\textwidth}
-        \centering
-        %\includegraphics[scale=0.4]{clip-ne-nue-T_10-lambda_1.png}
-        \caption{$\lambda = 1$}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.4\textwidth}
-        \centering
-        %\includegraphics[scale=0.4]{clip-ne-nue-T_10-lambda_1e-1.png}
-        \caption{$\lambda = 0.1$}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.4\textwidth}
-        \centering
-        %\includegraphics[scale=0.4]{clip-ne-nue-T_10-lambda_1e-2.png}
-        \caption{$\lambda = 0.01$}
-    \end{subfigure}
-    \hspace{0.2cm}
-    \begin{subfigure}[b]{0.4\textwidth}
-        \centering
-        %\includegraphics[scale=0.38]{clip-ne-nue-T_10-lambda_0.png}
-        \caption{$\lambda = 0$}
-    \end{subfigure}
-    \caption{Electron number density and velocity vector at the cross-section.
-The results are computed at $t = 10$ on a mesh with 1920 primal cells with 8 layers along $z$-axis.
-The velocity vector lengths, which indicates the magnitude, are rescaled by the same factor.}
-    \label{fig:clip-ne-nue-T_10}
-\end{figure}
-
 \section{Conclusion}
-\todo{}
-
-\begin{figure}
-    \centering
-    \begin{tikzpicture}
-        \coordinate (A1) at (0,1.5);
-        \coordinate (A2) at (0,1);
-        \coordinate (A3) at (0,-1);
-        \coordinate (A4) at (0,-1.5);
-        \coordinate (B1) at (6,1.5);
-        \coordinate (B2) at (6,1);
-        \coordinate (B3) at (6,-1);
-        \coordinate (B4) at (6,-1.5);
-        \draw[very thick] (A2) -- (A1) -- node[above]{$\Gamma_I$} (B1) -- (B2);
-        \draw[very thick] (A3) -- (A4) -- node[below]{$\Gamma_I$} (B4) -- (B3);
-        \draw[very thick, blue] (A2) -- node[left]  {$\Gamma_-$}  (A3);
-        \draw[very thick, red]  (B2) -- node[right] {$\Gamma_+$}  (B3);
-        \node at (3,0) {$\Omega$};
-    \end{tikzpicture}
-    \begin{tikzpicture}
-        \coordinate (A1) at (0,1.5);
-        \coordinate (A2) at (0,1);
-        \coordinate (A3) at (0,-1);
-        \coordinate (A4) at (0,-1.5);
-        \coordinate (B1) at (6,1.5);
-        \coordinate (B2) at (6,1);
-        \coordinate (B3) at (6,-1);
-        \coordinate (B4) at (6,-1.5);
-        \draw[very thick] (A2) -- (A1) -- node[above]{$\nabla \times \mathbf{H}\cdot \mathbf{n} = 0$, reflective wall}  node[below, gray]{$\nabla \times \mathbf{E} \cdot \mathbf{n} = 0$ on the whole boundary} (B1) -- (B2);
-        \draw[very thick] (A3) -- (A4) -- node[below]{$\nabla \times \mathbf{H}\cdot \mathbf{n} = 0$, reflective wall} (B4) -- (B3);
-        \draw[very thick, dashed, blue] (A2) -- node[left, yshift=0.3cm] {$\varphi^-(t)$} node[left, yshift=-0.3cm] {\textcolor{black}{open}} (A3);
-        \draw[very thick, dashed, red]  (B2) -- node[right, yshift=0.3cm]  {$\varphi^+(t)$} node[right, yshift=-0.3cm] {\textcolor{black}{open}}  (B3);
-        \node at (3,0) {\textbf{Plasma}};
-        \begin{scope}[shift={(6.5,-1.6)}]
-        \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
-        \draw[blue, -to] (0,0) -- (0.7,0) node[right]{\small $z$};
-        \end{scope}
-    \end{tikzpicture}
-    \caption{Illustration of the boundary conditions: (left) notation of each part of the boundary; (right) boundary conditions at each part of the boundary.\todo{Change the figure}}
-    \label{fig:bc}
-\end{figure}
 

### 2022-11-03 paper_version/main.tex
Polish until Conclusion

@@
 An asymptotic preserving scheme for single- and multi-fluid Euler-Maxwell system was proposed by \cite{degond_2012} for one spatial dimension.
-We start from their dimensionless model and extend the scheme to three dimensions.
+We extend their scheme to three dimensions.
 The key ingredients are (i) a discretization of Maxwell's equations based on primal and dual meshes in the spirit of discrete exterior calculus (DEC)/the finite integration technique (FIT), (ii) finite volume method (FVM) for the fluid equations on the dual mesh, and (iii) mixed implicit-explicit timestepping.
-This scheme turns out to be AP for $\lambda_D\to 0$ both in terms of structure and empirically in numerical test.
+The scheme is designed to be AP as $\lambda_D \rightarrow 0$ and this is validated through numerical experiments.
 Special care is necessary for the boundary conditions which must be valid in both regimes.
-Additionally, if the electromagnetic fields have to be modelled in an insulating region beyond the plasma domain, additional stabilization is necessary to accommodate Gauss's law.
+Additionally, if the electromagnetic fields have to be modelled in an insulating region beyond the plasma domain, additional stabilization to accommodate Gauss's law is necessary.
 
@@
 \begin{itemize}
-    \item we supplement the Maxwell-Euler system by inter-species friction, see Section ?;
-    \item we extend the spatially 1D scheme to three spatial dimensions;
+    \item we supplement the Maxwell-Euler system by inter-species friction;
+    \item we extend the spatially 1D scheme of \cite{degond_2012} to three spatial dimensions using discrete exterior calculus (DEC) for Maxwell's equations combined with a low-order finite volume method for Euler's equations;
     \item we propose an essential stabilization in non-conducting regions;
-    \item we introduce suitable boundary conditions for the electromagnetic fields at a spatial truncateion boundary.
+    \item we introduce suitable boundary conditions for the electromagnetic fields at a spatial truncation boundary.
 \end{itemize}
@@
 \ref{fig:domain_geometry}.
-However, one may then encounter subtle problems in defining proper mesh duality as we do in Section ?.
+However, one may encounter subtle problems in defining proper mesh duality as we need it in Section \ref{sec:mesh-duality}.
 Thus, for the sake of simplicity of presentation we forgo geometric generality.
 
-The quasi-neutral limit of the Maxwell system leads to a singularly perturbed problem in the sense that the system changes its type from hyperbolic to a mixture of hyperbolic, parabolic and elliptic, which poses challenge for simulations over different regimes.
-Such phenomena occur in many physical models, e.g.
+The quasi-neutral limit of the Maxwell system leads to a singularly perturbed problem in the sense that the system changes its type from hyperbolic to a mixture of hyperbolic, parabolic and elliptic, which poses a challenge for simulations in setting that encompass different regimes.
+Such situations occur in many physical models, e.g.
 vanishing viscosity in the Navier-Stokes equations\cite{Kato_1984}, zero-relaxation-limit of kinetic equations\cite{jin_2010} and zero-Mach-limit of compressible flows\cite{degond_2007, haack_2010}.
-It is desirable that numerical schemes are valid for all ranges of scaled parameters, and especially when they goes to zero.
-These schemes are said to be \emph{asymptotic-preserving}.
-The concept is sketched by the commutative diagram Fig.
-\ref{fig:commutative_diagram_ap} in \cite{jin_1999}.
-The parametric problem $P^\lambda$, which converges to its limit $P^0$ as the perturbed parameter $\lambda \rightarrow 0$, is discretized by the scheme $P^\lambda_h$ where $h$ denotes some discretization parameter, e.g.
+It is desirable that numerical schemes are valid for all ranges of scaled parameters.
+These schemes are then said to be \emph{asymptotic-preserving} (AP).
+The concept is sketched by the commutative diagram in \cite{jin_1999}.
+We discrete a parametric problem $P^\lambda$, which converges to its limit $P^0$ as the perturbed parameter $\lambda \rightarrow 0$ by the scheme $P^\lambda_h$ where $h$ denotes some discretization parameter, e.g.
 mesh size.
 The AP property requires the uniform convergence of $P^\lambda_h$ to the $P^\lambda$ as $\lambda\rightarrow0$.
-In the other word, an AP scheme $P^\lambda_h$ makes the diagram Fig.
-\ref{fig:commutative_diagram_ap} commutative.
 For more details about AP schemes, see \cite{jin_2010, degond_2017} for comprehensive reviews.
 
-\begin{figure}
-    \centering
-    \begin{tikzpicture}
-    \node (nw) {\Large $P^\lambda_h$};
-    \node (ne) [right=3cm of nw]{\Large $P^\lambda$};
-    \node (sw) [below=of nw]{\Large $P^0_h$};
-    \node (se) [right=3cm of sw]{\Large $P^0$};
-    \draw[->] (nw.east)  -- node [above,midway] {$h\rightarrow0$} (ne.west) ;
-    \draw[->] (nw.east)  --  (ne.west) ;
-    \draw[->] (nw.south) -- node [left,midway] {$\lambda\rightarrow0$} (sw.north);
-    \draw[->] (nw.south) -- node {} (sw.north);
-    \draw[->] (sw.east)  -- node [above,midway] {$h\rightarrow0$}(se.west);
-    \draw[->] (ne.south) -- node [left,midway] {$\lambda\rightarrow0$} (se.north);
-    \end{tikzpicture}
-    \caption{Commuting diagram of AP schemes}
-    \label{fig:commutative_diagram_ap}
-\end{figure}
-
 The content of this paper is organized as follows.
-In Section 2, we first give full details on the underlying equations of the Maxwell-Euler system and its rescaling procedure.
-Afterwards we introduce the ECE-type boundary conditions for our problem.
+In Section 2, we give a full description of the underlying equations of the Maxwell-Euler system and its rescaling procedure.
+Meanwhile, the boundary conditions in our setting is elaborated.
 A reformulation of Maxwell's equations in the insulating region is then presented.
-Section 3 is devoted to the discretization.
-\todo{outline}
+Section 3 is devoted to the spatial discretizatio.
+The concept of primal-dual meshes is introduced based on which FIT and FVM are applied.
+We discuss the fully-discretized AP scheme in Section 4 and do numerical experiments in Section 5.
 
@@
 \begin{comment}
-In this work, we discuss and implement the so-called \emph{Euler-Maxwell} system with a focus on its limiting behavior of quasi-neutrality, namely when the \emph{Debye length} goes to zero.
+In this work, we discuss and implement the so-called \emph{Euler-Maxwell} system with a focus on its limiting behavior of quasi-neutrality, i.e.
+when the \emph{Debye length} goes to zero.
 The dimensionless form of the Euler-Maxwell equations is parameterized by the rescaled Debye length $\lambda$ whose vanishing limit alters the mathematical nature of the equations.
@@
 The other emphasis of this work is the development of a 3D discretization framework for the Maxwell-Euler system.
-The key ingredient is the combination of the Finite Volume Method (FVM) for the Euler equations and the Finite Integration Technique (FIT) for Maxwell's equations.
+The key ingredient is the combination of the finite volume Method (FVM) for the Euler equations and the Finite Integration Technique (FIT) for Maxwell's equations.
 The latter one is usually treated as a generalization to Yee's scheme \citep{yee_1966} or FDTD.
@@
 Under moderate assumptions, plasmas, which are gases composed of charged particles (and possibly neutral particles), can be treated as fluids governed by hydrodynamic equations.
-Maxwell's equations take charge of their interaction with electromagnetic fields.
+Maxwell's equations describe their interaction with electromagnetic fields.
 For more details on the fluid model of plasma, see \cite{chen2016, remi_2014}.
@@
 \end{subequations}
-where the involved quantities are magnetic flux density $\mathbf{B}$, electric field intensity $\mathbf{E}$, electric induction $\mathbf{D}$, magnetic field intensity $\mathbf{H}$, electric current density $\mathbf{J}$ and electric charge density $\rho$.
+where the involved quantities are magnetic flux density $\mathbf{B}[\frac{\text{Wb}}{\text{m}^2}]$, electric field intensity $\mathbf{E}[\frac{\text{V}}{\text{m}}]$, electric induction $\mathbf{D}[\frac{\text{C}}{\text{m}^2}]$, magnetic field intensity $\mathbf{H}[\frac{\text{A}}{\text{m}}]$, electric current density $\mathbf{J}[\frac{\text{A}}{\text{m}^2}]$ and electric charge density $\rho[\frac{\text{C}}{\text{m}^3}]$.
 These equations are known as Faraday's law (\ref{equ:maxwell_faraday}), Amp\`{e}re's law (\ref{equ:maxwell_ampere}), Gauss's law for magnetism (\ref{equ:maxwell_gauss_B}) and Gauss's law for electric field (\ref{equ:maxwell_gauss_D}).
@@
 \end{equation}
-where $\varepsilon_0$ and $\mu_0$ are the vacuum permittivity and permeability of the medium.
-By definition of the electric current density $\mathbf{J}$ and electric charge density $\rho$, they are supposed to satisfy the continuity equation
+where $\varepsilon_0]$ and $\mu_0$ are the vacuum permittivity and permeability of the medium.
+The electric current density $\mathbf{J}$ and electric charge density $\rho$ are supposed to satisfy the charge conservation equation
 \begin{equation} \label{equ:charge_continuity}
@@
 \end{equation}
-Besides, on taking the divergence of equations (\ref{equ:maxwell_faraday}) and (\ref{equ:maxwell_ampere}) together with the relation (\ref{equ:charge_continuity}), it is possible to verify that Gauss's laws (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) are consequences of (\ref{equ:maxwell_faraday}) and (\ref{equ:maxwell_ampere}) provided that (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) are satisfied at the initial time.
+Besides, on taking the divergence of equations (\ref{equ:maxwell_faraday}) and (\ref{equ:maxwell_ampere}) together with the relation (\ref{equ:charge_continuity}), it is possible to verify that Gauss's laws (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) are consequences of (\ref{equ:maxwell_faraday}) and (\ref{equ:maxwell_ampere}) provided that (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) are satisfied at initial time.
 In other words, Gauss's laws (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) can be thought of as initial conditions.
 
-Each species in plasmas are treated as a compressible flow and assocated to one set of Euler equations that includes electromagnetic forces as well as other processes, e.g.
+Each species in a plasma can be modelled as a compressible fluid by a set of the Euler equations, which additionally includes electromagnetic forces as well as other processes, e.g.
 collisions and recombination.
@@
 \end{align}
-The subscript $*$ represents the indices for different species, and by convention we assign $* = e$ to electrons, $* = i$ to ions, and $* = n$ to neutral atoms.
-The involved fluid quantities are: number density $n_*$, particle mass $m_*$,  charge number $q_*$, velocity $\mathbf{u}_*$, pressure $p_*$, specific total energy $e_* := \frac{1}{2}|\mathbf{u}_*|^2 + \frac{p_*}{m_*n_*(\gamma - 1)}$, specific total enthalpy $h_* := e_* + \frac{p_*}{m_*n_*}$ and current density $\mathbf{J}_* := q_*n_*\mathbf{u}_*$.
-All the species are assumed ideal gases with heat capacity ratio $\gamma=5/3$ for monatomic gases.
+The subscript $*\in \{\text{electron}, \text{ion}, \cdots\}$ represents the indices for different species.
+The involved fluid quantities are: number density $n_*[\frac{1}{\text{m}^3}]$, particle mass $m_*[\text{kg}]$,  charge number $q_*[\text{C}]$, velocity $\mathbf{u}_*[\frac{\text{m}}{\text{s}}]$, pressure $p_*[\frac{\text{N}}{\text{m}^2}]$, specific total energy $e_* := \frac{1}{2}|\mathbf{u}_*|^2 + \frac{p_*}{m_*n_*(\gamma - 1)}[\frac{\text{J}}{\text{kg}}]$, specific total enthalpy $h_* := e_* + \frac{p_*}{m_*n_*}[\frac{\text{J}}{\text{kg}}]$ and current density $\mathbf{J}_* := q_*n_*\mathbf{u}_*[\frac{\text{A}}{\text{m}^2}]$.
+All the species are assumed to be ideal gases with heat capacity ratio $\gamma=5/3$ for monatomic gases.
 The left-hand side of the equations describes the convection of plasma fluids.
-The first term at the right-hand side denotes Lorentz force in the momentum equation and Joule heating in the energy equation.
+The first term at the right-hand side takes into account the Lorentz force in the momentum equation and Joule heating in the energy equation.
 $\Gamma_*, \mathbf{R}_*, Q_*$ are generic terms due to effects of inter-species collision, ionization, recombination, etc.
 
-For the sake of simplicity for presentation, we only consider ion-electron collision in this work, but extension to more species is straightforward.
-Under moderate assumptions, such collisions can be well modelled by frictions, and we simply present the expressions without derivation (see \citep[][sec.
-5.6.2]{chen2016}):
+For the sake of simplicity, we only consider ion-electron collision in this work, but extension to more species is straightforward.
+Under moderate assumptions, such collisions can be well modelled by friction terms (\citep[][sec.
+5.6.2]{chen2016})
 \begin{equation} \label{equ:collision}
@@
 \end{equation}
-which models the collision force that is applied on the electrons.
-ln$\Lambda$ is called the \emph{Coulomb logarithm}, which typically takes a numerical value of order 10–20 .
-Because of the conservation of momentum, the collision term for ions $\mathbf{R}_{i}^{\text{coll}}$ is nothing but the negation of $\mathbf{R}_{e}^{\text{coll}}$.
+which models the collision force that is acting on the electrons.
+ln$\Lambda$ is called the \emph{Coulomb logarithm}, which typically takes a value $10\sim20$ \cite{chen2016}.
+Because of the conservation of momentum, the collision term for ions $\mathbf{R}_{i}^{\text{coll}}$ is nothing but the negative of $\mathbf{R}_{e}^{\text{coll}}$.
 In this work, the other effects, e.g.
@@
 \subsection{Rescaling} \label{sec:rescaling}
-In the rescaling, the variables in the equations are taken as the ratio of their original quantities and reference units, which transforms the system into dimensionless form.
+In rescaling, variables in equations are replaced the ratio of original quantities and constant reference quantities, which transforms the system into dimensionless form.
 In this part, the rescaling procedure mostly follows that of \cite{degond_2017}.
 
-First, reference units for each quantity, e.g.
-the characteristic length and time scale, are prescribed.
+First, a reference value for each quantity, e.g.
+the characteristic length and time scale, is prescribed.
 We define $\overline{x}$ and $\overline{t}$ as space and time scale of interest, by which the reference velocity $\overline{v}$ is defined as $\overline{x}/\overline{t}$.
@@
 On top of that, the typical pressure is set $\overline{n}k_B\overline{T}$ with $k_B$ being the Boltzmann constant; the typical value for the specific total energy and enthalpy is set $\overline{u}^2$.
-Together with the physical parameters, namely, permittivity $\varepsilon_0$, permeability $\mu_0$, light speed $c^2 = (\varepsilon_0\mu_0)^{-1}$, Boltzmann constant $k_B$, the elementary charge $e$, and ion mass $m_i$, the following dimensionless parameters are induced,
+Together with the physical parameters, i.e.
+permittivity $\varepsilon_0$, permeability $\mu_0$, light speed $c^2 = (\varepsilon_0\mu_0)^{-1}$, Boltzmann constant $k_B$, the elementary charge $e$, and ion mass $m_i$, the following dimensionless parameters are induced,
 \begin{align*} 
@@
     \lambda &:= \frac{\lambda_D}{\overline{x}} \text{ the dimensionless Debye length, where }\lambda_D := \left(\frac{\varepsilon_0k_B\overline{T}}{e^2\overline{n}}\right)^{1/2}, &\\
-    \varepsilon_*^2 &:= \frac{m_*}{m_i} \text{ the species mass \emph{w.r.t.} the ion mass},\ \  * \in \{i,e,n,\cdots\}, &\\
+    \varepsilon_*^2 &:= \frac{m_*}{m_i} \text{ the species mass \emph{w.r.t.} the ion mass},\ \  * \in \{\text{ion},\text{electron},\text{neutron},\cdots\}, &\\
     g &:= \frac{1}{\overline{n}\lambda_D^3} \text{ the plasma parameter\footnotemark[2]}.&
@@
 
-By abuse of notation, the dimensionless quantities have the same symbol with their original ones without incurring any ambiguity.
-For the sake of simplicity, we only consider the collision terms, namely $\Gamma_* = 0, \mathbf{R}_* = \mathbf{R}_*^\text{coll}, Q_* = Q_*^\text{coll}$ in (\ref{equ:euler_}), while neglecting other effects.
+By abuse of notation, the dimensionless quantities have the same symbol as the original quantities.
+For the sake of simplicity, we only consider the collision terms, i.e.
+$\Gamma_* = 0, \mathbf{R}_* = \mathbf{R}_*^\text{coll}, Q_* = Q_*^\text{coll}$ in (\ref{equ:euler_}), while neglecting other effects.
 The rescaled Euler-Maxwell system reads
@@
 For a fully-ionized gas, we have the original expression of $\mathbf{R}_*^{\text{coll}}$ in (\ref{equ:collision}), and its rescaled expression becomes
-\begin{equation*}
-    \mathbf{R}_i^{\text{coll}} = \frac{Z\text{ln}\Lambda}{16\pi}g\lambda^{-1}M^{-1}\varepsilon_en_en_i(\mathbf{u}_i - \mathbf{u}_e). 
-\end{equation*}
-
-Following the assumption in \cite{degond_2017}, the reference speed $\overline{v}$ is of the same scale with the plasma speed $\overline{u}$ and the thermal speed $v_{th,i}$ whereas it is much smaller than the light speed $c$.
-To study the quasi-neutral regime, the dimensionless Debye length $\lambda$ is an asymptotic parameter ranging in $[0,1]$.
-It is assumed that $\alpha$ has the same magnitude as $\lambda$, and $\eta$ and $\beta$ are of order one.
+\begin{equation}
+    \mathbf{R}_i^{\text{coll}} = \frac{Z\text{ln}\Lambda}{16\pi}g\lambda^{-1}M^{-1}\varepsilon_en_en_i(\mathbf{u}_i - \mathbf{u}_e). \label{equ:rescaling_friction}
+\end{equation}
+
+ Assumptions can be made to reduce the number of dimensionless parameters.
+Following \cite{degond_2017}, the reference speed $\overline{v}$ is of the same scale as the plasma speed $\overline{u}$ and the thermal speed $v_{th,i}$ whereas it is much smaller than the light speed $c$.
+Also, it is assumed that $\eta$ and $\beta$ are of order one and $\xi$ has the same magnitude as $\lambda$.
 
 Special treatment is needed for the collision term.
-One would notice the inverse proportionality to $\lambda$, which would introduce a singular perturbation to the Euler system as $\lambda \rightarrow 0$.
+One could argue that the occurrence of $\lambda^{-1}$ in (\ref{equ:rescaling_friction}) could lead to singular perturbation of the Euler system as $\lambda \rightarrow 0$.
 However, the validity of such a collision model is doubtful when $\lambda \rightarrow 0$.
-From the physical viewpoint, the shielding effect characterized by Debye length $\lambda$ makes the impact parameter no larger than $\lambda$.
+From the physical viewpoint, the shielding effect characterized by the rescaled Debye length $\lambda$ makes the impact parameter no larger than $\lambda$.
 The $\lambda \rightarrow 0$ limit implies that the collisions happen in the atomic length scale, in which quantum-mechanical effects must be taken into effect \citep{frank_1972}.
@@
 We end up getting the rescaled Maxwell-Euler system parameterized by $\lambda$.
-The rescaling enables us to identify the magnitude of each term in the equations, which is revealed by the prefactor polynomial of $\lambda$.
 
 \subsection{Quasi-neutral Limit} \label{sec:quasi-neutral_limit}
-The Debye length $\lambda_D$ (see its definition at the preceding section) is an characteristic length over which local concentrations of charge are shielded out.
+The Debye length $\lambda_D$ (see its definition in the preceding section) is the characteristic length over which local concentrations of charge are shielded.
 For the underlying physics, see \cite[Sec.
 1.4]{chen2016}.
-In many situations, it has a rather low value compared to the interested length scale: the typical $\lambda_D$ for gas discharge and Tokamak is $10^{-4}$ m; for interstellar medium, the magnitude is about $1$ m \cite[ch.
+In many situations, it has a rather low value compared to the reference length scale: the typical $\lambda_D$ for gas discharge and Tokamak is $10^{-4}$ m; for interstellar medium, the magnitude is about $1$ m \cite[ch.
 20]{Blandford_2013}.
-That justifies the quasi-neutrality assumption that the plasma is locally neutral, namely $\rho = \sum_* q_*n_* = 0$.
-The limit model is obtained by formally taking the rescaled Debye length $\lambda$ to zero:
+That justifies the quasi-neutrality assumption that the plasma is locally neutral, i.e.
+$\rho = \sum_* q_*n_* = 0$.
+The limit model is obtained by formally setting the rescaled Debye length $\lambda$ to zero:
 \vspace{-\baselineskip}
@@
 \begin{align*}
-    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0,\\ 
-    \lambda^2 \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= - \mathbf{J}, \\
-    \nabla \cdot \mathbf{B} &= 0, \\
-    \lambda^2 \nabla \cdot \mathbf{D} &= \rho.
+    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0 \tag{\ref{equ:maxwell_faraday_rescaled}},\\ 
+    \lambda^2 \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= - \mathbf{J}, \tag{\ref{equ:maxwell_ampere_rescaled}}\\
+    \nabla \cdot \mathbf{B} &= 0, \tag{\ref{equ:maxwell_gauss_B_rescaled}}\\
+    \lambda^2 \nabla \cdot \mathbf{D} &= \rho. \tag{\ref{equ:maxwell_gauss_D_rescaled}}
 \end{align*}
 \end{subequations}
-
 \end{minipage}
-$\xrightarrow[]{\lambda \rightarrow 0}$
+\hspace{0.6cm}$\xrightarrow[]{\lambda \rightarrow 0}$
 \begin{minipage}{0.3\textwidth}
@@
 \end{center}
-The quasi-neutral condition (\ref{equ:maxwell_gauss_D_limit}) is the consequence of taking $\lambda = 0$ in Gauss's law for electric field (\ref{equ:maxwell_gauss_D_rescaled}).
+The quasi-neutral condition (\ref{equ:maxwell_gauss_D_limit}) is the consequence of taking $\lambda = 0$ in Gauss's law for the electric field (\ref{equ:maxwell_gauss_D_rescaled}).
 Like the non-neutral case, Gauss's laws (\ref{equ:maxwell_gauss_B_limit}) (\ref{equ:maxwell_gauss_D_limit}) are the consequence of (\ref{equ:maxwell_faraday_limit}) (\ref{equ:maxwell_ampere_limit}) provided (\ref{equ:maxwell_gauss_B_limit}) (\ref{equ:maxwell_gauss_D_limit}) are satisfied at initial time.
@@
 To be more specific, in the non-limit model the $\mathbf{E}$-field evolves with time whereas in the quasi-neutral model it responds instantaneously to other quantities according to the constraint (\ref{equ:maxwell_ampere_limit}).
-To make it clear, we replace the equation (\ref{equ:maxwell_ampere_rescaled}) by the sum of the curl of (\ref{equ:maxwell_faraday_rescaled}) and the time-derivative of (\ref{equ:maxwell_ampere_rescaled}).
+To make it clear, we replace (\ref{equ:maxwell_ampere_rescaled}) by the sum of the curl of (\ref{equ:maxwell_faraday_rescaled}) and the time-derivative of (\ref{equ:maxwell_ampere_rescaled}).
 Meanwhile exploiting the momentum equation in (\ref{equ:euler_rescaled}) to express $\partial_t\mathbf{J}$, we end up getting the equation that the $\mathbf{E}$-field satisfies
@@
 \end{equation*}
- The equation (\ref{equ:E}) implies the shift from the hyperbolic nature to the elliptic nature of the $\mathbf{E}$-field as $\lambda\rightarrow0$.
+ (\ref{equ:E}) implies the shift from hyperbolic to elliptic for the evolution equations for the $\mathbf{E}$-field as $\lambda\rightarrow0$.
 
@@
 The interface between the two domains is denoted by $\Gamma_W = \partial\Omega_I \cap \partial\Omega_P$.
-A geometric arrangement corresponding to this setting is visualized in Fig.
+A geometric arrangement corresponding to this setting is sketched in Fig.
 \ref{fig:domain_sketch} and is the one used in \cite[][ch.
@@
 
-The plasma fills $\Omega_P$ where the Euler system is defined and the boundary of plasmas lies on $\partial\Omega_P$.
-We consider the physical scenario where plasmas are confined with the solid insulator.
-Therefore, the interface $\Gamma_W$ is treated as reflective walls where fluid particles are bounced back while keeping the tangential velocity and energy unchanged.
-The contact boundary $\Gamma_C$ is where the plasma and energy flow across, modelled by open boundaries in the sense that they are free to flow through, namely, ions and electrons are emitted and absorbed by the electron.
+The plasma fills $\Omega_P$ where the Euler system is defined and the boundary of the plasma domain is $\partial\Omega_P$.
+We consider the physical scenario where plasmas are confined by solid insulator.
+Therefore, the interface $\Gamma_W$ is treated as reflective wall where fluid particles are bounced back while keeping the tangential velocity and energy unchanged.
+The contact boundary $\Gamma_C$ is where the plasma and energy flow across, modelled by open boundaries in the sense that fluids are free to flow through, i.e.
+ions and electrons are emitted and absorbed by the electrodes.
 
@@
 The Maxwell system is defined on the whole domain $\Omega$.
-External voltages are enforced on the contact boundary $\Gamma_C$ to model electrodes.
-More specifically, $\Gamma_C$ is composed of two disjoint connecting components $\Gamma_C^\pm$.
-Constant potentials are enforced on each component in the sense that $\Phi|_{\Gamma_C^\pm} = \Phi_\pm$.
-The insulating boundary blocks the energy interchange and therefore only admits zero electric and magnetic flux, in the sense that $\text{curl}\mathbf{E}\cdot \mathbf{n} = 0$ and $\text{curl}\mathbf{H}\cdot \mathbf{n} = 0$ where $\mathbf{n}$ is the outer normal vector.
-\todo{ECE BC}
+The insulating boundary blocks energy interchange and therefore only admits zero electric and magnetic flux, in the sense that $\text{curl}\mathbf{E}\cdot \mathbf{n} = 0$ and $\text{curl}\mathbf{H}\cdot \mathbf{n} = 0$ where $\mathbf{n}$ is the outer normal vector.
+We model the electrodes on the contact boundary $\Gamma_C = \Gamma_C^+\cup \Gamma_C^-$ which are two disjoint connecting components.
+A vanishing tangential component $\mathbf{E}_t$ of the $\mathbf{E}$-field is imposed on $\Gamma_C$.
+Since we have $\text{curl}\mathbf{E} \cdot \mathbf{n} = 0$ on the whole boundary $\partial\Omega$, there exists a scalar potential $\varphi$ defined on $\partial\Omega$ such that the tangential component $\mathbf{E}_t = \nabla_\Gamma \varphi$ where $\nabla_\Gamma$ denotes surface gradient.
+$\varphi$ is set constant in each component of $\Gamma_C$, i.e.
+external voltages are applied on the electrodes.
 \begin{figure}
@@
         \draw[very thick] (A3) -- (A4) -- node[below]{$\Gamma_I$} (B4) -- (B3);
-        \draw[very thick, dashed, blue] (A2) -- node[left] {$\Gamma_C^1$} (A3);
-        \draw[very thick, dashed, red]  (B2) -- node[right] {$\Gamma_C^2$}  (B3);
+        \draw[very thick, dashed, blue] (A2) -- node[left] {$\Gamma_C^-$} (A3);
+        \draw[very thick, dashed, red]  (B2) -- node[right] {$\Gamma_C^+$}  (B3);
         \node at (3,0) {Plasma domain $\Omega_P$};
@@
 \end{minipage}
-\caption{Sketch of the domain. The right figure shows the cross section on the $x$-$z$ plane.}
+\caption{Sketch of the domain. The right figure shows the cross section in the $x$-$z$ plane.}
 \label{fig:domain_sketch}
@@
     \mathbf{u_*}\cdot \mathbf{n} &= 0 \ \ \text{on} \ \ \Gamma_W, \\
-    \text{grad}n_* \cdot \mathbf{n} &= 0 \ \ \text{on} \ \ \Gamma_W. \\
-    \text{grad}e_* \cdot \mathbf{n} &= 0 \ \ \text{on} \ \ \Gamma_W. \\
-    \text{grad}\mathbf{U_*} \cdot \mathbf{n} &= \mathbf{0} \ \ \text{on} \ \ \Gamma_C.
+    \text{grad}\mathbf{u_*} \cdot \mathbf{n} &= \mathbf{0} \ \ \text{on} \ \ \Gamma_C, \\
+    \text{grad}n_* \cdot \mathbf{n} &= 0 \ \ \text{on} \ \ \Gamma_W \cup \Gamma_C, \\
+    \text{grad}e_* \cdot \mathbf{n} &= 0 \ \ \text{on} \ \ \Gamma_W \cup \Gamma_C.
 \end{align*}
@@
     \begin{align*}
-    \Phi = \Phi(t)\ \ &\text{on} \ \ \Gamma_C, \\
-    \text{curl} \mathbf{E} \cdot \mathbf{n} = 0\ \ &\text{on} \ \  \Gamma_I,  \\
-    \text{curl} \mathbf{H} \cdot \mathbf{n} = 0\ \ &\text{on} \ \  \Gamma_I.\
+    \text{curl} \mathbf{E} \cdot \mathbf{n} = 0\ \ &\text{on} \ \  \partial\Omega,  \\
+    \text{curl} \mathbf{H} \cdot \mathbf{n} = 0\ \ &\text{on} \ \  \Gamma_I,  \\
+    \varphi = \varphi^\pm(t)\ \ &\text{on} \ \ \Gamma_C^\pm.
     \end{align*}
@@
 \vspace{10pt}
-
 \begin{remark}
-    A small remark goes to the validity of assignment of electric potentials on $\Gamma_c^\pm$.
-Since the surface curl $\text{\emph{curl}}_\gamma\mathbf{E} = \text{\emph{curl}} \mathbf{E} \cdot \mathbf{n} = 0$, there exists a surface potential $\varphi$ such that the surface gradient $\nabla_\Gamma \varphi = \gamma_\tau \mathbf{E}$ where $\gamma_\tau $ is the tangential trace operator.
-However, for a geometric setting with non-trivial geometry, one needs to consider co-homology vector fields \cite{Hiptmair_2021}.
+    No boundary conditions for Maxwell's equations are needed on $\Gamma_W$.
+\end{remark}
+
+\begin{remark} For a geometric setting with non-trivial geometry, e.g.
+with a tunnel, \emph{curl}$\mathbf{E}\cdot\mathbf{n}$ does not lead to the existence of a surface potential $\varphi:\mathbf{E}_t = \nabla_\Gamma\varphi$.
+One needs to consider co-homology vector fields \cite{Hiptmair_2021}.
 \end{remark}
@@
 
-In non-neutral regime where $\lambda = \mathcal{O}(1)$, the Maxwell system in $\Omega_N$ is well-posed and Gauss's laws (\ref{equ:gauss_B_ins}) (\ref{equ:gauss_D_ins}) are redundant as long as they are satisfied at initial moment.
+In non-neutral regime where $\lambda = \mathcal{O}(1)$, the Maxwell system in $\Omega_N$ is well-posed and Gauss's laws (\ref{equ:gauss_B_ins}) (\ref{equ:gauss_D_ins}) are redundant as long as they are satisfied at initial time.
 Nonetheless, as the system approaches the quasi-neutral limit as $\lambda \rightarrow 0$, Gauss's law for $\mathbf{D}$-field (\ref{equ:gauss_D_ins}) becomes degenerate.
-Due to limited precision of computers, schemes based on this set of PDEs would run into instability.
-The vanishing divergence would be broken down as $\nabla \cdot \mathbf{D} = 0/\lambda^2 = 0$ would not hold numerically when $\lambda^2$ becomes extremely small.
-
-To see this issue from another perspective, we observe the limit Maxwell system in $\Omega_N$
+Due to limited machine precision, schemes based on this set of PDEs would become unstable as $\lambda \rightarrow 0$.
+The vanishing divergence would break down as $\nabla \cdot \mathbf{D} = 0/\lambda^2 = 0$ would not hold numerically when $\lambda^2$ becomes extremely small.
+
+To see this issue from another perspective, we examine the limit Maxwell system in $\Omega_N$
 \begin{subequations}
@@
 
-Again, Gauss's law for $\mathbf{B}$-field (\ref{equ:gauss_B_ins_limit}) is redundant while Gauss's law for $\mathbf{D}$-field (\ref{equ:gaus_D_ins_limit}) is no longer the consequence of the Amper\`{e}'s law and essential for the well-posedness of the problem \citep{ana_2010}.
-From this perspective, the degeneracy of Gauss's law for $\mathbf{D}$-field of the system (\ref{equ:faraday_ins_limit}) to (\ref{equ:gaus_D_ins_limit}) as $\lambda \rightarrow 0$ potentially poses some problem.
-
-In one word, the set of equations (\ref{equ:faraday_ins_limit}) to (\ref{equ:gaus_D_ins_limit}) ``approaches" an ill-posed situation as $\lambda \rightarrow 0$.
+Again, Gauss's law for the $\mathbf{B}$-field (\ref{equ:gauss_B_ins_limit}) is redundant while Gauss's law for $\mathbf{D}$-field (\ref{equ:gaus_D_ins_limit}) is no longer the consequence of Amper\`{e}'s law.
+However, it is essential for the well-posedness of the problem \citep{ana_2010}.
+From this perspective, the degeneracy of Gauss's law for $\mathbf{D}$-field in the system (\ref{equ:faraday_ins_limit}) to (\ref{equ:gaus_D_ins_limit}) as $\lambda \rightarrow 0$ poses some problem.
+
+In other words, the set of equations (\ref{equ:faraday_ins_limit}) to (\ref{equ:gaus_D_ins_limit}) ``approaches" an ill-posed situation as $\lambda \rightarrow 0$.
 This is totally fine in the continuous level while it could be problematic in the discrete level due to a limited floating-point precision.
@@
 This is done by taking the divergence of (\ref{equ:ampere_ins_reform}) such that the Laplace equation of $\psi$ with zero Dirichlet boundary condition gives vanishing $\psi$.
-The importance of this reformulation will be make clear in the numerical experiment.
-
-We would like to point out that this reformulation is not needed in the plasma domain $\Omega_P$ since the Maxwell system is uniformly well-posed for $\lambda \in [0,1]$ thanks to the existence of electric current and its dependence on the $\mathbf{E}$-field.
+The importance of this reformulation will be made clear in the numerical experiment.
+
+We would like to point out that this reformulation is not needed in the plasma domain $\Omega_P$ since the Maxwell system is uniformly well-posed for $\lambda \in [0,1]$ thanks to the existence of an electric current and its dependence on the $\mathbf{E}$-field.
 
@@
 \section{Spatial Discretization} \label{sec:spatial_discretization}
-\subsection{Primal-dual Staggered Meshes}
+\subsection{Primal-dual Staggered Meshes} \label{sec:mesh-duality}
 \subsubsection{Geometric Property}
@@
 The spatial domain is discretized by two meshes that interlace with each other, denoted by a mesh doublet $(\mathcal{M}, \Tilde{\mathcal{M}})$ for primal mesh and dual mesh respectively.
-The fundamental duality property requires that \emph{each edge of one mesh penetrates a face of the other mesh and that each vertex of one mesh lies at the center of a cell of the other mesh} \citep{weiland_2003}, which makes $(\mathcal{M}, \Tilde{\mathcal{M}})$ staggered.
+The fundamental duality property requires that \emph{each edge of one mesh penetrates a face of the other mesh and that each vertex of one mesh lies inside of a cell of the other mesh} \citep{weiland_2003}, which makes $(\mathcal{M}, \Tilde{\mathcal{M}})$ staggered.
 A simple example for Cartesian meshes is shown in Fig.
@@
 To clarify the notation, in three dimensions the primal mesh $\mathcal{M}$ is a cell complex defined by the set of elements $\{P, L, A, V\}$\footnote{The notation here is a bit floppy.
-$P, L, A, V$ can refer to a single element or a set of elements.} denoting \emph{vertices, edges, faces} and \emph{volume} respectively.
+$P, L, A, V$ can refer to a single element or a set of elements.} denoting \emph{vertices, edges, faces} and \emph{cells} respectively.
 In the same way, the dual mesh $\Tilde{\mathcal{M}}$ is defined by $\{\Tilde{P}, \Tilde{L}, \Tilde{A}, \Tilde{V}\}$.
 Elements of two meshes are associated with bijective mappings $P \leftrightarrow \Tilde{V}$, $L \leftrightarrow \Tilde{A}$, $A \leftrightarrow \Tilde{L}$ and $V \leftrightarrow \Tilde{P}$ which arise in a very natural way: $P(\Tilde{P} \text{ resp.})$ corresponds to $\Tilde{V}(V \text{ resp.})$ where it lies and $L(\Tilde{L} \text{ resp.})$ penetrates its corresponding $\Tilde{A}(A \text{ resp.})$.
-According to their dimensions, vertices, edges, faces and volumes are also termed 0-dim, 1-dim, 2-dim and 3-dim elements respectively.
+According to their dimensions, vertices, edges, faces and cells are also termed 0-dim, 1-dim, 2-dim and 3-dim elements respectively.
 Meanwhile, we denote by $N_\ast, \ast \in \{P, \Tilde{P}, L, \Tilde{L},A, \Tilde{A},V, \Tilde{V}\}$ the total number of elements in $\mathcal{M}, \Tilde{\mathcal{M}}$.
@@
 This particular choice is compatible with the cylindrical geometric setting that we are in, see Fig.
-\ref{fig:sketch_domain}.
-For a general setting, one directly decomposes the domain into tetrahedrons and constructs the Voronoi grid in the same manner as before, but the procedure is more complicated and time-consuming.
+\ref{fig:domain_sketch}.
+For a general setting, one can directly decompose the domain into tetrahedrons and constructs the Voronoi grid, but the procedure is more complicated and time-consuming and may not yield a valid dual mesh.
 The full discretization of the cylindrical domain is given in Fig.
@@
 
-The geometrical orthogonality between $L \leftrightarrow \Tilde{A}$ and $A \leftrightarrow \Tilde{L}$ is satisfied and would be a crucial property for approximating the material laws shown in the following section.
+The geometric orthogonality between $L \leftrightarrow \Tilde{A}$ and $A \leftrightarrow \Tilde{L}$ is satisfied and would be a crucial property for approximating the material laws shown in the following section.
 
 \begin{remark}
-    The use of the Delaunay-Voronoi based primal-dual meshes may lead to bad performance in simulations if there are obtuse-angle triangles in $\mathcal{M}$.
+    The use of the Delaunay-Voronoi based primal-dual meshes is problematic when there are obtuse-angle triangles in $\mathcal{M}$.
 In this case their circumcenters lie outside the triangles and the intersection between edges and faces is violated.
-An alternative approach is barycenter-based dual mesh, which is not constraint to an acute-angle triangulation \cite{Marrone_2001}.
+An alternative approach is barycenter-based dual meshes, which are not restricted to an acute-angle triangulation \cite{Marrone_2001}.
 \end{remark}
@@
 \subsubsection{Orientation and Incidence Matrices}
-Each geometrical element in the primal mesh $\mathcal{M}$ is (arbitrarily) endowed of an \emph{internal orientation} \footnote{This notion should not be aliased with \emph{inner orientation}, which has a slightly different definition, see \cite{tonti_2002}.}.
+Each geometric element in the primal mesh $\mathcal{M}$ is (arbitrarily) endowed with an \emph{internal orientation}\footnote{This notion should not be aliased with \emph{inner orientation}, which has a slightly different definition, see \cite{tonti_2002}.}.
 The notion is sketched in Fig.
 \ref{fig:orientation}.
-For the elements of the dual mesh $\Tilde{\mathcal{M}}$, we set their internal orientations to be aligned with their corresponding primal elements according to the bijective mappings.
+For the elements of the dual mesh $\Tilde{\mathcal{M}}$, we set their internal orientations to be aligned with their corresponding primal elements according to the bijective mappings, i.e.
+edges penetrate faces.
 
@@
 
-These information can be formulated into matrices with entries in $\{0,-1,+1\}$, called \emph{incidence matrices}.
+This information can be captured by matrices with entries in $\{0,-1,+1\}$, called \emph{incidence matrices}.
 To describe the primal face-to-edge relation, for instance, a sparse matrix $\mathbb{C} \in \mathbb{R}^{N_A \times N_L}$ is assembled whose $(i,j)$-entry is assigned $+1$ if the internal orientation of edge $L_j$ and its induced orientation with respect to face $A_i$ coincides; it is assigned $-1$ if two orientations are opposite; and assigned $0$ if $L_j$ is not a subset of the boundary of $A_i$.
-One would see in the later section that $\mathbb{C}$ functions as a discrete version of curl operator.
+We will see later that $\mathbb{C}$ functions as a discrete version of the curl operator.
 The other incidence matrices are constructed in the same manner, see Tab.
@@
     \hline
-         $\mathbb{D}\ (\Tilde{\mathbb{D}})$ & $N_V \times N_A\ (N_{\Tilde{V}} \times N_{\Tilde{A}})$ & volume $\rightarrow$ face & discrete div \\
+         $\mathbb{D}\ (\Tilde{\mathbb{D}})$ & $N_V \times N_A\ (N_{\Tilde{V}} \times N_{\Tilde{A}})$ & cell $\rightarrow$ face & discrete div \\
          $\mathbb{C}\ (\Tilde{\mathbb{C}})$ & $N_A \times N_L\ (N_{\Tilde{A}} \times N_{\Tilde{L}})$ & face $\rightarrow$ edge & discrete curl \\
@@
 
-These matrices are topological and thus invariant under smooth deformation of the domain.
-In the next section, we will show that they play a crucial role in constructing the topological relations of the unknowns.
+These matrices are topological and thus invariant under smooth deformation of the domain. In the next section, we will show that they play a crucial role in constructing discrete Maxwell's equations.
 
@@
     \caption{Illustration of internal and induced orientations.
-The internal orientation of each element is depicted in black color: vertices are oriented as \emph{sink} by default; edges are oriented by their pointing direction; faces are oriented by their normal vector; volumes are oriented as positive default.
-The induced orientations are depicted in blue color: the ending vertex of an edge is negatively oriented while the starting point is positively oriented; the orientations of edges with respect to a face obey the right-hand rule; a face of a volume are oriented by its outer normal vector.
+The internal orientation of each element is depicted in black color: vertices are oriented as \emph{sink} by default; edges are oriented by their pointing direction; faces are oriented by their normal vector; cells are oriented as positive default.
+The induced orientations are depicted in blue color: the ending vertex of an edge is negatively oriented while the starting point is positively oriented; the orientations of edges with respect to a face obey the right-hand rule; a face of a cell are oriented by its outer normal vector.
 }
@@
 \subsubsection{Cut-off Boundary}
-We can only solve problems on a bounded domain and thus the meshes are confined by a definite boundary.
-To make them aligned at boundary, we have to cut off the \emph{dual} elements near the boundary due to the staggered character.
-In the meantime, extra elements are needed to close $\Tilde{\mathcal{M}}$.
-These issues are illustrated in Fig.
+The primal mesh $\mathcal{M}$ is first generated and resolves the domain boundary.
+The dual mesh $\mathcal{M}'$ is generated afterwards.
+To make both meshes aligned at boundary, we have to truncate the \emph{dual} elements near the boundary due to the staggered character.
+In the meantime, auxiliary geometric entities are needed to close $\Tilde{\mathcal{M}}$, see Fig.
 \ref{fig:illustraion_dual_boundary}.
 
-Note that the auxiliary edges might not be straight and the auxiliary faces might not be flat, which necessitates a versatile data structure to include such situations.
+Note that the auxiliary edges might not be straight and the auxiliary faces might not be flat as is shown in Fig.
+\ref{fig:illustraion_dual_boundary}, which necessitates a versatile data structure to include such situations.
 In the following, the auxiliary elements would be treated as dual elements, which limits the validity of the relations in Tab.
-\ref{tab:incidence_relation} only for interior part of $\Tilde{\mathcal{M}}$.
+\ref{tab:incidence_relation} to interior part of $\Tilde{\mathcal{M}}$.
 
@@
 Before the cut-off, the boundary of $\Tilde{\mathcal{M}}$ is not well-defined.
-To resolve the same boundary as $\mathcal{M}$, boundary dual volumes are truncated and auxiliary elements are supplemented (shown in orange color).
-To be specific, in subfigure (c) four edges and one face are added in order to close this dual volume.
+To resolve the same boundary as $\mathcal{M}$, boundary dual cells are truncated and auxiliary elements are supplemented (shown in orange color).
+To be specific, in subfigure (c) four edges and one face are added in order to close this dual cell.
 Notice that these auxiliary edges and faces can be non-straight and non-flat.}
@@
 \subsection{Discrete Maxwell Equations}
-\subsubsection{The Finite Integration Technique (FIT)}
-We utilize the FIT to discretize Maxwell's equations.
+\subsubsection{Finite Integration Technique (FIT)}
+We utilize FIT to discretize Maxwell's equations.
 This framework was originally proposed in \cite{weiland_1977} and can be treated as a generalization of Yee's FDTD method \cite{yee_1966}.
@@
 \end{subequations}
-where $A, V$ stand for arbitrary surfaces and volumes in the spatial domain.
+where $A, V$ stand for arbitrary surfaces and cells in the spatial domain.
 
@@
 \begin{align}
-    &\sum_{j:L_j\in\partial A_i} \underbrace{\int_{L_j} \mathbf{E} \cdot d\mathbf{s}}_{e_j} = - \frac{\partial}{\partial t} \underbrace{\iint_{A_i} \mathbf{B} \cdot d\mathbf{A}}_{b_i},\ \ \ i = 1,...,N_A, \label{equ:maxwell_grid_faraday} \\
-    &\sum_{j:\Tilde{L}_j\in\partial \Tilde{A}_i} \underbrace{\int_{\Tilde{L}_j} \mathbf{H} \cdot d\mathbf{s}}_{h_j} = \frac{\partial}{\partial t} \underbrace{\iint_{\Tilde{A}_i} \mathbf{D} \cdot d\mathbf{A}}_{d_i} + \underbrace{\iint_{\Tilde{A}_i} \mathbf{J} \cdot d\mathbf{A}}_{j_i}, \ \ \ i = 1,...,N_{\Tilde{A}}, \label{equ:maxwell_grid_ampere}\\
+    &\sum_{j:L_j\in\partial A_i} \underbrace{\int_{L_j} \mathbf{E} \cdot d\mathbf{s}}_{:= e_j} = - \frac{\partial}{\partial t} \underbrace{\iint_{A_i} \mathbf{B} \cdot d\mathbf{A}}_{:= b_i},\ \ \ i = 1,...,N_A, \label{equ:maxwell_grid_faraday} \\
+    &\sum_{j:\Tilde{L}_j\in\partial \Tilde{A}_i} \underbrace{\int_{\Tilde{L}_j} \mathbf{H} \cdot d\mathbf{s}}_{:= h_j} = \frac{\partial}{\partial t} \underbrace{\iint_{\Tilde{A}_i} \mathbf{D} \cdot d\mathbf{A}}_{:= d_i} + \underbrace{\iint_{\Tilde{A}_i} \mathbf{J} \cdot d\mathbf{A}}_{:= j_i}, \ \ \ i = 1,...,N_{\Tilde{A}}, \label{equ:maxwell_grid_ampere}\\
     &\sum_{j:A_j\in \partial V_i} \iint_{A_j} \mathbf{B} \cdot d\mathbf{A} = 0,\ \ \ i = 1,..., N_V,\label{equ:maxwell_grid_gauss_B}\\
-    &\sum_{j:\Tilde{A}_j \in \partial\Tilde{V}_i}\iint_{\Tilde{A}_j} \mathbf{D} \cdot d\mathbf{A} = \underbrace{\iiint_{\Tilde{V}_i} \rho dV}_{q_i},\ \ \ i = 1,...,N_{\Tilde{V}}.
+    &\sum_{j:\Tilde{A}_j \in \partial\Tilde{V}_i}\iint_{\Tilde{A}_j} \mathbf{D} \cdot d\mathbf{A} = \underbrace{\iiint_{\Tilde{V}_i} \rho dV}_{:= q_i},\ \ \ i = 1,...,N_{\Tilde{V}}.
 \label{equ:maxwell_grid_gauss_D}
@@
 \begin{remark}
-    In the implementation, it always provides convenience to index a pair of corresponding primal and dual elements with the same number.
+    In an implementation, it is always convenient to index a pair of corresponding primal and dual elements with the same number.
 For instance, a primal face $A_k$ is penetrated by the dual edge $\Tilde{L}_k$.
-In the following discussion, we stick to this convention, which would simplify our notation.
+In the following discussion, we stick to this convention, which will simplify our notation.
 \end{remark}
@@
 The relations between scalar vectors, in the form of $\mathbf{b} = \mathbb{M}_\mu \mathbf{h}$ and $\mathbf{d} = \mathbb{M}_\varepsilon \mathbf{e}$, are to be derived.
-In the simplest case where permittivity $\mu$ and permeability $\varepsilon$ are homogeneous in the domain, and the orthogonality of ($\mathcal{M}, \Tilde{\mathcal{M}}$) pair is ensured, the material matrices are diagonal with entries
+In the simplest case where permittivity $\mu$ and permeability $\varepsilon$ are homogeneous in the domain, and the orthogonality of the pair ($\mathcal{M}, \Tilde{\mathcal{M}}$) is ensured, the material matrices are diagonal with entries
 
@@
 where $|\cdot|$ denotes taking length or area.
-We would like to remark that the approximation error is introduced due to the implicit assumption that vector fields are piecewise constant, see analysis in \cite{Marrone_2001}.
-
-With the aid of incidence matrices defined in the preceding section and given the discrete material law, (\ref{equ:maxwell_grid_faraday})-(\ref{equ:maxwell_grid_gauss_D}) can be reformulated by a set of algebraic equations:
+We would like to remark that the approximation error is introduced due to the implicit assumption that vector fields are piecewise constant, see the analysis in \cite{Marrone_2001}.
+
+With the aid of incidence matrices defined in the preceding section and given the discrete material law, (\ref{equ:maxwell_grid_faraday})-(\ref{equ:maxwell_grid_gauss_D}) can be recast into a set of algebraic equations:
 \begin{center}
@@
 \end{center}
-where the topping dot $\cdot$ stands for taking time derivative.
-
-At this point, we would like to emphasis the importance of the primal-dual staggered meshes: the material laws can be included in a rather simple way.
+where the topping dot $\cdot$ stands for taking the time derivative.
+
+At this point, we would like to emphasize the importance of the primal-dual staggered meshes: the material laws can be included in a rather simple way.
 For magnetic Gauss's law $\mathbf{D} = \varepsilon \mathbf{E}$, for instance, the $\mathbf{D}$-field is represented by a collection of face integrals $ (d_i)_{i}$ while $\mathbf{E}$-field is represented by a collection of edge integrals $ (e_i)_{i}$.
-The primal-dual meshes allow us to arrange them in a staggered way -- edges penetrate faces -- such that $\mathbf{D} = \varepsilon \mathbf{E}$ can be approximated by $\mathbf{d} = \mathbb{M}_{\varepsilon}\mathbf{e}$ in a local fashion, namely $\mathbb{M}_{\varepsilon}$ is diagonal.
-A more schematic illustration involves the language of differential forms and discrete Hodge operator, see \cite{bossavit1999, teixeira_1999, hip_1999}.
+The primal-dual meshes allow us to arrange them in a staggered way -- edges penetrate faces -- such that $\mathbf{D} = \varepsilon \mathbf{E}$ can be approximated by $\mathbf{d} = \mathbb{M}_{\varepsilon}\mathbf{e}$ in a local fashion, i.e.
+$\mathbb{M}_{\varepsilon}$ is diagonal.
+A more schematic illustration involves the language of differential forms and discrete Hodge operators, see \cite{bossavit1999, teixeira_1999, hip_1999}.
 
@@
 is reduced to a finite number of well-defined discrete unknowns \citep{weiland_2003}.
-Also, this discrete version of Maxwell's equations are topological in the sense that they are invariant under different coordinate systems.
+Also, this discrete version of Maxwell's equations (\ref{equ:alg_faraday})-(\ref{equ:alg_material_electric}) are topological in the sense that they are invariant under different coordinate systems.
 
@@
 The electromagnetic boundary $\Gamma_C, \Gamma_I$ is resolved by the primal mesh $\mathcal{M}$.
-As is mentioned in Section \ref{sec:BC}, a boundary scalar potential $\Phi$ can be introduced due to the vanishing surface curl of $\mathbf{E}$-field.
+As is mentioned in Section \ref{sec:BC}, a boundary scalar potential $\varphi$ can be introduced due to the vanishing surface curl of $\mathbf{E}$-field.
 It holds in the discrete level as well.
@@
     \begin{align*}
-    \varphi = \Phi(\mathbf{x}, t)\ \ &\text{on} \ \ \Gamma_C, \\
     \text{curl} \mathbf{E} \cdot \mathbf{n} = 0\ \ &\text{on} \ \  \Gamma_I,  \\
-    \text{curl} \mathbf{H} \cdot \mathbf{n} = 0\ \  &\text{on} \ \  \Gamma_I.\
+    \text{curl} \mathbf{H} \cdot \mathbf{n} = 0\ \  &\text{on} \ \  \Gamma_I, \\
+    \varphi = \varphi^\pm(t)\ \ &\text{on} \ \ \Gamma_C^\pm.
     \end{align*}
@@
             \begin{align}
-            \varphi_i = \Phi(P_i, t), \ \ &\forall i : P_i \subset \Gamma_C, \label{equ:bc_1}\\
             e_i = (\mathbb{G}\bm{\varphi})_i,\ \ &\forall i : L_i \subset \partial\Omega, \label{equ:bc_2}\\
-            (\Tilde{\mathbb{C}} \bm{h})_i = 0\ \ &\forall i : \Tilde{A}_i \subset \Gamma_I.\label{equ:bc_3}\
+            (\Tilde{\mathbb{C}} \bm{h})_i = 0\ \ &\forall i : \Tilde{A}_i \subset \Gamma_I,\label{equ:bc_3} \\
+            \varphi_i = \varphi^\pm(t), \ \ &\forall i : P_i \subset \Gamma_C^\pm. \label{equ:bc_1}
             \end{align}
@@
 \subsubsection{Reformulation} \label{sec:reform_discrete}
-In Section \ref{sec:reform_continuous}, we propose the stabilization of the Maxwell system in the non-conducting domain $\Omega_N$ by introducing a Lagrange multiplier.
+In Section \ref{sec:reform_continuous}, we propose a stabilization of the Maxwell system in the non-conducting domain $\Omega_N$ by introducing a Lagrange multiplier.
 In the semi-discrete level, the equations to be solved in $\Omega_N$ are
@@
 
-\subsubsection{An algebraic check on the well-posedness}
+\subsubsection{Remark: Balance of Equations and Unknowns}
 
@@
 \ref{tab:def_size_var}).
+\begin{center}
+\vspace{-0.5cm}
+\begin{minipage}[t]{0.4\textwidth}
     \begin{align*}
-    \#\  \text{primal cell}\ \  &N_V \\
-    \#\  \text{primal edge}\ \  &N_L := \underbrace{N^C_L + N^I_L}_{N^\partial_L} + N^\circ_L  \\
-    \#\  \text{primal face}\ \  &N_A := \underbrace{N_A^C + N^I_A}_{N^\partial_A} + N^\circ_A  \\
-    \#\  \text{primal vertex}\ \  &N_P := \underbrace{N_P^C + N^I_P}_{N^\partial_P} + N^\circ_P \\
-    \#\  \text{dual cell}\ \  &N_{\Tilde{V}} := N_P \\
-    \#\  \text{dual edge}\ \  &N_{\Tilde{L}} := \underbrace{N^\partial_{\Tilde{L}}}_{=N^\partial_L} + \underbrace{N^\circ_{\Tilde{L}}}_{=N_A} \\
-    \#\  \text{dual face}\ \  &N_{\Tilde{A}} := \underbrace{N^\partial_{\Tilde{A}}}_{=N^\partial_P} + \underbrace{N^\circ_{\Tilde{A}}}_{=N_L}
+        &\#\  \text{primal cell}\ \  N_V \\
+        &\#\  \text{primal edge}\ \  N_L := \underbrace{N^C_L + N^I_L}_{=N^\partial_L} + N^\circ_L  \\
+        &\#\  \text{primal face}\ \  N_A := \underbrace{N_A^C + N^I_A}_{=N^\partial_A} + N^\circ_A  \\
+        &\#\  \text{primal vertex}\ \  N_P := \underbrace{N_P^C + N^I_P}_{=N^\partial_P} + N^\circ_P
     \end{align*}
+\end{minipage}
+\begin{minipage}[t]{0.4\textwidth}
+    \begin{align*}
+        &\#\  \text{dual cell}\ \  N_{\Tilde{V}} := N_P \\
+        &\#\  \text{dual edge}\ \  N_{\Tilde{L}} := \underbrace{N^\partial_{\Tilde{L}}}_{=N^\partial_L} + \underbrace{N^\circ_{\Tilde{L}}}_{=N_A} \\
+        &\#\  \text{dual face}\ \  N_{\Tilde{A}} := \underbrace{N^\partial_{\Tilde{A}}}_{=N^\partial_P} + \underbrace{N^\circ_{\Tilde{A}}}_{=N_L}
+    \end{align*}
+\end{minipage}   
+\end{center}
+
 where the superscript indicates the locations where the elements lie.
-The equations $N^\partial_{\Tilde{L}} = N^\partial_L, N^\partial_{\Tilde{A}} = N^\partial_P$, revealing the bijective relation between the boundary primal elements and auxiliary elements, can be check easily by inspecting Fig.
+The equations $N^\partial_{\Tilde{L}} = N^\partial_L, N^\partial_{\Tilde{A}} = N^\partial_P$ reveal the bijective relation between the boundary primal elements and auxiliary elements, as can be checked easily by inspecting Fig.
 \ref{fig:illustraion_dual_boundary}.
@@
 \end{tabular}
-    \caption{Definitions and sizes of all the degrees of freedom.}
+    \caption{Definitions and sizes of all vectors of degrees of freedom.}
     \label{tab:def_size_var}
@@
 
-However, the matching of numbers of unknowns and equations does not necessarily result in a valid linear system.
-Inappropriate BCs could cause the singularity of the linear system as $\lambda \rightarrow 0$, which will be discussed later.
+However, the matching of numbers of unknowns and equations does not necessarily result in a valid linear system since the equations might be linearly dependent.
+We will see later in Section \ref{sec:inapp_bc} that inappropriate BCs could cause the singularity of the linear system as $\lambda \rightarrow 0$.
 
@@
 It is the cell average of quantities that evolves at each time step, based on the \emph{numerical flux} through the cell boundary.
-The construction of the numerical flux, which serves to approximate the real flux, is the essence of constructing an FVM scheme.
-Due to the convection nature of fluid dynamics, the numerical fluxes are supposed to respect the convection direction, namely, the \emph{upwind scheme} is preferable.
+The construction of the numerical flux, which serves to approximate the real flux, is the essence of constructing FVM schemes.
+Due to the convection nature of fluid dynamics, the numerical fluxes are supposed to respect the convection direction, that is, an \emph{upwind scheme} is preferable.
 To this end, people resort to the approximated solution of \emph{Riemann problems}.
@@
 \begin{equation} \label{equ:euler_grid} 
-    \dot{\overline{\mathbf{U}}}_i + \frac{1}{|V_i|}\sum_{j:A_j\in\partial V_i} |A_j|\underbrace{\frac{1}{|A_j|}\iint_{A_j}\mathbf{f}(\mathbf{U})\cdot \mathbf{n}_j \text{d}A}_{\overline{\mathbf{f}}_j \approx \mathbf{f}^\text{num}_j} = \underbrace{\frac{1}{|V_i|}\iiint_{V_i} \mathbf{RHS} \text{d}V}_{\overline{\mathbf{RHS}}_i}
+    \dot{\overline{\mathbf{U}}}_i + \frac{1}{|V_i|}\sum_{j:A_j\in\partial V_i} |A_j|\underbrace{\frac{1}{|A_j|}\iint_{A_j}\mathbf{f}(\mathbf{U})\cdot \mathbf{n}_j \text{d}A}_{:= \overline{\mathbf{f}}_j \approx \mathbf{f}^\text{num}_j} = \underbrace{\frac{1}{|V_i|}\iiint_{V_i} \mathbf{RHS} \text{d}V}_{:= \overline{\mathbf{RHS}}_i}
 \end{equation}
-where $\overline{\mathbf{U}}_i := \iiint_{V_i} \mathbf{U} \text{d}V / |V_i| \in L^2([0,T],\mathbb{R}^m)$ calculates the cell average, $\mathbf{n}_j$ is the outer normal vector of face $A_j$ with respect to the cell $V_i$.
+where $\overline{\mathbf{U}}_i := \iiint_{V_i} \mathbf{U} \text{d}V / |V_i| \in L^2([0,T],\mathbb{R}^m)$ is the cell average of $\mathbf{U}$ and $\mathbf{n}_j$ is the outer normal vector of face $A_j$ with respect to the cell $V_i$.
 We approximate the flux $\overline{\mathbf{f}}_j$ in (\ref{equ:euler_grid}) by a numerical flux $\mathbf{f}^\text{num}_j := \mathbf{f}^\text{num}\left(\overline{\mathbf{U}}_i, \overline{\mathbf{U}}_{k(i,j)}, \mathbf{n}_j\right)$, where $k(i,j)$ returns the index of the adjacent cell that shares $A_j$ with cell $V_i$.
@@
 To rewrite (\ref{equ:fvm}) into a matrix form, by abuse of notation we stack all the cell average $(\overline{\mathbf{U}}_i)_i$ into a matrix $\mathbf{U} \in \mathbb{R}^{N_{\Tilde{V}}^P \times m}$ with $\mathbf{U}_{i,:} = \overline{\mathbf{U}}_i$.
-Meanwhile, we denote by $\mathbf{F} \in \mathbb{R}^{N_{\Tilde{A}}^P \times m}$ the collection of the (total) numerical fluxes, namely $\mathbf{F}_{i,:} = \mathbf{f}^\text{num}_i$.
+Meanwhile, we denote by $\mathbf{F} \in \mathbb{R}^{N_{\Tilde{A}}^P \times m}$ the collection of the (total) numerical fluxes, i.e.
+$\mathbf{F}_{i,:} = \mathbf{f}^\text{num}_i$.
 In the same way, we denote by $\mathbf{RHS}\in \mathbb{R}^{N_{\Tilde{V}}^P \times m}$ the collection of $\overline{\mathbf{RHS}}_i$.
@@
 \subsubsection{Reconstruction of Lorentz Force}
-Since the electromagnetic fields are represented by integrals on edges and faces, we need to reconstruct their vector components for the computation of Lorentz force (and Joule heating) inside each dual volume.
+Since the electromagnetic fields are represented by integrals on edges and faces, we need to reconstruct their vector components for the computation of Lorentz force (and Joule heating) inside each dual cell.
 
@@
 \begin{itemize}
-    \item[-] given the fluxes at faces of a volume, reconstruct the vector field inside the volume;
-    \item[-] given the integrals along edges of a volume, reconstruct the vector field inside the volume. 
+    \item[-] given the fluxes at faces of a cell, reconstruct the vector field inside the cell;
+    \item[-] given the integrals along edges of a cell, reconstruct the vector field inside the cell. 
 \end{itemize}
-We adopt the principle of least square fitting, and reconstruct a \emph{constant} vector field inside each volume.
-For a volume $\Tilde{V}$ with $k$ faces with areas $\{A_i\}_{i=1}^k$, normal vectors $\{\mathbf{n}_i\}_{i=1}^k$ and fluxes $\{f_i\}_{i=1}^k$, a constant vector field $\mathbf{v}$ satisfying
+We adopt the principle of least square fitting, and reconstruct a \emph{constant} vector field inside each cell.
+For a cell $\Tilde{V}$ with $k$ faces with areas $\{A_i\}_{i=1}^k$, normal vectors $\{\mathbf{n}_i\}_{i=1}^k$ and fluxes $\{f_i\}_{i=1}^k$, a constant vector field $\mathbf{v}$ satisfying
 \begin{equation*}
@@
 The construction based on the integral quantities on edges can be done similarly.
-Assembling the local constructions for each dual volume, the global construction can be written as
+Assembling the local constructions for each dual cell, the global construction can be written as
 \begin{equation}
@@
 The BCs for the Euler system (see Section \ref{sec:BC}) are implemented by the approach of ghost cells \cite[][ch.
-7]{leveque_2007}, namely thinking of extending the domain by a few additional cells and prescribing the variables.
+7]{leveque_2007}, i.e.
+thinking of extending the domain by a few additional cells and prescribing the variables.
 In our case, the ghost cells at the open boundary at $\Gamma_C$ are set to have the equal values as the interior ones that are adjacent.
@@
 \end{equation*}
-where $j$ refers to the index of the volume adjacent to the boundary face $\Tilde{A}_i$ and is unique.
+where $j$ refers to the index of the cell adjacent to the boundary face $\Tilde{A}_i$ and is unique.
 For the reflective wall $\Gamma_W$, the momentum of a ghost cell are reversed with respect to its adjacent one while keeping the other quantities unchanged.
@@
     \begin{align}
-    \varphi_i = \Phi(P_i, t), \ \ &\forall i : P_i \subset \Gamma_C, \\
+    \varphi_i = \varphi(P_i, t), \ \ &\forall i : P_i \subset \Gamma_C, \\
     e_i = (\mathbb{G}\bm{\varphi})_i,\ \ &\forall i : L_i \subset \partial\Omega, \\
@@
 \begin{remark}
-    The 1D reduction of the FIT-FVM discretization can be interpreted in the sense of finite difference. 
+    The 1D reduction of FIT-FVM discretization can be interpreted in the sense of finite difference. 
 \end{remark}
@@
 In \cite{degond_2012}, based on the linearized stability analysis, the author shows that the full-implicit treatment of the Maxwell equations is essential to the stability in the quasi-neutral limit.
-Besides, the mass flux in the mass conservation equation and the current in Amp\`{e}re's law have the same degree of implicitness in order to guarantee the consistency with Gauss's law.
+Besides, the mass flux in the mass conservation equation and the current in Amp\`{e}re's law have the same level of implicitness in order to guarantee the consistency with Gauss's law.
 
@@
 
-\subsubsection{Inappropriate Boundary Condition}
+\subsubsection{Inappropriate Boundary Condition} \label{sec:inapp_bc}
 We notice that the boundary condition (\ref{equ:bc_zero_curl_h}) is not valid in the quasi-neutral limit, which is revealed by taking the limit of Amp\`{e}re's law in the non-conducting region (\ref{equ:maxwell_ampere_nonconducting_ap}).
@@
 Due to the fact that $\mathbf{j}$ and $\mathbf{d}$ are both defined on dual faces, it is reasonable to adopt a local relation between them.
-Therefore, we perform the \emph{diagonal lumping} trick on (\ref{equ:discrete_ohm}), namely rendering it diagonal by accumulating the row sum.
+Therefore, we perform the \emph{diagonal lumping} trick on (\ref{equ:discrete_ohm}), i.e.
+rendering it diagonal by accumulating the row sum.
 We observe enhanced stability in the numerical experiments with very minor changes in the results.
@@
 \section{Numerical Experiment}
-We conduct numerical experiments based on the geometrical setting and boundary conditions presented in Section \ref{sec:BC}.
+We conduct numerical experiments based on the geometric setting and boundary conditions as presented in Section \ref{sec:BC}.
 The primal-dual mesh pair $(\mathcal{M}, \mathcal{M}')$ is generated based on the code developed in \cite[][ch.
@@
 \end{figure}
-\subsection{Quasi-1D Problem}
-On noticing the radial symmetry of the domain as well as boundary conditions, the governing equations defined at the axis of symmetry, namely $z$-axis in this case, can be tremendously simplified thanks to vanishing radial components of vector variables and radial derivatives.
-The Euler-Maxwell system at the axis of symmetry is formulated as
+\subsection{Case 1: Quasi-1D Problem}
+On noticing the radial symmetry of the domain as well as boundary conditions, we can simplify the governing equations defined at the axis of symmetry, i.e.
+$z$-axis in this case, thanks to vanishing radial components of the vector fields and their radial derivatives.
+The Euler-Maxwell system at the axis of symmetry reduces to
 \begin{align*}
@@
 \end{align*}
-which shares a similar structure as the 1D model in Section \ref{sec:projection_to_1d}.
+which is similar to the 1D model in Section \ref{sec:projection_to_1d}.
 Therefore, it is reasonable to compare the results produced by the 1D scheme in Section \ref{sec:1d_fully_discrete_model} and the one on $z$-axis produced by the 3D scheme proposed in Section \ref{sec:3d_ap_scheme}.
@@
 
-\subsection{3D Cylindrical Problem}
-Sticking to the setting in Section \ref{sec:BC}, we set initial conditions
+\subsection{Case 2: 3D Cylindrical Problem}
+We stick to the setting in Section \ref{sec:BC} and use the following initial conditions
 \begin{equation*}
-    n_i(\mathbf{x}, 0) = n_e(\mathbf{x},0) = 1, \ \ \  p_i(\mathbf{x},0) = p_e(\mathbf{x},0) = 1.
+    n_\ast(\mathbf{x}, 0) = 1, \ \ \  p_\ast(\mathbf{x},0) = 1, \ \ \forall \mathbf{x}\in\Omega, \ast \in \{\text{electron}, \text{ion}\}.
 \end{equation*}
-All the other quantities are vanishing initially.
-The electrode at $\Gamma_C^1$(cathode) is grounded, and the one at $\Gamma_C^2$ (anode) has potential 1.0 throughout the simulation, namely $\Phi(\mathbf{x}, t)|_{\Gamma_C^1} = 0, \Phi(\mathbf{x}, t)|_{\Gamma_C^2} = 1$.
-The experiment is intended to study how a stationary system responds to an applied voltage.
+All the other quantities are set zero initially.
+The electrode at $\Gamma_C^-$(cathode) is grounded, and the one at $\Gamma_C^+$ (anode) has potential 1.0 throughout the simulation, i.e.
+$\varphi(\mathbf{x}, t)|_{\Gamma_C^-} = 0, \varphi(\mathbf{x}, t)|_{\Gamma_C^+} = 1$.
+The experiment is intended to investigate how a stationary system is driven by an applied voltage.
 
 \begin{remark}
-    Such an initial state is compatible with the BCs and the quasi-neutral condition $\rho = 0$. 
+    Such an initial state is compatible with the BCs and the quasi-neutral condition $\rho = 0$, which means no initial layer and boundary layer will arise when $\lambda \rightarrow 0$. 
 \end{remark}
@@
 In Fig.
-\ref{fig:3d_vec_field_E_B_ue} we present the vector fields of the numerical solutions for $\lambda = 1.0, 0.01, 0$ at $t = 0.1$, aiming to give an intuitive visualization.
-First of all, one \emph{a priori} expects the rotational symmetry in the solutions, which serves as a basic criterion to justify the results.
+\ref{fig:3d_vec_field_E_B_ue}, the numerical solutions for $\lambda = 1.0, 0.01, 0$ at $t = 0.1$ are visualized.
+The expected rotational symmetry of the problem is preserved.
 In terms of the 3D structure of the electromagnetic fields, the electric field points from the anode to the cathode, and the magnetic field is spiral-shaped and orthogonal to the electric field.
-The electrons move in the inverse direction of the electric field.
-Regarding the asymptotic behavior of the AP scheme, the primary concern is its validity in the limiting case.
-For this case, the scheme manages to produce a meaningful numerical solution when $\lambda = 0$.
-Besides, by comparing the solutions for different $\lambda$, the smooth transition from the non-neutrality to quasi-neutrality is observed, which is an implication that the scheme reproduces the asymptotic behavior of the analytical solutions from the non-neutral model to the quasi-neutral one.
+Regarding the asymptotic behavior of the AP scheme, the scheme does not incur any instability when we set $\lambda = 0$.
+Besides, smooth transition of the numerical solutions for different values of $\lambda$ is observed, as is the case for the continuous solutions as $\lambda \rightarrow 0$.
 \begin{figure}
@@
 Due to the high computational cost incurred by the curse of dimensionality, only meshes with limited size are tested and the asymptotic regime of the grid study might be not reached.
-Nevertheless, it still helps to reveal the independence of solutions with respect to meshes --- the norms of electron density and the magnetic field do not deviate in a divergent manner.
-The exception of the norm of the electric field possibly results from the singularity caused by the interface of the contacting and insulating surfaces, as will be seen later.
+Particularly, the divergence of the norm of $\mathbf{E}$-field may come from the singularity arising at the interface of the contacting and insulating surfaces, as is shown below.
+
 In Fig.
-\ref{fig:grid_study_3d_clip_lambda-1e-1} and \ref{fig:grid_study_3d_clip_lambda-0}, we plot the distribution of certain quantities at the cross-section based on different meshes for $\lambda = 0.1$ and $0$ at $t = 1$.
-Thanks to the rotational symmetry of the problem, the solution at the cross-section suffices to characterize the whole solution.
-The figures again demonstrate the stability of the numerical solutions with respect to mesh refinement in the sense that qualitatively the same solutions are produced by a series of meshes of different sizes.
-We would like to point out that singularity arises in the $\mathbf{E}$-field at the interface of contacting and insulating surfaces (two points at the left end and two at the right end).
-In numerical experiments, we observe an increasing magnitude of the $\mathbf{E}$-field at these points as the mesh is refined.
-Furthermore, it is noted from Fig.
-\ref{fig:grid_study_3d_clip_lambda-0} (last two rows) that when $\lambda = 0$, the charges carried by ions and electrons cancel out everywhere as indicated by the quasi-neutral condition $\rho = 0$.
+\ref{fig:grid_study_3d_clip_lambda-1e-1} and \ref{fig:grid_study_3d_clip_lambda-0}, we plot quantities at the cross-section generated by meshes of different sizes for $\lambda = 0.1$ and $0$ at $t = 1$.
+Qualitatively the same solutions are produced under different meshes.
+We would like to point out that singularity arises in the $\mathbf{E}$-field at the interface of contacting and insulating surfaces (two points at the left end and two at the right end), that is, an increasing magnitude of the $\mathbf{E}$-field at these points as the mesh is refined.
+Furthermore, as is shown in the last two rows of Fig.
+\ref{fig:grid_study_3d_clip_lambda-0}, when $\lambda = 0$ the charges carried by ions and electrons cancel out everywhere as is indicated by the quasi-neutral condition $\rho = 0$.
 
@@
 \ref{fig:origin-data_vs_time}.
-Being originally at rest, the system is excited by the suddenly applied voltage and generates oscillations that dampen over time.
+Being originally at rest, the system is excited by the applied voltage and generates oscillations that dampen over time.
 In general, a large value of $\lambda$ leads to stronger oscillations with larger amplitude whereas smaller $\lambda$ incurs more damping and the system rapidly reaches a steady state.
 It is a reflection of the shielding effect of plasma which is characterized by the Debye length.
-It can also be noticed that the electron velocity becomes steady much sooner than ion velocity, which is a consequence of the huge difference in inertia.
-Besides, the convergence of the discrete model as $\lambda \rightarrow 0$ can be observed---the solution becomes steady over time.
+It can also be noticed that the electron velocity becomes steady much sooner than ion velocity, which is a consequence of their large difference in inertia.
 \begin{figure}
@@
 
-A critical sign of quasi-neutrality is the vanishing charge.
-In fact, in Section \ref{sec:quasi-neutral_limit} we discuss the limiting model where $\rho = 0$ is satisfied.
-To examine that, the quantities at the $z$-axis over different $\lambda$ are provided in Fig.
+To examine the quasi-neutrality, we plot the quantities at the $z$-axis over different $\lambda$ in Fig.
 \ref{fig:zaxis-data_vs_z-T_10}.
-The right figure demonstrates the approaching and eventual coincidence of electron and ion densities as $\lambda \rightarrow 0$.
-Furthermore, with relatively small but non-zero $\lambda$, the bulk of the plasma is approximately neutral while the area near the electrodes is not, which is known as a plasma sheath and within such an area the quasi-neutrality is usually inappropriate.
+The right figure demonstrates the shielding effect of the charges as $\lambda \rightarrow 0$.
+
+\todo{demonstration instability without stabilization}
+\todo{redo the mesh study}
+
 \begin{figure}

### 2022-11-03 paper_version/main.tex
minor change

@@
 In the same way, the dual mesh $\Tilde{\mathcal{M}}$ is defined by $\{\Tilde{P}, \Tilde{L}, \Tilde{A}, \Tilde{V}\}$.
-Elements of two meshes are associated with bijective mappings $P \leftrightarrow \Tilde{V}$, $L \leftrightarrow \Tilde{A}$, $A \leftrightarrow \Tilde{L}$ and $V \leftrightarrow \Tilde{P}$ which arise in a very natural way: $P(\Tilde{P} \text{ resp.})$ corresponds to $\Tilde{V}(V \text{ resp.})$ where it lies and $L(\Tilde{L} \text{ resp.})$ penetrates its corresponding $\Tilde{A}(A \text{ resp.})$.
+Elements of two meshes are associated with bijective pairings $P \leftrightarrow \Tilde{V}$, $L \leftrightarrow \Tilde{A}$, $A \leftrightarrow \Tilde{L}$ and $V \leftrightarrow \Tilde{P}$ which arise in a very natural way: $P(\Tilde{P} \text{ resp.})$ corresponds to $\Tilde{V}(V \text{ resp.})$ where it lies and $L(\Tilde{L} \text{ resp.})$ penetrates its corresponding $\Tilde{A}(A \text{ resp.})$.
 According to their dimensions, vertices, edges, faces and cells are also termed 0-dim, 1-dim, 2-dim and 3-dim elements respectively.
@@
 \ref{fig:orientation}.
-For the elements of the dual mesh $\Tilde{\mathcal{M}}$, we set their internal orientations to be aligned with their corresponding primal elements according to the bijective mappings, i.e.
+For the elements of the dual mesh $\Tilde{\mathcal{M}}$, we set their internal orientations to be aligned with their corresponding primal elements according to the bijective pairings, i.e.
 edges penetrate faces.

### 2022-11-08 paper_version/main.tex
minor change

@@
 This mental experiment aims to help readers understand how the new 3D scheme originates from the 1D one.
-\subsubsection{Projection to one dimension} \label{sec:projection_to_1d}
+\subsubsection{Projection to One Dimension} \label{sec:projection_to_1d}
 Consider a mesh pair $(\mathcal{M}, \mathcal{M}')$ that are constructed by 2D extrusion along $z$-axis and are unbounded along transverse directions on $x$-$y$ plane.
@@
 
-\subsubsection{1D plasma fully-discrete model} \label{sec:1d_fully_discrete_model}
+\subsubsection{1D Fully-discrete Plasma Model} \label{sec:1d_fully_discrete_model}
 The following fully-discrete scheme is proposed in \cite{degond_2012}.
@@
 
-\subsubsection{CFL condition}
+\subsubsection{CFL Condition}
 It has been shown in \cite{degond_2012} that the stability-induced constraint on the time-step size does not depend on the value of $\lambda$ thanks to the implicitness in the discrete Maxwell system.
@@
 
-\subsubsection{Procedure of time-stepping}
+\subsubsection{Procedure of Time-stepping}
 The semi-implicit scheme (\ref{equ:maxwell_faraday_ap})-(\ref{equ:Q_coll_ap}) entails solving a linear system for each time step.
@@
 \section{Numerical Experiment}
+
 We conduct numerical experiments based on the geometric setting and boundary conditions as presented in Section \ref{sec:BC}.
@@
 \subsection{Case 2: 3D Cylindrical Problem}
+
+\todo{demonstration instability without stabilization}
+
+\todo{redo the mesh study}
+
+\todo{supplement results for sin voltage}
+
+\todo{visualize in a better way}
+
 We stick to the setting in Section \ref{sec:BC} and use the following initial conditions
@@
 
-\todo{demonstration instability without stabilization}
-\todo{redo the mesh study}
-
 \begin{figure}

### 2022-11-11 paper_version/main.tex
rewrite numerical experiments section

@@
 \usepackage{caption, subcaption}
+\captionsetup[figure]{labelfont={bf},name={Fig.},labelsep=period}
+\captionsetup[table]{labelfont={bf},name={Tab.},labelsep=period}
 \usepackage{authblk}
@@
     \includegraphics[scale=0.3]{dual_mesh.png}
-    \caption{Primal mesh (left) and dual mesh(right).}
+    \caption{Primal mesh (left) and dual mesh (right).}
     \label{fig:primal_dual_meshes}
@@
 
-\todo{demonstration instability without stabilization}
-
-\todo{redo the mesh study}
-
-\todo{supplement results for sin voltage}
-
-\todo{visualize in a better way}
-
 We stick to the setting in Section \ref{sec:BC} and use the following initial conditions
@@
 All the other quantities are set zero initially.
-The electrode at $\Gamma_C^-$(cathode) is grounded, and the one at $\Gamma_C^+$ (anode) has potential 1.0 throughout the simulation, i.e.
-$\varphi(\mathbf{x}, t)|_{\Gamma_C^-} = 0, \varphi(\mathbf{x}, t)|_{\Gamma_C^+} = 1$.
-The experiment is intended to investigate how a stationary system is driven by an applied voltage.
+We set $\varphi(\mathbf{x}, t)|_{\Gamma_C^-} = 0, \varphi(\mathbf{x}, t)|_{\Gamma_C^+} = 1$, that is, a constant voltage is applied at the anode and want to see how the system is driven.
+
+The cylindrical domain is 5.0 in length and 1.5 in radius. The plasma domain $\Omega_P$ has 1.0 in radius, i.e. the non-conducting domain $\Omega_N$ has an inner radius 1.0 and an outer radius 1.5.
 
@@
 In Fig.
-\ref{fig:3d_vec_field_E_B_ue}, the numerical solutions for $\lambda = 1.0, 0.01, 0$ at $t = 0.1$ are visualized.
-The expected rotational symmetry of the problem is preserved.
-In terms of the 3D structure of the electromagnetic fields, the electric field points from the anode to the cathode, and the magnetic field is spiral-shaped and orthogonal to the electric field.
-Regarding the asymptotic behavior of the AP scheme, the scheme does not incur any instability when we set $\lambda = 0$.
-Besides, smooth transition of the numerical solutions for different values of $\lambda$ is observed, as is the case for the continuous solutions as $\lambda \rightarrow 0$.
+\ref{fig:3d_vec_field_E_B_ue}, the numerical solutions for $\lambda = 1.0, 0.1$ and $0$ are shown and the 3D structure of the electromagnetic field is visualized.
+A qualitative verification can be done in many aspects.
+First, the rotational symmetry of the problem is preserved.
+Second, the $\mathbf{E}$-field points from $\Gamma^+_C$ to $\Gamma^-_C$ with a relatively uniform value of approximately 0.2 ($=\text{applied voltage}/\text{cylinder length}$) as a consequence of the curl-free property of the $\mathbf{E}$-field in steady state according to Faraday's law.
+This is also confirmed in Fig.
+\ref{fig:zaxis-data_vs_z-T_10}.
+Note that it does not hold for $\lambda = 1$ since the system has a large characteristic time and takes a long time to reach a equilibrium, which will be shown later in Fig.
+\ref{fig:origin-data_vs_time}.
+Besides, the $\mathbf{B}$-field is spiral-shaped and orthogonal to the $\mathbf{E}$-field.
+Also, under the driven force by the $\mathbf{E}$-field, the electrons move towards the anode $\Gamma^+_C$ as expected.
 \begin{figure}
     \centering
-    \includegraphics[scale=0.35]{E_lambda_1.png}
-    \includegraphics[scale=0.35]{B_lambda_1.png}
-    \includegraphics[scale=0.35]{ue_lambda_1.png} \\
-    (a) $\lambda = 1.0$ \\
-    \includegraphics[scale=0.35]{E_lambda_1e-2.png}
-    \includegraphics[scale=0.35]{B_lambda_1e-2.png}
-    \includegraphics[scale=0.35]{ue_lambda_1e-2.png} \\
-    (b) $\lambda = 0.01$ \\
-    \includegraphics[scale=0.35]{E_lambda_0.png}
-    \includegraphics[scale=0.35]{B_lambda_0.png}
-    \includegraphics[scale=0.35]{ue_lambda_0.png} \\
-    (c) $\lambda = 0$
-    \caption{Snapshots of the $\mathbf{E}$-field, $\mathbf{B}$-field, and $\mathbf{u}_e$ for different $\lambda$ at $t = 10$ based on a primal mesh with 1920 cells (8 cells along $z$-axis). } 
+    \begin{subfigure}[b]{\textwidth}
+        \hspace{-1cm}
+        \begin{tikzpicture}
+        \draw[blue, -to] (0,0) -- (20:0.7) node[right]{\small $z$};
+        \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
+        \draw[blue, -to] (0,0) -- (0.7,0) node[below]{\small $y$};
+        \end{tikzpicture}
+        \includegraphics[scale=0.25]{E-field_lambda-1.png}
+        \includegraphics[scale=0.25]{B-field_lambda-1.png}
+        \includegraphics[scale=0.25]{electronVel_lambda-1.png}
+        \caption{$\lambda = 1.0$}
+    \end{subfigure}
+     \begin{subfigure}[b]{\textwidth}
+        \hspace{-1cm}
+        \begin{tikzpicture}
+        \draw[blue, -to] (0,0) -- (20:0.7) node[right]{\small $z$};
+        \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
+        \draw[blue, -to] (0,0) -- (0.7,0) node[below]{\small $y$};
+        \end{tikzpicture}
+        \includegraphics[scale=0.25]{E-field_lambda-1e-1.png}
+        \hspace{0.3cm}
+        \includegraphics[scale=0.25]{B-field_lambda-1e-1.png}
+        \includegraphics[scale=0.25]{electronVel_lambda-1e-1.png}
+        \caption{$\lambda = 1.0$}
+    \end{subfigure}
+    \begin{subfigure}[b]{\textwidth}
+        \hspace{-1cm}
+        \begin{tikzpicture}
+        \draw[blue, -to] (0,0) -- (20:0.7) node[right]{\small $z$};
+        \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
+        \draw[blue, -to] (0,0) -- (0.7,0) node[below]{\small $y$};
+        \end{tikzpicture}
+        \includegraphics[scale=0.25]{E-field_lambda-0.png}
+        \hspace{0.3cm}
+        \includegraphics[scale=0.25]{B-field_lambda-0.png}
+        \includegraphics[scale=0.25]{electronVel_lambda-0.png}
+        \caption{$\lambda = 1.0$}
+    \end{subfigure}
+    \caption{Snapshots of the $\mathbf{E}$-field, $\mathbf{B}$-field, and $\mathbf{u}_e$ for different $\lambda$ at $t = 10$ based on a primal mesh with 1920 cells (16 cells along $z$-axis). } 
     \label{fig:3d_vec_field_E_B_ue}
@@
 
-We perform the grid study and show the result in Fig.
+Next, we perform a grid study.
+The norms of the solutions under mesh refinement is shown in Fig.
 \ref{fig:grid_study_3d}.
-Meshes with different refinement levels are tested for $\lambda = 1$ and $0.1$ at $t = 1$, and the norms of the quantities are calculated.
-Due to the high computational cost incurred by the curse of dimensionality, only meshes with limited size are tested and the asymptotic regime of the grid study might be not reached.
-Particularly, the divergence of the norm of $\mathbf{E}$-field may come from the singularity arising at the interface of the contacting and insulating surfaces, as is shown below.
-
-In Fig.
-\ref{fig:grid_study_3d_clip_lambda-1e-1} and \ref{fig:grid_study_3d_clip_lambda-0}, we plot quantities at the cross-section generated by meshes of different sizes for $\lambda = 0.1$ and $0$ at $t = 1$.
+Due to the high computational cost in 3D simulations, a reference solutions produced by a highly-refined mesh is not accessible.
+That is why we compute the norms and display results only generated by relatively coarse meshes.
+Fig.
+\ref{fig:grid_study_3d} gives an indication that the solutions are stable under mesh refinement.
+To reveal more features of the solutions, in Fig.
+\ref{fig:grid_study_3d_clip_lambda-1e-1} and \ref{fig:grid_study_3d_clip_lambda-0}, we plot quantities at the cross-section generated by meshes of different sizes for $\lambda = 0.1$ and $0$.
 Qualitatively the same solutions are produced under different meshes.
-We would like to point out that singularity arises in the $\mathbf{E}$-field at the interface of contacting and insulating surfaces (two points at the left end and two at the right end), that is, an increasing magnitude of the $\mathbf{E}$-field at these points as the mesh is refined.
-Furthermore, as is shown in the last two rows of Fig.
-\ref{fig:grid_study_3d_clip_lambda-0}, when $\lambda = 0$ the charges carried by ions and electrons cancel out everywhere as is indicated by the quasi-neutral condition $\rho = 0$.
 
@@
     \centering
-    \includegraphics[scale=0.9]{norm_vs_nCell-T_1.eps}
+    \includegraphics[scale=0.8]{norm-vs-mesh.eps}
     \caption{1-norms of quantities with respect to different mesh size: The results are computed for $\lambda = 1$ and $0.1$ at $t = 1$.}.
@@
     \centering
-    Refinement 1\hspace{2.5cm}Refinement 2\hspace{2.5cm}Refinement 3\hspace{1cm}
+    \textit{\textsf{Refinement 1\hspace{2.5cm}Refinement 2\hspace{2.5cm}Refinement 3\hspace{1cm}}}
 
@@
     \includegraphics[scale=0.27]{clip_ni_T-1_lambda-1e-1_32-3-4.png}
-    \caption{Quantities at the cross-section generated by meshes with different refinement level.
-Refinement 1: 1920 primal cells; Refinement 2: 14592 primal cells; Refinement 3: 30720 primal cells.
+    \caption{Quantities at the cross-section generated by meshes with different refinement level: 1920 primal cells in Refinement 1; 14592 primal cells in Refinement 2; 30720 primal cells in refinement 3.
 The snapshots are computed for $\lambda = 0.1$ at $t = 1$.}
@@
 
-To inspect how the system evolves, we extract the time histories of certain quantities at the origin (the center of the tube) up to $t = 10$ and display them in Fig.
+To inspect how the system evolves, the time histories of some quantities are displayed in Fig.
 \ref{fig:origin-data_vs_time}.
 Being originally at rest, the system is excited by the applied voltage and generates oscillations that dampen over time.
-In general, a large value of $\lambda$ leads to stronger oscillations with larger amplitude whereas smaller $\lambda$ incurs more damping and the system rapidly reaches a steady state.
-It is a reflection of the shielding effect of plasma which is characterized by the Debye length.
-It can also be noticed that the electron velocity becomes steady much sooner than ion velocity, which is a consequence of their large difference in inertia.
+A larger value of $\lambda$ leads to stronger oscillations with larger amplitude whereas smaller $\lambda$ incurs more damping and the system rapidly reaches a steady state, which is consistent to the fact that $\lambda$ characterizes the time scale of the electromagnetic field.
+From a different perspective, it is a reflection of the shielding effect of plasma which is characterized by the Debye length.
+Besides, the electrons move much faster and oscillate more than ions as a consequence of large difference in inertia.
+Furthermore, the structure-preserving property of our scheme is revealed by the exact balance of the currents at $\Gamma^+_C$ and $\Gamma^-_C$ \cite{Hiptmair_2021}, as is shown in the last figure in Fig.
+\ref{fig:origin-data_vs_time}.
+
 \begin{figure}
     \centering
-    \includegraphics[scale=0.9]{origin_data-vs-time_withInsulator.eps}
-    \caption{Time histories of quantities at the origin for different $\lambda$. The simulation is done on a mesh with 1920 primal cells with 8 layers along $z$-axis.}
+    \includegraphics[scale=0.9]{data-vs-time_stepVoltage.eps}
+    \caption{Time histories of quantities at the domain center and of the averaged current densities at $\Gamma^+_C$ (anode) and $\Gamma^-_C$ (cathode) for different value of $\lambda$.
+The simulations are done on a mesh with 1920 primal cells with 8 layers along $z$-axis.}
     \label{fig:origin-data_vs_time}
@@
 
-To examine the quasi-neutrality, we plot the quantities at the $z$-axis over different $\lambda$ in Fig.
+The stabilization proposed in Section \ref{sec:reform_discrete} is essential to achieve a stable result when $\lambda$ tends to zero.
+As is shown in Fig.
+\ref{fig:stabilization_comparison}, the scheme without stabilization produces blow-up when $\lambda$ is close to zero while the the one with stabilization remains stable.
+\begin{figure}
+    \centering
+    \includegraphics{stabilizationComparision_stepVoltage.eps}
+    \caption{Stabilization in the non-conducting domain $\Omega_N$. The $\mathbf{E}$-field z-component in a boundary cell in $\Omega_N$ is displayed over time. }
+    \label{fig:stabilization_comparison}
+\end{figure}
+
+The capability of our approach to address the non-neutral ($\lambda = \mathcal{O}(1)$) and quasi-neutral ($\lambda = 0$) regimes has been demonstrated in the aformentioned results in the sense that it is stable under different values of $\lambda$.
+Another important check goes to the quasi-neutral condition, i.e.
+$\rho = 0$ (\ref{equ:maxwell_gauss_D_limit}) when $\lambda = 0$.
+We display the $\mathbf{E}$-field and particle densities on $z$-axis in Fig.
 \ref{fig:zaxis-data_vs_z-T_10}.
-The right figure demonstrates the shielding effect of the charges as $\lambda \rightarrow 0$.
+The lower figure clearly demonstrates the matching of the density profiles of the electrons and ions.
 
@@
     \centering
-    \includegraphics{zaxis-data_vs_z-T_10.eps}
+    \includegraphics{data-vs-z_stepVoltage.eps}
     \caption{Quantities along $z$-axis for different $\lambda$: The results are computed at $t = 10$ on a mesh with 1920 primal cells with 8 layers along $z$-axis.}.

### 2022-11-11 paper_version/main.tex
fix some syntax errors in English

@@
 
-An asymptotic preserving scheme for single- and multi-fluid Euler-Maxwell system was proposed by \cite{degond_2012} for one spatial dimension.
+An asymptotic-preserving scheme for single- and multi-fluid Euler-Maxwell system was proposed by \cite{degond_2012} for one spatial dimension.
 We extend their scheme to three dimensions.
@@
 Consider a mesh pair $(\mathcal{M}, \mathcal{M}')$ that are constructed by 2D extrusion along $z$-axis and are unbounded along transverse directions on $x$-$y$ plane.
-On assuming the transverse invariance and rotational symmetry, one can reduce the 3D problem to a 1D one along $z$-axis.
+On assuming the transverse invariance and rotational symmetry, one can reduce the 3D problem to a 1D one along the $z$-axis.
 All the D.o.F.
 are now defined at the locations that are the projections of their original locations.
-For instance, an edge that is orthogonal to $z$-axis projects to a vertex while an edge parallel to $z$-axis projects to an edge.
+For instance, an edge that is orthogonal to the $z$-axis projects to a vertex while a parallel edge to the $z$-axis is projected to an edge.
 The procedure is sketched in Fig.
@@
 In \cite{degond_2012}, the authors consider a 1D Maxwell-Euler system by assuming vanishing traverse derivatives.
-Besides, $u_y, E_y, B_x, B_z$ are set zero for simplicity, which amounts to considering the TE mode.
+Besides, $u_y, E_y, B_x$, and $B_z$ are set to zero for simplicity, which amounts to considering the TE mode.
 The 1D reduced Maxwell-Euler system and its quasi-neutral limit are
@@
 \end{minipage}
-where the subscript indicates the direction of the component. Here they consider a isentropic process with the equation of state $p(n) = n^\gamma$.
+where the subscript indicates the direction of the component. Here they consider an isentropic process with the equation of state $p(n) = n^\gamma$.
 
@@
 The spatial discretization can be interpreted by the 1D projection procedure illustrated above.
-Here we want to discuss the time discretization with a focus on its semi-implicitness.
+Here we want to discuss time discretization with a focus on its semi-implicitness.
 From now on, we attach to variables a superscript involving $m$ to indicate the time step.
@@
 In \cite{degond_2012}, based on the linearized stability analysis, the author shows that the full-implicit treatment of the Maxwell equations is essential to the stability in the quasi-neutral limit.
-Besides, the mass flux in the mass conservation equation and the current in Amp\`{e}re's law have the same level of implicitness in order to guarantee the consistency with Gauss's law.
+Besides, the mass flux in the mass conservation equation and the current in Amp\`{e}re's law has the same level of implicitness to guarantee consistency with Gauss's law.
 
@@
 \end{subequations}
-The quantities with superscript $m+1/2$ implies its dependency on the quantities at both $m$-th and $(m+1)$-th iterations.
+The quantities with superscript $m+1/2$ indicate their dependency on the quantities at both $m$-th and $(m+1)$-th iterations.
 In the Rusanov flux (\ref{equ:flux_ap}), we denote by $u_\perp$ the normal component velocity with respect to the dual face $\Tilde{A}_j$.
-We refrain the illustration of the collision term (\ref{equ:R_coll_ap}) (\ref{equ:Q_coll_ap}) to the two-species case for the sake of simplicity.
+We restrain the illustration of the collision term (\ref{equ:R_coll_ap}) (\ref{equ:Q_coll_ap}) to the two-species case for the sake of simplicity.
 
@@
 It has been shown in \cite{degond_2012} that the stability-induced constraint on the time-step size does not depend on the value of $\lambda$ thanks to the implicitness in the discrete Maxwell system.
-However, the Euler system is discretized by an explicit scheme and thus still subject to a CFL condition.
-
-In our case we have an conservation law with source terms. Let us consider the model equation
+However, the Euler system is discretized by an explicit scheme and thus is still subject to a CFL condition.
+
+In our case, we have a conservation law with source terms. Let us consider the model equation
 \begin{equation*}
@@
 The discrete Maxwell system (\ref{equ:maxwell_faraday_ap})-(\ref{equ:gauss_nonconducting_ap}) is closed provided (\ref{equ:discrete_ohm}) and can be evolved by solving a linear system.
-The Euler system (\ref{equ:euler_ap}) can afterwards be evolved explicitly.
+The Euler system (\ref{equ:euler_ap}) can afterward be evolved explicitly.
 
@@
 Since in the quasi-neutral limit $\lambda \rightarrow 0$ we lose control of the $\mathbf{E}$-field through its time derivative, $\mathbb{M}_\sigma^m$ is crucial to the stability of the scheme.
-Due to the fact that $\mathbf{j}$ and $\mathbf{d}$ are both defined on dual faces, it is reasonable to adopt a local relation between them.
+Since $\mathbf{j}$ and $\mathbf{d}$ are both defined on dual faces, it is reasonable to adopt a local relation between them.
 Therefore, we perform the \emph{diagonal lumping} trick on (\ref{equ:discrete_ohm}), i.e.
@@
     \caption{Comparison of 1D two-fluid model and reduced 1D model on $z$-axis from 3D two-fluid model.
-The results are both generated on meshes with 64 cells along $z$-axis.
+The results are both generated on meshes with 64 cells along the $z$-axis.
 No friction term exists.
@@
 \end{equation*}
-All the other quantities are set zero initially.
+All the other quantities are set to zero initially.
 We set $\varphi(\mathbf{x}, t)|_{\Gamma_C^-} = 0, \varphi(\mathbf{x}, t)|_{\Gamma_C^+} = 1$, that is, a constant voltage is applied at the anode and want to see how the system is driven.
 
-The cylindrical domain is 5.0 in length and 1.5 in radius. The plasma domain $\Omega_P$ has 1.0 in radius, i.e. the non-conducting domain $\Omega_N$ has an inner radius 1.0 and an outer radius 1.5.
+The cylindrical domain is 5.0 in length and 1.5 in radius.
+The plasma domain $\Omega_P$ has 1.0 in radius, i.e.
+the non-conducting domain $\Omega_N$ has an inner radius of 1.0 and an outer radius of 1.5.
 
@@
 \ref{fig:3d_vec_field_E_B_ue}, the numerical solutions for $\lambda = 1.0, 0.1$ and $0$ are shown and the 3D structure of the electromagnetic field is visualized.
-A qualitative verification can be done in many aspects.
+Qualitative verification can be done in many aspects.
 First, the rotational symmetry of the problem is preserved.
-Second, the $\mathbf{E}$-field points from $\Gamma^+_C$ to $\Gamma^-_C$ with a relatively uniform value of approximately 0.2 ($=\text{applied voltage}/\text{cylinder length}$) as a consequence of the curl-free property of the $\mathbf{E}$-field in steady state according to Faraday's law.
+Second, the $\mathbf{E}$-field points from $\Gamma^+_C$ to $\Gamma^-_C$ with a relatively uniform value of approximately 0.2 ($=\text{applied voltage}/\text{cylinder length}$) as a consequence of the curl-free property of the $\mathbf{E}$-field in the steady state according to Faraday's law.
 This is also confirmed in Fig.
 \ref{fig:zaxis-data_vs_z-T_10}.
-Note that it does not hold for $\lambda = 1$ since the system has a large characteristic time and takes a long time to reach a equilibrium, which will be shown later in Fig.
+Note that it does not hold for $\lambda = 1$ since the system has a large characteristic time and takes a long time to reach an equilibrium, which will be shown later in Fig.
 \ref{fig:origin-data_vs_time}.
@@
 Next, we perform a grid study.
-The norms of the solutions under mesh refinement is shown in Fig.
+The norms of the solutions under mesh refinement are shown in Fig.
 \ref{fig:grid_study_3d}.
-Due to the high computational cost in 3D simulations, a reference solutions produced by a highly-refined mesh is not accessible.
+Due to the high computational cost in 3D simulations, reference solutions produced by a highly-refined mesh are not accessible.
 That is why we compute the norms and display results only generated by relatively coarse meshes.
 Fig.
-\ref{fig:grid_study_3d} gives an indication that the solutions are stable under mesh refinement.
+\ref{fig:grid_study_3d} indicates that the solutions are stable under mesh refinement.
 To reveal more features of the solutions, in Fig.
@@
     \includegraphics[scale=0.8]{norm-vs-mesh.eps}
-    \caption{1-norms of quantities with respect to different mesh size: The results are computed for $\lambda = 1$ and $0.1$ at $t = 1$.}.
+    \caption{1-norms of quantities with respect to different mesh sizes: The results are computed for $\lambda = 1$ and $0.1$ at $t = 1$.}.
     \label{fig:grid_study_3d}
@@
     \includegraphics[scale=0.27]{clip_ni_T-1_lambda-1e-1_32-3-4.png}
-    \caption{Quantities at the cross-section generated by meshes with different refinement level: 1920 primal cells in Refinement 1; 14592 primal cells in Refinement 2; 30720 primal cells in refinement 3.
+    \caption{Quantities at the cross-section generated by meshes with different refinement levels: 1920 primal cells in Refinement 1; 14592 primal cells in Refinement 2; 30720 primal cells in refinement 3.
 The snapshots are computed for $\lambda = 0.1$ at $t = 1$.}
@@
     \includegraphics[scale=0.27]{slice_ni_T-1_lambda-0_32-3-4.png}
-    \caption{Quantities at the cross-section generated by meshes with different refinement level.
+    \caption{Quantities at the cross-section generated by meshes with different refinement levels.
 Refinement 1: 1920 primal cells; Refinement 2: 14592 primal cells; Refinement 3: 30720 primal cells.
@@
 Being originally at rest, the system is excited by the applied voltage and generates oscillations that dampen over time.
-A larger value of $\lambda$ leads to stronger oscillations with larger amplitude whereas smaller $\lambda$ incurs more damping and the system rapidly reaches a steady state, which is consistent to the fact that $\lambda$ characterizes the time scale of the electromagnetic field.
+A larger value of $\lambda$ leads to stronger oscillations with larger amplitude whereas smaller $\lambda$ incurs more damping and the system rapidly reaches a steady state, which is consistent with the fact that $\lambda$ characterizes the time scale of the electromagnetic field.
 From a different perspective, it is a reflection of the shielding effect of plasma which is characterized by the Debye length.
-Besides, the electrons move much faster and oscillate more than ions as a consequence of large difference in inertia.
+Besides, the electrons move much faster and oscillate more than ions as a consequence of the large difference in inertia.
 Furthermore, the structure-preserving property of our scheme is revealed by the exact balance of the currents at $\Gamma^+_C$ and $\Gamma^-_C$ \cite{Hiptmair_2021}, as is shown in the last figure in Fig.
@@
     \includegraphics[scale=0.9]{data-vs-time_stepVoltage.eps}
-    \caption{Time histories of quantities at the domain center and of the averaged current densities at $\Gamma^+_C$ (anode) and $\Gamma^-_C$ (cathode) for different value of $\lambda$.
-The simulations are done on a mesh with 1920 primal cells with 8 layers along $z$-axis.}
+    \caption{Time histories of quantities at the domain center and of the averaged current densities at $\Gamma^+_C$ (anode) and $\Gamma^-_C$ (cathode) for different values of $\lambda$.
+The simulations are done on a mesh with 1920 primal cells with 8 layers along the $z$-axis.}
     \label{fig:origin-data_vs_time}
@@
 As is shown in Fig.
-\ref{fig:stabilization_comparison}, the scheme without stabilization produces blow-up when $\lambda$ is close to zero while the the one with stabilization remains stable.
+\ref{fig:stabilization_comparison}, the scheme without stabilization produces blow-up when $\lambda$ is close to zero while the one with stabilization remains stable.
 \begin{figure}
@@
 
-The capability of our approach to address the non-neutral ($\lambda = \mathcal{O}(1)$) and quasi-neutral ($\lambda = 0$) regimes has been demonstrated in the aformentioned results in the sense that it is stable under different values of $\lambda$.
+The capability of our approach to addressing the non-neutral ($\lambda = \mathcal{O}(1)$) and quasi-neutral ($\lambda = 0$) regimes has been demonstrated in the aforementioned results in the sense that it is stable under different values of $\lambda$.
 Another important check goes to the quasi-neutral condition, i.e.
 $\rho = 0$ (\ref{equ:maxwell_gauss_D_limit}) when $\lambda = 0$.
-We display the $\mathbf{E}$-field and particle densities on $z$-axis in Fig.
+We display the $\mathbf{E}$-field and particle densities on the $z$-axis in Fig.
 \ref{fig:zaxis-data_vs_z-T_10}.
-The lower figure clearly demonstrates the matching of the density profiles of the electrons and ions.
+The lower figure demonstrates the matching of the density profiles of the electrons and ions.
 

### 2022-11-11 paper_version/main.tex
fix some English syntax mistakes

@@
 We approximate the flux $\overline{\mathbf{f}}_j$ in (\ref{equ:euler_grid}) by a numerical flux $\mathbf{f}^\text{num}_j := \mathbf{f}^\text{num}\left(\overline{\mathbf{U}}_i, \overline{\mathbf{U}}_{k(i,j)}, \mathbf{n}_j\right)$, where $k(i,j)$ returns the index of the adjacent cell that shares $A_j$ with cell $V_i$.
-Classical numerical fluxes include Lax-Friedrich flux, Rusanov flux, Engquist-Osher flux, see \cite[][p.
+Classical numerical fluxes include Lax-Friedrich flux, Rusanov flux, and Engquist-Osher flux, see \cite[][p.
 44-46]{mishra_2019}.
@@
 
-We would like to emphasis that the Euler system is discretized on $\mathcal{M}'$ due to the fact that 1) the electric current is connected to the momenta of charged particles by (\ref{equ:maxwell_euler_coupling}); 2) the electric current is discretized on dual faces by (\ref{equ:maxwell_grid_ampere}).
+We would like to emphasize that the Euler system is discretized on $\mathcal{M}'$ due to the fact that 1) the electric current is connected to the momenta of charged particles by (\ref{equ:maxwell_euler_coupling}); 2) the electric current is discretized on dual faces by (\ref{equ:maxwell_grid_ampere}).
 
@@
     \item[-] given the fluxes at faces of a cell, reconstruct the vector field inside the cell;
-    \item[-] given the integrals along edges of a cell, reconstruct the vector field inside the cell. 
+    \item[-] given the integrals along the edges of a cell, reconstruct the vector field inside the cell. 
 \end{itemize}
-We adopt the principle of least square fitting, and reconstruct a \emph{constant} vector field inside each cell.
+We adopt the principle of least square fitting and reconstruct a \emph{constant} vector field inside each cell.
 For a cell $\Tilde{V}$ with $k$ faces with areas $\{A_i\}_{i=1}^k$, normal vectors $\{\mathbf{n}_i\}_{i=1}^k$ and fluxes $\{f_i\}_{i=1}^k$, a constant vector field $\mathbf{v}$ satisfying
@@
 thinking of extending the domain by a few additional cells and prescribing the variables.
-In our case, the ghost cells at the open boundary at $\Gamma_C$ are set to have the equal values as the interior ones that are adjacent.
-It is equivalent to enforce the numerical fluxes
+In our case, the ghost cells at the open boundary at $\Gamma_C$ are set to have equal values as the interior ones that are adjacent.
+It is equivalent to enforcing the numerical fluxes
 \begin{equation*}
@@
 where $j$ refers to the index of the cell adjacent to the boundary face $\Tilde{A}_i$ and is unique.
-For the reflective wall $\Gamma_W$, the momentum of a ghost cell are reversed with respect to its adjacent one while keeping the other quantities unchanged.
+For the reflective wall $\Gamma_W$, the momentum of a ghost cell is reversed with respect to its adjacent one while keeping the other quantities unchanged.
 Therefore, the numerical fluxes are

### 2022-11-11 paper_version/main.tex
a bit polishing

@@
 \subsection{Motivation: Reduction to 1D Discretization}
-Our work is an extension of the 1D scheme proposed in \cite{degond_2012} towards a scheme in three dimensions.
-Therefore, it is compatible with the original 1D scheme when one considers its reduction to one dimension.
-This mental experiment aims to help readers understand how the new 3D scheme originates from the 1D one.
+Our work is an extension of the 1D scheme proposed in \cite{degond_2012} towards three dimensions.
+Therefore, it is supposed to be compatible with the original 1D scheme when reduced to one dimension.
+This perspective helps to understand how the 3D scheme stems from the 1D one, which is not trivial.
+For the sake of presentation, we discuss their one-fluid model where ions are assumed immobile and only the motion of electrons is considered.
+
 \subsubsection{Projection to One Dimension} \label{sec:projection_to_1d}
-Consider a mesh pair $(\mathcal{M}, \mathcal{M}')$ that are constructed by 2D extrusion along $z$-axis and are unbounded along transverse directions on $x$-$y$ plane.
-On assuming the transverse invariance and rotational symmetry, one can reduce the 3D problem to a 1D one along the $z$-axis.
-All the D.o.F.
-are now defined at the locations that are the projections of their original locations.
-For instance, an edge that is orthogonal to the $z$-axis projects to a vertex while a parallel edge to the $z$-axis is projected to an edge.
-The procedure is sketched in Fig.
+Consider a mesh pair $(\mathcal{M}, \mathcal{M}')$ that are constructed by 2D extrusion along $z$-axis and are unbounded along transverse directions.
+On assuming the transverse invariance and rotational symmetry, we can ``project'' all the D.o.F.
+onto the $z$-axis.
+The idea is sketched in in Fig.
 \ref{fig:1d_reduction}.
@@
     \end{tikzpicture}
-    \caption{3D discretization to 1D. On the assumption of transverse invariance, we can reduce all the D.o.F. lying in the plane $z=z_k$ to the vertex at $z=z_k$. }
+    \caption{3D discretization to 1D.
+On the assumption of transverse invariance, we can reduce all the D.o.F.
+lying in the perpendicular plane $z=z_k$ to the vertex at $z=z_k$.
+For instance, an edge orthogonal to the $z$-axis is projected to a vertex while a parallel edge to the $z$-axis is projected to an edge.}
     \label{fig:1d_reduction}
@@
 
-In \cite{degond_2012}, the authors consider a 1D Maxwell-Euler system by assuming vanishing traverse derivatives.
-Besides, $u_y, E_y, B_x$, and $B_z$ are set to zero for simplicity, which amounts to considering the TE mode.
-The 1D reduced Maxwell-Euler system and its quasi-neutral limit are
+In \cite{degond_2012}, the author investigates a 1D Maxwell-Euler system by assuming vanishing traverse derivatives.
+For further simplicity, a transverse mode is considered, i.e.
+$u_y, E_y, B_x$, and $B_z$ are set to zero.
+The 1D reduced one-fluid Maxwell-Euler system and its quasi-neutral limit are
 
@@
 \end{minipage}
-where the subscript indicates the direction of the component. Here they consider an isentropic process with the equation of state $p(n) = n^\gamma$.
+where the subscript indicates the direction of the component. An isentropic process with the equation of state $p(n) = n^\gamma$ is assumed.
 
 \subsubsection{1D Fully-discrete Plasma Model} \label{sec:1d_fully_discrete_model}
-The following fully-discrete scheme is proposed in \cite{degond_2012}.
-The spatial discretization can be interpreted by the 1D projection procedure illustrated above.
-Here we want to discuss time discretization with a focus on its semi-implicitness.
-From now on, we attach to variables a superscript involving $m$ to indicate the time step.
+The fully-discrete scheme proposed in \cite{degond_2012} is given below.
+From now on, the superscript of variables involving $m$ indicates the time step.
 The scheme is built on a uniform 1D mesh with cell size $h$ and evolves the system with time step $\delta^m := t^{m+1} - t^m$:
@@
 \end{align*}
-The implicit terms are highlighted.
+The implicit terms are highlighted and are all essential to achieve the AP property.
 The implicitness of the electric field in the Lorentz force is shown to be necessary in \cite{fabre_1992} for the Euler-Poisson system.
@@
 \subsection{Semi-implicit Fully-discrete AP Scheme in 3D} \label{sec:3d_ap_scheme}
-Combining the 3D FIT-FVM framework presented in Section \ref{sec:spatial_discretization} and the time-stepping scheme shown below, we end up getting the following semi-implicit fully-discrete AP scheme in 3D:
+Combining the 3D FIT-FVM framework presented in Section \ref{sec:spatial_discretization} and the time-stepping scheme shown below, we propose the following semi-implicit fully-discrete AP scheme in 3D:
 \begin{subequations}
@@
 The quantities with superscript $m+1/2$ indicate their dependency on the quantities at both $m$-th and $(m+1)$-th iterations.
-In the Rusanov flux (\ref{equ:flux_ap}), we denote by $u_\perp$ the normal component velocity with respect to the dual face $\Tilde{A}_j$.
+In Rusanov flux (\ref{equ:flux_ap}), we denote by $u_\perp$ the normal component velocity with respect to the dual face $\Tilde{A}_j$.
 We restrain the illustration of the collision term (\ref{equ:R_coll_ap}) (\ref{equ:Q_coll_ap}) to the two-species case for the sake of simplicity.
@@
 \subsubsection{Inappropriate Boundary Condition} \label{sec:inapp_bc}
-We notice that the boundary condition (\ref{equ:bc_zero_curl_h}) is not valid in the quasi-neutral limit, which is revealed by taking the limit of Amp\`{e}re's law in the non-conducting region (\ref{equ:maxwell_ampere_nonconducting_ap}).
+We would like to point out that the boundary condition (\ref{equ:bc_zero_curl_h}) is not valid in the quasi-neutral limit, which is revealed by taking the limit of Amp\`{e}re's law in the non-conducting region (\ref{equ:maxwell_ampere_nonconducting_ap}).
 Since $\bm{\psi}^{m+1}$ can be shown to be zero by multiplying (\ref{equ:gauss_nonconducting_ap}) by $\mathbb{D}$, we obtain that
@@
 \begin{equation*}
-    [\mathbf{d}^{m+1} = 0]_i, \ \ \forall i : \Tilde{A}_i \subset \Omega_N,
+    [\mathbf{d}^{m+1} = 0]_i, \ \ \forall i : \Tilde{A}_i \subset \Omega_N.
 \end{equation*}
-since one can easily check that it is equivalent to (\ref{equ:bc_zero_curl_h}) for $\lambda = \mathcal{O}(1)$.
-In the meantime, it makes the Maxwell system in the non-conducting region well-posed in the quasi-neutral limit, which amounts to the eddy current model \cite{alfredo_2003}.
+One can easily check its equivalence to (\ref{equ:bc_zero_curl_h}) when $\lambda = \mathcal{O}(1)$.
+In fact, without this condition the Maxwell system in the non-conducting region is not well-posed when $\lambda = 0$ \cite{alfredo_2003}.
 
@@
 \end{equation*}
-which is proven necessary by numerical experiments.
+which is proved to be necessary by numerical experiments.
 
@@
 \end{equation*}
-Next, by the formula for the mass fluxes in (\ref{equ:flux_ap}), the expression for the currents in $\Omega_P$ (see (\ref{equ:maxwell_ampere_plasma_ap})) is written  
+Next, by the formula for the mass fluxes in (\ref{equ:flux_ap}), the expression for the currents in $\Omega_P$ (see (\ref{equ:maxwell_ampere_plasma_ap})) is written by 
 \begin{equation} \label{equ:discrete_ohm}
@@
 The discrete Maxwell system (\ref{equ:maxwell_faraday_ap})-(\ref{equ:gauss_nonconducting_ap}) is closed provided (\ref{equ:discrete_ohm}) and can be evolved by solving a linear system.
-The Euler system (\ref{equ:euler_ap}) can afterward be evolved explicitly.
+The Euler system (\ref{equ:euler_ap}) afterward evolves explicitly.
 
@@
 All the other quantities are set to zero initially.
-We set $\varphi(\mathbf{x}, t)|_{\Gamma_C^-} = 0, \varphi(\mathbf{x}, t)|_{\Gamma_C^+} = 1$, that is, a constant voltage is applied at the anode and want to see how the system is driven.
+We set $\varphi(\mathbf{x}, t)|_{\Gamma_C^-} = 0, \varphi(\mathbf{x}, t)|_{\Gamma_C^+} = 1$, that is, a constant voltage is applied at the anode and excites the system.
 
 The cylindrical domain is 5.0 in length and 1.5 in radius.
-The plasma domain $\Omega_P$ has 1.0 in radius, i.e.
+The plasma domain $\Omega_P$ is 1.0 in radius, i.e.
 the non-conducting domain $\Omega_N$ has an inner radius of 1.0 and an outer radius of 1.5.
@@
 \begin{remark}
-    Such an initial state is compatible with the BCs and the quasi-neutral condition $\rho = 0$, which means no initial layer and boundary layer will arise when $\lambda \rightarrow 0$. 
+    Such an initial state is compatible with the BCs and the quasi-neutral condition $\rho = 0$, which means no initial layer and boundary layer in the sense of perturbation theory will arise when $\lambda \rightarrow 0$.
 \end{remark}
@@
 In Fig.
-\ref{fig:3d_vec_field_E_B_ue}, the numerical solutions for $\lambda = 1.0, 0.1$ and $0$ are shown and the 3D structure of the electromagnetic field is visualized.
+\ref{fig:3d_vec_field_E_B_ue}, the numerical solutions for $\lambda = 1.0, 0.1$ and $0$ are shown to visualize the 3D structure of the electromagnetic field.
 Qualitative verification can be done in many aspects.
@@
 \ref{fig:grid_study_3d}.
-Due to the high computational cost in 3D simulations, reference solutions produced by a highly-refined mesh are not accessible.
-That is why we compute the norms and display results only generated by relatively coarse meshes.
+Due to the high computational cost in 3D simulations, reference solutions produced by a highly-refined mesh are not trivially accessible.
+That is why we demonstrate results generated by relatively coarse meshes.
 Fig.
@@
 To reveal more features of the solutions, in Fig.
-\ref{fig:grid_study_3d_clip_lambda-1e-1} and \ref{fig:grid_study_3d_clip_lambda-0}, we plot quantities at the cross-section generated by meshes of different sizes for $\lambda = 0.1$ and $0$.
+\ref{fig:grid_study_3d_clip_lambda-1e-1} and \ref{fig:grid_study_3d_clip_lambda-0}, we plot some quantities at the cross-section generated by meshes of different sizes for $\lambda = 0.1$ and $0$.
 Qualitatively the same solutions are produced under different meshes.
@@
 Being originally at rest, the system is excited by the applied voltage and generates oscillations that dampen over time.
-A larger value of $\lambda$ leads to stronger oscillations with larger amplitude whereas smaller $\lambda$ incurs more damping and the system rapidly reaches a steady state, which is consistent with the fact that $\lambda$ characterizes the time scale of the electromagnetic field.
+A larger value of $\lambda$ leads to oscillations with larger amplitude and slower damping whereas with a smaller $\lambda$ the system quickly reaches a steady state.
+It is consistent with the fact that $\lambda$ characterizes the time scale of the electromagnetic field.
 From a different perspective, it is a reflection of the shielding effect of plasma which is characterized by the Debye length.
@@
 As is shown in Fig.
-\ref{fig:stabilization_comparison}, the scheme without stabilization produces blow-up when $\lambda$ is close to zero while the one with stabilization remains stable.
+\ref{fig:stabilization_comparison}, the scheme without stabilization tends to blow up when $\lambda$ is close to zero while the one with stabilization remains stable.
 \begin{figure}
@@
 \ref{fig:zaxis-data_vs_z-T_10}.
-The lower figure demonstrates the matching of the density profiles of the electrons and ions.
+The lower figure demonstrates the matching of the density profiles of the electrons and ions, namely, the quasi-neutrality holds in the discrete level.
 

### 2022-11-21 paper_version/main.tex
minor
minor change
Change the numbering of elements (and dof) from i to k in order to avoid confusion with i for ions

@@
 \captionsetup[table]{labelfont={bf},name={Tab.},labelsep=period}
+\setlength\arrayrulewidth{0.7pt}
 \usepackage{authblk}
@@
 \newcommand{\todo}[1]{\textcolor{blue}{\fbox{\textbf{TODO: #1}}}}
+\newcommand{\mycomment}[1]{\textcolor{orange}{\textsf{\textbf{#1}}}}
 \newcommand{\todobox}[1]{
@@
 \section*{Abstract}
-A key coefficient characterizing plasmas is the so-called Debye length $\lambda_D$, whose size indicates to what extent electric charges can deviate from the neutral case: If $\lambda_D = \mathcal{O}(1)$ we face the non-neutral regime, while for $\lambda_D\to 0$ the plasma becomes quasi-neutral.
-Plasma models have rather different properties in these two regimes due to the singular perturbation arising from the $\lambda_D\to 0$ limit.
-Since both regimes may coexist in some plasma phenomena, it is desired to design numerical schemes that are \emph{robust} for arbitrary $\lambda_D$.
+A key coefficient characterizing plasmas is the so-called Debye length $\lambda_D$, whose magnitude indicates to what extent net electric charges deviate from zero.
+It may range over many orders of magnitude: If $\lambda_D = \mathcal{O}(1)$ we face the non-neutral regime, while for $\lambda_D\to 0$ the plasma becomes quasi-neutral.
+A singularly perturbed problem arises from the $\lambda_D\to 0$ limit, which leads to peculiar issues in numerical algorithms when both regimes coexist, for instance, in the fringes of electric arcs and near electrodes.
+It is desired to design numerical schemes that are \emph{robust} for arbitrary $\lambda_D$.
 More precisely, they should be \emph{asymptotic-preserving} (AP), in the sense that the limit $\lambda_D\to 0$ of the scheme yields a viable discretization for the continuous limit model.
@@
 \section{Introduction}
+
+\mycomment{Roman: more info from a physical point of view?}
+
 We consider a hydrodynamic multi-species plasma model, which boils down to the Maxwell-Euler system.
@@
 
-The quasi-neutral limit of the Maxwell system leads to a singularly perturbed problem in the sense that the system changes its type from hyperbolic to a mixture of hyperbolic, parabolic and elliptic, which poses a challenge for simulations in setting that encompass different regimes.
-Such situations occur in many physical models, e.g.
+The quasi-neutral limit of the Maxwell-Euler system leads to a singularly perturbed problem, that is, the PDE system changes its type \footnote{from hyperbolic to a mixed type}.
+This poses a challenge for simulations in settings encompassing different regimes.
+Singularly perturbed problems occur in many physical models, e.g.
 vanishing viscosity in the Navier-Stokes equations\cite{Kato_1984}, zero-relaxation-limit of kinetic equations\cite{jin_2010} and zero-Mach-limit of compressible flows\cite{degond_2007, haack_2010}.
@@
 The concept is sketched by the commutative diagram in \cite{jin_1999}.
-We discrete a parametric problem $P^\lambda$, which converges to its limit $P^0$ as the perturbed parameter $\lambda \rightarrow 0$ by the scheme $P^\lambda_h$ where $h$ denotes some discretization parameter, e.g.
+We discretize a parametric problem $P^\lambda$, which converges to its limit $P^0$ as the perturbed parameter $\lambda \rightarrow 0$ by the scheme $P^\lambda_h$ where $h$ denotes some discretization parameter, e.g.
 mesh size.
@@
 A reformulation of Maxwell's equations in the insulating region is then presented.
-Section 3 is devoted to the spatial discretizatio.
+Section 3 is devoted to the spatial discretization.
 The concept of primal-dual meshes is introduced based on which FIT and FVM are applied.
@@
 \subsection{The Maxwell-Euler System}
-Under moderate assumptions, plasmas, which are gases composed of charged particles (and possibly neutral particles), can be treated as fluids governed by hydrodynamic equations.
-Maxwell's equations describe their interaction with electromagnetic fields.
+Plasmas consist of electrically charged and neutral species that may be treated as gases.
+That is, they may be described by the Navier-Stokes equations augmented with source terms for species generation (ionization, recombination), forces (Lorentz force and interspecies friction), and energy (thermal relaxation among species, radiative heat transfer, Ohmic heating).
 For more details on the fluid model of plasma, see \cite{chen2016, remi_2014}.
@@
 \end{equation}
-where $\varepsilon_0]$ and $\mu_0$ are the vacuum permittivity and permeability of the medium.
-The electric current density $\mathbf{J}$ and electric charge density $\rho$ are supposed to satisfy the charge conservation equation
+where $\varepsilon_0[\frac{\text{F}}{\text{m}}]$ and $\mu_0[\frac{\text{N}}{\text{A}^{2}}]$ are vacuum permittivity and permeability of medium.
+By taking the time derivative of (\ref{equ:maxwell_gauss_D}) and the divergence of (\ref{equ:maxwell_ampere}), it is easy to see that the well-posedness requires the charge conservation equation
 \begin{equation} \label{equ:charge_continuity}
@@
 \end{align}
-The subscript $*\in \{\text{electron}, \text{ion}, \cdots\}$ represents the indices for different species.
+The subscript $*\in \{e, i, \cdots\}$ represents the indices for electron, ions and other species.
 The involved fluid quantities are: number density $n_*[\frac{1}{\text{m}^3}]$, particle mass $m_*[\text{kg}]$,  charge number $q_*[\text{C}]$, velocity $\mathbf{u}_*[\frac{\text{m}}{\text{s}}]$, pressure $p_*[\frac{\text{N}}{\text{m}^2}]$, specific total energy $e_* := \frac{1}{2}|\mathbf{u}_*|^2 + \frac{p_*}{m_*n_*(\gamma - 1)}[\frac{\text{J}}{\text{kg}}]$, specific total enthalpy $h_* := e_* + \frac{p_*}{m_*n_*}[\frac{\text{J}}{\text{kg}}]$ and current density $\mathbf{J}_* := q_*n_*\mathbf{u}_*[\frac{\text{A}}{\text{m}^2}]$.
@@
     \lambda &:= \frac{\lambda_D}{\overline{x}} \text{ the dimensionless Debye length, where }\lambda_D := \left(\frac{\varepsilon_0k_B\overline{T}}{e^2\overline{n}}\right)^{1/2}, &\\
-    \varepsilon_*^2 &:= \frac{m_*}{m_i} \text{ the species mass \emph{w.r.t.} the ion mass},\ \  * \in \{\text{ion},\text{electron},\text{neutron},\cdots\}, &\\
+    \varepsilon_*^2 &:= \frac{m_*}{m_i} \text{ the species mass \emph{w.r.t.} the ion mass},\ \  * \in \{i,e,\text{neutron},\cdots\}, &\\
     g &:= \frac{1}{\overline{n}\lambda_D^3} \text{ the plasma parameter\footnotemark[2]}.&
@@
     }
-    \fill[blue!50, opacity=0.2] (D1) -- (D2) -- (D3) -- (D4) -- (D5) -- (D6) -- cycle;
+    \fill[blue!50, opacity=0.5] (D1) -- (D2) -- (D3) -- (D4) -- (D5) -- (D6) -- cycle;
     \end{tikzpicture}}
@@
     \draw[blue, ultra thick] (D6) -- (DDD6);
-    \fill[blue!50, opacity=0.2] (D1) -- (D2) -- (D3) -- (D4) -- (D5) -- (D6);
+    \fill[blue!50, opacity=0.5] (D1) -- (D2) -- (D3) -- (D4) -- (D5) -- (D6);
     \end{tikzpicture}}
@@
          $\mathbb{G}^T = -\Tilde{\mathbb{D}}$  &  $\text{grad}^* = - \text{div}$\\
-         $\mathbb{C}^T = \Tilde{\mathbb{C}}$   &  $\text{curl}^* = - \text{curl}$\\
+         $\mathbb{C}^T = \Tilde{\mathbb{C}}$   &  $\text{curl}^* = \text{curl}$\\
          $\mathbb{D}^T = -\Tilde{\mathbb{G}}$  &  $\text{div}^* = - \text{grad}$\\
@@
 The primal mesh $\mathcal{M}$ is first generated and resolves the domain boundary.
-The dual mesh $\mathcal{M}'$ is generated afterwards.
+The dual mesh $\Tilde{\mathcal{M}}$ is generated afterwards.
 To make both meshes aligned at boundary, we have to truncate the \emph{dual} elements near the boundary due to the staggered character.
@@
 \begin{align}
-    &\sum_{j:L_j\in\partial A_i} \underbrace{\int_{L_j} \mathbf{E} \cdot d\mathbf{s}}_{:= e_j} = - \frac{\partial}{\partial t} \underbrace{\iint_{A_i} \mathbf{B} \cdot d\mathbf{A}}_{:= b_i},\ \ \ i = 1,...,N_A, \label{equ:maxwell_grid_faraday} \\
-    &\sum_{j:\Tilde{L}_j\in\partial \Tilde{A}_i} \underbrace{\int_{\Tilde{L}_j} \mathbf{H} \cdot d\mathbf{s}}_{:= h_j} = \frac{\partial}{\partial t} \underbrace{\iint_{\Tilde{A}_i} \mathbf{D} \cdot d\mathbf{A}}_{:= d_i} + \underbrace{\iint_{\Tilde{A}_i} \mathbf{J} \cdot d\mathbf{A}}_{:= j_i}, \ \ \ i = 1,...,N_{\Tilde{A}}, \label{equ:maxwell_grid_ampere}\\
-    &\sum_{j:A_j\in \partial V_i} \iint_{A_j} \mathbf{B} \cdot d\mathbf{A} = 0,\ \ \ i = 1,..., N_V,\label{equ:maxwell_grid_gauss_B}\\
-    &\sum_{j:\Tilde{A}_j \in \partial\Tilde{V}_i}\iint_{\Tilde{A}_j} \mathbf{D} \cdot d\mathbf{A} = \underbrace{\iiint_{\Tilde{V}_i} \rho dV}_{:= q_i},\ \ \ i = 1,...,N_{\Tilde{V}}.
+    &\sum_{k:L_k\in\partial A_l} \underbrace{\int_{L_k} \mathbf{E} \cdot d\mathbf{s}}_{:= e_k} = - \frac{\partial}{\partial t} \underbrace{\iint_{A_l} \mathbf{B} \cdot d\mathbf{A}}_{:= b_l},\ \ \ l = 1,...,N_A, \label{equ:maxwell_grid_faraday} \\
+    &\sum_{k:\Tilde{L}_k\in\partial \Tilde{A}_l} \underbrace{\int_{\Tilde{L}_k} \mathbf{H} \cdot d\mathbf{s}}_{:= h_k} = \frac{\partial}{\partial t} \underbrace{\iint_{\Tilde{A}_l} \mathbf{D} \cdot d\mathbf{A}}_{:= d_l} + \underbrace{\iint_{\Tilde{A}_l} \mathbf{J} \cdot d\mathbf{A}}_{:= j_l}, \ \ \ l = 1,...,N_{\Tilde{A}}, \label{equ:maxwell_grid_ampere}\\
+    &\sum_{k:A_k\in \partial V_l} \iint_{A_k} \mathbf{B} \cdot d\mathbf{A} = 0,\ \ \ l = 1,..., N_V,\label{equ:maxwell_grid_gauss_B}\\
+    &\sum_{k:\Tilde{A}_k \in \partial\Tilde{V}_l}\iint_{\Tilde{A}_k} \mathbf{D} \cdot d\mathbf{A} = \underbrace{\iiint_{\Tilde{V}_l} \rho dV}_{:= q_l},\ \ \ l = 1,...,N_{\Tilde{V}}.
 \label{equ:maxwell_grid_gauss_D}
@@
 \end{subequations}
-where $i, j$ are indices for elements in the meshes.
+where $k, l$ are numbering of elements in $(\mathcal{M}, \Tilde{\mathcal{M}})$.
 
@@
 \begin{equation} \label{equ:fit_scale_vector}
-    \mathbf{e} := (e_i)_{i=1}^{N_L},\ \ \mathbf{b} := (b_i)_{i=1}^{N_A}, \ \ \mathbf{h} := (h_i)_{i=1}^{N_{\Tilde{L}}}, \ \ \mathbf{d} := (d_i)_{i=1}^{N_{\Tilde{A}}}, \ \ \mathbf{j} := (j_i)_{i=1}^{N_{\Tilde{A}}}, \ \ \mathbf{q} := (q_i)_{i=1}^{N_{\Tilde{V}}}.
+    \mathbf{e} := (e_k)_{k=1}^{N_L},\ \ \mathbf{b} := (b_k)_{k=1}^{N_A}, \ \ \mathbf{h} := (h_k)_{k=1}^{N_{\Tilde{L}}}, \ \ \mathbf{d} := (d_k)_{k=1}^{N_{\Tilde{A}}}, \ \ \mathbf{j} := (j_k)_{k=1}^{N_{\Tilde{A}}}, \ \ \mathbf{q} := (q_k)_{i=k}^{N_{\Tilde{V}}}.
 \end{equation}
@@
 \begin{equation*}
-    (\mathbb{M}_\mu)_{i,i} = \frac{\mu|A_i|}{|\Tilde{L}_i|}, \ \ \ \ \ (\mathbb{M}_\varepsilon)_{i,i} = \frac{\varepsilon |\Tilde{A}_i|}{|L_i|},
+    (\mathbb{M}_\mu)_{k,k} = \frac{\mu|A_k|}{|\Tilde{L}_k|}, \ \ \ \ \ (\mathbb{M}_\varepsilon)_{k,k} = \frac{\varepsilon |\Tilde{A}_k|}{|L_k|},
 \end{equation*}
@@
 At this point, we would like to emphasize the importance of the primal-dual staggered meshes: the material laws can be included in a rather simple way.
-For magnetic Gauss's law $\mathbf{D} = \varepsilon \mathbf{E}$, for instance, the $\mathbf{D}$-field is represented by a collection of face integrals $ (d_i)_{i}$ while $\mathbf{E}$-field is represented by a collection of edge integrals $ (e_i)_{i}$.
+For magnetic Gauss's law $\mathbf{D} = \varepsilon \mathbf{E}$, for instance, the $\mathbf{D}$-field is represented by a collection of face integrals $ (d_k)_{k}$ while $\mathbf{E}$-field is represented by a collection of edge integrals $ (e_k)_{k}$.
 The primal-dual meshes allow us to arrange them in a staggered way -- edges penetrate faces -- such that $\mathbf{D} = \varepsilon \mathbf{E}$ can be approximated by $\mathbf{d} = \mathbb{M}_{\varepsilon}\mathbf{e}$ in a local fashion, i.e.
@@
 It holds in the discrete level as well.
-We assign each primal vertex $P_i \in \partial\Omega$ a scalar value $\varphi_i$.
+We associate each primal vertex $P_k \in \partial\Omega$ with a scalar value $\varphi_k$.
 Therefore, the boundary conditions (see Section \ref{sec:BC}) are discretized in the following way:
@@
             \begin{align}
-            e_i = (\mathbb{G}\bm{\varphi})_i,\ \ &\forall i : L_i \subset \partial\Omega, \label{equ:bc_2}\\
-            (\Tilde{\mathbb{C}} \bm{h})_i = 0\ \ &\forall i : \Tilde{A}_i \subset \Gamma_I,\label{equ:bc_3} \\
-            \varphi_i = \varphi^\pm(t), \ \ &\forall i : P_i \subset \Gamma_C^\pm. \label{equ:bc_1}
+            e_k = (\mathbb{G}\bm{\varphi})_k,\ \ &\forall k : L_k \subset \partial\Omega, \label{equ:bc_2}\\
+            (\Tilde{\mathbb{C}} \bm{h})_k = 0\ \ &\forall k : \Tilde{A}_k \subset \Gamma_I,\label{equ:bc_3} \\
+            \varphi_k = \varphi^\pm(t), \ \ &\forall k : P_k \subset \Gamma_C^\pm. \label{equ:bc_1}
             \end{align}
@@
 \end{subequations}
-
-where $\bm{\psi} = (\psi_i)_i$ denotes unknowns assigned to each primal vertex in $\Omega_N$ and the matrix $\mathbb{H}_{i,i} = \frac{|\Tilde{A}_i|}{|L_i|}$ transforms primal edge integrals to dual face fluxes\footnote{$\mathbb{H}$ functions as a discrete Hodge operator.}.
-To incorporate the zero Dirichlet BC, we limit the unknowns $(\psi_i)_{i=1}^{N^{N,\circ}_P}$ to primal vertices in $\Omega_N^\circ$.
+where $\bm{\psi} = (\psi_k)_k$ denotes unknowns assigned to each primal vertex in $\Omega_N$ and the matrix $\mathbb{H}_{k,k} = \frac{|\Tilde{A}_k|}{|L_k|}$ transforms primal edge integrals to dual face fluxes\footnote{$\mathbb{H}$ functions as a discrete Hodge operator.}.
+To incorporate the zero Dirichlet BC, we limit the unknowns $(\psi_k)_{k=1}^{N^{N,\circ}_P}$ to primal vertices in $\Omega_N^\circ$.
 
@@
 \begin{equation} \label{equ:euler_grid} 
-    \dot{\overline{\mathbf{U}}}_i + \frac{1}{|V_i|}\sum_{j:A_j\in\partial V_i} |A_j|\underbrace{\frac{1}{|A_j|}\iint_{A_j}\mathbf{f}(\mathbf{U})\cdot \mathbf{n}_j \text{d}A}_{:= \overline{\mathbf{f}}_j \approx \mathbf{f}^\text{num}_j} = \underbrace{\frac{1}{|V_i|}\iiint_{V_i} \mathbf{RHS} \text{d}V}_{:= \overline{\mathbf{RHS}}_i}
+    \dot{\overline{\mathbf{U}}}_k + \frac{1}{|V_k|}\sum_{l:A_l\in\partial V_k} |A_l|\underbrace{\frac{1}{|A_l|}\iint_{A_l}\mathbf{f}(\mathbf{U})\cdot \mathbf{n}_l \text{d}A}_{:= \overline{\mathbf{f}}_l \approx \mathbf{f}^\text{num}_l} = \underbrace{\frac{1}{|V_k|}\iiint_{V_k} \mathbf{RHS} \text{d}V}_{:= \overline{\mathbf{RHS}}_k}
 \end{equation}
-where $\overline{\mathbf{U}}_i := \iiint_{V_i} \mathbf{U} \text{d}V / |V_i| \in L^2([0,T],\mathbb{R}^m)$ is the cell average of $\mathbf{U}$ and $\mathbf{n}_j$ is the outer normal vector of face $A_j$ with respect to the cell $V_i$.
-We approximate the flux $\overline{\mathbf{f}}_j$ in (\ref{equ:euler_grid}) by a numerical flux $\mathbf{f}^\text{num}_j := \mathbf{f}^\text{num}\left(\overline{\mathbf{U}}_i, \overline{\mathbf{U}}_{k(i,j)}, \mathbf{n}_j\right)$, where $k(i,j)$ returns the index of the adjacent cell that shares $A_j$ with cell $V_i$.
+where $\overline{\mathbf{U}}_k := \iiint_{V_k} \mathbf{U} \text{d}V / |V_k| \in L^2([0,T],\mathbb{R}^m)$ is the cell average of $\mathbf{U}$ and $\mathbf{n}_l$ is the outer normal vector of face $A_l$ with respect to the cell $V_k$.
+We approximate the flux $\overline{\mathbf{f}}_l$ in (\ref{equ:euler_grid}) by a numerical flux $\mathbf{f}^\text{num}_l := \mathbf{f}^\text{num}\left(\overline{\mathbf{U}}_k, \overline{\mathbf{U}}_{\hat{k}(k,l)}, \mathbf{n}_l\right)$, where $\hat{k}(k,l)$ returns the index of the adjacent cell that shares $A_l$ with cell $V_k$.
 Classical numerical fluxes include Lax-Friedrich flux, Rusanov flux, and Engquist-Osher flux, see \cite[][p.
@@
 \begin{equation}
-    \dot{\overline{\mathbf{U}}}_i + \frac{1}{|V_i|}\sum_{j:A_j\in\partial V_i} |A_j| \mathbf{f}^\text{num}\left(\overline{\mathbf{U}}_i, \overline{\mathbf{U}}_{k(i,j)}, \mathbf{n}_j\right) = \overline{\mathbf{RHS}}_i.
+    \dot{\overline{\mathbf{U}}}_k + \frac{1}{|V_k|}\sum_{l:A_l\in\partial V_k} |A_l| \mathbf{f}^\text{num}\left(\overline{\mathbf{U}}_k, \overline{\mathbf{U}}_{\hat{k}(k,l)}, \mathbf{n}_l\right) = \overline{\mathbf{RHS}}_k.
     \label{equ:fvm}
 \end{equation}
-The Rusanov flux in multi-dimensions on face $A_j$ writes
+The Rusanov flux in multi-dimensions on face $A_l$ writes
 \begin{equation} \label{equ:rusanov-flux-3d}
@@
 
-We would like to emphasize that the Euler system is discretized on $\mathcal{M}'$ due to the fact that 1) the electric current is connected to the momenta of charged particles by (\ref{equ:maxwell_euler_coupling}); 2) the electric current is discretized on dual faces by (\ref{equ:maxwell_grid_ampere}).
-
-To rewrite (\ref{equ:fvm}) into a matrix form, by abuse of notation we stack all the cell average $(\overline{\mathbf{U}}_i)_i$ into a matrix $\mathbf{U} \in \mathbb{R}^{N_{\Tilde{V}}^P \times m}$ with $\mathbf{U}_{i,:} = \overline{\mathbf{U}}_i$.
+We would like to emphasize that the Euler system is discretized on $\Tilde{\mathcal{M}}$ due to the fact that 1) the electric current is connected to the momenta of charged particles by (\ref{equ:maxwell_euler_coupling}); 2) the electric current is discretized on dual faces by (\ref{equ:maxwell_grid_ampere}).
+
+To rewrite (\ref{equ:fvm}) into a matrix form, by abuse of notation we stack all the cell average $(\overline{\mathbf{U}}_k)_k$ into a matrix $\mathbf{U} \in \mathbb{R}^{N_{\Tilde{V}}^P \times m}$ with $\mathbf{U}_{k,:} = \overline{\mathbf{U}}_k$.
 Meanwhile, we denote by $\mathbf{F} \in \mathbb{R}^{N_{\Tilde{A}}^P \times m}$ the collection of the (total) numerical fluxes, i.e.
-$\mathbf{F}_{i,:} = \mathbf{f}^\text{num}_i$.
-In the same way, we denote by $\mathbf{RHS}\in \mathbb{R}^{N_{\Tilde{V}}^P \times m}$ the collection of $\overline{\mathbf{RHS}}_i$.
-Besides, we define the diagonal matrix $\mathbb{\Tilde{V}} \in \mathbb{R}^{N_{\Tilde{V}}^P \times N_{\Tilde{V}}^P}$ and $\mathbb{\Tilde{A}}\in \mathbb{R}^{N_{\Tilde{A}}^P \times N_{\Tilde{A}}^P}$ with $\mathbb{\Tilde{A}}_{i,i} = |\Tilde{A}_i|$.
+$\mathbf{F}_{k,:} = \mathbf{f}^\text{num}_k$.
+In the same way, we denote by $\mathbf{RHS}\in \mathbb{R}^{N_{\Tilde{V}}^P \times m}$ the collection of $\overline{\mathbf{RHS}}_k$.
+Besides, we define the diagonal matrix $\mathbb{\Tilde{V}} \in \mathbb{R}^{N_{\Tilde{V}}^P \times N_{\Tilde{V}}^P}$ and $\mathbb{\Tilde{A}}\in \mathbb{R}^{N_{\Tilde{A}}^P \times N_{\Tilde{A}}^P}$ with $\mathbb{\Tilde{A}}_{k,k} = |\Tilde{A}_k|$.
 Making use of the incidence matrices, we end up with
@@
 We adopt the principle of least square fitting and reconstruct a \emph{constant} vector field inside each cell.
-For a cell $\Tilde{V}$ with $k$ faces with areas $\{A_i\}_{i=1}^k$, normal vectors $\{\mathbf{n}_i\}_{i=1}^k$ and fluxes $\{f_i\}_{i=1}^k$, a constant vector field $\mathbf{v}$ satisfying
+For a cell $\Tilde{V}$ with $N_A$ faces with areas $\{A_k\}_{k=1}^{N_A}$, normal vectors $\{\mathbf{n}_k\}_{k=1}^{N_A}$ and fluxes $\{f_k\}_{k=1}^{N_A}$, a constant vector field $\mathbf{v}$ satisfying
 \begin{equation*}
-    \mathbf{v} = \argmin_{v\in \mathbb{R}^3} \sum_{i=1}^k(A_i\mathbf{v} \cdot \mathbf{n}_i - f_i)^2.   
+    \mathbf{v} = \argmin_{v\in \mathbb{R}^3} \sum_{k=1}^{N_A}(A_k\mathbf{v} \cdot \mathbf{n}_k - f_k)^2.   
 \end{equation*} can be computed through
@@
 \begin{equation*}
-    \mathbb{K} = [A_1\mathbf{n}_1, A_2\mathbf{n}_2, \cdots, A_k\mathbf{n}_k]^T,\ \ \ \mathbf{f} = [f_1, f_2, \cdots, f_k]^T,
+    \mathbb{K} = [A_1\mathbf{n}_1, A_2\mathbf{n}_2, \cdots, A_{N_A}\mathbf{n}_{N_A}]^T,\ \ \ \mathbf{f} = [f_1, f_2, \cdots, f_{N_A}]^T,
 \end{equation*}
@@
 where $\mathbf{d}, \mathbf{b}$ are stacked unknowns, see Tab.
-\ref{tab:def_size_var}; $\mathbf{E} := (\mathbf{E}_i)_{i=1}^{N_{\Tilde{V}}}$ and $\mathbf{B} := (\mathbf{B}_i)_{i=1}^{N_{\Tilde{V}}}$ are $N_{\Tilde{V}} \times 3$ matrices stacking the reconstructed $\mathbf{E}$-fields and $\mathbf{B}$-fields at each $\Tilde{V}$; $\Tilde{\mathbb{R}}_E$ and $\Tilde{\mathbb{R}}_B$ are thus rank-3 tensors.
+\ref{tab:def_size_var}; $\mathbf{E} := (\mathbf{E}_k)_{k=1}^{N_{\Tilde{V}}}$ and $\mathbf{B} := (\mathbf{B}_k)_{k=1}^{N_{\Tilde{V}}}$ are $N_{\Tilde{V}} \times 3$ matrices stacking the reconstructed $\mathbf{E}$-fields and $\mathbf{B}$-fields at each $\Tilde{V}$; $\Tilde{\mathbb{R}}_E$ and $\Tilde{\mathbb{R}}_B$ are thus rank-3 tensors.
 
@@
 \begin{equation*}
-    \mathbf{F}_i = {\mathbf{f}^\text{num}}(\mathbf{U}_j, \mathbf{U}_j, \mathbf{n}_i), \ \ \forall i: \Tilde{A}_i \subset \Gamma_C,
+    \mathbf{F}_k = {\mathbf{f}^\text{num}}(\mathbf{U}_l, \mathbf{U}_l, \mathbf{n}_k), \ \ \forall k: \Tilde{A}_k \subset \Gamma_C,
 \end{equation*}
-where $j$ refers to the index of the cell adjacent to the boundary face $\Tilde{A}_i$ and is unique.
+where $l$ refers to the index of the cell adjacent to the boundary face $\Tilde{A}_k$ and is unique.
 For the reflective wall $\Gamma_W$, the momentum of a ghost cell is reversed with respect to its adjacent one while keeping the other quantities unchanged.
@@
 \begin{equation*}
-    \mathbf{F}_i = \mathbf{f}^\text{num}(\mathbf{U}_j, \hat{\mathbf{U}}_j, \mathbf{n}_i), \ \ \forall i: \Tilde{A}_i \subset \Gamma_W,
+    \mathbf{F}_k = \mathbf{f}^\text{num}(\mathbf{U}_l, \hat{\mathbf{U}}_l, \mathbf{n}_k), \ \ \forall k: \Tilde{A}_k \subset \Gamma_W,
 \end{equation*}
@@
     \begin{align}
-        [\dot{\mathbf{b}} + \mathbb{C}\mathbf{e} = \mathbf{0}]_i, \ \ &\forall i: A_i \subset \Omega, \\
-        [\dot{\mathbf{d}} - \Tilde{\mathbb{C}}\mathbf{h} = - \Sigma_{\ast} q_*\bm{f}_{\ast}^{n}]_i, \ \ &\forall i: \Tilde{A}_i \subset \Omega_P,\\
-        [\dot{\mathbf{d}} - \Tilde{\mathbb{C}}\mathbf{h} + \mathbb{H} \mathbb{G} \bm{\psi} = \mathbf{0}]_i, \ \ &\forall i: \Tilde{A}_i \subset \Omega_N,\\
-        [\Tilde{\mathbb{D}}\mathbf{d} = \mathbf{0}]_i,\ \ &\forall i: \Tilde{V}_i \subset \Omega_N, \\
-        [\dot{\mathbf{U}}_\ast + \mathbb{\Tilde{V}}^{-1}\mathbb{\Tilde{D}}\mathbb{\Tilde{A}}\mathbf{F}_\ast = \mathbf{RHS}_\ast]_i,\ \ &\forall i: \Tilde{V}_i \subset \Omega_P, \\
-        [\mathbf{d} = \mathbb{M}_\varepsilon\mathbf{e}]_i,\ \ &\forall i:L_i \subset \Omega,\\
-        [\mathbf{h} = \mathbb{M}_\mu^{-1}\mathbf{b}]_i, \ \ &\forall i:A_i \subset \Omega,
+        [\dot{\mathbf{b}} + \mathbb{C}\mathbf{e} = \mathbf{0}]_k, \ \ &\forall k: A_k \subset \Omega, \\
+        [\dot{\mathbf{d}} - \Tilde{\mathbb{C}}\mathbf{h} = - \Sigma_{\ast} q_*\bm{f}_{\ast}^{n}]_k, \ \ &\forall k: \Tilde{A}_k \subset \Omega_P,\\
+        [\dot{\mathbf{d}} - \Tilde{\mathbb{C}}\mathbf{h} + \mathbb{H} \mathbb{G} \bm{\psi} = \mathbf{0}]_k, \ \ &\forall k: \Tilde{A}_k \subset \Omega_N,\\
+        [\Tilde{\mathbb{D}}\mathbf{d} = \mathbf{0}]_k,\ \ &\forall k: \Tilde{V}_k \subset \Omega_N, \\
+        [\dot{\mathbf{U}}_\ast + \mathbb{\Tilde{V}}^{-1}\mathbb{\Tilde{D}}\mathbb{\Tilde{A}}\mathbf{F}_\ast = \mathbf{RHS}_\ast]_k,\ \ &\forall k: \Tilde{V}_i \subset \Omega_P, \\
+        [\mathbf{d} = \mathbb{M}_\varepsilon\mathbf{e}]_k,\ \ &\forall k:L_k \subset \Omega,\\
+        [\mathbf{h} = \mathbb{M}_\mu^{-1}\mathbf{b}]_k, \ \ &\forall k:A_k \subset \Omega,
     \end{align}
@@
         \begin{align}
-            \hspace{1.6cm}\mathbf{j}_i =
+            \hspace{1.6cm}\mathbf{j}_k =
             \begin{cases}
-             \Sigma_{\ast} q_*\bm{f}_{\ast,i}^{n},&\forall i: \Tilde{A}_i \subset \Omega_P, \\
-            0,&\forall i: \Tilde{A}_i \subset \Omega_N,
+             \Sigma_{\ast} q_*\bm{f}_{\ast,k}^{n},&\forall k: \Tilde{A}_k \subset \Omega_P, \\
+            0,&\forall k: \Tilde{A}_k \subset \Omega_N,
             \end{cases}
@@
     \end{comment}
-where $\ast \in \{\text{electron}, \text{ion}, \dots\}$ and $\bm{f}^n$ denotes the mass flux.
-By $[\dots]_i$ we mean taking the $i$-th component of both sides of the equation.
-We have the following BCs:
+where $\ast \in \{e, i, \dots\}$ and $\bm{f}^n$ denotes the mass flux. By $[\cdots]_k$ we mean taking the $k$-th component of both sides of the equation. We have the following BCs:
     \begin{align}
-    \varphi_i = \varphi(P_i, t), \ \ &\forall i : P_i \subset \Gamma_C, \\
-    e_i = (\mathbb{G}\bm{\varphi})_i,\ \ &\forall i : L_i \subset \partial\Omega, \\
-    (\Tilde{\mathbb{C}} \bm{h})_i = 0,\ \ &\forall i : \Tilde{A}_i \subset \Gamma_I, \label{equ:bc_zero_curl_h} \\
-    \mathbf{F}_{\ast,i} = \mathbf{f}^\text{num}(\mathbf{U}_{\ast,j}, \mathbf{U}_{\ast,j}, \mathbf{n}_i), \ \ &\forall i: \Tilde{A}_i \subset \Gamma_C, \\
-    \mathbf{F}_{\ast,i} = \mathbf{f}^\text{num}(\mathbf{U}_{\ast,j}, \hat{\mathbf{U}}_{\ast,j}, \mathbf{n}_i), \ \ &\forall i: \Tilde{A}_i \subset \Gamma_W.
+    \varphi_k = \varphi(P_k, t), \ \ &\forall k : P_k \subset \Gamma_C, \\
+    e_k = (\mathbb{G}\bm{\varphi})_k,\ \ &\forall k : L_k \subset \partial\Omega, \\
+    (\Tilde{\mathbb{C}} \bm{h})_k = 0,\ \ &\forall k : \Tilde{A}_k \subset \Gamma_I, \label{equ:bc_zero_curl_h} \\
+    \mathbf{F}_{\ast,k} = \mathbf{f}^\text{num}(\mathbf{U}_{\ast,l}, \mathbf{U}_{\ast,l}, \mathbf{n}_k), \ \ &\forall k: \Tilde{A}_k \subset \Gamma_C, \\
+    \mathbf{F}_{\ast,k} = \mathbf{f}^\text{num}(\mathbf{U}_{\ast,l}, \hat{\mathbf{U}}_{\ast,l}, \mathbf{n}_k), \ \ &\forall k: \Tilde{A}_k \subset \Gamma_W.
     \end{align}
 \end{subequations}
-We would like to stress again that in our FIT-FVM framework Faraday's law is discretized on $\mathcal{M}$ while Amp\`{e}re's law is discretized on $\mathcal{M}'$ for a simple approximation of material laws.
-By arranging the Euler system on $\mathcal{M}'$, the connection between electric currents and fluid momenta is naturally established in the discrete level since they are defined on the same locations.
+We would like to stress again that in our FIT-FVM framework Faraday's law is discretized on $\mathcal{M}$ while Amp\`{e}re's law is discretized on $\Tilde{\mathcal{M}}$ for a simple approximation of material laws.
+By arranging the Euler system on $\Tilde{\mathcal{M}}$, the connection between electric currents and fluid momenta is naturally established in the discrete level since they are defined on the same locations.
 
@@
 \subsubsection{Projection to One Dimension} \label{sec:projection_to_1d}
-Consider a mesh pair $(\mathcal{M}, \mathcal{M}')$ that are constructed by 2D extrusion along $z$-axis and are unbounded along transverse directions.
+Consider a mesh pair $(\mathcal{M}, \Tilde{\mathcal{M}})$ that are constructed by 2D extrusion along $z$-axis and are unbounded along transverse directions.
 On assuming the transverse invariance and rotational symmetry, we can ``project'' all the D.o.F.
@@
 \begin{align}
-    \left[\delta_m^{-1} (\mathbf{b}^{m+1} - \mathbf{b}^{m}) + \mathbb{C}\mycolorbox{orange!30}{\mathbf{e}^{m+1}} = \mathbf{0} \right]_i,\ \ &\forall i:A_i \subset \Omega, \label{equ:maxwell_faraday_ap}\\
-    \left[\lambda^2\delta_m^{-1}(\mathbf{d}^{m+1} - \mathbf{d}^m)- \Tilde{\mathbb{C}}\mycolorbox{orange!30}{\mathbf{h}^{m+1}} = - \Sigma_\ast q_\ast \mycolorbox{orange!30}{\bm{f}^{n,m+1}_{\ast}}\right]_i,\ \ &\forall i:\Tilde{A}_i\subset\Omega_P, \label{equ:maxwell_ampere_plasma_ap}\\
-    \left[\lambda^2\delta_m^{-1}(\mathbf{d}^{m+1} - \mathbf{d}^m)- \Tilde{\mathbb{C}}\mycolorbox{orange!30}{\mathbf{h}^{m+1}} + \mathbb{H}\mathbb{G}\mycolorbox{orange!30}{\bm{\psi}^{m+1}} = \mathbf{0} \right]_i,\ \ &\forall i:\Tilde{A}_i\subset\Omega_N, \label{equ:maxwell_ampere_nonconducting_ap}\\
-    \left[\mathbb{D}\mycolorbox{orange!30}{\mathbf{d}^{m+1}} = \mathbf{0}\right]_i, \ \ &\forall i : \Tilde{V}_i \subset \Omega_N, \label{equ:gauss_nonconducting_ap} \\
-    \left[\delta_m^{-1}(\mathbf{U}_{*}^{m+1} - \mathbf{U}_{*}^{m}) + \mathbb{\Tilde{V}}^{-1}\mathbb{\Tilde{D}}\mathbb{\Tilde{A}}\mycolorbox{orange!30}{\mathbf{F}_\ast^{m+1/2}} = \mycolorbox{orange!30}{\mathbf{RHS}_\ast^{m+1/2}} \right]_i,\ \ &\forall i : \Tilde{V}_i \subset \Omega_P, \label{equ:euler_ap}
+    \left[\delta_m^{-1} (\mathbf{b}^{m+1} - \mathbf{b}^{m}) + \mathbb{C}\mycolorbox{orange!30}{\mathbf{e}^{m+1}} = \mathbf{0} \right]_k,\ \ &\forall k:A_k \subset \Omega, \label{equ:maxwell_faraday_ap}\\
+    \left[\lambda^2\delta_m^{-1}(\mathbf{d}^{m+1} - \mathbf{d}^m)- \Tilde{\mathbb{C}}\mycolorbox{orange!30}{\mathbf{h}^{m+1}} = - \Sigma_\ast q_\ast \mycolorbox{orange!30}{\bm{f}^{n,m+1}_{\ast}}\right]_k,\ \ &\forall k:\Tilde{A}_k\subset\Omega_P, \label{equ:maxwell_ampere_plasma_ap}\\
+    \left[\lambda^2\delta_m^{-1}(\mathbf{d}^{m+1} - \mathbf{d}^m)- \Tilde{\mathbb{C}}\mycolorbox{orange!30}{\mathbf{h}^{m+1}} + \mathbb{H}\mathbb{G}\mycolorbox{orange!30}{\bm{\psi}^{m+1}} = \mathbf{0} \right]_k,\ \ &\forall k:\Tilde{A}_k\subset\Omega_N, \label{equ:maxwell_ampere_nonconducting_ap}\\
+    \left[\mathbb{D}\mycolorbox{orange!30}{\mathbf{d}^{m+1}} = \mathbf{0}\right]_k, \ \ &\forall k : \Tilde{V}_k \subset \Omega_N, \label{equ:gauss_nonconducting_ap} \\
+    \left[\delta_m^{-1}(\mathbf{U}_{*}^{m+1} - \mathbf{U}_{*}^{m}) + \mathbb{\Tilde{V}}^{-1}\mathbb{\Tilde{D}}\mathbb{\Tilde{A}}\mycolorbox{orange!30}{\mathbf{F}_\ast^{m+1/2}} = \mycolorbox{orange!30}{\mathbf{RHS}_\ast^{m+1/2}} \right]_k,\ \ &\forall k : \Tilde{V}_k \subset \Omega_P, \label{equ:euler_ap}
 \end{align}
@@
 \begin{align}
-    \mathbf{U}_{*,i}^{m} &=
+    \mathbf{U}_{*,k}^{m} &=
     \begin{pmatrix}
@@
     n e
-    \end{pmatrix}^m_{\ast,i}, \\
-    \mathbf{F}_{*,i}^{m+1/2} &=
+    \end{pmatrix}^m_{\ast,k}, \\
+    \mathbf{F}_{*,k}^{m+1/2} &=
     \begin{pmatrix}
@@
     f^{e,m}
-    \end{pmatrix}_{\ast,i}
+    \end{pmatrix}_{\ast,k}
     = 
@@
     \frac{1}{2}\left[(nhu_\bot)^m_{L} + (nhu_\bot)^m_{R}\right] - \frac{1}{2}s^m\left[(ne)^m_{R} - (ne)^m_{L}\right]
-    \end{pmatrix}_{\ast,i}, \label{equ:flux_ap}\\
-    \mathbf{RHS}_{*,i}^{m+1/2} &=
+    \end{pmatrix}_{\ast,k}, \label{equ:flux_ap}\\
+    \mathbf{RHS}_{*,k}^{m+1/2} &=
     \begin{pmatrix}
@@
     \varepsilon_*^{-2}q_*(n\mathbf{u})^m_* \cdot \mycolorbox{orange!30}{\mathbf{E}^{m+1}}
-    \end{pmatrix}_i +
+    \end{pmatrix}_k +
     \begin{pmatrix}
@@
     \varepsilon_*^{-2}\mycolorbox{orange!30}{Q_*^{\text{coll}, m+1}} 
-    \end{pmatrix}_i, \label{equ:rhs_ap}\\
+    \end{pmatrix}_k, \label{equ:rhs_ap}\\
     \mathbf{E}^{m+1} &= \Tilde{\mathbb{R}}_E\mathbf{d}^{m+1},
@@
     \mathbf{B}^{m} = \Tilde{\mathbb{R}}_B\mathbf{b}^{m}, \\
-    \mathbf{R}_{*,i}^{\text{coll},m+1} &= 
+    \mathbf{R}_{*,k}^{\text{coll},m+1} &= 
     \begin{cases}
-    \alpha^\text{coll}\left[n_{\text{electron}}^m\mycolorbox{orange!30}{(n\mathbf{u})^{m+1}_{\text{ion}}} - n_{\text{ion}}^m\mycolorbox{orange!30}{(n\mathbf{u})^{m+1}_{\text{electron}}}\right]_i, \text{   if   } * = \text{electron} \\
-    \alpha^\text{coll}\left[n_{\text{ion}}^m\mycolorbox{orange!30}{(n\mathbf{u})^{m+1}_{\text{electron}}} - n_{\text{electron}}^m\mycolorbox{orange!30}{(n\mathbf{u})^{m+1}_{\text{ion}}}\right]_i, \text{   if   } * = \text{ion}
+    \alpha^\text{coll}\left[n_{e}^m\mycolorbox{orange!30}{(n\mathbf{u})^{m+1}_{i}} - n_{i}^m\mycolorbox{orange!30}{(n\mathbf{u})^{m+1}_{e}}\right]_k, \text{   if   } * = e \\
+    \alpha^\text{coll}\left[n_{i}^m\mycolorbox{orange!30}{(n\mathbf{u})^{m+1}_{e}} - n_{e}^m\mycolorbox{orange!30}{(n\mathbf{u})^{m+1}_{i}}\right]_k, \text{   if   } * = i
     \end{cases}  \label{equ:R_coll_ap}\\
-    Q_{*,i}^{\text{coll},m+1} &= \mycolorbox{orange!30}{\mathbf{R}_{*,i}^{\text{coll},m+1} \cdot \mathbf{u}_{\ast,i}^{m+1}} \label{equ:Q_coll_ap}
+    Q_{*,k}^{\text{coll},m+1} &= \mycolorbox{orange!30}{\mathbf{R}_{*,k}^{\text{coll},m+1} \cdot \mathbf{u}_{\ast,k}^{m+1}} \label{equ:Q_coll_ap}
 .\end{align}
@@
 The quantities with superscript $m+1/2$ indicate their dependency on the quantities at both $m$-th and $(m+1)$-th iterations.
-In Rusanov flux (\ref{equ:flux_ap}), we denote by $u_\perp$ the normal component velocity with respect to the dual face $\Tilde{A}_j$.
+In Rusanov flux (\ref{equ:flux_ap}), we denote by $u_\perp$ the normal component velocity with respect to the dual face $\Tilde{A}_k$.
 We restrain the illustration of the collision term (\ref{equ:R_coll_ap}) (\ref{equ:Q_coll_ap}) to the two-species case for the sake of simplicity.
@@
 \begin{equation*}
-    [\Tilde{\mathbb{C}}\mathbf{h}^{m+1} = 0]_i, \ \ \forall i : \Tilde{A}_i \subset \Omega_N,
+    [\Tilde{\mathbb{C}}\mathbf{h}^{m+1} = 0]_k, \ \ \forall k : \Tilde{A}_k \subset \Omega_N,
 \end{equation*}
@@
 \begin{equation*}
-    [\mathbf{d}^{m+1} = 0]_i, \ \ \forall i : \Tilde{A}_i \subset \Omega_N.
+    [\mathbf{d}^{m+1} = 0]_k, \ \ \forall k : \Tilde{A}_k \subset \Omega_N.
 \end{equation*}
@@
 We conduct numerical experiments based on the geometric setting and boundary conditions as presented in Section \ref{sec:BC}.
-The primal-dual mesh pair $(\mathcal{M}, \mathcal{M}')$ is generated based on the code developed in \cite[][ch.
+The primal-dual mesh pair $(\mathcal{M}, \Tilde{\mathcal{M}})$ is generated based on the code developed in \cite[][ch.
 1]{fuchs_2021}.
@@
 \begin{equation*}
-    n_\ast(\mathbf{x}, 0) = 1, \ \ \  p_\ast(\mathbf{x},0) = 1, \ \ \forall \mathbf{x}\in\Omega, \ast \in \{\text{electron}, \text{ion}\}.
+    n_\ast(\mathbf{x}, 0) = 1, \ \ \  p_\ast(\mathbf{x},0) = 1, \ \ \forall \mathbf{x}\in\Omega, \ast \in \{e, i\}.
 \end{equation*}

### 2022-11-21 paper_version/main.tex
incorporate Roman's comment

@@
 \newcommand{\todo}[1]{\textcolor{blue}{\fbox{\textbf{TODO: #1}}}}
-\newcommand{\mycomment}[1]{\textcolor{orange}{\textsf{\textbf{#1}}}}
+\newcommand{\mycomment}[1]{\noindent\textcolor{orange}{\underline{\textsf{\textbf{#1}}}}}
 \newcommand{\todobox}[1]{
@@
 For the sake of simplicity, we only consider ion-electron collision in this work, but extension to more species is straightforward.
-Under moderate assumptions, such collisions can be well modelled by friction terms (\citep[][sec.
+Such collisions can be well modelled by friction terms (\citep[][sec.
 5.6.2]{chen2016})
@@
 \end{equation}
-which models the collision force that is acting on the electrons.
-ln$\Lambda$ is called the \emph{Coulomb logarithm}, which typically takes a value $10\sim20$ \cite{chen2016}.
+which is the collision force acting on electrons.
+ln$\Lambda$ is called the \emph{Coulomb logarithm} and is usually taken as a constant \cite{chen2016}.
 Because of the conservation of momentum, the collision term for ions $\mathbf{R}_{i}^{\text{coll}}$ is nothing but the negative of $\mathbf{R}_{e}^{\text{coll}}$.
@@
 Combination of the two sets of equations (\ref{equ:maxwell_faraday}) to (\ref{equ:maxwell_gauss_D}) and (\ref{equ:euler_}) leads to the governing equations for a multi-species plasma model.
-The coupling of the two subsystems is due to the following relations that connect the fluid and electromagnetic quantities
+The coupling of the two subsystems is due to the fact that electric current is the flow of charged particles:
 \begin{equation} \label{equ:maxwell_euler_coupling}
@@
 \subsection{Rescaling} \label{sec:rescaling}
-In rescaling, variables in equations are replaced the ratio of original quantities and constant reference quantities, which transforms the system into dimensionless form.
+In rescaling, variables in equations are replaced by the ratio of original quantities and constant reference quantities, which transforms the system into dimensionless form.
 In this part, the rescaling procedure mostly follows that of \cite{degond_2017}.
@@
 By abuse of notation, the dimensionless quantities have the same symbol as the original quantities.
-For the sake of simplicity, we only consider the collision terms, i.e.
+For the sake of simplicity, we neglect ionization and recombination but focus on collision terms, i.e.
 $\Gamma_* = 0, \mathbf{R}_* = \mathbf{R}_*^\text{coll}, Q_* = Q_*^\text{coll}$ in (\ref{equ:euler_}), while neglecting other effects.
@@
 The $\lambda \rightarrow 0$ limit implies that the collisions happen in the atomic length scale, in which quantum-mechanical effects must be taken into effect \citep{frank_1972}.
-Therefore, for the sake of simplicity, we eliminate the perturbation parameter in the friction term by assuming $g \sim \lambda$ and keep the prefactor of collision term constant $\alpha^{\text{coll}}$ throughout the simulation.
+Therefore, we eliminate the perturbation parameter in the friction term by assuming $g \sim \lambda$ and keep the prefactor of collision term constant $\alpha^{\text{coll}}$ throughout the simulation.
 
@@
 \end{equation}
-and consequently, the rescaled friction heat for ions and electrons takes the expression
+and consequently, the rescaled friction heat for ions and electrons take the expression
 \begin{align*} 
@@
 \subsection{Quasi-neutral Limit} \label{sec:quasi-neutral_limit}
-The Debye length $\lambda_D$ (see its definition in the preceding section) is the characteristic length over which local concentrations of charge are shielded.
-For the underlying physics, see \cite[Sec.
-1.4]{chen2016}.
+The Debye length $\lambda_D$ (see its definition in the preceding section) is the characteristic length over which local concentrations of charge are shielded, see \cite[Sec.
+1.4]{chen2016} for the underlying physics.
 In many situations, it has a rather low value compared to the reference length scale: the typical $\lambda_D$ for gas discharge and Tokamak is $10^{-4}$ m; for interstellar medium, the magnitude is about $1$ m \cite[ch.
@@
 To be more specific, in the non-limit model the $\mathbf{E}$-field evolves with time whereas in the quasi-neutral model it responds instantaneously to other quantities according to the constraint (\ref{equ:maxwell_ampere_limit}).
-To make it clear, we replace (\ref{equ:maxwell_ampere_rescaled}) by the sum of the curl of (\ref{equ:maxwell_faraday_rescaled}) and the time-derivative of (\ref{equ:maxwell_ampere_rescaled}).
+We replace (\ref{equ:maxwell_ampere_rescaled}) by the sum of the curl of (\ref{equ:maxwell_faraday_rescaled}) and the time-derivative of (\ref{equ:maxwell_ampere_rescaled}).
 Meanwhile exploiting the momentum equation in (\ref{equ:euler_rescaled}) to express $\partial_t\mathbf{J}$, we end up getting the equation that the $\mathbf{E}$-field satisfies
@@
 \end{equation*}
- (\ref{equ:E}) implies the shift from hyperbolic to elliptic for the evolution equations for the $\mathbf{E}$-field as $\lambda\rightarrow0$.
+ (\ref{equ:E}) makes it obvious the shift from hyperbolic to elliptic for the evolution equations for the $\mathbf{E}$-field as $\lambda\rightarrow0$.
 
@@
 
-We consider a simply connected domain $\Omega$ that is decomposed into two sub-domains $\Omega_P$ and $\Omega_N$ representing plasma domain and non-conducting domain respectively.
-We use the notation $\Gamma_C := \partial\Omega \cap \partial\Omega_P$, denoting the contact boundary, and $\Gamma_I := \partial\Omega \cap \partial\Omega_N$ for the insulating boundary which an artificial cut-off boundary.
+We consider a simply-connected domain $\Omega$ comprising two sub-domains $\Omega_P$ and $\Omega_N$ representing plasma domain and non-conducting domain respectively.
+We use the notation $\Gamma_C := \partial\Omega \cap \partial\Omega_P$, denoting the contact boundary, and $\Gamma_I := \partial\Omega \cap \partial\Omega_N$ for the insulating boundary with an artificial cut-off boundary.
 The interface between the two domains is denoted by $\Gamma_W = \partial\Omega_I \cap \partial\Omega_P$.
@@
 
+\mycomment{Roman: expand on a relevant physical setting, e.g. wall-stabilized arc in hight voltage circuit breakers.}
+
 The plasma fills $\Omega_P$ where the Euler system is defined and the boundary of the plasma domain is $\partial\Omega_P$.
@@
 The Maxwell system is defined on the whole domain $\Omega$.
-The insulating boundary blocks energy interchange and therefore only admits zero electric and magnetic flux, in the sense that $\text{curl}\mathbf{E}\cdot \mathbf{n} = 0$ and $\text{curl}\mathbf{H}\cdot \mathbf{n} = 0$ where $\mathbf{n}$ is the outer normal vector.
+The insulating boundary blocks energy interchange and therefore only admits zero electric and magnetic flux, in the sense that $\text{curl}\mathbf{E}\cdot \mathbf{n} = 0$ and $\text{curl}\mathbf{H}\cdot \mathbf{n} = 0$ where $\mathbf{n}$ is the normal vector.
 We model the electrodes on the contact boundary $\Gamma_C = \Gamma_C^+\cup \Gamma_C^-$ which are two disjoint connecting components.
@@
 Since we have $\text{curl}\mathbf{E} \cdot \mathbf{n} = 0$ on the whole boundary $\partial\Omega$, there exists a scalar potential $\varphi$ defined on $\partial\Omega$ such that the tangential component $\mathbf{E}_t = \nabla_\Gamma \varphi$ where $\nabla_\Gamma$ denotes surface gradient.
-$\varphi$ is set constant in each component of $\Gamma_C$, i.e.
-external voltages are applied on the electrodes.
+$\varphi$ is set constant in each component of $\Gamma_C$, that is, from a physical point of view, $\varphi$ is the external potential difference applied to the electrodes.
 \begin{figure}
@@
 This is done by taking the divergence of (\ref{equ:ampere_ins_reform}) such that the Laplace equation of $\psi$ with zero Dirichlet boundary condition gives vanishing $\psi$.
-The importance of this reformulation will be made clear in the numerical experiment.
-
-We would like to point out that this reformulation is not needed in the plasma domain $\Omega_P$ since the Maxwell system is uniformly well-posed for $\lambda \in [0,1]$ thanks to the existence of an electric current and its dependence on the $\mathbf{E}$-field.
+The importance of this reformulation will be made clear in the numerical experiment, see Section \ref{sec:numerical_experiment}.
+
+We point out that this reformulation is not needed in the plasma domain $\Omega_P$ since the Maxwell system is uniformly well-posed for $\lambda \in [0,1]$ thanks to the existence of an electric current and its dependence on the $\mathbf{E}$-field.
 
@@
 \begin{figure}
+    \begin{subfigure}[b]{0.35\textwidth}
+    \centering
+    \begin{tikzpicture}[scale = 0.2]
+            \def\style{thick}
+            \draw[\style] (0,0) -- (1.5,0);
+            \draw[\style] (0,0) -- (0,5) -- (5,5) -- (5,2.5);
+            \draw[\style] (0,5) -- (2,7) node[left]{$\mathcal{M}$} -- (7,7) -- (5,5);
+            \draw[\style] (7,7) -- (7,3.5);
+            \draw[dashed, very thin] (1.5, 0) -- (5,0);
+            \draw[dashed, very thin] (5,0) -- (5,2.5);
+            \draw[dashed, very thin] (5,0) -- (7,2);
+            \draw[dashed, very thin] (7,2) -- (7,3.5);
+
+            \draw[fill = gray!60,\style] (5,2.5) -- (6,3.5) -- (7,3.5) -- (7,7) -- (5,5) -- cycle;
+            \draw[fill = gray!10,\style] (0,5) -- (5,5) -- (7,7) -- (2,7) -- cycle;
+            \draw[dashed, very thin] (5,0) -- (6.5,1.5) -- (5,1.5) -- cycle;
+
+            \begin{scope}[shift={(1.5,-3.5)}]
+            \draw[blue,\style] (0,0) -- (5,0)  node[right]{$\Tilde{\mathcal{M}}$};
+            \draw[blue,\style] (5,0) -- (5,5);
+            \draw[blue,\style] (5,5) -- (0,5);
+            \draw[blue,\style] (0,5) -- (0,0);
+            \draw[blue,\style] (0,5) -- (1,6);
+            \draw[blue,\style] (4.5,7) -- (7,7);
+            \draw[blue,\style] (7,7) -- (5,5);
+            \draw[blue,\style] (7,7) -- (7,2);
+            \draw[blue,\style] (7,2) -- (5,0);
+            \draw[dashed, very thin] (1,6) -- (2,7);
+            \draw[dashed, very thin] (2,7) -- (4.5,7);
+            \draw[fill = blue!10,\style] (0,5) -- (5,5) -- (7,7) -- (4.5,7) -- (3.5, 6) -- (1,6) -- cycle;
+            \draw[fill = blue!40,\style] (5,0) -- (7,2) -- (7,7) -- (5,5) -- cycle;
+            \draw[dashed, very thin] (1,6) -- (2,7) -- (3.5,7) -- (3.5,6) -- cycle;
+            \end{scope}
+        \end{tikzpicture}
+        \caption{3D case (Cartesian)}
+        \label{fig:cartesian}
+    \end{subfigure}
     \begin{subfigure}[b]{0.3\textwidth}
@@
     \label{fig:2d-extrusion}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.35\textwidth}
-    \centering
-    \begin{tikzpicture}[scale = 0.2]
-            \def\style{thick}
-            \draw[\style] (0,0) -- (1.5,0);
-            \draw[\style] (0,0) -- (0,5) -- (5,5) -- (5,2.5);
-            \draw[\style] (0,5) -- (2,7) node[left]{$\mathcal{M}$} -- (7,7) -- (5,5);
-            \draw[\style] (7,7) -- (7,3.5);
-            \draw[dashed, very thin] (1.5, 0) -- (5,0);
-            \draw[dashed, very thin] (5,0) -- (5,2.5);
-            \draw[dashed, very thin] (5,0) -- (7,2);
-            \draw[dashed, very thin] (7,2) -- (7,3.5);
-
-            \draw[fill = gray!60,\style] (5,2.5) -- (6,3.5) -- (7,3.5) -- (7,7) -- (5,5) -- cycle;
-            \draw[fill = gray!10,\style] (0,5) -- (5,5) -- (7,7) -- (2,7) -- cycle;
-            \draw[dashed, very thin] (5,0) -- (6.5,1.5) -- (5,1.5) -- cycle;
-
-            \begin{scope}[shift={(1.5,-3.5)}]
-            \draw[blue,\style] (0,0) -- (5,0)  node[right]{$\Tilde{\mathcal{M}}$};
-            \draw[blue,\style] (5,0) -- (5,5);
-            \draw[blue,\style] (5,5) -- (0,5);
-            \draw[blue,\style] (0,5) -- (0,0);
-            \draw[blue,\style] (0,5) -- (1,6);
-            \draw[blue,\style] (4.5,7) -- (7,7);
-            \draw[blue,\style] (7,7) -- (5,5);
-            \draw[blue,\style] (7,7) -- (7,2);
-            \draw[blue,\style] (7,2) -- (5,0);
-            \draw[dashed, very thin] (1,6) -- (2,7);
-            \draw[dashed, very thin] (2,7) -- (4.5,7);
-            \draw[fill = blue!10,\style] (0,5) -- (5,5) -- (7,7) -- (4.5,7) -- (3.5, 6) -- (1,6) -- cycle;
-            \draw[fill = blue!40,\style] (5,0) -- (7,2) -- (7,7) -- (5,5) -- cycle;
-            \draw[dashed, very thin] (1,6) -- (2,7) -- (3.5,7) -- (3.5,6) -- cycle;
-            \end{scope}
-        \end{tikzpicture}
-        \caption{3D case (Cartesian)}
-        \label{fig:cartesian}
     \end{subfigure}
@@
 The relations between scalar vectors, in the form of $\mathbf{b} = \mathbb{M}_\mu \mathbf{h}$ and $\mathbf{d} = \mathbb{M}_\varepsilon \mathbf{e}$, are to be derived.
-In the simplest case where permittivity $\mu$ and permeability $\varepsilon$ are homogeneous in the domain, and the orthogonality of the pair ($\mathcal{M}, \Tilde{\mathcal{M}}$) is ensured, the material matrices are diagonal with entries
+When permittivity $\mu$ and permeability $\varepsilon$ are homogeneous in the domain and the orthogonality of the pair ($\mathcal{M}, \Tilde{\mathcal{M}}$) holds, the discrete material laws involve diagonal matrices with entries
 
@@
 \subsubsection{Reformulation} \label{sec:reform_discrete}
-In Section \ref{sec:reform_continuous}, we propose a stabilization of the Maxwell system in the non-conducting domain $\Omega_N$ by introducing a Lagrange multiplier.
+In Section \ref{sec:reform_continuous}, we have proposed a stabilization of the Maxwell system in the non-conducting domain $\Omega_N$ by introducing a Lagrange multiplier.
 In the semi-discrete level, the equations to be solved in $\Omega_N$ are
@@
 \end{equation}
-where $\mathbf{U} \in L^2(\Omega \times [0,T], \mathbb{R}^m)$ stands for $m$ conservative variable, $\mathbf{f}(\mathbf{U}) \in L^2(\Omega \times  [0,T], \mathbb{R}^m)$ is the flux density, and $\mathbf{RHS} \in L^2(\Omega \times  [0,T], \mathbb{R}^m)$ is the source term.
+where $\mathbf{U} \in L^2(\Omega \times [0,T], \mathbb{R}^m)$ stands for $m$ conservative variables, $\mathbf{f}(\mathbf{U}) \in L^2(\Omega \times  [0,T], \mathbb{R}^m)$ is the flux density, and $\mathbf{RHS} \in L^2(\Omega \times  [0,T], \mathbb{R}^m)$ is the source term.
 
@@
 
-We would like to emphasize that the Euler system is discretized on $\Tilde{\mathcal{M}}$ due to the fact that 1) the electric current is connected to the momenta of charged particles by (\ref{equ:maxwell_euler_coupling}); 2) the electric current is discretized on dual faces by (\ref{equ:maxwell_grid_ampere}).
+We would like to emphasize that the Euler system is discretized on $\Tilde{\mathcal{M}}$ due to the fact that (i) the electric current is connected to the momenta of charged particles by (\ref{equ:maxwell_euler_coupling}); (ii) the electric current is discretized on dual faces by (\ref{equ:maxwell_grid_ampere}).
 
@@
 \subsubsection{Projection to One Dimension} \label{sec:projection_to_1d}
-Consider a mesh pair $(\mathcal{M}, \Tilde{\mathcal{M}})$ that are constructed by 2D extrusion along $z$-axis and are unbounded along transverse directions.
+Consider a mesh pair $(\mathcal{M}, \Tilde{\mathcal{M}})$ that are constructed by 2D extrusion along the $z$-axis and are unbounded along transverse directions.
 On assuming the transverse invariance and rotational symmetry, we can ``project'' all the D.o.F.
@@
 lying in the perpendicular plane $z=z_k$ to the vertex at $z=z_k$.
-For instance, an edge orthogonal to the $z$-axis is projected to a vertex while a parallel edge to the $z$-axis is projected to an edge.}
+For instance, an edge orthogonal to the $z$-axis is projected to a vertex on the $z$-axis while a parallel edge to the $z$-axis is projected to an edge on the $z$-axis.}
     \label{fig:1d_reduction}
@@
 \end{remark}
-\section{Numerical Experiment}
+\section{Numerical Experiment} \label{sec:numerical_experiment}
 
@@
 \ref{fig:origin-data_vs_time}.
-Besides, the $\mathbf{B}$-field is spiral-shaped and orthogonal to the $\mathbf{E}$-field.
+Besides, the $\mathbf{B}$-field is azimuthal (spiral-shaped) and orthogonal to the $\mathbf{E}$-field.
 Also, under the driven force by the $\mathbf{E}$-field, the electrons move towards the anode $\Gamma^+_C$ as expected.

### 2022-12-01 paper_version/main.tex
incorporate the latest comments

@@
 \usepackage{soul}
+%\usepackage{showlabels}
+\usepackage{multirow}
 
@@
 \begin{itemize}
-    \item we supplement the Maxwell-Euler system by inter-species friction;
-    \item we extend the spatially 1D scheme of \cite{degond_2012} to three spatial dimensions using discrete exterior calculus (DEC) for Maxwell's equations combined with a low-order finite volume method for Euler's equations;
-    \item we propose an essential stabilization in non-conducting regions;
-    \item we introduce suitable boundary conditions for the electromagnetic fields at a spatial truncation boundary.
+    \item We supplement the Maxwell-Euler system by inter-species friction terms.
+    \item We extend the spatially one-dimensional scheme of \cite{degond_2012} to three spatial dimensions using discrete exterior calculus (DEC) to discretize Maxwell's equations combined with a low-order finite volume method for Euler's equations.
+    \item We propose a stabilization in non-conducting regions which is essential for the efficacy of our method.
 \end{itemize}
 
-We stay close to \cite{degond_2012} in terms of discretization in time by semi-implicit time-stepping and by restricting to a cylindrical geometry shown in Fig.
+We stay close to \cite{degond_2012} in terms of discretization in time employing semi-implicit time-stepping.
+We also base our considerations on the model geometry shown in Fig.
 \ref{fig:domain_geometry}.
@@
 \ref{fig:domain_geometry}.
-However, one may encounter subtle problems in defining proper mesh duality as we need it in Section \ref{sec:mesh-duality}.
+However, one may encounter subtle problems in defining proper dual meshes as we need it in Section \ref{sec:mesh-duality}.
 Thus, for the sake of simplicity of presentation we forgo geometric generality.
 
-The quasi-neutral limit of the Maxwell-Euler system leads to a singularly perturbed problem, that is, the PDE system changes its type \footnote{from hyperbolic to a mixed type}.
+The quasi-neutral limit of the Maxwell-Euler system leads to a singularly perturbed problem, that is, the PDE system changes its type\footnote{from hyperbolic to a mixed type}.
 This poses a challenge for simulations in settings encompassing different regimes.
@@
 These schemes are then said to be \emph{asymptotic-preserving} (AP).
-The concept is sketched by the commutative diagram in \cite{jin_1999}.
-We discretize a parametric problem $P^\lambda$, which converges to its limit $P^0$ as the perturbed parameter $\lambda \rightarrow 0$ by the scheme $P^\lambda_h$ where $h$ denotes some discretization parameter, e.g.
-mesh size.
+We discretize a parametric problem $P^\lambda$, which converges to its limit $P^0$ as the perturbed parameter $\lambda \rightarrow 0$, by the scheme $P^\lambda_h$ where $h$ denotes some discretization parameter, e.g.
+the mesh size, see also the illustration by a commuting diagram in \cite[][fig.
+1]{jin_2010}.
 The AP property requires the uniform convergence of $P^\lambda_h$ to the $P^\lambda$ as $\lambda\rightarrow0$.
-For more details about AP schemes, see \cite{jin_2010, degond_2017} for comprehensive reviews.
-
-The content of this paper is organized as follows.
-In Section 2, we give a full description of the underlying equations of the Maxwell-Euler system and its rescaling procedure.
+Readers are referred to the comprehensive reviews in \cite{jin_2010, degond_2017} for more details about AP schemes.
+
+The content of this paper is organized as follows: In Section 2, we give a full description of the underlying equations of the Maxwell-Euler system and its rescaling procedure.
 Meanwhile, the boundary conditions in our setting is elaborated.
@@
 \section{Plasma model}
-\begin{comment}
-Under moderate assumptions, plasmas, which are gases composed of charged particles (and possibly neutral particles), can be treated as fluid and described by hydrodynamic equations.
-Maxwell's equations are involved to describe their induction of and interaction with electromagnetic fields.
-
-After rescalling all the variables with respect to the prescribed reference units, the Debye length $\lambda_D$, characterizing the charge screening ability of the plasma, would pop up and its zero limit, which is what we called \emph{quasi-neutral limit}, is of great interest, since the limit model largely simplifies the system and in many cases the accuracy of the assumption is satisfactory enough.
-
-In this section, the multi-species Maxwell-Euler equations with collision term is introduced first, followed by detailed rescalling procedure.
-The quasi-neutral model will be make clear by letting the rescaled Debye length $\lambda$ go to zero.
-Afterwards, a set of boundary conditions are presented and its validity to both non-limit and limit model is discussed.
-Finally, we would like to present a reformulation of the system which would be crucial to the stability of the numerical scheme.
-\end{comment}
-
-\begin{comment}
-In this work, we discuss and implement the so-called \emph{Euler-Maxwell} system with a focus on its limiting behavior of quasi-neutrality, i.e.
-when the \emph{Debye length} goes to zero.
-The dimensionless form of the Euler-Maxwell equations is parameterized by the rescaled Debye length $\lambda$ whose vanishing limit alters the mathematical nature of the equations.
-To be more concrete, the non-limit model ($\lambda = \mathcal{O}(1)$) is hyperbolic where information spreads with a finite speed whereas the limit model ($\lambda \rightarrow 0$) becomes elliptic, and any changes immediately influence the whole domain.
-In other words, the perturbation of $\lambda$ in the Maxwell-Euler system poses a singular perturbation problem.
-Such switching makes it difficult to handle both models in a single implementation framework, which, however, is desired in many cases where both models coexist in the computational domain.
-Now comes the concept of \emph{asymptotic-preserving}(AP) scheme.
-We turn to the celebrated commuting diagram Fig.
-\ref{fig:commuting_diagram_ap} for illustration.\todo{add illustration of AP schemes}.
-
-The other emphasis of this work is the development of a 3D discretization framework for the Maxwell-Euler system.
-The key ingredient is the combination of the finite volume Method (FVM) for the Euler equations and the Finite Integration Technique (FIT) for Maxwell's equations.
-The latter one is usually treated as a generalization to Yee's scheme \citep{yee_1966} or FDTD.
-The advantage of the FVM-FIT framework lie in the \emph{discrete exterior calculus} (DEC) nature of FIT and straightforward coupling of both systems through the primal-dual mesh pair.
-These would be made clear in the corresponding sections.
-
-\todo{add previous work on AP schemes, FIT, plasma simulation}.
-
-The content of this paper is organized as follows.
-In Section 2 we introduce the full Maxwell-Euler model for plasmas, followed by the rescaling procedure which is crucial to define the rescaled Debye length $\lambda$ and to identify its limiting behavior.
-In the meantime, it is essential to discuss what boundary conditions are appropriate for this singular perturbation problem.
-Section 3 is then dedicated to a brief introduction about \cite{degond_2012} based on which our work is extended.
-In Section 4, we first discuss our FVM-FIT framework in details, especially how the unknowns are assigned on the staggered meshes and the boundary treatment in 3D case.
-Afterwards, the full discretization scheme is presented.
-Special care shall be taken to the treatment of boundary conditions and insulator part of the domain as $\lambda \rightarrow 0$, which is crucial to make the scheme AP.
-A numerical experiment for a 3D cylindrical domain is presented in Section 5 where we want to demonstrate the capability of our scheme in dealing with both non-neutral and quasi-neutral regimes of plasmas.
-
-\begin{figure}
-    \centering
-    \begin{tikzpicture}
-    \node (nw) {\Large $P^\lambda_h$};
-    \node (ne) [right=3cm of nw]{\Large $P^\lambda$};
-    \node (sw) [below=of nw]{\Large $P^0_h$};
-    \node (se) [right=3cm of sw]{\Large $P^0$};
-    \draw[->] (nw.east)  -- node [above,midway] {$h\rightarrow0$} (ne.west) ;
-    \draw[->] (nw.east)  --  (ne.west) ;
-    \draw[->] (nw.south) -- node [left,midway] {$\lambda\rightarrow0$} (sw.north);
-    \draw[->] (nw.south) -- node {} (sw.north);
-    \draw[->] (sw.east)  -- node [above,midway] {$h\rightarrow0$}(se.west);
-    \draw[->] (ne.south) -- node [left,midway] {$\lambda\rightarrow0$} (se.north);
-    \end{tikzpicture}
-    \caption{Commuting diagram of AP schemes}
-    \label{fig:commuting_diagram_ap}
-\end{figure}
-\end{comment}
 
 \subsection{The Maxwell-Euler System}
-Plasmas consist of electrically charged and neutral species that may be treated as gases.
+Plasmas consist of electrically charged and neutral particle species that can be treated as fluids.
 That is, they may be described by the Navier-Stokes equations augmented with source terms for species generation (ionization, recombination), forces (Lorentz force and interspecies friction), and energy (thermal relaxation among species, radiative heat transfer, Ohmic heating).
-For more details on the fluid model of plasma, see \cite{chen2016, remi_2014}.
-
-The Maxwell's equations in SI units read
+For more details on fluid models of plasmas, see \cite{chen2016, remi_2014}.
+
+The electromagnetic effects in plasmas are governed by Maxwell's equations, which Maxwell's equations in SI units read
 \begin{subequations}
@@
 \end{subequations}
-where the involved quantities are magnetic flux density $\mathbf{B}[\frac{\text{Wb}}{\text{m}^2}]$, electric field intensity $\mathbf{E}[\frac{\text{V}}{\text{m}}]$, electric induction $\mathbf{D}[\frac{\text{C}}{\text{m}^2}]$, magnetic field intensity $\mathbf{H}[\frac{\text{A}}{\text{m}}]$, electric current density $\mathbf{J}[\frac{\text{A}}{\text{m}^2}]$ and electric charge density $\rho[\frac{\text{C}}{\text{m}^3}]$.
+where the involved quantities\footnote{SI units in square brackets.} are the magnetic flux density $\mathbf{B}[\frac{\text{Wb}}{\text{m}^2}]$, the electric field $\mathbf{E}[\frac{\text{V}}{\text{m}}]$, the electric displacement field $\mathbf{D}[\frac{\text{C}}{\text{m}^2}]$, the magnetic field $\mathbf{H}[\frac{\text{A}}{\text{m}}]$, the electric current density $\mathbf{J}[\frac{\text{A}}{\text{m}^2}]$ and the electric charge density $\rho[\frac{\text{C}}{\text{m}^3}]$.
 These equations are known as Faraday's law (\ref{equ:maxwell_faraday}), Amp\`{e}re's law (\ref{equ:maxwell_ampere}), Gauss's law for magnetism (\ref{equ:maxwell_gauss_B}) and Gauss's law for electric field (\ref{equ:maxwell_gauss_D}).
-For simplicity, we only consider isotropic and homogeneous media in vacuum.
-We consider the linear constitutive relations
+For simplicity, we only consider isotropic and homogeneous media in vacuum, which amounts to relying on the linear constitutive relations (namely, material laws):
 \begin{equation} \label{equ:material_law}
-    \mathbf{D} = \varepsilon_0 \mathbf{E}, \ \ \ \mathbf{B} = \mu_0\mathbf{H}, 
+    \mathbf{D} = \epsilon \mathbf{E}, \ \ \ \mathbf{B} = \mu\mathbf{H}, 
 \end{equation}
-where $\varepsilon_0[\frac{\text{F}}{\text{m}}]$ and $\mu_0[\frac{\text{N}}{\text{A}^{2}}]$ are vacuum permittivity and permeability of medium.
-By taking the time derivative of (\ref{equ:maxwell_gauss_D}) and the divergence of (\ref{equ:maxwell_ampere}), it is easy to see that the well-posedness requires the charge conservation equation
+where $\epsilon[\frac{\text{F}}{\text{m}}]$ and $\mu[\frac{\text{N}}{\text{A}^{2}}]$ are the permittivity and permeability and assumed to be constant in this paper.
+By taking the time derivative of (\ref{equ:maxwell_gauss_D}) and the divergence of (\ref{equ:maxwell_ampere}), it is easy to see that (\ref{equ:maxwell_ampere}) and (\ref{equ:maxwell_gauss_D}) implies the charge conservation
 \begin{equation} \label{equ:charge_continuity}
@@
 \end{equation}
-Besides, on taking the divergence of equations (\ref{equ:maxwell_faraday}) and (\ref{equ:maxwell_ampere}) together with the relation (\ref{equ:charge_continuity}), it is possible to verify that Gauss's laws (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) are consequences of (\ref{equ:maxwell_faraday}) and (\ref{equ:maxwell_ampere}) provided that (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) are satisfied at initial time.
+Besides, by taking the divergence of equations (\ref{equ:maxwell_faraday}) and (\ref{equ:maxwell_ampere}) together with the relation (\ref{equ:charge_continuity}), it is possible to verify that Gauss's laws (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) are consequences of (\ref{equ:maxwell_faraday}) and (\ref{equ:maxwell_ampere}) provided that (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) are satisfied at initial time.
 In other words, Gauss's laws (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) can be thought of as initial conditions.
 
-Each species in a plasma can be modelled as a compressible fluid by a set of the Euler equations, which additionally includes electromagnetic forces as well as other processes, e.g.
+Each species in a plasma can be modelled as a compressible fluid by a set of Euler equations, which additionally includes electromagnetic forces as well as other processes, e.g.
 collisions and recombination.
@@
 \begin{equation} \label{equ:collision}
-    \mathbf{R}_{e}^{\text{coll}} = \frac{\pi Ze^4m_e^{1/2}}{(4\pi\varepsilon_0)^2(k_BT_e)^{3/2}}\text{ln}\Lambda n_en_i(\mathbf{u}_i - \mathbf{u}_e) = - \mathbf{R}_{i}^{\text{coll}},  
+    \mathbf{R}_{e}^{\text{coll}} = \frac{\pi Ze^4m_e^{1/2}}{(4\pi\epsilon)^2(k_BT_e)^{3/2}}\text{ln}\Lambda n_en_i(\mathbf{u}_i - \mathbf{u}_e) = - \mathbf{R}_{i}^{\text{coll}},  
 \end{equation}
@@
 ionization and recombination, are not considered.
-For full details about the modeling of these physical processes, readers are referred to \cite{fuchs_2021}.
+For full details about the modeling of these physical processes, readers are referred to \cite[][sec.
+3.2]{fuchs_2021}.
 
@@
 In rescaling, variables in equations are replaced by the ratio of original quantities and constant reference quantities, which transforms the system into dimensionless form.
-In this part, the rescaling procedure mostly follows that of \cite{degond_2017}.
+In this part, the rescaling procedure mostly follows that of \cite[][sec.
+2.2]{degond_2017}.
 
@@
 The typical magnitudes of electromagnetic fields are $\overline{E}$ and $\overline{B}$.
-The typical magnitudes of fluid quantities are denoted by $\overline{u}$ for plasma drift velocity, $\overline{n}$ for plasma number density, $\overline{T}$ for plasma temperature.
-On top of that, the typical pressure is set $\overline{n}k_B\overline{T}$ with $k_B$ being the Boltzmann constant; the typical value for the specific total energy and enthalpy is set $\overline{u}^2$.
-Together with the physical parameters, i.e.
-permittivity $\varepsilon_0$, permeability $\mu_0$, light speed $c^2 = (\varepsilon_0\mu_0)^{-1}$, Boltzmann constant $k_B$, the elementary charge $e$, and ion mass $m_i$, the following dimensionless parameters are induced,
+The reference magnitudes of fluid quantities are denoted by $\overline{u}$ for plasma drift velocity, $\overline{n}$ for plasma number density, $\overline{T}$ for plasma temperature.
+On top of that, the reference pressure is set to $\overline{n}k_B\overline{T}$ with $k_B$ being the Boltzmann constant; the reference value for the specific total energy and enthalpy is set to $\overline{u}^2$.
+Also taking into account the physical constants, i.e.
+the reference permittivity $\overline{\epsilon}$, the reference permeability $\overline{\mu}$, the light speed $c^2 = (\overline{\epsilon}\overline{\mu})^{-1}$, Boltzmann constant $k_B$, the elementary charge $e$, and ion mass $m_i$, we introduce the following dimensionless parameters:
 \begin{align*} 
@@
     \beta &:= \frac{\overline{v}\overline{B}}{\overline{E}} \text{ the induced electric field \emph{w.r.t.} the total electric field}, &\\
-    \lambda &:= \frac{\lambda_D}{\overline{x}} \text{ the dimensionless Debye length, where }\lambda_D := \left(\frac{\varepsilon_0k_B\overline{T}}{e^2\overline{n}}\right)^{1/2}, &\\
-    \varepsilon_*^2 &:= \frac{m_*}{m_i} \text{ the species mass \emph{w.r.t.} the ion mass},\ \  * \in \{i,e,\text{neutron},\cdots\}, &\\
+    \lambda &:= \frac{\lambda_D}{\overline{x}} \text{ the dimensionless Debye length, where }\lambda_D := \left(\frac{\epsilon k_B\overline{T}}{e^2\overline{n}}\right)^{1/2}, &\\
+    \varepsilon_*^2 &:= \frac{m_*}{m_i} \text{ the species mass \emph{w.r.t.} the ion mass},\ \  * \in \{i,e,\cdots\}, &\\
     g &:= \frac{1}{\overline{n}\lambda_D^3} \text{ the plasma parameter\footnotemark[2]}.&
@@
 By abuse of notation, the dimensionless quantities have the same symbol as the original quantities.
-For the sake of simplicity, we neglect ionization and recombination but focus on collision terms, i.e.
+For the sake of simplicity, we neglect ionization and recombination but retain collision terms, i.e.
 $\Gamma_* = 0, \mathbf{R}_* = \mathbf{R}_*^\text{coll}, Q_* = Q_*^\text{coll}$ in (\ref{equ:euler_}), while neglecting other effects.
@@
  Assumptions can be made to reduce the number of dimensionless parameters.
-Following \cite{degond_2017}, the reference speed $\overline{v}$ is of the same scale as the plasma speed $\overline{u}$ and the thermal speed $v_{th,i}$ whereas it is much smaller than the light speed $c$.
+Following \cite[][sec.
+2.2]{degond_2017}, the reference speed $\overline{v}$ is of the same scale as the plasma speed $\overline{u}$ and the thermal speed $v_{th,i}$ whereas it is much smaller than the light speed $c$.
 Also, it is assumed that $\eta$ and $\beta$ are of order one and $\xi$ has the same magnitude as $\lambda$.
@@
 From the physical viewpoint, the shielding effect characterized by the rescaled Debye length $\lambda$ makes the impact parameter no larger than $\lambda$.
-The $\lambda \rightarrow 0$ limit implies that the collisions happen in the atomic length scale, in which quantum-mechanical effects must be taken into effect \citep{frank_1972}.
-Therefore, we eliminate the perturbation parameter in the friction term by assuming $g \sim \lambda$ and keep the prefactor of collision term constant $\alpha^{\text{coll}}$ throughout the simulation.
+The $\lambda \rightarrow 0$ limit implies that the collisions happen in the atomic length scale, in which quantum-mechanical effects must be taken into effect \cite[][pp.
+144-148]{frank_1972}.
+Therefore, we eliminate the perturbation parameter in the friction term by assuming $g \sim \lambda$ and keep the prefactor $\alpha^{\text{coll}}$ of the collision term constant throughout the simulation.
 
 \begin{remark}
-    It is also of research interest when there is an asymptotic parameter at the denominator of the friction term.
+    The case when there is an asymptotic parameter at the denominator of the friction term is of interest, too.
 Such problem is called relaxation limit, see \cite{peng_2011, wasiolek_2016, Li_2021, Chen_2000}.
@@
 
-In summary, we make the following choices
+In summary, we make the following choices\cite[][sec 2.2]{degond_2017}
 \begin{align*}
@@
 
-Under such assumptions on these dimensionless parameters, the rescaled Euler-Maxwell system is simplified into a parametric system with the dimensionless Debye length $\lambda$ being the asymptotic parameter
+Under such assumptions on these dimensionless parameters, the rescaled Euler-Maxwell system is simplified to a system of PDEs with the dimensionless Debye length $\lambda$ as asymptotic ($\lambda \rightarrow 0$) parameter
 \begin{subequations}
@@
 \end{align}
-\end{subequations}
+
 with the equation of state $e_* = \frac{1}{2}|\mathbf{u_*}|^2 + \frac{p_*}{\varepsilon^2_* n_* (\gamma - 1)}$ and $h_* = e_* + \frac{p_*}{\varepsilon^2_* n_*}$.
@@
 and consequently, the rescaled friction heat for ions and electrons take the expression
-\begin{align*} 
+\begin{align} 
     Q_i^{\text{coll}} &= \alpha^{\text{coll}}n_en_i \mathbf{u}_i (\mathbf{u}_i - \mathbf{u}_e), \\
     Q_e^{\text{coll}} &= \alpha^{\text{coll}}n_en_i \mathbf{u}_e (\mathbf{u}_e - \mathbf{u}_i).
-\end{align*}
-
-We end up getting the rescaled Maxwell-Euler system parameterized by $\lambda$.
+\end{align}
+The rescaled material laws (\ref{equ:material_law}) keep the same expressions: 
+\begin{equation} \label{equ:maxwell_material_law_rescaled}
+    \mathbf{D} = \epsilon \mathbf{E}, \ \ \ \mathbf{B} = \mu \mathbf{H}, 
+\end{equation}
+\end{subequations}
+but here $\epsilon, \mu$ are the rescaled permittivity and permeability.
+
+We end up with the rescaled Maxwell-Euler system (\ref{equ:maxwell_faraday_rescaled})-(\ref{equ:maxwell_material_law_rescaled}) parameterized by $\lambda$.
 
 \subsection{Quasi-neutral Limit} \label{sec:quasi-neutral_limit}
-The Debye length $\lambda_D$ (see its definition in the preceding section) is the characteristic length over which local concentrations of charge are shielded, see \cite[Sec.
+The Debye length $\lambda_D$ (see its definition in the preceding section) is the characteristic length over which local concentrations of charge are shielded, see \cite[sec.
 1.4]{chen2016} for the underlying physics.
-In many situations, it has a rather low value compared to the reference length scale: the typical $\lambda_D$ for gas discharge and Tokamak is $10^{-4}$ m; for interstellar medium, the magnitude is about $1$ m \cite[ch.
+In many situations, it has a rather low value compared to the reference length scale: the typical $\lambda_D$ for gas discharge and Tokamak is $10^{-4}$ meter; for interstellar medium, the magnitude is about $1$ meter\cite[ch.
 20]{Blandford_2013}.
@@
     \begin{minipage}{0.3\textwidth}
-\begin{subequations}
     \begin{align*}
@@
     \end{align*}
-\end{subequations}
 \end{minipage}
@@
 \end{center}
-The quasi-neutral condition (\ref{equ:maxwell_gauss_D_limit}) is the consequence of taking $\lambda = 0$ in Gauss's law for the electric field (\ref{equ:maxwell_gauss_D_rescaled}).
-Like the non-neutral case, Gauss's laws (\ref{equ:maxwell_gauss_B_limit}) (\ref{equ:maxwell_gauss_D_limit}) are the consequence of (\ref{equ:maxwell_faraday_limit}) (\ref{equ:maxwell_ampere_limit}) provided (\ref{equ:maxwell_gauss_B_limit}) (\ref{equ:maxwell_gauss_D_limit}) are satisfied at initial time.
-
-This limit poses a \emph{singular perturbation problem} in the sense that vanishing $\lambda$ changes the character of the PDE system.
-To be more specific, in the non-limit model the $\mathbf{E}$-field evolves with time whereas in the quasi-neutral model it responds instantaneously to other quantities according to the constraint (\ref{equ:maxwell_ampere_limit}).
-We replace (\ref{equ:maxwell_ampere_rescaled}) by the sum of the curl of (\ref{equ:maxwell_faraday_rescaled}) and the time-derivative of (\ref{equ:maxwell_ampere_rescaled}).
-Meanwhile exploiting the momentum equation in (\ref{equ:euler_rescaled}) to express $\partial_t\mathbf{J}$, we end up getting the equation that the $\mathbf{E}$-field satisfies
+The quasi-neutral condition (\ref{equ:maxwell_gauss_D_limit}) is the consequence of setting $\lambda = 0$ in Gauss's law for the electric field (\ref{equ:maxwell_gauss_D_rescaled}).
+As in the non-neutral case, Gauss's laws (\ref{equ:maxwell_gauss_B_limit}) (\ref{equ:maxwell_gauss_D_limit}) are the consequence of (\ref{equ:maxwell_faraday_limit}) (\ref{equ:maxwell_ampere_limit}) provided (\ref{equ:maxwell_gauss_B_limit}) (\ref{equ:maxwell_gauss_D_limit}) are satisfied at initial time.
+
+This limit represents a \emph{singular perturbation problem} in the sense that vanishing $\lambda$ changes the character of the PDE system.
+To be more specific, for $\lambda = \mathcal{O}(1)$ the $\mathbf{E}$-field evolves with time whereas in the quasi-neutral model it responds instantaneously to other quantities according to the constraint (\ref{equ:maxwell_ampere_limit}).
+We replace (\ref{equ:maxwell_ampere_rescaled}) by the sum of the rotation of (\ref{equ:maxwell_faraday_rescaled}) and the time-derivative of (\ref{equ:maxwell_ampere_rescaled}).
+Meanwhile, due to the link between fluid momenta $n_*u_*$ and current in (\ref{equ:maxwell_euler_coupling}), the term $\partial_t\mathbf{J}$ can be reformulated by the momentum equation according to (\ref{equ:euler_rescaled}) and we end up with the following wave equation with source terms:
 \begin{align}
-    \lambda^2\partial_t^2 \mathbf{E} + \nabla \times \nabla \times \mathbf{E} &= - a\mathbf{E} - \mathbf{b}, \label{equ:E}
+    \lambda^2\partial_t^2 \mathbf{E} + \nabla \times \nabla \times \mathbf{E} &= \mathbf{S}_1 + \mathbf{S}_2, \label{equ:E}
 \end{align}
 where
-\begin{equation*}
-    a = \sum_*\varepsilon_*^{-2}q_*^2n_*, \ \ \ \mathbf{b} = \sum_* \epsilon_*^{-2}q_*^2n_*\mathbf{u}_*\times\mathbf{B} - q_*\nabla\cdot(n_* \mathbf{u}_* \otimes \mathbf{u}_* + \varepsilon_*^{-2}p_*\mathbb{I}).
-\end{equation*}
- (\ref{equ:E}) makes it obvious the shift from hyperbolic to elliptic for the evolution equations for the $\mathbf{E}$-field as $\lambda\rightarrow0$.
+\begin{align*}
+    \mathbf{S}_1 &= - \left(\sum_*\varepsilon_*^{-2}q_*^2n_*\right)\mathbf{E}, \\
+    \mathbf{S}_2 &= \sum_* q_*\nabla\cdot(n_* \mathbf{u}_* \otimes \mathbf{u}_* - \varepsilon_*^{-2}p_*\mathbb{I}\varepsilon_*^{-2}q_*^2n_*\mathbf{u}_*\times\mathbf{B} - q_*\varepsilon_*^{-2}\mathbf{R}^\text{coll}_*).
+\end{align*}
+ It is obvious in (\ref{equ:E}) that the electric field propagate with finite speed (hyperbolic evolution) when $\lambda = \mathcal{O}(1)$, whereas for $\lambda = 0$ they respond instantaneously everywhere to local excitation (parabolic evolution/elliptic boundary value problems).
 
 \begin{remark}
-    The preceeding formal limit argument is rather heuristic.
-Deep mathematical tools from perturbation theory is needed to rigorously prove the convergence of the limiting sequence.
-This topic is beyond the scope of this paper and thus omitted.
+    The preceeding formal limit argument is heuristic.
+Deep mathematical tools from perturbation theory would be needed to rigorously prove the convergence of the limiting sequence.
+This topic is beyond the scope of this paper.
 Readers are referred to \cite[ch.
@@
 
-We consider a simply-connected domain $\Omega$ comprising two sub-domains $\Omega_P$ and $\Omega_N$ representing plasma domain and non-conducting domain respectively.
-We use the notation $\Gamma_C := \partial\Omega \cap \partial\Omega_P$, denoting the contact boundary, and $\Gamma_I := \partial\Omega \cap \partial\Omega_N$ for the insulating boundary with an artificial cut-off boundary.
+We consider a simply-connected domain $\Omega$ comprising two sub-domains $\Omega_P$ (plamsa domain) and $\Omega_N$ (non-conducting domain).
+They represent regions of space occupied by plasma and a non-conducting linear dielectric medium (e.g.
+glass) respectively.
+We use the notation $\Gamma_C := \partial\Omega \cap \partial\Omega_P$ to denote the contact boundary, and $\Gamma_I := \partial\Omega \cap \partial\Omega_N$ for the insulating boundary with an artificial cut-off boundary.
 The interface between the two domains is denoted by $\Gamma_W = \partial\Omega_I \cap \partial\Omega_P$.
@@
 
-The plasma fills $\Omega_P$ where the Euler system is defined and the boundary of the plasma domain is $\partial\Omega_P$.
-We consider the physical scenario where plasmas are confined by solid insulator.
+The Euler system is defined in $\Omega_P$ with boundary $\partial\Omega_P$.
+We consider the physical scenario where plasma is confined by a solid insulator.
 Therefore, the interface $\Gamma_W$ is treated as reflective wall where fluid particles are bounced back while keeping the tangential velocity and energy unchanged.
@@
 \begin{remark}
-    The treatment of electrodes as open boundary is a rather simplified approach. For more realistic electrode modelling, see \cite{godyak_1990, parker_1993}.
+    The treatment of electrodes as open boundary is am extreme simplification. For more realistic electrode modelling, see \cite{godyak_1990, parker_1993}.
 \end{remark}
@@
 The Maxwell system is defined on the whole domain $\Omega$.
-The insulating boundary blocks energy interchange and therefore only admits zero electric and magnetic flux, in the sense that $\text{curl}\mathbf{E}\cdot \mathbf{n} = 0$ and $\text{curl}\mathbf{H}\cdot \mathbf{n} = 0$ where $\mathbf{n}$ is the normal vector.
-We model the electrodes on the contact boundary $\Gamma_C = \Gamma_C^+\cup \Gamma_C^-$ which are two disjoint connecting components.
-A vanishing tangential component $\mathbf{E}_t$ of the $\mathbf{E}$-field is imposed on $\Gamma_C$.
-Since we have $\text{curl}\mathbf{E} \cdot \mathbf{n} = 0$ on the whole boundary $\partial\Omega$, there exists a scalar potential $\varphi$ defined on $\partial\Omega$ such that the tangential component $\mathbf{E}_t = \nabla_\Gamma \varphi$ where $\nabla_\Gamma$ denotes surface gradient.
-$\varphi$ is set constant in each component of $\Gamma_C$, that is, from a physical point of view, $\varphi$ is the external potential difference applied to the electrodes.
+The insulating boundary $\Gamma_I$ blocks energy interchange and therefore only admits zero electric and magnetic flux, in the sense that $\mathbf{D}\cdot \mathbf{n}|_{\Gamma_I} = 0$ and $\mathbf{B} \cdot \mathbf{n}|_{\Gamma_I} = 0$ where $\mathbf{n}$ is the normal vector.
+We model the electrodes by imposing boundary conditions on the contact boundary $\Gamma_C = \Gamma_C^+\cup \Gamma_C^-$ which is composed of two disjoint connected components.
+On the contact boundary $\Gamma_C$, the tangential component $\mathbf{E}_t$ of the $\mathbf{E}$-field is set to zero.
+By Faraday's law (\ref{equ:maxwell_faraday_rescaled}) we have $\nabla \times \mathbf{E} \cdot \mathbf{n} = 0$ on the whole (topologically trivial) boundary $\partial\Omega$.
+It admits a scalar potential $\varphi$ defined on $\partial\Omega$ such that $\mathbf{E}_t = \nabla_\Gamma \varphi$ where $\nabla_\Gamma$ denotes surface gradient.
+$\varphi$ is constant on $\Gamma_C^+$ and $\Gamma_C^-$.
+The difference of these two constant values is the voltage drop between the two contacts.
 \begin{figure}
@@
 
-    To summarize the boundary conditions for both systems:
+    We summarize the boundary conditions for both sets of equations:
 
@@
     \mathbf{u_*}\cdot \mathbf{n} &= 0 \ \ \text{on} \ \ \Gamma_W, \\
-    \text{grad}\mathbf{u_*} \cdot \mathbf{n} &= \mathbf{0} \ \ \text{on} \ \ \Gamma_C, \\
-    \text{grad}n_* \cdot \mathbf{n} &= 0 \ \ \text{on} \ \ \Gamma_W \cup \Gamma_C, \\
-    \text{grad}e_* \cdot \mathbf{n} &= 0 \ \ \text{on} \ \ \Gamma_W \cup \Gamma_C.
+    \nabla \mathbf{u_*} \cdot \mathbf{n} &= \mathbf{0} \ \ \text{on} \ \ \Gamma_C, \\
+    \nabla n_* \cdot \mathbf{n} &= 0 \ \ \text{on} \ \ \Gamma_W \cup \Gamma_C, \\
+    \nabla e_* \cdot \mathbf{n} &= 0 \ \ \text{on} \ \ \Gamma_W \cup \Gamma_C.
 \end{align*}
@@
     \begin{align*}
-    \text{curl} \mathbf{E} \cdot \mathbf{n} = 0\ \ &\text{on} \ \  \partial\Omega,  \\
-    \text{curl} \mathbf{H} \cdot \mathbf{n} = 0\ \ &\text{on} \ \  \Gamma_I,  \\
+    \mathbf{D} \cdot \mathbf{n} = 0\ \ &\text{on} \ \  \partial\Omega,  \\
+    \mathbf{B} \cdot \mathbf{n} = 0\ \ &\text{on} \ \  \Gamma_I,  \\
     \varphi = \varphi^\pm(t)\ \ &\text{on} \ \ \Gamma_C^\pm.
@@
 \begin{remark}
-    No boundary conditions for Maxwell's equations are needed on $\Gamma_W$.
+    No interface condition for Maxwell's equations is needed on $\Gamma_W$.
 \end{remark}
 
-\begin{remark} For a geometric setting with non-trivial geometry, e.g.
-with a tunnel, \emph{curl}$\mathbf{E}\cdot\mathbf{n}$ does not lead to the existence of a surface potential $\varphi:\mathbf{E}_t = \nabla_\Gamma\varphi$.
+\begin{remark} For a geometric setting with non-trivial topology, e.g.
+with a tunnel, $\nabla \times \mathbf{E}\cdot\mathbf{n} = 0$ does not support the existence of a surface potential $\varphi$ satisfying $\mathbf{E}_t = \nabla_\Gamma\varphi$.
 One needs to consider co-homology vector fields \cite{Hiptmair_2021}.
@@
 \ref{fig:domain_sketch}), the Euler system is not defined there due to the absence of plasmas.
-Consequently, the Maxwell system in $\Omega_N$ is described by
+Consequently, the Maxwell system in $\Omega_N$ boils down to
 \begin{subequations}
@@
 Nonetheless, as the system approaches the quasi-neutral limit as $\lambda \rightarrow 0$, Gauss's law for $\mathbf{D}$-field (\ref{equ:gauss_D_ins}) becomes degenerate.
-Due to limited machine precision, schemes based on this set of PDEs would become unstable as $\lambda \rightarrow 0$.
-The vanishing divergence would break down as $\nabla \cdot \mathbf{D} = 0/\lambda^2 = 0$ would not hold numerically when $\lambda^2$ becomes extremely small.
+Schemes based on this set of PDEs would become unstable as $\lambda \rightarrow 0$.
+The vanishing divergence constraint would evaporate as $\nabla \cdot \mathbf{D} = 0/\lambda^2 = 0$ would not hold numerically when $\lambda^2$ becomes extremely small.
 
@@
 
-Again, Gauss's law for the $\mathbf{B}$-field (\ref{equ:gauss_B_ins_limit}) is redundant while Gauss's law for $\mathbf{D}$-field (\ref{equ:gaus_D_ins_limit}) is no longer the consequence of Amper\`{e}'s law.
-However, it is essential for the well-posedness of the problem \citep{ana_2010}.
-From this perspective, the degeneracy of Gauss's law for $\mathbf{D}$-field in the system (\ref{equ:faraday_ins_limit}) to (\ref{equ:gaus_D_ins_limit}) as $\lambda \rightarrow 0$ poses some problem.
-
+Again, Gauss's law for the $\mathbf{B}$-field (\ref{equ:gauss_B_ins_limit}) is redundant while Gauss's law for the $\mathbf{D}$-field (\ref{equ:gaus_D_ins_limit}) is no longer the consequence of Amp\`{e}re's law (\ref{equ:ampere_ins_limit}).
+However, it is essential for the well-posedness of the problem \cite[][p.
+7]{ana_2010}.
+Obviously, the degeneracy of Gauss's law for the $\mathbf{D}$-field in the system (\ref{equ:faraday_ins_limit}) to (\ref{equ:gaus_D_ins_limit}) as $\lambda \rightarrow 0$ poses some problem.
 In other words, the set of equations (\ref{equ:faraday_ins_limit}) to (\ref{equ:gaus_D_ins_limit}) ``approaches" an ill-posed situation as $\lambda \rightarrow 0$.
-This is totally fine in the continuous level while it could be problematic in the discrete level due to a limited floating-point precision.
-
-We propose the following reformulation as a remedy, which introduces a Lagrange multiplier $\psi$ and removes the $\lambda^2$ prefactor in Gauss's law for $\mathbf{D}$-field:
+This is totally fine in the continuous level while it could be problematic on the discrete level due to limited machine precision.
+
+As a remedy, we propose the following reformulation which introduces a scalar Lagrange multiplier $\psi$ and removes the $\lambda^2$ prefactor in Gauss's law for the $\mathbf{D}$-field:
 \begin{subequations}
@@
 Supplemented with the boundary condition $\psi = 0$ on $\partial\Omega_N$, one can check that (\ref{equ:faraday_ins_reform}) to (\ref{equ:gauss_D_ins_reform}) are equivalent to the original formulation (\ref{equ:faraday_ins})-(\ref{equ:gauss_D_ins}) by verifying that $\psi = 0$ in $\Omega_N$.
-This is done by taking the divergence of (\ref{equ:ampere_ins_reform}) such that the Laplace equation of $\psi$ with zero Dirichlet boundary condition gives vanishing $\psi$.
-The importance of this reformulation will be made clear in the numerical experiment, see Section \ref{sec:numerical_experiment}.
+This is done by taking the divergence of (\ref{equ:ampere_ins_reform}), which results in $\delta\psi = 0$ and the zero Dirichlet boundary condition gives vanishing $\psi$.
+The importance of this reformulation will become clear in the numerical experiments, see Section \ref{sec:numerical_experiment}.
 
@@
 \subsection{Primal-dual Staggered Meshes} \label{sec:mesh-duality}
-\subsubsection{Geometric Property}
+\subsubsection{Definition and Geometric Construction}
 Prior to the spatial discretization of the Maxwell-Euler system, we introduce primal-dual staggered meshes that are necessary in the discretization framework we use.
-The spatial domain is discretized by two meshes that interlace with each other, denoted by a mesh doublet $(\mathcal{M}, \Tilde{\mathcal{M}})$ for primal mesh and dual mesh respectively.
-The fundamental duality property requires that \emph{each edge of one mesh penetrates a face of the other mesh and that each vertex of one mesh lies inside of a cell of the other mesh} \citep{weiland_2003}, which makes $(\mathcal{M}, \Tilde{\mathcal{M}})$ staggered.
+The spatial domain is covered by two meshes that interlace with each other, denoted by a mesh doublet $(\mathcal{M}, \Tilde{\mathcal{M}})$ for primal mesh and dual mesh respectively.
+The fundamental duality property requires that \emph{each edge of one mesh penetrates a face of the other mesh and that each vertex of one mesh lies inside of a cell of the other mesh} \cite[][sec.
+2]{weiland_2003}, which makes $(\mathcal{M}, \Tilde{\mathcal{M}})$ staggered to each other.
 A simple example for Cartesian meshes is shown in Fig.
@@
 
-To clarify the notation, in three dimensions the primal mesh $\mathcal{M}$ is a cell complex defined by the set of elements $\{P, L, A, V\}$\footnote{The notation here is a bit floppy.
-$P, L, A, V$ can refer to a single element or a set of elements.} denoting \emph{vertices, edges, faces} and \emph{cells} respectively.
+To clarify the notation, in three dimensions the primal mesh $\mathcal{M}$ is a cell complex defined by the set of mesh entities $\{P, L, A, V\}$\footnote{The notation here is a bit sloppy.
+$P, L, A, V$ can refer to a single entity or a set of entities depending on the context.} denoting \emph{vertices, edges, faces} and \emph{cells} respectively.
 In the same way, the dual mesh $\Tilde{\mathcal{M}}$ is defined by $\{\Tilde{P}, \Tilde{L}, \Tilde{A}, \Tilde{V}\}$.
-Elements of two meshes are associated with bijective pairings $P \leftrightarrow \Tilde{V}$, $L \leftrightarrow \Tilde{A}$, $A \leftrightarrow \Tilde{L}$ and $V \leftrightarrow \Tilde{P}$ which arise in a very natural way: $P(\Tilde{P} \text{ resp.})$ corresponds to $\Tilde{V}(V \text{ resp.})$ where it lies and $L(\Tilde{L} \text{ resp.})$ penetrates its corresponding $\Tilde{A}(A \text{ resp.})$.
-According to their dimensions, vertices, edges, faces and cells are also termed 0-dim, 1-dim, 2-dim and 3-dim elements respectively.
-Meanwhile, we denote by $N_\ast, \ast \in \{P, \Tilde{P}, L, \Tilde{L},A, \Tilde{A},V, \Tilde{V}\}$ the total number of elements in $\mathcal{M}, \Tilde{\mathcal{M}}$.
+The entities of two meshes are associated with bijective pairings $P \leftrightarrow \Tilde{V}$, $L \leftrightarrow \Tilde{A}$, $A \leftrightarrow \Tilde{L}$ and $V \leftrightarrow \Tilde{P}$ which arise in a very natural way: $P(\Tilde{P} \text{ resp.})$ corresponds to $\Tilde{V}(V \text{ resp.})$ in which it lies and $L(\Tilde{L} \text{ resp.})$ penetrates its corresponding $\Tilde{A}(A \text{ resp.})$.
+According to their dimensions, vertices, edges, faces and cells are also called 0-dim, 1-dim, 2-dim and 3-dim entities respectively.
+Meanwhile, we denote by $N_\ast, \ast \in \{P, \Tilde{P}, L, \Tilde{L},A, \Tilde{A},V, \Tilde{V}\}$ the total number of entities in $\mathcal{M}, \Tilde{\mathcal{M}}$.
 
@@
 
-In three dimensions, the meshes are constructed by extruding the 2D meshes vertically along one axis in a staggered manner \cite{Marrone_2001}.
+In three dimensions, the meshes are constructed by extruding the 2D meshes vertically along one axis in a staggered manner \cite[][sec.
+3.1]{Marrone_2001}.
 See an example in Fig.
@@
 For a general setting, one can directly decompose the domain into tetrahedrons and constructs the Voronoi grid, but the procedure is more complicated and time-consuming and may not yield a valid dual mesh.
-The full discretization of the cylindrical domain is given in Fig.
+The meshes for the cylindrical domain are displayed in Fig.
 \ref{fig:primal_dual_meshes}.
 
-The geometric orthogonality between $L \leftrightarrow \Tilde{A}$ and $A \leftrightarrow \Tilde{L}$ is satisfied and would be a crucial property for approximating the material laws shown in the following section.
+The geometric orthogonality between $L \leftrightarrow \Tilde{A}$ and $A \leftrightarrow \Tilde{L}$ is satisfied and will be a crucial property for approximating the material laws on the discrete level (which is the so-called Discrete Hodge operator \cite{hip_1999, bossavit1999}), as will be shown in Section \ref{sec:fit}.
 
@@
 In this case their circumcenters lie outside the triangles and the intersection between edges and faces is violated.
-An alternative approach is barycenter-based dual meshes, which are not restricted to an acute-angle triangulation \cite{Marrone_2001}.
+An alternative approach is barycenter-based dual meshes, which are not restricted to an acute-angle triangulation \cite[][sec.
+4.2]{Marrone_2001}.
 \end{remark}
@@
     \caption{Illustration of primal and dual meshes.
-(a) A Delaunay-Voronoi grid in 2D (b) The extrusion of 2D mesh.
+\textbf{(a)} A Delaunay-Voronoi grid in 2D.
+\textbf{(b)} The extrusion of 2D mesh.
 Six triangle prisms are primal cells (depicted by black and gray edges).
@@
 The dashed hexagon represents the intersection of the dual cell and primal cells.
-(c) A Cartesian case.}
+\textbf{(c)} A Cartesian case.}
     \label{fig:illustration_primal_dual}
@@
 \subsubsection{Orientation and Incidence Matrices}
-Each geometric element in the primal mesh $\mathcal{M}$ is (arbitrarily) endowed with an \emph{internal orientation}\footnote{This notion should not be aliased with \emph{inner orientation}, which has a slightly different definition, see \cite{tonti_2002}.}.
+Each geometric entity in the primal mesh $\mathcal{M}$ is (arbitrarily) endowed with an \emph{internal orientation}\footnote{This notion should not be aliased with \emph{inner orientation}, which has a slightly different definition, see \cite[][sec.
+3.1]{tonti_2002}.}.
 The notion is sketched in Fig.
 \ref{fig:orientation}.
-For the elements of the dual mesh $\Tilde{\mathcal{M}}$, we set their internal orientations to be aligned with their corresponding primal elements according to the bijective pairings, i.e.
+For the entities of the dual mesh $\Tilde{\mathcal{M}}$, we set their internal orientations to be aligned with their corresponding primal entities according to the bijective pairings, i.e.
 edges penetrate faces.
 
-Another orientation attribute, \emph{induced orientation}, is defined as follows: an induced orientation of a k-dim element $f$ with respect to a (k+1)-dim element $f'$, satisfying $f \subset \partial f' $, is determined by the internal orientation of $f'$ according to the rule shown in Fig.
+Another orientation attribute, \emph{induced orientation}, is defined as follows: an induced orientation of a k-dim entity $f$ with respect to a (k+1)-dim entity $f'$, satisfying $f \subset \partial f' $, is determined by the internal orientation of $f'$ according to the rules shown in Fig.
 \ref{fig:orientation}.
@@
 To describe the primal face-to-edge relation, for instance, a sparse matrix $\mathbb{C} \in \mathbb{R}^{N_A \times N_L}$ is assembled whose $(i,j)$-entry is assigned $+1$ if the internal orientation of edge $L_j$ and its induced orientation with respect to face $A_i$ coincides; it is assigned $-1$ if two orientations are opposite; and assigned $0$ if $L_j$ is not a subset of the boundary of $A_i$.
-We will see later that $\mathbb{C}$ functions as a discrete version of the curl operator.
+We will see later that $\mathbb{C}$ functions as a discrete version of the rotation operator.
 The other incidence matrices are constructed in the same manner, see Tab.
 \ref{tab:incidence_mat} for a summary.
-Given the link of orientations of $\mathcal{M}$ and $\Tilde{\mathcal{M}}$, we can derive the relations listed in Tab.
+Given the relationship of orientations of $\mathcal{M}$ and $\Tilde{\mathcal{M}}$, we can derive the relations listed in Tab.
 \ref{tab:incidence_relation}.
@@
     \centering
-    \begin{tabular}{c c c c}
+    \begin{tabular}{c c l l}
     \hline
@@
     \hline
-         $\mathbb{D}\ (\Tilde{\mathbb{D}})$ & $N_V \times N_A\ (N_{\Tilde{V}} \times N_{\Tilde{A}})$ & cell $\rightarrow$ face & discrete div \\
-         $\mathbb{C}\ (\Tilde{\mathbb{C}})$ & $N_A \times N_L\ (N_{\Tilde{A}} \times N_{\Tilde{L}})$ & face $\rightarrow$ edge & discrete curl \\
-         $\mathbb{G}\ (\Tilde{\mathbb{G}})$ & $N_L \times N_P\ (N_{\Tilde{L}} \times N_{\Tilde{P}})$ & edge $\rightarrow$ vertex & discrete grad \\
+         $\mathbb{D}\ (\Tilde{\mathbb{D}})$ & $N_V \times N_A\ (N_{\Tilde{V}} \times N_{\Tilde{A}})$ & cell $\rightarrow$ face & discrete divergence \\
+         $\mathbb{C}\ (\Tilde{\mathbb{C}})$ & $N_A \times N_L\ (N_{\Tilde{A}} \times N_{\Tilde{L}})$ & face $\rightarrow$ edge & discrete rotation \\
+         $\mathbb{G}\ (\Tilde{\mathbb{G}})$ & $N_L \times N_P\ (N_{\Tilde{L}} \times N_{\Tilde{P}})$ & edge $\rightarrow$ vertex & discrete gradient
+         \\
     \hline
@@
     \centering
-    \begin{tabular}{l c}
+    \begin{tabular}{l l}
     \hline
@@
     \hline
-         $\mathbb{G}^T = -\Tilde{\mathbb{D}}$  &  $\text{grad}^* = - \text{div}$\\
-         $\mathbb{C}^T = \Tilde{\mathbb{C}}$   &  $\text{curl}^* = \text{curl}$\\
-         $\mathbb{D}^T = -\Tilde{\mathbb{G}}$  &  $\text{div}^* = - \text{grad}$\\
-         $\mathbb{C}\mathbb{G} = \mathbf{0}, \Tilde{\mathbb{C}}\Tilde{\mathbb{G}} = \mathbf{0}$  &  curl $\circ$ grad = 0 \\
-         $\mathbb{D}\mathbb{C} = \mathbf{0}, \Tilde{\mathbb{D}}\Tilde{\mathbb{C}} = \mathbf{0}$   &  div $\circ$ curl = 0 \\
+         $\mathbb{G}^T = -\Tilde{\mathbb{D}}$  &  $\nabla ^* = - (\nabla \cdot) $\\
+         $\mathbb{C}^T = \Tilde{\mathbb{C}}$   &  $(\nabla \times) ^* = (\nabla \times) $\\
+         $\mathbb{D}^T = -\Tilde{\mathbb{G}}$  &  $(\nabla \cdot) ^* = - \nabla $\\
+         $\mathbb{C}\mathbb{G} = \mathbf{0}, \Tilde{\mathbb{C}}\Tilde{\mathbb{G}} = \mathbf{0}$  &  $(\nabla \times)\circ \nabla = 0$ \\
+         $\mathbb{D}\mathbb{C} = \mathbf{0}, \Tilde{\mathbb{D}}\Tilde{\mathbb{C}} = \mathbf{0}$   &  $(\nabla \cdot) \circ ( \nabla \times) = 0$ \\
     \hline
@@
     \caption{Illustration of internal and induced orientations.
-The internal orientation of each element is depicted in black color: vertices are oriented as \emph{sink} by default; edges are oriented by their pointing direction; faces are oriented by their normal vector; cells are oriented as positive default.
-The induced orientations are depicted in blue color: the ending vertex of an edge is negatively oriented while the starting point is positively oriented; the orientations of edges with respect to a face obey the right-hand rule; a face of a cell are oriented by its outer normal vector.
+The internal orientation of each entity is depicted in black: vertices are oriented as \emph{sink} by default; edges are oriented by their pointing direction; faces are oriented by their normal vector; cells are oriented positive by default.
+The induced orientations are depicted in blue: the ending vertex of an edge is negatively oriented while the starting point is positively oriented; the orientations of edges with respect to a face obey the right-hand rule; a face of a cell are oriented by its outer normal vector.
 }
@@
 The dual mesh $\Tilde{\mathcal{M}}$ is generated afterwards.
-To make both meshes aligned at boundary, we have to truncate the \emph{dual} elements near the boundary due to the staggered character.
+To make both meshes aligned at boundary, we have to truncate the \emph{dual} entities near the boundary due to the staggered character.
 In the meantime, auxiliary geometric entities are needed to close $\Tilde{\mathcal{M}}$, see Fig.
@@
 \ref{fig:illustraion_dual_boundary}, which necessitates a versatile data structure to include such situations.
-In the following, the auxiliary elements would be treated as dual elements, which limits the validity of the relations in Tab.
+In the following, the auxiliary entities would be treated as dual entities, which limits the validity of the relations in Tab.
 \ref{tab:incidence_relation} to interior part of $\Tilde{\mathcal{M}}$.
+For a more systematic illustration that considers the boundary dual entities, see \cite[][sec.
+5]{hip_1999}.
+
+\begin{figure}
+    \centering
+    \includegraphics[scale=0.3]{primal_mesh.png}
+    \hspace{1cm}
+    \includegraphics[scale=0.3]{dual_mesh.png}
+    \caption{Primal mesh (left) and dual mesh (right).}
+    \label{fig:primal_dual_meshes}
+\end{figure}
 
@@
 Before the cut-off, the boundary of $\Tilde{\mathcal{M}}$ is not well-defined.
-To resolve the same boundary as $\mathcal{M}$, boundary dual cells are truncated and auxiliary elements are supplemented (shown in orange color).
+To resolve the same boundary as $\mathcal{M}$, boundary dual cells are truncated and auxiliary entities are supplemented (shown in orange color).
 To be specific, in subfigure (c) four edges and one face are added in order to close this dual cell.
@@
 
+A pair of primal and dual meshes for the geometry in Fig. \ref{fig:domain_sketch} is displayed in Fig. \ref{fig:primal_dual_meshes}.
+
 \subsection{Discrete Maxwell Equations}
-\subsubsection{Finite Integration Technique (FIT)}
+\subsubsection{Finite Integration Technique (FIT)} \label{sec:fit}
 We utilize FIT to discretize Maxwell's equations.
-This framework was originally proposed in \cite{weiland_1977} and can be treated as a generalization of Yee's FDTD method \cite{yee_1966}.
-FIT is established based on the integral form of Maxwell's equations:
+This framework was originally proposed in \cite{weiland_1977} and can be regarded as a generalization of Yee's FDTD method \cite{yee_1966}.
+To derive the discrete Maxwell model under FIT, we first integrate the (rescaled) Maxwell equations (\ref{equ:maxwell_faraday_rescaled})-(\ref{equ:maxwell_gauss_D_rescaled})
 \begin{subequations}
 \begin{align}
-    &\oint_{\partial A} \mathbf{E} \cdot d\mathbf{s} \ = - \iint_A \frac{\partial \mathbf{B}}{\partial t} \cdot d\mathbf{A}, \label{equ:maxwell_int_faraday}\\
-    &\oint_{\partial A} \mathbf{H} \cdot d\mathbf{s} \ = \iint_A \left(\frac{\partial \mathbf{D}}{\partial t} + \mathbf{J}\right) \cdot d\mathbf{A}, \label{equ:maxwell_int_ampere}\\
-    &\oint_{\partial V} \mathbf{B} \cdot d\mathbf{A} = 0, \label{equ:maxwell_int_gauss_B}\\
-    &\oint_{\partial V} \mathbf{D} \cdot d\mathbf{A} = \iiint_V \rho dV. \label{equ:maxwell_int_gauss_D}
+    &\oint_{\partial A} \mathbf{E} \cdot \text{d}\mathbf{s} \ = - \iint_A {\partial_t \mathbf{B}} \cdot \text{d}\mathbf{A}, \label{equ:maxwell_int_faraday}\\
+    &\oint_{\partial A} \mathbf{H} \cdot \text{d}\mathbf{s} \ = \iint_A \left({\lambda^2\partial_t \mathbf{D}} + \mathbf{J}\right) \cdot \text{d}\mathbf{A}, \label{equ:maxwell_int_ampere}\\
+    &\oint_{\partial V} \mathbf{B} \cdot \text{d}\mathbf{A} = 0, \label{equ:maxwell_int_gauss_B}\\
+    &\oint_{\partial V} \lambda^2\mathbf{D} \cdot \text{d}\mathbf{A} = \iiint_V \rho \text{d}V. \label{equ:maxwell_int_gauss_D}
 \end{align}
@@
 
-Given the mesh pair $(\mathcal{M}, \Tilde{\mathcal{M}})$, the discrete Maxwell system is described by applying the integral equations (\ref{equ:maxwell_int_faraday})-(\ref{equ:maxwell_int_gauss_D}) to the elements in $(\mathcal{M}, \Tilde{\mathcal{M}})$.
+Given the mesh pair $(\mathcal{M}, \Tilde{\mathcal{M}})$, the discrete Maxwell system arises from applying the integral equations (\ref{equ:maxwell_int_faraday})-(\ref{equ:maxwell_int_gauss_D}) to the entities in $(\mathcal{M}, \Tilde{\mathcal{M}})$.
 We end up with
@@
 \begin{align}
-    &\sum_{k:L_k\in\partial A_l} \underbrace{\int_{L_k} \mathbf{E} \cdot d\mathbf{s}}_{:= e_k} = - \frac{\partial}{\partial t} \underbrace{\iint_{A_l} \mathbf{B} \cdot d\mathbf{A}}_{:= b_l},\ \ \ l = 1,...,N_A, \label{equ:maxwell_grid_faraday} \\
-    &\sum_{k:\Tilde{L}_k\in\partial \Tilde{A}_l} \underbrace{\int_{\Tilde{L}_k} \mathbf{H} \cdot d\mathbf{s}}_{:= h_k} = \frac{\partial}{\partial t} \underbrace{\iint_{\Tilde{A}_l} \mathbf{D} \cdot d\mathbf{A}}_{:= d_l} + \underbrace{\iint_{\Tilde{A}_l} \mathbf{J} \cdot d\mathbf{A}}_{:= j_l}, \ \ \ l = 1,...,N_{\Tilde{A}}, \label{equ:maxwell_grid_ampere}\\
-    &\sum_{k:A_k\in \partial V_l} \iint_{A_k} \mathbf{B} \cdot d\mathbf{A} = 0,\ \ \ l = 1,..., N_V,\label{equ:maxwell_grid_gauss_B}\\
-    &\sum_{k:\Tilde{A}_k \in \partial\Tilde{V}_l}\iint_{\Tilde{A}_k} \mathbf{D} \cdot d\mathbf{A} = \underbrace{\iiint_{\Tilde{V}_l} \rho dV}_{:= q_l},\ \ \ l = 1,...,N_{\Tilde{V}}.
+    \sum_{k:L_k\in\partial A_l} \underbrace{\int_{L_k} \mathbf{E} \cdot \text{d}\mathbf{s}}_{:= e_k} &= - {\partial_t} \underbrace{\iint_{A_l} \mathbf{B} \cdot \text{d}\mathbf{A}}_{:= b_l},&l = 1,...,N_A, \label{equ:maxwell_grid_faraday} \\
+    \sum_{k:\Tilde{L}_k\in\partial \Tilde{A}_l} \underbrace{\int_{\Tilde{L}_k} \mathbf{H} \cdot \text{d}\mathbf{s}}_{:= h_k} &= \lambda^2{\partial_t} \underbrace{\iint_{\Tilde{A}_l} \mathbf{D} \cdot \text{d}\mathbf{A}}_{:= d_l} + \underbrace{\iint_{\Tilde{A}_l} \mathbf{J} \cdot \text{d}\mathbf{A}}_{:= j_l}, &l = 1,...,N_{\Tilde{A}}, \label{equ:maxwell_grid_ampere}\\
+    \sum_{k:A_k\in \partial V_l} \iint_{A_k} \mathbf{B} \cdot \text{d}\mathbf{A} &= 0,&l = 1,..., N_V,\label{equ:maxwell_grid_gauss_B}\\
+    \lambda^2\sum_{k:\Tilde{A}_k \in \partial\Tilde{V}_l}\iint_{\Tilde{A}_k} \mathbf{D} \cdot \text{d}\mathbf{A} &= \underbrace{\iiint_{\Tilde{V}_l} \rho \text{d}V}_{:= q_l},&l = 1,...,N_{\Tilde{V}}.
 \label{equ:maxwell_grid_gauss_D}
@@
 \end{subequations}
-where $k, l$ are numbering of elements in $(\mathcal{M}, \Tilde{\mathcal{M}})$.
-
-The integral quantities are the unknowns to be solved.
-As is defined in (\ref{equ:maxwell_grid_faraday})-(\ref{equ:maxwell_grid_gauss_D}) by the underbraces, these scalar quantities are stacked into vectors:
+where $k, l$ are numbering the entities in $(\mathcal{M}, \Tilde{\mathcal{M}})$.
+
+The integral quantities are the unknowns of the discrete Maxwell model.
+As is defined in (\ref{equ:maxwell_grid_faraday})-(\ref{equ:maxwell_grid_gauss_D}) by the underbraces, these unknowns are stacked into vectors:
 \begin{equation} \label{equ:fit_scale_vector}
-    \mathbf{e} := (e_k)_{k=1}^{N_L},\ \ \mathbf{b} := (b_k)_{k=1}^{N_A}, \ \ \mathbf{h} := (h_k)_{k=1}^{N_{\Tilde{L}}}, \ \ \mathbf{d} := (d_k)_{k=1}^{N_{\Tilde{A}}}, \ \ \mathbf{j} := (j_k)_{k=1}^{N_{\Tilde{A}}}, \ \ \mathbf{q} := (q_k)_{i=k}^{N_{\Tilde{V}}}.
+    \mathbf{e} := \{e_k\}_{k=1}^{N_L},\ \ \mathbf{b} := \{b_k\}_{k=1}^{N_A}, \ \ \mathbf{h} := \{h_k\}_{k=1}^{N_{\Tilde{L}}}, \ \ \mathbf{d} := \{d_k\}_{k=1}^{N_{\Tilde{A}}}, \ \ \mathbf{j} := \{j_k\}_{k=1}^{N_{\Tilde{A}}}, \ \ \mathbf{q} := \{q_k\}_{i=k}^{N_{\Tilde{V}}}.
 \end{equation}
@@
 \begin{remark}
-    In an implementation, it is always convenient to index a pair of corresponding primal and dual elements with the same number.
+    In an implementation, it is always convenient to index a pair of corresponding primal and dual entities with the same number.
 For instance, a primal face $A_k$ is penetrated by the dual edge $\Tilde{L}_k$.
@@
 
-The material laws (\ref{equ:material_law}) need to be reformulated within this framework.
-The relations between scalar vectors, in the form of $\mathbf{b} = \mathbb{M}_\mu \mathbf{h}$ and $\mathbf{d} = \mathbb{M}_\varepsilon \mathbf{e}$, are to be derived.
-When permittivity $\mu$ and permeability $\varepsilon$ are homogeneous in the domain and the orthogonality of the pair ($\mathcal{M}, \Tilde{\mathcal{M}}$) holds, the discrete material laws involve diagonal matrices with entries
+The material laws (\ref{equ:material_law}) need to be taken into account within this framework, that is, relations $\mathbf{b} = \mathbb{M}_\mu \mathbf{h}$ and $\mathbf{d} = \mathbb{M}_\epsilon \mathbf{e}$ with suitable \emph{material} matrices $\mathbb{M}_\mu, \mathbb{M}_\epsilon$.
+When permittivity $\mu$ and permeability $\epsilon$ are homogeneous in the domain and the orthogonality of the pair ($\mathcal{M}, \Tilde{\mathcal{M}}$) holds, the discrete material laws involve diagonal matrices with entries
 
 \begin{equation*}
-    (\mathbb{M}_\mu)_{k,k} = \frac{\mu|A_k|}{|\Tilde{L}_k|}, \ \ \ \ \ (\mathbb{M}_\varepsilon)_{k,k} = \frac{\varepsilon |\Tilde{A}_k|}{|L_k|},
+    (\mathbb{M}_\mu)_{k,k} = \frac{\mu|A_k|}{|\Tilde{L}_k|}, \ \ \ \ \ (\mathbb{M}_\epsilon)_{k,k} = \frac{\epsilon |\Tilde{A}_k|}{|L_k|},
 \end{equation*}
 where $|\cdot|$ denotes taking length or area.
-We would like to remark that the approximation error is introduced due to the implicit assumption that vector fields are piecewise constant, see the analysis in \cite{Marrone_2001}.
+We would like to remark that the approximation error is introduced due to the implicit assumption that vector fields are piecewise constant, see the analysis in \cite[][sec.
+3.2]{Marrone_2001}.
 
@@
     \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \\
-    \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= -\mathbf{J}, \\
+    \lambda^2\partial_t \mathbf{D} - \nabla \times \mathbf{H} &= -\mathbf{J}, \\
     \nabla \cdot \mathbf{B} &= 0,  \\
-    \nabla \cdot \mathbf{D} &= \rho, \\
+    \lambda^2\nabla \cdot \mathbf{D} &= \rho, \\
     \mathbf{H} &= \mu^{-1} \mathbf{B}, \\
-    \mathbf{D} &= \varepsilon \mathbf{E}. 
+    \mathbf{D} &= \epsilon \mathbf{E}. 
 \end{align*}
@@
     \dot{\mathbf{b}} + \mathbb{C}\mathbf{e} &= \mathbf{0} , \label{equ:alg_faraday}\\
-    \dot{\mathbf{d}} - \Tilde{\mathbb{C}}\mathbf{h} &= - \mathbf{j}, \label{equ:alg_empere}\\
+    \lambda^2\dot{\mathbf{d}} - \Tilde{\mathbb{C}}\mathbf{h} &= - \mathbf{j}, \label{equ:alg_empere}\\
     \mathbb{D}\mathbf{b} &= \mathbf{0},  \label{equ:alg_gauss_b}\\
-    \Tilde{\mathbb{D}}\mathbf{d} &= \mathbf{q},  \label{equ:alg_gauss_d}\\
+    \lambda^2\Tilde{\mathbb{D}}\mathbf{d} &= \mathbf{q},  \label{equ:alg_gauss_d}\\
     \mathbf{h} &= \mathbb{M}_\mu^{-1} \mathbf{b}, \label{equ:alg_material_magnetic}\\
-    \mathbf{d} &= \mathbb{M}_{\varepsilon} \mathbf{e}, \label{equ:alg_material_electric} 
+    \mathbf{d} &= \mathbb{M}_{\epsilon} \mathbf{e}, \label{equ:alg_material_electric} 
 \end{align}
@@
 \end{center}
-where the topping dot $\cdot$ stands for taking the time derivative.
-
-At this point, we would like to emphasize the importance of the primal-dual staggered meshes: the material laws can be included in a rather simple way.
-For magnetic Gauss's law $\mathbf{D} = \varepsilon \mathbf{E}$, for instance, the $\mathbf{D}$-field is represented by a collection of face integrals $ (d_k)_{k}$ while $\mathbf{E}$-field is represented by a collection of edge integrals $ (e_k)_{k}$.
-The primal-dual meshes allow us to arrange them in a staggered way -- edges penetrate faces -- such that $\mathbf{D} = \varepsilon \mathbf{E}$ can be approximated by $\mathbf{d} = \mathbb{M}_{\varepsilon}\mathbf{e}$ in a local fashion, i.e.
-$\mathbb{M}_{\varepsilon}$ is diagonal.
-A more schematic illustration involves the language of differential forms and discrete Hodge operators, see \cite{bossavit1999, teixeira_1999, hip_1999}.
-
-This transformation does not introduce approximations \emph{except for} the discrete material laws. The essence of FIT lies in that the complexity of continuous electric and magnetic field quantities
-is reduced to a finite number of well-defined discrete unknowns \citep{weiland_2003}.
-Also, this discrete version of Maxwell's equations (\ref{equ:alg_faraday})-(\ref{equ:alg_material_electric}) are topological in the sense that they are invariant under different coordinate systems.
+where the dot above variables stands for the time derivative.
+
+At this point, we would like to emphasize the importance of the primal-dual staggered meshes: \emph{the material laws can be included in a rather simple way.} For Gauss's law $\mathbf{D} = \epsilon \mathbf{E}$, for instance, the $\mathbf{D}$-field is represented by a collection of face integrals $ \{d_k\}_{k}$ while the $\mathbf{E}$-field is represented by a collection of edge integrals $ \{e_k\}_{k}$.
+The primal-dual meshes allow us to arrange them in a staggered way -- edges penetrate faces -- such that $\mathbf{D} = \epsilon \mathbf{E}$ can be approximated by $\mathbf{d} = \mathbb{M}_{\epsilon}\mathbf{e}$ in a local fashion, i.e.
+$\mathbb{M}_{\epsilon}$ is diagonal.
+A more schematic illustration relies on the language of discrete exterior calculus (DEC), see \cite{bossavit1999, teixeira_1999, hip_1999}.
+
+The essence of FIT lies in: (i) The discrete Maxwell model (\ref{equ:alg_faraday})-(\ref{equ:alg_gauss_d}) are topological in the sense that they are invariant under different coordinate systems.
+Only the discrete material laws (\ref{equ:alg_material_magnetic})(\ref{equ:alg_material_magnetic}) depend on the geometric information.
+(ii) The discrete Maxwell model (\ref{equ:alg_faraday})-(\ref{equ:alg_gauss_d}) is free of approximation error, that is, it holds for analytical solutions.
+The consistency error is only introduced by the discrete material laws (\ref{equ:alg_material_magnetic})(\ref{equ:alg_material_magnetic}).
 
@@
 The electromagnetic boundary $\Gamma_C, \Gamma_I$ is resolved by the primal mesh $\mathcal{M}$.
-As is mentioned in Section \ref{sec:BC}, a boundary scalar potential $\varphi$ can be introduced due to the vanishing surface curl of $\mathbf{E}$-field.
-It holds in the discrete level as well.
+As is mentioned in Section \ref{sec:BC}, the zero magnetic flux $\mathbf{B}\cdot \mathbf{n}$ is equivalent to $\nabla\times\mathbf{E} \cdot \mathbf{n} = 0$, which allows a boundary scalar potential $\varphi$ such that the tangential component $\mathbf{E}_t$ of the $\mathbf{E}$-field is equal to $\nabla_\Gamma\varphi$.
+It holds on the discrete level as well.
 We associate each primal vertex $P_k \in \partial\Omega$ with a scalar value $\varphi_k$.
@@
     \begin{align*}
-    \text{curl} \mathbf{E} \cdot \mathbf{n} = 0\ \ &\text{on} \ \  \Gamma_I,  \\
-    \text{curl} \mathbf{H} \cdot \mathbf{n} = 0\ \  &\text{on} \ \  \Gamma_I, \\
-    \varphi = \varphi^\pm(t)\ \ &\text{on} \ \ \Gamma_C^\pm.
+    \mathbf{D} \cdot \mathbf{n} = 0\ \ &\text{on} \ \  \Gamma_I,  \\
+    \mathbf{B} \cdot \mathbf{n} = 0\ \  &\text{on} \ \  \Gamma_I, \\
+    \varphi = \varphi^\pm(t)\ \ &\text{on} \ \ \Gamma_C^\pm,
     \end{align*}
@@
     \end{minipage}
-    \begin{minipage}{0.4\textwidth}
+    \begin{minipage}{0.5\textwidth}
+        \centering
         \begin{subequations}
             \begin{align}
-            e_k = (\mathbb{G}\bm{\varphi})_k,\ \ &\forall k : L_k \subset \partial\Omega, \label{equ:bc_2}\\
-            (\Tilde{\mathbb{C}} \bm{h})_k = 0\ \ &\forall k : \Tilde{A}_k \subset \Gamma_I,\label{equ:bc_3} \\
-            \varphi_k = \varphi^\pm(t), \ \ &\forall k : P_k \subset \Gamma_C^\pm. \label{equ:bc_1}
+            d_k = 0,\ \ &\forall k : \Tilde{A}_k \subset \Gamma_I,\label{equ:bc_3} \\
+            e_k = (\mathbb{GX}_\varphi\bm{\varphi})_k,\ \ &\forall k : L_k \subset \partial\Omega, \label{equ:bc_2}\\
+            \varphi_k = \varphi^\pm(t), \ \ &\forall k : P_k \subset \Gamma_C^\pm, \label{equ:bc_1}
             \end{align}
@@
 \end{center}
-
-\subsubsection{Reformulation} \label{sec:reform_discrete}
+where $\mathbb{X}_\varphi \in \mathbb{R}^{N_P \times N_P^\partial}$ extends $\bm{\varphi}$ to all the primal verices by zero.
+Therefore, the surface gradient $\nabla_\Gamma$ is represented by $\mathbb{GX}_\varphi$.
+
+\subsubsection{Stabilization in $\Omega_N$} \label{sec:reform_discrete}
 In Section \ref{sec:reform_continuous}, we have proposed a stabilization of the Maxwell system in the non-conducting domain $\Omega_N$ by introducing a Lagrange multiplier.
 In the semi-discrete level, the equations to be solved in $\Omega_N$ are
+
+\begin{center}
+    \vspace{-0.5cm}
+    \begin{minipage}{0.3\textwidth}
+    \begin{align*}
+        \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \\ 
+        \lambda^2 \partial_t \mathbf{D} - \nabla \times \mathbf{H} + \colorbox{orange!20}{$\nabla \psi$} &= 0, \\
+        \nabla \cdot \mathbf{D} &= 0. 
+    \end{align*}
+    \end{minipage}
+    \begin{minipage}{0.1\textwidth}
+    \centering
+    \begin{tikzpicture}
+    \draw[thick, -{to}] (0,0) -- node[above]{$(\mathcal{M}, \Tilde{\mathcal{M}})$} (1.5,0);
+    \end{tikzpicture}
+    \end{minipage}
+    \begin{minipage}{0.5\textwidth}
         \begin{subequations}
         \begin{align}
-        \dot{\mathbf{b}} + \mathbb{C}\mathbf{e} &= \mathbf{0} ,\\
-        \dot{\mathbf{d}} - \Tilde{\mathbb{C}}\mathbf{h} + \colorbox{orange!20}{$\mathbb{H} \mathbb{G} \bm{\psi}$}&= \mathbf{0},\\
-        \Tilde{\mathbb{D}}\mathbf{d} &= \mathbf{0} \label{equ:discrete_zero_div}, 
+            [\dot{\mathbf{b}} + \mathbb{C}\mathbf{e} &= \mathbf{0}]_k,\ \ \forall k:A_k \subset \Omega_N,\\
+            [\lambda^2\dot{\mathbf{d}} - \Tilde{\mathbb{C}}\mathbf{h} + \colorbox{orange!20}{$\mathbb{H} \mathbb{G} \mathbb{X}_\psi \bm{\psi}$}&= \mathbf{0}]_k, \ \ \forall k: \Tilde{A}_k \subset \Omega_N \label{equ:discrete_ampere_ins}\\
+            [\Tilde{\mathbb{D}}\mathbf{d} &= \mathbf{0}]_k,\ \ \forall k:\Tilde{V}_k \subset \Omega_N \label{equ:discrete_zero_div}, 
         \end{align} 
     \end{subequations}
-where $\bm{\psi} = (\psi_k)_k$ denotes unknowns assigned to each primal vertex in $\Omega_N$ and the matrix $\mathbb{H}_{k,k} = \frac{|\Tilde{A}_k|}{|L_k|}$ transforms primal edge integrals to dual face fluxes\footnote{$\mathbb{H}$ functions as a discrete Hodge operator.}.
-To incorporate the zero Dirichlet BC, we limit the unknowns $(\psi_k)_{k=1}^{N^{N,\circ}_P}$ to primal vertices in $\Omega_N^\circ$.
-
-\subsubsection{Remark: Balance of Equations and Unknowns}
-
-We can heuristically examine the well-posedness of the (semi-)discrete Maxwell system by checking whether the numbers of unknowns (also called degrees of freedom (D.o.F.)) and equations coincide.
-Before counting, we make a meticulous classification for mesh elements according to their locations and summarize the notation for the sake of clarification (see Tab.
-\ref{tab:def_size_var}).
+    \end{minipage}
+\end{center}
+where $\bm{\psi} := \{\psi_k\}_{k=1}^{N_P^N}$ denotes unknowns assigned to each primal vertex in $\Omega_N$.
+The matrix $\mathbb{X}_\psi \in \mathbb{R}^{N_P \times N_P^{N}}$ extends $\bm{\psi}$ by zero to all the primal vertices, by which the zero Dirichlet boundary condition is incorporated.
+We need the matrix $(\mathbb{H})_{k,k} = {|\Tilde{A}_k|}/{|L_k|}$ to transform primal edge integrals to dual face fluxes since the discrete Amp\`{e}re's law (\ref{equ:discrete_ampere_ins}) is defined on dual faces on $\Omega_N$.
+
+\subsubsection{Numbers of Equations and Unknowns}
+
+We can examine the well-posedness of the (semi-)discrete Maxwell system by checking whether the numbers of unknowns (also called degrees of freedom (D.o.F.)) and equations coincide.
+
+First, we make a meticulous classification for mesh entities according to their locations:
 \begin{center}
@@
     \begin{align*}
-        &\#\  \text{primal cell}\ \  N_V \\
-        &\#\  \text{primal edge}\ \  N_L := \underbrace{N^C_L + N^I_L}_{=N^\partial_L} + N^\circ_L  \\
-        &\#\  \text{primal face}\ \  N_A := \underbrace{N_A^C + N^I_A}_{=N^\partial_A} + N^\circ_A  \\
-        &\#\  \text{primal vertex}\ \  N_P := \underbrace{N_P^C + N^I_P}_{=N^\partial_P} + N^\circ_P
+        &\#\  \text{primal cells}\ \  N_V \\
+        &\#\  \text{primal edges}\ \  N_L := \underbrace{N^C_L + N^I_L}_{=N^\partial_L} + N^\circ_L  \\
+        &\#\  \text{primal faces}\ \  N_A := \underbrace{N_A^C + N^I_A}_{=N^\partial_A} + N^\circ_A  \\
+        &\#\  \text{primal vertices}\ \  N_P := \underbrace{N_P^C + N^I_P}_{=N^\partial_P} + N^\circ_P
     \end{align*}
@@
     \begin{align*}
-        &\#\  \text{dual cell}\ \  N_{\Tilde{V}} := N_P \\
-        &\#\  \text{dual edge}\ \  N_{\Tilde{L}} := \underbrace{N^\partial_{\Tilde{L}}}_{=N^\partial_L} + \underbrace{N^\circ_{\Tilde{L}}}_{=N_A} \\
-        &\#\  \text{dual face}\ \  N_{\Tilde{A}} := \underbrace{N^\partial_{\Tilde{A}}}_{=N^\partial_P} + \underbrace{N^\circ_{\Tilde{A}}}_{=N_L}
+        &\#\  \text{dual cells}\ \  N_{\Tilde{V}} := N_P \\
+        &\#\  \text{dual edges}\ \  N_{\Tilde{L}} := \underbrace{N^\partial_{\Tilde{L}}}_{=N^\partial_L} + \underbrace{N^\circ_{\Tilde{L}}}_{=N_A} \\
+        &\#\  \text{dual faces}\ \  N_{\Tilde{A}} := \underbrace{N^\partial_{\Tilde{A}}}_{=N^\partial_P} + \underbrace{N^\circ_{\Tilde{A}}}_{=N_L}
     \end{align*}
@@
 \end{center}
-
-where the superscript indicates the locations where the elements lie.
-The equations $N^\partial_{\Tilde{L}} = N^\partial_L, N^\partial_{\Tilde{A}} = N^\partial_P$ reveal the bijective relation between the boundary primal elements and auxiliary elements, as can be checked easily by inspecting Fig.
+where the superscript indicates the locations where the entities lie.
+The equations $N^\partial_{\Tilde{L}} = N^\partial_L, N^\partial_{\Tilde{A}} = N^\partial_P$ reveal the bijective relation between the boundary primal entities and auxiliary entities, as can be checked easily by inspecting Fig.
 \ref{fig:illustraion_dual_boundary}.
-
+We also give a summary of the unknowns in Tab. \ref{tab:def_size_var}.
 \begin{table}[]
@@
      \hline
-     D.o.F.  & Meaning  & Size \\
+     Vector of unknowns  & Meaning  & Vector size \\
      \hline
      $\mathbf{e}$ & line integrals of $\mathbf{E}$-field at primal edges $L$& $N_L$ \\
-     $\bm{\varphi}$ & electric potentials at primal vertices $P$ on $\partial\Omega$ & $N_P^\partial$ \\
+     $\bm{\varphi}$ & boundary scalar potential $\varphi$ at primal vertices $P$ on $\partial\Omega$ & $N_P^\partial$ \\
      $\mathbf{b}$ & surface integrals of $\mathbf{B}$-field at primal faces $A$ & $N_A$ \\
@@
      $\mathbf{d}$ & surface integrals of $\mathbf{D}$-field at dual faces $\Tilde{A}$ & $N_{\Tilde{A}}$ \\
-     $\bm{\psi}$ & Lagrange multiplier at primal vertices $P$ in $\Omega_N^\circ$ & $N^{N,\circ}_P$\\ 
+     $\bm{\psi}$ & Lagrange multiplier $\psi$ at primal vertices $P$ in $\Omega_N$ & $N^{N}_P$\\ 
      \hline
 \end{tabular}
-    \caption{Definitions and sizes of all vectors of degrees of freedom.}
+    \caption{Definitions and sizes of the vectors of unknowns.}
     \label{tab:def_size_var}
@@
 \begin{align*}
-    \text{discrete Faraday law (\ref{equ:alg_faraday})} \ \ &\longrightarrow\ \  N_A \ \ \text{equations} \\
-    \text{discrete Ampere law (\ref{equ:alg_empere})} \ \ &\longrightarrow\ \  N_{\Tilde{A}} \ \ \text{equations} \\
+    \text{discrete Faraday's law (\ref{equ:alg_faraday})} \ \ &\longrightarrow\ \  N_A \ \ \text{equations} \\
+    \text{discrete Ampere's law (\ref{equ:alg_empere})} \ \ &\longrightarrow\ \  N_{\Tilde{A}} \ \ \text{equations} \\
     \text{discrete material laws (\ref{equ:alg_material_magnetic})(\ref{equ:alg_material_electric})} \ \ &\longrightarrow\ \  N_A + N_L \ \ \text{equations} \\
@@
     \text{boundary condition (\ref{equ:bc_3})} \ \ &\longrightarrow\ \  N_{\Tilde{A}}^I \ \ \text{equations}. \\
-    \text{vanishing divergence constraint (\ref{equ:discrete_zero_div})} \ \ &\longrightarrow\ \  N_P^{N,\circ} \ \ \text{equations}. \\
+    \text{vanishing divergence constraint (\ref{equ:discrete_zero_div})} \ \ &\longrightarrow\ \  N_{\Tilde{V}}^{N} \ \ \text{equations}. \\
 \end{align*}
-Comparing the numbers of D.o.F in Tab. \ref{tab:def_size_var} and of the equations we collect, we show that they are equal:
+Comparing the numbers of D.o.F in Tab. \ref{tab:def_size_var} and of the equations we collect above, we show that they are equal:
 \begin{align*}
-    \#\text{ of unknowns} &= \colorbox{violet!20}{$N_L$} + \colorbox{blue!20}{$N_A$} + \colorbox{gray!40}{$N_{\Tilde{L}}$} + \colorbox{orange!20}{$N_{\Tilde{A}}$} + \colorbox{green!20}{$N_P^\partial$} + \colorbox{yellow!40}{$N_P^{N,\circ}$}, \\
-    \#\text{ of equations} &= \colorbox{blue!20}{$N_A$} + \colorbox{orange!20}{$N_{\Tilde{A}}$} + \colorbox{gray!40}{$N_A$} + \colorbox{violet!20}{$N_L$} + \colorbox{gray!40}{$N_L^\partial$} + \colorbox{green!20}{$N_P^C + N_P^I$}+ \colorbox{yellow!40}{$N_P^{N,\circ}$},
+    \#\text{ of unknowns} &= \colorbox{violet!20}{$N_L$} + \colorbox{blue!20}{$N_A$} + \colorbox{gray!40}{$N_{\Tilde{L}}$} + \colorbox{orange!20}{$N_{\Tilde{A}}$} + \colorbox{green!20}{$N_P^\partial$} + \colorbox{yellow!40}{$N_P^{N}$}, \\
+    \#\text{ of equations} &= \colorbox{blue!20}{$N_A$} + \colorbox{orange!20}{$N_{\Tilde{A}}$} + \colorbox{gray!40}{$N_A+N_L^\partial$} + \colorbox{violet!20}{$N_L$} + \colorbox{green!20}{$N_P^C + N_P^I$}+ \colorbox{yellow!40}{$N_{\Tilde{V}}^N$},
 \end{align*}
@@
 
-However, the matching of numbers of unknowns and equations does not necessarily result in a valid linear system since the equations might be linearly dependent.
-We will see later in Section \ref{sec:inapp_bc} that inappropriate BCs could cause the singularity of the linear system as $\lambda \rightarrow 0$.
-
-\subsection{Discrete Euler Equations}
-We employ the finite volume method (FVM) to discretize the Euler system.
-As a classical framework for solving conservation laws and hyperbolic systems, FVM is derived from the integral form of the equations in each cell.
-It is the cell average of quantities that evolves at each time step, based on the \emph{numerical flux} through the cell boundary.
-The construction of the numerical flux, which serves to approximate the real flux, is the essence of constructing FVM schemes.
-Due to the convection nature of fluid dynamics, the numerical fluxes are supposed to respect the convection direction, that is, an \emph{upwind scheme} is preferable.
-To this end, people resort to the approximated solution of \emph{Riemann problems}.
-The method is briefly illustrated in the following.
-For detailed information, see the textbook \cite{leveque_2002}.
-
-The Euler equations (\ref{equ:euler_}) can be generalized into the form of conservation law with source terms:
+Of course, the matching numbers of unknowns and equations do not necessarily result in a valid linear system, since the equations might be linearly dependent.
+In fact, the linear system will be singular without the stabilization proposed in the previous section when $\lambda = 0$.
+
+\subsection{Discrete Euler Equations} \label{sec:discrete_euler}
+We employ the finite volume method (FVM) to discretize the Euler system. The Euler equations (\ref{equ:euler_}) can be cast into the form of conservation law with source terms:
 \begin{equation} \label{equ:euler_conservation}
@@
 \end{equation}
-where $\mathbf{U} \in L^2(\Omega \times [0,T], \mathbb{R}^m)$ stands for $m$ conservative variables, $\mathbf{f}(\mathbf{U}) \in L^2(\Omega \times  [0,T], \mathbb{R}^m)$ is the flux density, and $\mathbf{RHS} \in L^2(\Omega \times  [0,T], \mathbb{R}^m)$ is the source term.
-
-To obtain the semi-discretization, we first integrate (\ref{equ:euler_conservation}) over a cell $V_i$ 
+where $\mathbf{U} \in L^2(\Omega \times [0,T], \mathbb{R}^m)$ stands for $m$ conservative variables.
+In the case of the full 3D Euler equations (\ref{equ:euler_rescaled}), $m = 5$ and $\mathbf{U} := [n, n\mathbf{u}, ne]$.
+$\mathbf{f}(\mathbf{U}) \in L^2(\Omega \times  [0,T], \mathbb{R}^{3 \times m})$ is the flux function.
+$\mathbf{RHS} \in L^2(\Omega \times  [0,T], \mathbb{R}^m)$ is the source term.
+
+To obtain the semi-discretization, we first integrate (\ref{equ:euler_conservation}) over a \emph{dual} cell $\Tilde{V}_i \in \Omega_P$
 \begin{equation} \label{equ:euler_grid} 
-    \dot{\overline{\mathbf{U}}}_k + \frac{1}{|V_k|}\sum_{l:A_l\in\partial V_k} |A_l|\underbrace{\frac{1}{|A_l|}\iint_{A_l}\mathbf{f}(\mathbf{U})\cdot \mathbf{n}_l \text{d}A}_{:= \overline{\mathbf{f}}_l \approx \mathbf{f}^\text{num}_l} = \underbrace{\frac{1}{|V_k|}\iiint_{V_k} \mathbf{RHS} \text{d}V}_{:= \overline{\mathbf{RHS}}_k}
+    \dot{\overline{\mathbf{U}}}_k + \frac{1}{|\Tilde{V}_k|}\sum_{l:\Tilde{A}_l\in\partial \Tilde{V}_k} |\Tilde{A}_l|\underbrace{\frac{1}{|\Tilde{A}_l|}\iint_{\Tilde{A}_l}\mathbf{f}(\mathbf{U})\cdot \mathbf{n}_l \text{d}A}_{:= \overline{\mathbf{f}}_l \approx \mathbf{f}^\text{num}_l} = \underbrace{\frac{1}{|\Tilde{V}_k|}\iiint_{\Tilde{V}_k} \mathbf{RHS} \text{d}V}_{:= \overline{\mathbf{RHS}}_k},\ \ k = 1,2,\cdots,N_{\Tilde{V}}^P
 \end{equation}
-where $\overline{\mathbf{U}}_k := \iiint_{V_k} \mathbf{U} \text{d}V / |V_k| \in L^2([0,T],\mathbb{R}^m)$ is the cell average of $\mathbf{U}$ and $\mathbf{n}_l$ is the outer normal vector of face $A_l$ with respect to the cell $V_k$.
-We approximate the flux $\overline{\mathbf{f}}_l$ in (\ref{equ:euler_grid}) by a numerical flux $\mathbf{f}^\text{num}_l := \mathbf{f}^\text{num}\left(\overline{\mathbf{U}}_k, \overline{\mathbf{U}}_{\hat{k}(k,l)}, \mathbf{n}_l\right)$, where $\hat{k}(k,l)$ returns the index of the adjacent cell that shares $A_l$ with cell $V_k$.
-Classical numerical fluxes include Lax-Friedrich flux, Rusanov flux, and Engquist-Osher flux, see \cite[][p.
+where $\overline{\mathbf{U}}_k := \iiint_{\Tilde{V}_k} \mathbf{U} \text{d}V / |\Tilde{V}_k| \in L^2([0,T],\mathbb{R}^m)$ is the cell average of $\mathbf{U}$ and $\mathbf{n}_l$ is the outer normal vector of face $\Tilde{A}_l$ with respect to the cell $\Tilde{V}_k$.
+In FVM, the flux $\overline{\mathbf{f}}_l$ in (\ref{equ:euler_grid}) is approximated by a numerical flux $\mathbf{f}^\text{num}_l := \mathbf{f}^\text{num}\left(\overline{\mathbf{U}}_k, \overline{\mathbf{U}}_{\hat{k}(k,l)}, \mathbf{n}_l\right)$, where $\hat{k}(k,l)$ returns the index of the adjacent dual cell that shares $\Tilde{A}_l$ with cell $\Tilde{V}_k$.
+Classical numerical fluxes include Lax-Friedrich flux, Rusanov flux, and Engquist-Osher flux, see \cite[][pp.
 44-46]{mishra_2019}.
-Finally, we end up with the semi-discretized equation:
+We end up with the semi-discretized equation:
 \begin{equation}
-    \dot{\overline{\mathbf{U}}}_k + \frac{1}{|V_k|}\sum_{l:A_l\in\partial V_k} |A_l| \mathbf{f}^\text{num}\left(\overline{\mathbf{U}}_k, \overline{\mathbf{U}}_{\hat{k}(k,l)}, \mathbf{n}_l\right) = \overline{\mathbf{RHS}}_k.
+    \dot{\overline{\mathbf{U}}}_k + \frac{1}{|V_k|}\sum_{l:\Tilde{A}_l\in\partial \Tilde{V}_k} |\Tilde{A}_l| \mathbf{f}^\text{num}\left(\overline{\mathbf{U}}_k, \overline{\mathbf{U}}_{\hat{k}(k,l)}, \mathbf{n}_l\right) = \overline{\mathbf{RHS}}_k,\ \  k = 1,2,\cdots,N_{\Tilde{V}}^P.
     \label{equ:fvm}
 \end{equation}
-The Rusanov flux in multi-dimensions on face $A_l$ writes
+We employ the Rusanov flux, which writes
 \begin{equation} \label{equ:rusanov-flux-3d}
@@
 \end{equation}
-where $\overline{s} = \text{max}(s(\overline{\mathbf{U}}_L), s(\overline{\mathbf{U}}_R))$ with $s(\mathbf{U}) := |\mathbf{u}\cdot\mathbf{n}| + \sqrt{\gamma p/\rho}$ representing the largest wave speed.
-
-We would like to emphasize that the Euler system is discretized on $\Tilde{\mathcal{M}}$ due to the fact that (i) the electric current is connected to the momenta of charged particles by (\ref{equ:maxwell_euler_coupling}); (ii) the electric current is discretized on dual faces by (\ref{equ:maxwell_grid_ampere}).
-
-To rewrite (\ref{equ:fvm}) into a matrix form, by abuse of notation we stack all the cell average $(\overline{\mathbf{U}}_k)_k$ into a matrix $\mathbf{U} \in \mathbb{R}^{N_{\Tilde{V}}^P \times m}$ with $\mathbf{U}_{k,:} = \overline{\mathbf{U}}_k$.
-Meanwhile, we denote by $\mathbf{F} \in \mathbb{R}^{N_{\Tilde{A}}^P \times m}$ the collection of the (total) numerical fluxes, i.e.
-$\mathbf{F}_{k,:} = \mathbf{f}^\text{num}_k$.
-In the same way, we denote by $\mathbf{RHS}\in \mathbb{R}^{N_{\Tilde{V}}^P \times m}$ the collection of $\overline{\mathbf{RHS}}_k$.
-Besides, we define the diagonal matrix $\mathbb{\Tilde{V}} \in \mathbb{R}^{N_{\Tilde{V}}^P \times N_{\Tilde{V}}^P}$ and $\mathbb{\Tilde{A}}\in \mathbb{R}^{N_{\Tilde{A}}^P \times N_{\Tilde{A}}^P}$ with $\mathbb{\Tilde{A}}_{k,k} = |\Tilde{A}_k|$.
+where $\overline{s} = \text{max}\{s(\overline{\mathbf{U}}_L), s(\overline{\mathbf{U}}_R)\}$ with $s(\mathbf{U}) := |\mathbf{u}\cdot\mathbf{n}| + \sqrt{\gamma p/\rho}$ representing the largest wave speed.
+
+At this stage, we would like to discuss why the Euler system should be discretized on $\Tilde{\mathcal{M}}$.
+As is shown in the integrated Amp\`{e}re's law (\ref{equ:maxwell_int_ampere}), the electric currents are defined on dual faces $\Tilde{A}$.
+By solving the Euler equations on $\Tilde{\mathcal{M}}$, we have the mass flux on dual faces $\Tilde{A}$ as well.
+In this way, the connection between the charge conservation (\ref{equ:charge_continuity}) and the mass conservation (the 1st equation in \ref{equ:euler_}) due to the current-momentum coupling (\ref{equ:maxwell_euler_coupling}) is preserved on the discrete level.
+
+For the sake of presentation, we rewrite (\ref{equ:fvm}) into a matrix form.
+By abuse of notation, we stack all the cell average $\{\overline{\mathbf{U}}_k\}_{k=1}^{N^P_{\Tilde{V}}}$ into a matrix $\mathbf{U} \in \mathbb{R}^{N_{\Tilde{V}}^P \times 5}$ with $\mathbf{U}_{k,:} = \overline{\mathbf{U}}_k$.
+Further, we denote by $\mathbf{F} \in \mathbb{R}^{N_{\Tilde{A}}^P \times 5}$ the collection of the (total) numerical fluxes, i.e.
+$\mathbf{F}_{k,:} = \mathbf{f}^\text{num}_k = [f^\text{mass}_k, \bm{f}^\text{mom}_k, f^\text{ene}_k]$.
+In the same way, we denote by $\mathbf{RHS}\in \mathbb{R}^{N_{\Tilde{V}}^P \times 5}$ the collection of $\overline{\mathbf{RHS}}_k$.
+Besides, we define the diagonal matrix $\mathbb{\Tilde{V}} \in \mathbb{R}^{N_{\Tilde{V}}^P \times N_{\Tilde{V}}^P}$ and $\mathbb{\Tilde{A}}\in \mathbb{R}^{N_{\Tilde{A}}^P \times N_{\Tilde{A}}^P}$ with $(\mathbb{\Tilde{A}})_{k,k} = |\Tilde{A}_k|$.
 Making use of the incidence matrices, we end up with
-\begin{equation*}
+\begin{equation} \label{equ:euler_matrix_form}
     \dot{\mathbf{U}} + \mathbb{\Tilde{V}}^{-1}\mathbb{\Tilde{D}}\mathbb{\Tilde{A}}\mathbf{F}(\mathbf{U})  = \mathbf{RHS}(\mathbf{U},\mathbf{d},\mathbf{b}),
-\end{equation*}
-where the dependence of $\mathbf{RHS}$ on $\mathbf{d}, \mathbf{b}$ is implied by (\ref{equ:euler_rescaled}) and will be elaborated below.
+\end{equation}
+Recall that $\Tilde{\mathbb{D}}$ represents the discrete divergence of $\Tilde{\mathcal{M}}$.
+Dependence of $\mathbf{RHS}$ on $\mathbf{d}, \mathbf{b}$ is implied by (\ref{equ:euler_rescaled}) and will be elaborated next.
 
@@
 \begin{itemize}
-    \item[-] given the fluxes at faces of a cell, reconstruct the vector field inside the cell;
+    \item[-] given the fluxes at the faces of a cell, reconstruct the vector field inside the cell;
     \item[-] given the integrals along the edges of a cell, reconstruct the vector field inside the cell. 
@@
 \begin{equation*}
-    \mathbf{v} = \argmin_{v\in \mathbb{R}^3} \sum_{k=1}^{N_A}(A_k\mathbf{v} \cdot \mathbf{n}_k - f_k)^2.   
+    \mathbf{v} = \argmin_{\mathbf{w}\in \mathbb{R}^3} \sum_{k=1}^{N_A}(A_k\mathbf{w} \cdot \mathbf{n}_k - f_k)^2.   
 \end{equation*} can be computed through
@@
 \end{equation}
-where $\mathbf{d}, \mathbf{b}$ are stacked unknowns, see Tab.
-\ref{tab:def_size_var}; $\mathbf{E} := (\mathbf{E}_k)_{k=1}^{N_{\Tilde{V}}}$ and $\mathbf{B} := (\mathbf{B}_k)_{k=1}^{N_{\Tilde{V}}}$ are $N_{\Tilde{V}} \times 3$ matrices stacking the reconstructed $\mathbf{E}$-fields and $\mathbf{B}$-fields at each $\Tilde{V}$; $\Tilde{\mathbb{R}}_E$ and $\Tilde{\mathbb{R}}_B$ are thus rank-3 tensors.
+where $\mathbf{d}, \mathbf{b}$ are defined in Tab.
+\ref{tab:def_size_var}; $\mathbf{E} := \{\mathbf{E}_k\}_{k=1}^{N_{\Tilde{V}}}$ and $\mathbf{B} := \{\mathbf{B}_k\}_{k=1}^{N_{\Tilde{V}}}$ are $N_{\Tilde{V}} \times 3$ matrices containing the reconstructed $\mathbf{E}$-fields and $\mathbf{B}$-fields at each $\Tilde{V}$; $\Tilde{\mathbb{R}}_E$ and $\Tilde{\mathbb{R}}_B$ are thus rank-3 tensors.
 
 The problem of the reconstruction of vector fields on unstructured meshes is a widely studied topic.
-Apart from the least-square method, other methods include Perot's method \citep{perot_2000}, finite-element-based methods, etc., which potentially can achieve higher-order accuracy.
+Apart from the least-square method, other methods include Perot's method \citep{perot_2000}, finite-entity-based methods, etc., which potentially can achieve higher-order accuracy.
 See \cite[][sec.
@@
 
+The right-hand-side term in (\ref{equ:euler_matrix_form}) can be computed according to the rescaled Euler equations (\ref{equ:euler_rescaled}) with the reconstructed $\mathbf{E}$-field and $\mathbf{B}$-field by (\ref{equ:reconstruction}) defined in each dual cell.
+
 \subsubsection{Discrete Boundary Conditions}
-The BCs for the Euler system (see Section \ref{sec:BC}) are implemented by the approach of ghost cells \cite[][ch.
+The boundary conditions for the Euler system (see Section \ref{sec:BC}) are implemented by the approach of ghost cells \cite[][ch.
 7]{leveque_2007}, i.e.
@@
 It is equivalent to enforcing the numerical fluxes
-\begin{equation*}
+\begin{equation} \label{equ:discrete_open_bc}
     \mathbf{F}_k = {\mathbf{f}^\text{num}}(\mathbf{U}_l, \mathbf{U}_l, \mathbf{n}_k), \ \ \forall k: \Tilde{A}_k \subset \Gamma_C,
-\end{equation*}
+\end{equation}
 where $l$ refers to the index of the cell adjacent to the boundary face $\Tilde{A}_k$ and is unique.
@@
 Therefore, the numerical fluxes are
-\begin{equation*}
+\begin{equation} \label{equ:discrete_wall_bc}
     \mathbf{F}_k = \mathbf{f}^\text{num}(\mathbf{U}_l, \hat{\mathbf{U}}_l, \mathbf{n}_k), \ \ \forall k: \Tilde{A}_k \subset \Gamma_W,
-\end{equation*}
-where the value of the ghost cell $\hat{\mathbf{U}} = [n, n\mathbf{u} - 2(\mathbf{n}\cdot\mathbf{u})\mathbf{n}, ne]^T$ reverses the normal velocity of $\mathbf{U} = [n, n\mathbf{u}, ne]^T$.
+\end{equation}
+where the value of the ghost cell $\hat{\mathbf{U}}_l = [n, n\mathbf{u} - 2(\mathbf{n}\cdot\mathbf{u})\mathbf{n}, ne]^T$ reverses the normal velocity of $\mathbf{U}_l = [n, n\mathbf{u}, ne]^T$.
 
 \subsection{Summary: Spatially Semi-discrete Model}
-We collect all the equations and BCs presented above and make a summary for the spatially semi-discrete Maxwell-Euler system based on the FIT-FVM framework:
+We collect all the equations and boundary conditions presented above and give a summary for the spatially semi-discrete Maxwell-Euler system based on the FIT-FVM framework:
 \begin{subequations}
 \begin{align}
-        [\dot{\mathbf{b}} + \mathbb{C}\mathbf{e} = \mathbf{0}]_k, \ \ &\forall k: A_k \subset \Omega, \\
-        [\dot{\mathbf{d}} - \Tilde{\mathbb{C}}\mathbf{h} = - \Sigma_{\ast} q_*\bm{f}_{\ast}^{n}]_k, \ \ &\forall k: \Tilde{A}_k \subset \Omega_P,\\
-        [\dot{\mathbf{d}} - \Tilde{\mathbb{C}}\mathbf{h} + \mathbb{H} \mathbb{G} \bm{\psi} = \mathbf{0}]_k, \ \ &\forall k: \Tilde{A}_k \subset \Omega_N,\\
-        [\Tilde{\mathbb{D}}\mathbf{d} = \mathbf{0}]_k,\ \ &\forall k: \Tilde{V}_k \subset \Omega_N, \\
-        [\dot{\mathbf{U}}_\ast + \mathbb{\Tilde{V}}^{-1}\mathbb{\Tilde{D}}\mathbb{\Tilde{A}}\mathbf{F}_\ast = \mathbf{RHS}_\ast]_k,\ \ &\forall k: \Tilde{V}_i \subset \Omega_P, \\
-        [\mathbf{d} = \mathbb{M}_\varepsilon\mathbf{e}]_k,\ \ &\forall k:L_k \subset \Omega,\\
-        [\mathbf{h} = \mathbb{M}_\mu^{-1}\mathbf{b}]_k, \ \ &\forall k:A_k \subset \Omega,
+    (\ref{equ:alg_faraday}) & \implies \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;&  [\dot{\mathbf{b}} + \mathbb{C}\mathbf{e} = \mathbf{0}]_k, \ \ &\forall k: A_k \subset \Omega,  \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \label{equ:faraday_semi_discrete}\\
+    (\ref{equ:alg_empere})  & \implies & [\dot{\mathbf{d}} - \Tilde{\mathbb{C}}\mathbf{h} = - \Sigma_{\ast} q_*\bm{f}_{\ast}^\text{mass}]_k, \ \ &\forall k: \Tilde{A}_k \subset \Omega_P, \label{equ:empere_semi_discrete}\\
+    (\ref{equ:discrete_ampere_ins}) & \implies & [\dot{\mathbf{d}} - \Tilde{\mathbb{C}}\mathbf{h} + \mathbb{H} \mathbb{GX}_\psi \bm{\psi} = \mathbf{0}]_k, \ \ &\forall k: \Tilde{A}_k \subset \Omega_N, \label{equ:ampere_ins_semi_discrete}\\
+    (\ref{equ:discrete_zero_div}) & \implies & [\Tilde{\mathbb{D}}\mathbf{d} = \mathbf{0}]_k,\ \ &\forall k: \Tilde{V}_k \subset \Omega_N, \label{equ:zero_div_ins_semi_discrete}\\
+    (\ref{equ:euler_matrix_form}) & \implies & [\dot{\mathbf{U}}_\ast + \mathbb{\Tilde{V}}^{-1}\mathbb{\Tilde{D}}\mathbb{\Tilde{A}}\mathbf{F}_\ast = \mathbf{RHS}_\ast]_k,\ \ &\forall k: \Tilde{V}_i \subset \Omega_P, \label{equ:euler_semi_discrete} \\
+     (\ref{equ:alg_material_magnetic}) & \implies & [\mathbf{h} = \mathbb{M}_\mu^{-1}\mathbf{b}]_k, \ \ &\forall k:A_k \subset \Omega, \label{equ:material_law_h_semi_discrete}\\
+    (\ref{equ:alg_material_electric}) & \implies & [\mathbf{d} = \mathbb{M}_\epsilon\mathbf{e}]_k,\ \ &\forall k:L_k \subset \Omega \label{equ:material_law_d_semi_discrete},
 \end{align}
-    \begin{comment}
-        \vspace{-1cm}
+where $\ast \in \{e, i, \dots\}$ and $\bm{f}^\text{mass}$ denotes the mass flux which is defined in Section \ref{sec:discrete_euler}.
+By $[\cdots]_k$ we mean taking the $k$-th component of both sides of the equation.
+We have the following boundary conditions:
     \begin{align}
-            \hspace{1.6cm}\mathbf{j}_k =
-            \begin{cases}
-             \Sigma_{\ast} q_*\bm{f}_{\ast,k}^{n},&\forall k: \Tilde{A}_k \subset \Omega_P, \\
-            0,&\forall k: \Tilde{A}_k \subset \Omega_N,
-            \end{cases}
-        \end{align}
-    \end{comment}
-where $\ast \in \{e, i, \dots\}$ and $\bm{f}^n$ denotes the mass flux. By $[\cdots]_k$ we mean taking the $k$-th component of both sides of the equation. We have the following BCs:
-    \begin{align}
-    \varphi_k = \varphi(P_k, t), \ \ &\forall k : P_k \subset \Gamma_C, \\
-    e_k = (\mathbb{G}\bm{\varphi})_k,\ \ &\forall k : L_k \subset \partial\Omega, \\
-    (\Tilde{\mathbb{C}} \bm{h})_k = 0,\ \ &\forall k : \Tilde{A}_k \subset \Gamma_I, \label{equ:bc_zero_curl_h} \\
-    \mathbf{F}_{\ast,k} = \mathbf{f}^\text{num}(\mathbf{U}_{\ast,l}, \mathbf{U}_{\ast,l}, \mathbf{n}_k), \ \ &\forall k: \Tilde{A}_k \subset \Gamma_C, \\
-    \mathbf{F}_{\ast,k} = \mathbf{f}^\text{num}(\mathbf{U}_{\ast,l}, \hat{\mathbf{U}}_{\ast,l}, \mathbf{n}_k), \ \ &\forall k: \Tilde{A}_k \subset \Gamma_W.
+    (\ref{equ:bc_3}) & \implies \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;& d_k = 0,\ \ &\forall k : \Tilde{A}_k \subset \Gamma_I,\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\\
+    (\ref{equ:bc_2}) & \implies & e_k = (\mathbb{GX}_\varphi\bm{\varphi})_k,\ \ &\forall k : L_k \subset \partial\Omega, \\
+    (\ref{equ:bc_1}) & \implies & \varphi_k = \varphi^\pm(t), \ \ &\forall k : P_k \subset \Gamma_C^\pm, \\ 
+    (\ref{equ:discrete_open_bc}) & \implies & \mathbf{F}_{\ast,k} = \mathbf{f}^\text{num}(\mathbf{U}_{\ast,l}, \mathbf{U}_{\ast,l}, \mathbf{n}_k), \ \ &\forall k: \Tilde{A}_k \subset \Gamma_C, \\
+    (\ref{equ:discrete_wall_bc}) & \implies & \mathbf{F}_{\ast,k} = \mathbf{f}^\text{num}(\mathbf{U}_{\ast,l}, \hat{\mathbf{U}}_{\ast,l}, \mathbf{n}_k), \ \ &\forall k: \Tilde{A}_k \subset \Gamma_W.
     \end{align}
 \end{subequations}
+
 We would like to stress again that in our FIT-FVM framework Faraday's law is discretized on $\mathcal{M}$ while Amp\`{e}re's law is discretized on $\Tilde{\mathcal{M}}$ for a simple approximation of material laws.
-By arranging the Euler system on $\Tilde{\mathcal{M}}$, the connection between electric currents and fluid momenta is naturally established in the discrete level since they are defined on the same locations.
+By arranging the Euler system on $\Tilde{\mathcal{M}}$, the connection between electric currents and fluid momenta is naturally established on the discrete level since both are defined on the dual faces.
 
 \section{Full Discretization}
-\subsection{Motivation: Reduction to 1D Discretization}
+\subsection{Motivation: Reduction to One Spatial Dimension}
 Our work is an extension of the 1D scheme proposed in \cite{degond_2012} towards three dimensions.
 Therefore, it is supposed to be compatible with the original 1D scheme when reduced to one dimension.
-This perspective helps to understand how the 3D scheme stems from the 1D one, which is not trivial.
-For the sake of presentation, we discuss their one-fluid model where ions are assumed immobile and only the motion of electrons is considered.
+This perspective helps to understand how the 3D scheme stems from the 1D one.
+For the sake of presentation, we discuss the one-fluid model of \cite{degond_2012} where ions are assumed immobile and only the motion of electrons is considered.
 
 \subsubsection{Projection to One Dimension} \label{sec:projection_to_1d}
-Consider a mesh pair $(\mathcal{M}, \Tilde{\mathcal{M}})$ that are constructed by 2D extrusion along the $z$-axis and are unbounded along transverse directions.
-On assuming the transverse invariance and rotational symmetry, we can ``project'' all the D.o.F.
+Consider a mesh pair $(\mathcal{M}, \Tilde{\mathcal{M}})$ that is constructed by 2D extrusion along the $z$-axis and is unbounded in transverse directions.
+Assuming transverse invariance and rotational symmetry, we can ``project'' all the D.o.F.
 onto the $z$-axis.
@@
     \caption{3D discretization to 1D.
-On the assumption of transverse invariance, we can reduce all the D.o.F.
-lying in the perpendicular plane $z=z_k$ to the vertex at $z=z_k$.
+On the assumption of transverse invariance, we can reduce all the degrees of freedom lying in the perpendicular plane $z=z_k$ to the vertex at $z=z_k$.
 For instance, an edge orthogonal to the $z$-axis is projected to a vertex on the $z$-axis while a parallel edge to the $z$-axis is projected to an edge on the $z$-axis.}
@@
 
-\begin{remark}
-    The 1D reduction of FIT-FVM discretization can be interpreted in the sense of finite difference. 
-\end{remark}
-
-In \cite{degond_2012}, the author investigates a 1D Maxwell-Euler system by assuming vanishing traverse derivatives.
+In \cite{degond_2012}, the authors investigate a 1D Maxwell-Euler system by assuming vanishing traverse derivatives.
 For further simplicity, a transverse mode is considered, i.e.
 $u_y, E_y, B_x$, and $B_z$ are set to zero.
-The 1D reduced one-fluid Maxwell-Euler system and its quasi-neutral limit are
+The 1D reduced component-wise one-fluid Maxwell-Euler system and its quasi-neutral limit are
 
 \vspace{-0.3cm}
-\begin{minipage}{0.6\textwidth}
+\begin{minipage}{0.07\textwidth}
     \begin{align*}
-        \partial_t n + \partial_z(nu_z) &= 0, \\
-        \varepsilon^2[\partial_t(nu_x) + \partial_z(nu_zu_x)] &= - n(E_x - u_zB_y), \\
-        \varepsilon^2[\partial_t(nu_z) + \partial_z(nu_z^2)] + \partial_z(p(n)) &= -n(E_z + u_xB_y), \\
-        \partial_t B_y + \partial_z E_x &= 0, \\
-        \lambda^2 \partial_t E_x + \partial_z B_y &= nu_x, \\
-        \lambda^2 \partial_t E_z &= nu_z, \\
-        \lambda^2 \partial_z E_z &= 1 - n,
+        (\ref{equ:euler_rescaled})&\implies
+        \begin{cases}
+            \\
+            \\
+            \\
+        \end{cases} \\
+        (\ref{equ:maxwell_faraday_rescaled}) &\implies \\
+        (\ref{equ:maxwell_ampere_rescaled})  &\implies 
+        \begin{cases}
+            \\
+            \\
+        \end{cases} \\
+        (\ref{equ:maxwell_gauss_D_rescaled}) & \implies
     \end{align*}    
 \end{minipage}
-$\xrightarrow[]{\lambda \rightarrow 0}$
+\begin{minipage}{0.4\textwidth}
+    \begin{align*}
+        &\partial_t n + \partial_z(nu_z) = 0, \\
+        &\varepsilon^2[\partial_t(nu_x) + \partial_z(nu_zu_x)] = - n(E_x - u_zB_y), \\
+        &\varepsilon^2[\partial_t(nu_z) + \partial_z(nu_z^2)] + \partial_z(p(n)) = -n(E_z + u_xB_y), \\
+        &\partial_t B_y + \partial_z E_x = 0, \\
+        &\lambda^2 \partial_t E_x + \partial_z B_y = nu_x, \\
+        &\lambda^2 \partial_t E_z = nu_z, \\
+        &\lambda^2 \partial_z E_z = 1 - n,
+    \end{align*}
+\end{minipage}
+\hspace{0.5cm}$\xrightarrow[]{\lambda \rightarrow 0}$
 \begin{minipage}{0.3\textwidth}
@@
 \end{minipage}
-where the subscript indicates the direction of the component. An isentropic process with the equation of state $p(n) = n^\gamma$ is assumed.
-
-\subsubsection{1D Fully-discrete Plasma Model} \label{sec:1d_fully_discrete_model}
-The fully-discrete scheme proposed in \cite{degond_2012} is given below.
+where all the fluid variables are attributed to electrons and the subscript indicates the direction of the component.
+An isentropic fluid model with the equation of state $p(n) = n^\gamma$ is assumed to drop the energy equation.
+
+\subsubsection{1D Fully Discrete Plasma Model} \label{sec:1d_fully_discrete_model}
+The fully discrete scheme proposed in \cite{degond_2012} is given below.
 From now on, the superscript of variables involving $m$ indicates the time step.
-The scheme is built on a uniform 1D mesh with cell size $h$ and evolves the system with time step $\delta^m := t^{m+1} - t^m$:
+The scheme is built on a uniform 1D mesh with cell size $h$ and evolves the system with time step size $\delta^m := t^{m+1} - t^m$:
+
+\begin{minipage}{0.1\textwidth}
+\vspace{0.5cm}
     \begin{align*}
-    \frac{n^{m+1}_k - n^m_k}{\delta^m} + \frac{\mycolorbox{orange!30}{f^{n,m+1/2}_{k+1/2} - f^{n,m+1/2}_{k-1/2}}}{h} &= 0, \\
-    \frac{(nu_x)^{m+1}_k - (nu_x)^m_k}{\delta^m} + \frac{f^{u_x,m}_{k+1/2} - f^{u_x,m}_{k-1/2}}{h} &= -\frac{n^m_k \mycolorbox{orange!30}{E^{m+1}_{x,k}}}{\varepsilon^2} + \frac{n^m_k u^m_{z,k}\Tilde{B}^m_{y,k}}{\varepsilon^2},\\
-    \frac{(nu_z)^{m+1}_k - (nu_z)^m_k}{\delta^m} + \frac{f^{u_z,m}_{k+1/2} - f^{u_z,m}_{k-1/2}}{h} &= - \frac{n^m_k \mycolorbox{orange!30}{\Tilde{E}^{m+1}_{z,k}}}{\varepsilon^2} - \frac{n^m_k u^m_{x,k}\Tilde{B}^m_{y,k}}{\varepsilon^2}, \\
+        (\ref{equ:euler_semi_discrete}) &\implies \begin{cases}
+         \\
+         \\
+         \\
+         \\
+         \\
+         \\
+         \\
+        \end{cases} \\
+        (\ref{equ:faraday_semi_discrete}) & \implies \\
+        \\
+        (\ref{equ:empere_semi_discrete}) & \implies \begin{cases}
+        \\ 
+        \\
+        \\
+        \\
+        \end{cases}
+    \end{align*}
+\end{minipage}
+\begin{minipage}{0.6\textwidth}
+\begin{align*}
+    \frac{n^{m+1}_k - n^m_k}{\delta^m} + \frac{\mycolorbox{orange!30}{f^{\text{mass},m+1/2}_{k+1/2} - f^{\text{mass},m+1/2}_{k-1/2}}}{h} &= 0, \\
+    \frac{(nu_x)^{m+1}_k - (nu_x)^m_k}{\delta^m} + \frac{f^{\text{mom}_x,m}_{k+1/2} - f^{\text{mom}_x,m}_{k-1/2}}{h} &= -\frac{n^m_k \mycolorbox{orange!30}{E^{m+1}_{x,k}}}{\varepsilon^2} + \frac{n^m_k u^m_{z,k}\Tilde{B}^m_{y,k}}{\varepsilon^2},\\
+    \frac{(nu_z)^{m+1}_k - (nu_z)^m_k}{\delta^m} + \frac{f^{\text{mom}_z,m}_{k+1/2} - f^{\text{mom}_z,m}_{k-1/2}}{h} &= - \frac{n^m_k \mycolorbox{orange!30}{\Tilde{E}^{m+1}_{z,k}}}{\varepsilon^2} - \frac{n^m_k u^m_{x,k}\Tilde{B}^m_{y,k}}{\varepsilon^2}, \\
    \frac{B^{m+1}_{y,k+1/2} - B^{m}_{y,k+1/2}}{\delta^m} + \frac{\mycolorbox{orange!30}{E^{m+1}_{x,k+1} - E^{m+1}_{x,k}}}{h} &= 0, \\
     \lambda^2 \frac{E^{m+1}_{x,k} - E^{m}_{x,k}}{\delta^m} + \frac{\mycolorbox{orange!30}{B^{m+1}_{y,k+1/2} - B^{m+1}_{y,k-1/2}}}{h} &= \mycolorbox{orange!30}{(nu_x)^{m+1}_k}, \\
-    \lambda^2 \frac{E^{m+1}_{z,k+1/2} - E^{m}_{z,k+1/2}}{\delta^m} &= \mycolorbox{orange!30}{f^{m+1}_{n,k+1/2}}, 
+    \lambda^2 \frac{E^{m+1}_{z,k+1/2} - E^{m}_{z,k+1/2}}{\delta^m} &= \mycolorbox{orange!30}{f^{\text{mass},m+1/2}_{k+1/2}}, 
 \end{align*}
-where 
+\end{minipage}
+
+\noindent where
+
+\hspace{0.3cm}\begin{minipage}{0.1\textwidth}
+    \vspace{0.3cm}
+    (\ref{equ:reconstruction})$\implies$
+\end{minipage}
+\hspace{1cm}
+\begin{minipage}{0.6\textwidth}
 \begin{equation*}
@@
 \end{equation*}    
-are the averaged electromagnetic fields, and the fluxes read
+\end{minipage}
+
+\noindent are the averaged electromagnetic fields, and the fluxes read
+
+\hspace{0.2cm}\begin{minipage}{0.1\textwidth}
     \begin{align*}
-    f^{n,m+1/2}_{k+1/2} & = \frac{1}{2}[\mycolorbox{orange!30}{(nu_z)^{m+1}_k + (nu_z)^{m+1}_{k+1}} + \mu^m_{k+1/2}(n^m_k - n^m_{k+1})], \\
-    f^{u_x,m}_{k+1/2} & = \frac{1}{2}[(nu_zu_x)^{m}_k + (nu_zu_x)^{m}_{k+1} + \mu^m_{k+1/2}((nu_x)^m_k - (nu_x)^m_{k+1})], \\
-    f^{u_z,m}_{k+1/2} & = \frac{1}{2}[(nu_z^2 + p(n)/\varepsilon^2)^{m}_k + (nu_z^2 + p(n)/\varepsilon^2)^{m}_{k+1} + \mu^m_{k+1/2}((nu_z)^m_k - (nu_z)^m_{k+1})].
+        (\ref{equ:rusanov-flux-3d}) &\implies \begin{cases}
+         \\
+         \\
+         \\
+         \\
+         \\
+        \end{cases}
     \end{align*}
+\end{minipage}
+\begin{minipage}{0.6\textwidth}
+    \begin{align*}
+    f^{\text{mass},m+1/2}_{k+1/2} & = \frac{1}{2}[\mycolorbox{orange!30}{(nu_z)^{m+1}_k + (nu_z)^{m+1}_{k+1}} + \mu^m_{k+1/2}(n^m_k - n^m_{k+1})], \\
+    f^{\text{mom}_x,m}_{k+1/2} & = \frac{1}{2}[(nu_zu_x)^{m}_k + (nu_zu_x)^{m}_{k+1} + \mu^m_{k+1/2}((nu_x)^m_k - (nu_x)^m_{k+1})], \\
+    f^{\text{mom}_z,m}_{k+1/2} & = \frac{1}{2}[(nu_z^2 + p(n)/\varepsilon^2)^{m}_k + (nu_z^2 + p(n)/\varepsilon^2)^{m}_{k+1} + \mu^m_{k+1/2}((nu_z)^m_k - (nu_z)^m_{k+1})].
+\end{align*}
+\end{minipage}
+
 The implicit terms are highlighted and are all essential to achieve the AP property.
 The implicitness of the electric field in the Lorentz force is shown to be necessary in \cite{fabre_1992} for the Euler-Poisson system.
-In \cite{degond_2012}, based on the linearized stability analysis, the author shows that the full-implicit treatment of the Maxwell equations is essential to the stability in the quasi-neutral limit.
+In \cite{degond_2012}, based on the linearized stability analysis, the author shows that the full-implicit treatment of the Maxwell equations is essential to achieve stability in the quasi-neutral limit.
 Besides, the mass flux in the mass conservation equation and the current in Amp\`{e}re's law has the same level of implicitness to guarantee consistency with Gauss's law.
@@
 \begin{align}
-    \left[\delta_m^{-1} (\mathbf{b}^{m+1} - \mathbf{b}^{m}) + \mathbb{C}\mycolorbox{orange!30}{\mathbf{e}^{m+1}} = \mathbf{0} \right]_k,\ \ &\forall k:A_k \subset \Omega, \label{equ:maxwell_faraday_ap}\\
-    \left[\lambda^2\delta_m^{-1}(\mathbf{d}^{m+1} - \mathbf{d}^m)- \Tilde{\mathbb{C}}\mycolorbox{orange!30}{\mathbf{h}^{m+1}} = - \Sigma_\ast q_\ast \mycolorbox{orange!30}{\bm{f}^{n,m+1}_{\ast}}\right]_k,\ \ &\forall k:\Tilde{A}_k\subset\Omega_P, \label{equ:maxwell_ampere_plasma_ap}\\
-    \left[\lambda^2\delta_m^{-1}(\mathbf{d}^{m+1} - \mathbf{d}^m)- \Tilde{\mathbb{C}}\mycolorbox{orange!30}{\mathbf{h}^{m+1}} + \mathbb{H}\mathbb{G}\mycolorbox{orange!30}{\bm{\psi}^{m+1}} = \mathbf{0} \right]_k,\ \ &\forall k:\Tilde{A}_k\subset\Omega_N, \label{equ:maxwell_ampere_nonconducting_ap}\\
-    \left[\mathbb{D}\mycolorbox{orange!30}{\mathbf{d}^{m+1}} = \mathbf{0}\right]_k, \ \ &\forall k : \Tilde{V}_k \subset \Omega_N, \label{equ:gauss_nonconducting_ap} \\
-    \left[\delta_m^{-1}(\mathbf{U}_{*}^{m+1} - \mathbf{U}_{*}^{m}) + \mathbb{\Tilde{V}}^{-1}\mathbb{\Tilde{D}}\mathbb{\Tilde{A}}\mycolorbox{orange!30}{\mathbf{F}_\ast^{m+1/2}} = \mycolorbox{orange!30}{\mathbf{RHS}_\ast^{m+1/2}} \right]_k,\ \ &\forall k : \Tilde{V}_k \subset \Omega_P, \label{equ:euler_ap}
+    (\ref{equ:faraday_semi_discrete}) &\implies \;\;\;\;\;\;\;\;\;\;\;\;\;\; &
+    \left[\delta_m^{-1} (\mathbf{b}^{m+1} - \mathbf{b}^{m}) + \mathbb{C}\mycolorbox{orange!30}{\mathbf{e}^{m+1}} = \mathbf{0} \right]_k,\ \ &\forall k:A_k \subset \Omega, \;\;\;\;\;\;\;\;\;\;\;\label{equ:maxwell_faraday_ap}\\
+    (\ref{equ:empere_semi_discrete}) &\implies &
+    \left[\lambda^2\delta_m^{-1}(\mathbf{d}^{m+1} - \mathbf{d}^m)- \Tilde{\mathbb{C}}\mycolorbox{orange!30}{\mathbf{h}^{m+1}} = - \Sigma_\ast q_\ast \mycolorbox{orange!30}{\bm{f}^{\text{mass},m+1/2}_{\ast}}\right]_k,\ \ &\forall k:\Tilde{A}_k\subset\Omega_P, \label{equ:maxwell_ampere_plasma_ap}\\
+    (\ref{equ:ampere_ins_semi_discrete}) &\implies &
+    \left[\lambda^2\delta_m^{-1}(\mathbf{d}^{m+1} - \mathbf{d}^m)- \Tilde{\mathbb{C}}\mycolorbox{orange!30}{\mathbf{h}^{m+1}} + \mathbb{H}\mathbb{GX}_\psi\mycolorbox{orange!30}{\bm{\psi}^{m+1}} = \mathbf{0} \right]_k,\ \ &\forall k:\Tilde{A}_k\subset\Omega_N, \label{equ:maxwell_ampere_nonconducting_ap}\\
+    (\ref{equ:zero_div_ins_semi_discrete}) &\implies &
+    \left[\Tilde{\mathbb{D}}\mycolorbox{orange!30}{\mathbf{d}^{m+1}} = \mathbf{0}\right]_k, \ \ &\forall k : \Tilde{V}_k \subset \Omega_N, \label{equ:gauss_nonconducting_ap} \\
+    (\ref{equ:euler_semi_discrete}) &\implies &
+    \left[\delta_m^{-1}(\mathbf{U}_{*}^{m+1} - \mathbf{U}_{*}^{m}) + \mathbb{\Tilde{V}}^{-1}\mathbb{\Tilde{D}}\mathbb{\Tilde{A}}\mycolorbox{orange!30}{\mathbf{F}_\ast^{m+1/2}} = \mycolorbox{orange!30}{\mathbf{RHS}_\ast^{m+1/2}} \right]_k,\ \ &\forall k : \Tilde{V}_k \subset \Omega_P, \label{equ:euler_ap}\\
+    (\ref{equ:material_law_h_semi_discrete}) &\implies &
+    [\mathbf{h}^{m+1} = \mathbb{M}_\mu^{-1}\mathbf{b}^{m+1}]_k, \ \ &\forall k:A_k \subset \Omega, \label{equ:material_law_h_ap}\\
+    (\ref{equ:material_law_d_semi_discrete}) &\implies &
+    [\mathbf{d}^{m+1} = \mathbb{M}_\epsilon\mathbf{e}^{m+1}]_k,\ \ &\forall k:L_k \subset \Omega \label{equ:material_law_d_ap},
 \end{align}
@@
     \begin{pmatrix}
-    f^{n,m+1} \\
-    \bm{f}^{u,m} \\
-    f^{e,m}
+    f^{\text{mass},m+1/2} \\
+    \bm{f}^{\text{mom},m} \\
+    f^{\text{ene},m}
     \end{pmatrix}_{\ast,k}
@@
 In Rusanov flux (\ref{equ:flux_ap}), we denote by $u_\perp$ the normal component velocity with respect to the dual face $\Tilde{A}_k$.
-We restrain the illustration of the collision term (\ref{equ:R_coll_ap}) (\ref{equ:Q_coll_ap}) to the two-species case for the sake of simplicity.
+We confine the illustration of the collision term (\ref{equ:R_coll_ap}) (\ref{equ:Q_coll_ap}) to the two-species case for the sake of simplicity.
 
@@
 
-\subsubsection{Inappropriate Boundary Condition} \label{sec:inapp_bc}
-We would like to point out that the boundary condition (\ref{equ:bc_zero_curl_h}) is not valid in the quasi-neutral limit, which is revealed by taking the limit of Amp\`{e}re's law in the non-conducting region (\ref{equ:maxwell_ampere_nonconducting_ap}).
-Since $\bm{\psi}^{m+1}$ can be shown to be zero by multiplying (\ref{equ:gauss_nonconducting_ap}) by $\mathbb{D}$, we obtain that
-\begin{equation*}
-    [\Tilde{\mathbb{C}}\mathbf{h}^{m+1} = 0]_k, \ \ \forall k : \Tilde{A}_k \subset \Omega_N,
-\end{equation*}
-which makes the boundary condition (\ref{equ:bc_zero_curl_h}) an over-determined condition. We propose to replace (\ref{equ:bc_zero_curl_h}) by 
-\begin{equation*}
-    [\mathbf{d}^{m+1} = 0]_k, \ \ \forall k : \Tilde{A}_k \subset \Omega_N.
-\end{equation*}
-One can easily check its equivalence to (\ref{equ:bc_zero_curl_h}) when $\lambda = \mathcal{O}(1)$.
-In fact, without this condition the Maxwell system in the non-conducting region is not well-posed when $\lambda = 0$ \cite{alfredo_2003}.
-
-\subsubsection{CFL Condition}
-It has been shown in \cite{degond_2012} that the stability-induced constraint on the time-step size does not depend on the value of $\lambda$ thanks to the implicitness in the discrete Maxwell system.
-However, the Euler system is discretized by an explicit scheme and thus is still subject to a CFL condition.
-
-In our case, we have a conservation law with source terms. Let us consider the model equation
-\begin{equation*}
-    \partial_tu + c\partial_xu = \beta u, 
-\end{equation*}
-where $c>0$ and $\beta<0$ are constant. By a first-order upwind scheme
-\begin{equation*}
-    \delta_t^{-1}(u^{m+1}_k - u^m_k) + c\delta_x^{-1}(u^m_k - u^m_{k-1}) = \beta u^m_k,
-\end{equation*}
-we can perform Neumann analysis and deduce the CFL condition
-\begin{equation*}
-    \delta_t \leq \left[\frac{c}{\delta_x} + \frac{\beta}{2}\right]^{-1}.
-\end{equation*}
-On noticing the source term $\varepsilon_*^{-2}q_*(n\mathbf{u})^m_*\times\mathbf{B}^m$ in the momentum equation, we heuristically take the following restriction
-\begin{equation*}
-    \delta_t^m \leq \min_*\bigg\{\left[\frac{s^m_*}{\delta_x} + \frac{\varepsilon^{-2}_*|q_*||\mathbf{B}^m|}{2}\right]^{-1}\bigg\},
-\end{equation*}
-which is proved to be necessary by numerical experiments.
-
-\subsubsection{Procedure of Time-stepping}
+\todo{Theorem: 1d projection to 1d discrete model?}
+
+\begin{remark}
+    The AP scheme aims to remove the $\lambda$-dependence of the stability constraint on the time step size.
+Yet time-stepping of the discrete Euler system is still subject to the CFL condition due to its explicitness.
+\end{remark}
+
+\subsubsection{Linearly Semi-implicit Time-stepping}
 The semi-implicit scheme (\ref{equ:maxwell_faraday_ap})-(\ref{equ:Q_coll_ap}) entails solving a linear system for each time step.
-We would like to provide a brief guide on how to build such a linear system and evolve the system.
-
-The main step is to establish the connection between the mass fluxes $\mathbf{f}^{n,m+1}_*$ and discrete electric induction $\mathbf{d}$.
-From the momentum conservative equation, one can get the relation between the momenta $n\mathbf{u}^{m+1}_*$ and the reconstructed electric field $\mathbf{E}^{m+1}$.
-Given the reconstruction relation (\ref{equ:reconstruction}), we can get the following relation
-\begin{equation*}
+Despite the complexity of the whole scheme, we will illuminate the procedure of time-stepping.
+
+\noindent \textbf{Step 1.} We establish the connection between $\mathbf{f}^{\text{mass},m+1/2}_*$ and $\mathbf{d}$ through the momentum equation (see (\ref{equ:euler_ap})(\ref{equ:flux_ap})(\ref{equ:rhs_ap})).
+Relying on the reconstruction (\ref{equ:reconstruction}), the following formula can be achieved
+\begin{equation} \label{equ:relation_nu_and_d}
     (n\mathbf{u})_*^{m+1} = \hat{\mathbb{M}}^m_* \mathbf{d}^{m+1} + \bm{\eta}_*^m. 
-\end{equation*}
-Next, by the formula for the mass fluxes in (\ref{equ:flux_ap}), the expression for the currents in $\Omega_P$ (see (\ref{equ:maxwell_ampere_plasma_ap})) is written by 
+\end{equation}
+The expression for the current $\mathbf{J}^{m+1}$ in $\Omega_P$ (see (\ref{equ:maxwell_ampere_plasma_ap})) depends on the mass flux $\bm{f}^{\text{mass},{m+1}}_*$ which then relies on $(n\mathbf{u})_*^{m+1}$ through (\ref{equ:flux_ap}).
+One can formulate the following relation:
 \begin{equation} \label{equ:discrete_ohm}
@@
 \end{equation}
-The calculation of $\hat{\mathbb{M}}_*^m, \bm{\eta}_*^m, \mathbb{M}_\sigma^m, \mathbf{j}^m_{\text{aux}}$ is slightly lengthy but straightforward, so we omit the details.
-
-The discrete Maxwell system (\ref{equ:maxwell_faraday_ap})-(\ref{equ:gauss_nonconducting_ap}) is closed provided (\ref{equ:discrete_ohm}) and can be evolved by solving a linear system.
-The Euler system (\ref{equ:euler_ap}) afterward evolves explicitly.
+where $\mathbb{M}^m_\sigma \in \mathbb{R}^{N_{\Tilde{A}} \times N_{\Tilde{A}}}$ and $\mathbf{j}^m_{\text{aux}} \in \mathbb{R}^{N_{\Tilde{A}}}$.
+The formulas of $\hat{\mathbb{M}}_*^m, \bm{\eta}_*^m, \mathbb{M}_\sigma^m, \mathbf{j}^m_{\text{aux}}$ are slightly lengthy but straightforward, so we omit the details.
+
+\noindent \textbf{Step 2.} Provided (\ref{equ:discrete_ohm}), the discrete Maxwell system (\ref{equ:maxwell_faraday_ap})-(\ref{equ:gauss_nonconducting_ap}) is closed and can be evolved by solving a linear system.
+
+\noindent \textbf{Step 3.} With the updated $\mathbf{d}^{m+1}$, update the momenta $(n\mathbf{u})^{m+1}_*$ by (\ref{equ:relation_nu_and_d}).
+
+\noindent \textbf{Step 4.} the rest of the Euler system can be updated explicitly.
 
 \begin{remark}
-    The formula (\ref{equ:discrete_ohm}) functions as Ohm's law in the discrete level and $\mathbb{M}_\sigma^m$ can be treated as a "conductivity" matrix.
+    The formula (\ref{equ:discrete_ohm}) functions as Ohm's law on the discrete level.
+The $\mathbb{M}_\sigma^m$ can be treated as a ``conductivity" matrix.
 Since in the quasi-neutral limit $\lambda \rightarrow 0$ we lose control of the $\mathbf{E}$-field through its time derivative, $\mathbb{M}_\sigma^m$ is crucial to the stability of the scheme.
 Since $\mathbf{j}$ and $\mathbf{d}$ are both defined on dual faces, it is reasonable to adopt a local relation between them.
-Therefore, we perform the \emph{diagonal lumping} trick on (\ref{equ:discrete_ohm}), i.e.
-rendering it diagonal by accumulating the row sum.
-We observe enhanced stability in the numerical experiments with very minor changes in the results.
+Therefore, we perform the \emph{diagonal lumping} trick, i.e.
+rendering $\mathbb{M}_\sigma^m$ diagonal by accumulating the row sum.
+The lumped $\mathbb{M}_\sigma^m$ has a positive diagonal (for the entity corresponding to $\Omega_P$.
+the rest is zero since no current exists in $\Omega_N$).
+Enhanced stability is observed in the numerical experiments with very minor changes in the results.
 \end{remark}
-\section{Numerical Experiment} \label{sec:numerical_experiment}
+\section{Numerical Experiments} \label{sec:numerical_experiment}
 
@@
 We set the mass ratio $\varepsilon_e := m_e / m_i = 10^4$ and the collision parameter $\alpha^\text{coll} = 32$.
-\begin{figure}
-    \centering
-    \includegraphics[scale=0.3]{primal_mesh.png}
-    \hspace{1cm}
-    \includegraphics[scale=0.3]{dual_mesh.png}
-    \caption{Primal mesh (left) and dual mesh (right).}
-    \label{fig:primal_dual_meshes}
-\end{figure}
-\subsection{Case 1: Quasi-1D Problem}
-On noticing the radial symmetry of the domain as well as boundary conditions, we can simplify the governing equations defined at the axis of symmetry, i.e.
+
+\todo{Reference to github repository}
+
+\subsection{Case I: Quasi-1D Problem}
+Noticing the radial symmetry of the domain as well as boundary conditions, we can simplify the governing equations defined at the axis of symmetry, i.e.
 $z$-axis in this case, thanks to vanishing radial components of the vector fields and their radial derivatives.
-The Euler-Maxwell system at the axis of symmetry reduces to
+The (isentropic and collisionless) Euler-Maxwell system at the axis of symmetry reduces to
 \begin{align*}
     &\partial_t n_* + \partial_z(n_*u_{*,z}) = 0, \\
-    &\partial_t (n_* u_{*,z}) + \partial_z(n_*u_{*,z}^2) + \varepsilon_*^{-2} \partial_z p_* = \varepsilon_*^{-2}q_*n_*E_z, \\
-    &\partial_t (n_*e_*) + \partial_z (n_* h_* u_{*,z}) = \varepsilon_*^{-2} q_* n_* u_{*,z} E_z, \\
+    &\partial_t (n_* u_{*,z}) + \partial_z(n_*u_{*,z}^2) + \varepsilon_*^{-2} \partial_z p_*(n_*) = \varepsilon_*^{-2}q_*n_*E_z, \\
     \lambda^2 &\partial_t E_z = \sum_* - q_* n_* u_{*,z}.
 \end{align*}
-which is similar to the 1D model in Section \ref{sec:projection_to_1d}.
-Therefore, it is reasonable to compare the results produced by the 1D scheme in Section \ref{sec:1d_fully_discrete_model} and the one on $z$-axis produced by the 3D scheme proposed in Section \ref{sec:3d_ap_scheme}.
-Fig.
-\ref{fig:z_axis_reduction} demonstrates good matching.
+which shares the same equations as the 1D model in Section \ref{sec:projection_to_1d} after further dropping $u_x, B_y, E_x$.
+We compare the results produced by the 1D scheme (see Section \ref{sec:1d_fully_discrete_model}) and those produced by the 3D scheme (see Section \ref{sec:3d_ap_scheme}) restricted to the $z$-axis.
+The following initial conditions are used for both models
+\begin{equation*}
+    n_e(z,0) = n_i(z,0) = 1, u_z(z,0) = \chi_{[-0.1,0]}(z) - \chi_{[0,0.1]}(z),\ \ \forall z \in [-0.1,0.1].
+\end{equation*}
+where $\chi$ is the characteristic function. The other variables are initially zero. The case for $\lambda = 1$ is tested. Fig. \ref{fig:z_axis_reduction} demonstrates good matching.
+
 \begin{figure}
     \centering
-    \includegraphics{z_axis_reduction.eps}
-    \caption{Comparison of 1D two-fluid model and reduced 1D model on $z$-axis from 3D two-fluid model.
+    \includegraphics[scale=1.2]{z_axis_reduction.eps}
+    \caption{Case I: Comparison of 1D two-fluid model and reduced 1D model on $z$-axis from 3D two-fluid model.
 The results are both generated on meshes with 64 cells along the $z$-axis.
+$\lambda = 1$.
 No friction term exists.
@@
 
-\subsection{Case 2: 3D Cylindrical Problem}
+\subsection{Case II: 3D Cylindrical Problem}
 
@@
 \end{equation*}
-All the other quantities are set to zero initially.
+All the other variables are set to zero initially.
 We set $\varphi(\mathbf{x}, t)|_{\Gamma_C^-} = 0, \varphi(\mathbf{x}, t)|_{\Gamma_C^+} = 1$, that is, a constant voltage is applied at the anode and excites the system.
@@
 \begin{remark}
-    Such an initial state is compatible with the BCs and the quasi-neutral condition $\rho = 0$, which means no initial layer and boundary layer in the sense of perturbation theory will arise when $\lambda \rightarrow 0$.
+    Such an initial state is compatible with the boundary conditions and the quasi-neutral condition $\rho = 0$, which means no initial layer and boundary layer in the sense of perturbation theory will arise when $\lambda \rightarrow 0$.
 \end{remark}
@@
 First, the rotational symmetry of the problem is preserved.
-Second, the $\mathbf{E}$-field points from $\Gamma^+_C$ to $\Gamma^-_C$ with a relatively uniform value of approximately 0.2 ($=\text{applied voltage}/\text{cylinder length}$) as a consequence of the curl-free property of the $\mathbf{E}$-field in the steady state according to Faraday's law.
+Second, the $\mathbf{E}$-field points from $\Gamma^+_C$ to $\Gamma^-_C$ with a relatively uniform value of approximately 0.2 ($=\text{applied voltage}/\text{cylinder length}$) as a consequence of the irrotational $\mathbf{E}$-field in the steady state according to Faraday's law.
 This is also confirmed in Fig.
@@
 Besides, the $\mathbf{B}$-field is azimuthal (spiral-shaped) and orthogonal to the $\mathbf{E}$-field.
-Also, under the driven force by the $\mathbf{E}$-field, the electrons move towards the anode $\Gamma^+_C$ as expected.
+Also, under the electric force, the electrons move towards the anode $\Gamma^+_C$ as expected.
 \begin{figure}
@@
     \end{subfigure}
-    \caption{Snapshots of the $\mathbf{E}$-field, $\mathbf{B}$-field, and $\mathbf{u}_e$ for different $\lambda$ at $t = 10$ based on a primal mesh with 1920 cells (16 cells along $z$-axis). } 
+    \caption{Case II: Snapshots of the $\mathbf{E}$-field, $\mathbf{B}$-field, and $\mathbf{u}_e$ for different $\lambda$ at $t = 10$ based on a primal mesh with 1920 cells (16 cells along $z$-axis).
+}
     \label{fig:3d_vec_field_E_B_ue}
@@
 Due to the high computational cost in 3D simulations, reference solutions produced by a highly-refined mesh are not trivially accessible.
-That is why we demonstrate results generated by relatively coarse meshes.
-Fig.
-\ref{fig:grid_study_3d} indicates that the solutions are stable under mesh refinement.
+Therefore, we demonstrate results generated by relatively coarse meshes.
+Tab.
+\ref{tab:grid_study_norm} lists $L^2$-norms of the solutions on different meshes, which indicates  robustness with respect to mesh refinement.
 To reveal more features of the solutions, in Fig.
-\ref{fig:grid_study_3d_clip_lambda-1e-1} and \ref{fig:grid_study_3d_clip_lambda-0}, we plot some quantities at the cross-section generated by meshes of different sizes for $\lambda = 0.1$ and $0$.
-Qualitatively the same solutions are produced under different meshes.
+\ref{fig:grid_study_3d_clip_lambda-1e-1} and \ref{fig:grid_study_3d_clip_lambda-0} we plot the solutions at the cross-section generated by meshes of different sizes for $\lambda = 0.1$ and $0$.
+Qualitatively the same solutions are produced on meshes of different sizes.
+
+\begin{table}[]
+    \centering
+    \begin{tabular}{c | c c c | c c c}
+        \hline\hline
+        \multirow{2}{1em}{$N_V$} & \multicolumn{3}{c}{$\lambda = 1$} & \multicolumn{3}{c}{$\lambda = 0$} \\
+        \cline{2-4} \cline{5-7}
+        & $\|n_e \|_{L^2}$ & $\|\mathbf{E} \|_{L^2}$ & $\|\mathbf{B} \|_{L^2}$ & $\|n_e \|_{L^2}$ & $\|\mathbf{E} \|_{L^2}$ & $\|\mathbf{B} \|_{L^2}$  \\
+        \hline
+         1920  &  4.40 & 0.466 & 0.214 & 4.40 & 1.14 & 0.0155 \\
+         3840  &  4.40 & 0.443 & 0.208 & 4.40 & 1.14 & 0.0155 \\
+         14592 &  3.84 & 0.381 & 0.256 & 3.84 & 1.14 & 0.0135 \\ 
+         29184 &  3.84 & 0.362 & 0.256 & 3.84 & 1.14 & 0.0135 \\
+         \hline\hline
+    \end{tabular}
+    \caption{$L^2$-norms of the electron density, the $\mathbf{E}$-field and the $\mathbf{B}$-field on meshes of different size when $\lambda = 1$ or $\lambda = 0$.}
+    \label{tab:grid_study_norm}
+\end{table}
 
@@
     \centering
-    \includegraphics[scale=0.8]{norm-vs-mesh.eps}
-    \caption{1-norms of quantities with respect to different mesh sizes: The results are computed for $\lambda = 1$ and $0.1$ at $t = 1$.}.
-    \label{fig:grid_study_3d}
-\end{figure}
-
-\begin{figure}
+    \begin{minipage}{0.0\textwidth}
+    \Large
+    \vspace{0.4cm}
+    $\mathbf{|E|}$
+
+    \vspace{2.2cm}
+    $\mathbf{|B|}$
+
+    \vspace{2.2cm}
+    $n_e$
+
+    \vspace{1.9cm}
+    $n_i$
+    \end{minipage}
+    \begin{minipage}{0.9\textwidth}
     \centering
@@
     \includegraphics[scale=0.27]{clip_ni_T-1_lambda-1e-1_32-3-4.png}
-    \caption{Quantities at the cross-section generated by meshes with different refinement levels: 1920 primal cells in Refinement 1; 14592 primal cells in Refinement 2; 30720 primal cells in refinement 3.
+    \end{minipage}
+    \caption{Case II: Quantities at the cross-section generated by meshes with different refinement levels: 1920 primal cells in Refinement 1; 14592 primal cells in Refinement 2; 30720 primal cells in refinement 3.
 The snapshots are computed for $\lambda = 0.1$ at $t = 1$.}
@@
     \centering
+    \begin{minipage}{0.0\textwidth}
+    \Large
+    \vspace{0.4cm}
+    $\mathbf{|E|}$
+
+    \vspace{2.2cm}
+    $\mathbf{|B|}$
+
+    \vspace{2.2cm}
+    $n_e$
+
+    \vspace{1.9cm}
+    $n_i$
+    \end{minipage}
+    \begin{minipage}{0.9\textwidth}
+    \centering
     \textit{\textsf{Refinement 1\hspace{2.5cm}Refinement 2\hspace{2.5cm}Refinement 3\hspace{1cm}}}
-
     \includegraphics[scale=0.27]{slice_E_T-1_lambda-0_8-2-2.png}
@@
     \includegraphics[scale=0.27]{slice_E_T-1_lambda-0_32-3-4.png}
-    \includegraphics[scale=0.27]{slice_B_T-1_lambda-0_8-2-2.png}
-    \includegraphics[scale=0.27]{slice_B_T-1_lambda-0_16-3-3.png}
+
+    \hspace{0.0cm}
+    \includegraphics[scale=0.27]{slice_B_T-1_lambda-0_8-2-2.png}\hspace{0.02cm}
+    \includegraphics[scale=0.27]{slice_B_T-1_lambda-0_16-3-3.png}\hspace{0.02cm}
     \includegraphics[scale=0.27]{slice_B_T-1_lambda-0_32-3-4.png}
-    \includegraphics[scale=0.27]{slice_ne_T-1_lambda-0_8-2-2.png}
-    \includegraphics[scale=0.27]{slice_ne_T-1_lambda-0_16-3-3.png}
+
+    \hspace{0.04cm}
+    \includegraphics[scale=0.27]{slice_ne_T-1_lambda-0_8-2-2.png}\hspace{0.04cm}
+    \includegraphics[scale=0.27]{slice_ne_T-1_lambda-0_16-3-3.png}\hspace{0.03cm}
     \includegraphics[scale=0.27]{slice_ne_T-1_lambda-0_32-3-4.png}
-    \includegraphics[scale=0.27]{slice_ni_T-1_lambda-0_8-2-2.png}
-    \includegraphics[scale=0.27]{slice_ni_T-1_lambda-0_16-3-3.png}
+
+    \hspace{0.04cm}
+    \includegraphics[scale=0.27]{slice_ni_T-1_lambda-0_8-2-2.png}\hspace{0.04cm}
+    \includegraphics[scale=0.27]{slice_ni_T-1_lambda-0_16-3-3.png}\hspace{0.04cm}
     \includegraphics[scale=0.27]{slice_ni_T-1_lambda-0_32-3-4.png}
-    \caption{Quantities at the cross-section generated by meshes with different refinement levels.
+    \end{minipage}
+
+    \caption{Case II: Quantities at the cross-section generated by meshes with different refinement levels.
 Refinement 1: 1920 primal cells; Refinement 2: 14592 primal cells; Refinement 3: 30720 primal cells.
@@
 \ref{fig:origin-data_vs_time}.
-Being originally at rest, the system is excited by the applied voltage and generates oscillations that dampen over time.
+Being originally at rest, the system is excited by the applied voltage and generates oscillations that decay over time.
 A larger value of $\lambda$ leads to oscillations with larger amplitude and slower damping whereas with a smaller $\lambda$ the system quickly reaches a steady state.
@@
     \includegraphics[scale=0.9]{data-vs-time_stepVoltage.eps}
-    \caption{Time histories of quantities at the domain center and of the averaged current densities at $\Gamma^+_C$ (anode) and $\Gamma^-_C$ (cathode) for different values of $\lambda$.
+    \caption{Case II: Time histories of quantities at the domain center and of the averaged current densities at $\Gamma^+_C$ (anode) and $\Gamma^-_C$ (cathode) for different values of $\lambda$.
 The simulations are done on a mesh with 1920 primal cells with 8 layers along the $z$-axis.}
@@
     \includegraphics{stabilizationComparision_stepVoltage.eps}
-    \caption{Stabilization in the non-conducting domain $\Omega_N$. The $\mathbf{E}$-field z-component in a boundary cell in $\Omega_N$ is displayed over time. }
+    \caption{Case II: Stabilization in the non-conducting domain $\Omega_N$. The $\mathbf{E}$-field z-component in a boundary cell in $\Omega_N$ is displayed over time. }
     \label{fig:stabilization_comparison}
@@
 \ref{fig:zaxis-data_vs_z-T_10}.
-The lower figure demonstrates the matching of the density profiles of the electrons and ions, namely, the quasi-neutrality holds in the discrete level.
+The lower figure demonstrates the matching of the density profiles of the electrons and ions, namely, the quasi-neutrality holds on the discrete level.
 
@@
     \includegraphics{data-vs-z_stepVoltage.eps}
-    \caption{Quantities along $z$-axis for different $\lambda$: The results are computed at $t = 10$ on a mesh with 1920 primal cells with 8 layers along $z$-axis.}.
+    \caption{Case II: Quantities along $z$-axis for different $\lambda$: The results are computed at $t = 10$ on a mesh with 1920 primal cells with 8 layers along $z$-axis.}.
     \label{fig:zaxis-data_vs_z-T_10}

### 2022-12-01 paper_version/main.tex
minor change

@@
 We discretize a parametric problem $P^\lambda$, which converges to its limit $P^0$ as the perturbed parameter $\lambda \rightarrow 0$, by the scheme $P^\lambda_h$ where $h$ denotes some discretization parameter, e.g.
-the mesh size, see also the illustration by a commuting diagram in \cite[][fig.
+the mesh size, see also the illustration by a commuting diagram in \cite[][Fig.
 1]{jin_2010}.
@@
 ionization and recombination, are not considered.
-For full details about the modeling of these physical processes, readers are referred to \cite[][sec.
+For full details about the modeling of these physical processes, readers are referred to \cite[][Sec.
 3.2]{fuchs_2021}.
@@
 In rescaling, variables in equations are replaced by the ratio of original quantities and constant reference quantities, which transforms the system into dimensionless form.
-In this part, the rescaling procedure mostly follows that of \cite[][sec.
+In this part, the rescaling procedure mostly follows that of \cite[][Sec.
 2.2]{degond_2017}.
@@
 \footnotetext[1]{Abbreviation of \emph{with respect to}.}
-\footnotetext[2]{It is basically the reciprocal of the number of particles per Debye sphere, see \cite[][sec. 1.1]{gibbon2020}. Classical plasma theory assumes $g \ll 1$.}
+\footnotetext[2]{It is basically the reciprocal of the number of particles per Debye sphere, see \cite[][Sec. 1.1]{gibbon2020}. Classical plasma theory assumes $g \ll 1$.}
 
@@
  Assumptions can be made to reduce the number of dimensionless parameters.
-Following \cite[][sec.
+Following \cite[][Sec.
 2.2]{degond_2017}, the reference speed $\overline{v}$ is of the same scale as the plasma speed $\overline{u}$ and the thermal speed $v_{th,i}$ whereas it is much smaller than the light speed $c$.
@@
 A geometric arrangement corresponding to this setting is sketched in Fig.
-\ref{fig:domain_sketch} and is the one used in \cite[][ch.
+\ref{fig:domain_sketch} and is the one used in \cite[][Ch.
 1, sec.
@@
 The spatial domain is covered by two meshes that interlace with each other, denoted by a mesh doublet $(\mathcal{M}, \Tilde{\mathcal{M}})$ for primal mesh and dual mesh respectively.
-The fundamental duality property requires that \emph{each edge of one mesh penetrates a face of the other mesh and that each vertex of one mesh lies inside of a cell of the other mesh} \cite[][sec.
+The fundamental duality property requires that \emph{each edge of one mesh penetrates a face of the other mesh and that each vertex of one mesh lies inside of a cell of the other mesh} \cite[][Sec.
 2]{weiland_2003}, which makes $(\mathcal{M}, \Tilde{\mathcal{M}})$ staggered to each other.
@@
 
-In three dimensions, the meshes are constructed by extruding the 2D meshes vertically along one axis in a staggered manner \cite[][sec.
+In three dimensions, the meshes are constructed by extruding the 2D meshes vertically along one axis in a staggered manner \cite[][Sec.
 3.1]{Marrone_2001}.
@@
 In this case their circumcenters lie outside the triangles and the intersection between edges and faces is violated.
-An alternative approach is barycenter-based dual meshes, which are not restricted to an acute-angle triangulation \cite[][sec.
+An alternative approach is barycenter-based dual meshes, which are not restricted to an acute-angle triangulation \cite[][Sec.
 4.2]{Marrone_2001}.
@@
 \subsubsection{Orientation and Incidence Matrices}
-Each geometric entity in the primal mesh $\mathcal{M}$ is (arbitrarily) endowed with an \emph{internal orientation}\footnote{This notion should not be aliased with \emph{inner orientation}, which has a slightly different definition, see \cite[][sec.
+Each geometric entity in the primal mesh $\mathcal{M}$ is (arbitrarily) endowed with an \emph{internal orientation}\footnote{This notion should not be aliased with \emph{inner orientation}, which has a slightly different definition, see \cite[][Sec.
 3.1]{tonti_2002}.}.
@@
 \ref{tab:incidence_relation} to interior part of $\Tilde{\mathcal{M}}$.
-For a more systematic illustration that considers the boundary dual entities, see \cite[][sec.
+For a more systematic illustration that considers the boundary dual entities, see \cite[][Sec.
 5]{hip_1999}.
@@
 where $|\cdot|$ denotes taking length or area.
-We would like to remark that the approximation error is introduced due to the implicit assumption that vector fields are piecewise constant, see the analysis in \cite[][sec.
+We would like to remark that the approximation error is introduced due to the implicit assumption that vector fields are piecewise constant, see the analysis in \cite[][Sec.
 3.2]{Marrone_2001}.
@@
 Apart from the least-square method, other methods include Perot's method \citep{perot_2000}, finite-entity-based methods, etc., which potentially can achieve higher-order accuracy.
-See \cite[][sec.
+See \cite[][Sec.
 3.4.4]{fuchs_2021} and the references therein.
@@
 \subsubsection{Discrete Boundary Conditions}
-The boundary conditions for the Euler system (see Section \ref{sec:BC}) are implemented by the approach of ghost cells \cite[][ch.
+The boundary conditions for the Euler system (see Section \ref{sec:BC}) are implemented by the approach of ghost cells \cite[][Ch.
 7]{leveque_2007}, i.e.
@@
 We conduct numerical experiments based on the geometric setting and boundary conditions as presented in Section \ref{sec:BC}.
-The primal-dual mesh pair $(\mathcal{M}, \Tilde{\mathcal{M}})$ is generated based on the code developed in \cite[][ch.
+The primal-dual mesh pair $(\mathcal{M}, \Tilde{\mathcal{M}})$ is generated based on the code developed in \cite[][Ch.
 1]{fuchs_2021}.

### 2022-12-09 paper_version/main.tex
minor change
draft conclusion and polish reference

@@
 \section*{Abstract}
+\todo{polish the abstract}
+
 A key coefficient characterizing plasmas is the so-called Debye length $\lambda_D$, whose magnitude indicates to what extent net electric charges deviate from zero.
@@
 The scheme is designed to be AP as $\lambda_D \rightarrow 0$ and this is validated through numerical experiments.
-Special care is necessary for the boundary conditions which must be valid in both regimes.
-Additionally, if the electromagnetic fields have to be modelled in an insulating region beyond the plasma domain, additional stabilization to accommodate Gauss's law is necessary.
+Besides, if the electromagnetic fields have to be modelled in an non-conducting region beyond the plasma domain, additional stabilization to accommodate Gauss's law is necessary.
 
@@
 
-\subsubsection{Stabilization in $\Omega_N$} \label{sec:reform_discrete}
+\subsubsection{Stabilization in $\Omega_N$} \label{sec:reform-discrete}
 In Section \ref{sec:reform_continuous}, we have proposed a stabilization of the Maxwell system in the non-conducting domain $\Omega_N$ by introducing a Lagrange multiplier.
@@
 
+The source code is published in \cite{yu2022}.
+
 \todo{Reference to github repository}
@@
 \end{align*}
-which shares the same equations as the 1D model in Section \ref{sec:projection_to_1d} after further dropping $u_x, B_y, E_x$.
+which is nothing but the 1D model in Section \ref{sec:projection_to_1d} after further dropping $u_x, B_y, E_x$.
 We compare the results produced by the 1D scheme (see Section \ref{sec:1d_fully_discrete_model}) and those produced by the 3D scheme (see Section \ref{sec:3d_ap_scheme}) restricted to the $z$-axis.
@@
 Next, we perform a grid study.
-The norms of the solutions under mesh refinement are shown in Fig.
-\ref{fig:grid_study_3d}.
-Due to the high computational cost in 3D simulations, reference solutions produced by a highly-refined mesh are not trivially accessible.
+Due to the high computational cost in 3D simulations, reference solutions produced by a highly-refined mesh are not available.
 Therefore, we demonstrate results generated by relatively coarse meshes.
@@
 To reveal more features of the solutions, in Fig.
-\ref{fig:grid_study_3d_clip_lambda-1e-1} and \ref{fig:grid_study_3d_clip_lambda-0} we plot the solutions at the cross-section generated by meshes of different sizes for $\lambda = 0.1$ and $0$.
-Qualitatively the same solutions are produced on meshes of different sizes.
+\ref{fig:grid_study_3d_clip_lambda-1e-1} (for $\lambda = 0.1$) and \ref{fig:grid_study_3d_clip_lambda-0} (for $\lambda = 0$) we plot the solutions at the cross-section generated by meshes of different sizes on which qualitatively the same solutions are observed.
 
@@
 
-The stabilization proposed in Section \ref{sec:reform_discrete} is essential to achieve a stable result when $\lambda$ tends to zero.
+The stabilization proposed in Section \ref{sec:reform-discrete} is essential to achieve a stable result when $\lambda$ tends to zero.
 As is shown in Fig.
@@
 \section{Conclusion}
-
+We have developed an AP scheme for the Euler-Maxwell plasma model in three spatial dimensions that is versatile in both non-neutral $\lambda = \mathcal{O}(1)$ and quasi-neutral $\lambda \rightarrow 0$ regimes.
+The main features of our work lie in: i) Maxwell's equations are discretized on primal and dual meshes by FIT (in the spirit of DEC).
+By discretizing the Euler equations by FVM on dual mesh, the coupling of two systems is naturally realized via the connection of the mass flux and electric current at each dual face.
+ii) A non-conducting region is taken into account where additional stabilization is essential when $\lambda \rightarrow 0$.
+We enforce the vanishing divergence of the $\mathbf{D}$-field through a Lagrange multiplier for any value of $\lambda$.
+iii) The alignment of primal-dual meshes at the boundary entails cut-off cells and auxiliary unknowns have to be introduced.
+iv) A lumping trick is applied to the conductivity matrix (relating the electric current and the electric field) to enhance stability.
+
+Our approach has been tested on a cylindrical domain with ECE boundary conditions and the AP property has been verified numerically.
+To the best of the authors' knowledge, this work is among the first to try to solve the 3D fluid plasma model on unstructured meshes, which potentially gives more flexibility than the finite-difference-based approaches and reduces the computational cost compared to particle-based approaches.
+In particular, the AP property allows us to address regimes of the arbitrary value of the Debye length.
+
+\todo{Polish the reference}
 \bibliography{ref}

### 2022-12-09 paper_version/main.tex
minor change

@@
 In the same way, the dual mesh $\Tilde{\mathcal{M}}$ is defined by $\{\Tilde{P}, \Tilde{L}, \Tilde{A}, \Tilde{V}\}$.
-The entities of two meshes are associated with bijective pairings $P \leftrightarrow \Tilde{V}$, $L \leftrightarrow \Tilde{A}$, $A \leftrightarrow \Tilde{L}$ and $V \leftrightarrow \Tilde{P}$ which arise in a very natural way: $P(\Tilde{P} \text{ resp.})$ corresponds to $\Tilde{V}(V \text{ resp.})$ in which it lies and $L(\Tilde{L} \text{ resp.})$ penetrates its corresponding $\Tilde{A}(A \text{ resp.})$.
+The entities of two meshes are associated with bijective pairings $P \leftrightarrow \Tilde{V}$, $L \leftrightarrow \Tilde{A}$, $A \leftrightarrow \Tilde{L}$ and $V \leftrightarrow \Tilde{P}$ which arise in a very natural way: $P(\Tilde{P} \text{ resp.,})$ corresponds to $\Tilde{V}(V \text{ resp.,})$ in which it lies and $L(\Tilde{L} \text{ resp.,})$ penetrates its corresponding $\Tilde{A}(A \text{ resp.,})$.
 According to their dimensions, vertices, edges, faces and cells are also called 0-dim, 1-dim, 2-dim and 3-dim entities respectively.

### 2022-12-19 paper_version/main.tex
roman's comments and a new version of abstract

@@
 
+\noindent\textbf{A short version:}
+
+The Debye length $\lambda_D$, as a key characteristic coefficient of plasmas, may range over many orders of magnitude.
+The induced singularly perturbed problem is a challenge for plasma simulations.
+Recently so called asymptotic-preserving (AP) schemes, which target such problems, are studied widely.
+However, in the context of plasma simulations, only AP schemes in one spatial dimension are available.
+In this work, we construct an AP schemes for Maxwell-Euler equations in three spatial dimensions based on primal-dual meshes and the finite integration technique (FIT) for Maxwell's equations coupled with the finite volume method (FVM) for the fluid equations.
+Besides, issues like boundary treatment and stabilization in non-conducting regions are tackled.
+The AP property is verified numerically.
+We expect this new discretization approach is particularly suited for problems involving multiple scales of the Debye length, e.g.
+electric arcs.
+
+\noindent\textbf{A long version:}
+
+{\color{red}
 A key coefficient characterizing plasmas is the so-called Debye length $\lambda_D$, whose magnitude indicates to what extent net electric charges deviate from zero.
@@
 Besides, if the electromagnetic fields have to be modelled in an non-conducting region beyond the plasma domain, additional stabilization to accommodate Gauss's law is necessary.
+}
 
@@
 
-\mycomment{Roman: more info from a physical point of view?}
-
-We consider a hydrodynamic multi-species plasma model, which boils down to the Maxwell-Euler system.
-As in \cite{degond_2012}, our focus is an \emph{asymptotic-preserving} (AP) discretization in the quasi-neutral limit $\lambda_D \rightarrow 0$, where $\lambda_D$ is the rescaled Debye length, see Section \ref{sec:rescaling} for the underlying scaling arguments and \cite{degond_2012,degond_2017} for a discussion of the importance of the AP property in plasma codes.
+% \mycomment{Roman: more info from a physical point of view?} R.H. 19.12. Extended paragraph
+The starting point for this work was the desire to numerically simulate the formation and evolution of electric arcs at atmospheric pressures.
+We rely on a widely accepted description by means of a hydrodynamic multi-species plasma model, which boils down to the Maxwell-Euler system.
+The arc phenomenon covers a wide range of plasma regimes and the numerical model should be able to deal with all of them seamlessly and simultaneously.
+Thus in this work, as in \cite{degond_2012}, the focus is on \emph{asymptotic-preserving} (AP) discretization in the quasi-neutral limit $\lambda \rightarrow 0$, where $\lambda$ is the rescaled Debye length, see Section \ref{sec:rescaling} for the underlying scaling arguments and \cite{degond_2012,degond_2017} for a discussion of the importance of the AP property of numerical plasma models.
 
@@
 For the sake of simplicity, we only consider ion-electron collision in this work, but extension to more species is straightforward.
-Such collisions can be well modelled by friction terms (\citep[][sec.
+Such collisions can be well modelled by friction terms (\citep[][Sec.
 5.6.2]{chen2016})
@@
 \subsection{Quasi-neutral Limit} \label{sec:quasi-neutral_limit}
-The Debye length $\lambda_D$ (see its definition in the preceding section) is the characteristic length over which local concentrations of charge are shielded, see \cite[sec.
+The Debye length $\lambda_D$ (see its definition in the preceding section) is the characteristic length over which local concentrations of charge are shielded, see \cite[Sec.
 1.4]{chen2016} for the underlying physics.
-In many situations, it has a rather low value compared to the reference length scale: the typical $\lambda_D$ for gas discharge and Tokamak is $10^{-4}$ meter; for interstellar medium, the magnitude is about $1$ meter\cite[ch.
+In many situations, it has a rather low value compared to the reference length scale: the typical $\lambda_D$ for gas discharge and Tokamak is $10^{-4}$ meter; for interstellar medium, the magnitude is about $1$ meter\cite[Ch.
 20]{Blandford_2013}.
@@
 This topic is beyond the scope of this paper.
-Readers are referred to \cite[ch.
+Readers are referred to \cite[Ch.
 2]{remi_2014} \cite{Peng_2008} for the quasi-neutral limit of the Maxwell-Euler system, and \cite{mark_1995, Eckhaus_1980} for the general theory.
@@
 \ref{fig:domain_sketch} and is the one used in \cite[][Ch.
-1, sec.
+1, Sec.
 4]{fuchs_2021}.
-
-\mycomment{Roman: expand on a relevant physical setting, e.g. wall-stabilized arc in hight voltage circuit breakers.}
-
-The Euler system is defined in $\Omega_P$ with boundary $\partial\Omega_P$.
+This situation is simple, but highly relevant.
+It covers fundamental experimental set-ups, for example, those studying wall-stabilized electric arcs \cite{GGF05}, but is also adequate for a range of industrial plasmas, for instance, those occurring in high-voltage circuit breakers \cite{SEE15,MGU20}.
+%\mycomment{Roman: expand on a relevant physical setting, e.g. wall-stabilized arc in hight voltage circuit breakers.}
+
+The Euler equations are posed $\Omega_P$ and associated boundary conditions are imposed on $\partial\Omega_P$.
 We consider the physical scenario where plasma is confined by a solid insulator.
@@
 
-\todo{Reference to github repository}
-
 \subsection{Case I: Quasi-1D Problem}
@@
 
-Our approach has been tested on a cylindrical domain with ECE boundary conditions and the AP property has been verified numerically.
+Our approach has been tested on a cylindrical domain with settings meant for electric arc simulations.
+The AP property has been verified numerically.
 To the best of the authors' knowledge, this work is among the first to try to solve the 3D fluid plasma model on unstructured meshes, which potentially gives more flexibility than the finite-difference-based approaches and reduces the computational cost compared to particle-based approaches.
@@
 
-\todo{Polish the reference}
 \bibliography{ref}

### 2022-12-20 paper_version/main.tex
fix some typo

@@
 However, in the context of plasma simulations, only AP schemes in one spatial dimension are available.
-In this work, we construct an AP schemes for Maxwell-Euler equations in three spatial dimensions based on primal-dual meshes and the finite integration technique (FIT) for Maxwell's equations coupled with the finite volume method (FVM) for the fluid equations.
+In this work, we construct an AP scheme for Maxwell-Euler equations in three spatial dimensions based on primal-dual meshes and the finite integration technique (FIT) for Maxwell's equations coupled with the finite volume method (FVM) for the fluid equations.
 Besides, issues like boundary treatment and stabilization in non-conducting regions are tackled.
@@
 
-The quasi-neutral limit of the Maxwell-Euler system leads to a singularly perturbed problem, that is, the PDE system changes its type\footnote{from hyperbolic to a mixed type}.
+The quasi-neutral limit of the Maxwell-Euler system leads to a singularly perturbed problem, that is, the limiting PDE system changes its type\footnote{The Maxwell-Euler system transits from hyperbolic to a mixed type}.
 This poses a challenge for simulations in settings encompassing different regimes.
 Singularly perturbed problems occur in many physical models, e.g.
-vanishing viscosity in the Navier-Stokes equations\cite{Kato_1984}, zero-relaxation-limit of kinetic equations\cite{jin_2010} and zero-Mach-limit of compressible flows\cite{degond_2007, haack_2010}.
+vanishing viscosity in the Navier-Stokes equations \cite{Kato_1984}, zero-relaxation-limit of kinetic equations \cite{jin_2010} and zero-Mach-limit of compressible flows \cite{degond_2007, haack_2010}.
 It is desirable that numerical schemes are valid for all ranges of scaled parameters.
@@
 
-The content of this paper is organized as follows: In Section 2, we give a full description of the underlying equations of the Maxwell-Euler system and its rescaling procedure.
+The content of this paper is organized as follows: In Section \ref{sec:plasma-model}, we give a full description of the underlying equations of the Maxwell-Euler system and its rescaling procedure.
 Meanwhile, the boundary conditions in our setting is elaborated.
-A reformulation of Maxwell's equations in the insulating region is then presented.
-Section 3 is devoted to the spatial discretization.
-The concept of primal-dual meshes is introduced based on which FIT and FVM are applied.
-We discuss the fully-discretized AP scheme in Section 4 and do numerical experiments in Section 5.
+A reformulation of Maxwell's equations in the non-conducting region is presented.
+Section \ref{sec:spatial_discretization} is devoted to the spatial discretization.
+The concept of primal-dual meshes is introduced based on which FIT and FVM are utilized.
+We discuss the full AP discretization in Section \ref{sec:full-discretization} and do numerical experiments in Section \ref{sec:numerical_experiment}.
 
@@
 
-\section{Plasma model}
+\section{Plasma model} \label{sec:plasma-model}
 
 \subsection{The Maxwell-Euler System}
-Plasmas consist of electrically charged and neutral particle species that can be treated as fluids.
+Plasmas consist of electrically charged and (possibly) neutral particle species that can be treated as fluids.
 That is, they may be described by the Navier-Stokes equations augmented with source terms for species generation (ionization, recombination), forces (Lorentz force and interspecies friction), and energy (thermal relaxation among species, radiative heat transfer, Ohmic heating).
@@
 
-The electromagnetic effects in plasmas are governed by Maxwell's equations, which Maxwell's equations in SI units read
+The electromagnetic effects in plasmas are governed by Maxwell's equations:
 \begin{subequations}
@@
 These equations are known as Faraday's law (\ref{equ:maxwell_faraday}), Amp\`{e}re's law (\ref{equ:maxwell_ampere}), Gauss's law for magnetism (\ref{equ:maxwell_gauss_B}) and Gauss's law for electric field (\ref{equ:maxwell_gauss_D}).
-For simplicity, we only consider isotropic and homogeneous media in vacuum, which amounts to relying on the linear constitutive relations (namely, material laws):
+For simplicity, we only consider isotropic and homogeneous media.
+Namely, we rely on linear constitutive relations (i.e.
+material laws):
 \begin{equation} \label{equ:material_law}
@@
 \end{equation}
-where $\epsilon[\frac{\text{F}}{\text{m}}]$ and $\mu[\frac{\text{N}}{\text{A}^{2}}]$ are the permittivity and permeability and assumed to be constant in this paper.
+where $\epsilon[\frac{\text{F}}{\text{m}}]$ and $\mu[\frac{\text{N}}{\text{A}^{2}}]$ are the permittivity and permeability and assumed to be constant.
 By taking the time derivative of (\ref{equ:maxwell_gauss_D}) and the divergence of (\ref{equ:maxwell_ampere}), it is easy to see that (\ref{equ:maxwell_ampere}) and (\ref{equ:maxwell_gauss_D}) implies the charge conservation
@@
 
-Each species in a plasma can be modelled as a compressible fluid by a set of Euler equations, which additionally includes electromagnetic forces as well as other processes, e.g.
-collisions and recombination.
-The generic expressions are
+Each species in a plasma can be modelled as a compressible fluid through a set of Euler equations augmented by electromagnetic forces as well as other processes, e.g. collisions and recombination:
 \begin{align} \label{equ:euler_}
@@
 \end{align}
-The subscript $*\in \{e, i, \cdots\}$ represents the indices for electron, ions and other species.
-The involved fluid quantities are: number density $n_*[\frac{1}{\text{m}^3}]$, particle mass $m_*[\text{kg}]$,  charge number $q_*[\text{C}]$, velocity $\mathbf{u}_*[\frac{\text{m}}{\text{s}}]$, pressure $p_*[\frac{\text{N}}{\text{m}^2}]$, specific total energy $e_* := \frac{1}{2}|\mathbf{u}_*|^2 + \frac{p_*}{m_*n_*(\gamma - 1)}[\frac{\text{J}}{\text{kg}}]$, specific total enthalpy $h_* := e_* + \frac{p_*}{m_*n_*}[\frac{\text{J}}{\text{kg}}]$ and current density $\mathbf{J}_* := q_*n_*\mathbf{u}_*[\frac{\text{A}}{\text{m}^2}]$.
+The subscript $*\in \{e, i, \cdots\}$ labels electrons, ions or other species.
+The involved fluid quantities are: number density $n_*[\frac{1}{\text{m}^3}]$, particle mass $m_*[\text{kg}]$,  electric charge $q_*[\text{C}]$, velocity $\mathbf{u}_*[\frac{\text{m}}{\text{s}}]$, pressure $p_*[\frac{\text{N}}{\text{m}^2}]$, specific total energy $e_* := \frac{1}{2}|\mathbf{u}_*|^2 + \frac{p_*}{m_*n_*(\gamma - 1)}[\frac{\text{J}}{\text{kg}}]$, specific total enthalpy $h_* := e_* + \frac{p_*}{m_*n_*}[\frac{\text{J}}{\text{kg}}]$ and current density $\mathbf{J}_* := q_*n_*\mathbf{u}_*[\frac{\text{A}}{\text{m}^2}]$.
 All the species are assumed to be ideal gases with heat capacity ratio $\gamma=5/3$ for monatomic gases.
@@
 Combination of the two sets of equations (\ref{equ:maxwell_faraday}) to (\ref{equ:maxwell_gauss_D}) and (\ref{equ:euler_}) leads to the governing equations for a multi-species plasma model.
-The coupling of the two subsystems is due to the fact that electric current is the flow of charged particles:
+The coupling of the two subsystems is due to the fact that the flow of charged particles induces electric currents:
 \begin{equation} \label{equ:maxwell_euler_coupling}
@@
 
-First, a reference value for each quantity, e.g.
-the characteristic length and time scale, is prescribed.
+First, a reference value for each quantity is prescribed.
 We define $\overline{x}$ and $\overline{t}$ as space and time scale of interest, by which the reference velocity $\overline{v}$ is defined as $\overline{x}/\overline{t}$.
@@
     \zeta &:= \frac{\overline{u}}{\overline{v}} \text{ the plasma velocity \emph{w.r.t.} the speed of interest}, &\\
-    M &:= \frac{\overline{u}}{v_{th,i}} \text{ the plasma drift velocity \emph{w.r.t.} the thermal speed of ions, where } v_{th,i} := \left(\frac{k_B \overline{T}}{m_i}\right)^{1/2}, &\\
+    M &:= \frac{\overline{u}}{v_i^{\text{th}}} \text{ the plasma drift velocity \emph{w.r.t.} the thermal speed of ions, where } v_i^{\text{th}} := \left(\frac{k_B \overline{T}}{m_i}\right)^{1/2}, &\\
     \eta &:= \frac{e\overline{E}\overline{x}}{m_i\overline{u}^2} \text{ the electric energy \emph{w.r.t.} the kinetic energy of ions}, &\\
@@
 
-By abuse of notation, the dimensionless quantities have the same symbol as the original quantities.
-For the sake of simplicity, we neglect ionization and recombination but retain collision terms, i.e.
-$\Gamma_* = 0, \mathbf{R}_* = \mathbf{R}_*^\text{coll}, Q_* = Q_*^\text{coll}$ in (\ref{equ:euler_}), while neglecting other effects.
-The rescaled Euler-Maxwell system reads
+By abuse of notation, the rescaled variables share the same notation as before rescaling.
+We neglect ionization and recombination but retain collision terms, i.e.
+$\Gamma_* = 0, \mathbf{R}_* = \mathbf{R}_*^\text{coll}, Q_* = Q_*^\text{coll}$ in (\ref{equ:euler_}).
+The rescaled Euler-Maxwell system is
 \begin{subequations}
@@
 Following \cite[][Sec.
-2.2]{degond_2017}, the reference speed $\overline{v}$ is of the same scale as the plasma speed $\overline{u}$ and the thermal speed $v_{th,i}$ whereas it is much smaller than the light speed $c$.
+2.2]{degond_2017}, the reference speed $\overline{v}$ is of the same scale as the plasma speed $\overline{u}$ and the thermal speed $v_i^{\text{th}}$ whereas it is much smaller than the light speed $c$.
 Also, it is assumed that $\eta$ and $\beta$ are of order one and $\xi$ has the same magnitude as $\lambda$.
@@
 
-In summary, we make the following choices\cite[][sec 2.2]{degond_2017}
+In summary, we make the following choices \cite[][sec 2.2]{degond_2017}
 \begin{align*}
@@
 \end{equation}
-and consequently, the rescaled friction heat for ions and electrons take the expression
+and consequently, the rescaled friction heat for ions and electrons take the expression:
 \begin{align} 
@@
 \begin{equation} \label{equ:maxwell_material_law_rescaled}
-    \mathbf{D} = \epsilon \mathbf{E}, \ \ \ \mathbf{B} = \mu \mathbf{H}, 
+    \mathbf{D} = \epsilon \mathbf{E}, \ \ \ \mathbf{B} = \mu \mathbf{H}. 
 \end{equation}
 \end{subequations}
-but here $\epsilon, \mu$ are the rescaled permittivity and permeability.
-
-We end up with the rescaled Maxwell-Euler system (\ref{equ:maxwell_faraday_rescaled})-(\ref{equ:maxwell_material_law_rescaled}) parameterized by $\lambda$.
+Notice here $\epsilon, \mu$ are the rescaled permittivity and permeability.
+
+We end up with the rescaled Maxwell-Euler system: (\ref{equ:maxwell_faraday_rescaled})-(\ref{equ:maxwell_material_law_rescaled}) parameterized by $\lambda$.
 
 \subsection{Quasi-neutral Limit} \label{sec:quasi-neutral_limit}
-The Debye length $\lambda_D$ (see its definition in the preceding section) is the characteristic length over which local concentrations of charge are shielded, see \cite[Sec.
+The Debye length $\lambda_D$ (see its definition in the preceding section) is the characteristic length over which local net charge is shielded, see \cite[Sec.
 1.4]{chen2016} for the underlying physics.
-In many situations, it has a rather low value compared to the reference length scale: the typical $\lambda_D$ for gas discharge and Tokamak is $10^{-4}$ meter; for interstellar medium, the magnitude is about $1$ meter\cite[Ch.
+In many situations, it has a rather low value compared to the reference length scale: the typical $\lambda_D$ for gas discharge and Tokamak is $10^{-4}$ meter; for interstellar medium, the magnitude is about $1$ meter \cite[Ch.
 20]{Blandford_2013}.
-That justifies the quasi-neutrality assumption that the plasma is locally neutral, i.e.
-$\rho = \sum_* q_*n_* = 0$.
+That justifies the quasi-neutrality assumption that the plasma is quasi-neutral, i.e.
+$\rho = \sum_* q_*n_* \approx 0$.
 The limit model is obtained by formally setting the rescaled Debye length $\lambda$ to zero:
@@
 
-The Euler equations are posed $\Omega_P$ and associated boundary conditions are imposed on $\partial\Omega_P$.
+The Euler equations are defined in $\Omega_P$ with boundary conditions on $\partial\Omega_P$.
 We consider the physical scenario where plasma is confined by a solid insulator.
 Therefore, the interface $\Gamma_W$ is treated as reflective wall where fluid particles are bounced back while keeping the tangential velocity and energy unchanged.
-The contact boundary $\Gamma_C$ is where the plasma and energy flow across, modelled by open boundaries in the sense that fluids are free to flow through, i.e.
+The contact boundary $\Gamma_C$ is modelled by open boundaries where the plasma and energy can flow through, i.e.
 ions and electrons are emitted and absorbed by the electrodes.
@@
 \begin{remark}
-    The treatment of electrodes as open boundary is am extreme simplification. For more realistic electrode modelling, see \cite{godyak_1990, parker_1993}.
+    The treatment of electrodes as open boundary is a simplification. For more realistic electrode modelling, see \cite{godyak_1990, parker_1993}.
 \end{remark}
 
-The Maxwell system is defined on the whole domain $\Omega$.
-The insulating boundary $\Gamma_I$ blocks energy interchange and therefore only admits zero electric and magnetic flux, in the sense that $\mathbf{D}\cdot \mathbf{n}|_{\Gamma_I} = 0$ and $\mathbf{B} \cdot \mathbf{n}|_{\Gamma_I} = 0$ where $\mathbf{n}$ is the normal vector.
+Maxwell's equations are solved in the whole domain $\Omega$.
+The insulating boundary $\Gamma_I$ blocks energy interchange and therefore only admits zero electric and magnetic flux, that is, $\mathbf{D}\cdot \mathbf{n}|_{\Gamma_I} = 0$ and $\mathbf{B} \cdot \mathbf{n}|_{\Gamma_I} = 0$ where $\mathbf{n}$ is the normal vector.
 We model the electrodes by imposing boundary conditions on the contact boundary $\Gamma_C = \Gamma_C^+\cup \Gamma_C^-$ which is composed of two disjoint connected components.
-On the contact boundary $\Gamma_C$, the tangential component $\mathbf{E}_t$ of the $\mathbf{E}$-field is set to zero.
-By Faraday's law (\ref{equ:maxwell_faraday_rescaled}) we have $\nabla \times \mathbf{E} \cdot \mathbf{n} = 0$ on the whole (topologically trivial) boundary $\partial\Omega$.
-It admits a scalar potential $\varphi$ defined on $\partial\Omega$ such that $\mathbf{E}_t = \nabla_\Gamma \varphi$ where $\nabla_\Gamma$ denotes surface gradient.
+On the contact boundary $\Gamma_C$, the tangential component $\mathbf{E}_t$ of the $\mathbf{E}$-field is vanishing.
+By Faraday's law (\ref{equ:maxwell_faraday_rescaled}) we have $\nabla \times \mathbf{E} \cdot \mathbf{n} = 0$ on the whole (topologically trivial) boundary $\partial\Omega$, which admits a scalar potential $\varphi$ defined on $\partial\Omega$ such that $\mathbf{E}_t = \nabla_\Gamma \varphi$ where $\nabla_\Gamma$ denotes surface gradient.
 $\varphi$ is constant on $\Gamma_C^+$ and $\Gamma_C^-$.
@@
 Supplemented with the boundary condition $\psi = 0$ on $\partial\Omega_N$, one can check that (\ref{equ:faraday_ins_reform}) to (\ref{equ:gauss_D_ins_reform}) are equivalent to the original formulation (\ref{equ:faraday_ins})-(\ref{equ:gauss_D_ins}) by verifying that $\psi = 0$ in $\Omega_N$.
-This is done by taking the divergence of (\ref{equ:ampere_ins_reform}), which results in $\delta\psi = 0$ and the zero Dirichlet boundary condition gives vanishing $\psi$.
+This is done by taking the divergence of (\ref{equ:ampere_ins_reform}), which results in $\Delta\psi = 0$ and the zero Dirichlet boundary condition gives vanishing $\psi$.
 The importance of this reformulation will become clear in the numerical experiments, see Section \ref{sec:numerical_experiment}.
@@
 Prior to the spatial discretization of the Maxwell-Euler system, we introduce primal-dual staggered meshes that are necessary in the discretization framework we use.
-The spatial domain is covered by two meshes that interlace with each other, denoted by a mesh doublet $(\mathcal{M}, \Tilde{\mathcal{M}})$ for primal mesh and dual mesh respectively.
+The spatial domain is covered by two meshes interlacing with each other, denoted by a mesh doublet $(\mathcal{M}, \Tilde{\mathcal{M}})$ for primal mesh and dual mesh respectively.
 The fundamental duality property requires that \emph{each edge of one mesh penetrates a face of the other mesh and that each vertex of one mesh lies inside of a cell of the other mesh} \cite[][Sec.
@@
 \ref{fig:domain_sketch}.
-For a general setting, one can directly decompose the domain into tetrahedrons and constructs the Voronoi grid, but the procedure is more complicated and time-consuming and may not yield a valid dual mesh.
+For a general setting, one can directly decompose the domain into tetrahedrons and constructs the Voronoi grid, but the procedure is more complicated.
 The meshes for the cylindrical domain are displayed in Fig.
@@
 
-The geometric orthogonality between $L \leftrightarrow \Tilde{A}$ and $A \leftrightarrow \Tilde{L}$ is satisfied and will be a crucial property for approximating the material laws on the discrete level (which is the so-called Discrete Hodge operator \cite{hip_1999, bossavit1999}), as will be shown in Section \ref{sec:fit}.
+The geometric orthogonality between $L \leftrightarrow \Tilde{A}$ and $A \leftrightarrow \Tilde{L}$ is satisfied and will be a crucial property for approximating the material laws on the discrete level (which is the so-called discrete Hodge operator \cite{hip_1999, bossavit1999}), as will be shown in Section \ref{sec:fit}.
 
@@
 \textbf{(a)} A Delaunay-Voronoi grid in 2D.
-\textbf{(b)} The extrusion of 2D mesh.
+\textbf{(b)} A Cartesian case.
+\textbf{(c)} The extrusion of 2D mesh.
 Six triangle prisms are primal cells (depicted by black and gray edges).
@@
 The dashed hexagon represents the intersection of the dual cell and primal cells.
-\textbf{(c)} A Cartesian case.}
+}
     \label{fig:illustration_primal_dual}
@@
 
-This information can be captured by matrices with entries in $\{0,-1,+1\}$, called \emph{incidence matrices}.
+This information can be described by matrices with entries in $\{0,-1,+1\}$, called \emph{incidence matrices}.
 To describe the primal face-to-edge relation, for instance, a sparse matrix $\mathbb{C} \in \mathbb{R}^{N_A \times N_L}$ is assembled whose $(i,j)$-entry is assigned $+1$ if the internal orientation of edge $L_j$ and its induced orientation with respect to face $A_i$ coincides; it is assigned $-1$ if two orientations are opposite; and assigned $0$ if $L_j$ is not a subset of the boundary of $A_i$.
@@
 This framework was originally proposed in \cite{weiland_1977} and can be regarded as a generalization of Yee's FDTD method \cite{yee_1966}.
-To derive the discrete Maxwell model under FIT, we first integrate the (rescaled) Maxwell equations (\ref{equ:maxwell_faraday_rescaled})-(\ref{equ:maxwell_gauss_D_rescaled})
+To derive a discrete model for the (rescaled) Maxwell system (\ref{equ:maxwell_faraday_rescaled})-(\ref{equ:maxwell_gauss_D_rescaled}), we first take integrals
 \begin{subequations}
@@
 The material laws (\ref{equ:material_law}) need to be taken into account within this framework, that is, relations $\mathbf{b} = \mathbb{M}_\mu \mathbf{h}$ and $\mathbf{d} = \mathbb{M}_\epsilon \mathbf{e}$ with suitable \emph{material} matrices $\mathbb{M}_\mu, \mathbb{M}_\epsilon$.
-When permittivity $\mu$ and permeability $\epsilon$ are homogeneous in the domain and the orthogonality of the pair ($\mathcal{M}, \Tilde{\mathcal{M}}$) holds, the discrete material laws involve diagonal matrices with entries
+When the orthogonality of the pair ($\mathcal{M}, \Tilde{\mathcal{M}}$) holds, the discrete material only involve diagonal matrices with entries
 
@@
 By solving the Euler equations on $\Tilde{\mathcal{M}}$, we have the mass flux on dual faces $\Tilde{A}$ as well.
-In this way, the connection between the charge conservation (\ref{equ:charge_continuity}) and the mass conservation (the 1st equation in \ref{equ:euler_}) due to the current-momentum coupling (\ref{equ:maxwell_euler_coupling}) is preserved on the discrete level.
+In this way, the connection between the charge conservation (\ref{equ:charge_continuity}) and the mass conservation (the 1st equation in (\ref{equ:euler_})) due to the current-momentum coupling (\ref{equ:maxwell_euler_coupling}) is preserved on the discrete level.
 
@@
 
-The right-hand-side term in (\ref{equ:euler_matrix_form}) can be computed according to the rescaled Euler equations (\ref{equ:euler_rescaled}) with the reconstructed $\mathbf{E}$-field and $\mathbf{B}$-field by (\ref{equ:reconstruction}) defined in each dual cell.
+Therefore, the right-hand-side term in (\ref{equ:euler_matrix_form}) can be computed according to the rescaled Euler equations (\ref{equ:euler_rescaled}) with the reconstructed $\mathbf{E}$-field and $\mathbf{B}$-field by (\ref{equ:reconstruction}) defined in each dual cell.
 
@@
 7]{leveque_2007}, i.e.
-thinking of extending the domain by a few additional cells and prescribing the variables.
-In our case, the ghost cells at the open boundary at $\Gamma_C$ are set to have equal values as the interior ones that are adjacent.
+extending the domain by a layer of virtual cells with prescribed variables.
+In our case, the ghost cells at the open boundary at $\Gamma_C$ are assigned equal state as their adjacent interior cells.
 It is equivalent to enforcing the numerical fluxes
@@
 \end{equation}
-where the value of the ghost cell $\hat{\mathbf{U}}_l = [n, n\mathbf{u} - 2(\mathbf{n}\cdot\mathbf{u})\mathbf{n}, ne]^T$ reverses the normal velocity of $\mathbf{U}_l = [n, n\mathbf{u}, ne]^T$.
+where the state of the ghost cell $\hat{\mathbf{U}}_l = [n, n\mathbf{u} - 2(\mathbf{n}\cdot\mathbf{u})\mathbf{n}, ne]^T$ reverses the normal velocity of $\mathbf{U}_l = [n, n\mathbf{u}, ne]^T$.
 
@@
 We would like to stress again that in our FIT-FVM framework Faraday's law is discretized on $\mathcal{M}$ while Amp\`{e}re's law is discretized on $\Tilde{\mathcal{M}}$ for a simple approximation of material laws.
-By arranging the Euler system on $\Tilde{\mathcal{M}}$, the connection between electric currents and fluid momenta is naturally established on the discrete level since both are defined on the dual faces.
-
-\section{Full Discretization}
+By arranging the Euler system on $\Tilde{\mathcal{M}}$, the connection between electric currents and fluid momenta is naturally established and preserved in the discrete level since both are defined on the dual faces.
+
+\section{Full Discretization} \label{sec:full-discretization}
 \subsection{Motivation: Reduction to One Spatial Dimension}
@@
 
-\todo{Theorem: 1d projection to 1d discrete model?}
-
 \begin{remark}
     The AP scheme aims to remove the $\lambda$-dependence of the stability constraint on the time step size.
-Yet time-stepping of the discrete Euler system is still subject to the CFL condition due to its explicitness.
+Yet time-stepping of the discrete Euler system is still subject to the CFL condition due to the explicitness of the convection.
 \end{remark}
 
-\subsubsection{Linearly Semi-implicit Time-stepping}
+\subsubsection{Linearly Implicit Time-stepping}
 The semi-implicit scheme (\ref{equ:maxwell_faraday_ap})-(\ref{equ:Q_coll_ap}) entails solving a linear system for each time step.
@@
 \noindent \textbf{Step 1.} We establish the connection between $\mathbf{f}^{\text{mass},m+1/2}_*$ and $\mathbf{d}$ through the momentum equation (see (\ref{equ:euler_ap})(\ref{equ:flux_ap})(\ref{equ:rhs_ap})).
-Relying on the reconstruction (\ref{equ:reconstruction}), the following formula can be achieved
+Relying on the reconstruction (\ref{equ:reconstruction}), a formula of the following format can be achieved
 \begin{equation} \label{equ:relation_nu_and_d}
@@
 The expression for the current $\mathbf{J}^{m+1}$ in $\Omega_P$ (see (\ref{equ:maxwell_ampere_plasma_ap})) depends on the mass flux $\bm{f}^{\text{mass},{m+1}}_*$ which then relies on $(n\mathbf{u})_*^{m+1}$ through (\ref{equ:flux_ap}).
-One can formulate the following relation:
+Relying on (\ref{equ:relation_nu_and_d}), one can formulate the following relation:
 \begin{equation} \label{equ:discrete_ohm}
-    \mathbf{j}^{m+1} := \Sigma_\ast q_\ast \bm{f}^{n,m+1}_\ast = \mathbb{M}_\sigma^{m} \mathbf{d}^{m+1} + \mathbf{j}^m_{\text{aux}}.
+    \mathbf{j}^{m+1} := \Sigma_\ast q_\ast \bm{f}^{\text{mass},m+1}_\ast = \mathbb{M}_\sigma^{m} \mathbf{d}^{m+1} + \mathbf{j}^m_{\text{aux}}.
 \end{equation}
@@
     The formula (\ref{equ:discrete_ohm}) functions as Ohm's law on the discrete level.
-The $\mathbb{M}_\sigma^m$ can be treated as a ``conductivity" matrix.
-Since in the quasi-neutral limit $\lambda \rightarrow 0$ we lose control of the $\mathbf{E}$-field through its time derivative, $\mathbb{M}_\sigma^m$ is crucial to the stability of the scheme.
+Matrix $\mathbb{M}_\sigma^m$ can be treated as a ``conductivity" matrix.
+In the quasi-neutral limit $\lambda \rightarrow 0$ we lose control of the $\mathbf{E}$-field through its time derivative.
+Therefore, $\mathbb{M}_\sigma^m$ is crucial to the stability of the scheme.
 Since $\mathbf{j}$ and $\mathbf{d}$ are both defined on dual faces, it is reasonable to adopt a local relation between them.
@@
 First, the rotational symmetry of the problem is preserved.
-Second, the $\mathbf{E}$-field points from $\Gamma^+_C$ to $\Gamma^-_C$ with a relatively uniform value of approximately 0.2 ($=\text{applied voltage}/\text{cylinder length}$) as a consequence of the irrotational $\mathbf{E}$-field in the steady state according to Faraday's law.
-This is also confirmed in Fig.
-\ref{fig:zaxis-data_vs_z-T_10}.
-Note that it does not hold for $\lambda = 1$ since the system has a large characteristic time and takes a long time to reach an equilibrium, which will be shown later in Fig.
+Second, the $\mathbf{E}$-field points from $\Gamma^+_C$ to $\Gamma^-_C$ with a relatively uniform value of approximately 0.2 ($=\text{applied voltage}/\text{cylinder length}$) as a consequence of the irrotational $\mathbf{E}$-field in the steady state according to Faraday's law (which is also confirmed in Fig.
+\ref{fig:zaxis-data_vs_z-T_10}.) Note that it does not hold for $\lambda = 1$ since the system has a large characteristic time and takes a long time to reach an equilibrium, as will be shown later in Fig.
 \ref{fig:origin-data_vs_time}.
@@
 The capability of our approach to addressing the non-neutral ($\lambda = \mathcal{O}(1)$) and quasi-neutral ($\lambda = 0$) regimes has been demonstrated in the aforementioned results in the sense that it is stable under different values of $\lambda$.
-Another important check goes to the quasi-neutral condition, i.e.
-$\rho = 0$ (\ref{equ:maxwell_gauss_D_limit}) when $\lambda = 0$.
+Another important check goes to the quasi-neutral condition (\ref{equ:maxwell_gauss_D_limit}) when $\lambda = 0$.
 We display the $\mathbf{E}$-field and particle densities on the $z$-axis in Fig.
@@
 We have developed an AP scheme for the Euler-Maxwell plasma model in three spatial dimensions that is versatile in both non-neutral $\lambda = \mathcal{O}(1)$ and quasi-neutral $\lambda \rightarrow 0$ regimes.
-The main features of our work lie in: i) Maxwell's equations are discretized on primal and dual meshes by FIT (in the spirit of DEC).
+The main features of our work lie in: (i) Maxwell's equations are discretized on primal and dual meshes by FIT (in the spirit of DEC).
 By discretizing the Euler equations by FVM on dual mesh, the coupling of two systems is naturally realized via the connection of the mass flux and electric current at each dual face.
-ii) A non-conducting region is taken into account where additional stabilization is essential when $\lambda \rightarrow 0$.
+(ii) A non-conducting region is taken into account where additional stabilization is essential when $\lambda \rightarrow 0$.
 We enforce the vanishing divergence of the $\mathbf{D}$-field through a Lagrange multiplier for any value of $\lambda$.
-iii) The alignment of primal-dual meshes at the boundary entails cut-off cells and auxiliary unknowns have to be introduced.
+(iii) The alignment of primal-dual meshes at the boundary entails cut-off cells and auxiliary unknowns have to be introduced.
 iv) A lumping trick is applied to the conductivity matrix (relating the electric current and the electric field) to enhance stability.

### 2022-12-21 paper_version/main.tex
New abstract

@@
 \section*{Abstract}
-\todo{polish the abstract}
-
-\noindent\textbf{A short version:}
-
-The Debye length $\lambda_D$, as a key characteristic coefficient of plasmas, may range over many orders of magnitude.
+% \todo{polish the abstract}
+
+We elaborate a numerical method for a three-dimensional hydrodynamic multi-species plasma model which boils down to an extended Euler-Maxwell system.
+Our method is inspired by and extends the one-dimensional scheme from $[$P.~Degond, F.~Deluzet, and D.~Savelief, Numerical approximation of the Euler-Maxwell model in the quasineutral limit, Journal of Computational Physics, 231 (4), pp.~1917--1946, 2012$]$, it can cope with large variations of the so-called Debye length $\lambda_D$ and is robust in the quasi-neutral singular-perturbation limit $\lambda_D\to 0$, because it enjoys an \emph{asymptotic-preserving} (AP) property in the sense that in the sense that the limit $\lambda_D\to 0$ of the scheme yields a viable discretization for the continuous limit model.
+The key ingredients of our approach are (i) a discretization of Maxwell's equations based on primal and dual meshes in the spirit of \emph{discrete exterior calculus} (DEC) also known the finite integration technique (FIT), (ii) a finite volume method (FVM) for the fluid equations on the dual mesh, (iii) \emph{mixed implicit-explicit timestepping}, (iv) special no-flux and contact boundary conditions at an outer cut-off boundary, and (v) additional \emph{stabilization} in the non-conducting region outside the plasma domain based on direct enforcement of Gauss' law.
+Numerical tests provide strong evidence confirming the AP property of the new method.
+
+%The scheme is designed to be AP as $\lambda_D \rightarrow 0$ and this is validated through numerical experiments.
+Besides, if the electromagnetic fields have to be modelled in an non-conducting region beyond the plasma domain, additional stabilization to accommodate Gauss's law is necessary.
+
+%\noindent\textbf{A short version:}
+
+%The Debye length $\lambda_D$, as a key characteristic coefficient of plasmas, may range over many orders of magnitude.
 The induced singularly perturbed problem is a challenge for plasma simulations.
@@
 
-\noindent\textbf{A long version:}
-
-{\color{red}
-A key coefficient characterizing plasmas is the so-called Debye length $\lambda_D$, whose magnitude indicates to what extent net electric charges deviate from zero.
+%\noindent\textbf{A long version:}
+
+%{\color{red}
+%A key coefficient characterizing plasmas is the so-called Debye length $\lambda_D$, whose magnitude indicates to what extent net electric charges deviate from zero.
 It may range over many orders of magnitude: If $\lambda_D = \mathcal{O}(1)$ we face the non-neutral regime, while for $\lambda_D\to 0$ the plasma becomes quasi-neutral.
@@
 
-An asymptotic-preserving scheme for single- and multi-fluid Euler-Maxwell system was proposed by \cite{degond_2012} for one spatial dimension.
+%An asymptotic-preserving scheme for single- and multi-fluid Euler-Maxwell system was proposed by \cite{degond_2012} for one spatial dimension.
 We extend their scheme to three dimensions.
@@
 Besides, if the electromagnetic fields have to be modelled in an non-conducting region beyond the plasma domain, additional stabilization to accommodate Gauss's law is necessary.
-}
+%}
 

### 2022-12-21 paper_version/main.tex
Reformmatted abstract

@@
 
-We elaborate a numerical method for a three-dimensional hydrodynamic multi-species plasma model which boils down to an extended Euler-Maxwell system.
-Our method is inspired by and extends the one-dimensional scheme from $[$P.~Degond, F.~Deluzet, and D.~Savelief, Numerical approximation of the Euler-Maxwell model in the quasineutral limit, Journal of Computational Physics, 231 (4), pp.~1917--1946, 2012$]$, it can cope with large variations of the so-called Debye length $\lambda_D$ and is robust in the quasi-neutral singular-perturbation limit $\lambda_D\to 0$, because it enjoys an \emph{asymptotic-preserving} (AP) property in the sense that in the sense that the limit $\lambda_D\to 0$ of the scheme yields a viable discretization for the continuous limit model.
-The key ingredients of our approach are (i) a discretization of Maxwell's equations based on primal and dual meshes in the spirit of \emph{discrete exterior calculus} (DEC) also known the finite integration technique (FIT), (ii) a finite volume method (FVM) for the fluid equations on the dual mesh, (iii) \emph{mixed implicit-explicit timestepping}, (iv) special no-flux and contact boundary conditions at an outer cut-off boundary, and (v) additional \emph{stabilization} in the non-conducting region outside the plasma domain based on direct enforcement of Gauss' law.
-Numerical tests provide strong evidence confirming the AP property of the new method.
+We elaborate a numerical method for a three-dimensional hydrodynamic multi-species plasma
+model which boils down to an extended Euler-Maxwell system. Our method is inspired by and
+extends the one-dimensional scheme from $[$P.~Degond, F.~Deluzet, and D.~Savelief,
+Numerical approximation of the Euler-Maxwell model in the quasineutral limit, Journal of
+Computational Physics, 231 (4), pp.~1917--1946, 2012$]$, it can cope with large variations
+of the so-called Debye length $\lambda_D$ and is robust in the quasi-neutral
+singular-perturbation limit $\lambda_D\to 0$, because it enjoys an
+\emph{asymptotic-preserving} (AP) property in the sense that in the sense that the limit
+$\lambda_D\to 0$ of the scheme yields a viable discretization for the continuous limit
+model. The key ingredients of our approach are (i) a discretization of Maxwell's equations
+based on primal and dual meshes in the spirit of \emph{discrete exterior calculus} (DEC)
+also known the finite integration technique (FIT), (ii) a finite volume method (FVM) for
+the fluid equations on the dual mesh, (iii) \emph{mixed implicit-explicit timestepping},
+(iv) special no-flux and contact boundary conditions at an outer cut-off boundary, and (v)
+additional \emph{stabilization} in the non-conducting region outside the plasma domain
+based on direct enforcement of Gauss' law. Numerical tests provide strong evidence
+confirming the AP property of the new method.
 

### 2022-12-21 paper_version/main.tex
Edited Sections 1-2

@@
 extends the one-dimensional scheme from $[$P.~Degond, F.~Deluzet, and D.~Savelief,
-Numerical approximation of the Euler-Maxwell model in the quasineutral limit, Journal of
-Computational Physics, 231 (4), pp.~1917--1946, 2012$]$, it can cope with large variations
+\emph{Numerical approximation of the Euler-Maxwell model in the quasineutral limit}, Journal of
+Computational Physics, 231 (4), pp.~1917--1946, 2012$]$. It can cope with large variations
 of the so-called Debye length $\lambda_D$ and is robust in the quasi-neutral
@@
 % \mycomment{Roman: more info from a physical point of view?} R.H. 19.12. Extended paragraph
-The starting point for this work was the desire to numerically simulate the formation and evolution of electric arcs at atmospheric pressures.
-We rely on a widely accepted description by means of a hydrodynamic multi-species plasma model, which boils down to the Maxwell-Euler system.
-The arc phenomenon covers a wide range of plasma regimes and the numerical model should be able to deal with all of them seamlessly and simultaneously.
-Thus in this work, as in \cite{degond_2012}, the focus is on \emph{asymptotic-preserving} (AP) discretization in the quasi-neutral limit $\lambda \rightarrow 0$, where $\lambda$ is the rescaled Debye length, see Section \ref{sec:rescaling} for the underlying scaling arguments and \cite{degond_2012,degond_2017} for a discussion of the importance of the AP property of numerical plasma models.
+The starting point for this work was the desire to numerically simulate the formation and
+evolution of electric arcs at atmospheric pressures. Following common practise, we rely on
+a mathematical description by means of a hydrodynamic multi-species plasma model, which
+boils down to an extended Maxwell-Euler system. The arc phenomenon covers a wide range of
+plasma regimes and, thus, the design goal was a numerical model capable of dealing
+with all of them seamlessly and simultaneously. Thus in this work, as in
+\cite{degond_2012}, the focus is on \emph{asymptotic-preserving} (AP) discretization in
+the quasi-neutral limit $\lambda \rightarrow 0$, where $\lambda$ is the rescaled Debye
+length, see Section \ref{sec:rescaling} for the underlying scaling arguments and
+\cite{degond_2012,degond_2017} for a discussion of the importance of the AP property of
+numerical plasma models.
 
@@
 \item We supplement the Maxwell-Euler system by inter-species friction terms.
-    \item We extend the spatially one-dimensional scheme of \cite{degond_2012} to three spatial dimensions using discrete exterior calculus (DEC) to discretize Maxwell's equations combined with a low-order finite volume method for Euler's equations.
-    \item We propose a stabilization in non-conducting regions which is essential for the efficacy of our method.
+\item We extend the spatially one-dimensional scheme of \cite{degond_2012} to three
+  spatial dimensions using discrete exterior calculus (DEC) to discretize Maxwell's
+  equations combined with a low-order finite volume method for Euler's equations.
+\item We propose a stabilization in non-conducting regions which is essential for the
+  efficacy of our method.
 \end{itemize}
 
-We stay close to \cite{degond_2012} in terms of discretization in time employing semi-implicit time-stepping.
-We also base our considerations on the model geometry shown in Fig.
-\ref{fig:domain_geometry}.
-We would like to remark that the mesh-based numerical scheme proposed in this paper can in principle be adapted to geometric situations much more general than that of Fig.
-\ref{fig:domain_geometry}.
-However, one may encounter subtle problems in defining proper dual meshes as we need it in Section \ref{sec:mesh-duality}.
-Thus, for the sake of simplicity of presentation we forgo geometric generality.
-
-The quasi-neutral limit of the Maxwell-Euler system leads to a singularly perturbed problem, that is, the limiting PDE system changes its type\footnote{The Maxwell-Euler system transits from hyperbolic to a mixed type}.
-This poses a challenge for simulations in settings encompassing different regimes.
-Singularly perturbed problems occur in many physical models, e.g.
-vanishing viscosity in the Navier-Stokes equations \cite{Kato_1984}, zero-relaxation-limit of kinetic equations \cite{jin_2010} and zero-Mach-limit of compressible flows \cite{degond_2007, haack_2010}.
-It is desirable that numerical schemes are valid for all ranges of scaled parameters.
-These schemes are then said to be \emph{asymptotic-preserving} (AP).
-We discretize a parametric problem $P^\lambda$, which converges to its limit $P^0$ as the perturbed parameter $\lambda \rightarrow 0$, by the scheme $P^\lambda_h$ where $h$ denotes some discretization parameter, e.g.
-the mesh size, see also the illustration by a commuting diagram in \cite[][Fig.
-1]{jin_2010}.
-The AP property requires the uniform convergence of $P^\lambda_h$ to the $P^\lambda$ as $\lambda\rightarrow0$.
-Readers are referred to the comprehensive reviews in \cite{jin_2010, degond_2017} for more details about AP schemes.
-
-The content of this paper is organized as follows: In Section \ref{sec:plasma-model}, we give a full description of the underlying equations of the Maxwell-Euler system and its rescaling procedure.
-Meanwhile, the boundary conditions in our setting is elaborated.
-A reformulation of Maxwell's equations in the non-conducting region is presented.
-Section \ref{sec:spatial_discretization} is devoted to the spatial discretization.
-The concept of primal-dual meshes is introduced based on which FIT and FVM are utilized.
-We discuss the full AP discretization in Section \ref{sec:full-discretization} and do numerical experiments in Section \ref{sec:numerical_experiment}.
+We stay close to \cite{degond_2012} in terms of discretization in time employing
+semi-implicit time-stepping. We also base our considerations on the model geometry shown
+in Fig. \ref{fig:domain_geometry}. We would like to remark that the mesh-based numerical
+scheme proposed in this paper can in principle be adapted to geometric situations much
+more general than that of Fig. \ref{fig:domain_geometry}. However, one may encounter
+subtle problems in defining proper dual meshes as we need it in Section
+\ref{sec:mesh-duality}. Thus, for the sake of simplicity of presentation we forgo
+geometric generality.
+
+The quasi-neutral limit of the Maxwell-Euler system leads to a singularly perturbed
+problem, that is, the limiting PDE system changes its type\footnote{The type of the
+  Maxwell-Euler system switches from hyperbolic to mixed for $\lambda_{D}\to 0$}. This
+poses a challenge for simulations in settings encompassing different regimes. We remind
+that singularly perturbed problems occur in many physical models, e.g., in the case of
+vanishing viscosity in the Navier-Stokes equations \cite{Kato_1984}, the
+zero-relaxation-limit of kinetic equations \cite{jin_2010}, and the zero-Mach-number limit
+of compressible flows \cite{degond_2007, haack_2010}. Throughout, it is essential that
+numerical schemes remain valid even if crucial model parameters approach the limit. These
+schemes are then said to be \emph{asymptotic-preserving} (AP): Let us assume that we
+discretize a parameter($\lambda$)-dependent model $P^\lambda$, which converges to a limit
+$P^0$ as $\lambda \rightarrow 0$, by the scheme $P^\lambda_h$ where $h$ denotes some
+discretization parameter, e.g., the mesh size. The AP property amounts to uniform
+convergence of $P^\lambda_h$ to the $P^\lambda$ as $\lambda\rightarrow0$. Readers are
+referred to the illustration by a commuting diagram in \cite[][Fig. 1]{jin_2010} and, more
+generally, to the comprehensive reviews \cite{jin_2010, degond_2017} for more details
+about AP schemes.
+
+The content of this paper is organized as follows: In Section \ref{sec:plasma-model}, we
+give a full description of the underlying equations of the Maxwell-Euler system and its
+rescaling procedure. Meanwhile, the boundary conditions in our setting is elaborated. A
+reformulation of Maxwell's equations in the non-conducting region is presented. Section
+\ref{sec:spatial_discretization} is devoted to the spatial discretization. The concept of
+primal-dual meshes is introduced based on which FIT and FVM are utilized. We discuss the
+full AP discretization in Section \ref{sec:full-discretization} and do numerical
+experiments in Section \ref{sec:numerical_experiment}.
 
@@
     \centering
-    \begin{tikzpicture}
+    \begin{tikzpicture}[scale=1.2]
     \coordinate (O1) at (0,0);
@@
     \end{tikzpicture}
-\caption{The domain geometry}
+    \caption{The special geometric setting suggested by the simulation of electric arcs,
+      for which we discuss the new method.}
 \label{fig:domain_geometry}
@@
 \subsection{The Maxwell-Euler System}
-Plasmas consist of electrically charged and (possibly) neutral particle species that can be treated as fluids.
-That is, they may be described by the Navier-Stokes equations augmented with source terms for species generation (ionization, recombination), forces (Lorentz force and interspecies friction), and energy (thermal relaxation among species, radiative heat transfer, Ohmic heating).
-For more details on fluid models of plasmas, see \cite{chen2016, remi_2014}.
+
+Plasmas consist of electrically charged and (possibly) neutral particle species and we
+suppose that they can be treated as continua (fluids). That is, they may be described by the
+Navier-Stokes equations augmented with source terms for species generation (ionization,
+recombination), forces (Lorentz force and interspecies friction), and energy (thermal
+relaxation among species, radiative heat transfer, Ohmic heating). For more details on
+fluid models of plasmas, see \cite{chen2016, remi_2014}.
 
@@
 \end{subequations}
-where the involved quantities\footnote{SI units in square brackets.} are the magnetic flux density $\mathbf{B}[\frac{\text{Wb}}{\text{m}^2}]$, the electric field $\mathbf{E}[\frac{\text{V}}{\text{m}}]$, the electric displacement field $\mathbf{D}[\frac{\text{C}}{\text{m}^2}]$, the magnetic field $\mathbf{H}[\frac{\text{A}}{\text{m}}]$, the electric current density $\mathbf{J}[\frac{\text{A}}{\text{m}^2}]$ and the electric charge density $\rho[\frac{\text{C}}{\text{m}^3}]$.
-These equations are known as Faraday's law (\ref{equ:maxwell_faraday}), Amp\`{e}re's law (\ref{equ:maxwell_ampere}), Gauss's law for magnetism (\ref{equ:maxwell_gauss_B}) and Gauss's law for electric field (\ref{equ:maxwell_gauss_D}).
-For simplicity, we only consider isotropic and homogeneous media.
-Namely, we rely on linear constitutive relations (i.e.
-material laws):
+where the involved quantities\footnote{SI units in square brackets.} are the magnetic flux
+density $\mathbf{B}[\frac{\text{Wb}}{\text{m}^2}]$, the electric field
+$\mathbf{E}[\frac{\text{V}}{\text{m}}]$, the electric displacement field
+$\mathbf{D}[\frac{\text{C}}{\text{m}^2}]$, the magnetic field
+$\mathbf{H}[\frac{\text{A}}{\text{m}}]$, the electric current density
+$\mathbf{J}[\frac{\text{A}}{\text{m}^2}]$ and the electric charge density
+$\rho[\frac{\text{C}}{\text{m}^3}]$. These equations are known as Faraday's law
+(\ref{equ:maxwell_faraday}), Amp\`{e}re's law (\ref{equ:maxwell_ampere}), Gauss's law for
+magnetism (\ref{equ:maxwell_gauss_B}) and Gauss's law for electric field
+(\ref{equ:maxwell_gauss_D}). For simplicity, we only consider isotropic and homogeneous
+media. Namely, we rely on linear constitutive relations (material laws):
 \begin{equation} \label{equ:material_law}
-    \mathbf{D} = \epsilon \mathbf{E}, \ \ \ \mathbf{B} = \mu\mathbf{H}, 
+    \mathbf{D} = \epsilon \mathbf{E}\quad,\quad\mathbf{B} = \mu\mathbf{H}, 
 \end{equation}
-where $\epsilon[\frac{\text{F}}{\text{m}}]$ and $\mu[\frac{\text{N}}{\text{A}^{2}}]$ are the permittivity and permeability and assumed to be constant.
-By taking the time derivative of (\ref{equ:maxwell_gauss_D}) and the divergence of (\ref{equ:maxwell_ampere}), it is easy to see that (\ref{equ:maxwell_ampere}) and (\ref{equ:maxwell_gauss_D}) implies the charge conservation
+where $\epsilon[\frac{\text{F}}{\text{m}}]$ and $\mu[\frac{\text{N}}{\text{A}^{2}}]$ are
+the permittivity and permeability and assumed to be constant. By taking the time
+derivative of (\ref{equ:maxwell_gauss_D}) and the divergence of
+(\ref{equ:maxwell_ampere}), it is easy to see that (\ref{equ:maxwell_ampere}) and
+(\ref{equ:maxwell_gauss_D}) implies the charge conservation
 \begin{equation} \label{equ:charge_continuity}
@@
 \end{equation}
-Besides, by taking the divergence of equations (\ref{equ:maxwell_faraday}) and (\ref{equ:maxwell_ampere}) together with the relation (\ref{equ:charge_continuity}), it is possible to verify that Gauss's laws (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) are consequences of (\ref{equ:maxwell_faraday}) and (\ref{equ:maxwell_ampere}) provided that (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) are satisfied at initial time.
-In other words, Gauss's laws (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) can be thought of as initial conditions.
-
-Each species in a plasma can be modelled as a compressible fluid through a set of Euler equations augmented by electromagnetic forces as well as other processes, e.g. collisions and recombination:
+Besides, by taking the divergence of equations (\ref{equ:maxwell_faraday}) and
+(\ref{equ:maxwell_ampere}) together with the relation (\ref{equ:charge_continuity}), it is
+possible to verify that Gauss's laws (\ref{equ:maxwell_gauss_B})
+(\ref{equ:maxwell_gauss_D}) are consequences of (\ref{equ:maxwell_faraday}) and
+(\ref{equ:maxwell_ampere}) provided that (\ref{equ:maxwell_gauss_B})
+(\ref{equ:maxwell_gauss_D}) are satisfied at initial time. In other words, Gauss's laws
+(\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) can be thought of as initial
+conditions.
+
+We model each species in the plasma as a compressible fluid through a set of \emph{Euler
+  equations} augmented by electromagnetic forces as well as other processes,
+e.g. collisions and recombination:
 \begin{align} \label{equ:euler_}
@@
 \end{align}
-The subscript $*\in \{e, i, \cdots\}$ labels electrons, ions or other species.
-The involved fluid quantities are: number density $n_*[\frac{1}{\text{m}^3}]$, particle mass $m_*[\text{kg}]$,  electric charge $q_*[\text{C}]$, velocity $\mathbf{u}_*[\frac{\text{m}}{\text{s}}]$, pressure $p_*[\frac{\text{N}}{\text{m}^2}]$, specific total energy $e_* := \frac{1}{2}|\mathbf{u}_*|^2 + \frac{p_*}{m_*n_*(\gamma - 1)}[\frac{\text{J}}{\text{kg}}]$, specific total enthalpy $h_* := e_* + \frac{p_*}{m_*n_*}[\frac{\text{J}}{\text{kg}}]$ and current density $\mathbf{J}_* := q_*n_*\mathbf{u}_*[\frac{\text{A}}{\text{m}^2}]$.
-All the species are assumed to be ideal gases with heat capacity ratio $\gamma=5/3$ for monatomic gases.
-The left-hand side of the equations describes the convection of plasma fluids.
-The first term at the right-hand side takes into account the Lorentz force in the momentum equation and Joule heating in the energy equation.
-$\Gamma_*, \mathbf{R}_*, Q_*$ are generic terms due to effects of inter-species collision, ionization, recombination, etc.
-
-For the sake of simplicity, we only consider ion-electron collision in this work, but extension to more species is straightforward.
-Such collisions can be well modelled by friction terms (\citep[][Sec.
-5.6.2]{chen2016})
+The subscript $*\in \{e, i, \cdots\}$ labels electrons, ions or other species. The
+involved fluid quantities are: number density $n_*[\frac{1}{\text{m}^3}]$, particle mass
+$m_*[\text{kg}]$, electric charge $q_*[\text{C}]$, velocity
+$\mathbf{u}_*[\frac{\text{m}}{\text{s}}]$, pressure $p_*[\frac{\text{N}}{\text{m}^2}]$,
+specific total energy
+$e_* := \frac{1}{2}|\mathbf{u}_*|^2 + \frac{p_*}{m_*n_*(\gamma -
+  1)}[\frac{\text{J}}{\text{kg}}]$, specific total enthalpy
+$h_* := e_* + \frac{p_*}{m_*n_*}[\frac{\text{J}}{\text{kg}}]$ and current density
+$\mathbf{J}_* := q_*n_*\mathbf{u}_*[\frac{\text{A}}{\text{m}^2}]$. All species are
+assumed to be ideal gases with heat capacity ratio $\gamma=5/3$ for monatomic gases. The
+left-hand side of the equations describes the convection of plasma fluids. The first term
+at the right-hand side takes into account the Lorentz force in the momentum equation and
+Joule heating in the energy equation. $\Gamma_*, \mathbf{R}_*, Q_*$ are generic terms due
+to effects of inter-species collision, ionization, recombination, etc.
+
+Combining the two sets of equations (\ref{equ:maxwell_faraday}) to
+(\ref{equ:maxwell_gauss_D}) and (\ref{equ:euler_}) leads to the governing equations for a
+multi-species plasma model. The coupling of the two subsystems is due to the fact that the
+flow of charged particles induces electric currents:
+\begin{equation} \label{equ:maxwell_euler_coupling}
+    \rho = \sum_* q_*n_*\;, \quad \mathbf{J} = \sum_* q_*n_*\mathbf{u}_*. 
+\end{equation}
+
+\begin{remark}
+  \label{rem:coll}
+  For the sake of simplicity, we only consider ion-electron collision in this work, but
+extension to more species is straightforward. Such collisions can be well modelled by
+friction terms, for instance \citep[][Sec. 5.6.2]{chen2016}
 \begin{equation} \label{equ:collision}
@@
 \end{equation}
-which is the collision force acting on electrons.
-ln$\Lambda$ is called the \emph{Coulomb logarithm} and is usually taken as a constant \cite{chen2016}.
-Because of the conservation of momentum, the collision term for ions $\mathbf{R}_{i}^{\text{coll}}$ is nothing but the negative of $\mathbf{R}_{e}^{\text{coll}}$.
-In this work, the other effects, e.g.
-ionization and recombination, are not considered.
-For full details about the modeling of these physical processes, readers are referred to \cite[][Sec.
-3.2]{fuchs_2021}.
-
-Combination of the two sets of equations (\ref{equ:maxwell_faraday}) to (\ref{equ:maxwell_gauss_D}) and (\ref{equ:euler_}) leads to the governing equations for a multi-species plasma model.
-The coupling of the two subsystems is due to the fact that the flow of charged particles induces electric currents:
-\begin{equation} \label{equ:maxwell_euler_coupling}
-    \rho = \sum_* q_*n_*, \ \ \  \mathbf{J} = \sum_* q_*n_*\mathbf{u}_*. 
-\end{equation}
-
-\subsection{Rescaling} \label{sec:rescaling}
-In rescaling, variables in equations are replaced by the ratio of original quantities and constant reference quantities, which transforms the system into dimensionless form.
+which is the collision force acting on electrons. ln$\Lambda$ is called the \emph{Coulomb
+  logarithm} and is usually taken as a constant \cite{chen2016}. Because of the
+conservation of momentum, the collision term for ions $\mathbf{R}_{i}^{\text{coll}}$ is
+nothing but the negative of $\mathbf{R}_{e}^{\text{coll}}$. In this work, the other
+effects, e.g. ionization and recombination, are not considered. For full details about the
+modeling of these physical processes, readers are referred to
+\cite[][Sec. 3.2]{fuchs_2021}.
+\end{remark}
+
+\subsection{Rescaling}
+\label{sec:rescaling}
+% In rescaling, variables in equations are replaced by the ratio of original quantities and constant reference quantities, which transforms the system into dimensionless form.
 In this part, the rescaling procedure mostly follows that of \cite[][Sec.
@@
 
-First, a reference value for each quantity is prescribed.
-We define $\overline{x}$ and $\overline{t}$ as space and time scale of interest, by which the reference velocity $\overline{v}$ is defined as $\overline{x}/\overline{t}$.
-The typical magnitudes of electromagnetic fields are $\overline{E}$ and $\overline{B}$.
-The reference magnitudes of fluid quantities are denoted by $\overline{u}$ for plasma drift velocity, $\overline{n}$ for plasma number density, $\overline{T}$ for plasma temperature.
-On top of that, the reference pressure is set to $\overline{n}k_B\overline{T}$ with $k_B$ being the Boltzmann constant; the reference value for the specific total energy and enthalpy is set to $\overline{u}^2$.
-Also taking into account the physical constants, i.e.
-the reference permittivity $\overline{\epsilon}$, the reference permeability $\overline{\mu}$, the light speed $c^2 = (\overline{\epsilon}\overline{\mu})^{-1}$, Boltzmann constant $k_B$, the elementary charge $e$, and ion mass $m_i$, we introduce the following dimensionless parameters:
+We arrive at non-dimensional equations by following the rescaling procedure of
+\cite[][Sec. 2.2]{degond_2017}.  First, a reference value for each quantity is
+prescribed. We define $\overline{x}$ and $\overline{t}$ as space and time scale of
+interest, by which the reference velocity $\overline{v}$ is defined as
+$\overline{x}/\overline{t}$. The typical magnitudes of electromagnetic fields are
+$\overline{E}$ and $\overline{B}$. The reference magnitudes of fluid quantities are
+denoted by $\overline{u}$ for plasma drift velocity, $\overline{n}$ for plasma number
+density, $\overline{T}$ for plasma temperature. On top of that, the reference pressure is
+set to $\overline{n}k_B\overline{T}$ with $k_B$ being the Boltzmann constant; the
+reference value for the specific total energy and enthalpy is set to
+$\overline{u}^2$. Also taking into account the physical constants, i.e. the reference
+permittivity $\overline{\epsilon}$, the reference permeability $\overline{\mu}$, the light
+speed $c^2 = (\overline{\epsilon}\overline{\mu})^{-1}$, Boltzmann constant $k_B$, the
+elementary charge $e$, and ion mass $m_i$, we introduce the following dimensionless
+parameters:
 \begin{align*} 
@@
 
-By abuse of notation, the rescaled variables share the same notation as before rescaling.
-We neglect ionization and recombination but retain collision terms, i.e.
-$\Gamma_* = 0, \mathbf{R}_* = \mathbf{R}_*^\text{coll}, Q_* = Q_*^\text{coll}$ in (\ref{equ:euler_}).
-The rescaled Euler-Maxwell system is
+By abuse of notation, the rescaled variables share the same notation as before
+rescaling. We neglect ionization and recombination but retain collision terms,
+i.e. $\Gamma_* = 0, \mathbf{R}_* = \mathbf{R}_*^\text{coll}, Q_* = Q_*^\text{coll}$ in
+(\ref{equ:euler_}). The rescaled Euler-Maxwell system is
 \begin{subequations}
@@
 \end{subequations}
-where the equation of state becomes $e_* = \frac{1}{2}|\mathbf{u_*}|^2 + M^{-2}\frac{p_*}{\epsilon^2_* n_* (\gamma - 1)}$ and $h_* = e_* + M^{-2}\frac{p_*}{\epsilon^2_* n_*}$.
-For a fully-ionized gas, we have the original expression of $\mathbf{R}_*^{\text{coll}}$ in (\ref{equ:collision}), and its rescaled expression becomes
+where the equation of state becomes
+$e_* = \frac{1}{2}|\mathbf{u_*}|^2 + M^{-2}\frac{p_*}{\epsilon^2_* n_* (\gamma - 1)}$ and
+$h_* = e_* + M^{-2}\frac{p_*}{\epsilon^2_* n_*}$. For a fully-ionized gas, we have the
+original expression of $\mathbf{R}_*^{\text{coll}}$ in (\ref{equ:collision}), and its
+rescaled expression becomes
 \begin{equation}
@@
 
- Assumptions can be made to reduce the number of dimensionless parameters.
-Following \cite[][Sec.
-2.2]{degond_2017}, the reference speed $\overline{v}$ is of the same scale as the plasma speed $\overline{u}$ and the thermal speed $v_i^{\text{th}}$ whereas it is much smaller than the light speed $c$.
-Also, it is assumed that $\eta$ and $\beta$ are of order one and $\xi$ has the same magnitude as $\lambda$.
-
-Special treatment is needed for the collision term.
-One could argue that the occurrence of $\lambda^{-1}$ in (\ref{equ:rescaling_friction}) could lead to singular perturbation of the Euler system as $\lambda \rightarrow 0$.
-However, the validity of such a collision model is doubtful when $\lambda \rightarrow 0$.
-From the physical viewpoint, the shielding effect characterized by the rescaled Debye length $\lambda$ makes the impact parameter no larger than $\lambda$.
-The $\lambda \rightarrow 0$ limit implies that the collisions happen in the atomic length scale, in which quantum-mechanical effects must be taken into effect \cite[][pp.
-144-148]{frank_1972}.
-Therefore, we eliminate the perturbation parameter in the friction term by assuming $g \sim \lambda$ and keep the prefactor $\alpha^{\text{coll}}$ of the collision term constant throughout the simulation.
+Assumptions can be made to reduce the number of dimensionless parameters. Following
+\cite[][Sec. 2.2]{degond_2017}, the reference speed $\overline{v}$ is of the same scale as
+the plasma speed $\overline{u}$ and the thermal speed $v_i^{\text{th}}$ whereas it is much
+smaller than the light speed $c$. Also, it is assumed that $\eta$ and $\beta$ are of order
+one and $\xi$ has the same magnitude as $\lambda$.
 
 \begin{remark}
-    The case when there is an asymptotic parameter at the denominator of the friction term is of interest, too.
-Such problem is called relaxation limit, see \cite{peng_2011, wasiolek_2016, Li_2021, Chen_2000}.
+Special treatment is needed for the collision term. One could argue that the occurrence of
+$\lambda^{-1}$ in (\ref{equ:rescaling_friction}) could lead to singular perturbation of
+the Euler system as $\lambda \rightarrow 0$. However, the validity of such a collision
+model is doubtful when $\lambda \rightarrow 0$. From the physical viewpoint, the shielding
+effect characterized by the rescaled Debye length $\lambda$ limits the impact parameters
+to values $\sim\lambda$. The $\lambda \rightarrow 0$ limit implies that the collisions
+happen on the atomic length scale, in which quantum-mechanical effects must be taken into
+account \cite[][pp. 144-148]{frank_1972}. Therefore, we eliminate the perturbation
+parameter in the friction term by assuming $g \sim \lambda$ and keep the prefactor
+$\alpha^{\text{coll}}$ of the collision term constant throughout the simulation.
+
+The case when there is an asymptotic parameter in the denominator of the friction term is
+of interest, too. This situation is known as relaxation limit, see \cite{peng_2011,
+  wasiolek_2016, Li_2021, Chen_2000}.
 \end{remark}
@@
 \end{align*}
-
-Under such assumptions on these dimensionless parameters, the rescaled Euler-Maxwell system is simplified to a system of PDEs with the dimensionless Debye length $\lambda$ as asymptotic ($\lambda \rightarrow 0$) parameter
+Assuming this behavior of the dimensionless parameters, the rescaled Euler-Maxwell system
+is simplified to a system of PDEs with the dimensionless \emph{Debye length} $\lambda$ as
+single parameter, whose value may tend to zero:
 \begin{subequations}
+  \label{resc}
 \begin{align}
@@
 \end{align}
-
-with the equation of state $e_* = \frac{1}{2}|\mathbf{u_*}|^2 + \frac{p_*}{\varepsilon^2_* n_* (\gamma - 1)}$ and $h_* = e_* + \frac{p_*}{\varepsilon^2_* n_*}$.
-For a fully-ionized gas with only ions and electrons,
+with the equation of state
+$e_* = \frac{1}{2}|\mathbf{u_*}|^2 + \frac{p_*}{\varepsilon^2_* n_* (\gamma - 1)}$ and
+$h_* = e_* + \frac{p_*}{\varepsilon^2_* n_*}$. For a fully-ionized gas with only ions and
+electrons,
 \begin{equation} \label{equ:collision_rescaled} 
@@
 \end{equation}
-and consequently, the rescaled friction heat for ions and electrons take the expression:
+and consequently, the rescaled friction heat for ions and electrons take the form:
 \begin{align} 
@@
 \end{align}
-The rescaled material laws (\ref{equ:material_law}) keep the same expressions: 
+The rescaled material laws (\ref{equ:material_law}) are still given by 
 \begin{equation} \label{equ:maxwell_material_law_rescaled}
-    \mathbf{D} = \epsilon \mathbf{E}, \ \ \ \mathbf{B} = \mu \mathbf{H}. 
+    \mathbf{D} = \epsilon \mathbf{E}, \ \ \ \mathbf{B} = \mu \mathbf{H}, 
 \end{equation}
 \end{subequations}
-Notice here $\epsilon, \mu$ are the rescaled permittivity and permeability.
-
-We end up with the rescaled Maxwell-Euler system: (\ref{equ:maxwell_faraday_rescaled})-(\ref{equ:maxwell_material_law_rescaled}) parameterized by $\lambda$.
-
-\subsection{Quasi-neutral Limit} \label{sec:quasi-neutral_limit}
-The Debye length $\lambda_D$ (see its definition in the preceding section) is the characteristic length over which local net charge is shielded, see \cite[Sec.
-1.4]{chen2016} for the underlying physics.
-In many situations, it has a rather low value compared to the reference length scale: the typical $\lambda_D$ for gas discharge and Tokamak is $10^{-4}$ meter; for interstellar medium, the magnitude is about $1$ meter \cite[Ch.
-20]{Blandford_2013}.
-That justifies the quasi-neutrality assumption that the plasma is quasi-neutral, i.e.
-$\rho = \sum_* q_*n_* \approx 0$.
-The limit model is obtained by formally setting the rescaled Debye length $\lambda$ to zero:
-\vspace{-\baselineskip}
+with rescaled permittivity $\epsilon$ and permeability $\mu$, however. The
+$\lambda$-parameterized rescaled Maxwell-Euler system
+(\ref{equ:maxwell_faraday_rescaled})-(\ref{equ:maxwell_material_law_rescaled}) is the
+starting point for the development of the numerical method.
+
+\subsection{Quasi-neutral Limit}
+\label{sec:quasi-neutral_limit}
+
+The Debye length $\lambda_D$ is the characteristic length over which local net charge is
+shielded, see \cite[Sec. 1.4]{chen2016} for the underlying physics. In many situations, it
+has a very small value compared to the reference length scale: the typical $\lambda_D$ for
+gas discharge and Tokamak fusion reactors is $10^{-4}$ meter, for interstellar medium, the
+magnitude is about $1$ meter \cite[Ch. 20]{Blandford_2013}. Then the quasi-neutrality
+assumption $\rho = \sum_* q_*n_* \approx 0$ is justified, which yields the limit model,
+formally obtained by setting the rescaled Debye length $\lambda$ to zero in \eqref{resc}:
 \begin{center}
@@
 \end{document}
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: t
+%%% End:

### 2022-12-21 paper_version/main.tex
Edited Sections 2 & 3

@@
     \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday_rescaled} \\ 
-    \lambda^2 \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= - \mathbf{J}, \label{equ:maxwell_ampere_rescaled} \\
+    \colorbox{yellow!30}{$\displaystyle\lambda^2$} \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= - \mathbf{J}, \label{equ:maxwell_ampere_rescaled} \\
     \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B_rescaled}\\
-    \lambda^2 \nabla \cdot \mathbf{D} &= \rho, \label{equ:maxwell_gauss_D_rescaled} \\
+    \colorbox{yellow!30}{$\displaystyle\lambda^2$} \nabla \cdot \mathbf{D} &= \rho, \label{equ:maxwell_gauss_D_rescaled} \\
     \partial_t
@@
 magnitude is about $1$ meter \cite[Ch. 20]{Blandford_2013}. Then the quasi-neutrality
-assumption $\rho = \sum_* q_*n_* \approx 0$ is justified, which yields the limit model,
-formally obtained by setting the rescaled Debye length $\lambda$ to zero in \eqref{resc}:
+assumption $\rho = \sum_* q_*n_* \approx 0$ is justified, which is typical of the limit
+model.  Formally we obtain it by setting the rescaled Debye length $\lambda$ to zero in
+\eqref{resc}:
 \begin{center}
@@
   \begin{subequations}
+    \label{limit}
 \begin{align}
@@
 \end{center}
-The quasi-neutral condition (\ref{equ:maxwell_gauss_D_limit}) is the consequence of setting $\lambda = 0$ in Gauss's law for the electric field (\ref{equ:maxwell_gauss_D_rescaled}).
-As in the non-neutral case, Gauss's laws (\ref{equ:maxwell_gauss_B_limit}) (\ref{equ:maxwell_gauss_D_limit}) are the consequence of (\ref{equ:maxwell_faraday_limit}) (\ref{equ:maxwell_ampere_limit}) provided (\ref{equ:maxwell_gauss_B_limit}) (\ref{equ:maxwell_gauss_D_limit}) are satisfied at initial time.
-
-This limit represents a \emph{singular perturbation problem} in the sense that vanishing $\lambda$ changes the character of the PDE system.
-To be more specific, for $\lambda = \mathcal{O}(1)$ the $\mathbf{E}$-field evolves with time whereas in the quasi-neutral model it responds instantaneously to other quantities according to the constraint (\ref{equ:maxwell_ampere_limit}).
-We replace (\ref{equ:maxwell_ampere_rescaled}) by the sum of the rotation of (\ref{equ:maxwell_faraday_rescaled}) and the time-derivative of (\ref{equ:maxwell_ampere_rescaled}).
-Meanwhile, due to the link between fluid momenta $n_*u_*$ and current in (\ref{equ:maxwell_euler_coupling}), the term $\partial_t\mathbf{J}$ can be reformulated by the momentum equation according to (\ref{equ:euler_rescaled}) and we end up with the following wave equation with source terms:
+The quasi-neutrality condition (\ref{equ:maxwell_gauss_D_limit}) is the consequence of
+setting $\lambda = 0$ in Gauss's law for the electric field
+(\ref{equ:maxwell_gauss_D_rescaled}). As in the non-neutral case, Gauss's laws
+(\ref{equ:maxwell_gauss_B_limit}) (\ref{equ:maxwell_gauss_D_limit}) are the consequence of
+(\ref{equ:maxwell_faraday_limit}) (\ref{equ:maxwell_ampere_limit}) provided
+(\ref{equ:maxwell_gauss_B_limit}) (\ref{equ:maxwell_gauss_D_limit}) are satisfied at
+initial time.
+
+\begin{remark}
+  \label{rem:limit}
+  The limit \eqref{limit} represents a \emph{singular perturbation problem} in the sense
+  that vanishing $\lambda$ changes the character of the PDE system. To be more specific,
+  for $\lambda = \mathcal{O}(1)$ the $\mathbf{E}$-field evolves with time whereas in the
+  quasi-neutral model it responds instantaneously to other quantities according to the
+  constraint (\ref{equ:maxwell_ampere_limit}). We replace
+  (\ref{equ:maxwell_ampere_rescaled}) by the sum of the rotation of
+  (\ref{equ:maxwell_faraday_rescaled}) and the time-derivative of
+  (\ref{equ:maxwell_ampere_rescaled}). Meanwhile, due to the link between fluid momenta
+  $n_*u_*$ and current in (\ref{equ:maxwell_euler_coupling}), the term
+  $\partial_t\mathbf{J}$ can be reformulated by the momentum equation according to
+  (\ref{equ:euler_rescaled}) and we end up with the following wave equation with source
+  terms:
   \begin{align}
@@
   where
-\begin{align*}
+  \begin{align}
     \mathbf{S}_1 &= - \left(\sum_*\varepsilon_*^{-2}q_*^2n_*\right)\mathbf{E}, \\
-    \mathbf{S}_2 &= \sum_* q_*\nabla\cdot(n_* \mathbf{u}_* \otimes \mathbf{u}_* - \varepsilon_*^{-2}p_*\mathbb{I}\varepsilon_*^{-2}q_*^2n_*\mathbf{u}_*\times\mathbf{B} - q_*\varepsilon_*^{-2}\mathbf{R}^\text{coll}_*).
-\end{align*}
- It is obvious in (\ref{equ:E}) that the electric field propagate with finite speed (hyperbolic evolution) when $\lambda = \mathcal{O}(1)$, whereas for $\lambda = 0$ they respond instantaneously everywhere to local excitation (parabolic evolution/elliptic boundary value problems).
+    \mathbf{S}_2 &= \sum_* q_*\nabla\cdot(n_* \mathbf{u}_* \otimes \mathbf{u}_*
+    - \varepsilon_*^{-2}p_*\mathbb{I}\varepsilon_*^{-2}q_*^2n_*\mathbf{u}_*\times\mathbf{B}
+    - q_*\varepsilon_*^{-2}\mathbf{R}^\text{coll}_*).
+  \end{align}
+  It is obvious in (\ref{equ:E}) that the electric fields propagate with finite speed
+  (hyperbolic evolution) when $\lambda = \mathcal{O}(1)$, whereas for $\lambda = 0$ they
+  respond instantaneously everywhere to local excitation (parabolic evolution/elliptic
+  boundary value problems).
+\end{remark}
 
 \begin{remark}
-    The preceeding formal limit argument is heuristic.
-Deep mathematical tools from perturbation theory would be needed to rigorously prove the convergence of the limiting sequence.
-This topic is beyond the scope of this paper.
-Readers are referred to \cite[Ch.
-2]{remi_2014} \cite{Peng_2008} for the quasi-neutral limit of the Maxwell-Euler system, and \cite{mark_1995, Eckhaus_1980} for the general theory.
+  The preceeding formal limit argument is heuristic. Deep mathematical tools from
+  perturbation theory would be needed to rigorously prove the convergence of the limiting
+  sequence. This topic is beyond the scope of this paper. Readers are referred to
+  \cite[Ch. 2]{remi_2014} \cite{Peng_2008} for the quasi-neutral limit of the
+  Maxwell-Euler system, and \cite{mark_1995, Eckhaus_1980} for the general theory.
 \end{remark}
@@
 
-We consider a simply-connected domain $\Omega$ comprising two sub-domains $\Omega_P$ (plamsa domain) and $\Omega_N$ (non-conducting domain).
-They represent regions of space occupied by plasma and a non-conducting linear dielectric medium (e.g.
-glass) respectively.
-We use the notation $\Gamma_C := \partial\Omega \cap \partial\Omega_P$ to denote the contact boundary, and $\Gamma_I := \partial\Omega \cap \partial\Omega_N$ for the insulating boundary with an artificial cut-off boundary.
-The interface between the two domains is denoted by $\Gamma_W = \partial\Omega_I \cap \partial\Omega_P$.
-A geometric arrangement corresponding to this setting is sketched in Fig.
-\ref{fig:domain_sketch} and is the one used in \cite[][Ch.
-1, Sec.
-4]{fuchs_2021}.
-This situation is simple, but highly relevant.
-It covers fundamental experimental set-ups, for example, those studying wall-stabilized electric arcs \cite{GGF05}, but is also adequate for a range of industrial plasmas, for instance, those occurring in high-voltage circuit breakers \cite{SEE15,MGU20}.
-%\mycomment{Roman: expand on a relevant physical setting, e.g. wall-stabilized arc in hight voltage circuit breakers.}
-
-The Euler equations are defined in $\Omega_P$ with boundary conditions on $\partial\Omega_P$.
-We consider the physical scenario where plasma is confined by a solid insulator.
-Therefore, the interface $\Gamma_W$ is treated as reflective wall where fluid particles are bounced back while keeping the tangential velocity and energy unchanged.
-The contact boundary $\Gamma_C$ is modelled by open boundaries where the plasma and energy can flow through, i.e.
-ions and electrons are emitted and absorbed by the electrodes.
+We consider a simply-connected domain $\Omega$ comprising two sub-domains $\Omega_P$
+(\textbf{p}lasma domain) and $\Omega_N$ (\textbf{n}on-conducting domain). They represent
+regions of space occupied by plasma and a non-conducting linear dielectric medium
+(e.g. glass) respectively. We use the notation
+$\Gamma_C := \partial\Omega \cap \partial\Omega_P$ to denote the contact boundary, and
+$\Gamma_I := \partial\Omega \cap \partial\Omega_N$ for the insulating boundary which is an
+``artificial'' cut-off boundary. The interface between the two domains is denoted by
+$\Gamma_W = \partial\Omega_I \cap \partial\Omega_P$. A geometric arrangement corresponding
+to this setting is sketched in Fig. \ref{fig:domain_sketch} and is the one used in
+\cite[][Ch. 1, Sec. 4]{fuchs_2021}. This situation is simple, but highly relevant. It
+covers fundamental experimental set-ups, for example, those studying wall-stabilized
+electric arcs \cite{GGF05}, but is also adequate for a range of industrial plasmas, for
+instance, for those occurring in high-voltage circuit breakers \cite{SEE15,MGU20}.
+
+The Euler equations are defined in $\Omega_P$ with boundary conditions on
+$\partial\Omega_P$. We consider the physical scenario where the plasma is confined by a
+solid insulator. Therefore, the interface $\Gamma_W$ is treated as a reflective wall where
+fluid particles are bouncing back while keeping the tangential velocity and energy
+unchanged. The contact boundary $\Gamma_C$ is modelled by open boundaries, where charge
+carriers and energy can pass through, i.e., ions and electrons are emitted and absorbed by
+the electrodes.
 
 \begin{remark}
-    The treatment of electrodes as open boundary is a simplification. For more realistic electrode modelling, see \cite{godyak_1990, parker_1993}.
+  The treatment of electrodes as open boundary is a simplification. For more realistic
+  electrode modelling, see \cite{godyak_1990, parker_1993}.
 \end{remark}
 
-Maxwell's equations are solved in the whole domain $\Omega$.
-The insulating boundary $\Gamma_I$ blocks energy interchange and therefore only admits zero electric and magnetic flux, that is, $\mathbf{D}\cdot \mathbf{n}|_{\Gamma_I} = 0$ and $\mathbf{B} \cdot \mathbf{n}|_{\Gamma_I} = 0$ where $\mathbf{n}$ is the normal vector.
-We model the electrodes by imposing boundary conditions on the contact boundary $\Gamma_C = \Gamma_C^+\cup \Gamma_C^-$ which is composed of two disjoint connected components.
-On the contact boundary $\Gamma_C$, the tangential component $\mathbf{E}_t$ of the $\mathbf{E}$-field is vanishing.
-By Faraday's law (\ref{equ:maxwell_faraday_rescaled}) we have $\nabla \times \mathbf{E} \cdot \mathbf{n} = 0$ on the whole (topologically trivial) boundary $\partial\Omega$, which admits a scalar potential $\varphi$ defined on $\partial\Omega$ such that $\mathbf{E}_t = \nabla_\Gamma \varphi$ where $\nabla_\Gamma$ denotes surface gradient.
-$\varphi$ is constant on $\Gamma_C^+$ and $\Gamma_C^-$.
-The difference of these two constant values is the voltage drop between the two contacts.
+Maxwell's equations are posed on the whole domain $\Omega$. The insulating boundary
+$\Gamma_I$ blocks energy transfer and therefore only admits zero electric and magnetic
+flux, that is, $\mathbf{D}\cdot \mathbf{n}|_{\Gamma_I} = 0$ and
+$\mathbf{B} \cdot \mathbf{n}|_{\Gamma_I} = 0$ where $\mathbf{n}$ is the normal vector
+\cite{Hiptmair_2021}. We model the electrodes by imposing boundary conditions on the
+contact boundary $\Gamma_C = \Gamma_C^+\cup \Gamma_C^-$, which is composed of two disjoint
+connected components. On the contact boundary $\Gamma_C$, the tangential component
+$\mathbf{E}_t$ of the $\mathbf{E}$-field vanishes. By Faraday's law
+(\ref{equ:maxwell_faraday_rescaled}) we have
+$\nabla \times \mathbf{E} \cdot \mathbf{n} = 0$ on the whole (topologically trivial)
+boundary $\partial\Omega$, which admits a scalar potential $\varphi$ defined on
+$\partial\Omega$ such that $\mathbf{E}_t = \nabla_\Gamma \varphi$ where $\nabla_\Gamma$
+denotes surface gradient. The scalar potential $\varphi$ is constant on $\Gamma_C^+$ and
+$\Gamma_C^-$. The difference of these two constant values gives the voltage drop between the
+two contacts.
 \begin{figure}
@@
 \end{minipage}
-\caption{Sketch of the domain. The right figure shows the cross section in the $x$-$z$ plane.}
+\caption{The right figure shows the cross section in the $x$-$z$ plane and the different
+  parts of the boundary and interfaces.}
 \label{fig:domain_sketch}
 \end{figure}
-
 We summarize the boundary conditions for both sets of equations:
 
-\vspace{10pt}
 \begin{minipage}[t]{0.49\textwidth}
@@
 
-\begin{remark} For a geometric setting with non-trivial topology, e.g.
-with a tunnel, $\nabla \times \mathbf{E}\cdot\mathbf{n} = 0$ does not support the existence of a surface potential $\varphi$ satisfying $\mathbf{E}_t = \nabla_\Gamma\varphi$.
-One needs to consider co-homology vector fields \cite{Hiptmair_2021}.
+\begin{remark} For a geometric setting with non-trivial topology, e.g. with a tunnel,
+  $\nabla \times \mathbf{E}\cdot\mathbf{n} = 0$ does guarantee the existence of a surface
+  potential $\varphi$ satisfying $\mathbf{E}_t = \nabla_\Gamma\varphi$. One needs to
+  include co-homology vector fields \cite{Hiptmair_2021}.
 \end{remark}
 
-\subsection{Reformulation} \label{sec:reform_continuous}
-In the non-conducting domain $\Omega_N$ (see Fig.
-\ref{fig:domain_sketch}), the Euler system is not defined there due to the absence of plasmas.
-Consequently, the Maxwell system in $\Omega_N$ boils down to
+\subsection{Stabilization in $\Omega_{N}$}
+\label{sec:reform_continuous}
+
+No plasma fills the non-conducting domain $\Omega_N$ (see Fig. \ref{fig:domain_sketch}),
+and, consequently, the Maxwell system in $\Omega_N$ reduces to 
 \begin{subequations}
+  \label{eq:mxon}
 \begin{align}
@@
 \end{subequations}
-
-In non-neutral regime where $\lambda = \mathcal{O}(1)$, the Maxwell system in $\Omega_N$ is well-posed and Gauss's laws (\ref{equ:gauss_B_ins}) (\ref{equ:gauss_D_ins}) are redundant as long as they are satisfied at initial time.
-Nonetheless, as the system approaches the quasi-neutral limit as $\lambda \rightarrow 0$, Gauss's law for $\mathbf{D}$-field (\ref{equ:gauss_D_ins}) becomes degenerate.
-Schemes based on this set of PDEs would become unstable as $\lambda \rightarrow 0$.
-The vanishing divergence constraint would evaporate as $\nabla \cdot \mathbf{D} = 0/\lambda^2 = 0$ would not hold numerically when $\lambda^2$ becomes extremely small.
-
-To see this issue from another perspective, we examine the limit Maxwell system in $\Omega_N$
+In a non-neutral regime where $\lambda = \mathcal{O}(1)$, the Maxwell system in $\Omega_N$
+is well-posed and Gauss's laws (\ref{equ:gauss_B_ins}) (\ref{equ:gauss_D_ins}) are
+redundant as long as they are satisfied at initial time. Nonetheless, as the system
+approaches the quasi-neutral limit as $\lambda \rightarrow 0$, Gauss's law for the
+$\mathbf{D}$-field (\ref{equ:gauss_D_ins}) becomes degenerate. Schemes based on this set
+of PDEs would become unstable as $\lambda \rightarrow 0$. The vanishing divergence
+constraint would evaporate as $\nabla \cdot \mathbf{D} = 0/\lambda^2 = 0$ would not hold
+numerically when $\lambda^2$ becomes extremely small.
+
+To view this issue from another perspective, we examine the limit Maxwell system in
+$\Omega_N$:
 \begin{subequations}
@@
 
-Again, Gauss's law for the $\mathbf{B}$-field (\ref{equ:gauss_B_ins_limit}) is redundant while Gauss's law for the $\mathbf{D}$-field (\ref{equ:gaus_D_ins_limit}) is no longer the consequence of Amp\`{e}re's law (\ref{equ:ampere_ins_limit}).
-However, it is essential for the well-posedness of the problem \cite[][p.
-7]{ana_2010}.
-Obviously, the degeneracy of Gauss's law for the $\mathbf{D}$-field in the system (\ref{equ:faraday_ins_limit}) to (\ref{equ:gaus_D_ins_limit}) as $\lambda \rightarrow 0$ poses some problem.
-In other words, the set of equations (\ref{equ:faraday_ins_limit}) to (\ref{equ:gaus_D_ins_limit}) ``approaches" an ill-posed situation as $\lambda \rightarrow 0$.
-This is totally fine in the continuous level while it could be problematic on the discrete level due to limited machine precision.
-
-As a remedy, we propose the following reformulation which introduces a scalar Lagrange multiplier $\psi$ and removes the $\lambda^2$ prefactor in Gauss's law for the $\mathbf{D}$-field:
+Again, Gauss's law for the $\mathbf{B}$-field (\ref{equ:gauss_B_ins_limit}) is redundant,
+while Gauss's law for the $\mathbf{D}$-field (\ref{equ:gaus_D_ins_limit}) is no longer a
+consequence of Amp\`{e}re's law (\ref{equ:ampere_ins_limit}). However,
+\eqref{equ:gaus_D_ins_limit} is essential for the well-posedness of the problem \cite[][p.
+7]{ana_2010}. Obviously, the degeneracy of Gauss's law for the $\mathbf{D}$-field in the
+system (\ref{equ:faraday_ins_limit}) to (\ref{equ:gaus_D_ins_limit}) as
+$\lambda \rightarrow 0$ poses some problem. In other words, the set of equations
+(\ref{equ:faraday_ins_limit}) to (\ref{equ:gaus_D_ins_limit}) switches to an ill-posed
+situation for $\lambda=0$. I computations this will manifest itself as instability 
+already for ${\lambda>0}$.
+
+As a remedy, we propose the following reformulation which introduces a scalar Lagrange
+multiplier $\psi$ and removes the $\lambda^2$ prefactor in Gauss's law for the
+$\mathbf{D}$-field:
 \begin{subequations}
@@
 
-Supplemented with the boundary condition $\psi = 0$ on $\partial\Omega_N$, one can check that (\ref{equ:faraday_ins_reform}) to (\ref{equ:gauss_D_ins_reform}) are equivalent to the original formulation (\ref{equ:faraday_ins})-(\ref{equ:gauss_D_ins}) by verifying that $\psi = 0$ in $\Omega_N$.
-This is done by taking the divergence of (\ref{equ:ampere_ins_reform}), which results in $\Delta\psi = 0$ and the zero Dirichlet boundary condition gives vanishing $\psi$.
-The importance of this reformulation will become clear in the numerical experiments, see Section \ref{sec:numerical_experiment}.
-
-We point out that this reformulation is not needed in the plasma domain $\Omega_P$ since the Maxwell system is uniformly well-posed for $\lambda \in [0,1]$ thanks to the existence of an electric current and its dependence on the $\mathbf{E}$-field.
+Supplemented with the boundary condition $\psi = 0$ on $\partial\Omega_N$, one can check
+that (\ref{equ:faraday_ins_reform}) to (\ref{equ:gauss_D_ins_reform}) are equivalent to
+the original formulation (\ref{equ:faraday_ins})-(\ref{equ:gauss_D_ins}) by verifying that
+$\psi = 0$ in $\Omega_N$. This is done by taking the divergence of
+(\ref{equ:ampere_ins_reform}), which results in $\Delta\psi = 0$ and the zero Dirichlet
+boundary condition gives vanishing $\psi$. The importance of this reformulation will
+become clear through numerical experiments, see Section \ref{sec:numerical_experiment}.
+
+We point out that this reformulation is not needed in the plasma domain $\Omega_P$ since
+the Maxwell system is uniformly well-posed for $\lambda \in [0,1]$ thanks to the existence
+of an electric current and its dependence on the $\mathbf{E}$-field.
 
 \begin{comment}
-To devise an AP scheme, the dependence of the stability constraints of $h$ on $\lambda$ has to be removed.
-This is mainly achieved by utilizing implicit time-stepping for certain terms.
-As is summarized by \cite{degond_2017}, AP schemes aim to bridge several sets of equations describing the system in different regimes, rather than to alleviate the stability constraints of the numerical methods.
-In this sense, a fully-implicit scheme is likely to be overkill and thus a smart construction is necessary.
-The second consideration goes to the identification of a compatible boundary conditions for both regimes, which would be shown to be essential for the numerical stability.
-
-In the following sections, we first briefly discuss the 1D scheme for the Maxwell-Euler system devised by \cite{degond_2012} on which our work us built.
-This section also serves as a preliminary case study such that readers can better understand the 3D scheme.
+  To devise an AP scheme, the dependence of the stability constraints of $h$ on $\lambda$
+  has to be removed. This is mainly achieved by utilizing implicit time-stepping for
+  certain terms. As is summarized by \cite{degond_2017}, AP schemes aim to bridge several
+  sets of equations describing the system in different regimes, rather than to alleviate
+  the stability constraints of the numerical methods. In this sense, a fully-implicit
+  scheme is likely to be overkill and thus a smart construction is necessary. The second
+  consideration goes to the identification of a compatible boundary conditions for both
+  regimes, which would be shown to be essential for the numerical stability.
+
+  In the following sections, we first briefly discuss the 1D scheme for the Maxwell-Euler
+  system devised by \cite{degond_2012} on which our work us built. This section also
+  serves as a preliminary case study such that readers can better understand the 3D
+  scheme.
 \end{comment}
@@
 \subsubsection{Definition and Geometric Construction}
-Prior to the spatial discretization of the Maxwell-Euler system, we introduce primal-dual staggered meshes that are necessary in the discretization framework we use.
-The spatial domain is covered by two meshes interlacing with each other, denoted by a mesh doublet $(\mathcal{M}, \Tilde{\mathcal{M}})$ for primal mesh and dual mesh respectively.
-The fundamental duality property requires that \emph{each edge of one mesh penetrates a face of the other mesh and that each vertex of one mesh lies inside of a cell of the other mesh} \cite[][Sec.
-2]{weiland_2003}, which makes $(\mathcal{M}, \Tilde{\mathcal{M}})$ staggered to each other.
-A simple example for Cartesian meshes is shown in Fig.
-\ref{fig:cartesian}.
-
-To clarify the notation, in three dimensions the primal mesh $\mathcal{M}$ is a cell complex defined by the set of mesh entities $\{P, L, A, V\}$\footnote{The notation here is a bit sloppy.
-$P, L, A, V$ can refer to a single entity or a set of entities depending on the context.} denoting \emph{vertices, edges, faces} and \emph{cells} respectively.
-In the same way, the dual mesh $\Tilde{\mathcal{M}}$ is defined by $\{\Tilde{P}, \Tilde{L}, \Tilde{A}, \Tilde{V}\}$.
-The entities of two meshes are associated with bijective pairings $P \leftrightarrow \Tilde{V}$, $L \leftrightarrow \Tilde{A}$, $A \leftrightarrow \Tilde{L}$ and $V \leftrightarrow \Tilde{P}$ which arise in a very natural way: $P(\Tilde{P} \text{ resp.,})$ corresponds to $\Tilde{V}(V \text{ resp.,})$ in which it lies and $L(\Tilde{L} \text{ resp.,})$ penetrates its corresponding $\Tilde{A}(A \text{ resp.,})$.
-According to their dimensions, vertices, edges, faces and cells are also called 0-dim, 1-dim, 2-dim and 3-dim entities respectively.
-Meanwhile, we denote by $N_\ast, \ast \in \{P, \Tilde{P}, L, \Tilde{L},A, \Tilde{A},V, \Tilde{V}\}$ the total number of entities in $\mathcal{M}, \Tilde{\mathcal{M}}$.
-
-First, we illustrate the 2D case and construct the meshes based on the Delaunay-Voronoi approach: we start with a Delaunay triangulation $\mathcal{M}$ of the domain and construct $\Tilde{\mathcal{M}}$ by connecting \emph{circumcenters} of any two adjacent triangles, see Fig.
-\ref{fig:2d-mesh}.
-
-In three dimensions, the meshes are constructed by extruding the 2D meshes vertically along one axis in a staggered manner \cite[][Sec.
-3.1]{Marrone_2001}.
-See an example in Fig.
-\ref{fig:2d-extrusion}.
-In this way, the meshes are composed of prisms.
-This particular choice is compatible with the cylindrical geometric setting that we are in, see Fig.
-\ref{fig:domain_sketch}.
-For a general setting, one can directly decompose the domain into tetrahedrons and constructs the Voronoi grid, but the procedure is more complicated.
-The meshes for the cylindrical domain are displayed in Fig.
-\ref{fig:primal_dual_meshes}.
-
-The geometric orthogonality between $L \leftrightarrow \Tilde{A}$ and $A \leftrightarrow \Tilde{L}$ is satisfied and will be a crucial property for approximating the material laws on the discrete level (which is the so-called discrete Hodge operator \cite{hip_1999, bossavit1999}), as will be shown in Section \ref{sec:fit}.
+
+To prepare the spatial discretization of the Maxwell-Euler system, we introduce
+primal-dual staggered meshes, a key component of the discrete exterior calculus (DEC)
+discretization of Maxwell's equations. The spatial domain is covered by two meshes
+interlacing with each other, denoted by a mesh doublet
+$(\mathcal{M}, \Tilde{\mathcal{M}})$ for primal mesh and dual mesh respectively. The
+fundamental duality property requires that \emph{each edge of one mesh penetrates a face
+  of the other mesh and that each vertex of one mesh lies inside of a cell of the other
+  mesh} \cite[][Sec. 2]{weiland_2003}. Examples are shown in Fig.~\ref{fig:cartesian}.
+
+To clarify the notation, in three dimensions the primal mesh $\mathcal{M}$ is a cell
+complex defined by the set of mesh entities $\{P, L, A, V\}$\footnote{The notation here is
+  a bit sloppy. $P, L, A, V$ can refer to a single entity or a set of entities depending
+  on the context.} denoting \emph{vertices (points), edges, faces} and \emph{cells}
+respectively. In the same way, the dual mesh $\Tilde{\mathcal{M}}$ is defined by
+$\{\Tilde{P}, \Tilde{L}, \Tilde{A}, \Tilde{V}\}$. The entities of two meshes are
+connected by one-on-one pairings $P \leftrightarrow \Tilde{V}$,
+$L \leftrightarrow \Tilde{A}$, $A \leftrightarrow \Tilde{L}$ and
+$V \leftrightarrow \Tilde{P}$, which arise in a very natural way:
+$P(\Tilde{P} \text{ resp.,})$ corresponds to $\Tilde{V}(V \text{ resp.,})$ in which it
+lies and $L(\Tilde{L} \text{ resp.,})$ penetrates a corresponding
+$\Tilde{A}(A \text{ resp.,})$. According to their dimensions, vertices, edges, faces and
+cells are also called 0-dim, 1-dim, 2-dim and 3-dim entities respectively. Moreover, we
+denote by $N_\ast, \ast \in \{P, \Tilde{P}, L, \Tilde{L},A, \Tilde{A},V, \Tilde{V}\}$ the
+total number of entities in $\mathcal{M}, \Tilde{\mathcal{M}}$.
+
+In 2D we construct the pair of meshes based on the Delaunay-Voronoi approach: we start with a
+Delaunay triangulation $\mathcal{M}$ of the domain and construct $\Tilde{\mathcal{M}}$ by
+connecting \emph{circumcenters} of any two adjacent triangles, see Fig. \ref{fig:2d-mesh}.
+In three dimensions, the meshes are constructed by extruding the 2D meshes vertically
+along one axis in a staggered manner \cite[][Sec. 3.1]{Marrone_2001}. See an example in
+Fig. \ref{fig:2d-extrusion}. In this way, the meshes are composed of prisms. This
+particular choice is compatible with the cylindrical geometric setting that we are in, see
+Fig. \ref{fig:domain_sketch}. For a general setting, one can directly decompose the domain
+into tetrahedrons and constructs the Voronoi grid, but the procedure is more
+complicated. The meshes for the cylindrical domain are displayed in
+Fig. \ref{fig:primal_dual_meshes}.
+
+The geometric orthogonality between $L \leftrightarrow \Tilde{A}$ and
+$A \leftrightarrow \Tilde{L}$ is satisfied and will be a crucial property for
+approximating the material laws on the discrete level (which is the so-called discrete
+Hodge operator \cite{hip_1999, bossavit1999}), as will be shown in Section \ref{sec:fit}.
 
 \begin{remark}
-    The use of the Delaunay-Voronoi based primal-dual meshes is problematic when there are obtuse-angle triangles in $\mathcal{M}$.
-In this case their circumcenters lie outside the triangles and the intersection between edges and faces is violated.
-An alternative approach is barycenter-based dual meshes, which are not restricted to an acute-angle triangulation \cite[][Sec.
-4.2]{Marrone_2001}.
+  The use of the Delaunay-Voronoi based primal-dual meshes is problematic when there are
+  triangles with an obtuse angle in $\mathcal{M}$. In this case their circumcenters lie
+  outside the triangles and the intersection between edges and faces is violated. An
+  alternative approach is barycenter-based dual meshes, which are not restricted to an
+  acute-angle triangulation \cite[][Sec. 4.2]{Marrone_2001}.
 \end{remark}
@@
     \centering
-    \begin{tikzpicture}[scale = 0.2]
+    \begin{tikzpicture}[scale = 0.3]
             \def\style{thick}
@@
     \centering
-    \resizebox{0.45\textwidth}{!}{\begin{tikzpicture}
+    \resizebox{0.6\textwidth}{!}{\begin{tikzpicture}[scale = 1]
     \def\primalstyle{thick}
@@
     \centering
-    \resizebox{0.8\textwidth}{!}{\begin{tikzpicture}
+    \resizebox{0.9\textwidth}{!}{\begin{tikzpicture}[scale=1.1]
     \def\primalstyle{thick}
@@
     \hfill
-    \caption{Illustration of primal and dual meshes.
-\textbf{(a)} A Delaunay-Voronoi grid in 2D.
-\textbf{(b)} A Cartesian case.
-\textbf{(c)} The extrusion of 2D mesh.
-Six triangle prisms are primal cells (depicted by black and gray edges).
-One dual cell, which is a hexagon prism, is depicted by blue edges.
-The dashed hexagon represents the intersection of the dual cell and primal cells.
-}
+    \caption{Illustration of primal and dual meshes. \textbf{(a)} A Cartesian case
+      (``staggered grids'') \textbf{(a)} A Delaunay-Voronoi grid in 2D \textbf{(c)} The
+      extrusion of 2D mesh: six triangular prisms are primal cells (with black and
+      gray edges). One dual cell, which is a hexagonal prism, is depicted by blue edges. The
+      dashed hexagon represents the intersection of the dual cell and primal cells. }
     \label{fig:illustration_primal_dual}
@@
 \subsubsection{Orientation and Incidence Matrices}
-Each geometric entity in the primal mesh $\mathcal{M}$ is (arbitrarily) endowed with an \emph{internal orientation}\footnote{This notion should not be aliased with \emph{inner orientation}, which has a slightly different definition, see \cite[][Sec.
-3.1]{tonti_2002}.}.
-The notion is sketched in Fig.
-\ref{fig:orientation}.
-For the entities of the dual mesh $\Tilde{\mathcal{M}}$, we set their internal orientations to be aligned with their corresponding primal entities according to the bijective pairings, i.e.
-edges penetrate faces.
+
+Each geometric entity in the primal mesh $\mathcal{M}$ is (arbitrarily) endowed with an
+\emph{internal orientation}\footnote{This notion should not be confused with \emph{inner
+    orientation}, which has a slightly different definition, see
+  \cite[][Sec. 3.1]{tonti_2002}.}. The notion is illustrated in
+Fig. \ref{fig:orientation}. For the entities of the dual mesh $\Tilde{\mathcal{M}}$, we
+set their internal orientations to be aligned with their corresponding primal entities
+according to the bijective pairings, i.e. edges penetrate faces.
 
@@
     \centering
-    \begin{tabular}{l l}
+    \begin{tabular}{c c}
     \hline
-         Relation & Intuition \\
+         Property of incidence matrices & Corresponding rule in vector analysis \\
     \hline
@@
 \subsubsection{Cut-off Boundary}
-The primal mesh $\mathcal{M}$ is first generated and resolves the domain boundary.
-The dual mesh $\Tilde{\mathcal{M}}$ is generated afterwards.
-To make both meshes aligned at boundary, we have to truncate the \emph{dual} entities near the boundary due to the staggered character.
-In the meantime, auxiliary geometric entities are needed to close $\Tilde{\mathcal{M}}$, see Fig.
-\ref{fig:illustraion_dual_boundary}.
-
-Note that the auxiliary edges might not be straight and the auxiliary faces might not be flat as is shown in Fig.
-\ref{fig:illustraion_dual_boundary}, which necessitates a versatile data structure to include such situations.
-In the following, the auxiliary entities would be treated as dual entities, which limits the validity of the relations in Tab.
-\ref{tab:incidence_relation} to interior part of $\Tilde{\mathcal{M}}$.
-For a more systematic illustration that considers the boundary dual entities, see \cite[][Sec.
-5]{hip_1999}.
+
+The primal mesh $\mathcal{M}$ is generated first and resolves the domain boundary
+$\partial\Omega$. The dual mesh $\Tilde{\mathcal{M}}$ is generated afterwards. To make
+both meshes aligned at the boundary, we have to truncate the \emph{dual} entities near the
+boundary. In addition, auxiliary geometric entities are needed to close
+$\Tilde{\mathcal{M}}$, see Fig.~\ref{fig:illustraion_dual_boundary}.
+
+Note that the auxiliary edges might not be straight and the auxiliary faces might not be
+flat as is shown in Fig. \ref{fig:illustraion_dual_boundary}, which necessitates a
+versatile data structure to include such situations. In the following, the auxiliary
+entities would be treated as dual entities, which limits the validity of the relations in
+Tab. \ref{tab:incidence_relation} to interior part of $\Tilde{\mathcal{M}}$. For a more
+systematic illustration that considers the boundary dual entities, see
+\cite[][Sec. 5]{hip_1999}.
 
@@
 \subsubsection{Finite Integration Technique (FIT)} \label{sec:fit}
-We utilize FIT to discretize Maxwell's equations.
-This framework was originally proposed in \cite{weiland_1977} and can be regarded as a generalization of Yee's FDTD method \cite{yee_1966}.
-To derive a discrete model for the (rescaled) Maxwell system (\ref{equ:maxwell_faraday_rescaled})-(\ref{equ:maxwell_gauss_D_rescaled}), we first take integrals
+
+We utilize FIT to discretize Maxwell's equations. This framework was originally proposed
+in \cite{weiland_1977} and can be regarded as a generalization of Yee's FDTD method
+\cite{yee_1966}. To derive a discrete model for the (rescaled) Maxwell equations
+(\ref{equ:maxwell_faraday_rescaled})-(\ref{equ:maxwell_gauss_D_rescaled}), we first cast 
+them into integral form: 
 \begin{subequations}
@@
 
-Given the mesh pair $(\mathcal{M}, \Tilde{\mathcal{M}})$, the discrete Maxwell system arises from applying the integral equations (\ref{equ:maxwell_int_faraday})-(\ref{equ:maxwell_int_gauss_D}) to the entities in $(\mathcal{M}, \Tilde{\mathcal{M}})$.
-We end up with
+Given the mesh pair $(\mathcal{M}, \Tilde{\mathcal{M}})$, the discrete Maxwell system
+arises from restricting the integrals
+(\ref{equ:maxwell_int_faraday})-(\ref{equ:maxwell_int_gauss_D}) to the entities in
+$(\mathcal{M}, \Tilde{\mathcal{M}})$. We end up with
 \begin{subequations}
@@
 \end{subequations}
-where $k, l$ are numbering the entities in $(\mathcal{M}, \Tilde{\mathcal{M}})$.
-
-The integral quantities are the unknowns of the discrete Maxwell model.
-As is defined in (\ref{equ:maxwell_grid_faraday})-(\ref{equ:maxwell_grid_gauss_D}) by the underbraces, these unknowns are stacked into vectors:
-\begin{equation} \label{equ:fit_scale_vector}
+where $k, l$ number the entities in $(\mathcal{M}, \Tilde{\mathcal{M}})$.  The integral
+field quantities are the unknowns of the discrete Maxwell model. As is defined in
+(\ref{equ:maxwell_grid_faraday})-(\ref{equ:maxwell_grid_gauss_D}) by the underbraces,
+these unknowns are stacked into vectors:
+\begin{equation}
+  \label{equ:fit_scale_vector}
   \mathbf{e} := \{e_k\}_{k=1}^{N_L},\ \ \mathbf{b} := \{b_k\}_{k=1}^{N_A}, \ \ \mathbf{h} := \{h_k\}_{k=1}^{N_{\Tilde{L}}}, \ \ \mathbf{d} := \{d_k\}_{k=1}^{N_{\Tilde{A}}}, \ \ \mathbf{j} := \{j_k\}_{k=1}^{N_{\Tilde{A}}}, \ \ \mathbf{q} := \{q_k\}_{i=k}^{N_{\Tilde{V}}}.

### 2022-12-21 paper_version/main.tex
Finished revision

@@
 \usepackage[utf8]{inputenc}
+\usepackage{enumitem}
 \usepackage{amssymb}
@@
 
-The material laws (\ref{equ:material_law}) need to be taken into account within this framework, that is, relations $\mathbf{b} = \mathbb{M}_\mu \mathbf{h}$ and $\mathbf{d} = \mathbb{M}_\epsilon \mathbf{e}$ with suitable \emph{material} matrices $\mathbb{M}_\mu, \mathbb{M}_\epsilon$.
-When the orthogonality of the pair ($\mathcal{M}, \Tilde{\mathcal{M}}$) holds, the discrete material only involve diagonal matrices with entries
-
+The material laws (\ref{equ:material_law}) need to be taken into account within this
+framework, that is, relations $\mathbf{b} = \mathbb{M}_\mu \mathbf{h}$ and $\mathbf{d} =
+\mathbb{M}_\epsilon \mathbf{e}$ with suitable \emph{material} matrices $\mathbb{M}_\mu,
+\mathbb{M}_\epsilon$. When the orthogonality of the pair ($\mathcal{M},
+\Tilde{\mathcal{M}}$) holds, the discrete material laws can consistently be represented by
+\emph{diagonal matrices} with entries
 \begin{equation*}
@@
 \end{equation*}
-where $|\cdot|$ denotes taking length or area.
-We would like to remark that the approximation error is introduced due to the implicit assumption that vector fields are piecewise constant, see the analysis in \cite[][Sec.
-3.2]{Marrone_2001}.
-
-With the aid of incidence matrices defined in the preceding section and given the discrete material law, (\ref{equ:maxwell_grid_faraday})-(\ref{equ:maxwell_grid_gauss_D}) can be recast into a set of algebraic equations:
+where $|\cdot|$ denotes taking length or area. We would like to remark that an
+approximation error is introduced due to the implicit assumption that vector fields are
+piecewise constant, see the analysis in \cite[][Sec. 3.2]{Marrone_2001}.
+
+With the aid of incidence matrices defined in the preceding section and given the discrete
+material law, (\ref{equ:maxwell_grid_faraday})-(\ref{equ:maxwell_grid_gauss_D}) can be
+recast into a set of algebraic equations:
 \begin{center}
@@
 \end{center}
-where the dot above variables stands for the time derivative.
-
-At this point, we would like to emphasize the importance of the primal-dual staggered meshes: \emph{the material laws can be included in a rather simple way.} For Gauss's law $\mathbf{D} = \epsilon \mathbf{E}$, for instance, the $\mathbf{D}$-field is represented by a collection of face integrals $ \{d_k\}_{k}$ while the $\mathbf{E}$-field is represented by a collection of edge integrals $ \{e_k\}_{k}$.
-The primal-dual meshes allow us to arrange them in a staggered way -- edges penetrate faces -- such that $\mathbf{D} = \epsilon \mathbf{E}$ can be approximated by $\mathbf{d} = \mathbb{M}_{\epsilon}\mathbf{e}$ in a local fashion, i.e.
-$\mathbb{M}_{\epsilon}$ is diagonal.
-A more schematic illustration relies on the language of discrete exterior calculus (DEC), see \cite{bossavit1999, teixeira_1999, hip_1999}.
-
-The essence of FIT lies in: (i) The discrete Maxwell model (\ref{equ:alg_faraday})-(\ref{equ:alg_gauss_d}) are topological in the sense that they are invariant under different coordinate systems.
-Only the discrete material laws (\ref{equ:alg_material_magnetic})(\ref{equ:alg_material_magnetic}) depend on the geometric information.
-(ii) The discrete Maxwell model (\ref{equ:alg_faraday})-(\ref{equ:alg_gauss_d}) is free of approximation error, that is, it holds for analytical solutions.
-The consistency error is only introduced by the discrete material laws (\ref{equ:alg_material_magnetic})(\ref{equ:alg_material_magnetic}).
+where the dot on top of quantities stands for the time derivative.
+
+\begin{remark}
+  At this point, we would like to emphasize the importance of the primal-dual staggered
+  meshes: \emph{the material laws can be included in a rather simple way.} For Gauss's law
+  $\mathbf{D} = \epsilon \mathbf{E}$, for instance, the $\mathbf{D}$-field is represented
+  by a collection of face integrals $ \{d_k\}_{k}$ while the $\mathbf{E}$-field is
+  represented by a collection of edge integrals $ \{e_k\}_{k}$. The primal-dual meshes
+  allow us to arrange them in a staggered way -- edges penetrate faces -- such that
+  $\mathbf{D} = \epsilon \mathbf{E}$ can be approximated by
+  $\mathbf{d} = \mathbb{M}_{\epsilon}\mathbf{e}$ in a local fashion,
+  i.e. $\mathbb{M}_{\epsilon}$ is diagonal. A more schematic illustration relies on the
+  language of discrete exterior calculus (DEC), see \cite{bossavit1999, teixeira_1999,
+    hip_1999}.
+\end{remark}
+
+Summing up, the essence of DEC/FIT is the following:
+\begin{enumerate}[label={(\roman{*})}]
+\item The discrete Maxwell model (\ref{equ:alg_faraday})-(\ref{equ:alg_gauss_d}) are
+  topological in the sense that they are invariant under different coordinate
+  systems. Only the discrete material laws
+  (\ref{equ:alg_material_magnetic})(\ref{equ:alg_material_magnetic}) depend on the
+  geometric information.
+\item The discrete Maxwell model (\ref{equ:alg_faraday})-(\ref{equ:alg_gauss_d}) is free
+  of approximation error, that is, it holds for exact fields. A consistency error is
+  introduced only by the discrete material laws
+  (\ref{equ:alg_material_magnetic})(\ref{equ:alg_material_magnetic}).
+\end{enumerate}
 
 \subsubsection{Discrete Boundary Conditions}
-The electromagnetic boundary $\Gamma_C, \Gamma_I$ is resolved by the primal mesh $\mathcal{M}$.
-As is mentioned in Section \ref{sec:BC}, the zero magnetic flux $\mathbf{B}\cdot \mathbf{n}$ is equivalent to $\nabla\times\mathbf{E} \cdot \mathbf{n} = 0$, which allows a boundary scalar potential $\varphi$ such that the tangential component $\mathbf{E}_t$ of the $\mathbf{E}$-field is equal to $\nabla_\Gamma\varphi$.
-It holds on the discrete level as well.
-We associate each primal vertex $P_k \in \partial\Omega$ with a scalar value $\varphi_k$.
-Therefore, the boundary conditions (see Section \ref{sec:BC}) are discretized in the following way:
+
+The electromagnetic boundary $\partial\Omega = \Gamma_C\cup \Gamma_I$ is resolved by the
+primal mesh $\mathcal{M}$. As is mentioned in Section \ref{sec:BC}, the zero-magnetic-flux
+boundary condition $\mathbf{B}\cdot \mathbf{n}$ is equivalent to
+$(\nabla\times\mathbf{E}) \cdot \mathbf{n} = 0$, which paves the way for a surface scalar
+potential $\varphi:\partial\Omega\to\mathbb{R}$ such that the tangential component
+$\mathbf{E}_t$ of the $\mathbf{E}$-field is equal to $\nabla_\Gamma\varphi$. This remains
+true on the discrete level. We associate with each primal vertex $P_k \in \partial\Omega$
+a scalar value $\varphi_k$. Therefore, the boundary conditions (see Section \ref{sec:BC})
+are discretized in the following way:
 \begin{center}
@@
 \end{center}
-where $\mathbb{X}_\varphi \in \mathbb{R}^{N_P \times N_P^\partial}$ extends $\bm{\varphi}$ to all the primal verices by zero.
-Therefore, the surface gradient $\nabla_\Gamma$ is represented by $\mathbb{GX}_\varphi$.
+where $\mathbb{X}_\varphi \in \mathbb{R}^{N_P \times N_P^\partial}$ extends $\bm{\varphi}$
+to all the primal verices by zero. Obviously, the surface gradient $\nabla_\Gamma$ is
+represented by $\mathbb{GX}_\varphi$.
 
 \subsubsection{Stabilization in $\Omega_N$} \label{sec:reform-discrete}
-In Section \ref{sec:reform_continuous}, we have proposed a stabilization of the Maxwell system in the non-conducting domain $\Omega_N$ by introducing a Lagrange multiplier.
-In the semi-discrete level, the equations to be solved in $\Omega_N$ are
-
+
+In Section \ref{sec:reform_continuous}, we have proposed a stabilization of the Maxwell
+system in the non-conducting domain $\Omega_N$ by introducing a Lagrange multiplier. On
+the semi-discrete level, the equations to be solved in $\Omega_N$ are
 \begin{center}
-    \vspace{-0.5cm}
     \begin{minipage}{0.3\textwidth}
@@
 \end{center}
-where $\bm{\psi} := \{\psi_k\}_{k=1}^{N_P^N}$ denotes unknowns assigned to each primal vertex in $\Omega_N$.
-The matrix $\mathbb{X}_\psi \in \mathbb{R}^{N_P \times N_P^{N}}$ extends $\bm{\psi}$ by zero to all the primal vertices, by which the zero Dirichlet boundary condition is incorporated.
-We need the matrix $(\mathbb{H})_{k,k} = {|\Tilde{A}_k|}/{|L_k|}$ to transform primal edge integrals to dual face fluxes since the discrete Amp\`{e}re's law (\ref{equ:discrete_ampere_ins}) is defined on dual faces on $\Omega_N$.
+where $\bm{\psi} := \{\psi_k\}_{k=1}^{N_P^N}$ denotes unknowns assigned to each primal
+vertex in $\Omega_N$. The matrix $\mathbb{X}_\psi \in \mathbb{R}^{N_P \times N_P^{N}}$
+extends $\bm{\psi}$ by zero to all the primal vertices. This way the zero Dirichlet
+boundary condition is incorporated. We need the diagonal matrix
+$(\mathbb{H})_{k,k} = {|\Tilde{A}_k|}/{|L_k|}$ to transform primal edge integrals to dual
+face fluxes since the discrete Amp\`{e}re's law (\ref{equ:discrete_ampere_ins}) is defined
+on dual faces on $\Omega_N$.
 
@@
 
-We can examine the well-posedness of the (semi-)discrete Maxwell system by checking whether the numbers of unknowns (also called degrees of freedom (D.o.F.)) and equations coincide.
-
-First, we make a meticulous classification for mesh entities according to their locations:
+We can probe the well-posedness of the (semi-)discrete Maxwell system by checking whether
+the numbers of unknowns (also called degrees of freedom (D.o.F.)) and equations coincide.
+First, we count mesh entities according to their locations:
 \begin{center}
@@
     \begin{align*}
-        &\#\  \text{primal cells}\ \  N_V \\
-        &\#\  \text{primal edges}\ \  N_L := \underbrace{N^C_L + N^I_L}_{=N^\partial_L} + N^\circ_L  \\
-        &\#\  \text{primal faces}\ \  N_A := \underbrace{N_A^C + N^I_A}_{=N^\partial_A} + N^\circ_A  \\
-        &\#\  \text{primal vertices}\ \  N_P := \underbrace{N_P^C + N^I_P}_{=N^\partial_P} + N^\circ_P
+        &\#\  \text{primal cells}\ \  N_V, \\
+        &\#\  \text{primal edges}\ \  N_L := \underbrace{N^C_L + N^I_L}_{=N^\partial_L} + N^\circ_L,  \\
+        &\#\  \text{primal faces}\ \  N_A := \underbrace{N_A^C + N^I_A}_{=N^\partial_A} + N^\circ_A , \\
+        &\#\  \text{primal vertices}\ \  N_P := \underbrace{N_P^C + N^I_P}_{=N^\partial_P} + N^\circ_P,
     \end{align*}
@@
     \begin{align*}
-        &\#\  \text{dual cells}\ \  N_{\Tilde{V}} := N_P \\
-        &\#\  \text{dual edges}\ \  N_{\Tilde{L}} := \underbrace{N^\partial_{\Tilde{L}}}_{=N^\partial_L} + \underbrace{N^\circ_{\Tilde{L}}}_{=N_A} \\
-        &\#\  \text{dual faces}\ \  N_{\Tilde{A}} := \underbrace{N^\partial_{\Tilde{A}}}_{=N^\partial_P} + \underbrace{N^\circ_{\Tilde{A}}}_{=N_L}
+        &\#\  \text{dual cells}\ \  N_{\Tilde{V}} := N_P ,\\
+        &\#\  \text{dual edges}\ \  N_{\Tilde{L}} := \underbrace{N^\partial_{\Tilde{L}}}_{=N^\partial_L} + \underbrace{N^\circ_{\Tilde{L}}}_{=N_A} ,\\
+        &\#\  \text{dual faces}\ \  N_{\Tilde{A}} := \underbrace{N^\partial_{\Tilde{A}}}_{=N^\partial_P} + \underbrace{N^\circ_{\Tilde{A}}}_{=N_L},
     \end{align*}
@@
 \end{center}
-where the superscript indicates the locations where the entities lie.
-The equations $N^\partial_{\Tilde{L}} = N^\partial_L, N^\partial_{\Tilde{A}} = N^\partial_P$ reveal the bijective relation between the boundary primal entities and auxiliary entities, as can be checked easily by inspecting Fig.
-\ref{fig:illustraion_dual_boundary}.
-We also give a summary of the unknowns in Tab. \ref{tab:def_size_var}.
+where the superscripts indicate where the entities are located. The equalities
+$N^\partial_{\Tilde{L}} = N^\partial_L, N^\partial_{\Tilde{A}} = N^\partial_P$ reveal the
+bijective relation between the boundary primal entities and auxiliary entities, as can be
+checked easily by inspecting Fig.~\ref{fig:illustraion_dual_boundary}.  We also give a
+summary of the unknowns in Tab.~\ref{tab:def_size_var}.
 \begin{table}[]
@@
 \end{align*}
-Comparing the numbers of D.o.F in Tab. \ref{tab:def_size_var} and of the equations we collect above, we show that they are equal:
+Comparing the numbers of d.o.f. in Tab.~\ref{tab:def_size_var} and of the equations we
+collect above, we see that they are equal:
 \begin{align*}
     \#\text{ of unknowns} &= \colorbox{violet!20}{$N_L$} + \colorbox{blue!20}{$N_A$} + \colorbox{gray!40}{$N_{\Tilde{L}}$} + \colorbox{orange!20}{$N_{\Tilde{A}}$} + \colorbox{green!20}{$N_P^\partial$} + \colorbox{yellow!40}{$N_P^{N}$}, \\
-    \#\text{ of equations} &= \colorbox{blue!20}{$N_A$} + \colorbox{orange!20}{$N_{\Tilde{A}}$} + \colorbox{gray!40}{$N_A+N_L^\partial$} + \colorbox{violet!20}{$N_L$} + \colorbox{green!20}{$N_P^C + N_P^I$}+ \colorbox{yellow!40}{$N_{\Tilde{V}}^N$},
+    \#\text{ of equations} &= \colorbox{blue!20}{$N_A$} + \colorbox{orange!20}{$N_{\Tilde{A}}$} + \colorbox{gray!40}{$N_A+N_L^\partial$} + \colorbox{violet!20}{$N_L$} + \colorbox{green!20}{$N_P^C + N_P^I$}+ \colorbox{yellow!40}{$N_{\Tilde{V}}^N$}.
 \end{align*}
-where the terms with the same color are equal.
-
-Of course, the matching numbers of unknowns and equations do not necessarily result in a valid linear system, since the equations might be linearly dependent.
-In fact, the linear system will be singular without the stabilization proposed in the previous section when $\lambda = 0$.
+Of course, the matching numbers of unknowns and equations do not necessarily result in a
+valid linear system, since the equations might be linearly dependent. In fact, the linear
+system will be singular without the stabilization proposed in the previous section when
+$\lambda = 0$.
 
 \subsection{Discrete Euler Equations} \label{sec:discrete_euler}
-We employ the finite volume method (FVM) to discretize the Euler system. The Euler equations (\ref{equ:euler_}) can be cast into the form of conservation law with source terms:
+
+We employ the finite volume method (FVM) to discretize the Euler system. The Euler
+equations (\ref{equ:euler_}) can be cast into the form of conservation law with source
+terms:
 \begin{equation} \label{equ:euler_conservation}
@@
 \end{equation}
-where $\mathbf{U} \in L^2(\Omega \times [0,T], \mathbb{R}^m)$ stands for $m$ conservative variables.
-In the case of the full 3D Euler equations (\ref{equ:euler_rescaled}), $m = 5$ and $\mathbf{U} := [n, n\mathbf{u}, ne]$.
-$\mathbf{f}(\mathbf{U}) \in L^2(\Omega \times  [0,T], \mathbb{R}^{3 \times m})$ is the flux function.
-$\mathbf{RHS} \in L^2(\Omega \times  [0,T], \mathbb{R}^m)$ is the source term.
-
-To obtain the semi-discretization, we first integrate (\ref{equ:euler_conservation}) over a \emph{dual} cell $\Tilde{V}_i \in \Omega_P$
+where $\mathbf{U} \in L^2(\Omega \times [0,T], \mathbb{R}^m)$ stands for a vector of $m$
+conservative variables,
+$\mathbf{f}(\mathbf{U}) \in L^2(\Omega \times [0,T], \mathbb{R}^{3 \times m})$ is the flux
+function, and $\mathbf{RHS} \in L^2(\Omega \times [0,T], \mathbb{R}^m)$ is the source
+term.. In the case of the full 3D Euler equations (\ref{equ:euler_rescaled}), $m = 5$ and
+$\mathbf{U} := [n, n\mathbf{u}, ne]$.
+
+To obtain the semi-discretization, we first integrate (\ref{equ:euler_conservation}) over
+a \emph{dual} cell $\Tilde{V}_k \in \Omega_P$
 \begin{equation} \label{equ:euler_grid} 
@@
 \end{equation}
-where $\overline{\mathbf{U}}_k := \iiint_{\Tilde{V}_k} \mathbf{U} \text{d}V / |\Tilde{V}_k| \in L^2([0,T],\mathbb{R}^m)$ is the cell average of $\mathbf{U}$ and $\mathbf{n}_l$ is the outer normal vector of face $\Tilde{A}_l$ with respect to the cell $\Tilde{V}_k$.
-In FVM, the flux $\overline{\mathbf{f}}_l$ in (\ref{equ:euler_grid}) is approximated by a numerical flux $\mathbf{f}^\text{num}_l := \mathbf{f}^\text{num}\left(\overline{\mathbf{U}}_k, \overline{\mathbf{U}}_{\hat{k}(k,l)}, \mathbf{n}_l\right)$, where $\hat{k}(k,l)$ returns the index of the adjacent dual cell that shares $\Tilde{A}_l$ with cell $\Tilde{V}_k$.
-Classical numerical fluxes include Lax-Friedrich flux, Rusanov flux, and Engquist-Osher flux, see \cite[][pp.
-44-46]{mishra_2019}.
-We end up with the semi-discretized equation:
+where
+$\overline{\mathbf{U}}_k := \iiint_{\Tilde{V}_k} \mathbf{U} \text{d}V / |\Tilde{V}_k| \in
+L^2([0,T],\mathbb{R}^m)$ is the cell average of $\mathbf{U}$ and $\mathbf{n}_l$ is the
+outer normal vector of face $\Tilde{A}_l$ with respect to the cell $\Tilde{V}_k$. In FVM,
+the flux $\overline{\mathbf{f}}_l$ in (\ref{equ:euler_grid}) is approximated by a
+numerical flux
+$\mathbf{f}^\text{num}_l := \mathbf{f}^\text{num}\left(\overline{\mathbf{U}}_k,
+  \overline{\mathbf{U}}_{\hat{k}(k,l)}, \mathbf{n}_l\right)$, where $\hat{k}(k,l)$ returns
+the index of the adjacent dual cell that shares $\Tilde{A}_l$ with cell
+$\Tilde{V}_k$. Classical numerical fluxes include the Lax-Friedrich flux, the Rusanov
+flux, and the Engquist-Osher flux, see \cite[][pp. 44-46]{mishra_2019}. We end up with the
+semi-discretized equation:
 \begin{equation}
@@
 
-At this stage, we would like to discuss why the Euler system should be discretized on $\Tilde{\mathcal{M}}$.
-As is shown in the integrated Amp\`{e}re's law (\ref{equ:maxwell_int_ampere}), the electric currents are defined on dual faces $\Tilde{A}$.
-By solving the Euler equations on $\Tilde{\mathcal{M}}$, we have the mass flux on dual faces $\Tilde{A}$ as well.
-In this way, the connection between the charge conservation (\ref{equ:charge_continuity}) and the mass conservation (the 1st equation in (\ref{equ:euler_})) due to the current-momentum coupling (\ref{equ:maxwell_euler_coupling}) is preserved on the discrete level.
-
-For the sake of presentation, we rewrite (\ref{equ:fvm}) into a matrix form.
-By abuse of notation, we stack all the cell average $\{\overline{\mathbf{U}}_k\}_{k=1}^{N^P_{\Tilde{V}}}$ into a matrix $\mathbf{U} \in \mathbb{R}^{N_{\Tilde{V}}^P \times 5}$ with $\mathbf{U}_{k,:} = \overline{\mathbf{U}}_k$.
-Further, we denote by $\mathbf{F} \in \mathbb{R}^{N_{\Tilde{A}}^P \times 5}$ the collection of the (total) numerical fluxes, i.e.
-$\mathbf{F}_{k,:} = \mathbf{f}^\text{num}_k = [f^\text{mass}_k, \bm{f}^\text{mom}_k, f^\text{ene}_k]$.
-In the same way, we denote by $\mathbf{RHS}\in \mathbb{R}^{N_{\Tilde{V}}^P \times 5}$ the collection of $\overline{\mathbf{RHS}}_k$.
-Besides, we define the diagonal matrix $\mathbb{\Tilde{V}} \in \mathbb{R}^{N_{\Tilde{V}}^P \times N_{\Tilde{V}}^P}$ and $\mathbb{\Tilde{A}}\in \mathbb{R}^{N_{\Tilde{A}}^P \times N_{\Tilde{A}}^P}$ with $(\mathbb{\Tilde{A}})_{k,k} = |\Tilde{A}_k|$.
-Making use of the incidence matrices, we end up with
+At this stage, we would like to discuss why \emph{the Euler system should be discretized
+  on $\Tilde{\mathcal{M}}$}. As is shown in the integrated Amp\`{e}re's law
+(\ref{equ:maxwell_int_ampere}), the electric currents are defined on dual faces
+$\Tilde{A}$. By solving the Euler equations on $\Tilde{\mathcal{M}}$, we have the mass
+flux on dual faces $\Tilde{A}$ as well. In this way, the connection between the charge
+conservation (\ref{equ:charge_continuity}) and the mass conservation (the 1st equation in
+(\ref{equ:euler_})) due to the current-momentum coupling
+(\ref{equ:maxwell_euler_coupling}) is preserved on the discrete level.
+
+For the sake of presentation, we rewrite (\ref{equ:fvm}) into a matrix form. By abuse of
+notation, we stack all the cell average
+$\{\overline{\mathbf{U}}_k\}_{k=1}^{N^P_{\Tilde{V}}}$ into a matrix
+$\mathbf{U} \in \mathbb{R}^{N_{\Tilde{V}}^P \times 5}$ with
+$\mathbf{U}_{k,:} = \overline{\mathbf{U}}_k$. Further, we denote by
+$\mathbf{F} \in \mathbb{R}^{N_{\Tilde{A}}^P \times 5}$ the collection of the (total)
+numerical fluxes, i.e.
+$\mathbf{F}_{k,:} = \mathbf{f}^\text{num}_k = [f^\text{mass}_k, \bm{f}^\text{mom}_k,
+f^\text{ene}_k]$. In the same way, we denote by
+$\mathbf{RHS}\in \mathbb{R}^{N_{\Tilde{V}}^P \times 5}$ the collection of
+$\overline{\mathbf{RHS}}_k$. Besides, we define the diagonal matrices
+$\mathbb{\Tilde{V}} \in \mathbb{R}^{N_{\Tilde{V}}^P \times N_{\Tilde{V}}^P}$ and
+$\mathbb{\Tilde{A}}\in \mathbb{R}^{N_{\Tilde{A}}^P \times N_{\Tilde{A}}^P}$ with
+$(\mathbb{\Tilde{A}})_{k,k} = |\Tilde{A}_k|$. Making use of the incidence matrices, we end
+up with
 \begin{equation} \label{equ:euler_matrix_form}
@@
 \end{equation}
-Recall that $\Tilde{\mathbb{D}}$ represents the discrete divergence of $\Tilde{\mathcal{M}}$.
-Dependence of $\mathbf{RHS}$ on $\mathbf{d}, \mathbf{b}$ is implied by (\ref{equ:euler_rescaled}) and will be elaborated next.
+Recall that $\Tilde{\mathbb{D}}$ represents the discrete divergence of
+$\Tilde{\mathcal{M}}$. Dependence of $\mathbf{RHS}$ on $\mathbf{d}, \mathbf{b}$ is implied
+by (\ref{equ:euler_rescaled}) and will be elaborated next.
 
 \subsubsection{Reconstruction of Lorentz Force}
-Since the electromagnetic fields are represented by integrals on edges and faces, we need to reconstruct their vector components for the computation of Lorentz force (and Joule heating) inside each dual cell.
-
-The problem is twofold:
+
+Since the electromagnetic fields are represented by integrals on edges and faces, we need
+to reconstruct their vector components for the computation of Lorentz force (and Joule
+heating) inside each dual cell. The task involves two aspects:
 \begin{itemize}
@@
 \end{itemize}
-We adopt the principle of least square fitting and reconstruct a \emph{constant} vector field inside each cell.
-For a cell $\Tilde{V}$ with $N_A$ faces with areas $\{A_k\}_{k=1}^{N_A}$, normal vectors $\{\mathbf{n}_k\}_{k=1}^{N_A}$ and fluxes $\{f_k\}_{k=1}^{N_A}$, a constant vector field $\mathbf{v}$ satisfying
+We adopt the principle of least square fitting and reconstruct a \emph{constant} vector
+field inside each cell. For a cell $\Tilde{V}$ with $N_A$ faces with areas
+$\{A_k\}_{k=1}^{N_A}$, normal vectors $\{\mathbf{n}_k\}_{k=1}^{N_A}$ and fluxes
+$\{f_k\}_{k=1}^{N_A}$, a constant vector field $\mathbf{v}$ satisfying
 \begin{equation*}
@@
 \end{equation*}
-and each vector in $\mathbb{R}^3$ is treated as a column vector.
-The construction based on the integral quantities on edges can be done similarly.
-Assembling the local constructions for each dual cell, the global construction can be written as
+and each vector in $\mathbb{R}^3$ is treated as a column vector. The construction based on
+the integral quantities on edges can be done similarly. Assembling the local constructions
+for each dual cell, the global construction can be written as
 \begin{equation}
-    \mathbf{E} = \Tilde{\mathbb{R}}_E\mathbf{d},
-    \ \ \ \ 
-    \mathbf{B} = \Tilde{\mathbb{R}}_B\mathbf{b}, \label{equ:reconstruction}
+    \mathbf{E} = \Tilde{\mathbb{R}}_E\mathbf{d}\;,
+    \quad
+    \mathbf{B} = \Tilde{\mathbb{R}}_B\mathbf{b},
+    \label{equ:reconstruction}
 \end{equation}
-where $\mathbf{d}, \mathbf{b}$ are defined in Tab.
-\ref{tab:def_size_var}; $\mathbf{E} := \{\mathbf{E}_k\}_{k=1}^{N_{\Tilde{V}}}$ and $\mathbf{B} := \{\mathbf{B}_k\}_{k=1}^{N_{\Tilde{V}}}$ are $N_{\Tilde{V}} \times 3$ matrices containing the reconstructed $\mathbf{E}$-fields and $\mathbf{B}$-fields at each $\Tilde{V}$; $\Tilde{\mathbb{R}}_E$ and $\Tilde{\mathbb{R}}_B$ are thus rank-3 tensors.
-
-The problem of the reconstruction of vector fields on unstructured meshes is a widely studied topic.
-Apart from the least-square method, other methods include Perot's method \citep{perot_2000}, finite-entity-based methods, etc., which potentially can achieve higher-order accuracy.
-See \cite[][Sec.
-3.4.4]{fuchs_2021} and the references therein.
-
-Therefore, the right-hand-side term in (\ref{equ:euler_matrix_form}) can be computed according to the rescaled Euler equations (\ref{equ:euler_rescaled}) with the reconstructed $\mathbf{E}$-field and $\mathbf{B}$-field by (\ref{equ:reconstruction}) defined in each dual cell.
+where $\mathbf{d}, \mathbf{b}$ are defined in Tab. \ref{tab:def_size_var};
+$\mathbf{E} := \{\mathbf{E}_k\}_{k=1}^{N_{\Tilde{V}}}$ and
+$\mathbf{B} := \{\mathbf{B}_k\}_{k=1}^{N_{\Tilde{V}}}$ are $N_{\Tilde{V}} \times 3$
+matrices containing the reconstructed $\mathbf{E}$-fields and $\mathbf{B}$-fields at each
+$\Tilde{V}$; $\Tilde{\mathbb{R}}_E$ and $\Tilde{\mathbb{R}}_B$ are thus rank-3 tensors.
+
+The problem of the reconstruction of vector fields on unstructured meshes is a widely
+studied topic. Apart from the least-square method, other methods include Perot's method
+\citep{perot_2000}, finite-entity-based methods, etc., which potentially can achieve
+higher-order accuracy. See \cite[][Sec. 3.4.4]{fuchs_2021} and the references therein.
+
+Eventually, the right-hand-side term in (\ref{equ:euler_matrix_form}) can be computed by
+evaluating the right-hand-side of rescaled Euler equations (\ref{equ:euler_rescaled}) for
+the reconstructed $\mathbf{E}$-field and $\mathbf{B}$-field by (\ref{equ:reconstruction})
+defined in each dual cell.
 
 \subsubsection{Discrete Boundary Conditions}
-The boundary conditions for the Euler system (see Section \ref{sec:BC}) are implemented by the approach of ghost cells \cite[][Ch.
-7]{leveque_2007}, i.e.
-extending the domain by a layer of virtual cells with prescribed variables.
-In our case, the ghost cells at the open boundary at $\Gamma_C$ are assigned equal state as their adjacent interior cells.
-It is equivalent to enforcing the numerical fluxes
+
+The boundary conditions for the Euler system (see Section \ref{sec:BC}) are implemented by
+the approach of ghost cells \cite[][Ch. 7]{leveque_2007}, i.e. extending the domain by a
+layer of virtual cells with prescribed variables. In our case, the ghost cells at the open
+boundary at $\Gamma_C$ are assigned the same state as their adjacent interior cells. It is
+equivalent to enforcing the numerical fluxes
 \begin{equation} \label{equ:discrete_open_bc}
@@
 \end{equation}
-where $l$ refers to the index of the cell adjacent to the boundary face $\Tilde{A}_k$ and is unique.
-For the reflective wall $\Gamma_W$, the momentum of a ghost cell is reversed with respect to its adjacent one while keeping the other quantities unchanged.
-Therefore, the numerical fluxes are
-\begin{equation} \label{equ:discrete_wall_bc}
-    \mathbf{F}_k = \mathbf{f}^\text{num}(\mathbf{U}_l, \hat{\mathbf{U}}_l, \mathbf{n}_k), \ \ \forall k: \Tilde{A}_k \subset \Gamma_W,
+where $l$ refers to the (unique!) index of the cell adjacent to the boundary face
+$\Tilde{A}_k$. For the \emph{reflective wall} $\Gamma_W$, the momentum of a ghost cell is
+reversed with respect to its adjacent interior cell while keeping the other quantities
+unchanged. Therefore, in this case the numerical fluxes are
+\begin{equation} \label{equ:discrete_wall_bc} \mathbf{F}_k =
+  \mathbf{f}^\text{num}(\mathbf{U}_l, \hat{\mathbf{U}}_l, \mathbf{n}_k), \ \ \forall k:
+  \Tilde{A}_k \subset \Gamma_W,
 \end{equation}
-where the state of the ghost cell $\hat{\mathbf{U}}_l = [n, n\mathbf{u} - 2(\mathbf{n}\cdot\mathbf{u})\mathbf{n}, ne]^T$ reverses the normal velocity of $\mathbf{U}_l = [n, n\mathbf{u}, ne]^T$.
+where the state of the ghost cell
+$\hat{\mathbf{U}}_l = [n, n\mathbf{u} - 2(\mathbf{n}\cdot\mathbf{u})\mathbf{n}, ne]^T$
+reverses the normal velocity of $\mathbf{U}_l = [n, n\mathbf{u}, ne]^T$.
 
 \subsection{Summary: Spatially Semi-discrete Model}
-We collect all the equations and boundary conditions presented above and give a summary for the spatially semi-discrete Maxwell-Euler system based on the FIT-FVM framework:
+We collect all the equations and boundary conditions presented above and give a summary for the spatially semi-discrete Maxwell-Euler system based on the FIT/DEC-FVM framework:
 \begin{subequations}
@@
 
-We would like to stress again that in our FIT-FVM framework Faraday's law is discretized on $\mathcal{M}$ while Amp\`{e}re's law is discretized on $\Tilde{\mathcal{M}}$ for a simple approximation of material laws.
-By arranging the Euler system on $\Tilde{\mathcal{M}}$, the connection between electric currents and fluid momenta is naturally established and preserved in the discrete level since both are defined on the dual faces.
+We would like to stress again that in our FIT/DEC-FVM framework Faraday's law is
+discretized on the primal mesh $\mathcal{M}$ while Amp\`{e}re's law is discretized on the
+dual mesh $\Tilde{\mathcal{M}}$. The material laws directly connect primal and dual
+d.o.f. Using the cells of the dual mesh $\Tilde{\mathcal{M}}$ as finite-volumes for the
+Euler system the connection between electric currents and fluid momenta is perfectly
+represented in the discretization, since both are defined on the dual faces.
 
@@
 \subsection{Motivation: Reduction to One Spatial Dimension}
-Our work is an extension of the 1D scheme proposed in \cite{degond_2012} towards three dimensions.
-Therefore, it is supposed to be compatible with the original 1D scheme when reduced to one dimension.
-This perspective helps to understand how the 3D scheme stems from the 1D one.
-For the sake of presentation, we discuss the one-fluid model of \cite{degond_2012} where ions are assumed immobile and only the motion of electrons is considered.
+
+Our work extends the 1D scheme proposed in \cite{degond_2012} to three
+dimensions. Therefore, it is supposed to be compatible with the original 1D scheme when
+``projected'' to one dimension. This perspective helps to understand how the 3D scheme
+is linked to the 1D. For the sake of presentation, we discuss the one-fluid model of
+\cite{degond_2012}, for which ions are assumed immobile and only the motion of electrons is
+considered.
 
 \subsubsection{Projection to One Dimension} \label{sec:projection_to_1d}
-Consider a mesh pair $(\mathcal{M}, \Tilde{\mathcal{M}})$ that is constructed by 2D extrusion along the $z$-axis and is unbounded in transverse directions.
-Assuming transverse invariance and rotational symmetry, we can ``project'' all the D.o.F.
-onto the $z$-axis.
-The idea is sketched in in Fig.
-\ref{fig:1d_reduction}.
+
+Consider a primal-dual mesh pair $(\mathcal{M}, \Tilde{\mathcal{M}})$ that is constructed by 2D
+extrusion along the $z$-axis and is unbounded in transverse directions. Assuming
+transverse translation invariance and rotational symmetry, we can ``project'' all the d.o.f. onto the
+$z$-axis. The idea is sketched in in Fig.~\ref{fig:1d_reduction}.
 
@@
     \end{tikzpicture}
-    \caption{3D discretization to 1D.
-On the assumption of transverse invariance, we can reduce all the degrees of freedom lying in the perpendicular plane $z=z_k$ to the vertex at $z=z_k$.
-For instance, an edge orthogonal to the $z$-axis is projected to a vertex on the $z$-axis while a parallel edge to the $z$-axis is projected to an edge on the $z$-axis.}
+    \caption{``Projection'' of a 3D discretization to 1D. On the assumption of transverse
+      translation invariance, we can reduce all the degrees of freedom lying in the
+      perpendicular plane $z=z_k$ to the vertex at $z=z_k$. For instance, an edge
+      orthogonal to the $z$-axis is projected to a vertex on the $z$-axis while a parallel
+      edge to the $z$-axis is projected to an edge on the $z$-axis.}
     \label{fig:1d_reduction}
@@
 
-In \cite{degond_2012}, the authors investigate a 1D Maxwell-Euler system by assuming vanishing traverse derivatives.
-For further simplicity, a transverse mode is considered, i.e.
-$u_y, E_y, B_x$, and $B_z$ are set to zero.
-The 1D reduced component-wise one-fluid Maxwell-Euler system and its quasi-neutral limit are
+In \cite{degond_2012}, the authors investigate a 1D Maxwell-Euler system by assuming
+vanishing traverse derivatives. For further simplicity, a transverse mode is considered,
+i.e. $u_y, E_y, B_x$, and $B_z$ are set to zero.  The 1D reduced component-wise one-fluid
+Maxwell-Euler system and its quasi-neutral limit are
 
@@
 \end{minipage}
-where all the fluid variables are attributed to electrons and the subscript indicates the direction of the component.
-An isentropic fluid model with the equation of state $p(n) = n^\gamma$ is assumed to drop the energy equation.
-
-\subsubsection{1D Fully Discrete Plasma Model} \label{sec:1d_fully_discrete_model}
-The fully discrete scheme proposed in \cite{degond_2012} is given below.
-From now on, the superscript of variables involving $m$ indicates the time step.
-The scheme is built on a uniform 1D mesh with cell size $h$ and evolves the system with time step size $\delta^m := t^{m+1} - t^m$:
+where all the fluid variables are attributed to electrons and the subscript indicates the
+direction of the component. An isentropic fluid model with the equation of state
+$p(n) = n^\gamma$ is assumed to drop the energy equation.
+
+\subsubsection{1D Fully Discrete Plasma Model}
+\label{sec:1d_fully_discrete_model}
+
+The fully discrete scheme proposed in \cite{degond_2012} is given below. From now on, the
+superscript $m$ for any variable indicates the time step. The scheme is built on a uniform
+1D mesh with cell size $h$ and evolves the system with time step size
+$\delta^m := t^{m+1} - t^m$:
 
@@
 
-The implicit terms are highlighted and are all essential to achieve the AP property.
-The implicitness of the electric field in the Lorentz force is shown to be necessary in \cite{fabre_1992} for the Euler-Poisson system.
-In \cite{degond_2012}, based on the linearized stability analysis, the author shows that the full-implicit treatment of the Maxwell equations is essential to achieve stability in the quasi-neutral limit.
-Besides, the mass flux in the mass conservation equation and the current in Amp\`{e}re's law has the same level of implicitness to guarantee consistency with Gauss's law.
+The implicit terms are highlighted and are all essential to achieve the AP property. The
+implicitness of the electric field in the Lorentz force is shown to be necessary in
+\cite{fabre_1992} for the Euler-Poisson system. In \cite{degond_2012}, based on the
+linearized stability analysis, the author shows that the full-implicit treatment of the
+Maxwell equations is essential to achieve stability in the quasi-neutral limit. Besides,
+the mass flux in the mass conservation equation and the current in Amp\`{e}re's law has
+the same level of implicitness to guarantee consistency with Gauss's law.
 
 \subsection{Semi-implicit Fully-discrete AP Scheme in 3D} \label{sec:3d_ap_scheme}
-Combining the 3D FIT-FVM framework presented in Section \ref{sec:spatial_discretization} and the time-stepping scheme shown below, we propose the following semi-implicit fully-discrete AP scheme in 3D:
+
+Taking the cue from the formulas of Sec.~\ref{sec:1d_fully_discrete_model} and combining the
+3D FIT/DEC-FVM framework presented in Section \ref{sec:spatial_discretization} and the
+time-stepping scheme shown below, we propose the following semi-implicit fully-discrete AP
+scheme in 3D:
 \begin{subequations}
@@
 \end{subequations}
-The quantities with superscript $m+1/2$ indicate their dependency on the quantities at both $m$-th and $(m+1)$-th iterations.
-In Rusanov flux (\ref{equ:flux_ap}), we denote by $u_\perp$ the normal component velocity with respect to the dual face $\Tilde{A}_k$.
-We confine the illustration of the collision term (\ref{equ:R_coll_ap}) (\ref{equ:Q_coll_ap}) to the two-species case for the sake of simplicity.
-
-The time-stepping scheme mimics the 1D scheme shown in the previous section.
-The implicitness of the friction term is owing to the stiffness incurred from a potentially large value of the prefactor $\varepsilon^{-2}_*\alpha^\text{coll}$.
+A superscript $m+1/2$ indicate a dependence on the quantities at both time step $m$ and
+$(m+1)$. In the Rusanov flux (\ref{equ:flux_ap}), we denote by $u_\perp$ the normal
+component of the velocity $\mathbf{u}$ with respect to the dual face $\Tilde{A}_k$. For
+the sake of simplicity we have confine the presentation of the collision term
+(\ref{equ:R_coll_ap}) (\ref{equ:Q_coll_ap}) to the two-species case .
+
+The time-stepping scheme mimics the 1D scheme shown in the previous section. The
+implicit treatment of the friction term is necessary owing to its potential stiffness in
+case the prefactor $\varepsilon^{-2}_*\alpha^\text{coll}$ attains a large value.
 
 \begin{remark}
-    The AP scheme aims to remove the $\lambda$-dependence of the stability constraint on the time step size.
-Yet time-stepping of the discrete Euler system is still subject to the CFL condition due to the explicitness of the convection.
+  The AP scheme aims to remove the $\lambda$-dependence of the stability constraint on the
+  time step size. Yet time-step size for the fully discrete Euler system is still limited
+  by a CFL condition due to the explicit treatment of the fluid convection.
 \end{remark}
@@
 \subsubsection{Linearly Implicit Time-stepping}
-The semi-implicit scheme (\ref{equ:maxwell_faraday_ap})-(\ref{equ:Q_coll_ap}) entails solving a linear system for each time step.
-Despite the complexity of the whole scheme, we will illuminate the procedure of time-stepping.
-
-\noindent \textbf{Step 1.} We establish the connection between $\mathbf{f}^{\text{mass},m+1/2}_*$ and $\mathbf{d}$ through the momentum equation (see (\ref{equ:euler_ap})(\ref{equ:flux_ap})(\ref{equ:rhs_ap})).
-Relying on the reconstruction (\ref{equ:reconstruction}), a formula of the following format can be achieved
-\begin{equation} \label{equ:relation_nu_and_d}
-    (n\mathbf{u})_*^{m+1} = \hat{\mathbb{M}}^m_* \mathbf{d}^{m+1} + \bm{\eta}_*^m. 
+
+The semi-implicit scheme (\ref{equ:maxwell_faraday_ap})-(\ref{equ:Q_coll_ap}) merely entails
+solving a linear system in each time step. A single time step comprises the following
+computations:
+\medskip
+
+\noindent\fbox{\begin{minipage}[c]{0.985\linewidth}
+  \noindent \textbf{Step 1.} We establish the connection between
+  $\mathbf{f}^{\text{mass},m+1/2}_*$ and $\mathbf{d}$ through the momentum equation (see
+  (\ref{equ:euler_ap})(\ref{equ:flux_ap})(\ref{equ:rhs_ap})). Relying on the
+  reconstruction (\ref{equ:reconstruction}), the following formula emerges:
+  \begin{equation} \label{equ:relation_nu_and_d} (n\mathbf{u})_*^{m+1} =
+    \hat{\mathbb{M}}^m_* \mathbf{d}^{m+1} + \bm{\eta}_*^m.
   \end{equation}
-The expression for the current $\mathbf{J}^{m+1}$ in $\Omega_P$ (see (\ref{equ:maxwell_ampere_plasma_ap})) depends on the mass flux $\bm{f}^{\text{mass},{m+1}}_*$ which then relies on $(n\mathbf{u})_*^{m+1}$ through (\ref{equ:flux_ap}).
-Relying on (\ref{equ:relation_nu_and_d}), one can formulate the following relation:
-\begin{equation} \label{equ:discrete_ohm}
-    \mathbf{j}^{m+1} := \Sigma_\ast q_\ast \bm{f}^{\text{mass},m+1}_\ast = \mathbb{M}_\sigma^{m} \mathbf{d}^{m+1} + \mathbf{j}^m_{\text{aux}}.
+  The expression for the current $\mathbf{J}^{m+1}$ in $\Omega_P$ (see
+  (\ref{equ:maxwell_ampere_plasma_ap})) depends on the mass flux
+  $\bm{f}^{\text{mass},{m+1}}_*$ which, in turn, relies on $(n\mathbf{u})_*^{m+1}$ through
+  (\ref{equ:flux_ap}). Appealing to (\ref{equ:relation_nu_and_d}), one can formulate the
+  following relation:
+  \begin{equation}
+    \label{equ:discrete_ohm}
+    \mathbf{j}^{m+1} := \Sigma_\ast q_\ast \bm{f}^{\text{mass},m+1}_\ast = \mathbb{M}_\sigma^{m} \mathbf{d}^{m+1} + \mathbf{j}^m_{\text{aux}},
   \end{equation}
-where $\mathbb{M}^m_\sigma \in \mathbb{R}^{N_{\Tilde{A}} \times N_{\Tilde{A}}}$ and $\mathbf{j}^m_{\text{aux}} \in \mathbb{R}^{N_{\Tilde{A}}}$.
-The formulas of $\hat{\mathbb{M}}_*^m, \bm{\eta}_*^m, \mathbb{M}_\sigma^m, \mathbf{j}^m_{\text{aux}}$ are slightly lengthy but straightforward, so we omit the details.
-
-\noindent \textbf{Step 2.} Provided (\ref{equ:discrete_ohm}), the discrete Maxwell system (\ref{equ:maxwell_faraday_ap})-(\ref{equ:gauss_nonconducting_ap}) is closed and can be evolved by solving a linear system.
-
-\noindent \textbf{Step 3.} With the updated $\mathbf{d}^{m+1}$, update the momenta $(n\mathbf{u})^{m+1}_*$ by (\ref{equ:relation_nu_and_d}).
-
-\noindent \textbf{Step 4.} the rest of the Euler system can be updated explicitly.
+  where $\mathbb{M}^m_\sigma \in \mathbb{R}^{N_{\Tilde{A}} \times N_{\Tilde{A}}}$ and
+  $\mathbf{j}^m_{\text{aux}} \in \mathbb{R}^{N_{\Tilde{A}}}$.  The formulas of
+  $\hat{\mathbb{M}}_*^m, \bm{\eta}_*^m, \mathbb{M}_\sigma^m, \mathbf{j}^m_{\text{aux}}$
+  are slightly lengthy but straightforward, so we omit the details.
+
+  \noindent \textbf{Step 2.} After (\ref{equ:discrete_ohm}) has been evaluated, the
+  discrete Maxwell system
+  (\ref{equ:maxwell_faraday_ap})-(\ref{equ:gauss_nonconducting_ap}) is closed and can be
+  evolved by solving a linear system.
+
+  \noindent \textbf{Step 3.} With $\mathbf{d}^{m+1}$ at our disposal, we update the
+  momenta $(n\mathbf{u})^{m+1}_*$ according to (\ref{equ:relation_nu_and_d}).
+
+  \noindent \textbf{Step 4.} The remainder of the Euler system can be evolved explicitly.
+\end{minipage}}
+\medskip
 
 \begin{remark}
-    The formula (\ref{equ:discrete_ohm}) functions as Ohm's law on the discrete level.
-Matrix $\mathbb{M}_\sigma^m$ can be treated as a ``conductivity" matrix.
-In the quasi-neutral limit $\lambda \rightarrow 0$ we lose control of the $\mathbf{E}$-field through its time derivative.
-Therefore, $\mathbb{M}_\sigma^m$ is crucial to the stability of the scheme.
-Since $\mathbf{j}$ and $\mathbf{d}$ are both defined on dual faces, it is reasonable to adopt a local relation between them.
-Therefore, we perform the \emph{diagonal lumping} trick, i.e.
-rendering $\mathbb{M}_\sigma^m$ diagonal by accumulating the row sum.
-The lumped $\mathbb{M}_\sigma^m$ has a positive diagonal (for the entity corresponding to $\Omega_P$.
-the rest is zero since no current exists in $\Omega_N$).
-Enhanced stability is observed in the numerical experiments with very minor changes in the results.
+  The formula (\ref{equ:discrete_ohm}) functions as Ohm's law on the discrete
+  level. Matrix $\mathbb{M}_\sigma^m$ can be treated as a ``conductivity" matrix. In the
+  quasi-neutral limit $\lambda \rightarrow 0$ we lose control of the $\mathbf{E}$-field
+  through its time derivative. Therefore, $\mathbb{M}_\sigma^m$ is crucial to the
+  stability of the scheme. Since $\mathbf{j}$ and $\mathbf{d}$ are both defined on dual
+  faces, it is reasonable to adopt a local relation between them. Therefore, we perform
+  the \emph{diagonal lumping} trick, i.e. rendering $\mathbb{M}_\sigma^m$ diagonal by
+  accumulating the row sum. The lumped $\mathbb{M}_\sigma^m$ has a positive diagonal (for
+  the entity corresponding to $\Omega_P$. the rest is zero since no current exists in
+  $\Omega_N$). Enhanced stability is observed in the numerical experiments with very minor
+  changes in the results.
 \end{remark}
-\section{Numerical Experiments} \label{sec:numerical_experiment}
-
-We conduct numerical experiments based on the geometric setting and boundary conditions as presented in Section \ref{sec:BC}.
-The primal-dual mesh pair $(\mathcal{M}, \Tilde{\mathcal{M}})$ is generated based on the code developed in \cite[][Ch.
-1]{fuchs_2021}.
-An instance is shown in Fig.
-\ref{fig:primal_dual_meshes}.
-We consider a two-fluid plasma model which is composed of electrons and ions.
-We set the mass ratio $\varepsilon_e := m_e / m_i = 10^4$ and the collision parameter $\alpha^\text{coll} = 32$.
-
-The source code is published in \cite{yu2022}.
+
+\section{Numerical Tests} \label{sec:numerical_experiment}
+
+We conduct numerical tests based on the geometric setting and boundary conditions as
+presented in Section \ref{sec:BC}. The primal-dual mesh pair
+$(\mathcal{M}, \Tilde{\mathcal{M}})$ is generated as explained in
+\cite[][Ch. 1]{fuchs_2021}. An instance is shown in Fig.~\ref{fig:primal_dual_meshes}. We
+consider a two-fluid plasma model, which comprises electrons and ions. We set the mass
+ratio $\varepsilon_e := m_e / m_i = 10^4$ and the collision parameter
+$\alpha^\text{coll} = 32$. All source codes plus instructions for use are available from
+\url{https://github.com/TianweiCSE/APPM}.
 
 \subsection{Case I: Quasi-1D Problem}
-Noticing the radial symmetry of the domain as well as boundary conditions, we can simplify the governing equations defined at the axis of symmetry, i.e.
-$z$-axis in this case, thanks to vanishing radial components of the vector fields and their radial derivatives.
-The (isentropic and collisionless) Euler-Maxwell system at the axis of symmetry reduces to
+
+Exploiting the radial symmetry of the domain as well as of the boundary conditions, we can
+simplify the governing equations defined at the axis of symmetry, i.e. $z$-axis in this
+case, assuming vanishing radial components of the vector fields and their radial
+derivatives. The (isentropic and collisionless) Euler-Maxwell system at the axis of
+symmetry reduces to
 \begin{align*}
@@
 \end{align*}
-which is nothing but the 1D model in Section \ref{sec:projection_to_1d} after further dropping $u_x, B_y, E_x$.
-We compare the results produced by the 1D scheme (see Section \ref{sec:1d_fully_discrete_model}) and those produced by the 3D scheme (see Section \ref{sec:3d_ap_scheme}) restricted to the $z$-axis.
-The following initial conditions are used for both models
+which is nothing but the 1D model in Section \ref{sec:projection_to_1d} after further
+dropping $u_x, B_y, E_x$. We compare the results produced by the 1D scheme (see Section
+\ref{sec:1d_fully_discrete_model}) and those produced by the 3D scheme (see Section
+\ref{sec:3d_ap_scheme}) restricted to the $z$-axis. The following initial conditions are
+used for both models
 \begin{equation*}
-    n_e(z,0) = n_i(z,0) = 1, u_z(z,0) = \chi_{[-0.1,0]}(z) - \chi_{[0,0.1]}(z),\ \ \forall z \in [-0.1,0.1].
+    n_e(z,0) = n_i(z,0) = 1, u_z(z,0) = \chi_{[-0.1,0]}(z) - \chi_{[0,0.1]}(z)\quad \forall z \in [-0.1,0.1],
 \end{equation*}
-where $\chi$ is the characteristic function. The other variables are initially zero. The case for $\lambda = 1$ is tested. Fig. \ref{fig:z_axis_reduction} demonstrates good matching.
+where $\chi$ is the characteristic function. The other variables are initially
+zero. Results for the choice $\lambda = 1$ are given in Fig.~\ref{fig:z_axis_reduction}
+and demonstrate good matching.
 
@@
     \includegraphics[scale=1.2]{z_axis_reduction.eps}
-    \caption{Case I: Comparison of 1D two-fluid model and reduced 1D model on $z$-axis from 3D two-fluid model.
-The results are both generated on meshes with 64 cells along the $z$-axis.
-$\lambda = 1$.
-No friction term exists.
-$t = 5 \times 10^{-4}.$}
+    \caption{Case I, $\lambda = 1$: Comparison of 1D two-fluid model and of 3D results (at
+      time $t = 5 \times 10^{-4}$ projected onto the $z$-axis. The simulations were both
+      conducted on meshes with 64 cells along the $z$-axis. No friction terms were taken
+      into account.}
     \label{fig:z_axis_reduction}
@@
 
-The cylindrical domain is 5.0 in length and 1.5 in radius.
-The plasma domain $\Omega_P$ is 1.0 in radius, i.e.
-the non-conducting domain $\Omega_N$ has an inner radius of 1.0 and an outer radius of 1.5.
+The cylindrical domain is 5.0 in length and 1.5 in radius. The plasma domain $\Omega_P$ is
+1.0 in radius, i.e. the non-conducting domain $\Omega_N$ has an inner radius of 1.0 and an
+outer radius of 1.5.
 
 \begin{remark}
-    Such an initial state is compatible with the boundary conditions and the quasi-neutral condition $\rho = 0$, which means no initial layer and boundary layer in the sense of perturbation theory will arise when $\lambda \rightarrow 0$.
+  Such an initial state is compatible with the boundary conditions and the quasi-neutrality
+  condition $\rho = 0$, which means no initial layer and boundary layer in the sense of
+  perturbation theory will arise when $\lambda \rightarrow 0$.
 \end{remark}
 
-In Fig.
-\ref{fig:3d_vec_field_E_B_ue}, the numerical solutions for $\lambda = 1.0, 0.1$ and $0$ are shown to visualize the 3D structure of the electromagnetic field.
-Qualitative verification can be done in many aspects.
-First, the rotational symmetry of the problem is preserved.
-Second, the $\mathbf{E}$-field points from $\Gamma^+_C$ to $\Gamma^-_C$ with a relatively uniform value of approximately 0.2 ($=\text{applied voltage}/\text{cylinder length}$) as a consequence of the irrotational $\mathbf{E}$-field in the steady state according to Faraday's law (which is also confirmed in Fig.
-\ref{fig:zaxis-data_vs_z-T_10}.) Note that it does not hold for $\lambda = 1$ since the system has a large characteristic time and takes a long time to reach an equilibrium, as will be shown later in Fig.
-\ref{fig:origin-data_vs_time}.
-Besides, the $\mathbf{B}$-field is azimuthal (spiral-shaped) and orthogonal to the $\mathbf{E}$-field.
-Also, under the electric force, the electrons move towards the anode $\Gamma^+_C$ as expected.
+In Fig. \ref{fig:3d_vec_field_E_B_ue}, the numerical solutions for $\lambda = 1.0, 0.1$
+and $0$ are shown to visualize the 3D structure of the electromagnetic field. Qualitative
+verification can be done in many aspects. First, the rotational symmetry of the problem is
+preserved. Second, the $\mathbf{E}$-field points from $\Gamma^+_C$ to $\Gamma^-_C$ with a
+relatively uniform value of approximately 0.2
+($=\text{applied voltage}/\text{cylinder length}$) as a consequence of the irrotational
+$\mathbf{E}$-field in the steady state according to Faraday's law (, which is also confirmed
+in Fig.~\ref{fig:stabilization_comparison} \textbf{(b)}). Note that it does not hold for $\lambda = 1$
+since the system has a large characteristic time and takes a long time to reach an
+equilibrium, as will be shown later in Fig. \ref{fig:origin-data_vs_time}. Besides, the
+$\mathbf{B}$-field is azimuthal (vortex-shaped) and orthogonal to the
+$\mathbf{E}$-field. Also, under the electric force, the electrons move towards the anode
+$\Gamma^+_C$ as expected.
 \begin{figure}
@@
         \includegraphics[scale=0.25]{electronVel_lambda-1.png}
-        \caption{$\lambda = 1.0$}
+        \caption{\colorbox{yellow!30}{$\lambda = 1.0$}}
     \end{subfigure}
@@
         \includegraphics[scale=0.25]{electronVel_lambda-1e-1.png}
-        \caption{$\lambda = 1.0$}
+        \caption{\colorbox{yellow!30}{$\lambda = 0.1$}}
     \end{subfigure}
@@
         \includegraphics[scale=0.25]{electronVel_lambda-0.png}
-        \caption{$\lambda = 1.0$}
+        \caption{\colorbox{yellow!30}{$\lambda = 0.0$}}
     \end{subfigure}
@@
 
-Next, we perform a grid study.
-Due to the high computational cost in 3D simulations, reference solutions produced by a highly-refined mesh are not available.
-Therefore, we demonstrate results generated by relatively coarse meshes.
-Tab.
-\ref{tab:grid_study_norm} lists $L^2$-norms of the solutions on different meshes, which indicates robustness with respect to mesh refinement.
-To reveal more features of the solutions, in Fig.
-\ref{fig:grid_study_3d_clip_lambda-1e-1} (for $\lambda = 0.1$) and \ref{fig:grid_study_3d_clip_lambda-0} (for $\lambda = 0$) we plot the solutions at the cross-section generated by meshes of different sizes on which qualitatively the same solutions are observed.
+Next, we study the impact of mesh refinement. Due to the high computational cost in 3D
+simulations, reference solutions produced by a highly-refined mesh are not
+available. Therefore, we demonstrate results generated by relatively coarse
+meshes. Tab.~\ref{tab:grid_study_norm} lists $L^2$-norms of the solutions on different
+meshes, which indicates robustness with respect to mesh refinement. To reveal more
+features of the solutions, in Fig.~\ref{fig:grid_study_3d_clip_lambda-1e-1} (for
+$\lambda = 0.1$) and Fig.~\ref{fig:grid_study_3d_clip_lambda-0} (for $\lambda = 0$) we plot
+cross-section a the same locations for solutions produced on different meshes. Reasonable
+qualitative agreement is observed.
 
@@
         \hline\hline
-        \multirow{2}{1em}{$N_V$} & \multicolumn{3}{c}{$\lambda = 1$} & \multicolumn{3}{c}{$\lambda = 0$} \\
+        \multirow{2}{1em}{$N_V$} & \multicolumn{3}{c|}{\colorbox{yellow!30}{$\lambda = 1$}}
+        &
+        \multicolumn{3}{c}{\colorbox{yellow!30}{$\lambda = 0$}} \\
         \cline{2-4} \cline{5-7}
-        & $\|n_e \|_{L^2}$ & $\|\mathbf{E} \|_{L^2}$ & $\|\mathbf{B} \|_{L^2}$ & $\|n_e \|_{L^2}$ & $\|\mathbf{E} \|_{L^2}$ & $\|\mathbf{B} \|_{L^2}$  \\
+        & $\|n_e \|_{L^2}$ & $\|\mathbf{E} \|_{L^2}$ & $\|\mathbf{B} \|_{L^2}$ & $\|n_e
+        \|_{L^2}$
+        & $\|\mathbf{E} \|_{L^2}$ & $\|\mathbf{B} \|_{L^2}$  \\
         \hline
@@
     \end{tabular}
-    \caption{$L^2$-norms of the electron density, the $\mathbf{E}$-field and the $\mathbf{B}$-field on meshes of different size when $\lambda = 1$ or $\lambda = 0$.}
+    \caption{$L^2$-norms of the electron density, the $\mathbf{E}$-field and the
+      $\mathbf{B}$-field on meshes of different size when
+      \colorbox{yellow!30}{$\lambda = 1$} or $\lambda = 0$.}
     \label{tab:grid_study_norm}
@@
     \end{minipage}
-    \caption{Case II: Quantities at the cross-section generated by meshes with different refinement levels: 1920 primal cells in Refinement 1; 14592 primal cells in Refinement 2; 30720 primal cells in refinement 3.
-The snapshots are computed for $\lambda = 0.1$ at $t = 1$.}
+    \caption{Case II: Computed quantities at a cross-section on meshes with different
+      refinement levels: 1920 primal cells in Refinement 1; 14592 primal cells in
+      Refinement 2; 30720 primal cells in refinement 3. The snapshots are computed for
+      \colorbox{yellow!30}{$\lambda = 0.1$} at $t = 1$.}
     \label{fig:grid_study_3d_clip_lambda-1e-1}
@@
 
-    \caption{Case II: Quantities at the cross-section generated by meshes with different refinement levels.
-Refinement 1: 1920 primal cells; Refinement 2: 14592 primal cells; Refinement 3: 30720 primal cells.
-The snapshots are computed for $\lambda = 0$ at $t = 1$.}
+    \caption{Case II: Computed quantities at a cross-section on meshes on different
+      refinement levels. Refinement 1: 1920 primal cells; Refinement 2: 14592 primal
+      cells; Refinement 3: 30720 primal cells. The snapshots are computed for
+      \colorbox{yellow!30}{$\lambda = 0$} at $t = 1$.}
     \label{fig:grid_study_3d_clip_lambda-0}
@@
 
-To inspect how the system evolves, the time histories of some quantities are displayed in Fig.
-\ref{fig:origin-data_vs_time}.
-Being originally at rest, the system is excited by the applied voltage and generates oscillations that decay over time.
-A larger value of $\lambda$ leads to oscillations with larger amplitude and slower damping whereas with a smaller $\lambda$ the system quickly reaches a steady state.
-It is consistent with the fact that $\lambda$ characterizes the time scale of the electromagnetic field.
-From a different perspective, it is a reflection of the shielding effect of plasma which is characterized by the Debye length.
-Besides, the electrons move much faster and oscillate more than ions as a consequence of the large difference in inertia.
-Furthermore, the structure-preserving property of our scheme is revealed by the exact balance of the currents at $\Gamma^+_C$ and $\Gamma^-_C$ \cite{Hiptmair_2021}, as is shown in the last figure in Fig.
-\ref{fig:origin-data_vs_time}.
+To inspect how the system evolves, the time histories of some quantities are displayed in
+Fig.~\ref{fig:origin-data_vs_time}. Being in stable equilibrium at $t=0$, the system is
+excited by applying a voltage and this triggers oscillations that decay over time. A
+larger value of $\lambda$ leads to oscillations with larger amplitude and slower damping,
+whereas for a smaller $\lambda$ the system quickly reaches a steady state. It is
+consistent with the fact that $\lambda$ characterizes the time scale of the
+electromagnetic field. From a different perspective, it is a reflection of the shielding
+effect of the plasma which is characterized by the Debye length. Besides, the electrons
+move much faster and oscillate more than ions as a consequence of the large difference in
+inertia. Furthermore, the structure-preserving property of our scheme is revealed by the
+exact balance of the currents at $\Gamma^+_C$ and $\Gamma^-_C$ \cite{Hiptmair_2021}, as is
+shown in the bottom plot in Fig.~\ref{fig:origin-data_vs_time}.
 
@@
 
-The stabilization proposed in Section \ref{sec:reform-discrete} is essential to achieve a stable result when $\lambda$ tends to zero.
-As is shown in Fig.
-\ref{fig:stabilization_comparison}, the scheme without stabilization tends to blow up when $\lambda$ is close to zero while the one with stabilization remains stable.
+The stabilization proposed in Section \ref{sec:reform-discrete} is essential to achieve
+good results when $\lambda$ tends to zero. As is shown in
+Fig.~\ref{fig:stabilization_comparison} \textbf{(a)}, the scheme without stabilization incurs a blow-up
+when $\lambda$ is close to zero. The proposed stabilization clearly offers a remedy.
 \begin{figure}
     \centering
-    \includegraphics{stabilizationComparision_stepVoltage.eps}
-    \caption{Case II: Stabilization in the non-conducting domain $\Omega_N$. The $\mathbf{E}$-field z-component in a boundary cell in $\Omega_N$ is displayed over time. }
+\begin{minipage}[t]{0.4\textwidth}\centering
+  \includegraphics[width=\textwidth]{stabilizationComparision_stepVoltage.eps}
+
+  \parbox{0.9\textwidth}{\begin{tabular}[c]{ll}
+    \textbf{(a)} & time-dependent z-component of \\ & the $\mathbf{E}$-field
+    in a boundary cell on $\Omega_N$
+  \end{tabular}}
+\end{minipage}%    
+ \begin{minipage}[t]{0.6\textwidth}\centering
+   \includegraphics[width=\textwidth]{data-vs-z_stepVoltage.eps}
+
+   \parbox{0.9\textwidth}{\begin{tabular}[c]{ll}
+     \textbf{(b)} & Quantities along $z$-axis for different $\lambda$; the results \\ & 
+     are computed at $t = 10$ on a mesh with 1920 primal  \\ &  cells and 8 layers along $z$-axis.
+   \end{tabular}}
+\end{minipage}%
+
+\caption{Case II: \textbf{(a)} Stabilization in the non-conducting domain $\Omega_N$,
+  \textbf{(b)} Numerical quasi-neutrality    }
 \label{fig:stabilization_comparison}
@@
 
-The capability of our approach to addressing the non-neutral ($\lambda = \mathcal{O}(1)$) and quasi-neutral ($\lambda = 0$) regimes has been demonstrated in the aforementioned results in the sense that it is stable under different values of $\lambda$.
-Another important check goes to the quasi-neutral condition (\ref{equ:maxwell_gauss_D_limit}) when $\lambda = 0$.
-We display the $\mathbf{E}$-field and particle densities on the $z$-axis in Fig.
-\ref{fig:zaxis-data_vs_z-T_10}.
-The lower figure demonstrates the matching of the density profiles of the electrons and ions, namely, the quasi-neutrality holds on the discrete level.
-
-\begin{figure}
-    \centering
-    \includegraphics{data-vs-z_stepVoltage.eps}
-    \caption{Case II: Quantities along $z$-axis for different $\lambda$: The results are computed at $t = 10$ on a mesh with 1920 primal cells with 8 layers along $z$-axis.}.
-    \label{fig:zaxis-data_vs_z-T_10}
-\end{figure}
+The capability of our approach to deal with the non-neutral ($\lambda = \mathcal{O}(1)$)
+and quasi-neutral ($\lambda = 0$) regimes manifests itself in the reported numerical tests
+in that valid results are produced for different values of $\lambda$ including
+$\lambda=0$. It is instructive to verify the quasi-neutrality condition
+(\ref{equ:maxwell_gauss_D_limit}) when $\lambda = 0$. To that end we display the
+$\mathbf{E}$-field and particle densities on the $z$-axis in
+Fig.~\ref{fig:stabilization_comparison} \textbf{(b)}. The bottom plot demonstrates that
+the density profiles of the electrons and ions offset each other also for computed quantities:
+Quasi-neutrality holds on the discrete level.
 
 \section{Conclusion}
-We have developed an AP scheme for the Euler-Maxwell plasma model in three spatial dimensions that is versatile in both non-neutral $\lambda = \mathcal{O}(1)$ and quasi-neutral $\lambda \rightarrow 0$ regimes.
-The main features of our work lie in: (i) Maxwell's equations are discretized on primal and dual meshes by FIT (in the spirit of DEC).
-By discretizing the Euler equations by FVM on dual mesh, the coupling of two systems is naturally realized via the connection of the mass flux and electric current at each dual face.
-(ii) A non-conducting region is taken into account where additional stabilization is essential when $\lambda \rightarrow 0$.
-We enforce the vanishing divergence of the $\mathbf{D}$-field through a Lagrange multiplier for any value of $\lambda$.
-(iii) The alignment of primal-dual meshes at the boundary entails cut-off cells and auxiliary unknowns have to be introduced.
-iv) A lumping trick is applied to the conductivity matrix (relating the electric current and the electric field) to enhance stability.
-
-Our approach has been tested on a cylindrical domain with settings meant for electric arc simulations.
-The AP property has been verified numerically.
-To the best of the authors' knowledge, this work is among the first to try to solve the 3D fluid plasma model on unstructured meshes, which potentially gives more flexibility than the finite-difference-based approaches and reduces the computational cost compared to particle-based approaches.
-In particular, the AP property allows us to address regimes of the arbitrary value of the Debye length.
+
+We have developed an AP scheme for the Euler-Maxwell plasma model in three spatial
+dimensions that is applicable in both non-neutral $\lambda = \mathcal{O}(1)$ and
+quasi-neutral $\lambda \rightarrow 0$ regimes. The main features of our work lie in: (i)
+Maxwell's equations are discretized on primal and dual meshes by FIT (in the spirit of
+DEC). By discretizing the Euler equations by FVM on the dual mesh, the coupling of two systems
+is naturally realized via the connection of the mass flux and the electric current at each
+dual face. (ii) A non-conducting region is taken into account where additional
+stabilization is essential when $\lambda \rightarrow 0$. We enforce the vanishing
+divergence of the $\mathbf{D}$-field through a Lagrange multiplier for any value of
+$\lambda$. (iii) The alignment of primal-dual meshes at the boundary entails cut-off cells
+and auxiliary unknowns have to be introduced. iv) A lumping trick is applied to the
+conductivity matrix (relating the electric current and the electric field) to enhance
+stability.
+
+Our approach has been tested on a cylindrical domain with settings meant for electric arc
+simulations. The AP property has been verified numerically. To the best of the authors'
+knowledge, this work is among the first to try to solve the 3D fluid plasma model on
+unstructured meshes, which potentially gives more flexibility than the
+finite-difference-based approaches and reduces the computational cost compared to
+particle-based approaches. In particular, the AP property allows us to address regimes
+with vastly different Debye lengths.
 

### 2022-12-21 paper_version/main.tex
add tilde before \ref{}

@@
 the quasi-neutral limit $\lambda \rightarrow 0$, where $\lambda$ is the rescaled Debye
-length, see Section \ref{sec:rescaling} for the underlying scaling arguments and
+length, see Section~\ref{sec:rescaling} for the underlying scaling arguments and
 \cite{degond_2012,degond_2017} for a discussion of the importance of the AP property of
@@
 semi-implicit time-stepping. We also base our considerations on the model geometry shown
-in Fig. \ref{fig:domain_geometry}. We would like to remark that the mesh-based numerical
+in Fig.~\ref{fig:domain_geometry}. We would like to remark that the mesh-based numerical
 scheme proposed in this paper can in principle be adapted to geometric situations much
-more general than that of Fig. \ref{fig:domain_geometry}. However, one may encounter
+more general than that of Fig.~\ref{fig:domain_geometry}. However, one may encounter
 subtle problems in defining proper dual meshes as we need it in Section
@@
 convergence of $P^\lambda_h$ to the $P^\lambda$ as $\lambda\rightarrow0$. Readers are
-referred to the illustration by a commuting diagram in \cite[][Fig. 1]{jin_2010} and, more
+referred to the illustration by a commuting diagram in \cite[][Fig.~1]{jin_2010} and, more
 generally, to the comprehensive reviews \cite{jin_2010, degond_2017} for more details
@@
 
-The content of this paper is organized as follows: In Section \ref{sec:plasma-model}, we
+The content of this paper is organized as follows: In Section~\ref{sec:plasma-model}, we
 give a full description of the underlying equations of the Maxwell-Euler system and its
@@
 primal-dual meshes is introduced based on which FIT and FVM are utilized. We discuss the
-full AP discretization in Section \ref{sec:full-discretization} and do numerical
-experiments in Section \ref{sec:numerical_experiment}.
+full AP discretization in Section~\ref{sec:full-discretization} and do numerical
+experiments in Section~\ref{sec:numerical_experiment}.
 
@@
 $\Gamma_W = \partial\Omega_I \cap \partial\Omega_P$. A geometric arrangement corresponding
-to this setting is sketched in Fig. \ref{fig:domain_sketch} and is the one used in
+to this setting is sketched in Fig.~\ref{fig:domain_sketch} and is the one used in
 \cite[][Ch. 1, Sec. 4]{fuchs_2021}. This situation is simple, but highly relevant. It
@@
 
-No plasma fills the non-conducting domain $\Omega_N$ (see Fig. \ref{fig:domain_sketch}),
+No plasma fills the non-conducting domain $\Omega_N$ (see Fig.~\ref{fig:domain_sketch}),
 and, consequently, the Maxwell system in $\Omega_N$ reduces to 
@@
 boundary condition gives vanishing $\psi$. The importance of this reformulation will
-become clear through numerical experiments, see Section \ref{sec:numerical_experiment}.
+become clear through numerical experiments, see Section~\ref{sec:numerical_experiment}.
 
@@
 Delaunay triangulation $\mathcal{M}$ of the domain and construct $\Tilde{\mathcal{M}}$ by
-connecting \emph{circumcenters} of any two adjacent triangles, see Fig. \ref{fig:2d-mesh}.
+connecting \emph{circumcenters} of any two adjacent triangles, see Fig.~\ref{fig:2d-mesh}.
 In three dimensions, the meshes are constructed by extruding the 2D meshes vertically
 along one axis in a staggered manner \cite[][Sec. 3.1]{Marrone_2001}. See an example in
-Fig. \ref{fig:2d-extrusion}. In this way, the meshes are composed of prisms. This
+Fig.~\ref{fig:2d-extrusion}. In this way, the meshes are composed of prisms. This
 particular choice is compatible with the cylindrical geometric setting that we are in, see
-Fig. \ref{fig:domain_sketch}. For a general setting, one can directly decompose the domain
+Fig.~\ref{fig:domain_sketch}. For a general setting, one can directly decompose the domain
 into tetrahedrons and constructs the Voronoi grid, but the procedure is more
 complicated. The meshes for the cylindrical domain are displayed in
-Fig. \ref{fig:primal_dual_meshes}.
+Fig.~\ref{fig:primal_dual_meshes}.
 
@@
 approximating the material laws on the discrete level (which is the so-called discrete
-Hodge operator \cite{hip_1999, bossavit1999}), as will be shown in Section \ref{sec:fit}.
+Hodge operator \cite{hip_1999, bossavit1999}), as will be shown in Section~\ref{sec:fit}.
 
@@
   \cite[][Sec. 3.1]{tonti_2002}.}. The notion is illustrated in
-Fig. \ref{fig:orientation}. For the entities of the dual mesh $\Tilde{\mathcal{M}}$, we
+Fig.~\ref{fig:orientation}. For the entities of the dual mesh $\Tilde{\mathcal{M}}$, we
 set their internal orientations to be aligned with their corresponding primal entities
@@
 
-Another orientation attribute, \emph{induced orientation}, is defined as follows: an induced orientation of a k-dim entity $f$ with respect to a (k+1)-dim entity $f'$, satisfying $f \subset \partial f' $, is determined by the internal orientation of $f'$ according to the rules shown in Fig.
-\ref{fig:orientation}.
+Another orientation attribute, \emph{induced orientation}, is defined as follows: an induced orientation of a k-dim entity $f$ with respect to a (k+1)-dim entity $f'$, satisfying $f \subset \partial f' $, is determined by the internal orientation of $f'$ according to the rules shown in Fig.~\ref{fig:orientation}.
 
@@
 We will see later that $\mathbb{C}$ functions as a discrete version of the rotation operator.
-The other incidence matrices are constructed in the same manner, see Tab.
-\ref{tab:incidence_mat} for a summary.
-Given the relationship of orientations of $\mathcal{M}$ and $\Tilde{\mathcal{M}}$, we can derive the relations listed in Tab.
-\ref{tab:incidence_relation}.
+The other incidence matrices are constructed in the same manner, see Tab.~\ref{tab:incidence_mat} for a summary.
+Given the relationship of orientations of $\mathcal{M}$ and $\Tilde{\mathcal{M}}$, we can derive the relations listed in Tab.~\ref{tab:incidence_relation}.
 
@@
 Note that the auxiliary edges might not be straight and the auxiliary faces might not be
-flat as is shown in Fig. \ref{fig:illustraion_dual_boundary}, which necessitates a
+flat as is shown in Fig.~\ref{fig:illustraion_dual_boundary}, which necessitates a
 versatile data structure to include such situations. In the following, the auxiliary
 entities would be treated as dual entities, which limits the validity of the relations in
-Tab. \ref{tab:incidence_relation} to interior part of $\Tilde{\mathcal{M}}$. For a more
+Tab.~\ref{tab:incidence_relation} to interior part of $\Tilde{\mathcal{M}}$. For a more
 systematic illustration that considers the boundary dual entities, see
@@
 
-A pair of primal and dual meshes for the geometry in Fig. \ref{fig:domain_sketch} is displayed in Fig. \ref{fig:primal_dual_meshes}.
+A pair of primal and dual meshes for the geometry in Fig.~\ref{fig:domain_sketch} is displayed in Fig.~\ref{fig:primal_dual_meshes}.
 
@@
 The electromagnetic boundary $\partial\Omega = \Gamma_C\cup \Gamma_I$ is resolved by the
-primal mesh $\mathcal{M}$. As is mentioned in Section \ref{sec:BC}, the zero-magnetic-flux
+primal mesh $\mathcal{M}$. As is mentioned in Section~\ref{sec:BC}, the zero-magnetic-flux
 boundary condition $\mathbf{B}\cdot \mathbf{n}$ is equivalent to
@@
 true on the discrete level. We associate with each primal vertex $P_k \in \partial\Omega$
-a scalar value $\varphi_k$. Therefore, the boundary conditions (see Section \ref{sec:BC})
+a scalar value $\varphi_k$. Therefore, the boundary conditions (see Section~\ref{sec:BC})
 are discretized in the following way:
@@
 
-In Section \ref{sec:reform_continuous}, we have proposed a stabilization of the Maxwell
+In Section~\ref{sec:reform_continuous}, we have proposed a stabilization of the Maxwell
 system in the non-conducting domain $\Omega_N$ by introducing a Lagrange multiplier. On
@@
 \end{equation}
-where $\mathbf{d}, \mathbf{b}$ are defined in Tab. \ref{tab:def_size_var};
+where $\mathbf{d}, \mathbf{b}$ are defined in Tab.~\ref{tab:def_size_var};
 $\mathbf{E} := \{\mathbf{E}_k\}_{k=1}^{N_{\Tilde{V}}}$ and
@@
 
-The boundary conditions for the Euler system (see Section \ref{sec:BC}) are implemented by
+The boundary conditions for the Euler system (see Section~\ref{sec:BC}) are implemented by
 the approach of ghost cells \cite[][Ch. 7]{leveque_2007}, i.e. extending the domain by a
@@
 \end{align}
-where $\ast \in \{e, i, \dots\}$ and $\bm{f}^\text{mass}$ denotes the mass flux which is defined in Section \ref{sec:discrete_euler}.
+where $\ast \in \{e, i, \dots\}$ and $\bm{f}^\text{mass}$ denotes the mass flux which is defined in Section~\ref{sec:discrete_euler}.
 By $[\cdots]_k$ we mean taking the $k$-th component of both sides of the equation.
@@
 Taking the cue from the formulas of Sec.~\ref{sec:1d_fully_discrete_model} and combining the
-3D FIT/DEC-FVM framework presented in Section \ref{sec:spatial_discretization} and the
+3D FIT/DEC-FVM framework presented in Section~\ref{sec:spatial_discretization} and the
 time-stepping scheme shown below, we propose the following semi-implicit fully-discrete AP
@@
 We conduct numerical tests based on the geometric setting and boundary conditions as
-presented in Section \ref{sec:BC}. The primal-dual mesh pair
+presented in Section~\ref{sec:BC}. The primal-dual mesh pair
 $(\mathcal{M}, \Tilde{\mathcal{M}})$ is generated as explained in
@@
 \end{align*}
-which is nothing but the 1D model in Section \ref{sec:projection_to_1d} after further
+which is nothing but the 1D model in Section~\ref{sec:projection_to_1d} after further
 dropping $u_x, B_y, E_x$. We compare the results produced by the 1D scheme (see Section
@@
 
-We stick to the setting in Section \ref{sec:BC} and use the following initial conditions
+We stick to the setting in Section~\ref{sec:BC} and use the following initial conditions
 \begin{equation*}
@@
 
-In Fig. \ref{fig:3d_vec_field_E_B_ue}, the numerical solutions for $\lambda = 1.0, 0.1$
+In Fig.~\ref{fig:3d_vec_field_E_B_ue}, the numerical solutions for $\lambda = 1.0, 0.1$
 and $0$ are shown to visualize the 3D structure of the electromagnetic field. Qualitative
@@
 since the system has a large characteristic time and takes a long time to reach an
-equilibrium, as will be shown later in Fig. \ref{fig:origin-data_vs_time}. Besides, the
+equilibrium, as will be shown later in Fig.~\ref{fig:origin-data_vs_time}. Besides, the
 $\mathbf{B}$-field is azimuthal (vortex-shaped) and orthogonal to the
@@
       $\mathbf{B}$-field on meshes of different size when
-      \colorbox{yellow!30}{$\lambda = 1$} or $\lambda = 0$.}
+      \colorbox{yellow!30}{$\lambda = 1$} or \colorbox{yellow!30}{$\lambda = 0$}.}
     \label{tab:grid_study_norm}
@@
 
-The stabilization proposed in Section \ref{sec:reform-discrete} is essential to achieve
+The stabilization proposed in Section~\ref{sec:reform-discrete} is essential to achieve
 good results when $\lambda$ tends to zero. As is shown in

### 2023-01-04 paper_version/main.tex
minor change

@@
 \end{equation}
-where $\mathbf{U} \in L^2(\Omega \times [0,T], \mathbb{R}^m)$ stands for a vector of $m$
-conservative variables,
-$\mathbf{f}(\mathbf{U}) \in L^2(\Omega \times [0,T], \mathbb{R}^{3 \times m})$ is the flux
-function, and $\mathbf{RHS} \in L^2(\Omega \times [0,T], \mathbb{R}^m)$ is the source
-term.. In the case of the full 3D Euler equations (\ref{equ:euler_rescaled}), $m = 5$ and
+where $\mathbf{U} : \Omega \times [0,T] \rightarrow \mathbb{R}^m$ stands for $m$
+conservative variables;
+$\mathbf{f}(\mathbf{U}) : \Omega \times [0,T] \rightarrow \mathbb{R}^{3 \times m}$ is the flux
+function depending on $\mathbf{U}$; $\mathbf{RHS} : \Omega \times [0,T] \rightarrow \mathbb{R}^m$ is the source
+term. In the case of the full 3D Euler equations (\ref{equ:euler_rescaled}), $m = 5$ and
 $\mathbf{U} := [n, n\mathbf{u}, ne]$.

### 2023-02-23 paper_version/main.tex
final revise

@@
 
-\title{APPM report - Draft}
-\author[1]{R. Hiptmair}
-\author[1]{T.W. Yu}
-\author[2]{R. Fuchs}
-\affil[1]{Seminar for Applied Mathematics , ETH Z\"{u}rich}
-\affil[2]{IET Institut für Energietechnik, OST}
+\title{Asymptotic-Preserving Discretization of Three-Dimensional Plasma Fluid Models}
+\author[]{Tianwei Yu \thanks{Seminar for Applied Mathematics , ETH Z\"{u}rich, \texttt{tianwei.yu@math.ethz.ch}}}
+\author[]{Roman Fuchs \thanks{IET Institut für Energietechnik, OST, \texttt{roman.fuchs@ost.ch}}}
+\author[]{Ralf Hiptmair \thanks{Seminar for Applied Mathematics , ETH Z\"{u}rich, \texttt{ralf.hiptmair@math.ethz.ch}}}
+\affil[]{}
 \date{}
@@
 \end{equation}
-and consequently, the rescaled friction heat for ions and electrons take the form:
+and consequently, the rescaled friction heat for ions and electrons takes the form:
 \begin{align} 
@@
 
-The Debye length $\lambda_D$ is the characteristic length over which local net charge is
+The Debye length $\lambda_D$ is the characteristic length over which the local net charge is
 shielded, see \cite[Sec. 1.4]{chen2016} for the underlying physics. In many situations, it
@@
   for $\lambda = \mathcal{O}(1)$ the $\mathbf{E}$-field evolves with time whereas in the
-  quasi-neutral model it responds instantaneously to other quantities according to the
+  quasi-neutral model, it responds instantaneously to other quantities according to the
   constraint (\ref{equ:maxwell_ampere_limit}). We replace
@@
   $\partial_t\mathbf{J}$ can be reformulated by the momentum equation according to
-  (\ref{equ:euler_rescaled}) and we end up with the following wave equation with source
+  (\ref{equ:euler_rescaled}) and we end up with the following wave equation with the source
   terms:
@@
 \begin{remark}
-  The preceeding formal limit argument is heuristic. Deep mathematical tools from
+  The preceding formal limit argument is heuristic. Deep mathematical tools from
   perturbation theory would be needed to rigorously prove the convergence of the limiting
@@
   \cite[Ch. 2]{remi_2014} \cite{Peng_2008} for the quasi-neutral limit of the
-  Maxwell-Euler system, and \cite{mark_1995, Eckhaus_1980} for the general theory.
+  Maxwell-Euler system and \cite{mark_1995, Eckhaus_1980} for the general theory.
 \end{remark}
@@
 to this setting is sketched in Fig.~\ref{fig:domain_sketch} and is the one used in
-\cite[][Ch. 1, Sec. 4]{fuchs_2021}. This situation is simple, but highly relevant. It
+\cite[][Ch. 1, Sec. 4]{fuchs_2021}. This situation is simple but highly relevant. It
 covers fundamental experimental set-ups, for example, those studying wall-stabilized

### 2023-10-17 paper_version/main.tex
final check by Ralf

@@
 \begin{equation} \label{equ:collision}
-    \mathbf{R}_{e}^{\text{coll}} = \frac{\pi Ze^4m_e^{1/2}}{(4\pi\epsilon)^2(k_BT_e)^{3/2}}\text{ln}\Lambda n_en_i(\mathbf{u}_i - \mathbf{u}_e) = - \mathbf{R}_{i}^{\text{coll}},  
+    \mathbf{R}_{e}^{\text{coll}} = \frac{\pi Ze^4m_e^{1/2}}{(4\pi\epsilon)^2(k_BT_e)^{3/2}}\text{\emph{ln}}\Lambda n_en_i(\mathbf{u}_i - \mathbf{u}_e) = - \mathbf{R}_{i}^{\text{coll}},  
 \end{equation}
-which is the collision force acting on electrons. ln$\Lambda$ is called the \emph{Coulomb
+which is the collision force acting on electrons. \emph{ln}$\Lambda$ is called the \emph{Coulomb
   logarithm} and is usually taken as a constant \cite{chen2016}. Because of the
@@
 \cite[][Sec. 2.2]{degond_2017}.  First, a reference value for each quantity is
-prescribed. We define $\overline{x}$ and $\overline{t}$ as space and time scale of
+fixed. We define $\overline{x}$ and $\overline{t}$ as space and time scale of
 interest, by which the reference velocity $\overline{v}$ is defined as
@@
 $\overline{E}$ and $\overline{B}$. The reference magnitudes of fluid quantities are
-denoted by $\overline{u}$ for plasma drift velocity, $\overline{n}$ for plasma number
-density, $\overline{T}$ for plasma temperature. On top of that, the reference pressure is
+denoted by $\overline{u}$ for the plasma drift velocity, $\overline{n}$ for the plasma number
+density, $\overline{T}$ for the plasma temperature. On top of that, the reference pressure is
 set to $\overline{n}k_B\overline{T}$ with $k_B$ being the Boltzmann constant; the
@@
 
-By abuse of notation, the rescaled variables share the same notation as before
-rescaling. We neglect ionization and recombination but retain collision terms,
+Though rescaled, we keep the notations for the various quantities. We neglect ionization and recombination but retain collision terms,
 i.e. $\Gamma_* = 0, \mathbf{R}_* = \mathbf{R}_*^\text{coll}, Q_* = Q_*^\text{coll}$ in
@@
   \end{align}
-  It is obvious in (\ref{equ:E}) that the electric fields propagate with finite speed
-  (hyperbolic evolution) when $\lambda = \mathcal{O}(1)$, whereas for $\lambda = 0$ they
-  respond instantaneously everywhere to local excitation (parabolic evolution/elliptic
+  It is obvious in (\ref{equ:E}) that the electric field propagates with finite speed
+  (hyperbolic evolution) when $\lambda = \mathcal{O}(1)$, whereas for $\lambda = 0$ it
+  responds instantaneously everywhere to local excitation (parabolic evolution/elliptic
   boundary value problems).
@@
 \begin{remark} For a geometric setting with non-trivial topology, e.g. with a tunnel,
-  $\nabla \times \mathbf{E}\cdot\mathbf{n} = 0$ does guarantee the existence of a surface
+  $\nabla \times \mathbf{E}\cdot\mathbf{n} = 0$ does not guarantee the existence of a surface
   potential $\varphi$ satisfying $\mathbf{E}_t = \nabla_\Gamma\varphi$. One needs to
@@
 approaches the quasi-neutral limit as $\lambda \rightarrow 0$, Gauss's law for the
-$\mathbf{D}$-field (\ref{equ:gauss_D_ins}) becomes degenerate. Schemes based on this set
+$\mathbf{D}$-field (\ref{equ:gauss_D_ins}) is no longer enforced. Schemes based on this set
 of PDEs would become unstable as $\lambda \rightarrow 0$. The vanishing divergence
@@
 
-Another orientation attribute, \emph{induced orientation}, is defined as follows: an induced orientation of a k-dim entity $f$ with respect to a (k+1)-dim entity $f'$, satisfying $f \subset \partial f' $, is determined by the internal orientation of $f'$ according to the rules shown in Fig.~\ref{fig:orientation}.
+Another orientation attribute, \emph{induced orientation}, is defined as follows: an induced orientation of a k-dim entity $f$ with respect to a $(k+1)$-dim entity $f'$, satisfying $f \subset \partial f' $, is determined by the internal orientation of $f'$ according to the rules shown in Fig.~\ref{fig:orientation}.
 
@@
     \hline
-         Matrix & Size & Incidence relation & Intuition  \\
+         Matrix & Size & Incidence relation & Operator  \\
     \hline
@@
 versatile data structure to include such situations. In the following, the auxiliary
-entities would be treated as dual entities, which limits the validity of the relations in
-Tab.~\ref{tab:incidence_relation} to interior part of $\Tilde{\mathcal{M}}$. For a more
+entities will be treated as dual entities, which limits the validity of the relations in
+Tab.~\ref{tab:incidence_relation} to the interior part of $\Tilde{\mathcal{M}}$. For a more
 systematic illustration that considers the boundary dual entities, see
-\cite[][Sec. 5]{hip_1999}.
+\cite[][Sec. 5]{hip_1999}. A pair of primal and dual meshes for the geometry in Fig.~\ref{fig:domain_sketch} is displayed in Fig.~\ref{fig:primal_dual_meshes}.
 
@@
 
-A pair of primal and dual meshes for the geometry in Fig.~\ref{fig:domain_sketch} is displayed in Fig.~\ref{fig:primal_dual_meshes}.
-
 \subsection{Discrete Maxwell Equations}
@@
 where $\mathbb{X}_\varphi \in \mathbb{R}^{N_P \times N_P^\partial}$ extends $\bm{\varphi}$
-to all the primal verices by zero. Obviously, the surface gradient $\nabla_\Gamma$ is
+to all the primal vertices by zero. Obviously, the surface gradient $\nabla_\Gamma$ is
 represented by $\mathbb{GX}_\varphi$.
@@
 We employ the finite volume method (FVM) to discretize the Euler system. The Euler
-equations (\ref{equ:euler_}) can be cast into the form of conservation law with source
+equations (\ref{equ:euler_}) can be cast into the form of a conservation law with source
 terms:
@@
 Since the electromagnetic fields are represented by integrals on edges and faces, we need
-to reconstruct their vector components for the computation of Lorentz force (and Joule
+to reconstruct their vector components for the computation of the Lorentz force (and Joule
 heating) inside each dual cell. The task involves two aspects:
@@
 \begin{equation*}
-    \mathbf{v} = \argmin_{\mathbf{w}\in \mathbb{R}^3} \sum_{k=1}^{N_A}(A_k\mathbf{w} \cdot \mathbf{n}_k - f_k)^2.   
+    \mathbf{v} = \argmin_{\mathbf{w}\in \mathbb{R}^3} \sum_{k=1}^{N_A}(A_k\mathbf{w} \cdot \mathbf{n}_k - f_k)^2   
 \end{equation*} can be computed through
@@
 The problem of the reconstruction of vector fields on unstructured meshes is a widely
-studied topic. Apart from the least-square method, other methods include Perot's method
+studied topic. Apart from the least-squares method, other methods include Perot's method
 \citep{perot_2000}, finite-entity-based methods, etc., which potentially can achieve

### 2023-10-17 paper_version/main.tex
minor change

@@
 
-We elaborate a numerical method for a three-dimensional hydrodynamic multi-species plasma
-model which boils down to an extended Euler-Maxwell system. Our method is inspired by and
-extends the one-dimensional scheme from $[$P.~Degond, F.~Deluzet, and D.~Savelief,
-\emph{Numerical approximation of the Euler-Maxwell model in the quasineutral limit}, Journal of
-Computational Physics, 231 (4), pp.~1917--1946, 2012$]$. It can cope with large variations
-of the so-called Debye length $\lambda_D$ and is robust in the quasi-neutral
-singular-perturbation limit $\lambda_D\to 0$, because it enjoys an
-\emph{asymptotic-preserving} (AP) property in the sense that in the sense that the limit
-$\lambda_D\to 0$ of the scheme yields a viable discretization for the continuous limit
-model. The key ingredients of our approach are (i) a discretization of Maxwell's equations
-based on primal and dual meshes in the spirit of \emph{discrete exterior calculus} (DEC)
-also known the finite integration technique (FIT), (ii) a finite volume method (FVM) for
-the fluid equations on the dual mesh, (iii) \emph{mixed implicit-explicit timestepping},
-(iv) special no-flux and contact boundary conditions at an outer cut-off boundary, and (v)
-additional \emph{stabilization} in the non-conducting region outside the plasma domain
-based on direct enforcement of Gauss' law. Numerical tests provide strong evidence
-confirming the AP property of the new method.
+We elaborate a numerical method for a three-dimensional hydrodynamic multi-species plasma model described by the Euler-Maxwell equations.
+Our method is inspired by and extends the one-dimensional scheme from $[$P.~Degond, F.~Deluzet, and D.~Savelief, \emph{Numerical approximation of the Euler-Maxwell model in the quasineutral limit}, Journal of Computational Physics, 231 (4), pp.~1917--1946, 2012$]$.
+It can cope with large variations of the Debye length $\lambda_D$ and is robust in the quasi-neutral limit $\lambda_D\to 0$ thanks to its \emph{asymptotic-preserving} (AP) property.
+The key ingredients of our approach are (i) a discretization of Maxwell's equations based on primal and dual meshes in the spirit of \emph{discrete exterior calculus} (DEC) also known as the finite integration technique (FIT), (ii) a finite volume method (FVM) for the fluid equations on the dual mesh, (iii) \emph{mixed implicit-explicit timestepping}, (iv) special no-flux and contact boundary conditions at an outer cut-off boundary, and (v) additional \emph{stabilization} in the non-conducting region outside the plasma domain based on direct enforcement of Gauss' law.
+Numerical tests provide strong evidence confirming the AP property of the proposed method.
 

### 2024-03-07 paper_version/rebuttal_letter.tex
review

%-----------------------------------------------------------------------------%
\documentclass[a4paper, 10pt]{letter}

\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{bm}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{xcolor}
\geometry{a4paper,scale=0.8}

%-----------------------------------------------------------------------------%

\begin{document}

\begin{letter}
\opening{Dear Editors,}

We thank the reviews for the generous and insightful comments on our work and have revised the manuscript to address their concerns. The corresponding replies for each comments are attached in the end.

We believe that the manuscript is now suitable for publication.

\closing{On behalf of all authors,\\ \vspace{1cm} Tianwei Yu}
\end{letter}

\newpage

\begin{itemize}
  \item Question 1.1: \textcolor{violet}{Can the new 3D scheme reduces to Degond's 1D scheme?}
  \item[$\blacktriangleright$] Reply: \textcolor{blue}{
  Yes. The proposed numerical scheme in 3D is a natural extension of the 1D
  the scheme proposed by Degond et. al. This is justified by considering problems with
  transverse invariance (namely, variables keep constant along the x-axis and y-axis) and
  verifying that the "projected" 3D scheme coincides with the original 1D scheme at the z-axis.
  Section~4.1 is devoted to such a purpose. To better clarify this point, we add a remark
  right after the 3D full discretization: ``When applying the ``projection to one dimension"
  described in Section~4.1.1, the fully discrete 3D AP scheme (32) collapses to (31)
  discretization proposed in $[$P.~Degond, F.~Deluzet, and D.~Savelief, \emph{Numerical approximation of the Euler-Maxwell model in the quasineutral limit}, Journal of Computational Physics, 231 (4), pp.~1917--1946, 2012$]$. This is not a coincidence, because
  recovering of (31) under dimensional reduction has guided our construction."
  }

  \item Question 1.2: \textcolor{violet}{In Fig 8, Page 19, it seems the 1D results are better than the 3D results by using the same meshes. Can the new 3D scheme
  preserve some good properties of the original 1D scheme?}
  \item[$\blacktriangleright$] Reply: \textcolor{blue}{
  Technically speaking, Fig.~8 is a ``verification" rather than a ``comparison".
  The result produced by the 3D scheme, as illustrated in Section~5.1, is the
  solution along the z-axis for the cylindrical setting in Fig.~2. To better
  clarify this point, we add some comments in the description of Fig.~8:
  ``... The 3D result is generated under the setting in Fig.~2
  and restricted to the z-axis. The results are slightly different from
  the 1D result probably due to the impact of the outer boundary of the
  cylindrical domain."
  }

  \item Question 1.3: \textcolor{violet}{In numerical tests, the mass ratio and the collision parameter are computed by a constant number. Is it sufficient to
demonstrate the good performance of the new scheme?}
  \item[$\blacktriangleright$] Reply: \textcolor{blue}{
  We agree that the robustness with respect to the mass ratio and the collision parameter
  is worth studying in dealing with the plasma model.
  However, the objective of the proposed scheme is stability with respect to
  the Debye length $\lambda$. The impacts of the mass ratio and the collision parameter
  are not of our central interest.
  In fact, our scheme does not possess uniform stability over the mass ratio $\varepsilon_*$
  yet has it over the collision parameter $\alpha^{\text{coll}}$. This can be
  inferred from (32j) by noticing the explicit term
  $\varepsilon_*^{-2}q_*(n\mathbf{u})_*^m \times \mathbf{B}^m$
  and the implicit terms
  $\varepsilon_*^{-2}\mathbf{R}^{\text{coll}, m+1}_*, \varepsilon_*^{-2}Q^{\text{coll}, m+1}_*$.
  It seems possible to achieve stability over the mass ratio $\varepsilon_*$
  by replacing $\varepsilon_*^{-2}q_*(n\mathbf{u})_*^m \times \mathbf{B}^m$
  by $\varepsilon_*^{-2}q_*(n\mathbf{u})_*^{m+1} \times \mathbf{B}^{m}$.
  However, this would significantly change the time-stepping procedure.
  We decide not to pursue this and want to be aligned with Degond's scheme.
  }

  \item Question 1.4: \textcolor{violet}{Include the following references:
  [Fast-Converging and Asymptotic-Preserving Simulation of Frequency Domain Thermoreflectance, Jia Liu \& Lei Wu. Commun. Comput. Phys., 34 (2023), pp. 65-93.]
  [A Coupled FEM-BEM Approach for the Solution of the Free-Boundary Axi-Symmetric Plasma Equilibrium Problem. M. Bonotto, D. Abate, P. Bettni \& F. Villone. Commun. Comput. Phys., 31 (2022), pp. 27-59.]}
  \item[$\blacktriangleright$] Reply: \textcolor{blue}{Both paper is included in the introduction.
  The first paper is added to the literature review on AP schemes
  while the second one is mentioned when the symmetry of the problem is discussed.}
\end{itemize}

\newpage

\begin{itemize}
  \item Question 2.1: \textcolor{violet}{The literature review provided in the paper is incomplete.
  Numerous structure-preserving schemes for plasma models involving the Euler
  and Maxwell equations exist, such as the compressible ideal MHD model.
  Relevant works should include, but not be limited to:
  \begin{itemize}
      \item[1)] The positivity-preserving and divergence-free finite volume schemes and
  central discontinuous Galerkin schemes (also using the primal and dual meshes);
  see, e.g., [K. Wu, SIAM Journal on Numerical Analysis, 56(4):2124-2147, 2018]
  and [K. Wu, H. Jiang, and C.-W. Shu, SIAM Journal on Numerical Analysis, 61: 250-285, 2023].
      \item[2)] These schemes are designed by using the geometric quasilinearization framework in
  [K. Wu and C.-W. Shu, SIAM Review, 65(4):1031-1073, 2023],
  where the multicomponent MHD equations for multi-species plasma were also studied.
      \item[3)] High-order asymptotic preserving (AP) finite difference WENO schemes with
  constrained transport were also developed for MHD equations in
  [W. Chen, K. Wu, and T. Xiong, Journal of Computational Physics, 488: 112240, 2023].
  \end{itemize}}

  \item[$\blacktriangleright$] Reply: \textcolor{blue}{
  We have added a paragraph at the end of Section~2.2. A short discussion and literature
  review on the numerical methods for plasma models is presented with a focus on the
  structure-preserving property. The literature mentioned in 3) is included in the
  literature review in Section~1 when discussing AP schemes.
  }

  \item Questions 2.2: \textcolor{violet}{The author did not provide an accuracy test
  for the convergence rate of their proposed numerical method.
  An illustrative example can be found in section 6.2 of
  [K. Wu, H. Jiang, and C.-W. Shu, SIAM Journal on Numerical Analysis, 61: 250-285, 2023],
  as well as in Examples 5.1 and 5.2 in [W. Chen, K. Wu, and T. Xiong, Journal of Computational Physics, 488: 112240, 2023]}
  \item[$\blacktriangleright$] Reply: \textcolor{blue}{
  To handle this issue, we put some effort into re-devising the matrix assembly which
  now admits a fast iterative solver such that reference solutions on sufficiently refined
  meshes are possible. A new case involving a cuboid domain is tested and
  $L^1$ and $L^2$ errors at different values of $\lambda$ are reported in the same manner as suggested by the second paper.
  A smooth test case seems hard to construct due to the presence of the interface of two different
  electromagnetic boundary conditions in our underlying setting depicted in Fig.~2.
  }

  \item Question 2.3: \textcolor{violet}{
  Limited Numerical Examples: All the numerical examples provided in the paper
  are either one-dimensional or three-dimensional cylindrical. To strengthen the paper's contribution,
  it is advisable to include a genuinely three-dimensional example.
  This is especially relevant as one of the primary contributions of the paper lies in the
  extension of a one-dimensional scheme to three dimensions.
  }
  \item[$\blacktriangleright$] Reply: \textcolor{blue}{
  We include a slightly more general 3D case in Case IV. Yet we would like to mention that 
  our current framework of primal-dual mesh generation is based on the idea of
  ``extruding 2D mesh" in Sec.~4.2.1 of
  $[$Marrone, Massimiliano.\emph{Computational Aspects of the Cell Method in Electrodynamics - Abstract.} Journal of Electromagnetic Waves and Applications 15 (2001): 407 - 408.$]$.
  It has not been extended yet to arbitrary geometries, which possibly takes quite some effort.
  Therefore, we have decided to defer this part to future work. Nevertheless,
  the proposed scheme can be directly applied to arbitrary domains
  as long as the primal-dual meshes are generated properly.
  }
\end{itemize}

\end{document}
%-----------------------------------------------------------------------------%

### 2024-03-07 paper_version/main.tex
review

@@
 \usepackage{multirow}
+\usepackage{comment}
 
@@
 }
+
+\def\ifUpdate{1}
+
+\newcommand{\review}[1]{\textcolor{blue}{\if\ifUpdate1\textbf{#1}\fi}}
+\newcommand{\reviewDel}[1]{\begin{comment} #1 \end{comment}}
 
@@
 We stay close to \cite{degond_2012} in terms of discretization in time employing
-semi-implicit time-stepping. We also base our considerations on the model geometry shown
-in Fig.~\ref{fig:domain_geometry}. We would like to remark that the mesh-based numerical
+semi-implicit time-stepping. We base our illustration on the model case shown
+in Fig.~\ref{fig:domain_geometry}. Yet we would like to remark that the mesh-based numerical
 scheme proposed in this paper can in principle be adapted to geometric situations much
-more general than that of Fig.~\ref{fig:domain_geometry}. However, one may encounter
-subtle problems in defining proper dual meshes as we need it in Section
-\ref{sec:mesh-duality}. Thus, for the sake of simplicity of presentation we forgo
-geometric generality.
+more general than that of Fig.~\ref{fig:domain_geometry}. \review{In particular, we do not 
+assume the solution to enjoy the rotational symmetry. If the symmetry is assumed, 
+it can be exploited for reduction to two spatial dimensions \cite{bonotto_2022}.}
 
@@
   Maxwell-Euler system switches from hyperbolic to mixed for $\lambda_{D}\to 0$}. This
-poses a challenge for simulations in settings encompassing different regimes. We remind
-that singularly perturbed problems occur in many physical models, e.g., in the case of
-vanishing viscosity in the Navier-Stokes equations \cite{Kato_1984}, the
-zero-relaxation-limit of kinetic equations \cite{jin_2010}, and the zero-Mach-number limit
-of compressible flows \cite{degond_2007, haack_2010}. Throughout, it is essential that
+poses a challenge for simulations in settings encompassing different regimes. 
+Beside the quasi-neutral limit, we remind
+that singularly perturbed problems occur in extensively many physical models, 
+e.g., in the case of vanishing viscosity problem \cite{Kato_1984, bianchini_2005, temam_1997}, the
+zero-relaxation-limit of kinetic-type equations \cite{raymond_2009, degond_1996}, and the incompressible limit
+of compressible flows \cite{klainerman_1981}. Throughout, it is essential that
 numerical schemes remain valid even if crucial model parameters approach the limit. These
@@
 discretization parameter, e.g., the mesh size. The AP property amounts to uniform
-convergence of $P^\lambda_h$ to the $P^\lambda$ as $\lambda\rightarrow0$. Readers are
-referred to the illustration by a commuting diagram in \cite[][Fig.~1]{jin_2010} and, more
-generally, to the comprehensive reviews \cite{jin_2010, degond_2017} for more details
-about AP schemes.
+convergence of $P^\lambda_h$ to the $P^\lambda$ as $\lambda\rightarrow0$. 
+The concept is effectively depicted by a commuting diagram in \cite[][Fig.~1]{jin_2010}. 
+\review{AP schemes have been extensively studied for various problems, e.g. the diffusive limit of the kinetic equations \cite{jin_1999, liu_2023}, 
+the low Mach-number limit of compressible flows \cite{degond_2007, haack_2010} and magnetohydrodynamics\cite{chen_2023}, 
+the quasi-neutral limit of drift-diffusion equations \cite{chatard_2014, claire_2007}. 
+More generally, readers are referred to the comprehensive reviews \cite{jin_2010, degond_2017}.}
 
@@
     \draw[very thick] (PP1) -- (PP2); 
-    \draw[black, very thick] (SS2) arc (101.31:180+101.31:1.5);
+    \draw[violet] (SS2) arc (101.31:180+101.31:1.5);
     \draw[very thick] (PP2) arc (101.31-180:101.31:1.5);
@@
 extension to more species is straightforward. Such collisions can be well modelled by
-friction terms, for instance \citep[][Sec. 5.6.2]{chen2016}
+friction terms, for instance \citep[][Sec.~5.6.2]{chen2016}
 \begin{equation} \label{equ:collision}
@@
 modeling of these physical processes, readers are referred to
-\cite[][Sec. 3.2]{fuchs_2021}.
+\cite[][Sec.~3.2]{fuchs_2021}.
 \end{remark}
@@
 % In rescaling, variables in equations are replaced by the ratio of original quantities and constant reference quantities, which transforms the system into dimensionless form.
-In this part, the rescaling procedure mostly follows that of \cite[][Sec.
-2.2]{degond_2017}.
+In this part, the rescaling procedure mostly follows that of \cite[][Sec.~2.2]{degond_2017}.
 
 We arrive at non-dimensional equations by following the rescaling procedure of
-\cite[][Sec. 2.2]{degond_2017}.  First, a reference value for each quantity is
+\cite[][Sec.~2.2]{degond_2017}.  First, a reference value for each quantity is
 fixed. We define $\overline{x}$ and $\overline{t}$ as space and time scale of
@@
 \footnotetext[1]{Abbreviation of \emph{with respect to}.}
-\footnotetext[2]{It is basically the reciprocal of the number of particles per Debye sphere, see \cite[][Sec. 1.1]{gibbon2020}. Classical plasma theory assumes $g \ll 1$.}
+\footnotetext[2]{It is basically the reciprocal of the number of particles per Debye sphere, see \cite[][Sec.~1.1]{gibbon2020}. Classical plasma theory assumes $g \ll 1$.}
 
@@
 Assumptions can be made to reduce the number of dimensionless parameters. Following
-\cite[][Sec. 2.2]{degond_2017}, the reference speed $\overline{v}$ is of the same scale as
+\cite[][Sec.~2.2]{degond_2017}, the reference speed $\overline{v}$ is of the same scale as
 the plasma speed $\overline{u}$ and the thermal speed $v_i^{\text{th}}$ whereas it is much
@@
 single parameter, whose value may tend to zero:
-\begin{subequations}
+\begin{subequations} \label{equ:euler-maxwell-rescaled}
   \label{resc}
@@
 
+\review{
+It is worth mentioning that an important aspect of devising numerical schemes is the structure-preserving property which is concerned with keeping some constraints at the discrete level.
+In this context, some typical constraints are the positivity of densities and pressures, the entropy inequality, zero divergence of the $\mathbf{B}$-field, etc.
+There are in general two ways of numerically approaching the coupled system (\ref{equ:euler-maxwell-rescaled}) or its reduced models, e.g.
+the magnetohydrodynamic (MHD) equations.
+The first approach is to lump all the equations into one hyperbolic system of conservation laws and apply finite volume methods.
+Such numerical methods are rather simple to implement and also computationally efficient.
+Complications typically go to ensuring the stability and the divergence constraint which requires suitable numerical fluxes and limiters.
+Schemes that are provably positive, entropy-stable, or divergence-free have been constructed, see \cite{wu_2018, wu_2023a, wu_2023b, kumar_2011, fuchs_2009} and references therein.
+The second class of numerical methods handles the electromagnetic part and the fluid part separately.
+The rationale behind such a splitting strategy is that dedicated solvers for subsystems are rather mature.
+Particularly, the divergence constraint can be easily handled by finite element exterior calculus.
+Yet the implementation of coupled solvers is usually complicated.
+To name some related work, \cite{fuchs_2009} applies dedicated finite volume schemes to each subsystem; \cite{hu_2017, hiptmair_2018} treat the electromagnetic part via finite element exterior calculus.
+The scheme proposed in this work lies in the second category and by construction satisfies the divergence-free constraint at the discrete level.
+Nevertheless, we do not pursue the structure-preserving property while focusing on the asymptotic-preserving property in this work.
+}
+
 \subsection{Quasi-neutral Limit}
@@
 The Debye length $\lambda_D$ is the characteristic length over which the local net charge is
-shielded, see \cite[Sec. 1.4]{chen2016} for the underlying physics. In many situations, it
+shielded, see \cite[Sec.~1.4]{chen2016} for the underlying physics. In many situations, it
 has a very small value compared to the reference length scale: the typical $\lambda_D$ for
 gas discharge and Tokamak fusion reactors is $10^{-4}$ meter, for interstellar medium, the
-magnitude is about $1$ meter \cite[Ch. 20]{Blandford_2013}. Then the quasi-neutrality
+magnitude is about $1$ meter \cite[Chapt.~20]{Blandford_2013}. Then the quasi-neutrality
 assumption $\rho = \sum_* q_*n_* \approx 0$ is justified, which is typical of the limit
@@
   sequence. This topic is beyond the scope of this paper. Readers are referred to
-  \cite[Ch. 2]{remi_2014} \cite{Peng_2008} for the quasi-neutral limit of the
+  \cite[Chapt.~2]{remi_2014} \cite{Peng_2008} for the quasi-neutral limit of the
   Maxwell-Euler system and \cite{mark_1995, Eckhaus_1980} for the general theory.
@@
 to this setting is sketched in Fig.~\ref{fig:domain_sketch} and is the one used in
-\cite[][Ch. 1, Sec. 4]{fuchs_2021}. This situation is simple but highly relevant. It
+\cite[][Chapt.~1, Sec.~4]{fuchs_2021}. This situation is simple but highly relevant. It
 covers fundamental experimental set-ups, for example, those studying wall-stabilized
@@
     \begin{scope}[shift={(5.5,-1.4)}]
-    \draw[blue, -to] (0,0) -- (0.65,0.12) node[right]{\small $z$};
+        \draw[blue, -to] (0,0) -- (20:0.7) node[right]{\small $z$};
         \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
@@
   of the other mesh and that each vertex of one mesh lies inside of a cell of the other
-  mesh} \cite[][Sec. 2]{weiland_2003}. Examples are shown in Fig.~\ref{fig:cartesian}.
+  mesh} \cite[][Sec.~2]{weiland_2003}. Examples are shown in Fig.~\ref{fig:cartesian}.
 
@@
 In three dimensions, the meshes are constructed by extruding the 2D meshes vertically
-along one axis in a staggered manner \cite[][Sec. 3.1]{Marrone_2001}. See an example in
+along one axis in a staggered manner \cite[][Sec.~3.1]{Marrone_2001}. See an example in
 Fig.~\ref{fig:2d-extrusion}. In this way, the meshes are composed of prisms. This
@@
   alternative approach is barycenter-based dual meshes, which are not restricted to an
-  acute-angle triangulation \cite[][Sec. 4.2]{Marrone_2001}.
+  acute-angle triangulation \cite[][Sec.~4.2]{Marrone_2001}.
 \end{remark}
@@
     orientation}, which has a slightly different definition, see
-  \cite[][Sec. 3.1]{tonti_2002}.}. The notion is illustrated in
+  \cite[][Sec.~3.1]{tonti_2002}.}. The notion is illustrated in
 Fig.~\ref{fig:orientation}. For the entities of the dual mesh $\Tilde{\mathcal{M}}$, we
@@
 systematic illustration that considers the boundary dual entities, see
-\cite[][Sec. 5]{hip_1999}. A pair of primal and dual meshes for the geometry in Fig.~\ref{fig:domain_sketch} is displayed in Fig.~\ref{fig:primal_dual_meshes}.
+\cite[][Sec.~5]{hip_1999}. A pair of primal and dual meshes for the geometry in Fig.~\ref{fig:domain_sketch} is displayed in Fig.~\ref{fig:primal_dual_meshes}.
 
@@
 approximation error is introduced due to the implicit assumption that vector fields are
-piecewise constant, see the analysis in \cite[][Sec. 3.2]{Marrone_2001}.
+piecewise constant, see the analysis in \cite[][Sec.~3.2]{Marrone_2001}.
 
@@
 
-\subsubsection{Reconstruction of Lorentz Force}
+\subsubsection{Reconstruction of Lorentz Force} \label{sec:recon_lorentz_f}
 
@@
 \citep{perot_2000}, finite-entity-based methods, etc., which potentially can achieve
-higher-order accuracy. See \cite[][Sec. 3.4.4]{fuchs_2021} and the references therein.
+higher-order accuracy. See \cite[][Sec.~3.4.4]{fuchs_2021} and the references therein.
 
@@
 The boundary conditions for the Euler system (see Section~\ref{sec:BC}) are implemented by
-the approach of ghost cells \cite[][Ch. 7]{leveque_2007}, i.e. extending the domain by a
+the approach of ghost cells \cite[][Chapt.~7]{leveque_2007}, i.e. extending the domain by a
 layer of virtual cells with prescribed variables. In our case, the ghost cells at the open
@@
 
+\review{
+\begin{remark}
+When applying the ``projection to one dimension"
+  described in Section~4.1.1, the fully discrete 3D AP scheme (32) collapses to (31)
+  discretization proposed in \cite{degond_2012}. This is not a coincidence, because
+  recovering of (31) under dimensional reduction has guided our construction.
+\end{remark}
+}
+
 \begin{remark}
@@
 $(\mathcal{M}, \Tilde{\mathcal{M}})$ is generated as explained in
-\cite[][Ch. 1]{fuchs_2021}. An instance is shown in Fig.~\ref{fig:primal_dual_meshes}. We
+\cite[][Chapt.~1]{fuchs_2021}. An instance is shown in Fig.~\ref{fig:primal_dual_meshes}. We
 consider a two-fluid plasma model, which comprises electrons and ions. We set the mass
@@
       conducted on meshes with 64 cells along the $z$-axis. No friction terms were taken
-      into account.}
+      into account. \review{The 3D result is generated under the setting in Fig.~2
+  and restricted to the z-axis. They are slightly different from
+  the 1D results possibly due to the impact of the outer boundary of the
+  3D domain.}}
     \label{fig:z_axis_reduction}
@@
 
-\subsection{Case II: 3D Cylindrical Problem}
+\review{
+\subsection{Case II: 3D cuboid domain (convergence study for a range of $\epsilon$)} 
+The scheme is tested at different mesh resolutions and the convergence rates are estimated.
+The problem setting follows the one depicted in Fig.~\ref{fig:domain_sketch} while we adopt a cuboid domain, see Fig.~\ref{fig:cube_domain_sketch}.
+Under this setting, we decompose the domain with structured Cartesian meshes and benefit from simpler error computation.
+The initial conditions are
+\begin{equation*}
+    n_\ast(\mathbf{x}, 0) = 1, \ \ \  p_\ast(\mathbf{x},0) = 1, \ \ \forall \mathbf{x}\in\Omega, \ast \in \{e, i\}
+\end{equation*}
+and zero for the other variables.
+We set $\varphi(\mathbf{x}, t)|_{\Gamma_C^-} = 0, \varphi(\mathbf{x}, t)|_{\Gamma_C^+} = 10\times t$, that is, one electrode is grounded and a linear voltage is applied on the other electrode.
+The results are computed for the final time $t = 0.01$.
+Tab.~\ref{tab:grid_study_cube} lists the errors for the $\mathbf{E}$-field, $\mathbf{B}$-field, and electron densities where the reference solutions are generated by a sufficiently fine mesh with $2^{18} = 262144$ cells.
+The results show uniform convergence over $0\leq \lambda \leq 1$, a justification of the AP property.
+It is expected that the convergence rate does not exceed one since the reconstruction of the electromagnetic field discussed in Section~\ref{sec:recon_lorentz_f} is only of first order and the numerical flux used for solving the Euler equations is also of first order.
+The $1/2$-order reduction observed in the $L^2$-error of the $\mathbf{E}$-field and the electron density is possibly the consequence of singularity in the solution due to the interface of different types of boundary conditions (electrodes and insulating boundary).
+\begin{table}[!ht]
+    \review{
+    \centering
+    \subfloat[\colorbox{yellow!30}{$\lambda = 1$}]{
+        \begin{tabular}{c | c c | c c | c c }
+            \hline\hline
+            \multirow{2}{1em}{$N_V$} & \multicolumn{2}{c|}{$\mathbf{E}$-field}
+            &
+            \multicolumn{2}{c|}{$\mathbf{B}$-field} & \multicolumn{2}{c}{electron density} \\
+            \cline{2-4} \cline{5-7}
+            & $L^1$-error & $L^2$-error & $L^1$-error & $L^2$-error
+            & $L^1$-error & $L^2$-error  \\
+            \hline
+             64   &  0.369 & 0.0712 & 5.88 & 1.14 & 6.67 & 1.83 \\
+             512  &  0.195 & 0.0493 & 3.13 & 0.77 & 3.09 & 1.36 \\
+             4096 &  0.087 & 0.0332 & 0.98 & 0.34 & 1.26 & 0.76 \\
+             \hline
+             aver. rate & 1.05 & 0.55 & 1.34 & 0.90 & 1.21 & 0.65 \\
+             \hline\hline
+        \end{tabular}
+    }\\
+    \vspace{0.5cm}\subfloat[\colorbox{yellow!30}{$\lambda = 0.01$}]{
+        \begin{tabular}{c | c c | c c | c c }
+            \hline\hline
+            \multirow{2}{1em}{$N_V$} & \multicolumn{2}{c|}{$\mathbf{E}$-field}
+            &
+            \multicolumn{2}{c|}{$\mathbf{B}$-field} & \multicolumn{2}{c}{electron density} \\
+            \cline{2-4} \cline{5-7}
+            & $L^1$-error & $L^2$-error & $L^1$-error & $L^2$-error
+            & $L^1$-error & $L^2$-error  \\
+            \hline
+             64   &  0.141 & 0.0271 & 1.52E-3 & 2.67E-4 & 6.67 & 1.83 \\
+             512  &  0.094 & 0.0214 & 8.21E-4 & 1.47E-4 & 3.09 & 1.36 \\
+             4096 &  0.041 & 0.0113 & 3.84E-4 & 6.93E-5 & 1.26 & 0.76 \\
+             \hline
+             aver. rate & 0.93 & 0.66 & 1.00 & 0.98 & 1.21 & 0.65 \\
+             \hline\hline
+        \end{tabular}
+    }\\
+    \vspace{0.5cm}\subfloat[\colorbox{yellow!30}{$\lambda = 0$}]{
+        \begin{tabular}{c | c c | c c | c c }
+            \hline\hline
+            \multirow{2}{1em}{$N_V$} & \multicolumn{2}{c|}{$\mathbf{E}$-field}
+            &
+            \multicolumn{2}{c|}{$\mathbf{B}$-field} & \multicolumn{2}{c}{electron density} \\
+            \cline{2-4} \cline{5-7}
+            & $L^1$-error & $L^2$-error & $L^1$-error & $L^2$-error
+            & $L^1$-error & $L^2$-error  \\
+            \hline
+             64   &  0.127 & 0.0274 & 9.46E-4 & 1.58E-4 & 6.67 & 1.83 \\
+             512  &  0.100 & 0.0212 & 6.26E-4 & 1.05E-4 & 3.09 & 1.36 \\
+             4096 &  0.038 & 0.0110 & 2.49E-4 & 4.33E-5 & 1.26 & 0.76 \\
+             \hline
+             aver. rate & 0.96 & 0.69 & 1.00 & 0.98 & 1.21 & 0.65 \\
+             \hline\hline
+        \end{tabular}
+    }
+    \caption{\review{Case II:  $L^1$ and $L^2$ errors of the $\mathbf{E}$-field, the $\mathbf{B}$-field, and the electron density and their convergence rates for a range of $\lambda$.
+The reference solution is computed at a sufficiently mesh resolution with $2^{18} = 262144$ primal cells.}}
+    \label{tab:grid_study_cube}}
+\end{table}
+}
+\begin{figure}
+    \centering
+
+    \begin{minipage}{0.3\textwidth}
+    \vspace{-2cm}
+        \resizebox{\textwidth}{!}{
+            \begin{tikzpicture}[>=stealth]
+                % Electrode 1
+                \coordinate (O1) at (0,0);
+                \draw[violet,very thick] (O1) rectangle ++(2,2) node[midway, blue] {Electrode};
+                \fill[blue, opacity=0.2] (O1) rectangle ++(2,2);
+
+                % Electrode 2
+                \coordinate (O2) at (4.5,1);
+                \draw[violet,very thick] (O2) rectangle ++(2,2) node[midway, red] {Electrode};
+                \fill[blue, opacity=0.2] (O2) rectangle ++(2,2);
+
+                % Connecting lines
+                \coordinate (N1) at  ([shift={(0,2)}]O1);
+                \coordinate (E1) at  ([shift={(2,0)}]O1);
+                \coordinate (NE1) at ([shift={(2,2)}]O1);
+                \coordinate (N2) at  ([shift={(0,2)}]O2); 
+                \coordinate (E2) at  ([shift={(2,0)}]O2);
+                \coordinate (NE2) at ([shift={(2,2)}]O2); 
+                \draw[violet] (O1) -- (O2);
+                \draw[violet] (N1) -- (N2);
+                \draw[violet] (E1) -- (E2);
+                \draw[violet] (NE1) -- (NE2);
+
+                 % Plasma
+                \node at (barycentric cs:NE1=1,O2=1) {Plasma}; 
+                \fill[red, opacity=0.2] (O2) rectangle ++(2,2);
+
+                \coordinate (_O1) at (-0.5, -0.5);
+                \coordinate (_O2) at (4.0,0.5);
+                \draw[very thick] (_O1) rectangle ++(3,3);
+                \draw[very thick] (_O2) rectangle ++(3,3);
+                \coordinate (_N1) at  ([shift={(0,3)}]_O1);
+                \coordinate (_E1) at  ([shift={(3,0)}]_O1);
+                \coordinate (_NE1) at ([shift={(3,3)}]_O1);
+                \coordinate (_N2) at  ([shift={(0,3)}]_O2); 
+                \coordinate (_E2) at  ([shift={(3,0)}]_O2);
+                \coordinate (_NE2) at ([shift={(3,3)}]_O2); 
+                \draw[very thick] (_O1) -- (_O2);
+                \draw[very thick] (_N1) -- (_N2);
+                \draw[very thick] (_E1) -- (_E2);
+                \draw[very thick] (_NE1) -- (_NE2);
+
+                \draw[-to] (barycentric cs:_N1=1,_NE1=1,_N2=1,_NE2=1) to[out=90,in=0] ([shift={(-0.5,0.5)}]barycentric cs:_N1=1,_NE1=1,_N2=1,_NE2=1) node[left, gray] {Insulator};
+                % Axes
+                 \begin{scope}[shift={(6.5,-0.9)}]
+                    \draw[blue, -to] (0,0) -- (20:0.7) node[right]{\small $z$};
+                    \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
+                    \draw[blue, -to] (0,0) -- (0.7,0) node[below]{\small $y$};
+                \end{scope}
+            \end{tikzpicture}
+        }
+    \end{minipage}
+    \hspace{1cm}
+    \includegraphics[scale=0.2]{paper_version/cube_mesh_primal.png}
+    \hspace{1cm}
+    \includegraphics[scale=0.2]{paper_version/cube_mesh_dual.png}
+    \caption{\review{Case II: domain sketch (left); primal mesh (middle); dual mesh (right).}}
+    \label{fig:cube_domain_sketch}
+\end{figure}
+
+\subsection{Case III: 3D cylindrical domain}
 
@@
 All the other variables are set to zero initially.
-We set $\varphi(\mathbf{x}, t)|_{\Gamma_C^-} = 0, \varphi(\mathbf{x}, t)|_{\Gamma_C^+} = 1$, that is, a constant voltage is applied at the anode and excites the system.
+We set $\varphi(\mathbf{x}, t)|_{\Gamma_C^-} = 0, \varphi(\mathbf{x}, t)|_{\Gamma_C^+} = \tanh(100\times t)$, that is, a smooth voltage jump is applied at the anode and excites the system.
 
@@
 ($=\text{applied voltage}/\text{cylinder length}$) as a consequence of the irrotational
-$\mathbf{E}$-field in the steady state according to Faraday's law (, which is also confirmed
+$\mathbf{E}$-field in the steady state according to Faraday's law (which is also confirmed
 in Fig.~\ref{fig:stabilization_comparison} \textbf{(b)}). Note that it does not hold for $\lambda = 1$
@@
         \end{tikzpicture}
-        \includegraphics[scale=0.25]{E-field_lambda-1.png}
-        \includegraphics[scale=0.25]{B-field_lambda-1.png}
-        \includegraphics[scale=0.25]{electronVel_lambda-1.png}
+        \includegraphics[scale=0.2]{E-field_lambda-1.png}\hspace{0.6cm}
+        \includegraphics[scale=0.2]{B-field_lambda-1.png}
+        \includegraphics[scale=0.2]{electronVel_lambda-1.png}
         \caption{\colorbox{yellow!30}{$\lambda = 1.0$}}
@@
         \end{tikzpicture}
-        \includegraphics[scale=0.25]{E-field_lambda-1e-1.png}
+        \includegraphics[scale=0.2]{E-field_lambda-1e-1.png}
         \hspace{0.3cm}
-        \includegraphics[scale=0.25]{B-field_lambda-1e-1.png}
-        \includegraphics[scale=0.25]{electronVel_lambda-1e-1.png}
+        \includegraphics[scale=0.2]{B-field_lambda-1e-1.png}
+        \includegraphics[scale=0.2]{electronVel_lambda-1e-1.png}
         \caption{\colorbox{yellow!30}{$\lambda = 0.1$}}
@@
         \end{tikzpicture}
-        \includegraphics[scale=0.25]{E-field_lambda-0.png}
+        \includegraphics[scale=0.2]{E-field_lambda-0.png}
         \hspace{0.3cm}
-        \includegraphics[scale=0.25]{B-field_lambda-0.png}
-        \includegraphics[scale=0.25]{electronVel_lambda-0.png}
+        \includegraphics[scale=0.2]{B-field_lambda-0.png}
+        \includegraphics[scale=0.2]{electronVel_lambda-0.png}
         \caption{\colorbox{yellow!30}{$\lambda = 0.0$}}
     \end{subfigure}
-    \caption{Case II: Snapshots of the $\mathbf{E}$-field, $\mathbf{B}$-field, and $\mathbf{u}_e$ for different $\lambda$ at $t = 10$ based on a primal mesh with 1920 cells (16 cells along $z$-axis).
-}
+    \caption{Case III: Snapshots of the $\mathbf{E}$-field, $\mathbf{B}$-field, and $\mathbf{u}_e$ for different $\lambda$ at $t = 0.5$. } 
     \label{fig:3d_vec_field_E_B_ue}
@@
 
+\if\ifUpdate0
 Next, we study the impact of mesh refinement. Due to the high computational cost in 3D
@@
 \end{figure}
+\fi
 
@@
     \includegraphics[scale=0.9]{data-vs-time_stepVoltage.eps}
-    \caption{Case II: Time histories of quantities at the domain center and of the averaged current densities at $\Gamma^+_C$ (anode) and $\Gamma^-_C$ (cathode) for different values of $\lambda$.
+    \caption{Case III: Time histories of quantities at the domain center and of the averaged current densities at $\Gamma^+_C$ (anode) and $\Gamma^-_C$ (cathode) for different values of $\lambda$.
 The simulations are done on a mesh with 1920 primal cells with 8 layers along the $z$-axis.}
@@
   \parbox{0.9\textwidth}{\begin{tabular}[c]{ll}
-    \textbf{(a)} & time-dependent z-component of \\ & the $\mathbf{E}$-field
+    \textbf{(a)} & Time-dependent z-component of \\ & the $\mathbf{E}$-field
     in a boundary cell on $\Omega_N$
@@
 
-\caption{Case II: \textbf{(a)} Stabilization in the non-conducting domain $\Omega_N$,
-  \textbf{(b)} Numerical quasi-neutrality    }
+\caption{Case III: \textbf{(a)} Stabilization in the non-conducting domain $\Omega_N$,
+  \textbf{(b)} Numerical quasi-neutrality.    }
 \label{fig:stabilization_comparison}
@@
 Quasi-neutrality holds on the discrete level.
+
+\review{
+\subsection{Case IV: 3D bended cylindrical domain}
+To demonstrate the performance of the proposed scheme on more general three-dimensional settings, we bend the cylinder domain in Case III (see Fig.~\ref{fig:domain_sketch}), as is shown in Fig.~\ref{fig:bend_domain_sketch}.
+The same initial and boundary conditions as Case III are used.
+The numerical results of the electromagnetic field for $\lambda = 0$ and $1$ is displayed in Fig.~\ref{fig:3d_vec_field_E_B_bend}.
+It can be observed the qualitatively similar phenomena as Case~III (see Fig.~\ref{fig:3d_vec_field_E_B_ue}), that is, the electromagnetic field in the bulk of the domain develops much faster at small $\lambda$.}
+\begin{figure}
+    \centering
+    \begin{minipage}{0.3\textwidth}
+    \vspace{-2cm}
+        \resizebox{\textwidth}{!}{
+            \begin{tikzpicture}
+                \coordinate (O1) at (0,0);
+                \draw[violet] (O1) circle (1) node[blue] {Electrode};
+                \fill[blue, opacity=0.2] (O1) circle (1);
+                \draw[very thick] (O1) circle (1.5);
+                \coordinate (O2) at (4.5,2);
+                %\draw[violet] (O2) circle (1);
+                \node at (O2) {\textcolor{red}{Electrode}};
+
+                \coordinate (S1) at ([shift={(-0.707,0.707)}]O1);
+                \coordinate (S2) at ([shift={(-0.196,0.98)}]O2);
+                \coordinate (P1) at ([shift={(0.707,-0.707)}]O1);
+                \coordinate (P2) at ([shift={(0.196,-0.98)}]O2);
+                \draw[violet] (S1) to[out=45, in=180 + 10] (S2);
+                \draw[violet] (P1) to[out=45, in=180 + 10] (P2);
+                \coordinate (SS1) at ([shift={({-0.707*1.5},{0.707*1.5})}]O1);
+                \coordinate (SS2) at ([shift={({-0.196*1.5},{0.99*1.5})}]O2);
+                \coordinate (PP1) at ([shift={({0.707*1.5},{-0.707*1.5})}]O1);
+                \coordinate (PP2) at ([shift={({0.196*1.5},{-0.99*1.5})}]O2);
+                \draw[very thick] (SS1) to[out=45, in=180 + 10] (SS2);
+                \draw[very thick] (PP1) to[out=45, in=180 + 10] (PP2); 
+                \draw[very thick] (SS2) to[out=-180+10, in=180+10] (PP2);
+                \draw[very thick] (PP2) to[out=10, in=10] (SS2);
+                \draw[violet] (S2) to[out=-180+10, in=180+10] (P2) to[out=10, in=10] (S2);
+                \fill[red, opacity=0.2] (S2) to[out=-180+10, in=180+10] (P2) to[out=10, in=10] (S2);
+                \draw[-to] ([shift={(3,1.5)}]SS1) to[out=90,in=0] ([shift={(-0.5,0.7)}]barycentric cs:SS1=1,SS2=1) node[left, gray] {Insulator};
+                \node at (barycentric cs:P1=1,SS2=1) {Plasma};
+            \end{tikzpicture}
+        }
+    \end{minipage}
+    \hspace{1cm}
+    \includegraphics[scale=0.2]{paper_version/primal_mesh_bend.png}
+    \hspace{1cm}
+    \includegraphics[scale=0.2]{paper_version/dual_mesh_bend.png}
+    \caption{\review{Case IV: domain sketch (left); primal mesh (middle); dual mesh (right).}}
+    \label{fig:bend_domain_sketch}
+\end{figure}
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{\textwidth}
+        \centering
+        \includegraphics[scale=0.3]{paper_version/E-field_lamnbda-1_bend.png}\hspace{1cm}
+        \includegraphics[scale=0.3]{paper_version/B-field_lamnbda-1_bend.png}
+        \caption{\colorbox{yellow!30}{$\lambda = 1$}}
+    \end{subfigure}
+    \begin{subfigure}[b]{\textwidth}
+        \centering
+        \includegraphics[scale=0.3]{paper_version/E-field_lamnbda-0_bend.png}\hspace{1cm}
+        \includegraphics[scale=0.3]{paper_version/B-field_lamnbda-0_bend.png}
+        \caption{\colorbox{yellow!30}{$\lambda = 0$}}
+    \end{subfigure}
+    \caption{Case IV: Snapshots of the $\mathbf{E}$-field and $\mathbf{B}$-field for different $\lambda$ at $t = 0.05$.}
+    \label{fig:3d_vec_field_E_B_bend}
+\end{figure}
 

### 2024-03-07 paper_version/rebuttal_letter/rebuttal_letter.tex
update

--- 2024-03-07 paper_version/rebuttal_letter.tex
@@
-%-----------------------------------------------------------------------------%
-\documentclass[a4paper, 10pt]{letter}
+%% journalrebuttal.tex
+%% Copyright 2020 Pranav Hosangadi
+%
+% This work may be distributed and/or modified under the
+% conditions of the LaTeX Project Public License, either version 1.3
+% of this license or (at your option) any later version.
+% The latest version of this license is in
+%   http://www.latex-project.org/lppl.txt
+% and version 1.3 or later is part of all distributions of LaTeX
+% version 2005/12/01 or later.
+%
+% This work has the LPPL maintenance status `maintained'.
+% 
+% The Current Maintainer of this work is Pranav Hosangadi.
+%
+% This work consists of the file journalrebuttal.cls and the demo
+% file journalrebuttal.tex
+%% 
+%%
+%% journalrebuttal.tex
+%% Example usage for journalrebuttal.cls: 
+%%    A LaTeX class to create rebuttal documents for journal
+%%    reviews
+%% Created: 2020-06-28
+%% Author: Pranav Hosangadi (pranav.hosangadi@gmail.com)
+%% https://github.com/pranavh/JournalRebuttal_LaTeX
+%% Last Modified: 2020-06-29
+%% Version: 1.0
+%%
+\documentclass[12pt]{journalrebuttal}
+\title{\textcolor{blue}{Asymptotic-Preserving Discretization of Three-Dimensional Plasma Fluid Models}}
+\author{Tianwei Yu, Roman Fuchs, Ralf Hiptmair}
+\journal{\emph{Communications in Computational Physics}}
+\manuscriptid{CICP-OA-2023-0270.R1}
 
-\usepackage[utf8]{inputenc}
-\usepackage{enumitem}
-\usepackage{amssymb}
-\usepackage{amsmath}
-\usepackage{amsthm}
-\usepackage{bm}
-\usepackage{hyperref}
-\usepackage{geometry}
-\usepackage{xcolor}
-\geometry{a4paper,scale=0.8}
+\usepackage{verbatim}
 
-%-----------------------------------------------------------------------------%
+%% You can define Note commands using the \ColorNote command 
+%% provided in the class. 
+\newcommand{\PHNote}[1]{\ColorNote{red}{PH}{#1}}
 
 \begin{document}
+%\pagenumbering{arabic}
+\maketitle
 
-\begin{letter}
-\opening{Dear Editors,}
-
-We thank the reviews for the generous and insightful comments on our work and have revised the manuscript to address their concerns.
-The corresponding replies for each comments are attached in the end.
-
-We believe that the manuscript is now suitable for publication.
-
-\closing{On behalf of all authors,\\ \vspace{1cm} Tianwei Yu}
-\end{letter}
-
-\newpage
-
-\begin{itemize}
-  \item Question 1.1: \textcolor{violet}{Can the new 3D scheme reduces to Degond's 1D scheme?}
-  \item[$\blacktriangleright$] Reply: \textcolor{blue}{
+We sincerely thank the reviewers for the generous and insightful comments on our work and have revised the manuscript to address their concerns.
+The corresponding replies for each comments are attached below.
+\nextreviewer
+\begin{revcomment}
+    \textcolor{violet}{Can the new 3D scheme reduces to Degond's 1D scheme?}
+\end{revcomment} 
+    \begin{response}
+    \textcolor{blue}{
     Yes. The proposed numerical scheme in 3D is a natural extension of the 1D
-  the scheme proposed by Degond et. al. This is justified by considering problems with
+    the scheme proposed in $[$P.~Degond, F.~Deluzet, and D.~Savelief, \emph{Numerical approximation 
+    of the Euler-Maxwell model in the quasineutral limit}, Journal of Computational Physics, 231 (4), 
+    pp.~1917--1946, 2012$]$. This is justified by considering problems with
     transverse invariance (namely, variables keep constant along the x-axis and y-axis) and
@@
     described in Section~4.1.1, the fully discrete 3D AP scheme (32) collapses to (31)
-  discretization proposed in $[$P.~Degond, F.~Deluzet, and D.~Savelief, \emph{Numerical approximation of the Euler-Maxwell model in the quasineutral limit}, Journal of Computational Physics, 231 (4), pp.~1917--1946, 2012$]$.
-This is not a coincidence, because
+    discretization proposed by Degond et. al. This is not a coincidence, because
     recovering of (31) under dimensional reduction has guided our construction."
     }
+\end{response}
 
-  \item Question 1.2: \textcolor{violet}{In Fig 8, Page 19, it seems the 1D results are better than the 3D results by using the same meshes. Can the new 3D scheme
-  preserve some good properties of the original 1D scheme?}
-  \item[$\blacktriangleright$] Reply: \textcolor{blue}{
+\begin{revcomment}
+    \textcolor{violet}{
+    In Fig 8, Page 19, it seems the 1D results are better 
+    than the 3D results by using the same meshes. Can the new 3D scheme
+    preserve some good properties of the original 1D scheme?
+    }
+\end{revcomment}
+\begin{response}
+    \textcolor{blue}{
     Technically speaking, Fig.~8 is a ``verification" rather than a ``comparison".
@@
     }
+\end{response}
 
-  \item Question 1.3: \textcolor{violet}{In numerical tests, the mass ratio and the collision parameter are computed by a constant number. Is it sufficient to
-demonstrate the good performance of the new scheme?}
-  \item[$\blacktriangleright$] Reply: \textcolor{blue}{
+\begin{revcomment}
+    \textcolor{violet}{
+    In numerical tests, the mass ratio and the collision parameter 
+    are computed by a constant number. Is it sufficient to
+    demonstrate the good performance of the new scheme?
+    }
+\end{revcomment}
+\begin{response}
+    \textcolor{blue}{
     We agree that the robustness with respect to the mass ratio and the collision parameter
@@
     }
+\end{response}
 
-  \item Question 1.4: \textcolor{violet}{Include the following references:
-  [Fast-Converging and Asymptotic-Preserving Simulation of Frequency Domain Thermoreflectance, Jia Liu \& Lei Wu. Commun. Comput. Phys., 34 (2023), pp. 65-93.]
-  [A Coupled FEM-BEM Approach for the Solution of the Free-Boundary Axi-Symmetric Plasma Equilibrium Problem.
-M.
-Bonotto, D.
-Abate, P.
-Bettni \& F.
-Villone.
-Commun.
-Comput.
-Phys., 31 (2022), pp.
-27-59.]}
-  \item[$\blacktriangleright$] Reply: \textcolor{blue}{Both paper is included in the introduction.
+\begin{revcomment}
+    \textcolor{violet}{
+    Include the following references:
+    [Fast-Converging and Asymptotic-Preserving Simulation of Frequency Domain Thermoreflectance, 
+    Jia Liu \& Lei Wu. Commun. Comput. Phys., 34 (2023), pp. 65-93.]
+    [A Coupled FEM-BEM Approach for the Solution of the Free-Boundary Axi-Symmetric Plasma 
+    Equilibrium Problem. M. Bonotto, D. Abate, P. Bettni \& F. Villone. Commun. Comput. Phys., 31 
+    (2022), pp. 27-59.]
+    }
+\end{revcomment}
+\begin{response}
+    \textcolor{blue}{
+    Both paper is included in the introduction.
     The first paper is added to the literature review on AP schemes
-  while the second one is mentioned when the symmetry of the problem is discussed.}
-\end{itemize}
+    while the second one is mentioned when the symmetry of the problem is discussed.
+    }
+\end{response}
 
-\newpage
-
-\begin{itemize}
-  \item Question 2.1: \textcolor{violet}{The literature review provided in the paper is incomplete.
+\nextreviewer
+\begin{revcomment}
+    \textcolor{violet}{
+    The literature review provided in the paper is incomplete.
     Numerous structure-preserving schemes for plasma models involving the Euler
@@
     [W. Chen, K. Wu, and T. Xiong, Journal of Computational Physics, 488: 112240, 2023].
-  \end{itemize}}
-
-  \item[$\blacktriangleright$] Reply: \textcolor{blue}{
+    \end{itemize}
+    }
+\end{revcomment}
+\begin{response}
+    \textcolor{blue}{
     We have added a paragraph at the end of Section~2.2. A short discussion and literature
@@
     }
+\end{response}
 
-  \item Questions 2.2: \textcolor{violet}{The author did not provide an accuracy test
+\begin{revcomment}
+    \textcolor{violet}{
+    The author did not provide an accuracy test
     for the convergence rate of their proposed numerical method.
@@
     [K. Wu, H. Jiang, and C.-W. Shu, SIAM Journal on Numerical Analysis, 61: 250-285, 2023],
-  as well as in Examples 5.1 and 5.2 in [W. Chen, K. Wu, and T. Xiong, Journal of Computational Physics, 488: 112240, 2023]}
-  \item[$\blacktriangleright$] Reply: \textcolor{blue}{
+    as well as in Examples 5.1 and 5.2 in [W. Chen, K. Wu, and T. Xiong, Journal of Computational 
+    Physics, 488: 112240, 2023].
+    }    
+\end{revcomment}
+\begin{response}
+    \textcolor{blue}{
     To handle this issue, we put some effort into re-devising the matrix assembly which
@@
     meshes are possible. A new case involving a cuboid domain is tested and
-  $L^1$ and $L^2$ errors at different values of $\lambda$ are reported in the same manner as suggested by the second paper.
+    $L^1$ and $L^2$ errors at different values of $\lambda$ are reported in the same manner as 
+    suggested by the second paper.
     A smooth test case seems hard to construct due to the presence of the interface of two different
@@
     }    
+\end{response}
 
-  \item Question 2.3: \textcolor{violet}{
+\begin{revcomment}
+    \textcolor{violet}{
     Limited Numerical Examples: All the numerical examples provided in the paper
-  are either one-dimensional or three-dimensional cylindrical. To strengthen the paper's contribution,
+    are either one-dimensional or three-dimensional cylindrical. To strengthen the paper's 
+    contribution,
     it is advisable to include a genuinely three-dimensional example.
@@
     }
-  \item[$\blacktriangleright$] Reply: \textcolor{blue}{
+\end{revcomment}
+\begin{response}
+    \textcolor{blue}{
     We include a slightly more general 3D case in Case IV. Yet we would like to mention that 
@@
     ``extruding 2D mesh" in Sec.~4.2.1 of
-  $[$Marrone, Massimiliano.\emph{Computational Aspects of the Cell Method in Electrodynamics - Abstract.} Journal of Electromagnetic Waves and Applications 15 (2001): 407 - 408.$]$.
+    $[$Marrone, Massimiliano.\emph{Computational Aspects of the Cell Method in Electrodynamics - 
+    Abstract.} Journal of Electromagnetic Waves and Applications 15 (2001): 407 - 408.$]$.
     It has not been extended yet to arbitrary geometries, which possibly takes quite some effort.
@@
     }
-\end{itemize}
+\end{response}
+
+\makerule
 
 \end{document}
-%-----------------------------------------------------------------------------%

### 2024-03-07 paper_version/main.tex
update

@@
 \newcommand{\review}[1]{\textcolor{blue}{\if\ifUpdate1\textbf{#1}\fi}}
-\newcommand{\reviewDel}[1]{\begin{comment} #1 \end{comment}}
 
@@
 more general than that of Fig.~\ref{fig:domain_geometry}. \review{In particular, we do not 
-assume the solution to enjoy the rotational symmetry. If the symmetry is assumed, 
+assume the problem to enjoy the rotational symmetry. If the symmetry is assumed, 
 it can be exploited for reduction to two spatial dimensions \cite{bonotto_2022}.}
@@
     \centering
-    \includegraphics[scale=0.3]{primal_mesh.png}
+    \includegraphics[scale=0.3]{paper_version/figures/primal_mesh.png}
     \hspace{1cm}
-    \includegraphics[scale=0.3]{dual_mesh.png}
+    \includegraphics[scale=0.3]{paper_version/figures/dual_mesh.png}
     \caption{Primal mesh (left) and dual mesh (right).}
@@
 \review{
-\subsection{Case II: 3D cuboid domain (convergence study for a range of $\epsilon$)} 
-The scheme is tested at different mesh resolutions and the convergence rates are estimated.
+\subsection{Case II: 3D cuboid domain (convergence study for a range of $\lambda$)} 
 The problem setting follows the one depicted in Fig.~\ref{fig:domain_sketch} while we adopt a cuboid domain, see Fig.~\ref{fig:cube_domain_sketch}.
@@
 The results are computed for the final time $t = 0.01$.
-Tab.~\ref{tab:grid_study_cube} lists the errors for the $\mathbf{E}$-field, $\mathbf{B}$-field, and electron densities where the reference solutions are generated by a sufficiently fine mesh with $2^{18} = 262144$ cells.
+The scheme is tested at different mesh resolutions and the convergence rates are estimated.
+Tab.~\ref{tab:grid_study_cube} lists the errors for the $\mathbf{E}$-field, $\mathbf{B}$-field, and electron densities where the reference solutions are generated by a sufficiently fine mesh with $2^{18} = 262144$ primal cells.
 The results show uniform convergence over $0\leq \lambda \leq 1$, a justification of the AP property.
@@
     \hspace{1cm}
-    \includegraphics[scale=0.2]{paper_version/cube_mesh_primal.png}
+    \includegraphics[scale=0.2]{paper_version/figures/cube_mesh_primal.png}
     \hspace{1cm}
-    \includegraphics[scale=0.2]{paper_version/cube_mesh_dual.png}
+    \includegraphics[scale=0.2]{paper_version/figures/cube_mesh_dual.png}
     \caption{\review{Case II: domain sketch (left); primal mesh (middle); dual mesh (right).}}
@@
         \end{tikzpicture}
-        \includegraphics[scale=0.2]{E-field_lambda-1.png}\hspace{0.6cm}
-        \includegraphics[scale=0.2]{B-field_lambda-1.png}
-        \includegraphics[scale=0.2]{electronVel_lambda-1.png}
+        \includegraphics[scale=0.2]{paper_version/figures/E-field_lambda-1.png}\hspace{0.6cm}
+        \includegraphics[scale=0.2]{paper_version/figures/B-field_lambda-1.png}
+        \includegraphics[scale=0.2]{paper_version/figures/electronVel_lambda-1.png}
         \caption{\colorbox{yellow!30}{$\lambda = 1.0$}}
@@
         \end{tikzpicture}
-        \includegraphics[scale=0.2]{E-field_lambda-1e-1.png}
+        \includegraphics[scale=0.2]{paper_version/figures/E-field_lambda-1e-1.png}
         \hspace{0.3cm}
-        \includegraphics[scale=0.2]{B-field_lambda-1e-1.png}
-        \includegraphics[scale=0.2]{electronVel_lambda-1e-1.png}
+        \includegraphics[scale=0.2]{paper_version/figures/B-field_lambda-1e-1.png}
+        \includegraphics[scale=0.2]{paper_version/figures/electronVel_lambda-1e-1.png}
         \caption{\colorbox{yellow!30}{$\lambda = 0.1$}}
@@
         \end{tikzpicture}
-        \includegraphics[scale=0.2]{E-field_lambda-0.png}
+        \includegraphics[scale=0.2]{paper_version/figures/E-field_lambda-0.png}
         \hspace{0.3cm}
-        \includegraphics[scale=0.2]{B-field_lambda-0.png}
-        \includegraphics[scale=0.2]{electronVel_lambda-0.png}
+        \includegraphics[scale=0.2]{paper_version/figures/B-field_lambda-0.png}
+        \includegraphics[scale=0.2]{paper_version/figures/electronVel_lambda-0.png}
         \caption{\colorbox{yellow!30}{$\lambda = 0.0$}}
@@
 The same initial and boundary conditions as Case III are used.
-The numerical results of the electromagnetic field for $\lambda = 0$ and $1$ is displayed in Fig.~\ref{fig:3d_vec_field_E_B_bend}.
+The numerical results of the electromagnetic field for $\lambda = 0$ and $1$ are displayed in Fig.~\ref{fig:3d_vec_field_E_B_bend}.
 It can be observed the qualitatively similar phenomena as Case~III (see Fig.~\ref{fig:3d_vec_field_E_B_ue}), that is, the electromagnetic field in the bulk of the domain develops much faster at small $\lambda$.}
@@
     \hspace{1cm}
-    \includegraphics[scale=0.2]{paper_version/primal_mesh_bend.png}
+    \includegraphics[scale=0.2]{paper_version/figures/primal_mesh_bend.png}
     \hspace{1cm}
-    \includegraphics[scale=0.2]{paper_version/dual_mesh_bend.png}
+    \includegraphics[scale=0.2]{paper_version/figures/dual_mesh_bend.png}
     \caption{\review{Case IV: domain sketch (left); primal mesh (middle); dual mesh (right).}}
@@
         \centering
-        \includegraphics[scale=0.3]{paper_version/E-field_lamnbda-1_bend.png}\hspace{1cm}
-        \includegraphics[scale=0.3]{paper_version/B-field_lamnbda-1_bend.png}
+        \includegraphics[scale=0.3]{paper_version/figures/E-field_lamnbda-1_bend.png}\hspace{1cm}
+        \includegraphics[scale=0.3]{paper_version/figures/B-field_lamnbda-1_bend.png}
         \caption{\colorbox{yellow!30}{$\lambda = 1$}}
@@
         \centering
-        \includegraphics[scale=0.3]{paper_version/E-field_lamnbda-0_bend.png}\hspace{1cm}
-        \includegraphics[scale=0.3]{paper_version/B-field_lamnbda-0_bend.png}
+        \includegraphics[scale=0.3]{paper_version/figures/E-field_lamnbda-0_bend.png}\hspace{1cm}
+        \includegraphics[scale=0.3]{paper_version/figures/B-field_lamnbda-0_bend.png}
         \caption{\colorbox{yellow!30}{$\lambda = 0$}}

### 2024-03-07 paper_version/main.tex
fix error in plotting eps

@@
 \usepackage{comment}
+%\usepackage[outdir=./]{epstopdf}
 
@@
     \centering
-    \includegraphics[scale=0.3]{paper_version/figures/primal_mesh.png}
+    \includegraphics[scale=0.3]{./figures/primal_mesh.png}
     \hspace{1cm}
-    \includegraphics[scale=0.3]{paper_version/figures/dual_mesh.png}
+    \includegraphics[scale=0.3]{./figures/dual_mesh.png}
     \caption{Primal mesh (left) and dual mesh (right).}
@@
     \centering
-    \includegraphics[scale=1.2]{z_axis_reduction.eps}
+    \includegraphics[scale=1.2]{./figures/z_axis_reduction.eps}
     \caption{Case I, $\lambda = 1$: Comparison of 1D two-fluid model and of 3D results (at
@@
     \hspace{1cm}
-    \includegraphics[scale=0.2]{paper_version/figures/cube_mesh_primal.png}
+    \includegraphics[scale=0.2]{./figures/cube_mesh_primal.png}
     \hspace{1cm}
-    \includegraphics[scale=0.2]{paper_version/figures/cube_mesh_dual.png}
+    \includegraphics[scale=0.2]{./figures/cube_mesh_dual.png}
     \caption{\review{Case II: domain sketch (left); primal mesh (middle); dual mesh (right).}}
@@
         \end{tikzpicture}
-        \includegraphics[scale=0.2]{paper_version/figures/E-field_lambda-1.png}\hspace{0.6cm}
-        \includegraphics[scale=0.2]{paper_version/figures/B-field_lambda-1.png}
-        \includegraphics[scale=0.2]{paper_version/figures/electronVel_lambda-1.png}
+        \includegraphics[scale=0.2]{./figures/E-field_lambda-1.png}\hspace{0.6cm}
+        \includegraphics[scale=0.2]{./figures/B-field_lambda-1.png}
+        \includegraphics[scale=0.2]{./figures/electronVel_lambda-1.png}
         \caption{\colorbox{yellow!30}{$\lambda = 1.0$}}
@@
         \end{tikzpicture}
-        \includegraphics[scale=0.2]{paper_version/figures/E-field_lambda-1e-1.png}
+        \includegraphics[scale=0.2]{./figures/E-field_lambda-1e-1.png}
         \hspace{0.3cm}
-        \includegraphics[scale=0.2]{paper_version/figures/B-field_lambda-1e-1.png}
-        \includegraphics[scale=0.2]{paper_version/figures/electronVel_lambda-1e-1.png}
+        \includegraphics[scale=0.2]{./figures/B-field_lambda-1e-1.png}
+        \includegraphics[scale=0.2]{./figures/electronVel_lambda-1e-1.png}
         \caption{\colorbox{yellow!30}{$\lambda = 0.1$}}
@@
         \end{tikzpicture}
-        \includegraphics[scale=0.2]{paper_version/figures/E-field_lambda-0.png}
+        \includegraphics[scale=0.2]{./figures/E-field_lambda-0.png}
         \hspace{0.3cm}
-        \includegraphics[scale=0.2]{paper_version/figures/B-field_lambda-0.png}
-        \includegraphics[scale=0.2]{paper_version/figures/electronVel_lambda-0.png}
+        \includegraphics[scale=0.2]{./figures/B-field_lambda-0.png}
+        \includegraphics[scale=0.2]{./figures/electronVel_lambda-0.png}
         \caption{\colorbox{yellow!30}{$\lambda = 0.0$}}
@@
   \centering
-    \includegraphics[scale=0.9]{data-vs-time_stepVoltage.eps}
+    \includegraphics[scale=0.9]{./figures/data-vs-time_stepVoltage }
     \caption{Case III: Time histories of quantities at the domain center and of the averaged current densities at $\Gamma^+_C$ (anode) and $\Gamma^-_C$ (cathode) for different values of $\lambda$.
@@
 \begin{minipage}[t]{0.4\textwidth}\centering
-  \includegraphics[width=\textwidth]{stabilizationComparision_stepVoltage.eps}
+  \includegraphics[width=\textwidth]{./figures/stabilizationComparision_stepVoltage}
 
@@
  \begin{minipage}[t]{0.6\textwidth}\centering
-   \includegraphics[width=\textwidth]{data-vs-z_stepVoltage.eps}
+   \includegraphics[width=\textwidth]{./figures/data-vs-z_stepVoltage}
 
@@
     \hspace{1cm}
-    \includegraphics[scale=0.2]{paper_version/figures/primal_mesh_bend.png}
+    \includegraphics[scale=0.2]{./figures/primal_mesh_bend.png}
     \hspace{1cm}
-    \includegraphics[scale=0.2]{paper_version/figures/dual_mesh_bend.png}
+    \includegraphics[scale=0.2]{./figures/dual_mesh_bend.png}
     \caption{\review{Case IV: domain sketch (left); primal mesh (middle); dual mesh (right).}}
@@
         \centering
-        \includegraphics[scale=0.3]{paper_version/figures/E-field_lamnbda-1_bend.png}\hspace{1cm}
-        \includegraphics[scale=0.3]{paper_version/figures/B-field_lamnbda-1_bend.png}
+        \includegraphics[scale=0.3]{./figures/E-field_lamnbda-1_bend.png}\hspace{1cm}
+        \includegraphics[scale=0.3]{./figures/B-field_lamnbda-1_bend.png}
         \caption{\colorbox{yellow!30}{$\lambda = 1$}}
@@
         \centering
-        \includegraphics[scale=0.3]{paper_version/figures/E-field_lamnbda-0_bend.png}\hspace{1cm}
-        \includegraphics[scale=0.3]{paper_version/figures/B-field_lamnbda-0_bend.png}
+        \includegraphics[scale=0.3]{./figures/E-field_lamnbda-0_bend.png}\hspace{1cm}
+        \includegraphics[scale=0.3]{./figures/B-field_lamnbda-0_bend.png}
         \caption{\colorbox{yellow!30}{$\lambda = 0$}}

### 2024-03-14 paper_version/main.tex
Add files via upload

@@
 \newcommand{\mycolorbox}[2]{\colorbox{#1}{$\displaystyle#2$}}
-\newcommand{\todo}[1]{\textcolor{blue}{\fbox{\textbf{TODO: #1}}}}
+\newcommand{\todo}[1]{\textcolor{green!50!black}{\fbox{\textbf{TODO: #1}}}}
 \newcommand{\mycomment}[1]{\noindent\textcolor{orange}{\underline{\textsf{\textbf{#1}}}}}
@@
 
-\newcommand{\review}[1]{\textcolor{blue}{\if\ifUpdate1\textbf{#1}\fi}}
+\newcommand{\review}[1]{{\color{blue}{\if\ifUpdate1\sf{#1}\fi}}}
 
 \title{Asymptotic-Preserving Discretization of Three-Dimensional Plasma Fluid Models}
-\author[]{Tianwei Yu \thanks{Seminar for Applied Mathematics , ETH Z\"{u}rich, \texttt{tianwei.yu@math.ethz.ch}}}
+\author[]{Tianwei Yu \thanks{Seminar for Applied Mathematics, ETH Z\"{u}rich, \texttt{tianwei.yu@math.ethz.ch}}}
 \author[]{Roman Fuchs \thanks{IET Institut für Energietechnik, OST, \texttt{roman.fuchs@ost.ch}}}
-\author[]{Ralf Hiptmair \thanks{Seminar for Applied Mathematics , ETH Z\"{u}rich, \texttt{ralf.hiptmair@math.ethz.ch}}}
+\author[]{Ralf Hiptmair \thanks{Seminar for Applied Mathematics, ETH Z\"{u}rich, \texttt{ralf.hiptmair@math.ethz.ch}}}
 \affil[]{}
-\date{}
+\date{(1)}
 
@@
 \maketitle
+
+% \todo{Do not directly insert numbers of formulas, figure, sections. Always use \LaTeX's
+%  \symbol{92}label-\symbol{92}ref facility.}
 
@@
 
-%An asymptotic-preserving scheme for single- and multi-fluid Euler-Maxwell system was proposed by \cite{degond_2012} for one spatial dimension.
+%An asymptotic-preserving scheme for single- and multi-fluid Euler-Maxwell system was proposed by~\cite{degond_2012} for one spatial dimension.
 We extend their scheme to three dimensions.
@@
 plasma regimes and, thus, the design goal was a numerical model capable of dealing
-with all of them seamlessly and simultaneously. Thus in this work, as in
-\cite{degond_2012}, the focus is on \emph{asymptotic-preserving} (AP) discretization in
+with all of them seamlessly and simultaneously. Thus, in this work, as in
+~\cite{degond_2012}, the focus is on \emph{asymptotic-preserving} (AP) discretization in
 the quasi-neutral limit $\lambda \rightarrow 0$, where $\lambda$ is the rescaled Debye
-length, see Section~\ref{sec:rescaling} for the underlying scaling arguments and
-\cite{degond_2012,degond_2017} for a discussion of the importance of the AP property of
+length, see Sec.~\ref{sec:rescaling} for the underlying scaling arguments and
+~\cite{degond_2012,degond_2017} for a discussion of the importance of the AP property of
 numerical plasma models.
 
-Our approach is inspired by \cite{degond_2012}, but goes beyond that work in various directions:
+Our approach is inspired by~\cite{degond_2012}, but goes beyond that work in various directions:
 \begin{itemize}
 \item We supplement the Maxwell-Euler system by inter-species friction terms.
-\item We extend the spatially one-dimensional scheme of \cite{degond_2012} to three
+\item We extend the spatially one-dimensional scheme of~\cite{degond_2012} to three
   spatial dimensions using discrete exterior calculus (DEC) to discretize Maxwell's
@@
 
-We stay close to \cite{degond_2012} in terms of discretization in time employing
-semi-implicit time-stepping. We base our illustration on the model case shown
-in Fig.~\ref{fig:domain_geometry}. Yet we would like to remark that the mesh-based numerical
-scheme proposed in this paper can in principle be adapted to geometric situations much
-more general than that of Fig.~\ref{fig:domain_geometry}. \review{In particular, we do not 
-assume the problem to enjoy the rotational symmetry. If the symmetry is assumed, 
-it can be exploited for reduction to two spatial dimensions \cite{bonotto_2022}.}
+We stay close to~\cite{degond_2012} in terms of discretization in time employing
+semi-implicit time-stepping and base our illustration on the model situations shown in
+Fig.~\ref{fig:domain_geometry}. Yet, we would like to remark that the mesh-based numerical
+scheme proposed in this paper can in principle be adapted to settings more general
+than those of Fig.~\ref{fig:domain_geometry}. \review{In particular, we do not assume any
+  rotational symmetry, which would allow reduction to two spatial dimensions~\cite{bonotto_2022}.}
 
@@
   Maxwell-Euler system switches from hyperbolic to mixed for $\lambda_{D}\to 0$}. This
-poses a challenge for simulations in settings encompassing different regimes. 
-Beside the quasi-neutral limit, we remind
-that singularly perturbed problems occur in extensively many physical models, 
-e.g., in the case of vanishing viscosity problem \cite{Kato_1984, bianchini_2005, temam_1997}, the
-zero-relaxation-limit of kinetic-type equations \cite{raymond_2009, degond_1996}, and the incompressible limit
-of compressible flows \cite{klainerman_1981}. Throughout, it is essential that
-numerical schemes remain valid even if crucial model parameters approach the limit. These
-schemes are then said to be \emph{asymptotic-preserving} (AP): Let us assume that we
-discretize a parameter($\lambda$)-dependent model $P^\lambda$, which converges to a limit
-$P^0$ as $\lambda \rightarrow 0$, by the scheme $P^\lambda_h$ where $h$ denotes some
-discretization parameter, e.g., the mesh size. The AP property amounts to uniform
-convergence of $P^\lambda_h$ to the $P^\lambda$ as $\lambda\rightarrow0$. 
-The concept is effectively depicted by a commuting diagram in \cite[][Fig.~1]{jin_2010}. 
-\review{AP schemes have been extensively studied for various problems, e.g. the diffusive limit of the kinetic equations \cite{jin_1999, liu_2023}, 
-the low Mach-number limit of compressible flows \cite{degond_2007, haack_2010} and magnetohydrodynamics\cite{chen_2023}, 
-the quasi-neutral limit of drift-diffusion equations \cite{chatard_2014, claire_2007}. 
-More generally, readers are referred to the comprehensive reviews \cite{jin_2010, degond_2017}.}
-
-The content of this paper is organized as follows: In Section~\ref{sec:plasma-model}, we
+poses a challenge for simulations in settings encompassing different regimes.  Beside the
+quasi-neutral limit, we remind that singularly perturbed problems occur in extensively
+many physical models, e.g., in the case of vanishing viscosity problem~\cite{Kato_1984,
+  bianchini_2005, temam_1997}, the zero-relaxation-limit of kinetic-type equations
+~\cite{raymond_2009, degond_1996}, and the incompressible limit of compressible flows
+~\cite{klainerman_1981}. Throughout, it is essential that numerical schemes remain valid
+even if crucial model parameters approach the limit. These schemes are then said to be
+\emph{asymptotic-preserving} (AP): Let us assume that we discretize a
+parameter (denoted by $\lambda$) dependent model $P^\lambda$, which converges to a limit $P^0$ as
+$\lambda \rightarrow 0$, by the scheme $P^\lambda_h$ where $h$ denotes some discretization
+parameter, e.g., the mesh size. The AP property amounts to uniform convergence of
+$P^\lambda_h$ to the $P^\lambda$ as $\lambda\rightarrow0$.  The concept is effectively
+depicted by a commuting diagram in~\cite[][Fig.~1]{jin_2010}.  \review{AP schemes have
+  been extensively studied for various problems, e.g., the diffusive limit of kinetic
+  equations~\cite{jin_1999, liu_2023}, the low Mach-number limit of compressible flow
+  models~\cite{degond_2007, haack_2010}, magnetohydrodynamics~\cite{chen_2023}, the
+  quasi-neutral limit of drift-diffusion equations~\cite{chatard_2014, claire_2007}.  For
+  more information readers are referred to the comprehensive reviews~\cite{jin_2010,
+    degond_2017}.}
+
+The content of this paper is organized as follows: In Sec.~\ref{sec:plasma-model}, we
 give a full description of the underlying equations of the Maxwell-Euler system and its
 rescaling procedure. Meanwhile, the boundary conditions in our setting is elaborated. A
-reformulation of Maxwell's equations in the non-conducting region is presented. Section
-\ref{sec:spatial_discretization} is devoted to the spatial discretization. The concept of
+reformulation of Maxwell's equations in the non-conducting region is presented. Sec.
+~\ref{sec:spatial_discretization} is devoted to the spatial discretization. The concept of
 primal-dual meshes is introduced based on which FIT and FVM are utilized. We discuss the
-full AP discretization in Section~\ref{sec:full-discretization} and do numerical
-experiments in Section~\ref{sec:numerical_experiment}.
+full AP discretization in Sec.~\ref{sec:full-discretization} and do numerical
+experiments in Sec.~\ref{sec:numerical_experiment}.
 
 \begin{figure}
-    \centering
-    \begin{tikzpicture}[scale=1.2]
+    \begin{subfigure}{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}[scale=0.9]
         \coordinate (O1) at (0,0);
@@
         \draw[-to] (barycentric cs:SS1=1,SS2=1,S1=1,S2=1) to[out=90,in=0] ([shift={(-0.5,0.5)}]barycentric cs:SS1=1,SS2=1,S1=1,S2=1) node[left, gray] {Insulator};
-    \begin{scope}[shift={(5.5,-1.4)}]
-    \draw[blue, -to] (0,0) -- (0.65,0.12) node[right]{\small $z$};
-    \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
-    \draw[blue, -to] (0,0) -- (0.7,0) node[below]{\small $y$};
-    \end{scope}
         \end{tikzpicture}
+        \caption{Cylinder geometry}\label{fig:cylinder_geo}
+    \end{subfigure}
+    \begin{subfigure}{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}[scale=0.8]
+            % Electrode 1
+            \coordinate (O1) at (0,0);
+            \draw[violet] (O1) rectangle ++(2,2) node[midway, blue] {Electrode};
+            \fill[blue, opacity=0.2] (O1) rectangle ++(2,2);
+
+            % Electrode 2
+            \coordinate (O2) at (4.5,1);
+            \draw[violet] (O2) rectangle ++(2,2) node[midway, red] {Electrode};
+            \fill[blue, opacity=0.2] (O2) rectangle ++(2,2);
+
+            % Connecting lines
+            \coordinate (N1) at  ([shift={(0,2)}]O1);
+            \coordinate (E1) at  ([shift={(2,0)}]O1);
+            \coordinate (NE1) at ([shift={(2,2)}]O1);
+            \coordinate (N2) at  ([shift={(0,2)}]O2); 
+            \coordinate (E2) at  ([shift={(2,0)}]O2);
+            \coordinate (NE2) at ([shift={(2,2)}]O2); 
+            \draw[violet] (O1) -- (O2);
+            \draw[violet] (N1) -- (N2);
+            \draw[violet] (E1) -- (E2);
+            \draw[violet] (NE1) -- (NE2);
+
+             % Plasma
+            \node at (barycentric cs:NE1=1,O2=1) {Plasma}; 
+            \fill[red, opacity=0.2] (O2) rectangle ++(2,2);
+
+            \coordinate (_O1) at (-0.5, -0.5);
+            \coordinate (_O2) at (4.0,0.5);
+            \draw[very thick] (_O1) rectangle ++(3,3);
+            \draw[very thick] ([shift={(3,0)}]_O2) -- ++(0,3) -- ++(-3,0);
+            \draw[violet] (_O2) -- ++(3,0);
+            \draw[violet] (_O2) -- ++(0,3); 
+            \coordinate (_N1) at  ([shift={(0,3)}]_O1);
+            \coordinate (_E1) at  ([shift={(3,0)}]_O1);
+            \coordinate (_NE1) at ([shift={(3,3)}]_O1);
+            \coordinate (_N2) at  ([shift={(0,3)}]_O2); 
+            \coordinate (_E2) at  ([shift={(3,0)}]_O2);
+            \coordinate (_NE2) at ([shift={(3,3)}]_O2); 
+            \draw[violet] (_O1) -- (_O2);
+            \draw[very thick] (_N1) -- (_N2);
+            \draw[very thick] (_E1) -- (_E2);
+            \draw[very thick] (_NE1) -- (_NE2);
+
+            \draw[-to] (barycentric cs:_N1=1,_NE1=1,_N2=1,_NE2=1) to[out=90,in=0] ([shift={(-0.5,0.5)}]barycentric cs:_N1=1,_NE1=1,_N2=1,_NE2=1) node[left, gray] {Insulator};
+        \end{tikzpicture}
+        \caption{Cuboid geometry}\label{fig:cube_geo}
+    \end{subfigure}
     \caption{The special geometric setting suggested by the simulation of electric arcs,
-      for which we discuss the new method.}
+        for which we discuss the new method.
+        % \todo{Move geometry from Fig.~9 here. Display both side-by-side.}
+    }
     \label{fig:domain_geometry}
@@
 
-\section{Plasma model} \label{sec:plasma-model}
+\section{Plasma model}\label{sec:plasma-model}
 
@@
 
-Plasmas consist of electrically charged and (possibly) neutral particle species and we
+Plasmas consist of electrically charged and (possibly) neutral particle species, and we
 suppose that they can be treated as continua (fluids). That is, they may be described by the
@@
 relaxation among species, radiative heat transfer, Ohmic heating). For more details on
-fluid models of plasmas, see \cite{chen2016, remi_2014}.
+fluid models of plasmas, see~\cite{chen2016, remi_2014}.
 
@@
   equations} augmented by electromagnetic forces as well as other processes,
-e.g. collisions and recombination:
+e.g.\ collisions and recombination:
 \begin{align} \label{equ:euler_}
@@
 \end{align}
-The subscript $*\in \{e, i, \cdots\}$ labels electrons, ions or other species. The
+The subscript $*\in \{e, i, \ldots\}$ labels electrons, ions or other species. The
 involved fluid quantities are: number density $n_*[\frac{1}{\text{m}^3}]$, particle mass
@@
 
-\begin{remark}
-  \label{rem:coll}
+\begin{remark}\label{rem:coll}
   For the sake of simplicity, we only consider ion-electron collision in this work, but
 extension to more species is straightforward. Such collisions can be well modelled by
-friction terms, for instance \citep[][Sec.~5.6.2]{chen2016}
+friction terms, for instance~\citep[][Sec.~5.6.2]{chen2016}
 \begin{equation} \label{equ:collision}
-    \mathbf{R}_{e}^{\text{coll}} = \frac{\pi Ze^4m_e^{1/2}}{(4\pi\epsilon)^2(k_BT_e)^{3/2}}\text{\emph{ln}}\Lambda n_en_i(\mathbf{u}_i - \mathbf{u}_e) = - \mathbf{R}_{i}^{\text{coll}},  
+    \mathbf{R}_{e}^{\text{coll}} = \frac{\pi Ze^4m_e^{1/2}}{{(4\pi\epsilon)}^2{(k_B T_e)}^{3/2}}\text{\emph{ln}}\Lambda n_e n_i(\mathbf{u}_i - \mathbf{u}_e) = - \mathbf{R}_{i}^{\text{coll}},  
 \end{equation}
 which is the collision force acting on electrons. \emph{ln}$\Lambda$ is called the \emph{Coulomb
-  logarithm} and is usually taken as a constant \cite{chen2016}. Because of the
+  logarithm} and is usually taken as a constant~\cite{chen2016}. Because of the
 conservation of momentum, the collision term for ions $\mathbf{R}_{i}^{\text{coll}}$ is
 nothing but the negative of $\mathbf{R}_{e}^{\text{coll}}$. In this work, the other
-effects, e.g. ionization and recombination, are not considered. For full details about the
+effects, e.g.\ ionization and recombination, are not considered. For full details about the
 modeling of these physical processes, readers are referred to
-\cite[][Sec.~3.2]{fuchs_2021}.
+~\cite[][Sec.~3.2]{fuchs_2021}.
 \end{remark}
 
-\subsection{Rescaling}
-\label{sec:rescaling}
+\subsection{Rescaling}\label{sec:rescaling}
 % In rescaling, variables in equations are replaced by the ratio of original quantities and constant reference quantities, which transforms the system into dimensionless form.
-In this part, the rescaling procedure mostly follows that of \cite[][Sec.~2.2]{degond_2017}.
+In this part, the rescaling procedure mostly follows that of~\cite[][Sec.~2.2]{degond_2017}.
 
 We arrive at non-dimensional equations by following the rescaling procedure of
-\cite[][Sec.~2.2]{degond_2017}.  First, a reference value for each quantity is
+~\cite[][Sec.~2.2]{degond_2017}.  First, a reference value for each quantity is
 fixed. We define $\overline{x}$ and $\overline{t}$ as space and time scale of
@@
 reference value for the specific total energy and enthalpy is set to
-$\overline{u}^2$. Also taking into account the physical constants, i.e. the reference
+$\overline{u}^2$. Also taking into account the physical constants, i.e.\ the reference
 permittivity $\overline{\epsilon}$, the reference permeability $\overline{\mu}$, the light
-speed $c^2 = (\overline{\epsilon}\overline{\mu})^{-1}$, Boltzmann constant $k_B$, the
+speed $c^2 = {(\overline{\epsilon}\overline{\mu})}^{-1}$, Boltzmann constant $k_B$, the
 elementary charge $e$, and ion mass $m_i$, we introduce the following dimensionless
@@
   \lambda &:= \frac{\lambda_D}{\overline{x}} \text{ the dimensionless Debye length, where }\lambda_D := \left(\frac{\epsilon k_B\overline{T}}{e^2\overline{n}}\right)^{1/2}, &\\
-  \varepsilon_*^2 &:= \frac{m_*}{m_i} \text{ the species mass \emph{w.r.t.} the ion mass},\ \  * \in \{i,e,\cdots\}, &\\
+  \varepsilon_*^2 &:= \frac{m_*}{m_i} \text{ the species mass \emph{w.r.t.} the ion mass},\ \  * \in \{i,e,\ldots\}, &\\
   g &:= \frac{1}{\overline{n}\lambda_D^3} \text{ the plasma parameter\footnotemark[2]}.&
@@
 \footnotetext[1]{Abbreviation of \emph{with respect to}.}
-\footnotetext[2]{It is basically the reciprocal of the number of particles per Debye sphere, see \cite[][Sec.~1.1]{gibbon2020}. Classical plasma theory assumes $g \ll 1$.}
+\footnotetext[2]{It is basically the reciprocal of the number of particles per Debye sphere, see~\cite[][Sec.~1.1]{gibbon2020}. Classical plasma theory assumes $g \ll 1$.}
 
@@
 Assumptions can be made to reduce the number of dimensionless parameters. Following
-\cite[][Sec.~2.2]{degond_2017}, the reference speed $\overline{v}$ is of the same scale as
+~\cite[][Sec.~2.2]{degond_2017}, the reference speed $\overline{v}$ is of the same scale as
 the plasma speed $\overline{u}$ and the thermal speed $v_i^{\text{th}}$ whereas it is much
@@
 happen on the atomic length scale, in which quantum-mechanical effects must be taken into
-account \cite[][pp. 144-148]{frank_1972}. Therefore, we eliminate the perturbation
+account~\cite[][pp. 144-148]{frank_1972}. Therefore, we eliminate the perturbation
 parameter in the friction term by assuming $g \sim \lambda$ and keep the prefactor
@@
 The case when there is an asymptotic parameter in the denominator of the friction term is
-of interest, too. This situation is known as relaxation limit, see \cite{peng_2011,
+of interest, too. This situation is known as relaxation limit, see~\cite{peng_2011,
   wasiolek_2016, Li_2021, Chen_2000}.
@@
 
-In summary, we make the following choices \cite[][sec 2.2]{degond_2017}
+In summary, we make the following choices~\cite[][sec 2.2]{degond_2017}
 \begin{align*}
@@
 single parameter, whose value may tend to zero:
-\begin{subequations} \label{equ:euler-maxwell-rescaled}
-  \label{resc}
+\begin{subequations}\label{equ:euler-maxwell-rescaled}\label{resc}
 \begin{align}
@@
 $\lambda$-parameterized rescaled Maxwell-Euler system
-(\ref{equ:maxwell_faraday_rescaled})-(\ref{equ:maxwell_material_law_rescaled}) is the
+(\ref{equ:maxwell_faraday_rescaled})- (\ref{equ:maxwell_material_law_rescaled}) is the
 starting point for the development of the numerical method.
@@
 \review{
-It is worth mentioning that an important aspect of devising numerical schemes is the structure-preserving property which is concerned with keeping some constraints at the discrete level.
-In this context, some typical constraints are the positivity of densities and pressures, the entropy inequality, zero divergence of the $\mathbf{B}$-field, etc.
-There are in general two ways of numerically approaching the coupled system (\ref{equ:euler-maxwell-rescaled}) or its reduced models, e.g.
-the magnetohydrodynamic (MHD) equations.
-The first approach is to lump all the equations into one hyperbolic system of conservation laws and apply finite volume methods.
-Such numerical methods are rather simple to implement and also computationally efficient.
-Complications typically go to ensuring the stability and the divergence constraint which requires suitable numerical fluxes and limiters.
-Schemes that are provably positive, entropy-stable, or divergence-free have been constructed, see \cite{wu_2018, wu_2023a, wu_2023b, kumar_2011, fuchs_2009} and references therein.
-The second class of numerical methods handles the electromagnetic part and the fluid part separately.
-The rationale behind such a splitting strategy is that dedicated solvers for subsystems are rather mature.
-Particularly, the divergence constraint can be easily handled by finite element exterior calculus.
-Yet the implementation of coupled solvers is usually complicated.
-To name some related work, \cite{fuchs_2009} applies dedicated finite volume schemes to each subsystem; \cite{hu_2017, hiptmair_2018} treat the electromagnetic part via finite element exterior calculus.
-The scheme proposed in this work lies in the second category and by construction satisfies the divergence-free constraint at the discrete level.
-Nevertheless, we do not pursue the structure-preserving property while focusing on the asymptotic-preserving property in this work.
+  \begin{remark}
+    Structure preservation, that is, respecting inherent constraints satisfied by solution
+    fields on the discrete level, is a major concern in discretization of
+    (\ref{equ:euler-maxwell-rescaled}) or related reduced models. Important constraints
+    are the positivity of densities, entropy inequalities, and zero divergence of the
+    $\mathbf{B}$-field. Two main approaches can be distinguished:
+
+    \begin{enumerate}[label={(\roman{*})}]
+    \item The first is to combine all equations into one hyperbolic system of conservation
+      laws and apply finite volume methods. Such numerical methods are rather simple to
+      implement and also computationally efficient. The challenge is to ensure the
+      stability and the divergence constraint, which requires suitable numerical fluxes
+      and limiters. Schemes that are provably positive, entropy-stable, or divergence-free
+      have been constructed, see~\cite{wu_2018, wu_2023a, wu_2023b, kumar_2011,
+        fuchs_2009}, and the references therein.
+    \item The second class of numerical methods tackles the electromagnetic and fluid
+      subsystems separately. The rationale behind such a splitting strategy is that rather
+      mature schemes for these parts are available. In particular, the divergence
+      constraint can be easily handled by finite element exterior calculus. Yet the
+      implementation of coupled solvers is usually complicated. To name some related work,~\cite{fuchs_2009} 
+      applies dedicated finite volume schemes to each subsystem;~\cite{hu_2017, hiptmair_2018} 
+      treat the electromagnetic part via finite element
+      exterior calculus.
+    \end{enumerate}
+    The scheme proposed in this work belongs to the second category and by construction
+    satisfies the divergence-free constraint at the discrete level. Yet, our focus is on
+    the AP property and not primarily on structure preservation.
+  \end{remark}
+  % It is worth mentioning that an important aspect of devising numerical schemes is
+  % the structure-preserving property which is concerned with keeping some constraints at
+  % the discrete level. In this context, some typical constraints are the positivity of
+  % densities and pressures, the entropy inequality, zero divergence of the
+  % $\mathbf{B}$-field, etc. There are in general two ways of numerically approaching the
+  % coupled system (\ref{equ:euler-maxwell-rescaled}) or its reduced models, e.g. the
+  % magnetohydrodynamic (MHD) equations. The first approach is to lump all the equations
+  % into one hyperbolic system of conservation laws and apply finite volume methods. Such
+  % numerical methods are rather simple to implement and also computationally
+  % efficient. Complications typically go to ensuring the stability and the divergence
+  % constraint which requires suitable numerical fluxes and limiters. Schemes that are
+  % provably positive, entropy-stable, or divergence-free have been constructed, see
+  %~\cite{wu_2018, wu_2023a, wu_2023b, kumar_2011, fuchs_2009} and references therein. The
+  % second class of numerical methods handles the electromagnetic part and the fluid part
+  % separately. The rationale behind such a splitting strategy is that dedicated solvers for
+  % subsystems are rather mature. Particularly, the divergence constraint can be easily
+  % handled by finite element exterior calculus. Yet the implementation of coupled solvers
+  % is usually complicated. To name some related work,~\cite{fuchs_2009} applies dedicated
+  % finite volume schemes to each subsystem;~\cite{hu_2017, hiptmair_2018} treat the
+  % electromagnetic part via finite element exterior calculus. The scheme proposed in this
+  % work lies in the second category and by construction satisfies the divergence-free
+  % constraint at the discrete level. Nevertheless, we do not pursue the
+  % structure-preserving property while focusing on the asymptotic-preserving property in
+  % this work.
 }
 
-\subsection{Quasi-neutral Limit}
-\label{sec:quasi-neutral_limit}
+\subsection{Quasi-neutral Limit}\label{sec:quasi-neutral_limit}
 
 The Debye length $\lambda_D$ is the characteristic length over which the local net charge is
-shielded, see \cite[Sec.~1.4]{chen2016} for the underlying physics. In many situations, it
+shielded, see~\cite[Sec.~1.4]{chen2016} for the underlying physics. In many situations, it
 has a very small value compared to the reference length scale: the typical $\lambda_D$ for
 gas discharge and Tokamak fusion reactors is $10^{-4}$ meter, for interstellar medium, the
-magnitude is about $1$ meter \cite[Chapt.~20]{Blandford_2013}. Then the quasi-neutrality
+magnitude is about $1$ meter~\cite[Chapt.~20]{Blandford_2013}. Then the quasi-neutrality
 assumption $\rho = \sum_* q_*n_* \approx 0$ is justified, which is typical of the limit
 model.  Formally we obtain it by setting the rescaled Debye length $\lambda$ to zero in
-\eqref{resc}:
+~\eqref{resc}:
 \begin{center}
@@
 \begin{minipage}{0.3\textwidth}
-  \begin{subequations}
-    \label{limit}
+  \begin{subequations}\label{limit}
 \begin{align}
@@
   sequence. This topic is beyond the scope of this paper. Readers are referred to
-  \cite[Chapt.~2]{remi_2014} \cite{Peng_2008} for the quasi-neutral limit of the
-  Maxwell-Euler system and \cite{mark_1995, Eckhaus_1980} for the general theory.
+ ~\cite[Chapt.~2]{remi_2014}~\cite{Peng_2008} for the quasi-neutral limit of the
+  Maxwell-Euler system and~\cite{mark_1995, Eckhaus_1980} for some general theory.
 \end{remark}
@@
 
-We consider a simply-connected domain $\Omega$ comprising two sub-domains $\Omega_P$
+We consider a simply-connected domain $\Omega$ comprising two subdomains $\Omega_P$
 (\textbf{p}lasma domain) and $\Omega_N$ (\textbf{n}on-conducting domain). They represent
@@
 covers fundamental experimental set-ups, for example, those studying wall-stabilized
-electric arcs \cite{GGF05}, but is also adequate for a range of industrial plasmas, for
-instance, for those occurring in high-voltage circuit breakers \cite{SEE15,MGU20}.
+electric arcs~\cite{GGF05}, but is also adequate for a range of industrial plasmas, for
+instance, for those occurring in high-voltage circuit breakers~\cite{SEE15,MGU20}.
 
@@
   The treatment of electrodes as open boundary is a simplification. For more realistic
-  electrode modelling, see \cite{godyak_1990, parker_1993}.
+  electrode modelling, see~\cite{godyak_1990, parker_1993}.
 \end{remark}
@@
   potential $\varphi$ satisfying $\mathbf{E}_t = \nabla_\Gamma\varphi$. One needs to
-  include co-homology vector fields \cite{Hiptmair_2021}.
+  include co-homology vector fields~\cite{Hiptmair_2021}.
 \end{remark}
@@
 consequence of Amp\`{e}re's law (\ref{equ:ampere_ins_limit}). However,
-\eqref{equ:gaus_D_ins_limit} is essential for the well-posedness of the problem \cite[][p.
+\eqref{equ:gaus_D_ins_limit} is essential for the well-posedness of the problem~\cite[][p.
 7]{ana_2010}. Obviously, the degeneracy of Gauss's law for the $\mathbf{D}$-field in the
@@
 boundary condition gives vanishing $\psi$. The importance of this reformulation will
-become clear through numerical experiments, see Section~\ref{sec:numerical_experiment}.
+become clear through numerical experiments, see Sec.~\ref{sec:numerical_experiment}.
 
@@
   has to be removed. This is mainly achieved by utilizing implicit time-stepping for
-  certain terms. As is summarized by \cite{degond_2017}, AP schemes aim to bridge several
+  certain terms. As is summarized by~\cite{degond_2017}, AP schemes aim to bridge several
   sets of equations describing the system in different regimes, rather than to alleviate
@@
   In the following sections, we first briefly discuss the 1D scheme for the Maxwell-Euler
-  system devised by \cite{degond_2012} on which our work us built. This section also
+  system devised by~\cite{degond_2012} on which our work us built. This section also
   serves as a preliminary case study such that readers can better understand the 3D
@@
   of the other mesh and that each vertex of one mesh lies inside of a cell of the other
-  mesh} \cite[][Sec.~2]{weiland_2003}. Examples are shown in Fig.~\ref{fig:cartesian}.
+  mesh}~\cite[][Sec.~2]{weiland_2003}. Examples are shown in Fig.~\ref{fig:cartesian}.
 
@@
 In three dimensions, the meshes are constructed by extruding the 2D meshes vertically
-along one axis in a staggered manner \cite[][Sec.~3.1]{Marrone_2001}. See an example in
+along one axis in a staggered manner~\cite[][Sec.~3.1]{Marrone_2001}. See an example in
 Fig.~\ref{fig:2d-extrusion}. In this way, the meshes are composed of prisms. This
@@
 approximating the material laws on the discrete level (which is the so-called discrete
-Hodge operator \cite{hip_1999, bossavit1999}), as will be shown in Section~\ref{sec:fit}.
+Hodge operator~\cite{hip_1999, bossavit1999}), as will be shown in Sec.~\ref{sec:fit}.
 
@@
   alternative approach is barycenter-based dual meshes, which are not restricted to an
-  acute-angle triangulation \cite[][Sec.~4.2]{Marrone_2001}.
+  acute-angle triangulation~\cite[][Sec.~4.2]{Marrone_2001}.
 \end{remark}
@@
     orientation}, which has a slightly different definition, see
-  \cite[][Sec.~3.1]{tonti_2002}.}. The notion is illustrated in
+ ~\cite[][Sec.~3.1]{tonti_2002}.}. The notion is illustrated in
 Fig.~\ref{fig:orientation}. For the entities of the dual mesh $\Tilde{\mathcal{M}}$, we
@@
 \begin{figure}
+    \begin{subfigure}[v]{\textwidth}
         \centering
@@
         \includegraphics[scale=0.3]{./figures/dual_mesh.png}
-    \caption{Primal mesh (left) and dual mesh (right).}
-    \label{fig:primal_dual_meshes}
+        \caption{Cylinder geometry
+          % \todo{Move primal-dual mesh pair from Fig.~9 here.}
+        }\label{fig:primal_dual_meshes}
+    \end{subfigure}
+    \begin{subfigure}[v]{\textwidth}
+        \centering
+        \includegraphics[scale=0.25]{./figures/cube_mesh_primal.png}
+        \hspace{1.2cm}
+        \includegraphics[scale=0.25]{./figures/cube_mesh_dual.png}
+        \caption{Cuboid geometry
+          % \todo{Move primal-dual mesh pair from Fig.~9 here.}
+        }\label{fig:primal_dual_meshes_cube}
+    \end{subfigure}
+    \caption{Examples of primal (left) and dual meshes (right)}
+    \label{fig:examples_primal_dual_mehes}
 \end{figure}
@@
 We utilize FIT to discretize Maxwell's equations. This framework was originally proposed
-in \cite{weiland_1977} and can be regarded as a generalization of Yee's FDTD method
+in~\cite{weiland_1977} and can be regarded as a generalization of Yee's FDTD method
 \cite{yee_1966}. To derive a discrete model for the (rescaled) Maxwell equations
@@
 approximation error is introduced due to the implicit assumption that vector fields are
-piecewise constant, see the analysis in \cite[][Sec.~3.2]{Marrone_2001}.
+piecewise constant, see the analysis in~\cite[][Sec.~3.2]{Marrone_2001}.
 
@@
   i.e. $\mathbb{M}_{\epsilon}$ is diagonal. A more schematic illustration relies on the
-  language of discrete exterior calculus (DEC), see \cite{bossavit1999, teixeira_1999,
+  language of discrete exterior calculus (DEC), see~\cite{bossavit1999, teixeira_1999,
     hip_1999}.
@@
 The electromagnetic boundary $\partial\Omega = \Gamma_C\cup \Gamma_I$ is resolved by the
-primal mesh $\mathcal{M}$. As is mentioned in Section~\ref{sec:BC}, the zero-magnetic-flux
+primal mesh $\mathcal{M}$. As is mentioned in Sec.~\ref{sec:BC}, the zero-magnetic-flux
 boundary condition $\mathbf{B}\cdot \mathbf{n}$ is equivalent to
@@
 true on the discrete level. We associate with each primal vertex $P_k \in \partial\Omega$
-a scalar value $\varphi_k$. Therefore, the boundary conditions (see Section~\ref{sec:BC})
+a scalar value $\varphi_k$. Therefore, the boundary conditions (see Sec.~\ref{sec:BC})
 are discretized in the following way:
@@
 
-In Section~\ref{sec:reform_continuous}, we have proposed a stabilization of the Maxwell
+In Sec.~\ref{sec:reform_continuous}, we have proposed a stabilization of the Maxwell
 system in the non-conducting domain $\Omega_N$ by introducing a Lagrange multiplier. On
@@
         \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \\ 
-        \lambda^2 \partial_t \mathbf{D} - \nabla \times \mathbf{H} + \colorbox{orange!20}{$\nabla \psi$} &= 0, \\
+        \lambda^2 \partial_t \mathbf{D} - \nabla \times \mathbf{H} + \colorbox{orange!20}{$\nabla\psi$} &= 0, \\
         \nabla \cdot \mathbf{D} &= 0. 
@@
 \begin{equation} \label{equ:euler_grid} 
-    \dot{\overline{\mathbf{U}}}_k + \frac{1}{|\Tilde{V}_k|}\sum_{l:\Tilde{A}_l\in\partial \Tilde{V}_k} |\Tilde{A}_l|\underbrace{\frac{1}{|\Tilde{A}_l|}\iint_{\Tilde{A}_l}\mathbf{f}(\mathbf{U})\cdot \mathbf{n}_l \text{d}A}_{:= \overline{\mathbf{f}}_l \approx \mathbf{f}^\text{num}_l} = \underbrace{\frac{1}{|\Tilde{V}_k|}\iiint_{\Tilde{V}_k} \mathbf{RHS} \text{d}V}_{:= \overline{\mathbf{RHS}}_k},\ \ k = 1,2,\cdots,N_{\Tilde{V}}^P
+    \dot{\overline{\mathbf{U}}}_k + \frac{1}{|\Tilde{V}_k|}\sum_{l:\Tilde{A}_l\in\partial \Tilde{V}_k} |\Tilde{A}_l|\underbrace{\frac{1}{|\Tilde{A}_l|}\iint_{\Tilde{A}_l}\mathbf{f}(\mathbf{U})\cdot \mathbf{n}_l \text{d}A}_{:= \overline{\mathbf{f}}_l \approx \mathbf{f}^\text{num}_l} = \underbrace{\frac{1}{|\Tilde{V}_k|}\iiint_{\Tilde{V}_k} \mathbf{RHS} \text{d}V}_{:= \overline{\mathbf{RHS}}_k},\ \ k = 1,2,\ldots,N_{\Tilde{V}}^P
 \end{equation}
@@
 $\Tilde{V}_k$. Classical numerical fluxes include the Lax-Friedrich flux, the Rusanov
-flux, and the Engquist-Osher flux, see \cite[][pp. 44-46]{mishra_2019}. We end up with the
+flux, and the Engquist-Osher flux, see~\cite[][Sec.~12.6]{leveque_2002}. We end up with the
 semi-discretized equation:
 \begin{equation}
-  \dot{\overline{\mathbf{U}}}_k + \frac{1}{|V_k|}\sum_{l:\Tilde{A}_l\in\partial \Tilde{V}_k} |\Tilde{A}_l| \mathbf{f}^\text{num}\left(\overline{\mathbf{U}}_k, \overline{\mathbf{U}}_{\hat{k}(k,l)}, \mathbf{n}_l\right) = \overline{\mathbf{RHS}}_k,\ \  k = 1,2,\cdots,N_{\Tilde{V}}^P.
+  \dot{\overline{\mathbf{U}}}_k + \frac{1}{|V_k|}\sum_{l:\Tilde{A}_l\in\partial \Tilde{V}_k} |\Tilde{A}_l| \mathbf{f}^\text{num}\left(\overline{\mathbf{U}}_k, \overline{\mathbf{U}}_{\hat{k}(k,l)}, \mathbf{n}_l\right) = \overline{\mathbf{RHS}}_k,\ \  k = 1,2,\ldots,N_{\Tilde{V}}^P.
     \label{equ:fvm}
@@
 
-\subsubsection{Reconstruction of Lorentz Force} \label{sec:recon_lorentz_f}
+\subsubsection{Reconstruction of Lorentz Force}\label{sec:recon_lorentz_f}
 
@@
 \end{itemize}
-We adopt the principle of least square fitting and reconstruct a \emph{constant} vector
+We adopt the principle of least squares fitting and reconstruct a \emph{constant} vector
 field inside each cell. For a cell $\Tilde{V}$ with $N_A$ faces with areas
@@
 \begin{equation*}
-    \mathbb{K} = [A_1\mathbf{n}_1, A_2\mathbf{n}_2, \cdots, A_{N_A}\mathbf{n}_{N_A}]^T,\ \ \ \mathbf{f} = [f_1, f_2, \cdots, f_{N_A}]^T,
+    \mathbb{K} = [A_1\mathbf{n}_1, A_2\mathbf{n}_2, \ldots, A_{N_A}\mathbf{n}_{N_A}]^T,\ \ \ \mathbf{f} = [f_1, f_2, \ldots, f_{N_A}]^T,
 \end{equation*}
@@
 \citep{perot_2000}, finite-entity-based methods, etc., which potentially can achieve
-higher-order accuracy. See \cite[][Sec.~3.4.4]{fuchs_2021} and the references therein.
+higher-order accuracy. See~\cite[][Sec.~3.4.4]{fuchs_2021} and the references therein.
 
@@
 
-The boundary conditions for the Euler system (see Section~\ref{sec:BC}) are implemented by
-the approach of ghost cells \cite[][Chapt.~7]{leveque_2007}, i.e. extending the domain by a
+The boundary conditions for the Euler system (see Sec.~\ref{sec:BC}) are implemented by
+the approach of ghost cells~\cite[][Chapt.~7]{leveque_2007}, i.e. extending the domain by a
 layer of virtual cells with prescribed variables. In our case, the ghost cells at the open
@@
 \end{align}
-where $\ast \in \{e, i, \dots\}$ and $\bm{f}^\text{mass}$ denotes the mass flux which is defined in Section~\ref{sec:discrete_euler}.
-By $[\cdots]_k$ we mean taking the $k$-th component of both sides of the equation.
+where $\ast \in \{e, i, \dots\}$ and $\bm{f}^\text{mass}$ denotes the mass flux which is defined in Sec.~\ref{sec:discrete_euler}.
+By $[\ldots]_k$ we mean taking the $k$-th component of both sides of the equation.
 We have the following boundary conditions:
@@
 
-Our work extends the 1D scheme proposed in \cite{degond_2012} to three
+Our work extends the 1D scheme proposed in~\cite{degond_2012} to three
 dimensions. Therefore, it is supposed to be compatible with the original 1D scheme when
@@
 is linked to the 1D. For the sake of presentation, we discuss the one-fluid model of
-\cite{degond_2012}, for which ions are assumed immobile and only the motion of electrons is
+~\cite{degond_2012}, for which ions are assumed immobile and only the motion of electrons is
 considered.
@@
 transverse translation invariance and rotational symmetry, we can ``project'' all the d.o.f. onto the
-$z$-axis. The idea is sketched in in Fig.~\ref{fig:1d_reduction}.
+$z$-axis. The idea is sketched in Fig.~\ref{fig:1d_reduction}.
 
@@
 
-In \cite{degond_2012}, the authors investigate a 1D Maxwell-Euler system by assuming
+In~\cite{degond_2012}, the authors investigate a 1D Maxwell-Euler system by assuming
 vanishing traverse derivatives. For further simplicity, a transverse mode is considered,
@@
 
-\subsubsection{1D Fully Discrete Plasma Model}
-\label{sec:1d_fully_discrete_model}
-
-The fully discrete scheme proposed in \cite{degond_2012} is given below. From now on, the
+\subsubsection{1D Fully Discrete Plasma Model}\label{sec:1d_fully_discrete_model}
+
+The fully discrete scheme proposed in~\cite{degond_2012} is given below. From now on, the
 superscript $m$ for any variable indicates the time step. The scheme is built on a uniform
@@
 implicitness of the electric field in the Lorentz force is shown to be necessary in
-\cite{fabre_1992} for the Euler-Poisson system. In \cite{degond_2012}, based on the
+~\cite{fabre_1992} for the Euler-Poisson system. In~\cite{degond_2012}, based on the
 linearized stability analysis, the author shows that the full-implicit treatment of the
@@
 Taking the cue from the formulas of Sec.~\ref{sec:1d_fully_discrete_model} and combining the
-3D FIT/DEC-FVM framework presented in Section~\ref{sec:spatial_discretization} and the
+3D FIT/DEC-FVM framework presented in Sec.~\ref{sec:spatial_discretization} and the
 time-stepping scheme shown below, we propose the following semi-implicit fully-discrete AP
@@
 \begin{subequations}
+  \label{eq:32}
 \begin{align}
@@
 the sake of simplicity we have confine the presentation of the collision term
-(\ref{equ:R_coll_ap}) (\ref{equ:Q_coll_ap}) to the two-species case .
+(\ref{equ:R_coll_ap}) (\ref{equ:Q_coll_ap}) to the two-species case.
 
@@
 \begin{remark}
-When applying the ``projection to one dimension"
-  described in Section~4.1.1, the fully discrete 3D AP scheme (32) collapses to (31)
-  discretization proposed in \cite{degond_2012}. This is not a coincidence, because
-  recovering of (31) under dimensional reduction has guided our construction.
+  When applying the ``projection to one dimension'' described in Sec.~\ref{sec:projection_to_1d}, the fully
+  discrete 3D AP scheme~(\ref{equ:maxwell_faraday_ap})-(\ref{equ:Q_coll_ap}) collapses to the scheme of~\cite{degond_2012}
+  presented in Sec.~\ref{sec:1d_fully_discrete_model}. This is not a coincidence, because recovering that scheme under
+  dimensional reduction has guided our construction.
 \end{remark}
@@
   The formula (\ref{equ:discrete_ohm}) functions as Ohm's law on the discrete
-  level. Matrix $\mathbb{M}_\sigma^m$ can be treated as a ``conductivity" matrix. In the
+  level. Matrix $\mathbb{M}_\sigma^m$ can be treated as a ``conductivity'' matrix. In the
   quasi-neutral limit $\lambda \rightarrow 0$ we lose control of the $\mathbf{E}$-field
@@
 We conduct numerical tests based on the geometric setting and boundary conditions as
-presented in Section~\ref{sec:BC}. The primal-dual mesh pair
+presented in Sec.~\ref{sec:BC}. The primal-dual mesh pair
 $(\mathcal{M}, \Tilde{\mathcal{M}})$ is generated as explained in
-\cite[][Chapt.~1]{fuchs_2021}. An instance is shown in Fig.~\ref{fig:primal_dual_meshes}. We
-consider a two-fluid plasma model, which comprises electrons and ions. We set the mass
+~\cite[][Chapt.~1]{fuchs_2021}. Examples are shown in Fig.~\ref{fig:examples_primal_dual_mehes}. 
+We consider a two-fluid plasma model, which comprises electrons and ions. We set the mass
 ratio $\varepsilon_e := m_e / m_i = 10^4$ and the collision parameter
@@
 \end{align*}
-which is nothing but the 1D model in Section~\ref{sec:projection_to_1d} after further
-dropping $u_x, B_y, E_x$. We compare the results produced by the 1D scheme (see Section
-\ref{sec:1d_fully_discrete_model}) and those produced by the 3D scheme (see Section
-\ref{sec:3d_ap_scheme}) restricted to the $z$-axis. The following initial conditions are
+which is nothing but the 1D model in Sec.~\ref{sec:projection_to_1d} after further
+dropping $u_x, B_y, E_x$. We compare the results produced by the 1D scheme (see Sec.
+~\ref{sec:1d_fully_discrete_model}) and those produced by the 3D scheme (see Sec.
+~\ref{sec:3d_ap_scheme}) restricted to the $z$-axis. The following initial conditions are
 used for both models
@@
     \caption{Case I, $\lambda = 1$: Comparison of 1D two-fluid model and of 3D results (at
-      time $t = 5 \times 10^{-4}$ projected onto the $z$-axis. The simulations were both
+      time $t = 5 \times 10^{-4}$) projected onto the $z$-axis. The simulations were both
       conducted on meshes with 64 cells along the $z$-axis. No friction terms were taken
-      into account. \review{The 3D result is generated under the setting in Fig.~2
-  and restricted to the z-axis. They are slightly different from
-  the 1D results possibly due to the impact of the outer boundary of the
-  3D domain.}}
-    \label{fig:z_axis_reduction}
+      into account. \review{The 3D fields are computed for the axi-symmetric geometry
+        shown in Fig.~\ref{fig:domain_sketch} and then restricted to the $z$-axis. They
+        slightly differ from 1D results, possibly due to the impact of the cut-off boundary of the 3D domain.}}\label{fig:z_axis_reduction}
 \end{figure}
@@
 \review{
-\subsection{Case II: 3D cuboid domain (convergence study for a range of $\lambda$)} 
-The problem setting follows the one depicted in Fig.~\ref{fig:domain_sketch} while we adopt a cuboid domain, see Fig.~\ref{fig:cube_domain_sketch}.
-Under this setting, we decompose the domain with structured Cartesian meshes and benefit from simpler error computation.
-The initial conditions are
+  \subsection{Case II, convergence: 3D ``cuboid domain''}
+
+  We rely on the geometry from Fig.~\ref{fig:cube_geo} and the setting in Fig.~\ref{fig:domain_sketch}. The computational
+  domain is equipped with structured Cartesian meshes in Fig.~\ref{fig:primal_dual_meshes_cube}. The initial conditions are
 \begin{equation*}
-    n_\ast(\mathbf{x}, 0) = 1, \ \ \  p_\ast(\mathbf{x},0) = 1, \ \ \forall \mathbf{x}\in\Omega, \ast \in \{e, i\}
+    n_\ast(\mathbf{x}, 0) = 1, \ \ \  p_\ast(\mathbf{x},0) = 1, \ \ \forall \mathbf{x}\in\Omega, \ast \in \{e, i\},
 \end{equation*}
-and zero for the other variables.
-We set $\varphi(\mathbf{x}, t)|_{\Gamma_C^-} = 0, \varphi(\mathbf{x}, t)|_{\Gamma_C^+} = 10\times t$, that is, one electrode is grounded and a linear voltage is applied on the other electrode.
-The results are computed for the final time $t = 0.01$.
-The scheme is tested at different mesh resolutions and the convergence rates are estimated.
-Tab.~\ref{tab:grid_study_cube} lists the errors for the $\mathbf{E}$-field, $\mathbf{B}$-field, and electron densities where the reference solutions are generated by a sufficiently fine mesh with $2^{18} = 262144$ primal cells.
-The results show uniform convergence over $0\leq \lambda \leq 1$, a justification of the AP property.
-It is expected that the convergence rate does not exceed one since the reconstruction of the electromagnetic field discussed in Section~\ref{sec:recon_lorentz_f} is only of first order and the numerical flux used for solving the Euler equations is also of first order.
-The $1/2$-order reduction observed in the $L^2$-error of the $\mathbf{E}$-field and the electron density is possibly the consequence of singularity in the solution due to the interface of different types of boundary conditions (electrodes and insulating boundary).
+and zero for the other variables. We set
+$\varphi(\mathbf{x}, t)|_{\Gamma_C^-} = 0, \varphi(\mathbf{x}, t)|_{\Gamma_C^+} = 10\times
+t$, that is, one electrode is grounded and a ramp voltage is applied on the other
+electrode. The results are computed for final time $t = 0.01$.  The scheme is tested for
+different mesh resolutions and the convergence rates are
+estimated. Tab.~\ref{tab:grid_study_cube} lists the errors for the $\mathbf{E}$-field,
+$\mathbf{B}$-field, and electron densities with reference solutions generated on a
+sufficiently fine mesh with $2^{18} = 262144$ primal cells. The results confirm uniform
+algebraic convergence over $0\leq \lambda \leq 1$, a vindication of the AP property. It is
+natural that the convergence rate does not exceed $1$, since the reconstruction of the
+electromagnetic field discussed in Sec.~\ref{sec:recon_lorentz_f} is only of first
+order and the numerical flux used for solving the Euler equations is also of first
+order. The $1/2$-order reduction observed for the $L^2$-error of the $\mathbf{E}$-field
+and the electron density is possibly the consequence of singularities of the solution due
+to abutting different types of boundary conditions (electrodes and insulating boundary).
 \begin{table}[!ht]
@@
     }
-    \caption{\review{Case II:  $L^1$ and $L^2$ errors of the $\mathbf{E}$-field, the $\mathbf{B}$-field, and the electron density and their convergence rates for a range of $\lambda$.
-The reference solution is computed at a sufficiently mesh resolution with $2^{18} = 262144$ primal cells.}}
+    \caption{\review{Case II:  $L^1$ and $L^2$ errors of the $\mathbf{E}$-field, the
+        $\mathbf{B}$-field, and the electron density and their convergence rates for
+        different values of $\lambda$. The reference solution is computed at a sufficient mesh
+        resolution with $2^{18} = 262144$ primal cells.}
+    }
     \label{tab:grid_study_cube}}
@@
 }
-\begin{figure}
-    \centering
-
-    \begin{minipage}{0.3\textwidth}
-    \vspace{-2cm}
-        \resizebox{\textwidth}{!}{
-            \begin{tikzpicture}[>=stealth]
-                % Electrode 1
-                \coordinate (O1) at (0,0);
-                \draw[violet,very thick] (O1) rectangle ++(2,2) node[midway, blue] {Electrode};
-                \fill[blue, opacity=0.2] (O1) rectangle ++(2,2);
-
-                % Electrode 2
-                \coordinate (O2) at (4.5,1);
-                \draw[violet,very thick] (O2) rectangle ++(2,2) node[midway, red] {Electrode};
-                \fill[blue, opacity=0.2] (O2) rectangle ++(2,2);
-
-                % Connecting lines
-                \coordinate (N1) at  ([shift={(0,2)}]O1);
-                \coordinate (E1) at  ([shift={(2,0)}]O1);
-                \coordinate (NE1) at ([shift={(2,2)}]O1);
-                \coordinate (N2) at  ([shift={(0,2)}]O2); 
-                \coordinate (E2) at  ([shift={(2,0)}]O2);
-                \coordinate (NE2) at ([shift={(2,2)}]O2); 
-                \draw[violet] (O1) -- (O2);
-                \draw[violet] (N1) -- (N2);
-                \draw[violet] (E1) -- (E2);
-                \draw[violet] (NE1) -- (NE2);
-
-                 % Plasma
-                \node at (barycentric cs:NE1=1,O2=1) {Plasma}; 
-                \fill[red, opacity=0.2] (O2) rectangle ++(2,2);
-
-                \coordinate (_O1) at (-0.5, -0.5);
-                \coordinate (_O2) at (4.0,0.5);
-                \draw[very thick] (_O1) rectangle ++(3,3);
-                \draw[very thick] (_O2) rectangle ++(3,3);
-                \coordinate (_N1) at  ([shift={(0,3)}]_O1);
-                \coordinate (_E1) at  ([shift={(3,0)}]_O1);
-                \coordinate (_NE1) at ([shift={(3,3)}]_O1);
-                \coordinate (_N2) at  ([shift={(0,3)}]_O2); 
-                \coordinate (_E2) at  ([shift={(3,0)}]_O2);
-                \coordinate (_NE2) at ([shift={(3,3)}]_O2); 
-                \draw[very thick] (_O1) -- (_O2);
-                \draw[very thick] (_N1) -- (_N2);
-                \draw[very thick] (_E1) -- (_E2);
-                \draw[very thick] (_NE1) -- (_NE2);
-
-                \draw[-to] (barycentric cs:_N1=1,_NE1=1,_N2=1,_NE2=1) to[out=90,in=0] ([shift={(-0.5,0.5)}]barycentric cs:_N1=1,_NE1=1,_N2=1,_NE2=1) node[left, gray] {Insulator};
-                % Axes
-                 \begin{scope}[shift={(6.5,-0.9)}]
-                    \draw[blue, -to] (0,0) -- (20:0.7) node[right]{\small $z$};
-                    \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
-                    \draw[blue, -to] (0,0) -- (0.7,0) node[below]{\small $y$};
-                \end{scope}
-            \end{tikzpicture}
-        }
-    \end{minipage}
-    \hspace{1cm}
-    \includegraphics[scale=0.2]{./figures/cube_mesh_primal.png}
-    \hspace{1cm}
-    \includegraphics[scale=0.2]{./figures/cube_mesh_dual.png}
-    \caption{\review{Case II: domain sketch (left); primal mesh (middle); dual mesh (right).}}
-    \label{fig:cube_domain_sketch}
-\end{figure}
 
@@
 
-We stick to the setting in Section~\ref{sec:BC} and use the following initial conditions
+We stick to the setting in Fig.~\ref{fig:domain_sketch} and the mesh in Fig.~\ref{fig:primal_dual_meshes} using the following initial conditions
 \begin{equation*}
@@
 outer radius of 1.5.
-
-\begin{remark}
-  Such an initial state is compatible with the boundary conditions and the quasi-neutrality
-  condition $\rho = 0$, which means no initial layer and boundary layer in the sense of
-  perturbation theory will arise when $\lambda \rightarrow 0$.
-\end{remark}
 
@@
     \end{subfigure}
-    \caption{Case III: Snapshots of the $\mathbf{E}$-field, $\mathbf{B}$-field, and $\mathbf{u}_e$ for different $\lambda$ at $t = 0.5$. } 
+    \caption{Case III: Snapshots of the $\mathbf{E}$-field, $\mathbf{B}$-field, and $\mathbf{u}_e$ for different values of $\lambda$ at $t = 0.5$. } 
     \label{fig:3d_vec_field_E_B_ue}
@@
 whereas for a smaller $\lambda$ the system quickly reaches a steady state. It is
-consistent with the fact that $\lambda$ characterizes the time scale of the
+consistent with the fact that $\lambda$ characterizes the timescale of the
 electromagnetic field. From a different perspective, it is a reflection of the shielding
@@
 inertia. Furthermore, the structure-preserving property of our scheme is revealed by the
-exact balance of the currents at $\Gamma^+_C$ and $\Gamma^-_C$ \cite{Hiptmair_2021}, as is
+exact balance of the currents at $\Gamma^+_C$ and $\Gamma^-_C$~\cite{Hiptmair_2021}, as is
 shown in the bottom plot in Fig.~\ref{fig:origin-data_vs_time}.
@@
 
-The stabilization proposed in Section~\ref{sec:reform-discrete} is essential to achieve
+The stabilization proposed in Sec.~\ref{sec:reform-discrete} is essential to achieve
 good results when $\lambda$ tends to zero. As is shown in
@@
 \review{
-\subsection{Case IV: 3D bended cylindrical domain}
-To demonstrate the performance of the proposed scheme on more general three-dimensional settings, we bend the cylinder domain in Case III (see Fig.~\ref{fig:domain_sketch}), as is shown in Fig.~\ref{fig:bend_domain_sketch}.
-The same initial and boundary conditions as Case III are used.
-The numerical results of the electromagnetic field for $\lambda = 0$ and $1$ are displayed in Fig.~\ref{fig:3d_vec_field_E_B_bend}.
-It can be observed the qualitatively similar phenomena as Case~III (see Fig.~\ref{fig:3d_vec_field_E_B_ue}), that is, the electromagnetic field in the bulk of the domain develops much faster at small $\lambda$.}
+  \subsection{Case IV: 3D curved cylindrical domain}
+
+  To demonstrate the performance of the proposed scheme in more general three-dimensional
+  settings, we bend the cylinder domain in Case III (see Fig.~\ref{fig:domain_sketch}), as
+  is shown in Fig.~\ref{fig:bend_domain_sketch}. The same initial and boundary conditions
+  as in Case III are imposed. Primal and dual meshes with straight edges and flat faces
+  are generated by extrusion in the direction of a bent central axis.
+
+  The numerical approximations of the electromagnetic fields for $\lambda = 0$ and $1$ are
+  displayed in Fig.~\ref{fig:3d_vec_field_E_B_bend}. We observe qualitatively similar
+  phenomena to Case~III (see Fig.~\ref{fig:3d_vec_field_E_B_ue}), that is, the
+  electromagnetic field in the bulk of the domain develops much faster at small
+  $\lambda$.}
 \begin{figure}
@@
     \includegraphics[scale=0.2]{./figures/dual_mesh_bend.png}
-    \caption{\review{Case IV: domain sketch (left); primal mesh (middle); dual mesh (right).}}
+    \caption{\review{Case IV: geometry (left); primal mesh (middle); dual mesh (right).}}
     \label{fig:bend_domain_sketch}
@@
 $\lambda$. (iii) The alignment of primal-dual meshes at the boundary entails cut-off cells
-and auxiliary unknowns have to be introduced. iv) A lumping trick is applied to the
+and auxiliary unknowns have to be introduced. (iv) A lumping trick is applied to the
 conductivity matrix (relating the electric current and the electric field) to enhance
@@
 
+% \todo{Carefully check references!}
+
 \bibliography{ref}
